### 2012-04-30 inst/examples/Sethi.Rmd
Sethi example seperately

`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, refresh=1 or`

``` {r  echo=FALSE }
opts_knit$set(upload.fun = socialR::flickr.url)
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
````

# Sethi Model
 * author Carl Boettiger, <cboettig@gmail.com>
 * license: CC0

 Implements a numerical version of the SDP described in `r knitcitations::citep("10.1016/j.jeem.2004.11.005")`.

Clear the workspace and load package dependencies: 
``` {r  setup, echo=FALSE}
rm(list=ls())   
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
````

### Define parameters

``` {r }
gridsize <- 100   # gridsize (discretized population)
sigma_g <- 0.2    # Noise in population growth
sigma_m <- 0.2     # noise in stock assessment measurement
sigma_i <- 0.2     # noise in implementation of the quota
````

we'll use log normal noise functions. 
For Reed, only `z_g` will be random.
Sethi et al will add the other forms

``` {r  noise_dists}
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
````

Chose the state equation / population dynamics function

``` {r }
f <- BevHolt
````

Note that the `pdg_control` pacakge already has a definition for the `BevHolt` function, (typing the function name prints the function)

``` {r }
BevHolt
````

That is, \( f(x,h) = \frac{A x}{1 + B x} \)

Of course we could pass in any custom function of stocksize `x`, harvest `h` and parameter vector `p` in place of `BevHolt`.  Note that we would need to write this function explicitly so that it can take vector values of `x` (i.e. uses `sapply`), an annoying feature of `R` for users comming from Matlab.

We must now define parameters for the function.  Note that the positive stationary root of the model is given by \( (A-1)/B \), which we'll store for future reference as `K`.

``` {r }
pars <- c(1.5, 0.05)
K <- (pars[1] - 1)/pars[2]
````

and we use a harvest-based profit function with default parameters

``` {r  profit}
profit <- profit_harvest(price=1, c0 = 0.01) 
````

The profit_harvest function has the form \( \Pi = h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x} \), conditioned on \( h > x \) and \(x > 0 \).  Note that the R code defines a function from another function using a trick known as a _closure_.  Again we could write a custom profit function as long as it can take a vector stock size `x` and a scalar harvest level `h`.  Details for provided functions can be found in the manual, i.e. `?profit_harvest`.

Now we must set up the discrete grids for stock size and havest levels (which will use same resolution as for stock), in order to calculate the SDP solution.   Here we set the gridsize to 100.

``` {r  grid}
x_grid <- seq(0, 2 * K, length = 100)  
h_grid <- x_grid  
````

### Calculate the transition matrix (with noise in growth only)

We calculate the stochastic transition matrix for the probability of going from any state \(x_t \) to any other state \(x_{t+1}\) the following year, for each possible choice of harvest \( h_t \).  This provides a look-up table for the dynamic programming calculations.

In the Sethi case, computing the distribution over multiple sources of noise is actually quite difficult.  Simulation turns out to be more efficient than numerically integrating over each distribution.  This code parallelizes the operation over four cores, but can be scaled to an arbitrary cluster. Since we're focused on the Reed example for the moment, we can ignore this step.

``` {r  parallel}
require(snowfall) 
sfInit(parallel=TRUE, cpu=4)
SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=999)
````
Note that `SDP_Mat` is specified from the calculation above, as are our grids and our profit function. `OptTime` is the stopping time.  `xT` specifies a boundary condition at the stopping time. A reward for meeting this boundary must be specified for it to make any difference.  `delta` indicates the economic discount rate. Again, details are in the function documentation.

### Find the optimum by dynamic programming

Bellman's algorithm to compute the optimal solution for all possible trajectories.

``` {r  find_dp_opt }
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
                     profit, delta=0.05, reward=0)
````

### Simulate

Now we'll simulate 100 replicates of this stochastic process under the Reed optimal harvest policy determined above.

``` {r  simulate }
sims <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i)
})
````

The forward simulation algorithm needs an initial condition `x0` which we set equal to the carrying capacity, as well as our population dynamics `f`, parameters `pars`, grids, and noise coefficients.  Recall in the Reed case only `z_g`, growth, is stochastic.

## Summarize and plot the results

R makes it easy to work with this big replicate data set.  We make data tidy (melt), fast (data.tables), and nicely labeled.

``` {r  tidy}
dat <- melt(sims, id=names(sims[[1]]))  
dt <- data.table(dat)
setnames(dt, "L1", "reps") # names are nice
````

### Plots

Let's begin by looking at the dynamics of a single replicate. The line shows Reed's S, the level above which the stock should be harvested (where catch should be the difference between stock and S).  To confirm that this policy is being followed, note that harvesting only occurs when the stock is above this line, and harvest is proportional to the amount by which it is above.  Change the replicate `reps==` to see the results from a different replicate.

``` {r  p0}
ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, fishstock)) +
  geom_abline(intercept=opt$S, slope = 0) +
  geom_line(aes(time, harvest), col="darkgreen") 
````

This plot summarizes the stock dynamics by visualizing the replicates. Reed's S shown again, along with the dotted line showing the allee threshold, below which the stock will go to zero (unless rescued stochastically).

``` {r  p1}
p1 <- ggplot(dt) + geom_abline(intercept=opt$S, slope = 0) + 
  geom_abline(intercept=xT, slope = 0, lty=2) 
p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.2)
````

We can also look at the harvest dynamics:

``` {r  p2}
p1 + geom_line(aes(time, harvest, group = reps), alpha = 0.1, col="darkgreen")
````

This strategy is supposed to be a constant-escapement strategy. We can visualize the escapement:

``` {r  p3}
p1 + geom_line(aes(time, escapement, group = reps), alpha = 0.1, col="darkgrey")
````

### Visualizing the optimal policy
Note that when the boundary is sufficiently far away, i.e. for the first couple timesteps, the optimal policy is stationary.  The optimal policy is shown here over time, where the color indicates the harvest recommended for each possible stock value at that time (shown on the vertical axis).  Note that below a certain stock value, harvesting is not recommended and the dots turn red (Reed's constant escapement rule!)  However, at very low values, harvesting starts again (orange dots), because of the allee effect - these populations are doomed anyway, so may as well fish all that remains.

Note that interestingly, populations just below the allee threshold are given the chance to be rescued stochastically early on - that small chance that they recover is worth the expected loss.  The "no-harvest" zones stand out clearly in the red areas of this graph.

``` {r  policy, fig.width=9}
policy <- melt(opt$D)
policy_zoom <- subset(policy, x_grid[Var1] < max(dt$fishstock) )
p5 <- ggplot(policy_zoom) + 
  geom_point(aes(Var2, (x_grid[Var1]), col=h_grid[value])) + 
  labs(x = "time", y = "fishstock") +
  scale_colour_gradientn(colours = rainbow(4)) +
  geom_abline(intercept=opt$S, slope = 0) +
  geom_abline(intercept=xT, slope=0, lty=2)
p5
````

The harvest intensity is limited by the stock size.

``` {r  policy2, fig.width=10}
p6 <- ggplot(policy_zoom) + 
  geom_point(aes(Var2, (x_grid[Var1]), col=x_grid[Var1] - h_grid[value])) + 
  labs(x = "time", y = "fishstock") +
  scale_colour_gradientn(colours = rainbow(4)) +
  geom_abline(intercept=opt$S, slope = 0) +
  geom_abline(intercept=xT, slope=0, lty=2)
p6 + geom_line(aes(time, fishstock, group = reps), alpha = 0.1, data=dt)
````

``` {r biblio, include=FALSE}
knitcitations::bibliography()
````

### 2012-04-30 R/determine_SDP_matrix.R

@@ -124,7 +124,7 @@ SDP_by_simulation <- function(f, p, x_grid, h_grid, z_g, z_m, z_i, reps = 999){
   SDP_Mat <- sfLapply(h_grid, function(h){ 
     mat <- sapply(x_grid, function(x){
       x_t1 <- replicate(reps, z_g() * z_i() * f(x, z_m() * h, p)) 
-      a <- bin( x_t1, binwidth=bw, range=c(lower, upper))$count
+      a <- mybin( x_t1, binwidth=bw, range=c(lower, upper))$count
       a / sum(a) 
     })
     t(mat)
@@ -132,4 +132,72 @@ SDP_by_simulation <- function(f, p, x_grid, h_grid, z_g, z_m, z_i, reps = 999){
   SDP_Mat
 }
 
+
+
+
+
+# Bin data from old version of ggplot2
+# This function powers \code{\link{stat_bin}}R
+#
+# @keyword internal
+bin <- function(x, weight=NULL, binwidth=NULL, origin=NULL, breaks=NULL, range=NULL, width=0.9, drop = FALSE) {
+  
+  if (is.null(weight))  weight <- rep(1, length(x))
+  weight[is.na(weight)] <- 0
+
+  if (is.null(range))    range <- range(x, na.rm = TRUE, finite=TRUE)
+  if (is.null(binwidth)) binwidth <- diff(range) / 30
+
+  if (is.integer(x)) {
+    bins <- x
+    x <- sort(unique(bins))
+    width <- width    
+  } else if (diff(range) == 0) {
+    width <- width
+    bins <- x
+  } else { # if (is.numeric(x)) 
+    if (is.null(breaks)) {
+      if (is.null(origin)) {
+        breaks <- fullseq(range, binwidth)        
+      } else {
+        breaks <- seq(origin, max(range) + binwidth, binwidth)
+      }
+    }
+    bins <- cut(x, sort(breaks), include.lowest=TRUE)
+    left <- breaks[-length(breaks)]
+    right <- breaks[-1]
+    x <- (left + right)/2
+    width <- diff(breaks)
+  }
+
+  results <- data.frame(
+    count = as.numeric(tapply(weight, bins, sum, na.rm=TRUE)),
+    x = x,
+    width = width
+  )
+
+  res <- within(results, {
+    count[is.na(count)] <- 0
+    density <- count / width / sum(count, na.rm=TRUE)
+    ncount <- count / max(count, na.rm=TRUE)
[…]

### 2012-05-01 inst/examples/Sethi.Rmd
Sethi example corrected

@@
-`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, refresh=1 or`
+`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, refresh=2 or`
 
-``` {r  echo=FALSE }
+``` {r  echo=FALSE, cache=FALSE }
 opts_knit$set(upload.fun = socialR::flickr.url)
@@
 require(data.table)
+rm(list=ls())
 ````
 
-### Define parameters
+Define noise parameters
 
 ``` {r }
-gridsize <- 100   # gridsize (discretized population)
-sigma_g <- 0.2    # Noise in population growth
-sigma_m <- 0.2     # noise in stock assessment measurement
-sigma_i <- 0.2     # noise in implementation of the quota
+sigma_g <- 0.1    # Noise in population growth
+sigma_m <- 0.1     # noise in stock assessment measurement
+sigma_i <- 0.1     # noise in implementation of the quota
 ````
@@
 For Reed, only `z_g` will be random.
-Sethi et al will add the other forms
+Sethi et al will add the other forms of noise:
 
@@
 This code parallelizes the operation over four cores, but can be scaled to an arbitrary cluster.
-Since we're focused on the Reed example for the moment, we can ignore this step.
 
@@
 
-Now we'll simulate 100 replicates of this stochastic process under the Reed optimal harvest policy determined above.
+Now we'll simulate 100 replicates of this stochastic process under the optimal harvest policy determined above.
 
@@
 The forward simulation algorithm needs an initial condition `x0` which we set equal to the carrying capacity, as well as our population dynamics `f`, parameters `pars`, grids, and noise coefficients.
-Recall in the Reed case only `z_g`, growth, is stochastic.
+Recall in the Reed case only `z_g`, growth, is stochastic, while in the Sethi example we now have three forms of stochasticity -- growth, measurement, and implementation.
 
@@
 
-``` {r  p0}
+``` {r  onerep }
 ggplot(subset(dt,reps==1)) +
@@
 
-This plot summarizes the stock dynamics by visualizing the replicates.
-Reed's S shown again, along with the dotted line showing the allee threshold, below which the stock will go to zero (unless rescued stochastically).
+This plot summarizes the stock dynamics by visualizing the replicates. Reed's S shown again.
 
-``` {r  p1}
-p1 <- ggplot(dt) + geom_abline(intercept=opt$S, slope = 0) + 
-  geom_abline(intercept=xT, slope = 0, lty=2) 
+``` {r  all}
+p1 <- ggplot(dt) + geom_abline(intercept=opt$S, slope = 0) 
 p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.2)
@@
 
-``` {r  p2}
+``` {r  harvestplot}
 p1 + geom_line(aes(time, harvest, group = reps), alpha = 0.1, col="darkgreen")
@@
 
-``` {r  p3}
+``` {r  escapement}
 p1 + geom_line(aes(time, escapement, group = reps), alpha = 0.1, col="darkgrey")
@@
   scale_colour_gradientn(colours = rainbow(4)) +
-  geom_abline(intercept=opt$S, slope = 0) +
-  geom_abline(intercept=xT, slope=0, lty=2)
+  geom_abline(intercept=opt$S, slope = 0) 
 p5
@@
   scale_colour_gradientn(colours = rainbow(4)) +
-  geom_abline(intercept=opt$S, slope = 0) +
-  geom_abline(intercept=xT, slope=0, lty=2)
+  geom_abline(intercept=opt$S, slope = 0) 
 p6 + geom_line(aes(time, fishstock, group = reps), alpha = 0.1, data=dt)
@@
 
-``` {r biblio, include=FALSE}
+# References
+
+``` {r biblio, echo=FALSE}
 knitcitations::bibliography()

### 2012-05-01 R/determine_SDP_matrix.R

@@ -119,7 +119,7 @@ SDP_by_simulation <- function(f, p, x_grid, h_grid, z_g, z_m, z_i, reps = 999){
 
   bw <- x_grid[2] - x_grid[1]
   lower <-x_grid[1]
-  upper <- x_grid[length(x_grid)-1]
+  upper <- x_grid[length(x_grid)] + bw
 
   SDP_Mat <- sfLapply(h_grid, function(h){ 
     mat <- sapply(x_grid, function(x){
@@ -140,7 +140,7 @@ SDP_by_simulation <- function(f, p, x_grid, h_grid, z_g, z_m, z_i, reps = 999){
 # This function powers \code{\link{stat_bin}}R
 #
 # @keyword internal
-bin <- function(x, weight=NULL, binwidth=NULL, origin=NULL, breaks=NULL, range=NULL, width=0.9, drop = FALSE) {
+mybin <- function(x, weight=NULL, binwidth=NULL, origin=NULL, breaks=NULL, range=NULL, width=0.9, drop = FALSE) {
   
   if (is.null(weight))  weight <- rep(1, length(x))
   weight[is.na(weight)] <- 0
@@ -195,8 +195,8 @@ bin <- function(x, weight=NULL, binwidth=NULL, origin=NULL, breaks=NULL, range=N
 # @seealso \code{\link{reshape}{round_any}}
 fullseq <- function(range, size) {
   seq(
-    round_any(range[1], size, floor), 
-    round_any(range[2], size, ceiling), 
+    plyr::round_any(range[1], size, floor), 
+    plyr::round_any(range[2], size, ceiling), 
     by=size
   )
 }

### 2012-05-01 inst/examples/Sethi.Rmd
some formatting corrections, (thank goodness for caching)

@@
 
-That is, \( f(x,h) = \frac{A x}{1 + B x} \)
+That is, \\( f(x,h) = \frac{A x}{1 + B x} \\)
 
@@
 
-We must now define parameters for the function.  Note that the positive stationary root of the model is given by \( (A-1)/B \), which we'll store for future reference as `K`.
+We must now define parameters for the function.  Note that the positive stationary root of the model is given by \\( \frac{A-1}{B} \\), which we'll store for future reference as `K`.
 
@@
 
-The profit_harvest function has the form \( \Pi = h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x} \), conditioned on \( h > x \) and \(x > 0 \).
+The `profit_harvest` function has the form \\( \Pi = h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x} \\), conditioned on \\( h > x \\) and \\(x > 0 \\).
 Note that the R code defines a function from another function using a trick known as a _closure_.
@@
 
-We calculate the stochastic transition matrix for the probability of going from any state \(x_t \) to any other state \(x_{t+1}\) the following year, for each possible choice of harvest \( h_t \).
+We calculate the stochastic transition matrix for the probability of going from any state \\(x_t \\) to any other state \\(x_{t+1}\\) the following year, for each possible choice of harvest \\( h_t \\).
 This provides a look-up table for the dynamic programming calculations.
@@
 ### Visualizing the optimal policy
+
 Note that when the boundary is sufficiently far away, i.e.
@@
 The optimal policy is shown here over time, where the color indicates the harvest recommended for each possible stock value at that time (shown on the vertical axis).
-Note that below a certain stock value, harvesting is not recommended and the dots turn red (Reed's constant escapement rule!)  However, at very low values, harvesting starts again (orange dots), because of the allee effect - these populations are doomed anyway, so may as well fish all that remains.
-
-Note that interestingly, populations just below the allee threshold are given the chance to be rescued stochastically early on - that small chance that they recover is worth the expected loss.
-The "no-harvest" zones stand out clearly in the red areas of this graph.
+Observe that the solution does not correspond to a simple Reed-style rule.
 
@@
 
-``` {r biblio, echo=FALSE}
-knitcitations::bibliography()
+``` {r biblio, echo=FALSE, results="asis"}
+I(knitcitations::bibliography())
 ````

### 2012-05-01 inst/examples/Sethi.Rmd
avoid repeat citation

@@
 })
+knitcitations::cleanbib()
 ````

### 2012-05-02 inst/examples/Sethi.Rmd
updated

--- 2012-05-01 inst/examples/Sethi.Rmd
@@
 ``` {r  echo=FALSE, cache=FALSE }
+render_jekyll()
 opts_knit$set(upload.fun = socialR::flickr.url)

### 2012-05-02 inst/examples/policycosts/stochastic_norms.Rmd
single source for norms

`ro fig.width=10, fig.height=7, message=FALSE, comment=NA, cache=FALSE, verbose=TRUE or`

``` {r setup, include=FALSE, cache=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
options(device = function(width=5, height=5) pdf(NULL, width = width, height = height))
````

# Asymmetric Policy Costs 
 * author Carl Boettiger, <cboettig@gmail.com>
 * license: CC0

## Setup the system

``` {r setupsource}
rm(list=ls())   
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)

delta <- 0.05     # economic discounting rate
OptTime <- 50     # stopping time
gridsize <- 50   # gridsize (discretized population)
sigma_g <- 0.2    # Noise in population growth
sigma_m <- 0.     # noise in stock assessment measurement
sigma_i <- 0.     # noise in implementation of the quota
reward <- 0       # bonus for satisfying the boundary condition

## @knitr noise_dists
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
z_i <- function() rlnorm(1,  0, sigma_i) # mean 1

f <- BevHolt                # Select the state equation
pars <- c(1.5, 0.05)             # parameters for the state equation
K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
xT <- 0                     # boundary conditions
x0 <- K

## @knitr profit_
profit <- profit_harvest(price = 10, c0 = 30, c1 = 10)

## @knitr create_grid_
x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
h_grid <- seq(0.01, 0.8 * K, length = gridsize)

## @knitr reed_sdp
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                     profit, delta, reward=reward)
````

``` {r fees}
L1 <- function(c2) function(h, h_prev)  c2 * abs(h - h_prev) 
free_increase <- function(c2) function(h, h_prev)  c2 * abs(min(h - h_prev, 0)) # increasing harvest is free
free_decrease <- function(c2) function(h, h_prev)  c2 * max(h - h_prev, 0) # decreasing harvest is free
fixed <-  function(c2) function(h, h_prev) c2
L2 <- function(c2) function(h, h_prev)  c2 * (h - h_prev) ^ 2
````

Solve the policy cost for the specified penalty function

``` {r policycost_optim}
c2 <- 4
penalty <- free_decrease(c2)
policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                    profit, delta, reward, penalty = penalty)
cache=FALSE
````

### Simulate

Now we'll simulate 100 replicates of this stochastic process under the optimal harvest policy determined above.  We use a modified simulation function that can simulate an alternate policy (the Reed optimum, where policy costs are zero, `opt$D` ) and a focal policy, `policycost$D`

``` {r simulate_policy, cache=cache}
sims <- lapply(1:100, function(i)
  simulate_optim(f, pars, x_grid, h_grid, x0, policycost$D, z_g, z_m, z_i, opt$D, profit=profit, penalty=penalty)
  )
````

Make data tidy (melt), fast (data.tables), and nicely labeled.

``` {r tidy, cache=cache}
dat <- melt(sims, id=names(sims[[1]]))  
dt <- data.table(dat)
setnames(dt, "L1", "reps") # names are nice
````

### Plots

A single replicate, alternate dynamics show the Reed optimum, while harvest/fishstock show the impact of having policy costs.

``` {r rep1, cache=cache}
ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, alternate)) +
  geom_line(aes(time, fishstock), col="darkblue") +
  geom_line(aes(time, harvest), col="purple") + 
  geom_line(aes(time, harvest_alt), col="darkgreen") 
````

A second replicate

``` {r rep2, cache=cache}
ggplot(subset(dt,reps==2)) +
  geom_line(aes(time, alternate)) +
  geom_line(aes(time, fishstock), col="darkblue") +
  geom_line(aes(time, harvest), col="purple") + 
  geom_line(aes(time, harvest_alt), col="darkgreen") 
````

Profits

``` {r rep1profit, cache=cache}
ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, profit_fishing)) +
  geom_line(aes(time, policy_cost), col="darkblue") 
````

We can visualize the equilibrium policy for each possible harvest:

``` {r policy, cache=cache}
policy <- sapply(1:length(h_grid), function(i) policycost$D[[i]][,1])
ggplot(melt(policy)) + 
  geom_point(aes(h_grid[Var2], (x_grid[Var1]), col=h_grid[value]-h_grid[Var2])) + 
    labs(x = "prev harvest", y = "fishstock") +
      scale_colour_gradientn(colours = rainbow(4)) 
````

Here we plot previous harvest against the recommended harvest, coloring by stocksize.  Note this swaps the y axis from above with the color density.  Hence each x-axis value has all possible colors, but they map down onto a subset of optimal harvest values (depending on their stock).

``` {r harvestchanges, cache=cache}
policy <- sapply(1:length(h_grid), function(i) policycost$D[[i]][,1])
ggplot(melt(policy)) + 
  geom_point(aes(h_grid[Var2], (h_grid[value]), col = x_grid[Var1]), position=position_jitter(w=.005,h=.005), alpha=.5) + 
    labs(x = "prev harvest", y = "harvest") +
      scale_colour_gradientn(colours = rainbow(4)) 
````

### 2012-05-02 inst/examples/policycosts/stochastic_norms.Rmd
updated with profits

@@
 
-# Asymmetric Policy Costs 
+# Policy Costs 
  * author Carl Boettiger, <cboettig@gmail.com>
@@
 c2 <- 4
-penalty <- free_decrease(c2)
+penalty <- fixed(c2)
 policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
@@
 
-### Plots
+# Plots
 
@@
 
-Profits
+## Profits
 
@@
   geom_line(aes(time, policy_cost), col="darkblue")
+
+````
+
+``` {r policycost, cache=cache}
+costs <- dt[ , sum(policy_cost), by=reps]
+profits <-dt[ , sum(profit_fishing), by=reps]
+
+qplot(costs$V1)
+qplot(profits$V1)
+qplot(profits-costs$V1)
 ````

### 2012-05-02 inst/examples/policycosts/stochastic_norms.Rmd
fixed third profit plot
updated fixed costs

@@
 ## @knitr profit_
-profit <- profit_harvest(price = 10, c0 = 30, c1 = 10)
+profit <- profit_harvest(price = 10, c0 = 30, c1 = 0)
 
@@
 free_decrease <- function(c2) function(h, h_prev)  c2 * max(h - h_prev, 0) # decreasing harvest is free
-fixed <-  function(c2) function(h, h_prev) c2
+fixed <-  function(c2) function(h, h_prev) c2 * as.numeric( !(h == h_prev) )
 L2 <- function(c2) function(h, h_prev)  c2 * (h - h_prev) ^ 2
@@
 
-``` {r policycost_optim}
-c2 <- 4
+``` {r policycost_optim }
+c2 <- 4.0
 penalty <- fixed(c2)
@@
 qplot(profits$V1)
-qplot(profits-costs$V1)
+qplot(profits$V1-costs$V1)
 ````

### 2012-05-02 R/policy_costs.R

@@ -62,7 +62,7 @@ optim_policy <- function(SDP_Mat, x_grid, h_grid, OptTime, xT, profit,
       out <- sapply(1:gridsize, function(j){
         value <- max(V1[j,], na.rm = T) # each col is a diff h, max over these
         index <- which.max(V1[j,])  # store index so we can recover h's
-        penalty_free <- V0[j, index]
+        penalty_free <- V0[j, index] # The profit from fishing before adjustment costs are paid
         c(value, index, penalty_free) # returns both profit value & index of optimal h.  
       })
       # Sets V[t+1] = max_h V[t] at each possible state value, x

### 2012-05-02 inst/examples/policycosts/exact_npv.Rmd
updated exact npv calc

`ro warning=FALSE, message=FALSE, comment=NA, cache=TRUE-->
``` {r setup, include=FALSE }
opts_knit$set(upload.fun = socialR::flickr.url)
````

 * author Carl Boettiger, <cboettig@gmail.com>
 * license: CC0

## Setup the system
``` {r libraries }
rm(list=ls())   
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
````

``` {r pars  }
delta <- 0.05     # economic discounting rate
OptTime <- 50     # stopping time
gridsize <- 100   # gridsize (discretized population)
sigma_g <- 0.2    # Noise in population growth
sigma_m <- 0.     # noise in stock assessment measurement
sigma_i <- 0.     # noise in implementation of the quota
reward <- 0       # bonus for satisfying the boundary condition
````

``` {r noise_dists }
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
````

``` {r BevHolt_ }
f <- BevHolt                # Select the state equation
pars <- c(1.5, 0.05)             # parameters for the state equation
K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
xT <- 0                     # boundary conditions
x0 <- K
````

``` {r profit_ }
profit <- profit_harvest(price = 10, c0 = 30, c1 = 0)
````

``` {r create_grid_ }
x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
h_grid <- seq(0.01, 0.8 * K, length = gridsize)  
````

## Declare the different penalty norms

``` {r fees }
L1 <- function(c2) function(h, h_prev)  c2 * abs(h - h_prev) 
asymmetric <- function(c2) function(h, h_prev)  c2 * max(h - h_prev, 0)
fixed <-  function(c2) function(h, h_prev) c2 * as.numeric( !(h == h_prev) )
L2 <- function(c2) function(h, h_prev)  c2 * (h - h_prev) ^ 2
free_increase <- function(c2) function(h, h_prev)  c2 * abs(min(h - h_prev, 0)) # increasing harvest is free
````

Calculate the transition matrix and intialize the the list of penalty functions and cost levels we will be looping over.
``` {r  }
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
penaltyfns <- list(L2=L2, L1=L1, asy=asymmetric, fixed=fixed, asy2=free_increase)
c2 <- seq(0, 8, length.out = 9)
````

This can take a while, so we use explicit parallelization, 
``` {r  }
require(snowfall)
sfInit(cpu=5, parallel=T)
sfLibrary(pdgControl)
sfExportAll()
````

## Loop over penalty functions and magnitudes

``` {r  }
policies <- 
sfSapply(penaltyfns, function(penalty){
  policies <- 
  sapply(c2, function(c2){
      policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                        profit, delta, reward, penalty = penalty(c2))
      i <- which(x_grid > K)[1]
      max(policycost$penalty_free_V[i,]) 
  })
})
````
Note that `optim_policy` has been updated to return the equilibrium value of profits from fish harvests before the adjustment costs have been paid, `penalty_free_V`.  This containst the values for all possible states, we simply evaluate it at the carrying capacity (which is our initial condition.)  The index in `x_grid` that corresponds to the carrying capacity (initial condition) `i` indicates this.

Quadratic costs on fishing effort have to be done separately,
``` {r  }
quad <- 
  sapply(c2, function(c2){
  effort_penalty = function(x,h) .1*c2*h/x
  policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                        profit, delta, reward, penalty = fixed(0), 
                        effort_penalty)
      i <- which(x_grid > K)[1]
      max(policycost$penalty_free_V[i,]) # chooses the most sensible harvest in t=1
})
dat <- cbind(policies, quad)
````

Tidy up the data and plot the net present value (before the penalty has been paid) relative to that achieved when managed without a penalty.  
``` {r  }
npv0 <- dat[1,3] 
dat <- data.frame(c2=c2,dat)
dat <- melt(dat, id="c2")
ggplot(dat, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
````

### 2012-05-11 inst/examples/value_of_information.Rmd
added value of information example

--- 2012-05-02 inst/examples/Sethi.Rmd
@@
-`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, refresh=2 or`
+`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, refresh=2 fig.width=10, fig.height=10 or`
 
@@
 
-# Sethi Model
+# Calculating the value of information
  * author Carl Boettiger, <cboettig@gmail.com>
@@
  Implements a numerical version of the SDP described in `r knitcitations::citep("10.1016/j.jeem.2004.11.005")`.
+ Compute the optimal solution under different forms of uncertainty and compare the results.
 
-Clear the workspace and load package dependencies: 
 ``` {r  setup, echo=FALSE}
@@
 Define noise parameters
-
-``` {r }
-sigma_g <- 0.1    # Noise in population growth
-sigma_m <- 0.1     # noise in stock assessment measurement
-sigma_i <- 0.1     # noise in implementation of the quota
-````
-
-we'll use log normal noise functions. 
-For Reed, only `z_g` will be random.
-Sethi et al will add the other forms of noise:
-
-``` {r  noise_dists}
-z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
-z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
-````
 
@@
 
-### Calculate the transition matrix (with noise in growth only)
+# Scenarios:
 
@@
 Simulation turns out to be more efficient than numerically integrating over each distribution.
-This code parallelizes the operation over four cores, but can be scaled to an arbitrary cluster.
 
-``` {r  parallel}
-require(snowfall) 
-sfInit(parallel=TRUE, cpu=4)
-SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=999)
+## No Uncertainty
+
+``` {r noisefns}
+sigma_g <- 0.0    # Noise in population growth
+sigma_m <- 0.0     # noise in stock assessment measurement
+sigma_i <- 0.0     # noise in implementation of the quota
+z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
+z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
+z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
 ````
-Note that `SDP_Mat` is specified from the calculation above, as are our grids and our profit function.
-`OptTime` is the stopping time.
-`xT` specifies a boundary condition at the stopping time.
-A reward for meeting this boundary must be specified for it to make any difference.
-`delta` indicates the economic discount rate.
-Again, details are in the function documentation.
+Find the transition matrix
 
-### Find the optimum by dynamic programming
+``` {r  SDP_Mat}
+SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
+````
 
-Bellman's algorithm to compute the optimal solution for all possible trajectories.
+Find the optimum solution
 
@@
 
-### Simulate
-
-Now we'll simulate 100 replicates of this stochastic process under the optimal harvest policy determined above.
+Simulate
 
 ``` {r  simulate }
-sims <- lapply(1:100, function(i){
-  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i)
+sims_known <- lapply(1:100, function(i){
+  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
 })
@@
 
-The forward simulation algorithm needs an initial condition `x0` which we set equal to the carrying capacity, as well as our population dynamics `f`, parameters `pars`, grids, and noise coefficients.
-Recall in the Reed case only `z_g`, growth, is stochastic, while in the Sethi example we now have three forms of stochasticity -- growth, measurement, and implementation.
+## Growth uncertainty
+
+``` {r }
+sigma_g <- 0.1    # Noise in population growth
+sigma_m <- 0.0     # noise in stock assessment measurement
+sigma_i <- 0.0     # noise in implementation of the quota
+z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
+z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
+z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
+````
+Find the transition matrix
+
+``` {r }
+SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
+````
+
+Find the optimum solution
+
+``` {r }
+opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
+                     profit, delta=0.05, reward=0)
+````
+
+Simulate
+
+``` {r }
+sims_g <- lapply(1:100, function(i){
+  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
+})
+````
+
+## Growth & stock measurement uncertainty
+
+``` {r }
+sigma_g <- 0.1    # Noise in population growth
+sigma_m <- 0.1     # noise in stock assessment measurement
+sigma_i <- 0.0     # noise in implementation of the quota
+z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
+z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
+z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
+````
+
+Find the transition matrix.  Use the simulation method to account for the extra uncertainties
+
+``` {r }
+require(snowfall) 
+sfInit(parallel=TRUE, cpu=4)
+SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=999)
+````
+
+Find the optimum solution
+
+``` {r }
+opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
+                     profit, delta=0.05, reward=0)
+````
+
+Simulate
+
+``` {r }
+sims_gm <- lapply(1:100, function(i){
+  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
+})
+````
+
+## Growth, stock measurement & implementation uncertainty
+
+``` {r }
+sigma_g <- 0.1    # Noise in population growth
+sigma_m <- 0.1     # noise in stock assessment measurement
+sigma_i <- 0.1     # noise in implementation of the quota
+z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
+z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
+z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
+````
+
+Find the transition matrix.  Use the simulation method to account for the extra uncertainties
+
+``` {r }
+require(snowfall) 
+sfInit(parallel=TRUE, cpu=4)
+SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=999)
+````
+
+Find the optimum solution
+
+``` {r }
+opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
+                     profit, delta=0.05, reward=0)
+````
+
+Simulate
+
+``` {r }
+sims_gmi <- lapply(1:100, function(i){
+  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
+})
+````
 
@@
 ``` {r  tidy}
-dat <- melt(sims, id=names(sims[[1]]))  
+
+sims <- list(known = sims_known, growth = sims_g, growth_stock = sims_gm, growth_stock_harvest = sims_gmi)
+
+dat <- melt(sims, id=names(sims_known[[1]]))  
 dt <- data.table(dat)
-setnames(dt, "L1", "reps") # names are nice
+setnames(dt, c("L2", "L1"), c("reps", "uncertainty")) # names are nice
 ````
@@
   geom_abline(intercept=opt$S, slope = 0) +
-  geom_line(aes(time, harvest), col="darkgreen") 
+  geom_line(aes(time, harvest), col="darkgreen") + 
+  facet_wrap(~uncertainty) 
 ````
@@
 p1 <- ggplot(dt) + geom_abline(intercept=opt$S, slope = 0) 
-p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.2)
+p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.2) + facet_wrap(~uncertainty)
 ````
@@
 ``` {r  harvestplot}
-p1 + geom_line(aes(time, harvest, group = reps), alpha = 0.1, col="darkgreen")
+p1 + geom_line(aes(time, harvest, group = reps), alpha = 0.1, col="darkgreen") + facet_wrap(~uncertainty)
 ````
@@
 ``` {r  escapement}
-p1 + geom_line(aes(time, escapement, group = reps), alpha = 0.1, col="darkgrey")
+p1 + geom_line(aes(time, escapement, group = reps), alpha = 0.1, col="darkgrey") + facet_wrap(~uncertainty)
 ````
 
-### Visualizing the optimal policy
+``` {r }
+ggplot(subset(dt,reps==1)) +
+  geom_line(aes(time, profit_fishing)) +
+  geom_line(aes(time, policy_cost), col="darkblue") + facet_wrap(~uncertainty)
 
-Note that when the boundary is sufficiently far away, i.e.
-for the first couple timesteps, the optimal policy is stationary.
-The optimal policy is shown here over time, where the color indicates the harvest recommended for each possible stock value at that time (shown on the vertical axis).
-Observe that the solution does not correspond to a simple Reed-style rule.
-
-``` {r  policy, fig.width=9}
-policy <- melt(opt$D)
-policy_zoom <- subset(policy, x_grid[Var1] < max(dt$fishstock) )
-p5 <- ggplot(policy_zoom) + 
-  geom_point(aes(Var2, (x_grid[Var1]), col=h_grid[value])) + 
-  labs(x = "time", y = "fishstock") +
-  scale_colour_gradientn(colours = rainbow(4)) +
-  geom_abline(intercept=opt$S, slope = 0) 
-p5
 ````
 
-The harvest intensity is limited by the stock size.
+``` {r }
+profits <-dt[ , sum(profit), by=c("reps", "uncertainty")] 
+ggplot(profits) + geom_histogram(aes(V1)) + facet_wrap(~uncertainty)
+````
 
-``` {r  policy2, fig.width=10}
-p6 <- ggplot(policy_zoom) + 
-  geom_point(aes(Var2, (x_grid[Var1]), col=x_grid[Var1] - h_grid[value])) + 
-  labs(x = "time", y = "fishstock") +
-  scale_colour_gradientn(colours = rainbow(4)) +
-  geom_abline(intercept=opt$S, slope = 0) 
-p6 + geom_line(aes(time, fishstock, group = reps), alpha = 0.1, data=dt)
+Summary stats
+
+``` {r }
+profits[, mean(V1), by=uncertainty]
+profits[, sd(V1), by=uncertainty]
 ````

### 2012-05-11 R/ForwardSimulate.R

@@ -15,11 +15,13 @@
 #'  assessment of stock size
 #' @param z_i a function which returns a random number from a distribution 
 #' for the implementation uncertainty in quotas 
+#' @param profit function, if known
 #' @return a data frame with the time, fishstock, harvested amount,
 #'  and what the escapement ("unharvested"). 
 #' @export
 ForwardSimulate <- function(f, pars, x_grid, h_grid, x0, D, z_g,
-                            z_m=function(x) 1, z_i = function(x) 1){
+                            z_m=function(x) 1, z_i = function(x) 1, 
+                            profit=NULL){
   # initialize variables with initial conditions
   OptTime <- dim(D)[2]    # Stopping time
   x_h <- numeric(OptTime) # population dynamics with harvest
@@ -28,7 +30,8 @@ ForwardSimulate <- function(f, pars, x_grid, h_grid, x0, D, z_g,
   
   s <- x_h # also track escapement
   x <- x_h # What would happen with no havest
-  
+  p <- numeric(OptTime)
+ 
     
   ## Simulate through time ##
   for(t in 1:(OptTime-1)){
@@ -43,12 +46,13 @@ ForwardSimulate <- function(f, pars, x_grid, h_grid, x0, D, z_g,
     z <- z_g() 
     # population grows
     x_h[t+1] <- z * f(x_h[t], h[t], pars) # with havest
-    s[t]   <- x_h[t] - q_t # anticipated escapement
+    s[t+1]   <- x_h[t] - q_t # anticipated escapement
     x[t+1]   <- z * f(x[t], 0, pars) # havest-free dynamics
-  }
+    p[t] <- profit(x_h[t], h[t])
+}
   # formats output 
   data.frame(time = 1:OptTime, fishstock = x_h, harvest = h,
-             unharvested = x, escapement = s) 
+             unharvested = x, escapement = s, profit = p) 
 }
 
 

### 2012-05-11 inst/examples/policycosts/exact_npv.Rmd

@@
 penaltyfns <- list(L2=L2, L1=L1, asy=asymmetric, fixed=fixed, asy2=free_increase)
-c2 <- seq(0, 8, length.out = 9)
+c2 <- seq(0, 22, length.out = 30)
 ````

### 2012-05-11 inst/examples/value_of_information.Rmd
value of information
snowfall only once

@@
-`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, refresh=2 fig.width=10, fig.height=10 or`
+`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10 or`
 
@@
 ``` {r }
-require(snowfall) 
-sfInit(parallel=TRUE, cpu=4)
 SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=999)

### 2012-05-11 inst/examples/value_of_information.Rmd

@@
-`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10 or`
+`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10, cache.path="run2/" or`
 
@@
 require(snowfall) 
-sfInit(parallel=TRUE, cpu=4)
+sfInit(parallel=TRUE, cpu=16)
 SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=999)

### 2012-05-11 inst/examples/value_of_information.Rmd
highlighting

@@
-`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10, cache.path="run2/" or`
+`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10, refresh=1 or`
 
@@
 ``` {r noisefns}
-sigma_g <- 0.0    # Noise in population growth
+sigma_g <- 0.01    # Noise in population growth
 sigma_m <- 0.0     # noise in stock assessment measurement
@@
 ``` {r }
-sigma_g <- 0.1    # Noise in population growth
+sigma_g <- 0.15    # Noise in population growth
 sigma_m <- 0.0     # noise in stock assessment measurement
@@
 ``` {r }
-sigma_g <- 0.1    # Noise in population growth
-sigma_m <- 0.1     # noise in stock assessment measurement
-sigma_i <- 0.0     # noise in implementation of the quota
-z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
+sigma_m <- 0.15     # noise in stock assessment measurement
 z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
-z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
 ````
@@
 ``` {r }
-sigma_g <- 0.1    # Noise in population growth
-sigma_m <- 0.1     # noise in stock assessment measurement
-sigma_i <- 0.1     # noise in implementation of the quota
-z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
+sigma_i <- 0.15     # noise in implementation of the quota
 z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
@@
 ggplot(subset(dt,reps==1)) +
-  geom_line(aes(time, profit_fishing)) +
-  geom_line(aes(time, policy_cost), col="darkblue") + facet_wrap(~uncertainty)
+  geom_line(aes(time, profit))  + facet_wrap(~uncertainty)
 

### 2012-05-11 inst/examples/value_of_information.Rmd
value of information

@@
  Implements a numerical version of the SDP described in `r knitcitations::citep("10.1016/j.jeem.2004.11.005")`.
- Compute the optimal solution under different forms of uncertainty and compare the results.
+ Compute the optimal solution under different forms of uncertainty.
+The true uncertainty is much smaller than that assumed, just a small uncertainty in growth.
+We compare the case where the uncertainty is equal to this tiny growth uncertainty to policies derived under much greater uncertainty assumptions, and see how the resulting profit varies.
 
@@
 sigma_g <- 0.15    # Noise in population growth
-sigma_m <- 0.0     # noise in stock assessment measurement
-sigma_i <- 0.0     # noise in implementation of the quota
 z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
-z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
 ````
@@
 
-Simulate
+Simulate.  The real world doesn't have as much uncertainty as we do in our knowledge of the state.
 
 ``` {r }
+sigma_g <- 0.05    # Noise in population growth
+z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
 sims_g <- lapply(1:100, function(i){
-  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
+  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, profit=profit)
 })
@@
 ``` {r }
+sigma_g <- 0.15    # Noise in population growth
 sigma_m <- 0.15     # noise in stock assessment measurement
+z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
 z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
+z_i <- function() 1
 ````
@@
 ``` {r }
+sigma_g <- 0.05    # Noise in population growth
+z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
+z_m <- function() 1
+z_i <- function() 1
 sims_gm <- lapply(1:100, function(i){
@@
 ``` {r }
+sigma_g <- 0.15    # Noise in population growth
+sigma_m <- 0.15     # noise in stock assessment measurement
 sigma_i <- 0.15     # noise in implementation of the quota
+z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
+z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
 z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
@@
 ``` {r }
+sigma_g <- 0.05    # Noise in population growth
+z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
+z_m <- function() 1
+z_i <- function() 1
 sims_gmi <- lapply(1:100, function(i){

### 2012-05-12 inst/examples/cost_of_underestimating.Rmd
updated example with cost of underestimating (and fixed jekyll rendering in earlier examples

--- 2012-05-11 inst/examples/value_of_information.Rmd
@@
 ``` {r  echo=FALSE, cache=FALSE }
-render_jekyll()
 opts_knit$set(upload.fun = socialR::flickr.url)
@@
  Implements a numerical version of the SDP described in `r knitcitations::citep("10.1016/j.jeem.2004.11.005")`.
- Compute the optimal solution under different forms of uncertainty.
-The true uncertainty is much smaller than that assumed, just a small uncertainty in growth.
-We compare the case where the uncertainty is equal to this tiny growth uncertainty to policies derived under much greater uncertainty assumptions, and see how the resulting profit varies.
+ Compute the optimal solution under different forms of uncertainty and compare the results.
 
@@
 
-We calculate the stochastic transition matrix for the probability of going from any state \\(x_t \\) to any other state \\(x_{t+1}\\) the following year, for each possible choice of harvest \\( h_t \\).
-This provides a look-up table for the dynamic programming calculations.
-
-In the Sethi case, computing the distribution over multiple sources of noise is actually quite difficult.
-Simulation turns out to be more efficient than numerically integrating over each distribution.
-
-## No Uncertainty
+## Ignoring uncertainty
 
@@
 ``` {r  simulate }
+sigma_g <- 0.15    # Noise in population growth
+sigma_m <- 0.15     # noise in stock assessment measurement
+sigma_i <- 0.15     # noise in implementation of the quota
+z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
+z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
+z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
 sims_known <- lapply(1:100, function(i){
@@
 z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
+z_m <- function() 1 
+z_i <- function() 1
 ````
@@
 
-Simulate.  The real world doesn't have as much uncertainty as we do in our knowledge of the state.
+Simulate
 
 ``` {r }
-sigma_g <- 0.05    # Noise in population growth
+sigma_g <- 0.15    # Noise in population growth
+sigma_m <- 0.15     # noise in stock assessment measurement
+sigma_i <- 0.15     # noise in implementation of the quota
 z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
+z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
+z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
+
 sims_g <- lapply(1:100, function(i){
-  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, profit=profit)
+  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
 })
@@
 ``` {r }
-sigma_g <- 0.05    # Noise in population growth
+sigma_g <- 0.15    # Noise in population growth
+sigma_m <- 0.15     # noise in stock assessment measurement
+sigma_i <- 0.15     # noise in implementation of the quota
 z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() 1
-z_i <- function() 1
+z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
+z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
 sims_gm <- lapply(1:100, function(i){
@@
 ``` {r }
-sigma_g <- 0.05    # Noise in population growth
+sigma_g <- 0.15    # Noise in population growth
+sigma_m <- 0.15     # noise in stock assessment measurement
+sigma_i <- 0.15     # noise in implementation of the quota
 z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() 1
-z_i <- function() 1
+z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
+z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
 sims_gmi <- lapply(1:100, function(i){

### 2012-05-12 inst/examples/value_of_information.Rmd
updated example with cost of underestimating (and fixed jekyll rendering in earlier examples

@@
-`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10, refresh=1 or`
+`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10, refresh=5 or`
 
 ``` {r  echo=FALSE, cache=FALSE }
-render_jekyll()
 opts_knit$set(upload.fun = socialR::flickr.url)

### 2012-05-12 inst/examples/value_under_allee.Rmd
value under allee -- value_of_information, but with allee model

--- 2012-05-12 inst/examples/value_of_information.Rmd
@@
-`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10, refresh=5 or`
+`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10, refresh=7 or`
 
@@
 ``` {r }
-f <- BevHolt
+f <- Myer_harvest
+pars <- c(1, 2, 6) 
+p <- pars # shorthand 
+K <- p[1] * p[3] / 2 + sqrt( (p[1] * p[3]) ^ 2 - 4 * p[3] ) / 2
+x0 <- K - sigma_g ^ 2 / 2 
 ````
 
-Note that the `pdg_control` pacakge already has a definition for the `BevHolt` function, (typing the function name prints the function)
+Take a look at the model:
 
 ``` {r }
-BevHolt
+f
 ````
 
-That is, \\( f(x,h) = \frac{A x}{1 + B x} \\)
-
-Of course we could pass in any custom function of stocksize `x`, harvest `h` and parameter vector `p` in place of `BevHolt`.
-Note that we would need to write this function explicitly so that it can take vector values of `x` (i.e.
-uses `sapply`), an annoying feature of `R` for users comming from Matlab.
-
-We must now define parameters for the function.  Note that the positive stationary root of the model is given by \\( \frac{A-1}{B} \\), which we'll store for future reference as `K`.
-
-``` {r }
-pars <- c(1.5, 0.05)
-K <- (pars[1] - 1)/pars[2]
-````
-
-and we use a harvest-based profit function with default parameters
+We use a harvest-based profit function with default parameters
 
@@
 The `profit_harvest` function has the form \\( \Pi = h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x} \\), conditioned on \\( h > x \\) and \\(x > 0 \\).
-Note that the R code defines a function from another function using a trick known as a _closure_.
-Again we could write a custom profit function as long as it can take a vector stock size `x` and a scalar harvest level `h`.
-Details for provided functions can be found in the manual, i.e.
-`?profit_harvest`.
 

### 2012-05-12 inst/examples/value_under_allee.Rmd
updated with larger noise

@@
-`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10, refresh=7 or`
+`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10, refresh=8 or`
 
@@
 
- Implements a numerical version of the SDP described in `r knitcitations::citep("10.1016/j.jeem.2004.11.005")`.
+ Implements a numerical version of the SDP described in `r knitcitations::citep("10.1016/j.jeem.200.5.11.005")`.
  Compute the optimal solution under different forms of uncertainty.
@@
 p <- pars # shorthand 
-K <- p[1] * p[3] / 2 + sqrt( (p[1] * p[3]) ^ 2 - 4 * p[3] ) / 2
+K <- p[1] * p[3] / 2 + sqrt( (p[1] * p[3]) ^ 2 -0.5 * p[3] ) / 2
 x0 <- K - sigma_g ^ 2 / 2 
@@
 ``` {r }
-sigma_g <- 0.15    # Noise in population growth
+sigma_g <- 0.5    # Noise in population growth
 z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
@@
 ``` {r }
-sigma_g <- 0.15    # Noise in population growth
-sigma_m <- 0.15     # noise in stock assessment measurement
+sigma_g <- 0.5    # Noise in population growth
+sigma_m <- 0.5     # noise in stock assessment measurement
 z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
@@
 ``` {r }
-sigma_g <- 0.15    # Noise in population growth
-sigma_m <- 0.15     # noise in stock assessment measurement
-sigma_i <- 0.15     # noise in implementation of the quota
+sigma_g <- 0.5    # Noise in population growth
+sigma_m <- 0.5     # noise in stock assessment measurement
+sigma_i <- 0.5     # noise in implementation of the quota
 z_g <- function() rlnorm(1,  0, sigma_g) # mean 1

### 2012-05-16 inst/examples/reckless_driver.Rmd
reckless driver scenario

--- 2012-05-12 inst/examples/cost_of_underestimating.Rmd
@@
-`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10, refresh=1 or`
+`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10, refresh=1, cache.path="reckless_driver/" or`
 
@@
 
-# Calculating the value of information
+# Reckless Driver Scenario
+
+Manager assumes the world is basically deterministic, performs in a variety of scenarios of an increasingly uncertain world.
+
  * author Carl Boettiger, <cboettig@gmail.com>
@@
 ``` {r  simulate }
-sigma_g <- 0.15    # Noise in population growth
-sigma_m <- 0.15     # noise in stock assessment measurement
-sigma_i <- 0.15     # noise in implementation of the quota
+sigma_g <- 0.01    # Noise in population growth
 z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
-z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
+z_m <- function() 1 
+z_i <- function() 1 
 sims_known <- lapply(1:100, function(i){
@@
 
+Simulate
+
 ``` {r }
@@
 z_i <- function() 1
-````
-Find the transition matrix
-
-``` {r }
-SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
-````
-
-Find the optimum solution
-
-``` {r }
-opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
-                     profit, delta=0.05, reward=0)
-````
-
-Simulate
-
-``` {r }
-sigma_g <- 0.15    # Noise in population growth
-sigma_m <- 0.15     # noise in stock assessment measurement
-sigma_i <- 0.15     # noise in implementation of the quota
-z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
-z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
 
@@
 
+```
+
+Simulate
+
 ``` {r }
@@
 z_i <- function() 1 
-````
-
-Find the transition matrix.  Use the simulation method to account for the extra uncertainties
-
-``` {r }
-require(snowfall) 
-sfInit(parallel=TRUE, cpu=16)
-SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=999)
-````
-
-Find the optimum solution
-
-``` {r }
-opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
-                     profit, delta=0.05, reward=0)
-````
-
-Simulate
-
-``` {r }
-sigma_g <- 0.15    # Noise in population growth
-sigma_m <- 0.15     # noise in stock assessment measurement
-sigma_i <- 0.15     # noise in implementation of the quota
-z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
-z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
 sims_gm <- lapply(1:100, function(i){
@@
 ## Growth, stock measurement & implementation uncertainty
-
-``` {r }
-sigma_g <- 0.15    # Noise in population growth
-sigma_m <- 0.15     # noise in stock assessment measurement
-sigma_i <- 0.15     # noise in implementation of the quota
-z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
-z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
-````
-
-Find the transition matrix.  Use the simulation method to account for the extra uncertainties
-
-``` {r }
-SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=999)
-````
-
-Find the optimum solution
-
-``` {r }
-opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
-                     profit, delta=0.05, reward=0)
-````
 

### 2012-05-16 inst/examples/value_of_stochasticity.Rmd
reckless driver scenario

--- 2012-05-11 inst/examples/value_of_information.Rmd
@@
-`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10, refresh=1 or`
+`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10, cache.path="value_of_stochasticity/" or`
 
 ``` {r  echo=FALSE, cache=FALSE }
-render_jekyll()
 opts_knit$set(upload.fun = socialR::flickr.url)

### 2012-05-16 inst/examples/cost_of_bias.Rmd
cost of bias

`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=6, fig.height=6, cache.path="cost_of_bias/", include=FALSE or`

```{r echo=FALSE, cache=FALSE }
opts_knit$set(upload.fun = socialR::flickr.url)
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
knitcitations::cleanbib()
````

# Calculating the cost of bias  
 * author Carl Boettiger, <cboettig@gmail.com>
 * license: CC0

 * knitr-formatted [source code](#)
 * [Cached data](#)

Implements a numerical version of the SDP described in `r knitcitations::citep("10.1016/j.jeem.2004.11.005")`.  Then compute the optimal solution under different forms of uncertainty and compare the results.

``` {r setup, echo=FALSE}
rm(list=ls())   
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
rm(list=ls())
````

## Model setup

We will assume a Beverton-Holt state equation / population dynamics function, <span> \( f(x,h) = \frac{A x}{1 + B x} \)</span>

```{r model}
f <- BevHolt
pars <- c(1.5, 0.05)
K <- (pars[1] - 1)/pars[2]
````
with parameters A = `r pars[1]` and B = `r pars[2]`.  The positive stationary root of the model is given by <span>\( \frac{A-1}{B} \)</span>, `r K`.

```{r profit}
p <- 1
c0 <- 0.01
c1 <- 0
profit <- profit_harvest(price=p, c0 = c0, c1 = c1) 
````

We also assume a profit function of the form <span>\( \Pi = p h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x} \)</span>, conditioned on <span>\( h > x \)</span> and <span>\(x > 0 \)</span>, with price p = `r p`, c0 = `r c0`, and c1 = `r c1`.

```{r grid}
x_grid <- seq(0, 2 * K, length = 100)  
h_grid <- x_grid  
````

and solve the problem on a discrete grid of `r length(x_grid)` for stock size and range `r min(x_grid)`, `r max(x_grid)`.  We use the same set of gridpoints for the possible harvest levels.

## Scenarios

We calculate the stochastic transition matrix for the probability of going from any state \\(x_t \\) to any other state \\(x_{t+1}\\) the following year, for each possible choice of harvest \\( h_t \\).  This provides a look-up table for the dynamic programming calculations. In the Sethi case, computing the distribution over multiple sources of noise is actually quite difficult.  Simulation turns out to be more efficient than numerically integrating over each distribution.  We use this matrix to compute the optimum strategy for all possible states of the world by dynamic programming, and then simulate replicates while applying this rule.

### No Uncertainty

The first scenario considers the completely deterministic case.

```{r }
z_g <- function() 1 
z_m <- function() 1 
z_i <- function() 1 
````

```{r }
deterministic_SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
````

```{r }
det_opt <- find_dp_optim(deterministic_SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
                     profit, delta=0.05, reward=0)
````

We simulate 100 replicates of this system.  We will used a fixed seed so that we can compare these replicates to simulations under different conditions.  (Of course the seed is irrelevant at this stage since this is actually deterministic).

```{r }
set.seed(42)
sims_one <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, det_opt$D, z_g, z_m, z_i, profit)
})
````
### Growth uncertainty

```{r }
sigma_g <- 0.15    # Noise in population growth
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1 
z_i <- function() 1 
````

The next scenario introduces growth uncertainty into the model, <span> \( x_{t+1} = z_g f(x_t) \) </span>, where `z_g` is lognormal with logmean 0 and logsd of `r sigma_g`.

```{r }
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
````

```{r }
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
                     profit, delta=0.05, reward=0)
````

As before, we simulate 100 replicates using the same random number sequence, now under this case where the noise in growth is intrinsic and is being accounted for by the management.

```{r }
set.seed(42)
sims_two <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````

### Growth uncertainty & bias

`` {r }
est_pars <- pars
par_var <- .1
````

This time we consider the same optimization under uncertainty as before, but the simulations introduce bias through a random estimate of the growth rate parameter A, drawn from a normal with mean equal to the true value `pars[1]` and variance `r par_var`.   Since A is a constant multiplier in the growth dynamics, this is equivalent to a random estimate of mean of the noise process `z_g`.  Our estimate of the parameter is drawn from the distribution and then held fixed for that replicate.  Each replicate draws its own value, so average parameter estimate across the replicates should be close to the true value.  _Isn't this equivalent to the standard parameter uncertainty?_

```{r }
set.seed(42)
sims_three <- lapply(1:100, function(i){
  est_pars[1] <- rnorm(1, pars[1], par_var)
  ForwardSimulate(f, est_pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````

## Unbiased error in growth estimate

```{r }
sigma_g <- sqrt(0.15^2 + par_var^2)   # Noise in population growth
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1 
z_i <- function() 1 
````

We will compare this result to the situation of underestimating the uncertainty in the growth rate, but knowning the parameter exactly.  We use the deterministic optimum solution under a reality that has log-normal growth noise equal to the sum of the variances in the previous example, \( \sigma_g = \)  `r sigma_g`.

```{r }
set.seed(42)
sims_four <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, det_opt$D, z_g, z_m, z_i, profit)
})
````

## Summarize and plot the results

```{r tidy}
sims <- list(known = sims_one, Growth = sims_two, Bias = sims_three, Underestimate = sims_four)

dat <- melt(sims, id=names(sims_one[[1]]))  
dt <- data.table(dat)
setnames(dt, c("L2", "L1"), c("reps", "uncertainty")) # names are nice
````

### Plots

Let's begin by looking at the dynamics of a single replicate. The line shows Reed's S, the level above which the stock should be harvested (where catch should be the difference between stock and S).  To confirm that this policy is being followed, note that harvesting only occurs when the stock is above this line, and harvest is proportional to the amount by which it is above.  Change the replicate `reps==` to see the results from a different replicate.

``` {r  onerep }
ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, fishstock)) +
  geom_abline(intercept=opt$S, slope = 0) +
  geom_line(aes(time, harvest), col="darkgreen") + 
  facet_wrap(~uncertainty) 
````

This plot summarizes the stock dynamics by visualizing the replicates. Reed's S shown again.

``` {r  fig.cap="the induced dynamics in the stock size over time, for all replicates, by scenario"}
p1 <- ggplot(dt) + geom_abline(intercept=opt$S, slope = 0) 
p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.1) + facet_wrap(~uncertainty)
````

``` {r fig.cap="The profits made in each time interval of a single replicate, by scenario"}
ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, profit))  + facet_wrap(~uncertainty)

````

``` {r fig.cap="the distribution of profits by scenario"}
profits <-dt[ , sum(profit), by=c("reps", "uncertainty")] 
ggplot(profits) + geom_histogram(aes(V1)) + facet_wrap(~uncertainty)
````

Summary statistics tell the final story:

``` {r }
profits[, mean(V1), by=uncertainty]
profits[, sd(V1), by=uncertainty]
````

# References

``` {r biblio, echo=FALSE, results="asis"}
I(knitcitations::bibliography())
````

### 2012-05-16 inst/examples/cost_of_bias.Rmd
cost of bias

@@
-`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=6, fig.height=6, cache.path="cost_of_bias/", include=FALSE or`
+`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=6, fig.height=6, cache.path="cost_of_bias/", echo=FALSE or`
 
@@
 
- * knitr-formatted [source code](#)
- * [Cached data](#)
+ * knitr-formatted [source code](https://github.com/cboettig/pdg_control/blob/master/inst/examples/cost_of_bias.Rmd)
+ * [Cached data](http://two.ucdavis.edu/cboettig/data/cost_of_bias/)
 
@@
 
-This time we consider the same optimization under uncertainty as before, but the simulations introduce bias through a random estimate of the growth rate parameter A, drawn from a normal with mean equal to the true value `pars[1]` and variance `r par_var`.
+This time we consider the same optimization under uncertainty as before, but the simulations introduce bias through a random estimate of the growth rate parameter A, drawn from a normal with mean equal to the true value `r pars[1]` and variance `r par_var`.
 Since A is a constant multiplier in the growth dynamics, this is equivalent to a random estimate of mean of the noise process `z_g`.

### 2012-05-16 inst/examples/cost_of_bias.Rmd
cost of bias

@@
 
-```{r }
+```{r}
 set.seed(42)
@@
 
-`` {r }
+```{r}
 est_pars <- pars
@@
 
-```{r }
+```{r}
 sigma_g <- sqrt(0.15^2 + par_var^2)   # Noise in population growth

### 2012-05-18 inst/examples/cost_of_bias.Rmd
cost of bias baseline against known bias

@@
 This provides a look-up table for the dynamic programming calculations.
-In the Sethi case, computing the distribution over multiple sources of noise is actually quite difficult.
-Simulation turns out to be more efficient than numerically integrating over each distribution.
-We use this matrix to compute the optimum strategy for all possible states of the world by dynamic programming, and then simulate replicates while applying this rule.
 
@@
 set.seed(42)
+bias <- rnorm(100, pars[1], par_var)
 sims_three <- lapply(1:100, function(i){
-  est_pars[1] <- rnorm(1, pars[1], par_var)
+  est_pars[1] <- bias[i]
   ForwardSimulate(f, est_pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
@@
 
-## Unbiased error in growth estimate
+## Known bias
+
+The correct baseline comparison against the above scenario, Mike points out to me, still includes the bias, but solves for the optimal solution of that random draw.
+This is much slower since it requires solving a new optimum each time, but parallelizes well.
 
 ```{r}
-sigma_g <- sqrt(0.15^2 + par_var^2)   # Noise in population growth
-z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() 1 
-z_i <- function() 1 
-````
-
-We will compare this result to the situation of underestimating the uncertainty in the growth rate, but knowning the parameter exactly.
-We use the deterministic optimum solution under a reality that has log-normal growth noise equal to the sum of the variances in the previous example, \( \sigma_g = \)  `r sigma_g`.
-
-```{r}
-set.seed(42)
-sims_four <- lapply(1:100, function(i){
-  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, det_opt$D, z_g, z_m, z_i, profit)
+require(snowfall)
+sfInit(parallel=T, cpu=16)
+sfLibrary(pdgControl)
+sfExportAll()
+sims_four <- sfLapply(1:100, function(i){
+  est_pars[1] <- bias[i] 
+  SDP_Mat <- determine_SDP_matrix(f, est_pars, x_grid, h_grid, sigma_g )
+  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
+                     profit, delta=0.05, reward=0)
+  ForwardSimulate(f, est_pars, x_grid, h_grid, x0=K, det_opt$D, z_g, z_m, z_i, profit)
 })
@@
 ```{r tidy}
-sims <- list(known = sims_one, Growth = sims_two, Bias = sims_three, Underestimate = sims_four)
+sims <- list(known = sims_one, Growth = sims_two, RandomBias = sims_three, KnownBias = sims_four)
 
@@
 
-Summary statistics tell the final story:
+Summary statistics
 
@@
 profits[, sd(V1), by=uncertainty]
+````
+
+```{r }
+save(list="dt", file="bias.rda")
+````
+
+Direct comparisons:
+
+```{r echo=TRUE}
+setkey(dt, uncertainty)
+cost_of_bias = dt[knownBias, sum(profit), by=reps]$V1 - dt[randomBias, sum(profit), by=reps]$V1
+cost_of_bias
+mean(cost_of_bias)
+sd(cost_of_bias)
 ````

### 2012-05-18 inst/examples/policycosts/stochastic_norms.Rmd
cost of bias baseline against known bias

@@
 
-# Policy Costs 
+# Policy Costs Baseline 
  * author Carl Boettiger, <cboettig@gmail.com>
@@
 ``` {r policycost_optim }
-c2 <- 4.0
-penalty <- fixed(c2)
+c2 <- 0.0
+penalty <- L1(c2)
 policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 

### 2012-05-18 inst/examples/cost_of_bias.Rmd
cost of bias -- huh? what cost?

@@
 est_pars <- pars
-par_var <- .1
+par_var <- .2
 ````
@@
 ```{r}
+bias <- rnorm(100, pars[1], par_var)
 set.seed(42)
-bias <- rnorm(100, pars[1], par_var)
 sims_three <- lapply(1:100, function(i){
@@
 })
+````
+
+For the record, the biases by index number are:
+
+```{r }
+bias
 ````
@@
 ```{r}
-require(snowfall)
-sfInit(parallel=T, cpu=16)
-sfLibrary(pdgControl)
-sfExportAll()
-sims_four <- sfLapply(1:100, function(i){
+#require(snowfall)
+#sfInit(parallel=T, cpu=16)
+#sfLibrary(pdgControl)
+#sfExportAll()
+set.seed(42)
+sims_four <- lapply(1:100, function(i){
   est_pars[1] <- bias[i] 
@@
 setkey(dt, uncertainty)
-cost_of_bias = dt[knownBias, sum(profit), by=reps]$V1 - dt[randomBias, sum(profit), by=reps]$V1
+cost_of_bias = dt[uncertainty=="KnownBias", sum(profit), by=reps]$V1 - dt[uncertainty=="RandomBias", sum(profit), by=reps]$V1
 cost_of_bias

### 2012-05-22 inst/examples/policycosts/exact_npv.Rmd
use specific cache file

--- 2012-05-02 inst/examples/policycosts/exact_npv.Rmd
@@
-`ro warning=FALSE, message=FALSE, comment=NA, cache=TRUE-->
+`ro warning=FALSE, message=FALSE, comment=NA, cache=TRUE, cache.path="exact.npv/"-->
 ``` {r setup, include=FALSE }
@@
 Calculate the transition matrix and intialize the the list of penalty functions and cost levels we will be looping over.
-``` {r  }
+
+``` {r  SDP}
 SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
 penaltyfns <- list(L2=L2, L1=L1, asy=asymmetric, fixed=fixed, asy2=free_increase)
-c2 <- seq(0, 8, length.out = 9)
+c2 <- seq(0, 22, length.out = 30)
 ````
@@
 This can take a while, so we use explicit parallelization, 
-``` {r  }
+``` {r  parallel}
 require(snowfall)
-sfInit(cpu=5, parallel=T)
+sfInit(cpu=16, parallel=T)
 sfLibrary(pdgControl)
@@
 
-``` {r  }
+``` {r  bigloop}
 policies <- 
@@
 Quadratic costs on fishing effort have to be done separately,
-``` {r  }
+``` {r  quadcosts}
 quad <- 
@@
 Tidy up the data and plot the net present value (before the penalty has been paid) relative to that achieved when managed without a penalty.  
-``` {r  }
+``` {r npv-plot}
 npv0 <- dat[1,3] 

### 2012-05-22 inst/examples/policycosts/exact_npv.Rmd
cleanup

@@
 ````
+
 Note that `optim_policy` has been updated to return the equilibrium value of profits from fish harvests before the adjustment costs have been paid, `penalty_free_V`.
@@
 Quadratic costs on fishing effort have to be done separately,
+
 ``` {r  quadcosts}
@@
 Tidy up the data and plot the net present value (before the penalty has been paid) relative to that achieved when managed without a penalty.
+
 ``` {r npv-plot}
@@
 ````
+
+Find the value of `c2` that brings each penalty closest to 75% of the cost-free adjustment value:
+
+```{r }
+dat <- data.table(dat)
+dat[,findInterval(.75*npv0, (npv0-value)/value), by="variable"]
+````

### 2012-05-22 inst/examples/policycosts/npv.R

@@ -1,94 +1,0 @@
-## @knitr libraries
-rm(list=ls())   
-require(pdgControl)
-require(reshape2)
-require(ggplot2)
-require(data.table)
-
-
-
-## @knitr unnamed-chunk-1
-delta <- 0.05     # economic discounting rate
-OptTime <- 50     # stopping time
-gridsize <- 40   # gridsize (discretized population)
-sigma_g <- 0.2    # Noise in population growth
-sigma_m <- 0.     # noise in stock assessment measurement
-sigma_i <- 0.     # noise in implementation of the quota
-reward <- 0       # bonus for satisfying the boundary condition
-
-
-
-
-## @knitr noise_dists
-z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
-z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
-
-
-
-
-## @knitr BevHolt_
-f <- BevHolt                # Select the state equation
-pars <- c(1.5, 0.05)             # parameters for the state equation
-K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
-xT <- 0                     # boundary conditions
-x0 <- K
-
-
-## @knitr profit_
-profit <- profit_harvest(price = 10, c0 = 30, c1 = 0.0)
-
-
-## @knitr create_grid_
-x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
-h_grid <- seq(0.01, 0.8 * K, length = gridsize)  
-
-
-## @knitr fees
-L1 <- function(c2) function(h, h_prev)  c2 * abs(h - h_prev) 
-asymmetric <- function(c2) function(h, h_prev)  c2 * max(h_prev - h, 0)
-fixed <-  function(c2) function(h, h_prev) c2
-L2 <- function(c2) function(h, h_prev)  c2 * (h - h_prev) ^ 2
-
-SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
-penaltyfns <- list(L2=L2, L1=L1, asy=asymmetric, fixed=fixed)
-c2 <- seq(0, 30, length.out = 31)
-
-
-
-require(snowfall)
-sfInit(cpu=4, parallel=T)
-sfLibrary(pdgControl)
-sfExportAll()
-
-
-policies <- 
-sfSapply(penaltyfns, function(penalty){
-  policies <- 
-  sapply(c2, function(c2){
[…]

### 2012-05-22 inst/examples/policycosts/exact_npv.Rmd
compute comperable intervals

@@
-`ro warning=FALSE, message=FALSE, comment=NA, cache=TRUE, cache.path="exact.npv/"-->
+`ro warning=FALSE, message=FALSE, comment=NA, cache=TRUE, cache.path="exact.npv/" or`
+
 ``` {r setup, include=FALSE }
@@
 
-```{r }
+```{r comparison}
 dat <- data.table(dat)
-dat[,findInterval(.75*npv0, (npv0-value)/value), by="variable"]
+int <- dat[,findInterval(.75*npv0, (npv0-value)/value), by="variable"]$V1
+dat$c2[int]
 ````

### 2012-05-22 inst/examples/policycosts/stochastic_norms.Rmd
formatting

@@
 sigma_g <- 0.2    # Noise in population growth
-sigma_m <- 0.     # noise in stock assessment measurement
-sigma_i <- 0.     # noise in implementation of the quota
 reward <- 0       # bonus for satisfying the boundary condition
 
-## @knitr noise_dists
 z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
-z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
+z_m <- function() 1
+z_i <- function() 1
 
@@
 
-## @knitr profit_
 profit <- profit_harvest(price = 10, c0 = 30, c1 = 0)
 
-## @knitr create_grid_
 x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
@@
 
-## @knitr reed_sdp
 SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )

### 2012-05-23 inst/examples/policycosts/L1.Rmd
updated runs at comperable induced costs, using values from exact_npv

--- 2012-05-22 inst/examples/policycosts/stochastic_norms.Rmd
@@
-`ro fig.width=10, fig.height=7, message=FALSE, comment=NA, cache=FALSE, verbose=TRUE or`
+`ro fig.width=10, fig.height=7, message=FALSE, comment=NA, cache=TRUE, verbose=TRUE, cache.path="L1/" or`
 
@@
 
-# Policy Costs Baseline 
+# Policy Costs L1
  * author Carl Boettiger, <cboettig@gmail.com>
@@
 ``` {r policycost_optim }
-c2 <- 0.0
+c2 <- 1.52
 penalty <- L1(c2)

### 2012-05-23 inst/examples/policycosts/L2.Rmd
updated runs at comperable induced costs, using values from exact_npv

--- 2012-05-22 inst/examples/policycosts/stochastic_norms.Rmd
@@
-`ro fig.width=10, fig.height=7, message=FALSE, comment=NA, cache=FALSE, verbose=TRUE or`
+`ro fig.width=10, fig.height=7, message=FALSE, comment=NA, cache=TRUE, verbose=TRUE, cache.path="L2/" or`
 
@@
 
-# Policy Costs Baseline 
+# Policy Costs L2
  * author Carl Boettiger, <cboettig@gmail.com>
@@
 ``` {r policycost_optim }
-c2 <- 0.0
-penalty <- L1(c2)
+c2 <- 0.7586
+penalty <- L2(c2)
 policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 

### 2012-05-23 inst/examples/policycosts/fixed.Rmd
updated runs at comperable induced costs, using values from exact_npv

--- 2012-05-22 inst/examples/policycosts/stochastic_norms.Rmd
@@
-`ro fig.width=10, fig.height=7, message=FALSE, comment=NA, cache=FALSE, verbose=TRUE or`
+`ro fig.width=10, fig.height=7, message=FALSE, comment=NA, cache=TRUE, verbose=TRUE, cache.path="fixed/" or`
 
@@
 
-# Policy Costs Baseline 
+# Policy Costs fixed fee 
  * author Carl Boettiger, <cboettig@gmail.com>
@@
 ``` {r policycost_optim }
-c2 <- 0.0
-penalty <- L1(c2)
+c2 <- 9.103
+penalty <- fixed(c2)
 policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 

### 2012-05-23 inst/examples/policycosts/L1.Rmd
use the selected coefficient to implement a comparable cost in each case

@@
                     profit, delta, reward, penalty = penalty)
-cache=FALSE
 ````
@@
 
-``` {r simulate_policy, cache=cache}
+``` {r simulate_policy}
 sims <- lapply(1:100, function(i)
@@
 
-``` {r tidy, cache=cache}
+``` {r tidy}
 dat <- melt(sims, id=names(sims[[1]]))  
@@
 
-``` {r rep1, cache=cache}
+``` {r rep1}
 ggplot(subset(dt,reps==1)) +
@@
 
-``` {r rep2, cache=cache}
+``` {r rep2}
 ggplot(subset(dt,reps==2)) +
@@
 
-``` {r rep1profit, cache=cache}
+``` {r rep1profit}
 ggplot(subset(dt,reps==1)) +
@@
 
-``` {r policycost, cache=cache}
+``` {r policycost}
 costs <- dt[ , sum(policy_cost), by=reps]
@@
 
-``` {r policy, cache=cache}
+``` {r policy}
 policy <- sapply(1:length(h_grid), function(i) policycost$D[[i]][,1])
@@
 
-``` {r harvestchanges, cache=cache}
+``` {r harvestchanges}
 policy <- sapply(1:length(h_grid), function(i) policycost$D[[i]][,1])

### 2012-05-23 inst/examples/policycosts/L1.Rmd
include mean/sd data on induced and direct costs

@@
 
+These need to be discounted!
+
 ``` {r policycost}
-costs <- dt[ , sum(policy_cost), by=reps]
-profits <-dt[ , sum(profit_fishing), by=reps]
+costs <- dt[ , sum(policy_cost * (1-delta)^(time-1)), by=reps]
+profits <-dt[ , sum(profit_fishing * (1-delta)^(time-1)), by=reps]
 
@@
 ````
+
+## Results
+
+Parameters have been chosen to achieve a 25% reduction in the net present value of the stock induced by the policy cost.
+The net present value is 380.4 according the the exact calculation (see npv0 in [exact_npv.md](https://github.com/cboettig/pdg_control/blob/master/inst/examples/policycosts/exact_npv.md)) which looks close to the average in the stochastic realizations [baseline.md](https://github.com/cboettig/pdg_control/blob/master/inst/examples/policycosts/baseline.md).
+
+```{r}
+mean(profits$V1)
+sd(profits$V1)
+````
+
+Compare these induced costs to the costs of actual adjustment.  Direct costs:
+
+```{r}
+mean(costs$V1)
+sd(costs$V1)
+````
+
+Induced costs:
+
+```{r}
+380.4 - mean(profits$V1)
+````

### 2012-05-23 inst/examples/policycosts/baseline.Rmd
include mean/sd data on induced and direct costs

--- 2012-05-23 inst/examples/policycosts/L1.Rmd
@@
-`ro fig.width=10, fig.height=7, message=FALSE, comment=NA, cache=TRUE, verbose=TRUE, cache.path="L1/" or`
+`ro fig.width=10, fig.height=7, message=FALSE, comment=NA, cache=TRUE, verbose=TRUE, cache.path="baseline/" or`
 
@@
 
-# Policy Costs L1
+# Baseline Policy Costs (no cost)
  * author Carl Boettiger, <cboettig@gmail.com>
@@
 ``` {r policycost_optim }
-c2 <- 1.52
+c2 <- 0 
 penalty <- L1(c2)
@@
 ````
+
+## Results
+
+```{r }
+mean(profits$V1)
+sd(profits$V1)
+````

### 2012-05-23 inst/examples/policycosts/exact_npv.Rmd

@@
 ``` {r setup, include=FALSE }
-opts_knit$set(upload.fun = socialR::flickr.url)
+#opts_knit$set(upload.fun = socialR::flickr.url)
 ````
@@
 npv0 <- dat[1,3] 
+npv0
 dat <- data.frame(c2=c2,dat)
 dat <- melt(dat, id="c2")
-ggplot(dat, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
+ggplot(dat, aes(c2, value, col=variable)) + geom_point() + geom_line()
 ````
@@
 ```{r comparison}
-dat <- data.table(dat)
-int <- dat[,findInterval(.75*npv0, (npv0-value)/value), by="variable"]$V1
-dat$c2[int]
+closest <- function(x, v){
+	which.min(abs(v-x))
+}
+
+ggplot(dat, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
+dt <- data.table(dat)
+index <- dt[,closest(.25, (npv0-value)/value), by=variable]
+cbind(index, c2=c2[index$V1])
 ````

### 2012-05-23 inst/examples/policycosts/free_decrease.Rmd
updated examples with corrected policy adjustment costs in the simulation

--- 2012-05-23 inst/examples/policycosts/fixed.Rmd
@@
-`ro fig.width=10, fig.height=7, message=FALSE, comment=NA, cache=TRUE, verbose=TRUE, cache.path="fixed/" or`
+`ro message=FALSE, comment=NA, cache=TRUE, verbose=TRUE, cache.path="free_decrease/" or`
 
@@
 
-# Policy Costs fixed fee 
+# Asymmetric Policy Costs, decreases to quota are free 
  * author Carl Boettiger, <cboettig@gmail.com>
@@
 ``` {r policycost_optim }
-c2 <- 9.103
-penalty <- fixed(c2)
+c2 <- 1.52
+penalty <- free_decrease(c2)
 policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 

### 2012-05-23 inst/examples/policycosts/free_increase.Rmd
updated examples with corrected policy adjustment costs in the simulation

--- 2012-05-23 inst/examples/policycosts/fixed.Rmd
@@
-`ro fig.width=10, fig.height=7, message=FALSE, comment=NA, cache=TRUE, verbose=TRUE, cache.path="fixed/" or`
+`ro message=FALSE, comment=NA, cache=TRUE, verbose=TRUE, cache.path="free_increase/" or`
 
@@
 
-# Policy Costs fixed fee 
+# Asymmetric Policy Costs, increases to quota are free 
  * author Carl Boettiger, <cboettig@gmail.com>
@@
 ``` {r policycost_optim }
-c2 <- 9.103
-penalty <- fixed(c2)
+c2 <- 1.52
+penalty <- free_increase(c2)
 policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 

### 2012-05-23 inst/examples/policycosts/exact_npv.Rmd
npv_exact figure2

@@
 
-```{r comparison}
+```{r comparison_plot}
+ggplot(dat, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
+````
+
+```{r numeric_value}
 closest <- function(x, v){
@@
 }
-
-ggplot(dat, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
 dt <- data.table(dat)

### 2012-06-13 inst/examples/cost_of_bias.Rmd
updated runs

@@
-`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=6, fig.height=6, cache.path="cost_of_bias/", echo=FALSE or`
+`ro cache=FALSE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=6, fig.height=6, cache.path="cost_of_bias/", verbose=TRUE  or`
 
@@
 
-``` {r setup, echo=FALSE}
+``` {r setup, echo=FALSE, cache=FALSE}
 rm(list=ls())   
@@
 require(data.table)
-rm(list=ls())
 ````
@@
 ```{r }
+sigma_g <- 0.0    # Noise in population growth
 z_g <- function() 1 

### 2012-06-13 inst/examples/value_of_information.Rmd
reckless driver scenario
updated runs

@@
-`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10, refresh=5 or`
+`ro cache=FALSE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10, cache.path="value_of_information/", verbose=TRUE or`
 
@@
 
-``` {r  setup, echo=FALSE}
+``` {r  setup, echo=FALSE, cache=FALSE}
 rm(list=ls())   
@@
 
-Note that the `pdg_control` pacakge already has a definition for the `BevHolt` function, (typing the function name prints the function)
+Note that the `pdg_control` package already has a definition for the `BevHolt` function, (typing the function name prints the function)
 
@@
 Note that we would need to write this function explicitly so that it can take vector values of `x` (i.e.
-uses `sapply`), an annoying feature of `R` for users comming from Matlab.
+uses `sapply`), an annoying feature of `R` for users coming from Matlab.
 
@@
 sigma_i <- 0.0     # noise in implementation of the quota
-z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
-z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
+z_g <- function() 1 
+z_m <- function() 1
+z_i <- function() 1 
 ````

### 2012-06-13 inst/examples/Reed.Rmd
Reed using new extension, plotting policy function

--- 2012-05-01 inst/examples/Sethi.Rmd
@@
-`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, refresh=2 or`
+`ro cache=FALSE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE or`
 
-``` {r  echo=FALSE, cache=FALSE }
+``` {r  echo=FALSE }
 opts_knit$set(upload.fun = socialR::flickr.url)
@@
 
-# Sethi Model
+# Reed Model
  * author Carl Boettiger, <cboettig@gmail.com>
@@
 
- Implements a numerical version of the SDP described in `r knitcitations::citep("10.1016/j.jeem.2004.11.005")`.
+ Implements a numerical version of the SDP described in:
+
+   Reed, W.J., 1979. Optimal Escapement Levels in Stochastic
+   and Deterministic Harvesting Models. Journal of Environmental 
+   Economics and Management. 6: 350-363.
 
@@
 require(data.table)
-rm(list=ls())
 ````
 
-Define noise parameters
+### Define parameters
 
 ``` {r }
-sigma_g <- 0.1    # Noise in population growth
-sigma_m <- 0.1     # noise in stock assessment measurement
-sigma_i <- 0.1     # noise in implementation of the quota
+gridsize <- 100   # gridsize (discretized population)
+sigma_g <- 0.2    # Noise in population growth
+sigma_m <- 0.     # noise in stock assessment measurement
+sigma_i <- 0.     # noise in implementation of the quota
 ````
@@
 For Reed, only `z_g` will be random.
-Sethi et al will add the other forms of noise:
+Sethi et al will add the other forms
 
@@
 
-That is, \\( f(x,h) = \frac{A x}{1 + B x} \\)
+That is, \( f(x,h) = \frac{A x}{1 + B x} \)
 
@@
 
-We must now define parameters for the function.  Note that the positive stationary root of the model is given by \\( \frac{A-1}{B} \\), which we'll store for future reference as `K`.
+We must now define parameters for the function.  Note that the positive stationary root of the model is given by \( (A-1)/B \), which we'll store for future reference as `K`.
 
@@
 ``` {r  profit}
-profit <- profit_harvest(price=1, c0 = 0.01) 
+profit <- profit_harvest(price=1, c0 = 0.1) 
 ````
 
-The `profit_harvest` function has the form \\( \Pi = h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x} \\), conditioned on \\( h > x \\) and \\(x > 0 \\).
+The profit_harvest function has the form \( \Pi = h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x} \), conditioned on \( h > x \) and \(x > 0 \).
 Note that the R code defines a function from another function using a trick known as a _closure_.
@@
 ### Calculate the transition matrix (with noise in growth only)      
+We calculate the stochastic transition matrix for the probability of going from any state \(x_t \) to any other state \(x_{t+1}\) the following year, for each possible choice of harvest \( h_t \).
+This provides a look-up table for the dynamic programming calculations.
+Take a look at the R code and the documentation for `determine_SDP_matrix` to see what this function is actually doing.
+The implementation is quite simple.
 
-We calculate the stochastic transition matrix for the probability of going from any state \\(x_t \\) to any other state \\(x_{t+1}\\) the following year, for each possible choice of harvest \\( h_t \\).
-This provides a look-up table for the dynamic programming calculations.
-
-In the Sethi case, computing the distribution over multiple sources of noise is actually quite difficult.
-Simulation turns out to be more efficient than numerically integrating over each distribution.
-This code parallelizes the operation over four cores, but can be scaled to an arbitrary cluster.
-
-``` {r  parallel}
-require(snowfall) 
-sfInit(parallel=TRUE, cpu=4)
-SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=999)
+``` {r  SDP_Mat}
+SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
 ````
-Note that `SDP_Mat` is specified from the calculation above, as are our grids and our profit function.
-`OptTime` is the stopping time.
-`xT` specifies a boundary condition at the stopping time.
-A reward for meeting this boundary must be specified for it to make any difference.
-`delta` indicates the economic discount rate.
-Again, details are in the function documentation.
 
@@
 
+Note that `SDP_Mat` is specified from the calculation above, as are our grids and our profit function.
+`OptTime` is the stopping time.
+`xT` specifies a boundary condition at the stopping time.
+A reward for meeting this boundary must be specified for it to make any difference.
+`delta` indicates the economic discount rate.
+Again, details are in the function documentation.
+
+We can take a look at the policy function,
+
+``` {r }
+qplot(x_grid, opt$D[,1], xlab="stock size", ylab="harvest")
+````
+
+In the Sethi case, computing the distribution over multiple sources of noise is actually quite difficult.
+Simulation turns out to be more efficient than numerically integrating over each distribution.
+This code parallelizes the operation over four cores, but can be scaled to an arbitrary cluster.
+Since we're focused on the Reed example for the moment, we can ignore this step.
+
+``` {r  parallel}
+require(snowfall) 
+sfInit(parallel=TRUE, cpu=4)
+sethi_SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=999)
+sethi_opt <- find_dp_optim(sethi_SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
+                     profit, delta=0.05, reward=0)
+````
+
+We can take a look at the stochastically estimated policy function,
+
+``` {r }
+qplot(x_grid, sethi_opt$D[,1], xlab="stock size", ylab="harvest")
+````
+
 ### Simulate 
-
-Now we'll simulate 100 replicates of this stochastic process under the optimal harvest policy determined above.
+Now we'll simulate 100 replicates of this stochastic process under the Reed optimal harvest policy determined above.
 
@@
 The forward simulation algorithm needs an initial condition `x0` which we set equal to the carrying capacity, as well as our population dynamics `f`, parameters `pars`, grids, and noise coefficients.
-Recall in the Reed case only `z_g`, growth, is stochastic, while in the Sethi example we now have three forms of stochasticity -- growth, measurement, and implementation.
+Recall in the Reed case only `z_g`, growth, is stochastic.
 
@@
 
-``` {r  onerep }
+``` {r  p0}
 ggplot(subset(dt,reps==1)) +
@@
 
-This plot summarizes the stock dynamics by visualizing the replicates. Reed's S shown again.
+This plot summarizes the stock dynamics by visualizing the replicates.
+Reed's S shown again, along with the dotted line showing the allee threshold, below which the stock will go to zero (unless rescued stochastically).
 
-``` {r  all}
-p1 <- ggplot(dt) + geom_abline(intercept=opt$S, slope = 0) 
+``` {r  p1}
+p1 <- ggplot(dt) + geom_abline(intercept=opt$S, slope = 0) + 
+  geom_abline(intercept=xT, slope = 0, lty=2) 
 p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.2)
@@
 
-``` {r  harvestplot}
+``` {r  p2}
 p1 + geom_line(aes(time, harvest, group = reps), alpha = 0.1, col="darkgreen")
@@
 
-``` {r  escapement}
+``` {r  p3}
 p1 + geom_line(aes(time, escapement, group = reps), alpha = 0.1, col="darkgrey")
@@
 ### Visualizing the optimal policy
-
 Note that when the boundary is sufficiently far away, i.e.
@@
 The optimal policy is shown here over time, where the color indicates the harvest recommended for each possible stock value at that time (shown on the vertical axis).
-Observe that the solution does not correspond to a simple Reed-style rule.
+Note that below a certain stock value, harvesting is not recommended and the dots turn red (Reed's constant escapement rule!)  However, at very low values, harvesting starts again (orange dots), because of the allee effect - these populations are doomed anyway, so may as well fish all that remains.
+
+Note that interestingly, populations just below the allee threshold are given the chance to be rescued stochastically early on - that small chance that they recover is worth the expected loss.
+The "no-harvest" zones stand out clearly in the red areas of this graph.
 
@@
   scale_colour_gradientn(colours = rainbow(4)) +
-  geom_abline(intercept=opt$S, slope = 0) 
+  geom_abline(intercept=opt$S, slope = 0) +
+  geom_abline(intercept=xT, slope=0, lty=2)
 p5
@@
   scale_colour_gradientn(colours = rainbow(4)) +
-  geom_abline(intercept=opt$S, slope = 0) 
+  geom_abline(intercept=opt$S, slope = 0) +
+  geom_abline(intercept=xT, slope=0, lty=2)
 p6 + geom_line(aes(time, fishstock, group = reps), alpha = 0.1, data=dt)
 ````
-
-# References
-
-``` {r biblio, echo=FALSE, results="asis"}
-I(knitcitations::bibliography())
-````

### 2012-06-13 inst/examples/Reed.Rmd
hmm, plotting constant escapement

@@
 ``` {r  profit}
-profit <- profit_harvest(price=1, c0 = 0.1) 
+profit <- profit_harvest(price=1, c0 = 0.0001) 
 ````
@@
 ``` {r }
-qplot(x_grid, opt$D[,1], xlab="stock size", ylab="harvest")
+qplot(x_grid, x_grid[opt$D[,1]], xlab="stock size", ylab="harvest")
+````
+
+Note that this corresponds to constant optimal escapement, 
+``` {r }
+qplot(x_grid, x_grid - x_grid[opt$D[,1]], xlab="stock size", ylab="escapement")
 ````
@@
 
-``` {r  parallel}
+``` {r  parallel, eval=FALSE}
 require(snowfall) 
@@
                      profit, delta=0.05, reward=0)
-````
-
-We can take a look at the stochastically estimated policy function,
-
-``` {r }
 qplot(x_grid, sethi_opt$D[,1], xlab="stock size", ylab="harvest")

### 2012-06-13 inst/examples/Reed.Rmd
adding plots of policy function and value function

@@
 ``` {r  profit}
-profit <- profit_harvest(price=1, c0 = 0.0001) 
+profit <- profit_harvest(price=1, c0 = 0.01) 
 ````
@@
 ``` {r  grid}
-x_grid <- seq(0, 2 * K, length = 100)  
+x_grid <- seq(0, 1.5 * K, length = 100)  
 h_grid <- x_grid  
@@
 
-We can take a look at the policy function,
+Plot the policy function (in terms of escapement, `x-h`, rather than harvest `h`) at equilibrium (first time-step):
 
-``` {r }
-qplot(x_grid, x_grid[opt$D[,1]], xlab="stock size", ylab="harvest")
+``` {r policyfn_plot}
+qplot(x_grid, x_grid - x_grid[opt$D[,1]], xlab="stock size", ylab="escapement")
 ````
 
-Note that this corresponds to constant optimal escapement, 
-``` {r }
-qplot(x_grid, x_grid - x_grid[opt$D[,1]], xlab="stock size", ylab="escapement")
+and the value function (at equilibrium):
+
+``` {r valuefn_plot}
+qplot(x_grid, opt$V, xlab="stock size", ylab="value")
 ````

### 2012-06-13 inst/examples/Sethi.Rmd
adding plots of policy function and value function

--- 2012-05-01 inst/examples/Sethi.Rmd
@@
-`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, refresh=2 or`
+`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE or`
 
@@
                      profit, delta=0.05, reward=0)
+````
+
+Plot the policy function:
+
+``` {r policyfn_plot}
+qplot(x_grid, x_grid - x_grid[opt$D[,1]], xlab="stock size", ylab="escapement")
+````
+
+and the value function:
+
+``` {r valuefn_plot}
+qplot(x_grid, opt$V, xlab="stock size", ylab="value")
 ````

### 2012-06-13 inst/examples/cost_of_bias.Rmd
cost of bias, zero

--- 2012-05-18 inst/examples/cost_of_bias.Rmd
@@
                      profit, delta=0.05, reward=0)
-  ForwardSimulate(f, est_pars, x_grid, h_grid, x0=K, det_opt$D, z_g, z_m, z_i, profit)
+  ForwardSimulate(f, est_pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
 })

### 2012-06-13 inst/examples/additive_information.Rmd

--- 2012-06-13 inst/examples/cost_of_bias.Rmd
@@
 
-# Calculating the cost of bias  
+# Calculating if information costs are essentially addititve or not.   
  * author Carl Boettiger, <cboettig@gmail.com>
@@
 
-The first scenario considers the completely deterministic case.
+The first scenario considers managing with the completely deterministic rules when in fact both measurement and growth are stochastic.
 
@@
 
-We simulate 100 replicates of this system.
+We simulate 100 replicates of this system in which measurement and growth are actually stochastic.
 We will used a fixed seed so that we can compare these replicates to simulations under different conditions.
-(Of course the seed is irrelevant at this stage since this is actually deterministic).
 
 ```{r }
+z_g <- function() rlnorm(1,  0, 0.15) 
+z_m <- function() rlnorm(1,  0, 0.15) 
+z_i <- function() 1 
 set.seed(42)
@@
 ````
+
 ### Growth uncertainty
@@
 
-As before, we simulate 100 replicates using the same random number sequence, now under this case where the noise in growth is intrinsic and is being accounted for by the management.
+As before, we simulate 100 replicates using the same random number sequence, now under this case where the noise in growth is being accounted for by the management, but not the measurement noise.
 
 ```{r}
+z_g <- function() rlnorm(1,  0, 0.15) 
+z_m <- function() rlnorm(1,  0, 0.15) 
+z_i <- function() 1 
 set.seed(42)
@@
 
-### Growth uncertainty & bias
+### Measurement uncertainty
+
+```{r }
+sigma_m <- 0.15    # Noise in population growth
+z_g <- function() 1
+z_m <- function() rlnorm(1,  0, sigma_m)  
+z_i <- function() 1 
+````
+
+The next scenario introduces growth uncertainty into the model, <span> \( x_{t+1} = f( z_m x_t) \) </span>, where `z_m` is lognormal with logmean 0 and logsd of `r sigma_m`.
+We solve the SDP this time using the simulation approach
+
+```{r }
+SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=999)
+````
+
+```{r }
+opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
+                     profit, delta=0.05, reward=0)
+````
+
+As before, we simulate 100 replicates using the same random number sequence, now under this case where the noise comes from measurement and is accounted for by the management, but not the growth noise.
 
 ```{r}
-est_pars <- pars
-par_var <- .2
-````
-
-This time we consider the same optimization under uncertainty as before, but the simulations introduce bias through a random estimate of the growth rate parameter A, drawn from a normal with mean equal to the true value `r pars[1]` and variance `r par_var`.
-Since A is a constant multiplier in the growth dynamics, this is equivalent to a random estimate of mean of the noise process `z_g`.
-Our estimate of the parameter is drawn from the distribution and then held fixed for that replicate.
-Each replicate draws its own value, so average parameter estimate across the replicates should be close to the true value.
-_Isn't this equivalent to the standard parameter uncertainty?_
-
-```{r}
-bias <- rnorm(100, pars[1], par_var)
+z_g <- function() rlnorm(1,  0, 0.15) 
+z_m <- function() rlnorm(1,  0, 0.15) 
+z_i <- function() 1 
 set.seed(42)
 sims_three <- lapply(1:100, function(i){
-  est_pars[1] <- bias[i]
-  ForwardSimulate(f, est_pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
+  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
 })
@@
 
-For the record, the biases by index number are:
+### Both types of uncertainty
 
 ```{r }
-bias
+sigma_m <- 0.15    # Noise in population growth
+z_g <- function() rlnorm(1,  0, sigma_m)
+z_m <- function() rlnorm(1,  0, sigma_m)  
+z_i <- function() 1 
 ````
 
-## Known bias
+```{r }
+SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=999)
+````
 
-The correct baseline comparison against the above scenario, Mike points out to me, still includes the bias, but solves for the optimal solution of that random draw.
-This is much slower since it requires solving a new optimum each time, but parallelizes well.
+```{r }
+opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
+                     profit, delta=0.05, reward=0)
+````
+
+As before, we simulate 100 replicates using the same random number sequence, now under this case where the noise comes from measurement and is accounted for by the management, but not the growth noise.
 
 ```{r}
-#require(snowfall)
-#sfInit(parallel=T, cpu=16)
-#sfLibrary(pdgControl)
-#sfExportAll()
+z_g <- function() rlnorm(1,  0, 0.15) 
+z_m <- function() rlnorm(1,  0, 0.15) 
+z_i <- function() 1 
 set.seed(42)
-sims_four <- lapply(1:100, function(i){
-  est_pars[1] <- bias[i] 
-  SDP_Mat <- determine_SDP_matrix(f, est_pars, x_grid, h_grid, sigma_g )
-  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
-                     profit, delta=0.05, reward=0)
-  ForwardSimulate(f, est_pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
+sims_three <- lapply(1:100, function(i){
+  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
 })

### 2012-06-13 inst/examples/policycosts/fixed.Rmd

@@
-`ro fig.width=10, fig.height=7, message=FALSE, comment=NA, cache=TRUE, verbose=TRUE, cache.path="fixed/" or`
+`ro message=FALSE, comment=NA, cache=FALSE, verbose=TRUE, cache.path="fixed/" or`
 

### 2012-06-13 inst/examples/Sethi.Rmd
Sethi stochastic integration with only 99 reps

@@
-`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE or`
+`ro cache=FALSE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE or`
 
@@
 sfInit(parallel=TRUE, cpu=4)
-SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=999)
+SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=99)
 ````

### 2012-06-13 inst/examples/Sethi.Rmd
Sethi 9999 reps on zero

@@
 require(snowfall) 
-sfInit(parallel=TRUE, cpu=4)
-SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=99)
+sfInit(parallel=TRUE, cpu=16)
+SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=9999)
 ````

### 2012-06-13 inst/examples/Sethi_policyfns.Rmd

--- 2012-06-13 inst/examples/Sethi.Rmd
@@
-`ro cache=FALSE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE or`
+`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache.path="Sethi_policyfn/" or`
 
@@
 
-Define noise parameters
-
-``` {r }
-sigma_g <- 0.1    # Noise in population growth
-sigma_m <- 0.1     # noise in stock assessment measurement
-sigma_i <- 0.1     # noise in implementation of the quota
-````
-
-we'll use log normal noise functions. 
-For Reed, only `z_g` will be random.
-Sethi et al will add the other forms of noise:
-
-``` {r  noise_dists}
-z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
-z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
-````
-
 Chose the state equation / population dynamics function
@@
 
-Note that the `pdg_control` pacakge already has a definition for the `BevHolt` function, (typing the function name prints the function)
-
-``` {r }
-BevHolt
-````
-
 That is, \\( f(x,h) = \frac{A x}{1 + B x} \\)
-
-Of course we could pass in any custom function of stocksize `x`, harvest `h` and parameter vector `p` in place of `BevHolt`.
-Note that we would need to write this function explicitly so that it can take vector values of `x` (i.e.
-uses `sapply`), an annoying feature of `R` for users comming from Matlab.
 
@@
 The `profit_harvest` function has the form \\( \Pi = h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x} \\), conditioned on \\( h > x \\) and \\(x > 0 \\).
-Note that the R code defines a function from another function using a trick known as a _closure_.
-Again we could write a custom profit function as long as it can take a vector stock size `x` and a scalar harvest level `h`.
-Details for provided functions can be found in the manual, i.e.
-`?profit_harvest`.
-
-Now we must set up the discrete grids for stock size and havest levels (which will use same resolution as for stock), in order to calculate the SDP solution.   Here we set the gridsize to 100.
+We set up the discrete grids for stock size and havest levels (which will use same resolution as for stock), in order to calculate the SDP solution.
+Here we set the gridsize to 100.
 
@@
 
-### Calculate the transition matrix (with noise in growth only)
+## Scenarios
 
-We calculate the stochastic transition matrix for the probability of going from any state \\(x_t \\) to any other state \\(x_{t+1}\\) the following year, for each possible choice of harvest \\( h_t \\).
-This provides a look-up table for the dynamic programming calculations.
+### Large Measurement error
 
-In the Sethi case, computing the distribution over multiple sources of noise is actually quite difficult.
-Simulation turns out to be more efficient than numerically integrating over each distribution.
-This code parallelizes the operation over four cores, but can be scaled to an arbitrary cluster.
+``` {r  noise_dists}
+sigma_g <- 0.01    # Noise in population growth
+sigma_m <- 0.25     # noise in stock assessment measurement
+sigma_i <- 0.01     # noise in implementation of the quota
+z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
+z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
+z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
+````
 
@@
 require(snowfall) 
-sfInit(parallel=TRUE, cpu=4)
-SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=99)
+sfInit(parallel=TRUE, cpu=16)
+SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=19999)
 ````
@@
 
-### Simulate
+### Large growth error
 
-Now we'll simulate 100 replicates of this stochastic process under the optimal harvest policy determined above.
-
-``` {r  simulate }
-sims <- lapply(1:100, function(i){
-  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i)
-})
+``` {r  noise_dists2}
+sigma_g <- 0.25    # Noise in population growth
+sigma_m <- 0.01     # noise in stock assessment measurement
+sigma_i <- 0.01     # noise in implementation of the quota
+z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
+z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
+z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
 ````
 
-The forward simulation algorithm needs an initial condition `x0` which we set equal to the carrying capacity, as well as our population dynamics `f`, parameters `pars`, grids, and noise coefficients.
-Recall in the Reed case only `z_g`, growth, is stochastic, while in the Sethi example we now have three forms of stochasticity -- growth, measurement, and implementation.
+``` {r  parallel2}
+SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=19999)
+opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
+                     profit, delta=0.05, reward=0)
+```
 
-## Summarize and plot the results
+Plot the policy function:
 
-R makes it easy to work with this big replicate data set.  We make data tidy (melt), fast (data.tables), and nicely labeled.
-
-``` {r  tidy}
-dat <- melt(sims, id=names(sims[[1]]))  
-dt <- data.table(dat)
-setnames(dt, "L1", "reps") # names are nice
+``` {r policyfn_plot2}
+qplot(x_grid, x_grid - x_grid[opt$D[,1]], xlab="stock size", ylab="escapement")
 ````
 
-### Plots
+and the value function:
 
-Let's begin by looking at the dynamics of a single replicate.
-The line shows Reed's S, the level above which the stock should be harvested (where catch should be the difference between stock and S).
-To confirm that this policy is being followed, note that harvesting only occurs when the stock is above this line, and harvest is proportional to the amount by which it is above.
-Change the replicate `reps==` to see the results from a different replicate.
-
-``` {r  onerep }
-ggplot(subset(dt,reps==1)) +
-  geom_line(aes(time, fishstock)) +
-  geom_abline(intercept=opt$S, slope = 0) +
-  geom_line(aes(time, harvest), col="darkgreen") 
+``` {r valuefn_plot2}
+qplot(x_grid, opt$V, xlab="stock size", ylab="value")
 ````
-
-This plot summarizes the stock dynamics by visualizing the replicates. Reed's S shown again.
-
-``` {r  all}
-p1 <- ggplot(dt) + geom_abline(intercept=opt$S, slope = 0) 
-p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.2)
-````
-
-We can also look at the harvest dynamics:
-
-``` {r  harvestplot}
-p1 + geom_line(aes(time, harvest, group = reps), alpha = 0.1, col="darkgreen")
-````
-
-This strategy is supposed to be a constant-escapement strategy. We can visualize the escapement:
-
-``` {r  escapement}
-p1 + geom_line(aes(time, escapement, group = reps), alpha = 0.1, col="darkgrey")
-````
-
-### Visualizing the optimal policy
-
-Note that when the boundary is sufficiently far away, i.e.
-for the first couple timesteps, the optimal policy is stationary.
-The optimal policy is shown here over time, where the color indicates the harvest recommended for each possible stock value at that time (shown on the vertical axis).
-Observe that the solution does not correspond to a simple Reed-style rule.
-
-``` {r  policy, fig.width=9}
-policy <- melt(opt$D)
-policy_zoom <- subset(policy, x_grid[Var1] < max(dt$fishstock) )
-p5 <- ggplot(policy_zoom) + 
-  geom_point(aes(Var2, (x_grid[Var1]), col=h_grid[value])) + 
-  labs(x = "time", y = "fishstock") +
-  scale_colour_gradientn(colours = rainbow(4)) +
-  geom_abline(intercept=opt$S, slope = 0) 
-p5
-````
-
-The harvest intensity is limited by the stock size.
-
-``` {r  policy2, fig.width=10}
-p6 <- ggplot(policy_zoom) + 
-  geom_point(aes(Var2, (x_grid[Var1]), col=x_grid[Var1] - h_grid[value])) + 
-  labs(x = "time", y = "fishstock") +
-  scale_colour_gradientn(colours = rainbow(4)) +
-  geom_abline(intercept=opt$S, slope = 0) 
-p6 + geom_line(aes(time, fishstock, group = reps), alpha = 0.1, data=dt)
-````
-
-# References
-
-``` {r biblio, echo=FALSE, results="asis"}
-I(knitcitations::bibliography())
-````

### 2012-06-13 inst/examples/Sethi_policyfns.Rmd
Sethi Policy functions results

@@
 Clear the workspace and load package dependencies: 
-``` {r  setup, echo=FALSE}
+``` {r  setup, echo=FALSE, cache=FALSE}
 rm(list=ls())   
@@
 sfInit(parallel=TRUE, cpu=16)
+```
+
+``` {r sdp1}
 SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=19999)
@@
 ``` {r  find_dp_opt }
-opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
+measure <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
                      profit, delta=0.05, reward=0)
-````
-
-Plot the policy function:
-
-``` {r policyfn_plot}
-qplot(x_grid, x_grid - x_grid[opt$D[,1]], xlab="stock size", ylab="escapement")
-````
-
-and the value function:
-
-``` {r valuefn_plot}
-qplot(x_grid, opt$V, xlab="stock size", ylab="value")
 ````
@@
 SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=19999)
-opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
+growth <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
                      profit, delta=0.05, reward=0)
@@
 
-Plot the policy function:
+### Large implementation error
 
-``` {r policyfn_plot2}
-qplot(x_grid, x_grid - x_grid[opt$D[,1]], xlab="stock size", ylab="escapement")
+``` {r  noise_dists3}
+sigma_g <- 0.01    # Noise in population growth
+sigma_m <- 0.01     # noise in stock assessment measurement
+sigma_i <- 0.25     # noise in implementation of the quota
+z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
+z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
+z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
 ````
 
-and the value function:
+``` {r  parallel3}
+SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=19999)
+imp <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
+                     profit, delta=0.05, reward=0)
+```
 
-``` {r valuefn_plot2}
-qplot(x_grid, opt$V, xlab="stock size", ylab="value")
+``` {r plots}
+require(reshape2)
+policy <- melt( data.frame(stock=x_grid, implementation = x_grid[imp$D[,1]], measurement = x_grid[measure$D[,1]], growth = x_grid[growth$D[,1]]), id="stock")
+value <-  melt(data.frame(stock=x_grid, implementation = imp$V, measurement = measure$V, growth = growth$V), id="stock")
+ggplot(policy) + geom_point(aes(stock, stock-value, color=variable))
+ggplot(value) + geom_point(aes(stock, stock-value, color=variable))
+ggplot(policy) + geom_smooth(aes(stock, stock-value, color=variable))
+ggplot(value) + geom_smooth(aes(stock, stock-value, color=variable))
 ````

### 2012-06-13 inst/examples/Sethi_policyfns.Rmd
updated plots of Sethi figure 3 includes net present value (value function) and escapement (policy function) for implementation, growth, and measurement uncertainty

@@
 
-``` {r plots}
+``` {r plots, fig.width=7}
 require(reshape2)
@@
 value <-  melt(data.frame(stock=x_grid, implementation = imp$V, measurement = measure$V, growth = growth$V), id="stock")
-ggplot(policy) + geom_point(aes(stock, stock-value, color=variable))
-ggplot(value) + geom_point(aes(stock, stock-value, color=variable))
-ggplot(policy) + geom_smooth(aes(stock, stock-value, color=variable))
-ggplot(value) + geom_smooth(aes(stock, stock-value, color=variable))
+ggplot(policy) + geom_point(aes(stock, stock-value, color=variable)) + ylab("escapement") 
+ggplot(value) + geom_point(aes(stock, value, color=variable)) + ylab("Net Present Value")
+ggplot(policy) + geom_smooth(aes(stock, stock-value, color=variable))+ ylab("escapement") 
+ggplot(value) + geom_smooth(aes(stock, value, color=variable)) + ylab("Net Present Value")
 ````

### 2012-06-14 inst/examples/Sethi_policyfns.Rmd
Sethi policy function (show libraries)

@@
 Clear the workspace and load package dependencies: 
-``` {r  setup, echo=FALSE, cache=FALSE}
+``` {r  setup, cache=FALSE}
 rm(list=ls())   

### 2012-06-14 inst/examples/value_of_information.Rmd
value of information now handles all cases

@@
-`ro cache=FALSE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10, cache.path="value_of_information/", verbose=TRUE or`
+`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="value_of_information/", verbose=TRUE or`
 
@@
 # Calculating the value of information
- * author Carl Boettiger, <cboettig@gmail.com>
- * license: CC0
 
@@
  Compute the optimal solution under different forms of uncertainty.
-The true uncertainty is much smaller than that assumed, just a small uncertainty in growth.
-We compare the case where the uncertainty is equal to this tiny growth uncertainty to policies derived under much greater uncertainty assumptions, and see how the resulting profit varies.
 
 ``` {r  setup, echo=FALSE, cache=FALSE}
-rm(list=ls())   
+# load required libraries
 require(pdgControl)
@@
 
-Define noise parameters
-
-Chose the state equation / population dynamics function
+We consider a Beverton Holt state equation governing population dynamics, \\( f(x,h) = \frac{A x}{1 + B x} \\)
 
@@
 
-Note that the `pdg_control` package already has a definition for the `BevHolt` function, (typing the function name prints the function)
-
-``` {r }
-BevHolt
-````
-
-That is, \\( f(x,h) = \frac{A x}{1 + B x} \\)
-
-Of course we could pass in any custom function of stocksize `x`, harvest `h` and parameter vector `p` in place of `BevHolt`.
-Note that we would need to write this function explicitly so that it can take vector values of `x` (i.e.
-uses `sapply`), an annoying feature of `R` for users coming from Matlab.
-
-We must now define parameters for the function.  Note that the positive stationary root of the model is given by \\( \frac{A-1}{B} \\), which we'll store for future reference as `K`.
+With parameters `A` = `r A <- 1.5` and `B` = `r B <- 0.05`.
 
@@
 
-and we use a harvest-based profit function with default parameters
+Note that the positive stationary root of the model is given by \\( \frac{A-1}{B} \\), or carring capacity `K` = `r K`.  
+We consider a profits from fishing to be a function of harvest `h` and stock size `x`,  \\( \Pi(x,h) = h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x} \\), conditioned on \\( h > x \\) and \\(x > 0 \\),
 
 ``` {r  profit}
-profit <- profit_harvest(price=1, c0 = 0.01) 
+price <- 1
+c0 <- 0.01
+c1 <- 0
+profit <- profit_harvest(price=price, c0 = c0, c1=c1) 
 ````
 
-The `profit_harvest` function has the form \\( \Pi = h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x} \\), conditioned on \\( h > x \\) and \\(x > 0 \\).
-Note that the R code defines a function from another function using a trick known as a _closure_.
-Again we could write a custom profit function as long as it can take a vector stock size `x` and a scalar harvest level `h`.
-Details for provided functions can be found in the manual, i.e.
-`?profit_harvest`.
+with price `r price`, `c0` `r c0` and `c1` `r c1`.
 
-Now we must set up the discrete grids for stock size and havest levels (which will use same resolution as for stock), in order to calculate the SDP solution.   Here we set the gridsize to 100.
+``` {r }
+xmin <- 0
+xmax <- 1.5 * K
+grid_n <- 100
+````
+
+We seek a harvest policy which maximizes the discounted profit from the fishery using a stochastic dynamic programming approach over a discrete grid of stock sizes from `r xmin` to `r xmax` on a grid of `r grid_n` points, and over an identical discrete grid of possible harvest values.
 
 ``` {r  grid}
-x_grid <- seq(0, 2 * K, length = 100)  
+x_grid <- seq(xmin, xmax, length = grid_n)  
 h_grid <- x_grid  
@@
 
+``` {r pars}
+delta <- 0.05
+xT <- 0
+OptTime <- 25
+````
+
+We will determine the optimal solution over a `r OptTime` time step window with boundary condition for stock at `r xT` and discounting rate of `r delta`.
+
 # Scenarios:
 
-We calculate the stochastic transition matrix for the probability of going from any state \\(x_t \\) to any other state \\(x_{t+1}\\) the following year, for each possible choice of harvest \\( h_t \\).
-This provides a look-up table for the dynamic programming calculations.
+We use Monte Carlo integration over the noise processes to determine the transition matrix.
 
-In the Sethi case, computing the distribution over multiple sources of noise is actually quite difficult.
-Simulation turns out to be more efficient than numerically integrating over each distribution.
-
-## No Uncertainty
-
-``` {r noisefns}
-sigma_g <- 0.01    # Noise in population growth
-sigma_m <- 0.0     # noise in stock assessment measurement
-sigma_i <- 0.0     # noise in implementation of the quota
-z_g <- function() 1 
-z_m <- function() 1
-z_i <- function() 1 
-````
-Find the transition matrix
-
-``` {r  SDP_Mat}
-SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
+```{r beparallel, cache=FALSE}
+sfInit(parallel=TRUE, cpu=16)
+sfExportAll()
 ````
 
-Find the optimum solution
+``` {r policyscenarios}
+scenario <- function(policy_g, policy_m, policy_i){
 
-``` {r  find_dp_opt }
-opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
-                     profit, delta=0.05, reward=0)
+  z_g <- function() rlnorm(1,  0, policy_g) 
+  z_m <- function() rlnorm(1,  0, policy_m) 
+  z_i <- function() rlnorm(1,  0, policy_i)
+
+  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=2e4)
+  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
+                       profit, delta, reward=0)
+}
 ````
 
-Simulate
-
-``` {r  simulate }
-sims_known <- lapply(1:100, function(i){
-  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
-})
+``` {r runall}
+det <- scenario(0, 0.0, 0.0)
+g <- scenario(0.2, 0.0, 0.0)
+m <- scenario(0.0, 0.2, 0.0)
+i <- scenario(0.0, 0.0, 0.2)
+gm <- scenario(0.2, 0.2, 0.0)
+gi <- scenario(0.2, 0.0, 0.2)
+gmi <- scenario(0.2, 0.2, 0.2)
 ````
 
-## Growth uncertainty
+### plots
 
 ``` {r }
-sigma_g <- 0.15    # Noise in population growth
-z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
+require(reshape2)
+policy <- melt(data.frame(stock = x_grid, det = det$D[,1], g = g$D[,1], m = m$D[,1], gm = gm$D[,1], gi = gi$D[,1], gmi = gmi$D[,1]), id = "stock")
+ggplot(policy) + geom_point(aes(stock, stock-x_grid[value], color=variable)) + ylab("escapement") 
+ggplot(policy) + geom_smooth(aes(stock, stock-x_grid[value], color=variable))+ ylab("escapement")
+
+value <- melt(data.frame(stock = x_grid, det=det$V g = g$V, m = m$V, gm = gm$V, gi = gi$V, gmi = gmi$V), id = "stock")
+ggplot(value) + geom_point(aes(stock, value, color=variable)) + ylab("Net Present Value")
+ggplot(value) + geom_smooth(aes(stock, value, color=variable)) + ylab("Net Present Value")
 ````
-Find the transition matrix
+
+## Simulations
 
 ``` {r } 
-SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
+simulatereps <- function(opt, true_g, true_m, true_i){
+  z_g <- function() rlnorm(1,  0, true_g) 
+  z_m <- function() rlnorm(1,  0, true_m) 
+  z_i <- function() rlnorm(1,  0, true_i)
+
+  sims <- lapply(1:100, function(i){
+    ForwardSimulate(f, pars, x_grid, h_grid, x0 = K, opt$D, z_g, z_m, z_i, profit)
+  })
+
+  list(sims = sims, opt = opt, policy_uncertainty = c(policy_g, policy_m, policy_i),
+  true_stochasticity = c(true_g, true_m, true_i))
+}
 ````
 
-Find the optimum solution
+Corner cases
 
-``` {r }
-opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
-                     profit, delta=0.05, reward=0)
-````
-
-Simulate.  The real world doesn't have as much uncertainty as we do in our knowledge of the state.
-
-``` {r }
-sigma_g <- 0.05    # Noise in population growth
-z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-sims_g <- lapply(1:100, function(i){
-  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, profit=profit)
-})
-````
-
-## Growth & stock measurement uncertainty
-
-``` {r }
-sigma_g <- 0.15    # Noise in population growth
-sigma_m <- 0.15     # noise in stock assessment measurement
-z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
-z_i <- function() 1
-````
-
-Find the transition matrix.  Use the simulation method to account for the extra uncertainties
-
-``` {r }
-require(snowfall) 
-sfInit(parallel=TRUE, cpu=16)
-SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=999)
-````
-
-Find the optimum solution
-
-``` {r }
-opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
-                     profit, delta=0.05, reward=0)
-````
-
-Simulate
-
-``` {r }
-sigma_g <- 0.05    # Noise in population growth
-z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() 1
-z_i <- function() 1
-sims_gm <- lapply(1:100, function(i){
-  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
-})
-````
-
-## Growth, stock measurement & implementation uncertainty
-
-``` {r }
-sigma_g <- 0.15    # Noise in population growth
-sigma_m <- 0.15     # noise in stock assessment measurement
-sigma_i <- 0.15     # noise in implementation of the quota
-z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
-z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
-````
-
-Find the transition matrix.  Use the simulation method to account for the extra uncertainties
-
-``` {r }
-SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=999)
-````
-
-Find the optimum solution
-
-``` {r }
-opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
-                     profit, delta=0.05, reward=0)
-````
-
-Simulate
-
-``` {r }
-sigma_g <- 0.05    # Noise in population growth
-z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() 1
-z_i <- function() 1
-sims_gmi <- lapply(1:100, function(i){
-  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
-})
-````
-
-## Summarize and plot the results
-
-R makes it easy to work with this big replicate data set.  We make data tidy (melt), fast (data.tables), and nicely labeled.
-
-``` {r  tidy}
-
-sims <- list(known = sims_known, growth = sims_g, growth_stock = sims_gm, growth_stock_harvest = sims_gmi)
-
-dat <- melt(sims, id=names(sims_known[[1]]))  
-dt <- data.table(dat)
-setnames(dt, c("L2", "L1"), c("reps", "uncertainty")) # names are nice
-````
-
-### Plots
-
-Let's begin by looking at the dynamics of a single replicate.
-The line shows Reed's S, the level above which the stock should be harvested (where catch should be the difference between stock and S).
-To confirm that this policy is being followed, note that harvesting only occurs when the stock is above this line, and harvest is proportional to the amount by which it is above.
-Change the replicate `reps==` to see the results from a different replicate.
-
-``` {r  onerep }
-ggplot(subset(dt,reps==1)) +
-  geom_line(aes(time, fishstock)) +
-  geom_abline(intercept=opt$S, slope = 0) +
-  geom_line(aes(time, harvest), col="darkgreen") + 
-  facet_wrap(~uncertainty) 
-````
-
-This plot summarizes the stock dynamics by visualizing the replicates. Reed's S shown again.
-
-``` {r  all}
-p1 <- ggplot(dt) + geom_abline(intercept=opt$S, slope = 0) 
-p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.2) + facet_wrap(~uncertainty)
-````
-
-We can also look at the harvest dynamics:
-
-``` {r  harvestplot}
-p1 + geom_line(aes(time, harvest, group = reps), alpha = 0.1, col="darkgreen") + facet_wrap(~uncertainty)
-````
-
-This strategy is supposed to be a constant-escapement strategy. We can visualize the escapement:
-
-``` {r  escapement}
-p1 + geom_line(aes(time, escapement, group = reps), alpha = 0.1, col="darkgrey") + facet_wrap(~uncertainty)
-````
-
-``` {r }
-ggplot(subset(dt,reps==1)) +
-  geom_line(aes(time, profit))  + facet_wrap(~uncertainty)
-
-````
-
-``` {r }
-profits <-dt[ , sum(profit), by=c("reps", "uncertainty")] 
-ggplot(profits) + geom_histogram(aes(V1)) + facet_wrap(~uncertainty)
-````
-
-Summary stats
-
-``` {r }
-profits[, mean(V1), by=uncertainty]
-profits[, sd(V1), by=uncertainty]
+```{r }
+base <- simulatereps(det, 0, 0, 0)
+full <- simulatereps(gmi, .2, .2, .2)
+cautious <- simulatereps(gmi, 0, 0, 0)
+reckless <- simulatereps(det, .2, .2, .2)
 ````

### 2012-06-14 inst/examples/Sethi_policyfns.Rmd
updated run on policyfns

@@
 
-Clear the workspace and load package dependencies: 
 ``` {r  setup, cache=FALSE}
+## Clear the workspace and load package dependencies: 
 rm(list=ls())   
@@
 
-Chose the state equation / population dynamics function
+We consider a Beverton Holt state equation governing population dynamics, \\( f(x,h) = \frac{A x}{1 + B x} \\)
 
@@
 
-That is, \\( f(x,h) = \frac{A x}{1 + B x} \\)
-
-We must now define parameters for the function.  Note that the positive stationary root of the model is given by \\( \frac{A-1}{B} \\), which we'll store for future reference as `K`.
+With parameters `A` = `r A <- 1.5` and `B` = `r B <- 0.05`.
 
@@
 
-and we use a harvest-based profit function with default parameters
+Note that the positive stationary root of the model is given by \\( \frac{A-1}{B} \\), or carring capacity `K` = `r K`.  
+We consider a profits from fishing to be a function of harvest `h` and stock size `x`,  \\( \Pi(x,h) = h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x} \\), conditioned on \\( h > x \\) and \\(x > 0 \\),
 
 ``` {r  profit}
-profit <- profit_harvest(price=1, c0 = 0.01) 
+price <- 1
+c0 <- 0.01
+c1 <- 0
+profit <- profit_harvest(price=price, c0 = c0, c1=c1) 
 ````
 
-The `profit_harvest` function has the form \\( \Pi = h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x} \\), conditioned on \\( h > x \\) and \\(x > 0 \\).
-We set up the discrete grids for stock size and havest levels (which will use same resolution as for stock), in order to calculate the SDP solution.
-Here we set the gridsize to 100.
+with price `r price`, `c0` `r c0` and `c1` `r c1`.
+
+``` {r }
+xmin <- 0
+xmax <- 1.5 * K
+grid_n <- 100
+````
+
+We seek a harvest policy which maximizes the discounted profit from the fishery using a stochastic dynamic programming approach over a discrete grid of stock sizes from `r xmin` to `r xmax` on a grid of `r grid_n` points, and over an identical discrete grid of possible harvest values.
 
 ``` {r  grid}
-x_grid <- seq(0, 1.5 * K, length = 100)  
+x_grid <- seq(xmin, xmax, length = grid_n)  
 h_grid <- x_grid  
 ````
+
+``` {r miscpars}
+delta <- 0.05
+xT <- 0
+OptTime <- 25
+````
+
+We will determine the optimal solution over a `r OptTime` time step window with boundary condition for stock at `r xT` and discounting rate of `r delta`.
+Different scenarios introduce different assumptions about the sources of noise.
+Unlike `r knitcitations::citep("10.1016/j.jeem.2004.11.005")`, we use log normal insead of uniform noise, which requires Monte Carlo integration to estimate the transition matrix.
+Note that we also have a Beverton-Holt recruitment function instead of the logistic map, and differ in the precise choice of parameters for the state equation, noise, discounting, profit function, etc.
 
@@
 ````
-Note that `SDP_Mat` is specified from the calculation above, as are our grids and our profit function.
-`OptTime` is the stopping time.
-`xT` specifies a boundary condition at the stopping time.
-A reward for meeting this boundary must be specified for it to make any difference.
-`delta` indicates the economic discount rate.
-Again, details are in the function documentation.
 
 ### Find the optimum by dynamic programming
-
-Bellman's algorithm to compute the optimal solution for all possible trajectories.
 
@@
 ````
+
+Note that growth noise gives the constant escapement solution, as expected, but large measurement noise results in raising the maximum escapement, particularly at large stock sizes.
+If the measured population was unusually high you might assume it was a measurement error and not increase your target harvest immediately, so this makes some intuitive sense.

### 2012-06-14 inst/examples/value_of_information.Rmd
updated run on policyfns

@@
 
-``` {r pars}
+``` {r miscpars}
 delta <- 0.05
@@
 
-```{r beparallel, cache=FALSE}
+``` {r beparallel, cache=FALSE}
+require(snowfall)
 sfInit(parallel=TRUE, cpu=16)
-sfExportAll()
 ````
@@
 
-``` {r }
+``` {r sethiplots}
 require(reshape2)

### 2012-06-14 inst/examples/value_of_information.Rmd
value-of-information for corner case scenarios
value-of-information for corner case scenarios, now with plots

@@
 
-value <- melt(data.frame(stock = x_grid, det=det$V g = g$V, m = m$V, gm = gm$V, gi = gi$V, gmi = gmi$V), id = "stock")
+value <- melt(data.frame(stock = x_grid, det=det$V, g = g$V, m = m$V, gm = gm$V, gi = gi$V, gmi = gmi$V), id = "stock")
 ggplot(value) + geom_point(aes(stock, value, color=variable)) + ylab("Net Present Value")
@@
 base <- simulatereps(det, 0, 0, 0)
+reckless <- simulatereps(det, .2, .2, .2)
+````
+
+```{r }
 full <- simulatereps(gmi, .2, .2, .2)
 cautious <- simulatereps(gmi, 0, 0, 0)
-reckless <- simulatereps(det, .2, .2, .2)
 ````
@@
 ``` {r biblio, echo=FALSE, results="asis"}
-I(knitcitations::bibliography())
+I(print(knitcitations::bibliography(), "html"))
 ````

### 2012-06-15 inst/examples/value_of_information.Rmd
updated plots, deterministic example, summary stats on sims

@@
 knitcitations::cleanbib()
+cache=FALSE
+plotcache=FALSE
 ````
@@
 
+``` {r not_all_zero}
+det <- scenario(0.01, 0.0, 0.0)
+````
+
 ### plots
 
-``` {r sethiplots}
+``` {r sethiplots, cache=cacheplots}
 require(reshape2)
@@
 
-  list(sims = sims, opt = opt, policy_uncertainty = c(policy_g, policy_m, policy_i),
-  true_stochasticity = c(true_g, true_m, true_i))
+  list(sims = sims, opt = opt, true_stochasticity = c(true_g, true_m, true_i))
 }
@@
 
-```{r }
+``` {r cache=cache}
 base <- simulatereps(det, 0, 0, 0)
@@
 
-```{r }
+``` {r cache=cache}
 full <- simulatereps(gmi, .2, .2, .2)
 cautious <- simulatereps(gmi, 0, 0, 0)
+````
+
+``` {r tidy, cache=FALSE}
+sims <- list(base = base$sims, full = full$sims, reckless=reckless$sims, cautious=cautious$sims)
+dat <- melt(sims, id=names(sims[[1]][[1]]))  
+dt <- data.table(dat)
+setnames(dt, c("L2", "L1"), c("reps", "uncertainty")) # names are nice
+````
+
+### Plots
+
+``` {r  onerep, cache=plotcache }
+ggplot(subset(dt,reps==1)) +
+  geom_line(aes(time, fishstock)) +
+  geom_abline(intercept=opt$S, slope = 0) +
+  geom_line(aes(time, harvest), col="darkgreen") + 
+  facet_wrap(~uncertainty) 
+````
+
+This plot summarizes the stock dynamics by visualizing the replicates. Reed's S shown again.
+
+``` {r  fig.cap="the induced dynamics in the stock size over time, for all replicates, by scenario", cache=plotcache}
+p1 <- ggplot(dt) + geom_abline(intercept=opt$S, slope = 0) 
+p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.1) + facet_wrap(~uncertainty)
+````
+
+``` {r fig.cap="The profits made in each time interval of a single replicate, by scenario", cache=plotcache}
+ggplot(subset(dt,reps==1)) +
+  geom_line(aes(time, profit))  + facet_wrap(~uncertainty)
+
+````
+
+``` {r fig.cap="the distribution of profits by scenario", cache=plotcache}
+profits <-dt[ , sum(profit), by=c("reps", "uncertainty")] 
+ggplot(profits) + geom_histogram(aes(V1)) + facet_wrap(~uncertainty)
+````
+
+Summary statistics
+
+``` {r, cache=FALSE}
+profits[, mean(V1), by=uncertainty]
+profits[, sd(V1), by=uncertainty]
 ````
@@
 ``` {r biblio, echo=FALSE, results="asis"}
-I(print(knitcitations::bibliography(), "html"))
+print(knitcitations::bibliography(), "html")
 ````

### 2012-06-15 inst/examples/value_of_information.Rmd
fixed plots

--- 2012-06-14 inst/examples/value_of_information.Rmd
@@
 
+``` {r not_all_zero}
+det <- scenario(0.01, 0.0, 0.0)
+````
+
 ### plots
 
-``` {r sethiplots}
+``` {r sethiplots, cache=FALSE}
 require(reshape2)
@@
 
-```{r }
+``` {r cache=FALSE}
 base <- simulatereps(det, 0, 0, 0)
@@
 
-```{r }
+``` {r cache=FALSE}
 full <- simulatereps(gmi, .2, .2, .2)
 cautious <- simulatereps(gmi, 0, 0, 0)
+````
+
+``` {r tidy, cache=FALSE}
+sims <- list(base = base$sims, full = full$sims, reckless=reckless$sims, cautious=cautious$sims)
+dat <- melt(sims, id=names(sims[[1]][[1]]))  
+dt <- data.table(dat)
+setnames(dt, c("L2", "L1"), c("reps", "uncertainty")) # names are nice
+````
+
+### Plots
+
+``` {r  onerep, cache=FALSE }
+ggplot(subset(dt,reps==1)) +
+  geom_line(aes(time, fishstock)) +
+  geom_line(aes(time, harvest), col="darkgreen") + 
+  facet_wrap(~uncertainty) 
+````
+
+This plot summarizes the stock dynamics by visualizing the replicates.
+
+``` {r  fig.cap="the induced dynamics in the stock size over time, for all replicates, by scenario", cache=FALSE}
+p1 <- ggplot(dt) 
+p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.1) + facet_wrap(~uncertainty)
+````
+
+``` {r fig.cap="The profits made in each time interval of a single replicate, by scenario", cache=FALSE}
+ggplot(subset(dt,reps==1)) +
+  geom_line(aes(time, profit))  + facet_wrap(~uncertainty)
+
+````
+
+``` {r fig.cap="the distribution of profits by scenario", cache=FALSE}
+profits <-dt[ , sum(profit), by=c("reps", "uncertainty")] 
+ggplot(profits) + geom_histogram(aes(V1)) + facet_wrap(~uncertainty)
+````
+
+Summary statistics
+
+``` {r, cache=FALSE}
+profits[, mean(V1), by=uncertainty]
+profits[, sd(V1), by=uncertainty]
 ````

### 2012-06-15 inst/examples/value_of_information.Rmd
summary stats

@@
 
-``` {r cache=FALSE}
+``` {r }
 base <- simulatereps(det, 0, 0, 0)
@@
 
-``` {r cache=FALSE}
+``` {r }
 full <- simulatereps(gmi, .2, .2, .2)
@@
 
-``` {r tidy, cache=FALSE}
+``` {r tidy}
 sims <- list(base = base$sims, full = full$sims, reckless=reckless$sims, cautious=cautious$sims)
@@
 
-``` {r  onerep, cache=FALSE }
+``` {r  onerep}
 ggplot(subset(dt,reps==1)) +
@@
 
-``` {r  fig.cap="the induced dynamics in the stock size over time, for all replicates, by scenario", cache=FALSE}
+``` {r  fig.cap="the induced dynamics in the stock size over time, for all replicates, by scenario"}
 p1 <- ggplot(dt) 
@@
 
-``` {r fig.cap="The profits made in each time interval of a single replicate, by scenario", cache=FALSE}
+``` {r fig.cap="The profits made in each time interval of a single replicate, by scenario"}
 ggplot(subset(dt,reps==1)) +
@@
 
-``` {r fig.cap="the distribution of profits by scenario", cache=FALSE}
+``` {r fig.cap="the distribution of profits by scenario"}
 profits <-dt[ , sum(profit), by=c("reps", "uncertainty")] 
@@
 
-``` {r, cache=FALSE}
+``` {r cache=FALSE}
 profits[, mean(V1), by=uncertainty]

### 2012-06-15 inst/examples/Reed.Rmd
allee voi example

@@
 opts_knit$set(upload.fun = socialR::flickr.url)
-options(device = function(width = 5, height = 5) {
-    pdf(NULL, width = width, height = height)
-})
+#options(device = function(width = 5, height = 5) {
+#    pdf(NULL, width = width, height = height)
+#})
 ````
@@
 ``` {r }
-f <- BevHolt
-````
-
-Note that the `pdg_control` pacakge already has a definition for the `BevHolt` function, (typing the function name prints the function)
-
-``` {r }
-BevHolt
-````
-
-That is, \( f(x,h) = \frac{A x}{1 + B x} \)
-
-Of course we could pass in any custom function of stocksize `x`, harvest `h` and parameter vector `p` in place of `BevHolt`.
-Note that we would need to write this function explicitly so that it can take vector values of `x` (i.e.
-uses `sapply`), an annoying feature of `R` for users comming from Matlab.
-
-We must now define parameters for the function.  Note that the positive stationary root of the model is given by \( (A-1)/B \), which we'll store for future reference as `K`.
-
-``` {r }
-pars <- c(1.5, 0.05)
-K <- (pars[1] - 1)/pars[2]
+f <- RickerAllee
+K <- 4 
+xT <- 2 # final value, also allee threshold
+pars <- c(1.5, K, xT) 
 ````
@@
 ``` {r  profit}
-profit <- profit_harvest(price=1, c0 = 0.01) 
+profit <- profit_harvest(price=1, c0 = 0.01, c1=0) 
 ````
@@
 ``` {r policyfn_plot}
-qplot(x_grid, x_grid - x_grid[opt$D[,1]], xlab="stock size", ylab="escapement")
+q1 <- qplot(x_grid, x_grid - x_grid[opt$D[,1]], xlab="stock size", ylab="escapement") + 
+geom_point(aes(x,y), data=data.frame(x=opt$S, y=opt$S), col="red")
+q1
 ````
@@
 ``` {r valuefn_plot}
-qplot(x_grid, opt$V, xlab="stock size", ylab="value")
+q2 <- qplot(x_grid, opt$V, xlab="stock size", ylab="value") + 
+geom_vline(xintercept=opt$S)
+q2
 ````
@@
 ````
-
-We can also look at the harvest dynamics:
-
-``` {r  p2}
-p1 + geom_line(aes(time, harvest, group = reps), alpha = 0.1, col="darkgreen")
-````
-
-This strategy is supposed to be a constant-escapement strategy. We can visualize the escapement:
-
-``` {r  p3}
-p1 + geom_line(aes(time, escapement, group = reps), alpha = 0.1, col="darkgrey")
-````
-
-### Visualizing the optimal policy
-Note that when the boundary is sufficiently far away, i.e.
-for the first couple timesteps, the optimal policy is stationary.
-The optimal policy is shown here over time, where the color indicates the harvest recommended for each possible stock value at that time (shown on the vertical axis).
-Note that below a certain stock value, harvesting is not recommended and the dots turn red (Reed's constant escapement rule!)  However, at very low values, harvesting starts again (orange dots), because of the allee effect - these populations are doomed anyway, so may as well fish all that remains.
-
-Note that interestingly, populations just below the allee threshold are given the chance to be rescued stochastically early on - that small chance that they recover is worth the expected loss.
-The "no-harvest" zones stand out clearly in the red areas of this graph.
-
-``` {r  policy, fig.width=9}
-policy <- melt(opt$D)
-policy_zoom <- subset(policy, x_grid[Var1] < max(dt$fishstock) )
-p5 <- ggplot(policy_zoom) + 
-  geom_point(aes(Var2, (x_grid[Var1]), col=h_grid[value])) + 
-  labs(x = "time", y = "fishstock") +
-  scale_colour_gradientn(colours = rainbow(4)) +
-  geom_abline(intercept=opt$S, slope = 0) +
-  geom_abline(intercept=xT, slope=0, lty=2)
-p5
-````
-
-The harvest intensity is limited by the stock size.
-
-``` {r  policy2, fig.width=10}
-p6 <- ggplot(policy_zoom) + 
-  geom_point(aes(Var2, (x_grid[Var1]), col=x_grid[Var1] - h_grid[value])) + 
-  labs(x = "time", y = "fishstock") +
-  scale_colour_gradientn(colours = rainbow(4)) +
-  geom_abline(intercept=opt$S, slope = 0) +
-  geom_abline(intercept=xT, slope=0, lty=2)
-p6 + geom_line(aes(time, fishstock, group = reps), alpha = 0.1, data=dt)
-````

### 2012-06-15 inst/examples/value_of_information_allee.Rmd
allee voi example

--- 2012-06-15 inst/examples/value_of_information.Rmd
@@
 
-# Calculating the value of information
+# Calculating the value of information with highly nonlinear value function
 
  Implements a numerical version of the SDP described in `r knitcitations::citep("10.1016/j.jeem.2004.11.005")`.
- Compute the optimal solution under different forms of uncertainty.
+ Compute the optimal solution under different forms of uncertainty, but under strong allee dynamics
 
@@
 
-We consider a Beverton Holt state equation governing population dynamics, \\( f(x,h) = \frac{A x}{1 + B x} \\)
+We consider the state dynamics
 
 ``` {r }
-f <- BevHolt
+f <- RickerAllee
+K <- 4 
+xT <- 2 # final value, also allee threshold
+pars <- c(1.5, K, xT) 
+f
 ````
 
-With parameters `A` = `r A <- 1.5` and `B` = `r B <- 0.05`.
-
-``` {r }
-pars <- c(1.5, 0.05)
-K <- (pars[1] - 1)/pars[2]
-````
-
-Note that the positive stationary root of the model is given by \\( \frac{A-1}{B} \\), or carring capacity `K` = `r K`.  
 We consider a profits from fishing to be a function of harvest `h` and stock size `x`,  \\( \Pi(x,h) = h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x} \\), conditioned on \\( h > x \\) and \\(x > 0 \\),
@@
 det <- scenario(0, 0.0, 0.0)
-g <- scenario(0.2, 0.0, 0.0)
-m <- scenario(0.0, 0.2, 0.0)
-i <- scenario(0.0, 0.0, 0.2)
-gm <- scenario(0.2, 0.2, 0.0)
-gi <- scenario(0.2, 0.0, 0.2)
-gmi <- scenario(0.2, 0.2, 0.2)
+g <- scenario(0.1, 0.0, 0.0)
+m <- scenario(0.0, 0.1, 0.0)
+i <- scenario(0.0, 0.0, 0.1)
+gm <- scenario(0.1, 0.1, 0.0)
+gi <- scenario(0.1, 0.0, 0.1)
+gmi <- scenario(0.1, 0.1, 0.1)
 ````
@@
 ``` {r not_all_zero}
-det <- scenario(0.01, 0.0, 0.0)
+det <- scenario(0.001, 0.0, 0.0)
 ````
@@
 base <- simulatereps(det, 0, 0, 0)
-reckless <- simulatereps(det, .2, .2, .2)
+reckless <- simulatereps(det, .1, .1, .1)
 ````
@@
 ``` {r }
-full <- simulatereps(gmi, .2, .2, .2)
+full <- simulatereps(gmi, .1, .1, .1)
 cautious <- simulatereps(gmi, 0, 0, 0)

### 2012-06-18 inst/examples/value_of_information.Rmd
new runs

@@
 
-``` {r } 
+``` {r simfn} 
 simulatereps <- function(opt, true_g, true_m, true_i){
@@
 
-  list(sims = sims, opt = opt, true_stochasticity = c(true_g, true_m, true_i))
+#  list(sims = sims, opt = opt, true_stochasticity = c(true_g, true_m, true_i))
+  sims
 }
@@
 
-Corner cases
+All cases
 
-``` {r }
-base <- simulatereps(det, 0, 0, 0)
-reckless <- simulatereps(det, .2, .2, .2)
+``` {r runallsims} 
+policyfn <- list(det=det, g=g, m=m, i=i, gm=gm, gi=gi, gmi=gmi)
+noise <- list(s0=c(0,0,0), sg=c(.2, 0, 0), sm=c(0, .2, 0), si=c(0,0,.2), sgm=c(.2, .2, 0), sgi=c(.2, 0, .2), sgmi=c(.2, .2, .2)) 
+allcases <- lapply(policyfn, function(policyfn_i){
+  lapply(noise, function(noise_i){
+    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3]
+  })
+})
 ````
 
-``` {r }
-full <- simulatereps(gmi, .2, .2, .2)
-cautious <- simulatereps(gmi, 0, 0, 0)
-````
-
-``` {r tidy}
-sims <- list(base = base$sims, full = full$sims, reckless=reckless$sims, cautious=cautious$sims)
+``` {r tidyall}
+sims <- unlist(allcases, recursive=FALSE)
 dat <- melt(sims, id=names(sims[[1]][[1]]))  
@@
 
-``` {r  fig.cap="the induced dynamics in the stock size over time, for all replicates, by scenario"}
+``` {r stock, fig.cap="the induced dynamics in the stock size over time, for all replicates, by scenario"}
 p1 <- ggplot(dt) 
@@
 
-``` {r fig.cap="The profits made in each time interval of a single replicate, by scenario"}
+``` {r profits_time, fig.cap="The profits made in each time interval of a single replicate, by scenario"}
 ggplot(subset(dt,reps==1)) +
@@
 
-``` {r fig.cap="the distribution of profits by scenario"}
+``` {r profits, fig.cap="the distribution of profits by scenario"}
 profits <-dt[ , sum(profit), by=c("reps", "uncertainty")] 

### 2012-06-18 inst/examples/value_of_information_allee.Rmd
new runs
table of final results

@@
-`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="value_of_information/", verbose=TRUE or`
+`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="value_of_information_allee/", verbose=TRUE or`
 
@@
 
-Corner cases
+All cases
 
-``` {r }
-base <- simulatereps(det, 0, 0, 0)
-reckless <- simulatereps(det, .1, .1, .1)
+``` {r runallsims} 
+policyfn <- list(det=det, g=g, m=m, i=i, gm=gm, gi=gi, gmi=gmi)
+noise <- list(s0=c(0,0,0), sg=c(.2, 0, 0), sm=c(0, .2, 0), si=c(0,0,.2), sgm=c(.2, .2, 0), sgi=c(.2, 0, .2), sgmi=c(.2, .2, .2)) 
+allcases <- lapply(policyfn, function(policyfn_i){
+  lapply(noise, function(noise_i){
+    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3])
+  })
+})
 ````
 
-``` {r }
-full <- simulatereps(gmi, .1, .1, .1)
-cautious <- simulatereps(gmi, 0, 0, 0)
-````
-
-``` {r tidy}
-sims <- list(base = base$sims, full = full$sims, reckless=reckless$sims, cautious=cautious$sims)
+``` {r tidyall}
+sims <- unlist(allcases, recursive=FALSE)
 dat <- melt(sims, id=names(sims[[1]][[1]]))  
@@
 
-``` {r  onerep}
+``` {r  onerep, dependson="tidyall"}
 ggplot(subset(dt,reps==1)) +
@@
 
-``` {r  fig.cap="the induced dynamics in the stock size over time, for all replicates, by scenario"}
+``` {r stock, fig.cap="the induced dynamics in the stock size over time, for all replicates, by scenario", dependson="tidyall"}
 p1 <- ggplot(dt) 
@@
 
-``` {r fig.cap="The profits made in each time interval of a single replicate, by scenario"}
+``` {r profits_time, fig.cap="The profits made in each time interval of a single replicate, by scenario", dependson="tidyall"}
 ggplot(subset(dt,reps==1)) +
@@
 
-``` {r fig.cap="the distribution of profits by scenario"}
+``` {r profits, fig.cap="the distribution of profits by scenario", dependson="tidyall"}
 profits <-dt[ , sum(profit), by=c("reps", "uncertainty")] 
@@
 
-``` {r cache=FALSE}
-profits[, mean(V1), by=uncertainty]
-profits[, sd(V1), by=uncertainty]
+``` {r summarystats, cache=FALSE}
+means <- profits[, mean(V1), by=uncertainty]
+sds <- profits[, sd(V1), by=uncertainty]
+````
+
+``` {r prettytable, cache=FALSE, results="asis"}
+require(xtable)
+uncertainties <- c("deter", "growth", "measure", "implement", "growth+measure", "growth+implement", "all")
+print(xtable(matrix(means$V1, nrow=7, dimnames=list(uncertainties, uncertainties))), type="html")
+print(xtable(matrix(sds$V1, nrow=7, dimnames=list(uncertainties, uncertainties))), type="html")
 ````

### 2012-06-18 inst/examples/value_of_information_allee.Rmd
allee example with table

@@
 uncertainties <- c("deter", "growth", "measure", "implement", "growth+measure", "growth+implement", "all")
-print(xtable(matrix(means$V1, nrow=7, dimnames=list(uncertainties, uncertainties))), type="html")
-print(xtable(matrix(sds$V1, nrow=7, dimnames=list(uncertainties, uncertainties))), type="html")
+print(xtable(matrix(means$V1, nrow=7, dimnames=list(uncertainties, uncertainties)), caption="Mean realized net present value over simulations"), type="html")
+print(xtable(matrix(sds$V1, nrow=7, dimnames=list(uncertainties, uncertainties)), caption="Standard deviation in realized net present value over simulations"), type="html")
 ````

### 2012-06-19 inst/examples/value_of_information.Rmd

@@
 
-``` {r sethiplots, cache=FALSE}
+``` {r sethiplots, dependson="runall"}
 require(reshape2)
@@
   lapply(noise, function(noise_i){
-    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3]
+    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3])
   })
@@
 
-``` {r stock, fig.cap="the induced dynamics in the stock size over time, for all replicates, by scenario"}
+``` {r stock, fig.cap="the induced dynamics in the stock size over time, for all replicates, by scenario", dependson="tidyall"}
 p1 <- ggplot(dt) 
@@
 
-``` {r profits_time, fig.cap="The profits made in each time interval of a single replicate, by scenario"}
+``` {r profits_time, fig.cap="The profits made in each time interval of a single replicate, by scenario", dependson="tidyall"}
 ggplot(subset(dt,reps==1)) +
@@
 
-``` {r profits, fig.cap="the distribution of profits by scenario"}
+``` {r profits, fig.cap="the distribution of profits by scenario", dependson="tidyall"}
 profits <-dt[ , sum(profit), by=c("reps", "uncertainty")] 

### 2012-06-19 inst/examples/voi_sethi_parameters.Rmd
voi with sethi parameterization

--- 2012-06-19 inst/examples/value_of_information.Rmd
@@
-`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="value_of_information/", verbose=TRUE or`
+`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="voi_sethi_parameters/", verbose=TRUE or`
 
@@
 
-We consider a Beverton Holt state equation governing population dynamics, \\( f(x,h) = \frac{A x}{1 + B x} \\)
+`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10, cache.path="value_of_information/" or`
+
+``` {r  echo=FALSE, cache=FALSE }
+opts_knit$set(upload.fun = socialR::flickr.url)
+options(device = function(width = 5, height = 5) {
+    pdf(NULL, width = width, height = height)
+})
+knitcitations::cleanbib()
+````
+
+Chose the state equation / population dynamics function
 
 ``` {r }
-f <- BevHolt
+f <- function(x,h,p){
+	S = x - h
+	p[1] * S * (1 - S/p[2]) + S
+}
 ````
 
-With parameters `A` = `r A <- 1.5` and `B` = `r B <- 0.05`.
+With parameters `r` = `r r <- 1` and `K` = `r K <- 100`.
 
 ``` {r }
-pars <- c(1.5, 0.05)
-K <- (pars[1] - 1)/pars[2]
+pars <- c(r, K)
 ````
 
-Note that the positive stationary root of the model is given by \\( \frac{A-1}{B} \\), or carring capacity `K` = `r K`.  
 We consider a profits from fishing to be a function of harvest `h` and stock size `x`,  \\( \Pi(x,h) = h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x} \\), conditioned on \\( h > x \\) and \\(x > 0 \\),
@@
 price <- 1
-c0 <- 0.01
+c0 <- 0.0
 c1 <- 0
@@
 
-with price `r price`, `c0` `r c0` and `c1` `r c1`.
+with price = `r price`, `c0` = `r c0` and `c1` = `r c1`.
 
@@
 
-  z_g <- function() rlnorm(1,  0, policy_g) 
-  z_m <- function() rlnorm(1,  0, policy_m) 
-  z_i <- function() rlnorm(1,  0, policy_i)
+  z_g <- function() 1+(2*runif(1, 0,  1)-1) * policy_g
+  z_m <- function() 1+(2*runif(1, 0,  1)-1) * policy_m
+  z_i <- function() 1+(2*runif(1, 0,  1)-1) * policy_i
 
@@
 ``` {r runall}
-det <- scenario(0, 0.0, 0.0)
-g <- scenario(0.2, 0.0, 0.0)
-m <- scenario(0.0, 0.2, 0.0)
-i <- scenario(0.0, 0.0, 0.2)
-gm <- scenario(0.2, 0.2, 0.0)
-gi <- scenario(0.2, 0.0, 0.2)
-gmi <- scenario(0.2, 0.2, 0.2)
-````
-
-``` {r not_all_zero}
-det <- scenario(0.01, 0.0, 0.0)
+det <- scenario(0.1, 0.0, 0.0)
+g   <- scenario(0.5, 0.0, 0.0)
+m   <- scenario(0.0, 0.5, 0.0)
+i   <- scenario(0.0, 0.0, 0.5)
+gm  <- scenario(0.5, 0.5, 0.0)
+gi  <- scenario(0.5, 0.0, 0.5)
+im  <- scenario(0.0, 0.5, 0.5)
+gmi <- scenario(0.5, 0.5, 0.5)
 ````
@@
 require(reshape2)
-policy <- melt(data.frame(stock = x_grid, det = det$D[,1], g = g$D[,1], m = m$D[,1], gm = gm$D[,1], gi = gi$D[,1], gmi = gmi$D[,1]), id = "stock")
-ggplot(policy) + geom_point(aes(stock, stock-x_grid[value], color=variable)) + ylab("escapement") 
-ggplot(policy) + geom_smooth(aes(stock, stock-x_grid[value], color=variable))+ ylab("escapement")
+policy <- melt(data.frame(stock = x_grid, det = det$D[,1], g = g$D[,1], m = m$D[,1], i= m$D[,i], gm = gm$D[,1], gi = gi$D[,1], gmi = gmi$D[,1]), id = "stock")
+ggplot(policy) + geom_point(aes(stock, stock-x_grid[value], color=variable)) 
+	geom_smooth(aes(stock, stock-x_grid[value], color=variable)) + ylab("escapement")
+
+ggplot(policy) + geom_point(aes(stock, stock-x_grid[value], color=variable)) 
+	geom_smooth(aes(stock, x_grid[value], color=variable)) + ylab("harvest")
 
 value <- melt(data.frame(stock = x_grid, det=det$V, g = g$V, m = m$V, gm = gm$V, gi = gi$V, gmi = gmi$V), id = "stock")
-ggplot(value) + geom_point(aes(stock, value, color=variable)) + ylab("Net Present Value")
+ggplot(value) + geom_point(aes(stock, value, color=variable)) +
 	ggplot(value) + geom_smooth(aes(stock, value, color=variable)) + ylab("Net Present Value")
@@
 
-``` {r profits_time, fig.cap="The profits made in each time interval of a single replicate, by scenario", dependson="tidyall"}
-ggplot(subset(dt,reps==1)) +
-  geom_line(aes(time, profit))  + facet_wrap(~uncertainty)
-
-````
-
 ``` {r profits, fig.cap="the distribution of profits by scenario", dependson="tidyall"}
@@
 require(xtable)
-uncertainties <- c("deter", "growth", "measure", "implement", "growth+measure", "growth+implement", "all")
+uncertainties <- c("deterministic", "growth", "measure", "implement", "growth+measure", "growth+implement", "measure+implement", "all")
 print(xtable(matrix(means$V1, nrow=7, dimnames=list(uncertainties, uncertainties))), type="html")
@@
 print(knitcitations::bibliography(), "html")
-````
+`

### 2012-06-19 inst/examples/value_of_information.Rmd
debug growth on value_of_information

@@
 
+**quick debug check -- make z_g shocks only negative to confirm growth noise isn't good**
+
 ``` {r simfn} 
 simulatereps <- function(opt, true_g, true_m, true_i){
-  z_g <- function() rlnorm(1,  0, true_g) 
+  z_g <- function() min(rlnorm(1,  0, true_g), 1)
   z_m <- function() rlnorm(1,  0, true_m) 
@@
 
-``` {r runallsims} 
+``` {r runallsims, dependson="simfn"} 
 policyfn <- list(det=det, g=g, m=m, i=i, gm=gm, gi=gi, gmi=gmi)
@@
 
-``` {r tidyall}
+``` {r tidyall, dependson="runallsims"}
 sims <- unlist(allcases, recursive=FALSE)

### 2012-06-19 inst/examples/value_of_information.Rmd
restore original value_of_information (without all-negative growth shocks)

@@
 
-**quick debug check -- make z_g shocks only negative to confirm growth noise isn't good**
-
 ``` {r simfn} 
 simulatereps <- function(opt, true_g, true_m, true_i){
-  z_g <- function() min(rlnorm(1,  0, true_g), 1)
+  z_g <- function() rlnorm(1,  0, true_g)
   z_m <- function() rlnorm(1,  0, true_m) 

### 2012-06-20 inst/examples/Reed.Rmd
Reed exploring
Reed with uniform small noise

@@
 opts_knit$set(upload.fun = socialR::flickr.url)
-#options(device = function(width = 5, height = 5) {
-#    pdf(NULL, width = width, height = height)
-#})
+orig = getOptions("device")
+options(device = function(width = 5, height = 5) {
+    pdf(NULL, width = width, height = height)
+})
+knitcitations::cleanbib()
 ````
@@
 # Reed Model
- * author Carl Boettiger, <cboettig@gmail.com>
- * license: CC0
 
- Implements a numerical version of the SDP described in:
+ * Author [Carl Boettiger](http://carlboettiger.info), <cboettig@gmail.com>
+ * License: [CC0](http://creativecommons.org/publicdomain/zero/1.0/)
+ * Description:  Implements a numerical version of the SDP described in `r knitcitations::citet("10.1016/0095-0696(79)90014-7")`.
 
-   Reed, W.J., 1979. Optimal Escapement Levels in Stochastic
-   and Deterministic Harvesting Models. Journal of Environmental 
-   Economics and Management. 6: 350-363.
-
-Clear the workspace and load package dependencies: 
-``` {r  setup, echo=FALSE}
-rm(list=ls())   
+``` {r  setup, echo=FALSE, cache=FALSE}
+# load required libraries
 require(pdgControl)
@@
 require(data.table)
-````
-
-### Define parameters
-
-``` {r }
-gridsize <- 100   # gridsize (discretized population)
-sigma_g <- 0.2    # Noise in population growth
-sigma_m <- 0.     # noise in stock assessment measurement
-sigma_i <- 0.     # noise in implementation of the quota
-````
-
-we'll use log normal noise functions. 
-For Reed, only `z_g` will be random.
-Sethi et al will add the other forms
-
-``` {r  noise_dists}
-z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
-z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
+rm(list=ls())
 ````
@@
 ``` {r }
-f <- RickerAllee
-K <- 4 
-xT <- 2 # final value, also allee threshold
-pars <- c(1.5, K, xT) 
+#f <- function(x,h,p){
+#	S = x - h
+#	p[1] * S * (1 - S/p[2]) + S
+#}
 ````
 
-and we use a harvest-based profit function with default parameters
+With parameters `r` = `r r <- 1` and `K` = `r K <- 100`.
+
+``` {r }
+#pars <- c(r, K)
+````
+
+## OR
+
+We consider a Beverton Holt state equation governing population dynamics, \\( f(x,h) = \frac{A x}{1 + B x} \\)
+
+``` {r }
+f <- BevHolt
+````
+
+With parameters `A` = `r A <- 1.5` and `B` = `r B <- 0.05`.
+
+``` {r }
+pars <- c(1.5, 0.05)
+K <- (pars[1] - 1)/pars[2]
+````
+
+We consider a profits from fishing to be a function of harvest `h` and stock size `x`,
+
+<div> $$ \Pi(x,h) = h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x}, $$ </div>
+
+conditioned on h > x and x > 0,
 
 ``` {r  profit}
-profit <- profit_harvest(price=1, c0 = 0.01, c1=0) 
+price <- 1
+c0 <- 0.0
+c1 <- 0
+profit <- profit_harvest(price=price, c0 = c0, c1=c1) 
 ````
 
-The profit_harvest function has the form \( \Pi = h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x} \), conditioned on \( h > x \) and \(x > 0 \).
-Note that the R code defines a function from another function using a trick known as a _closure_.
-Again we could write a custom profit function as long as it can take a vector stock size `x` and a scalar harvest level `h`.
-Details for provided functions can be found in the manual, i.e.
-`?profit_harvest`.
+with price = `r price`, `c0` = `r c0` and `c1` = `r c1`.
 
-Now we must set up the discrete grids for stock size and havest levels (which will use same resolution as for stock), in order to calculate the SDP solution.   Here we set the gridsize to 100.
+``` {r }
+xmin <- 0
+xmax <- 1.5 * K
+grid_n <- 100
+````
+
+We seek a harvest policy which maximizes the discounted profit from the fishery using a stochastic dynamic programming approach over a discrete grid of stock sizes from `r xmin` to `r xmax` on a grid of `r grid_n` points, and over an identical discrete grid of possible harvest values.
 
 ``` {r  grid}
-x_grid <- seq(0, 1.5 * K, length = 100)  
+x_grid <- seq(xmin, xmax, length = grid_n)  
 h_grid <- x_grid  
@@
 
-### Calculate the transition matrix (with noise in growth only)      
-We calculate the stochastic transition matrix for the probability of going from any state \(x_t \) to any other state \(x_{t+1}\) the following year, for each possible choice of harvest \( h_t \).
-This provides a look-up table for the dynamic programming calculations.
-Take a look at the R code and the documentation for `determine_SDP_matrix` to see what this function is actually doing.
-The implementation is quite simple.
+``` {r miscpars}
+delta <- 0.05
+xT <- 0
+OptTime <- 25
+sigma_g <- .1
+````
+
+We will determine the optimal solution over a `r OptTime` time step window with boundary condition for stock at `r xT` and discounting rate of `r delta`.
+The Reed model considers a stochastic growth model
+
+<div> $$ x_{t+1} = z_g f(x_t) $$ </div>
+
+for the random variable `z_g`, given by
+
+``` {r noise}
+z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
+````
+
+No other sources of noise enter into the dynamics.
+
+``` {r othernoise}
+z_m <- function() 1
+z_i <- function() 1
+````
 
 ``` {r  SDP_Mat}
-SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
+pdfn <- function(P, s){
+  dunif(P, 1 - s, 1 + s)
+}
+SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
 ````
@@
 q2
-````
-
-In the Sethi case, computing the distribution over multiple sources of noise is actually quite difficult.
-Simulation turns out to be more efficient than numerically integrating over each distribution.
-This code parallelizes the operation over four cores, but can be scaled to an arbitrary cluster.
-Since we're focused on the Reed example for the moment, we can ignore this step.
-
-``` {r  parallel, eval=FALSE}
-require(snowfall) 
-sfInit(parallel=TRUE, cpu=4)
-sethi_SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=999)
-sethi_opt <- find_dp_optim(sethi_SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
-                     profit, delta=0.05, reward=0)
-qplot(x_grid, sethi_opt$D[,1], xlab="stock size", ylab="harvest")
 ````
@@
 ````
+
+# References
+
+``` {r biblio, echo=FALSE, results="asis"}
+knitcitations::bibliography("html")
+````
+
+``` {r cleanup}
+options(device=orig)
+````

### 2012-06-20 inst/examples/Reed.Rmd
Reed with uniform large noise
Reed with uniform large noise, logistic map

@@
 ``` {r }
-#f <- function(x,h,p){
-#	S = x - h
-#	p[1] * S * (1 - S/p[2]) + S
-#}
+f <- function(x,h,p){
+	S = x - h
+	p[1] * S * (1 - S/p[2]) + S
+}
 ````
@@
 ``` {r }
-#pars <- c(r, K)
-````
-
-## OR
-
-We consider a Beverton Holt state equation governing population dynamics, \\( f(x,h) = \frac{A x}{1 + B x} \\)
-
-``` {r }
-f <- BevHolt
-````
-
-With parameters `A` = `r A <- 1.5` and `B` = `r B <- 0.05`.
-
-``` {r }
-pars <- c(1.5, 0.05)
-K <- (pars[1] - 1)/pars[2]
+pars <- c(r, K)
 ````
@@
 OptTime <- 25
-sigma_g <- .1
+sigma_g <- .5
 ````
@@
 ``` {r  p0}
-ggplot(subset(dt,reps==1)) +
+p0 <- ggplot(subset(dt,reps==1)) +
   geom_line(aes(time, fishstock)) +
@@
   geom_line(aes(time, harvest), col="darkgreen") 
+p0
 ````
@@
   geom_abline(intercept=xT, slope = 0, lty=2) 
-p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.2)
+p1 <- p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.2)
+p1
 ````

### 2012-06-20 inst/examples/Reed.Rmd
Sethi with uniform small noise, logistic map

@@
 
-``` {r  echo=FALSE }
+``` {r  echo=FALSE, cache=FALSE}
 opts_knit$set(upload.fun = socialR::flickr.url)

### 2012-06-20 inst/examples/Sethi.Rmd
Sethi with uniform small noise, logistic map

--- 2012-06-13 inst/examples/Sethi.Rmd
@@
 opts_knit$set(upload.fun = socialR::flickr.url)
+orig = getOptions("device")
 options(device = function(width = 5, height = 5) {
@@
 
-Define noise parameters
+Chose the state equation / population dynamics function as a logistic map:
 
 ``` {r }
-sigma_g <- 0.1    # Noise in population growth
-sigma_m <- 0.1     # noise in stock assessment measurement
-sigma_i <- 0.1     # noise in implementation of the quota
+f <- function(x,h,p){
+	S = x - h
+	p[1] * S * (1 - S/p[2]) + S
+}
 ````
 
-we'll use log normal noise functions. 
-For Reed, only `z_g` will be random.
-Sethi et al will add the other forms of noise:
+With parameters `r` = `r r <- 1` and `K` = `r K <- 100`.
 
-``` {r  noise_dists}
-z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
-z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
+``` {r }
+pars <- c(r, K)
 ````
 
-Chose the state equation / population dynamics function
+We consider a profits from fishing to be a function of harvest `h` and stock size `x`,
+
+<div> $$ \Pi(x,h) = h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x}, $$ </div>
+
+conditioned on h > x and x > 0,
+
+``` {r  profit}
+price <- 1
+c0 <- 0.0
+c1 <- 0
+profit <- profit_harvest(price=price, c0 = c0, c1=c1) 
+````
+
+with price = `r price`, `c0` = `r c0` and `c1` = `r c1`.
 
 ``` {r }
-f <- BevHolt
+xmin <- 0
+xmax <- 1.5 * K
+grid_n <- 100
 ````
 
-Note that the `pdg_control` pacakge already has a definition for the `BevHolt` function, (typing the function name prints the function)
-
-``` {r }
-BevHolt
-````
-
-That is, \\( f(x,h) = \frac{A x}{1 + B x} \\)
-
-Of course we could pass in any custom function of stocksize `x`, harvest `h` and parameter vector `p` in place of `BevHolt`.
-Note that we would need to write this function explicitly so that it can take vector values of `x` (i.e.
-uses `sapply`), an annoying feature of `R` for users comming from Matlab.
-
-We must now define parameters for the function.  Note that the positive stationary root of the model is given by \\( \frac{A-1}{B} \\), which we'll store for future reference as `K`.
-
-``` {r }
-pars <- c(1.5, 0.05)
-K <- (pars[1] - 1)/pars[2]
-````
-
-and we use a harvest-based profit function with default parameters
-
-``` {r  profit}
-profit <- profit_harvest(price=1, c0 = 0.01) 
-````
-
-The `profit_harvest` function has the form \\( \Pi = h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x} \\), conditioned on \\( h > x \\) and \\(x > 0 \\).
-Note that the R code defines a function from another function using a trick known as a _closure_.
-Again we could write a custom profit function as long as it can take a vector stock size `x` and a scalar harvest level `h`.
-Details for provided functions can be found in the manual, i.e.
-`?profit_harvest`.
-
-Now we must set up the discrete grids for stock size and havest levels (which will use same resolution as for stock), in order to calculate the SDP solution.   Here we set the gridsize to 100.
+We seek a harvest policy which maximizes the discounted profit from the fishery using a stochastic dynamic programming approach over a discrete grid of stock sizes from `r xmin` to `r xmax` on a grid of `r grid_n` points, and over an identical discrete grid of possible harvest values.
 
 ``` {r  grid}
-x_grid <- seq(0, 1.5 * K, length = 100)  
+x_grid <- seq(xmin, xmax, length = grid_n)  
 h_grid <- x_grid  
@@
 
-### Calculate the transition matrix (with noise in growth only)
+``` {r miscpars}
+delta <- 0.05
+xT <- 0
+OptTime <- 25
+sigma_g <- .1
+sigma_m <- .1
+sigma_i <- .1
+````
 
-We calculate the stochastic transition matrix for the probability of going from any state \\(x_t \\) to any other state \\(x_{t+1}\\) the following year, for each possible choice of harvest \\( h_t \\).
-This provides a look-up table for the dynamic programming calculations.
+We will determine the optimal solution over a `r OptTime` time step window with boundary condition for stock at `r xT` and discounting rate of `r delta`.
+The Reed model considers a stochastic growth model
+
+<div> $$ x_{t+1} = z_g f(x_t) $$ </div>
+
+for the random variable `z_g`, given by
+
+``` {r noise}
+z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
+z_m <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
+z_i <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
+````
+
+With `sigma_g` = `r sigma_g`, `sigma_m` = `r sigma_m`, `sigma_i` = `r sigma_i`.
 
@@
 sfInit(parallel=TRUE, cpu=4)
-SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=99)
+SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=1e5)
 ````
@@
 
-Plot the policy function:
+``` {r sethiplots, dependson="runall"}
+policy <- data.frame(stock = x_grid, value = opt$D[,1])
+ggplot(policy) + 
+  geom_point(aes(stock, stock-x_grid[value], color=variable)) + 
+	geom_smooth(aes(stock, stock-x_grid[value])) + ylab("escapement")
 
-``` {r policyfn_plot}
-qplot(x_grid, x_grid - x_grid[opt$D[,1]], xlab="stock size", ylab="escapement")
-````
+ggplot(policy) + 
+  geom_point(aes(stock, x_grid[value], color=variable)) 
+	geom_smooth(aes(stock, x_grid[value], color=variable)) + ylab("harvest")
 
-and the value function:
-
-``` {r valuefn_plot}
-qplot(x_grid, opt$V, xlab="stock size", ylab="value")
+value <- data.frame(stock = x_grid, value=opt$V)
+ggplot(value) + 
+  geom_point(aes(stock, value, color=variable)) +
+  geom_smooth(aes(stock, value, color=variable)) +
+  ylab("Net Present Value")
 ````
@@
 
-``` {r  onerep }
-ggplot(subset(dt,reps==1)) +
+``` {r  p0}
+p0 <- ggplot(subset(dt,reps==1)) +
   geom_line(aes(time, fishstock)) +
@@
   geom_line(aes(time, harvest), col="darkgreen") 
+p0
 ````
 
-This plot summarizes the stock dynamics by visualizing the replicates. Reed's S shown again.
+This plot summarizes the stock dynamics by visualizing the replicates.
+Reed's S shown again, along with the dotted line showing the allee threshold, below which the stock will go to zero (unless rescued stochastically).
 
-``` {r  all}
-p1 <- ggplot(dt) + geom_abline(intercept=opt$S, slope = 0) 
-p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.2)
-````
-
-We can also look at the harvest dynamics:
-
-``` {r  harvestplot}
-p1 + geom_line(aes(time, harvest, group = reps), alpha = 0.1, col="darkgreen")
-````
-
-This strategy is supposed to be a constant-escapement strategy. We can visualize the escapement:
-
-``` {r  escapement}
-p1 + geom_line(aes(time, escapement, group = reps), alpha = 0.1, col="darkgrey")
-````
-
-### Visualizing the optimal policy
-
-Note that when the boundary is sufficiently far away, i.e.
-for the first couple timesteps, the optimal policy is stationary.
-The optimal policy is shown here over time, where the color indicates the harvest recommended for each possible stock value at that time (shown on the vertical axis).
-Observe that the solution does not correspond to a simple Reed-style rule.
-
-``` {r  policy, fig.width=9}
-policy <- melt(opt$D)
-policy_zoom <- subset(policy, x_grid[Var1] < max(dt$fishstock) )
-p5 <- ggplot(policy_zoom) + 
-  geom_point(aes(Var2, (x_grid[Var1]), col=h_grid[value])) + 
-  labs(x = "time", y = "fishstock") +
-  scale_colour_gradientn(colours = rainbow(4)) +
-  geom_abline(intercept=opt$S, slope = 0) 
-p5
-````
-
-The harvest intensity is limited by the stock size.
-
-``` {r  policy2, fig.width=10}
-p6 <- ggplot(policy_zoom) + 
-  geom_point(aes(Var2, (x_grid[Var1]), col=x_grid[Var1] - h_grid[value])) + 
-  labs(x = "time", y = "fishstock") +
-  scale_colour_gradientn(colours = rainbow(4)) +
-  geom_abline(intercept=opt$S, slope = 0) 
-p6 + geom_line(aes(time, fishstock, group = reps), alpha = 0.1, data=dt)
+``` {r  p1}
+p1 <- ggplot(dt) + geom_abline(intercept=opt$S, slope = 0) + 
+  geom_abline(intercept=xT, slope = 0, lty=2) 
+p1 <- p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.2)
+p1
 ````
@@
 ``` {r biblio, echo=FALSE, results="asis"}
-I(knitcitations::bibliography())
+knitcitations::bibliography("html")
 ````
+
+``` {r cleanup}
+options(device=orig)
+````

### 2012-06-20 inst/examples/voi_sethi_parameters.Rmd
Sethi with uniform small noise, logistic map

@@
 policy <- melt(data.frame(stock = x_grid, det = det$D[,1], g = g$D[,1], m = m$D[,1], i= m$D[,i], gm = gm$D[,1], gi = gi$D[,1], gmi = gmi$D[,1]), id = "stock")
-ggplot(policy) + geom_point(aes(stock, stock-x_grid[value], color=variable)) 
-	geom_smooth(aes(stock, stock-x_grid[value], color=variable)) + ylab("escapement")
+ggplot(policy) + 
+  geom_point(aes(stock, stock-x_grid[value], color=variable)) +
+	geom_smooth(aes(stock, stock-x_grid[value], color=variable)) +
+  ylab("escapement")
 
-ggplot(policy) + geom_point(aes(stock, stock-x_grid[value], color=variable)) 
-	geom_smooth(aes(stock, x_grid[value], color=variable)) + ylab("harvest")
+ggplot(policy) +
+  geom_point(aes(stock, stock-x_grid[value], color=variable)) +
+	geom_smooth(aes(stock, x_grid[value], color=variable)) +
+  ylab("harvest")
 
-value <- melt(data.frame(stock = x_grid, det=det$V, g = g$V, m = m$V, gm = gm$V, gi = gi$V, gmi = gmi$V), id = "stock")
-ggplot(value) + geom_point(aes(stock, value, color=variable)) +
-	ggplot(value) + geom_smooth(aes(stock, value, color=variable)) + ylab("Net Present Value")
+value <- melt(data.frame(stock = x_grid, det=det$V, 
+                         g = g$V, m = m$V, gm = gm$V, 
+                         gi = gi$V, gmi = gmi$V), id = "stock")
+
+ggplot(value) + 
+  geom_point(aes(stock, value, color=variable)) +
+  geom_smooth(aes(stock, value, color=variable)) +
+  ylab("Net Present Value")
 ````

### 2012-06-20 inst/examples/value_of_information.Rmd
Sethi with uniform noise, logistic map

@@
-`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="value_of_information/", verbose=TRUE or`
+`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="value_of_information_symmc/", verbose=TRUE or`
 
@@
 
+**Test with symmetric noise functions**
+
 ``` {r policyscenarios}
@@
 
-  z_g <- function() rlnorm(1,  0, policy_g) 
-  z_m <- function() rlnorm(1,  0, policy_m) 
-  z_i <- function() rlnorm(1,  0, policy_i)
+  z_g <- function() rnorm(1,  0, policy_g) 
+  z_m <- function() rnorm(1,  0, policy_m) 
+  z_i <- function() rnorm(1,  0, policy_i)
 
@@
 ``` {r runall}
+lvl <- 0.1
 det <- scenario(0, 0.0, 0.0)
-g <- scenario(0.2, 0.0, 0.0)
-m <- scenario(0.0, 0.2, 0.0)
-i <- scenario(0.0, 0.0, 0.2)
-gm <- scenario(0.2, 0.2, 0.0)
-gi <- scenario(0.2, 0.0, 0.2)
-gmi <- scenario(0.2, 0.2, 0.2)
+g <- scenario(lvl, 0.0, 0.0)
+m <- scenario(0.0, lvl, 0.0)
+i <- scenario(0.0, 0.0, lvl)
+gm <- scenario(lvl, lvl, 0.0)
+gi <- scenario(lvl, 0.0, lvl)
+gmi <- scenario(lvl, lvl, lvl)
 ````
@@
 policyfn <- list(det=det, g=g, m=m, i=i, gm=gm, gi=gi, gmi=gmi)
-noise <- list(s0=c(0,0,0), sg=c(.2, 0, 0), sm=c(0, .2, 0), si=c(0,0,.2), sgm=c(.2, .2, 0), sgi=c(.2, 0, .2), sgmi=c(.2, .2, .2)) 
+noise <- list(s0=c(0,0,0), sg=c(lvl, 0, 0), sm=c(0, lvl, 0), si=c(0,0,lvl), sgm=c(lvl, lvl, 0), sgi=c(lvl, 0, lvl), sgmi=c(lvl, lvl, lvl)) 
 allcases <- lapply(policyfn, function(policyfn_i){

### 2012-06-21 inst/examples/criticaltransition.Rmd
criticaltransition model

--- 2012-06-20 inst/examples/Reed.Rmd
@@
 
-``` {r  echo=FALSE }
+``` {r  echo=FALSE, cache=FALSE}
 opts_knit$set(upload.fun = socialR::flickr.url)
-orig = getOptions("device")
+orig = getOption("device")
 options(device = function(width = 5, height = 5) {
@@
 
-# Reed Model
+# Critical transition
 
@@
  * License: [CC0](http://creativecommons.org/publicdomain/zero/1.0/)
- * Description:  Implements a numerical version of the SDP described in `r knitcitations::citet("10.1016/0095-0696(79)90014-7")`.
+ * Description:  Implements a numerical version of the SDP described in `r knitcitations::citet("10.1016/0095-0696(79)90014-7")`, in which the dynamics are slowly moving towards a tipping point.
 
@@
 ``` {r }
-f <- function(x,h,p){
-	S = x - h
-	p[1] * S * (1 - S/p[2]) + S
-}
+f <- May
 ````
 
-With parameters `r` = `r r <- 1` and `K` = `r K <- 100`.
+With parameters
 
 ``` {r }
-pars <- c(r, K)
+pars <- c(r = .75, k = 10, a=1, H=1, Q = 3)
+K <- 8 # approx
 ````
@@
 ### Simulate
-Now we'll simulate 100 replicates of this stochastic process under the Reed optimal harvest policy determined above.
+
+Now we'll simulate 100 replicates of this stochastic process, but with the system dynamics gradually changing over time.   
+The bifurcation parameter will increase from `r pars[3]` to `r pars[3] + 2`.
+
+``` {r simulationfunction}
+ForwardSimulate <- 
+  function(f, pars, x_grid, h_grid, x0, D, z_g,
+         z_m=function(x) 1, z_i = function(x) 1, 
+         profit=NULL){
+
+  OptTime <- dim(D)[2]    # Stopping time
+  x_h <- numeric(OptTime) # population dynamics with harvest
+  h <- numeric(OptTime) # optimal havest level
+  x_h[1] <- x0  # initial values
+  s <- x_h # also track escapement
+  x <- x_h # What would happen with no havest
+  p <- numeric(OptTime)
+
+  ## Simulate through time ##
+  for(t in 1:(OptTime-1)){
+
+    # Move towards collapse
+    pars[3] <- pars[3] + 2/OptTime
+
+    # Assess stock, with potential measurement error
+    m_t <- x_h[t] * z_m()
+    # Current state (is closest to which grid posititon) 
+    St <- which.min(abs(x_grid - m_t)) 
+    q_t <- h_grid[D[St, (t + 1) ]] 
+    # Implement harvest/(effort) based on quota with noise 
+    h[t] <- q_t * z_i()
+    # Noise in growth 
+    z <- z_g() 
+    # population grows
+    x_h[t+1] <- z * f(x_h[t], h[t], pars) # with havest
+    s[t+1]   <- x_h[t] - q_t # anticipated escapement
+    x[t+1]   <- z * f(x[t], 0, pars) # havest-free dynamics
+    p[t] <- profit(x_h[t], h[t])
+  }
+  data.frame(time = 1:OptTime, fishstock = x_h, harvest = h,
+             unharvested = x, escapement = s, profit = p) 
+}
+
+````
 
@@
 
-``` {r cleanup}
-options(device=orig)
+``` {r cleanup, echo=FALSE, include=FALSE}
+options(device='orig')
 ````

### 2012-06-21 inst/examples/Sethi.Rmd

@@
 require(snowfall) 
-sfInit(parallel=TRUE, cpu=4)
+sfInit(parallel=TRUE, cpu=16)
 SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=1e5)

### 2012-06-21 inst/examples/Sethi.Rmd
Sethi with uniform noise, logistic

@@
-`ro cache=FALSE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE or`
+`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache.path="Sethi/" or`
 
@@
 opts_knit$set(upload.fun = socialR::flickr.url)
-orig = getOptions("device")
+orig = getOption("device")
 options(device = function(width = 5, height = 5) {
@@
 
-``` {r sethiplots, dependson="runall"}
+``` {r sethiplots}
 policy <- data.frame(stock = x_grid, value = opt$D[,1])
 ggplot(policy) + 
-  geom_point(aes(stock, stock-x_grid[value], color=variable)) + 
+  geom_point(aes(stock, stock-x_grid[value])) + 
 	geom_smooth(aes(stock, stock-x_grid[value])) + ylab("escapement")
@@
 ggplot(policy) + 
-  geom_point(aes(stock, x_grid[value], color=variable)) 
-	geom_smooth(aes(stock, x_grid[value], color=variable)) + ylab("harvest")
+  geom_point(aes(stock, x_grid[value])) + 
+	geom_smooth(aes(stock, x_grid[value])) + ylab("harvest")
 
@@
 ggplot(value) + 
-  geom_point(aes(stock, value, color=variable)) +
-  geom_smooth(aes(stock, value, color=variable)) +
+  geom_point(aes(stock, value)) +
+  geom_smooth(aes(stock, value)) +
   ylab("Net Present Value")

### 2012-06-21 inst/examples/criticaltransition.Rmd
critical transition examples

@@
 opts_knit$set(upload.fun = socialR::flickr.url)
-orig = getOption("device")
 options(device = function(width = 5, height = 5) {
@@
 xT <- 0
-OptTime <- 25
+OptTime <- 200
 sigma_g <- .5
@@
 ``` {r  find_dp_opt }
-opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
-                     profit, delta=0.05, reward=0)
+opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=OptTime, xT=xT, 
+                     profit, delta=delta, reward=0)
 ````
@@
 Now we'll simulate 100 replicates of this stochastic process, but with the system dynamics gradually changing over time.
-The bifurcation parameter will increase from `r pars[3]` to `r pars[3] + 2`.
 
 ``` {r simulationfunction}
+Dt <- 1
+
 ForwardSimulate <- 
@@
     # Move towards collapse
-    pars[3] <- pars[3] + 2/OptTime
+    pars[3] <- pars[3] + Dt/OptTime
 
@@
 ````
+
+The bifurcation parameter will increase from `r pars[3]` to `r pars[3] + Dt*(OptTime-1)/OptTime`.
 
@@
 ````
-
-``` {r cleanup, echo=FALSE, include=FALSE}
-options(device='orig')
-````

### 2012-06-21 inst/examples/voi_sethi_parameters.Rmd
local edits on zero

@@
 ``` {r runall}
-det <- scenario(0.1, 0.0, 0.0)
-g   <- scenario(0.5, 0.0, 0.0)
-m   <- scenario(0.0, 0.5, 0.0)
-i   <- scenario(0.0, 0.0, 0.5)
-gm  <- scenario(0.5, 0.5, 0.0)
-gi  <- scenario(0.5, 0.0, 0.5)
-im  <- scenario(0.0, 0.5, 0.5)
-gmi <- scenario(0.5, 0.5, 0.5)
+lvl <- 0.1
+det <- scenario(0.01, 0.0, 0.0)
+g   <- scenario(lvl, 0.0, 0.0)
+m   <- scenario(0.0, lvl, 0.0)
+i   <- scenario(0.0, 0.0, lvl)
+gm  <- scenario(lvl, lvl, 0.0)
+gi  <- scenario(lvl, 0.0, lvl)
+im  <- scenario(0.0, lvl, lvl)
+gmi <- scenario(lvl, lvl, lvl)
 ````
@@
 require(reshape2)
-policy <- melt(data.frame(stock = x_grid, det = det$D[,1], g = g$D[,1], m = m$D[,1], i= m$D[,i], gm = gm$D[,1], gi = gi$D[,1], gmi = gmi$D[,1]), id = "stock")
+policy <- melt(data.frame(stock = x_grid, det = det$D[,1], 
+               g = g$D[,1], m = m$D[,1], i= m$D[,i], 
+               gm = gm$D[,1], gi = gi$D[,1], gmi = gmi$D[,1]), 
+               id = "stock")
+
 ggplot(policy) + 

### 2012-06-21 inst/examples/criticaltransition.Rmd
add warning signals stats calc to criticaltransitions

@@
-`ro cache=FALSE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE or`
+`ro tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache=TRUE, cache.path="criticaltransition/" or`
 
@@
 
+## Calculate warning signals
+
+``` {r libs2}
+library(earlywarning)
+````
+
+``` {r earlywarning}
+acor_tau <- dt[fishstock > 1.5, 
+               warningtrend(data.frame(time=time, value=fishstock),
+                            window_autocorr),
+               by=reps]
+
+var_tau <- dt[fishstock > 1.5, 
+              warningtrend(data.frame(time=time, value=fishstock),
+                          window_var),
+              by=reps]
+````
+
+``` {r modelbased}
+m <- dt[fishstock > 1.5, 
+        stability_model(data.frame(time=time, value=fishstock),
+                          "LSN")$pars["m"],
+        by=reps]
+````
+
+``` {r summaryplot}
+signals <- melt(data.frame(var=var_tau$V1, acor=acor_tau$V1, m=m$V1))
+ggplot(signals) + geom_density(aes(value)) + facet_wrap(~variable)
+````
+
 # References

### 2012-06-21 inst/examples/Sethi.Rmd

@@
 opts_knit$set(upload.fun = socialR::flickr.url)
-orig = getOption("device")
+op = options()
 options(device = function(width = 5, height = 5) {
@@
 OptTime <- 25
-sigma_g <- .1
-sigma_m <- .1
-sigma_i <- .1
+sigma_g <- .5
+sigma_m <- .5
+sigma_i <- .5
 ````
@@
 
-``` {r noise}
+``` {r noise, dependson="miscpars"}
 z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
-z_m <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
-z_i <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
+z_m <- function() 1+(2*runif(1, 0,  1)-1) * sigma_m
+z_i <- function() 1+(2*runif(1, 0,  1)-1) * sigma_i
 ````
@@
 
-``` {r  parallel}
+``` {r  parallel, cache=FALSE}
 require(snowfall) 
 sfInit(parallel=TRUE, cpu=16)
+````
+
+``` {r sdp_mat, dependson="noise"}
 SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=1e5)
@@
 
-``` {r  find_dp_opt }
+``` {r  find_dp_opt, dependson="sdp_mat" }
 opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
@@
 
-``` {r sethiplots}
+``` {r sethiplots, dependson="find_dp_opt"}
 policy <- data.frame(stock = x_grid, value = opt$D[,1])
@@
 
-``` {r  simulate }
+``` {r  simulate, dependson="find_dp_opt" }
 sims <- lapply(1:100, function(i){
@@
 
-``` {r  tidy}
+``` {r  tidy, dependson="simulate"}
 dat <- melt(sims, id=names(sims[[1]]))  
@@
 
-``` {r  p0}
+``` {r  p0, dependson="tidy"}
 p0 <- ggplot(subset(dt,reps==1)) +
@@
 
-``` {r  p1}
+``` {r  p1, dependson="tidy"}
 p1 <- ggplot(dt) + geom_abline(intercept=opt$S, slope = 0) + 
@@
 ``` {r biblio, echo=FALSE, results="asis"}
-knitcitations::bibliography("html")
+print(knitcitations::bibliography(), style="html")
 ````
 
-``` {r cleanup}
-options(device=orig)
+``` {r reset, echo=FALSE, include=FALSE}
+options(op)
 ````

### 2012-06-21 inst/examples/criticaltransition.Rmd
criticaltransition with warning signals, graph fixed

@@
 signals <- melt(data.frame(var=var_tau$V1, acor=acor_tau$V1, m=m$V1))
-ggplot(signals) + geom_density(aes(value)) + facet_wrap(~variable)
+ggplot(signals) + geom_histogram(aes(value)) + facet_wrap(~variable, scales="free")
 ````

### 2012-06-21 inst/examples/value_of_information.Rmd
criticaltransition with warning signals, graph fixed

@@
 require(reshape2)
-policy <- melt(data.frame(stock = x_grid, det = det$D[,1], g = g$D[,1], m = m$D[,1], gm = gm$D[,1], gi = gi$D[,1], gmi = gmi$D[,1]), id = "stock")
+policy <- melt(data.frame(stock = x_grid, det = det$D[,1], g = g$D[,1], m = m$D[,1], i=i$D[,1], gm = gm$D[,1], gi = gi$D[,1], gmi = gmi$D[,1]), id = "stock")
 ggplot(policy) + geom_point(aes(stock, stock-x_grid[value], color=variable)) + ylab("escapement") 
@@
 
-value <- melt(data.frame(stock = x_grid, det=det$V, g = g$V, m = m$V, gm = gm$V, gi = gi$V, gmi = gmi$V), id = "stock")
+value <- melt(data.frame(stock = x_grid, det=det$V, g = g$V, m = m$V, i=i$V, gm = gm$V, gi = gi$V, gmi = gmi$V), id = "stock")
 ggplot(value) + geom_point(aes(stock, value, color=variable)) + ylab("Net Present Value")
@@
 simulatereps <- function(opt, true_g, true_m, true_i){
-  z_g <- function() rlnorm(1,  0, true_g)
-  z_m <- function() rlnorm(1,  0, true_m) 
-  z_i <- function() rlnorm(1,  0, true_i)
+  z_g <- function() rnorm(1,  0, true_g)
+  z_m <- function() rnorm(1,  0, true_m) 
+  z_i <- function() rnorm(1,  0, true_i)
 
@@
 ``` {r biblio, echo=FALSE, results="asis"}
-print(knitcitations::bibliography(), "html")
+knitcitations::bibliography("html")
 ````

### 2012-06-21 inst/examples/voi_sethi_parameters.Rmd
criticaltransition with warning signals, graph fixed

@@
 rm(list=ls())
-````
-
-`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10, cache.path="value_of_information/" or`
-
-``` {r  echo=FALSE, cache=FALSE }
-opts_knit$set(upload.fun = socialR::flickr.url)
-options(device = function(width = 5, height = 5) {
-    pdf(NULL, width = width, height = height)
-})
-knitcitations::cleanbib()
 ````
@@
 policy <- melt(data.frame(stock = x_grid, det = det$D[,1], 
-               g = g$D[,1], m = m$D[,1], i= m$D[,i], 
+               g = g$D[,1], m = m$D[,1], i= m$D[,1], 
                gm = gm$D[,1], gi = gi$D[,1], gmi = gmi$D[,1]), 
@@
 ``` {r biblio, echo=FALSE, results="asis"}
-print(knitcitations::bibliography(), "html")
-`
+knitcitations::bibliography("html")
+````

### 2012-06-21 inst/examples/May.Rmd
May's nonlinear harvesting dynamics

--- 2012-06-21 inst/examples/criticaltransition.Rmd
@@
-`ro cache=FALSE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE or`
+`ro tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache=TRUE, cache.path="May/" or`
 
@@
 K <- 8 # approx
+````
+
+Ask R to show us how this function is defined, and plot the transition point using these parameters.
+
+``` {r showMay, fig.keep="last"}
+May
+
+curve(.75*(1-x/10), 0, 10)
+curve(1*x^2/(x^3+1), 0, 10, add=T, col="blue")
+curve(1.9*x^2/(x^3+1), 0, 10, add=T, col="red")
 ````
@@
 ``` {r noise}
-z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
+z_g <- function() rlnorm(1, 0, sigma_g)
 ````
@@
 ``` {r  SDP_Mat}
-pdfn <- function(P, s){
-  dunif(P, 1 - s, 1 + s)
-}
-SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
+SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g)
 ````
@@
 
-Now we'll simulate 100 replicates of this stochastic process, but with the system dynamics gradually changing over time.
-
-``` {r simulationfunction}
-Dt <- 1
-
-ForwardSimulate <- 
-  function(f, pars, x_grid, h_grid, x0, D, z_g,
-         z_m=function(x) 1, z_i = function(x) 1, 
-         profit=NULL){
-
-  OptTime <- dim(D)[2]    # Stopping time
-  x_h <- numeric(OptTime) # population dynamics with harvest
-  h <- numeric(OptTime) # optimal havest level
-  x_h[1] <- x0  # initial values
-  s <- x_h # also track escapement
-  x <- x_h # What would happen with no havest
-  p <- numeric(OptTime)
-
-  ## Simulate through time ##
-  for(t in 1:(OptTime-1)){
-
-    # Move towards collapse
-    pars[3] <- pars[3] + Dt/OptTime
-
-    # Assess stock, with potential measurement error
-    m_t <- x_h[t] * z_m()
-    # Current state (is closest to which grid posititon) 
-    St <- which.min(abs(x_grid - m_t)) 
-    q_t <- h_grid[D[St, (t + 1) ]] 
-    # Implement harvest/(effort) based on quota with noise 
-    h[t] <- q_t * z_i()
-    # Noise in growth 
-    z <- z_g() 
-    # population grows
-    x_h[t+1] <- z * f(x_h[t], h[t], pars) # with havest
-    s[t+1]   <- x_h[t] - q_t # anticipated escapement
-    x[t+1]   <- z * f(x[t], 0, pars) # havest-free dynamics
-    p[t] <- profit(x_h[t], h[t])
-  }
-  data.frame(time = 1:OptTime, fishstock = x_h, harvest = h,
-             unharvested = x, escapement = s, profit = p) 
-}
-
-````
-
-The bifurcation parameter will increase from `r pars[3]` to `r pars[3] + Dt*(OptTime-1)/OptTime`.
-
+Now we'll simulate 100 replicates of this stochastic process,
 ``` {r  simulate }
@@
 ````
-
-The forward simulation algorithm needs an initial condition `x0` which we set equal to the carrying capacity, as well as our population dynamics `f`, parameters `pars`, grids, and noise coefficients.
-Recall in the Reed case only `z_g`, growth, is stochastic.
 
@@
 
+## Calculate warning signals
+
 # References

### 2012-06-21 inst/examples/cautious.Rmd
Example of cautious (non-optimal) strategy, fishing at fixed fraction of optinal

--- 2012-06-21 inst/examples/May.Rmd
@@
-`ro tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache=TRUE, cache.path="May/" or`
+`ro tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache=TRUE, cache.path="cautious/" or`
 
@@
 
-``` {r }
+``` {r stateeqn}
 f <- May
@@
 
-``` {r }
+``` {r pars}
 pars <- c(r = .75, k = 10, a=1, H=1, Q = 3)
@@
 
-``` {r }
+``` {r gridpars}
 xmin <- 0
@@
 
-``` {r  grid}
+``` {r  grid, dependson="gridpars"}
 x_grid <- seq(xmin, xmax, length = grid_n)  
@@
 xT <- 0
-OptTime <- 200
+OptTime <- 25
 sigma_g <- .5
@@
 
-``` {r  SDP_Mat}
+``` {r  SDP_Mat, dependson="grid"}
 SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g)
@@
 
-Bellman's algorithm to compute the optimal solution for all possible trajectories.
+Bellman's algorithm to compute the a cautious solution that selects a fraction `P` = `r P <- 1` of the optimal harvest solution for all possible trajectories in the iterative optimization.
 
-``` {r  find_dp_opt }
-opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=OptTime, xT=xT, 
-                     profit, delta=delta, reward=0)
+``` {r  find_dp_opt, dependson="SDP_Mat"}
+opt <- find_dp_cautious(SDP_Mat, x_grid, h_grid, OptTime, xT, 
+                     profit, delta, reward=0, P = P)
 ````
@@
 
-``` {r policyfn_plot}
+``` {r policyfn_plot, dependson="find_dp_opt"}
 q1 <- qplot(x_grid, x_grid - x_grid[opt$D[,1]], xlab="stock size", ylab="escapement") + 
@@
 
-``` {r valuefn_plot}
+``` {r valuefn_plot, dependson="find_dp_opt"}
 q2 <- qplot(x_grid, opt$V, xlab="stock size", ylab="value") + 
@@
 Now we'll simulate 100 replicates of this stochastic process,
-``` {r  simulate }
+``` {r  simulate, dependson="find_dp_opt" }
 sims <- lapply(1:100, function(i){
@@
 p1
+````
+``` {r  p2, dependson="tidy"}
+p2 <- ggplot(dt) + geom_abline(intercept=opt$S, slope = 0) + 
+  geom_abline(intercept=xT, slope = 0, lty=2) 
+p2 <- p2 + geom_line(aes(time, harvest, group = reps), alpha = 0.2)
+p2
+````
+
+``` {r profits, fig.cap="the distribution of profits by scenario", dependson="tidy"}
+profits <-dt[ , sum(profit), by="reps"] 
+ggplot(profits) + geom_histogram(aes(V1)) 
 ````

### 2012-06-21 inst/examples/cautious.Rmd
Cautious with lnorm noise at .2, P=1

@@
 
-``` {r miscpars}
+``` {r miscpars, dependson="grid"}
 delta <- 0.05
@@
 OptTime <- 25
-sigma_g <- .5
+sigma_g <- .2
+P <- 1
 ````
@@
 
-``` {r  SDP_Mat, dependson="grid"}
+``` {r  SDP_Mat, dependson="miscpars"}
 SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g)
@@
 
-Bellman's algorithm to compute the a cautious solution that selects a fraction `P` = `r P <- 1` of the optimal harvest solution for all possible trajectories in the iterative optimization.
+Bellman's algorithm to compute the a cautious solution that selects a fraction `P` = `P` of the optimal harvest solution for all possible trajectories in the iterative optimization.
 

### 2012-06-21 inst/examples/voi_sethi_parameters.Rmd
fixed tables for voi_sethi low noise

@@
 ggplot(policy) +
-  geom_point(aes(stock, stock-x_grid[value], color=variable)) +
+  geom_point(aes(stock, x_grid[value], color=variable)) +
 	geom_smooth(aes(stock, x_grid[value], color=variable)) +
@@
 require(xtable)
-uncertainties <- c("deterministic", "growth", "measure", "implement", "growth+measure", "growth+implement", "measure+implement", "all")
+uncertainties <- c("deterministic", "growth", "measure", "implement", "growth+measure", "growth+implement", "all")
 print(xtable(matrix(means$V1, nrow=7, dimnames=list(uncertainties, uncertainties))), type="html")

### 2012-06-21 inst/examples/voi_sethi_parameters.Rmd
updated zero with the cautious optimization fn

@@
 simulatereps <- function(opt, true_g, true_m, true_i){
-  z_g <- function() rlnorm(1,  0, true_g) 
-  z_m <- function() rlnorm(1,  0, true_m) 
-  z_i <- function() rlnorm(1,  0, true_i)
+
+  z_g <- function() 1+(2*runif(1, 0,  1)-1) * true_g
+  z_m <- function() 1+(2*runif(1, 0,  1)-1) * true_m
+  z_i <- function() 1+(2*runif(1, 0,  1)-1) * true_i
 
@@
 
-#  list(sims = sims, opt = opt, true_stochasticity = c(true_g, true_m, true_i))
   sims

### 2012-06-21 inst/examples/voi_sethi_parameters.Rmd
sethi larger (0.3) noise

@@
-`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="voi_sethi_parameters/", verbose=TRUE or`
+`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="voi_sethi_parameters_bignoise/", verbose=TRUE or`
 
@@
 
+Determine the policies for each of the scenarios (noise combinations).
+
 ``` {r runall}
-lvl <- 0.1
+lvl <- 0.3
+````
+
+``` {r }
 det <- scenario(0.01, 0.0, 0.0)
+````
+
+``` {r }
 g   <- scenario(lvl, 0.0, 0.0)
+````
+
+``` {r }
 m   <- scenario(0.0, lvl, 0.0)
+````
+
+``` {r }
 i   <- scenario(0.0, 0.0, lvl)
+````
+
+``` {r }
 gm  <- scenario(lvl, lvl, 0.0)
+````
+
+``` {r }
 gi  <- scenario(lvl, 0.0, lvl)
-im  <- scenario(0.0, lvl, lvl)
+````
+
+``` {r }
+mi  <- scenario(0.0, lvl, lvl)
+````
+
+``` {r }
 gmi <- scenario(lvl, lvl, lvl)
@@
 
-``` {r sethiplots, dependson="runall"}
+``` {r sethiplots}
 require(reshape2)
@@
 ``` {r runallsims, dependson="simfn"} 
-policyfn <- list(det=det, g=g, m=m, i=i, gm=gm, gi=gi, gmi=gmi)
-noise <- list(s0=c(0,0,0), sg=c(lvl, 0, 0), sm=c(0, lvl, 0), si=c(0,0,lvl), sgm=c(lvl, lvl, 0), sgi=c(lvl, 0, lvl), sgmi=c(lvl, lvl, lvl)) 
+policyfn <- list(det=det, g=g, m=m, i=i, gm=gm, gi=gi, mi=mi, gmi=gmi)
+noise <- list(s0=c(0,0,0), sg=c(lvl, 0, 0), sm=c(0, lvl, 0), si=c(0,0,lvl), sgm=c(lvl, lvl, 0), sgi=c(lvl, 0, lvl), smi = c(0, lvl, lvl), sgmi=c(lvl, lvl, lvl)) 
 allcases <- lapply(policyfn, function(policyfn_i){
@@
 require(xtable)
-uncertainties <- c("deterministic", "growth", "measure", "implement", "growth+measure", "growth+implement", "all")
-print(xtable(matrix(means$V1, nrow=7, dimnames=list(uncertainties, uncertainties))), type="html")
-print(xtable(matrix(sds$V1, nrow=7, dimnames=list(uncertainties, uncertainties))), type="html")
+uncertainties <- c("det", "growth", "measure", "impl", "growth+measure", "growth+impl", "impl+measure" "all")
+print(xtable(matrix(means$V1, nrow=8, dimnames=list(uncertainties, uncertainties))), type="html")
+print(xtable(matrix(sds$V1, nrow=8, dimnames=list(uncertainties, uncertainties))), type="html")
 ````

### 2012-06-22 inst/examples/Sethi.Rmd
so far big noise okay

@@
-`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache.path="Sethi/" or`
+`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache.path="Sethi_bignoise/" or`
 
@@
 OptTime <- 25
-sigma_g <- .5
-sigma_m <- .5
+sigma_g <- .001
+sigma_m <- .001
 sigma_i <- .5

### 2012-06-23 inst/examples/Sethi.Rmd
logistic function was missing max(x-h, 0) step

@@
 f <- function(x,h,p){
-	S = x - h
+  sapply(x, function(x){
+  	S = max(x - h, 0)
   	p[1] * S * (1 - S/p[2]) + S
+  })
 }
@@
 OptTime <- 25
-sigma_g <- .001
-sigma_m <- .001
+sigma_g <- .5
+sigma_m <- .5
 sigma_i <- .5
@@
 ``` {r biblio, echo=FALSE, results="asis"}
-print(knitcitations::bibliography(), style="html")
+knitcitations::bibliography("html")
 ````

### 2012-06-23 inst/examples/voi_sethi_parameters.Rmd
logistic function was missing max(x-h, 0) step

@@
 ``` {r runall}
-lvl <- 0.3
+lvl <- 0.5
 ````
@@
 ``` {r }
-det <- scenario(0.01, 0.0, 0.0)
+det <- scenario(0.00101, 0.001, 0.001)
 ````
@@
 ``` {r }
-g   <- scenario(lvl, 0.0, 0.0)
+g   <- scenario(lvl, 0.001, 0.001)
 ````
@@
 ``` {r }
-m   <- scenario(0.0, lvl, 0.0)
+m   <- scenario(0.001, lvl, 0.001)
 ````
@@
 ``` {r }
-i   <- scenario(0.0, 0.0, lvl)
+i   <- scenario(0.001, 0.001, lvl)
 ````
@@
 ``` {r }
-gm  <- scenario(lvl, lvl, 0.0)
+gm  <- scenario(lvl, lvl, 0.001)
 ````
@@
 ``` {r }
-gi  <- scenario(lvl, 0.0, lvl)
+gi  <- scenario(lvl, 0.001, lvl)
 ````
@@
 ``` {r }
-mi  <- scenario(0.0, lvl, lvl)
+mi  <- scenario(0.001, lvl, lvl)
 ````
@@
 policyfn <- list(det=det, g=g, m=m, i=i, gm=gm, gi=gi, mi=mi, gmi=gmi)
-noise <- list(s0=c(0,0,0), sg=c(lvl, 0, 0), sm=c(0, lvl, 0), si=c(0,0,lvl), sgm=c(lvl, lvl, 0), sgi=c(lvl, 0, lvl), smi = c(0, lvl, lvl), sgmi=c(lvl, lvl, lvl)) 
+noise <- list(s0.001=c(0.001,0.001,0.001), sg=c(lvl, 0.001, 0.001), sm=c(0.001, lvl, 0.001), si=c(0.001,0.001,lvl), sgm=c(lvl, lvl, 0.001), sgi=c(lvl, 0.001, lvl), smi = c(0.001, lvl, lvl), sgmi=c(lvl, lvl, lvl))
 allcases <- lapply(policyfn, function(policyfn_i){
@@
 ``` {r stock, fig.cap="the induced dynamics in the stock size over time, for all replicates, by scenario", dependson="tidyall"}
-p1 <- ggplot(dt) 
+p1 <- ggplot(subset(dt, fishstock>0)) 
 p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.1) + facet_wrap(~uncertainty)

### 2012-06-23 inst/examples/voi_sethi_parameters.Rmd
added table

@@
 require(xtable)
-uncertainties <- c("det", "growth", "measure", "impl", "growth+measure", "growth+impl", "impl+measure" "all")
+uncertainties <- c("det", "growth", "measure", "impl", "growth+measure", "growth+impl", "impl+measure", "all")
 print(xtable(matrix(means$V1, nrow=8, dimnames=list(uncertainties, uncertainties))), type="html")

### 2012-06-23 inst/examples/value_of_information.Rmd

@@
-`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="value_of_information_symmc/", verbose=TRUE or`
+`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="value_of_information/", verbose=TRUE or`
 
@@
 
-  z_g <- function() rnorm(1,  0, policy_g) 
-  z_m <- function() rnorm(1,  0, policy_m) 
-  z_i <- function() rnorm(1,  0, policy_i)
+  z_g <- function() rlnorm(1,  0, policy_g) 
+  z_m <- function() rlnorm(1,  0, policy_m) 
+  z_i <- function() rlnorm(1,  0, policy_i)
 
@@
 ``` {r runall}
-lvl <- 0.1
+lvl <- 0.2
 det <- scenario(0, 0.0, 0.0)
@@
 simulatereps <- function(opt, true_g, true_m, true_i){
-  z_g <- function() rnorm(1,  0, true_g)
-  z_m <- function() rnorm(1,  0, true_m) 
-  z_i <- function() rnorm(1,  0, true_i)
+  z_g <- function() rlnorm(1,  0, true_g)
+  z_m <- function() rlnorm(1,  0, true_m) 
+  z_i <- function() rlnorm(1,  0, true_i)
 

### 2012-06-23 inst/examples/voi_sethi_parameters.Rmd
do all low and real deterministic
voi with sethi parameters

--- 2012-06-23 inst/examples/voi_sethi_parameters.Rmd
@@
 ``` {r }
-det <- scenario(0.00101, 0.001, 0.001)
+det <- scenario(0.0, 0.00, 0.00)
 ````
@@
 ``` {r }
-g   <- scenario(lvl, 0.001, 0.001)
+all_low <- scenario(0.1, 0.1, 0.1)
 ````
@@
 ``` {r }
-m   <- scenario(0.001, lvl, 0.001)
+g   <- scenario(lvl, 0, 0)
 ````
@@
 ``` {r }
-i   <- scenario(0.001, 0.001, lvl)
+m   <- scenario(0, lvl, 0)
 ````
@@
 ``` {r }
-gm  <- scenario(lvl, lvl, 0.001)
+i   <- scenario(0, 0, lvl)
 ````
@@
 ``` {r }
-gi  <- scenario(lvl, 0.001, lvl)
+gm  <- scenario(lvl, lvl, 0)
 ````
@@
 ``` {r }
-mi  <- scenario(0.001, lvl, lvl)
+gi  <- scenario(lvl, 0, lvl)
+````
+
+``` {r }
+mi  <- scenario(0, lvl, lvl)
 ````
@@
 ``` {r runallsims, dependson="simfn"} 
-policyfn <- list(det=det, g=g, m=m, i=i, gm=gm, gi=gi, mi=mi, gmi=gmi)
-noise <- list(s0.001=c(0.001,0.001,0.001), sg=c(lvl, 0.001, 0.001), sm=c(0.001, lvl, 0.001), si=c(0.001,0.001,lvl), sgm=c(lvl, lvl, 0.001), sgi=c(lvl, 0.001, lvl), smi = c(0.001, lvl, lvl), sgmi=c(lvl, lvl, lvl))
+policyfn <- list(det=det, low=low, g=g, m=m, i=i, gm=gm, gi=gi, mi=mi, gmi=gmi)
+noise <- list( det  = c(0,0,0),        low = c(0.1, .1, .1),  growth = c(lvl, 0, 0),
+               measure  = c(0, lvl, 0),implement = c(0,0,lvl),growth_measure = c(lvl, lvl, 0), 
+               growth_implement = c(lvl, 0, lvl),  measure_implement = c(0, lvl, lvl), all = c(lvl, lvl, lvl)) 
 allcases <- lapply(policyfn, function(policyfn_i){
@@
 require(xtable)
-uncertainties <- c("det", "growth", "measure", "impl", "growth+measure", "growth+impl", "impl+measure" "all")
+uncertainties <- names(noise) 
 print(xtable(matrix(means$V1, nrow=8, dimnames=list(uncertainties, uncertainties))), type="html")

### 2012-06-25 inst/examples/voi_sethi_parameters.Rmd
do all low noise, and real deterministic

@@
 
+```{r }
+low <- all_low
+````
+
 ### plots
 
-``` {r sethiplots}
+``` {r sethiplots, rerun=TRUE}
 require(reshape2)
-policy <- melt(data.frame(stock = x_grid, det = det$D[,1], 
+policy <- melt(data.frame(stock = x_grid, det = det$D[,1], low=low$D[,1],
                g = g$D[,1], m = m$D[,1], i= m$D[,1], 
-               gm = gm$D[,1], gi = gi$D[,1], gmi = gmi$D[,1]), 
+               gm = gm$D[,1], gi = gi$D[,1], mi = mi$D[,1], gmi = gmi$D[,1]), 
                id = "stock")
@@
 
-value <- melt(data.frame(stock = x_grid, det=det$V, 
+value <- melt(data.frame(stock = x_grid, det=det$V, low = low$V, 
                          g = g$V, m = m$V, gm = gm$V, 
-                         gi = gi$V, gmi = gmi$V), id = "stock")
+                         gi = gi$V, mi=mi$V, gmi = gmi$V), id = "stock")
 
@@
 
-``` {r simfn} 
+``` {r simfn, rerun=TRUE} 
 simulatereps <- function(opt, true_g, true_m, true_i){
@@
 uncertainties <- names(noise) 
-print(xtable(matrix(means$V1, nrow=8, dimnames=list(uncertainties, uncertainties))), type="html")
-print(xtable(matrix(sds$V1, nrow=8, dimnames=list(uncertainties, uncertainties))), type="html")
+print(xtable(matrix(means$V1, nrow=length(noise), dimnames=list(uncertainties, uncertainties))), type="html")
+print(xtable(matrix(sds$V1, nrow=length(noise), dimnames=list(uncertainties, uncertainties))), type="html")
 ````

### 2012-06-25 inst/examples/voi_May.Rmd
Queueing up May model with allee effect

--- 2012-06-25 inst/examples/voi_sethi_parameters.Rmd
@@
-`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="voi_sethi_parameters_bignoise/", verbose=TRUE or`
+`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="voi_May/", verbose=TRUE or`
 
@@
 
-# Calculating the value of information
+# Value of information under the May alternative stable states model with uniform noise
 
@@
 ````
+With parameters
 
-Chose the state equation / population dynamics function
-
-``` {r }
-f <- function(x,h,p){
-  sapply(x, function(x){
-  	S = max(x - h, 0)
-  	p[1] * S * (1 - S/p[2]) + S
-  })
-}
+``` {r pars}
+pars <- c(r = .75, k = 10, a=1, H=1, Q = 3)
+K <- 8 # approx
 ````
 
-With parameters `r` = `r r <- 1` and `K` = `r K <- 100`.
+Ask R to show us how this function is defined, and plot the transition point using these parameters.
 
-``` {r }
-pars <- c(r, K)
+``` {r showMay, fig.keep="last"}
+May
+curve(.75*(1-x/10), 0, 10)
+curve(1*x^2/(x^3+1), 0, 10, add=T, col="blue")
+curve(1.9*x^2/(x^3+1), 0, 10, add=T, col="red")
 ````

### 2012-06-25 inst/examples/voi_May.Rmd
may model with uniform noise

@@
 ``` {r  echo=FALSE, cache=FALSE }
-opts_knit$set(upload.fun = socialR::flickr.url)
+#opts_knit$set(upload.fun = socialR::flickr.url)
 options(device = function(width = 5, height = 5) {
@@
 # Value of information under the May alternative stable states model with uniform noise
-
- Implements a numerical version of the SDP described in `r knitcitations::citep("10.1016/j.jeem.2004.11.005")`.
- Compute the optimal solution under different forms of uncertainty.
 
@@
 ````
+
+Chose the state equation / population dynamics function
+
+``` {r stateeqn}
+f <- May
+````
+
 With parameters
@@
 ````
-
-# References
-
-``` {r biblio, echo=FALSE, results="asis"}
-knitcitations::bibliography("html")
-````

### 2012-06-25 inst/examples/figure3.Rmd
figure3

--- 2012-06-23 inst/examples/voi_sethi_parameters.Rmd
@@
 
-  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=2e4)
+  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=2e5)
   opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
@@
 
+```{r }
+low <- all_low
+````
+
 ### plots
 
-``` {r sethiplots}
+``` {r sethiplots, rerun=TRUE}
 require(reshape2)
-policy <- melt(data.frame(stock = x_grid, det = det$D[,1], 
-               g = g$D[,1], m = m$D[,1], i= m$D[,1], 
-               gm = gm$D[,1], gi = gi$D[,1], gmi = gmi$D[,1]), 
+policy <- melt(data.frame(stock = x_grid, det = det$D[,1], low=low$D[,1],
+               g = g$D[,1], m = m$D[,1], i= i$D[,1], 
+               gm = gm$D[,1], gi = gi$D[,1], mi = mi$D[,1], gmi = gmi$D[,1]), 
+               id = "stock")
+policy <- melt(data.frame(stock = x_grid, low=low$D[,1],
+               g = g$D[,1], m = m$D[,1], i= i$D[,1]), 
                id = "stock")
@@
 ggplot(policy) + 
-  geom_point(aes(stock, stock-x_grid[value], color=variable)) +
+#  geom_point(aes(stock, stock-x_grid[value], color=variable)) +
 	geom_smooth(aes(stock, stock-x_grid[value], color=variable)) +
   ylab("escapement") 
-
-ggplot(policy) +
-  geom_point(aes(stock, x_grid[value], color=variable)) +
-	geom_smooth(aes(stock, x_grid[value], color=variable)) +
-  ylab("harvest")
-
-value <- melt(data.frame(stock = x_grid, det=det$V, 
-                         g = g$V, m = m$V, gm = gm$V, 
-                         gi = gi$V, gmi = gmi$V), id = "stock")
-
-ggplot(value) + 
-  geom_point(aes(stock, value, color=variable)) +
-  geom_smooth(aes(stock, value, color=variable)) +
-  ylab("Net Present Value")
-````
-
-## Simulations
-
-``` {r simfn} 
-simulatereps <- function(opt, true_g, true_m, true_i){
-
-  z_g <- function() 1+(2*runif(1, 0,  1)-1) * true_g
-  z_m <- function() 1+(2*runif(1, 0,  1)-1) * true_m
-  z_i <- function() 1+(2*runif(1, 0,  1)-1) * true_i
-
-  sims <- lapply(1:100, function(i){
-    ForwardSimulate(f, pars, x_grid, h_grid, x0 = K, opt$D, z_g, z_m, z_i, profit)
-  })
-
-  sims
-}
-````
-
-All cases
-
-``` {r runallsims, dependson="simfn"} 
-policyfn <- list(det=det, low=low, g=g, m=m, i=i, gm=gm, gi=gi, mi=mi, gmi=gmi)
-noise <- list( det  = c(0,0,0),        low = c(0.1, .1, .1),  growth = c(lvl, 0, 0),
-               measure  = c(0, lvl, 0),implement = c(0,0,lvl),growth_measure = c(lvl, lvl, 0), 
-               growth_implement = c(lvl, 0, lvl),  measure_implement = c(0, lvl, lvl), all = c(lvl, lvl, lvl)) 
-allcases <- lapply(policyfn, function(policyfn_i){
-  lapply(noise, function(noise_i){
-    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3])
-  })
-})
-````
-
-``` {r tidyall, dependson="runallsims"}
-sims <- unlist(allcases, recursive=FALSE)
-dat <- melt(sims, id=names(sims[[1]][[1]]))  
-dt <- data.table(dat)
-setnames(dt, c("L2", "L1"), c("reps", "uncertainty")) # names are nice
-````
-
-### Plots
-
-``` {r  onerep, dependson="tidyall"}
-ggplot(subset(dt,reps==1)) +
-  geom_line(aes(time, fishstock)) +
-  geom_line(aes(time, harvest), col="darkgreen") + 
-  facet_wrap(~uncertainty) 
-````
-
-This plot summarizes the stock dynamics by visualizing the replicates.
-
-``` {r stock, fig.cap="the induced dynamics in the stock size over time, for all replicates, by scenario", dependson="tidyall"}
-p1 <- ggplot(subset(dt, fishstock>0)) 
-p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.1) + facet_wrap(~uncertainty)
-````
-
-``` {r profits, fig.cap="the distribution of profits by scenario", dependson="tidyall"}
-profits <-dt[ , sum(profit), by=c("reps", "uncertainty")] 
-ggplot(profits) + geom_histogram(aes(V1)) + facet_wrap(~uncertainty)
-````
-
-Summary statistics
-
-``` {r summarystats, cache=FALSE}
-means <- profits[, mean(V1), by=uncertainty]
-sds <- profits[, sd(V1), by=uncertainty]
-````
-
-``` {r prettytable, cache=FALSE, results="asis"}
-require(xtable)
-uncertainties <- names(noise) 
-print(xtable(matrix(means$V1, nrow=8, dimnames=list(uncertainties, uncertainties))), type="html")
-print(xtable(matrix(sds$V1, nrow=8, dimnames=list(uncertainties, uncertainties))), type="html")
-````
-
-# References
-
-``` {r biblio, echo=FALSE, results="asis"}
-knitcitations::bibliography("html")
-````
+```

### 2012-06-26 inst/examples/logistic_lognormal.Rmd
running bh+uniform and logistic+lognormal

--- 2012-06-25 inst/examples/voi_sethi_parameters.Rmd
@@
-`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="voi_sethi_parameters_bignoise/", verbose=TRUE or`
+`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="logistic_lognormal/", verbose=TRUE or`
 
@@
 
-  z_g <- function() 1+(2*runif(1, 0,  1)-1) * policy_g
-  z_m <- function() 1+(2*runif(1, 0,  1)-1) * policy_m
-  z_i <- function() 1+(2*runif(1, 0,  1)-1) * policy_i
+  z_g <- function() rlnorm(1,0, policy_g)
+  z_m <- function() rlnorm(1,0, policy_m)
+  z_i <- function() rlnorm(1,0,policy_i)
 
-  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=2e4)
+  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=2e5)
   opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
@@
 
-  z_g <- function() 1+(2*runif(1, 0,  1)-1) * true_g
-  z_m <- function() 1+(2*runif(1, 0,  1)-1) * true_m
-  z_i <- function() 1+(2*runif(1, 0,  1)-1) * true_i
+  z_g <- function() rlnorm(1,0, true_g)
+  z_m <- function() rlnorm(1,0, true_m)
+  z_i <- function() rlnorm(1,0, true_i)
 

### 2012-06-27 inst/examples/bh_uniform.Rmd

--- 2012-06-25 inst/examples/voi_sethi_parameters.Rmd
@@
-`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="voi_sethi_parameters_bignoise/", verbose=TRUE or`
+`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="bh_uniform/", verbose=TRUE or`
 
@@
 ``` {r }
-f <- function(x,h,p){
-  sapply(x, function(x){
-  	S = max(x - h, 0)
-  	p[1] * S * (1 - S/p[2]) + S
-  })
-}
+f <- BevHolt
 ````
 
-With parameters `r` = `r r <- 1` and `K` = `r K <- 100`.
+With parameters `A` = `r A <- 1.5` and `B` = `r B <- 0.05`.
 
 ``` {r }
-pars <- c(r, K)
+pars <- c(1.5, 0.05)
+K <- (pars[1] - 1)/pars[2]
 ````

### 2012-06-27 inst/examples/cautious.Rmd
cautious loop over possible P

@@
 sigma_g <- .2
-P <- 1
+P <- .5
 ````
@@
 
+``` {r beparallel, cache=FALSE}
+require(snowfall)
+sfInit(parallel=TRUE, cpu=16)
+````
+
 Bellman's algorithm to compute the a cautious solution that selects a fraction `P` = `P` of the optimal harvest solution for all possible trajectories in the iterative optimization.
+Loop over 10 values of P.
 
 ``` {r  find_dp_opt, dependson="SDP_Mat"}
-opt <- find_dp_cautious(SDP_Mat, x_grid, h_grid, OptTime, xT, 
-                     profit, delta, reward=0, P = P)
+P <- seq(0, 1, length.out=10)
+opts <- lapply(P, function(P) 
+  find_dp_cautious(SDP_Mat, x_grid, h_grid, OptTime, xT, 
+                     profit, delta, reward=0, P = P))
 ````
@@
 ``` {r policyfn_plot, dependson="find_dp_opt"}
-q1 <- qplot(x_grid, x_grid - x_grid[opt$D[,1]], xlab="stock size", ylab="escapement") + 
-geom_point(aes(x,y), data=data.frame(x=opt$S, y=opt$S), col="red")
-q1
+require(reshape2)
+policy <- melt(as.data.frame(cbind(stock=x_grid, sapply(opts, function(x) x$D[,1])), id="stock")
+ggplot(policy) + geom_lines(aes(stock, value, color=variable))
 ````
-
-and the value function (at equilibrium):
-
-``` {r valuefn_plot, dependson="find_dp_opt"}
-q2 <- qplot(x_grid, opt$V, xlab="stock size", ylab="value") + 
-geom_vline(xintercept=opt$S)
-q2
-````
-
-### Simulate
-
-Now we'll simulate 100 replicates of this stochastic process,
-``` {r  simulate, dependson="find_dp_opt" }
-sims <- lapply(1:100, function(i){
-  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i)
-})
-````
-
-## Summarize and plot the results
-
-R makes it easy to work with this big replicate data set.  We make data tidy (melt), fast (data.tables), and nicely labeled.
-
-``` {r  tidy, dependson="simulate"}
-dat <- melt(sims, id=names(sims[[1]]))  
-dt <- data.table(dat)
-setnames(dt, "L1", "reps") # names are nice
-````
-
-### Plots
-
-Let's begin by looking at the dynamics of a single replicate.
-The line shows Reed's S, the level above which the stock should be harvested (where catch should be the difference between stock and S).
-To confirm that this policy is being followed, note that harvesting only occurs when the stock is above this line, and harvest is proportional to the amount by which it is above.
-Change the replicate `reps==` to see the results from a different replicate.
-
-``` {r  p0, dependson="tidy"}
-p0 <- ggplot(subset(dt,reps==1)) +
-  geom_line(aes(time, fishstock)) +
-  geom_abline(intercept=opt$S, slope = 0) +
-  geom_line(aes(time, harvest), col="darkgreen") 
-p0
-````
-
-This plot summarizes the stock dynamics by visualizing the replicates.
-Reed's S shown again, along with the dotted line showing the allee threshold, below which the stock will go to zero (unless rescued stochastically).
-
-``` {r  p1, dependson="tidy"}
-p1 <- ggplot(dt) + geom_abline(intercept=opt$S, slope = 0) + 
-  geom_abline(intercept=xT, slope = 0, lty=2) 
-p1 <- p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.2)
-p1
-````
-``` {r  p2, dependson="tidy"}
-p2 <- ggplot(dt) + geom_abline(intercept=opt$S, slope = 0) + 
-  geom_abline(intercept=xT, slope = 0, lty=2) 
-p2 <- p2 + geom_line(aes(time, harvest, group = reps), alpha = 0.2)
-p2
-````
-
-``` {r profits, fig.cap="the distribution of profits by scenario", dependson="tidy"}
-profits <-dt[ , sum(profit), by="reps"] 
-ggplot(profits) + geom_histogram(aes(V1)) 
-````
-
-## Calculate warning signals
-
-# References
-
-``` {r biblio, echo=FALSE, results="asis"}
-knitcitations::bibliography("html")
-````

### 2012-06-27 inst/examples/cautious.Rmd
caution curves

@@
 })
-knitcitations::cleanbib()
 ````
@@
  * License: [CC0](http://creativecommons.org/publicdomain/zero/1.0/)
- * Description:  Implements a numerical version of the SDP described in `r knitcitations::citet("10.1016/0095-0696(79)90014-7")`, in which the dynamics are slowly moving towards a tipping point.
 
@@
 require(snowfall)
-sfInit(parallel=TRUE, cpu=16)
+sfInit(parallel=TRUE, cpu=2)
 ````
@@
 require(reshape2)
-policy <- melt(as.data.frame(cbind(stock=x_grid, sapply(opts, function(x) x$D[,1])), id="stock")
-ggplot(policy) + geom_lines(aes(stock, value, color=variable))
+dat <- sapply(opts, function(x) x$D[,1])
+dat <- as.data.frame(cbind(stock=x_grid, dat))
+names(dat) <- c("stock", as.character(round(P,2)))
+policy <- melt(dat, id="stock")
+ggplot(policy) + geom_line(aes(stock,x_grid - x_grid[value], color=variable)) + ylab("escapement")
 ````
+
+``` {r valuefn_plot, dependson="find_dp_opt"}
+dat <- sapply(opts, function(x) x$V)
+dat <- as.data.frame(cbind(stock=x_grid, dat))
+names(dat) <- c("stock", as.character(round(P,2)))
+policy <- melt(dat, id="stock")
+ggplot(policy) + geom_line(aes(stock, value, color=variable)) + ylab("Net present value")
+
+x0_i <- which.min(abs(x_grid-K))
+values <- sapply(opts, function(x) x$V[x0_i])
+names(values) <- as.character(round(P,2))
+values
+````

### 2012-06-28 inst/examples/bh_uniform.Rmd
exploring conditions responsible for noise becoming more or less cautious than deterministic

@@
-`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="bh_uniform/", verbose=TRUE or`
+`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="bh_uniform_fast/", verbose=TRUE or`
 
@@
 
-  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=2e5)
+  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=2e4)
   opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 

### 2012-06-28 inst/examples/logistic_lognormal.Rmd
exploring conditions responsible for noise becoming more or less cautious than deterministic

@@
-`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="logistic_lognormal/", verbose=TRUE or`
+`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="logistic_lognormal_fast/", verbose=TRUE or`
 

### 2012-06-28 inst/examples/logistic_lognormal.Rmd
cleaner plots

@@
 ggplot(policy) + 
-  geom_point(aes(stock, stock-x_grid[value], color=variable)) +
-	geom_smooth(aes(stock, stock-x_grid[value], color=variable)) +
+  geom_point(aes(stock, stock-x_grid[value], color=variable), shape='+') +
+	stat_smooth(aes(stock, stock-x_grid[value], color=variable), degree=1, se=FALSE) +
   ylab("escapement")
@@
 ggplot(policy) +
-  geom_point(aes(stock, x_grid[value], color=variable)) +
-	geom_smooth(aes(stock, x_grid[value], color=variable)) +
+  geom_point(aes(stock, x_grid[value], color=variable), shape='+') +
+	stat_smooth(aes(stock, x_grid[value], color=variable), degree=1, se=FALSE) +
   ylab("harvest")
@@
   geom_point(aes(stock, value, color=variable)) +
-  geom_smooth(aes(stock, value, color=variable)) +
+  stat_smooth(aes(stock, value, color=variable), degree=1, se=FALSE) +
   ylab("Net Present Value")
@@
 
-### Plots
-
-``` {r  onerep, dependson="tidyall"}
-ggplot(subset(dt,reps==1)) +
-  geom_line(aes(time, fishstock)) +
-  geom_line(aes(time, harvest), col="darkgreen") + 
-  facet_wrap(~uncertainty) 
-````
-
-This plot summarizes the stock dynamics by visualizing the replicates.
-
-``` {r stock, fig.cap="the induced dynamics in the stock size over time, for all replicates, by scenario", dependson="tidyall"}
-p1 <- ggplot(subset(dt, fishstock>0)) 
-p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.1) + facet_wrap(~uncertainty)
-````
-
-``` {r profits, fig.cap="the distribution of profits by scenario", dependson="tidyall"}
-profits <-dt[ , sum(profit), by=c("reps", "uncertainty")] 
-ggplot(profits) + geom_histogram(aes(V1)) + facet_wrap(~uncertainty)
-````
-
 Summary statistics

### 2012-06-28 inst/examples/bh_uniform.Rmd
cleaner plots

@@
 ``` {r }
-pars <- c(1.5, 0.05)
+pars <- c(A, B)
 K <- (pars[1] - 1)/pars[2]
@@
 
-``` {r sethiplots, rerun=TRUE}
+``` {r sethiplots}
 require(reshape2)
@@
 ggplot(policy) + 
-  geom_point(aes(stock, stock-x_grid[value], color=variable)) +
-	geom_smooth(aes(stock, stock-x_grid[value], color=variable)) +
+  geom_point(aes(stock, stock-x_grid[value], color=variable), shape='+') +
+	stat_smooth(aes(stock, stock-x_grid[value], color=variable), 
+    degree=1, se=FALSE, span=0.3) +
   ylab("escapement")
@@
 ggplot(policy) +
-  geom_point(aes(stock, x_grid[value], color=variable)) +
-	geom_smooth(aes(stock, x_grid[value], color=variable)) +
+  geom_point(aes(stock, x_grid[value], color=variable), shape='+') +
+	stat_smooth(aes(stock, x_grid[value], color=variable),
+    degree=1, se=FALSE, span=0.3) +
   ylab("harvest")
@@
 ggplot(value) + 
-  geom_point(aes(stock, value, color=variable)) +
-  geom_smooth(aes(stock, value, color=variable)) +
+  geom_point(aes(stock, value, color=variable), shape='+') +
+#  stat_smooth(aes(stock, value, color=variable),
+#    degree=0, se=FALSE, span=0.15) +
   ylab("Net Present Value")

### 2012-06-28 inst/examples/logistic_lognormal.Rmd
cleaner plots

@@
   geom_point(aes(stock, stock-x_grid[value], color=variable), shape='+') +
-	stat_smooth(aes(stock, stock-x_grid[value], color=variable), degree=1, se=FALSE) +
+	stat_smooth(aes(stock, stock-x_grid[value], color=variable), 
+    degree=1, se=FALSE, span=0.3) +
   ylab("escapement")
@@
   geom_point(aes(stock, x_grid[value], color=variable), shape='+') +
-	stat_smooth(aes(stock, x_grid[value], color=variable), degree=1, se=FALSE) +
+	stat_smooth(aes(stock, x_grid[value], color=variable),
+    degree=1, se=FALSE, span=0.3) +
   ylab("harvest")
@@
 ggplot(value) + 
-  geom_point(aes(stock, value, color=variable)) +
-  stat_smooth(aes(stock, value, color=variable), degree=1, se=FALSE) +
+  geom_point(aes(stock, value, color=variable), shape='+') +
+#  stat_smooth(aes(stock, value, color=variable),
+#    degree=0, se=FALSE, span=0.15) +
   ylab("Net Present Value")

### 2012-06-28 inst/examples/voi_sethi_parameters.Rmd
cleaner plots

@@
-`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="voi_sethi_parameters_bignoise/", verbose=TRUE or`
+`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="voi_sethi_parameters/", verbose=TRUE or`
 

### 2012-06-28 inst/examples/bh_lognormal.Rmd
bh lognormal queued on zero

--- 2012-06-28 inst/examples/bh_uniform.Rmd
@@
-`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="bh_uniform_fast/", verbose=TRUE or`
+`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="bh_lognormal/", verbose=TRUE or`
 
@@
 
-With parameters `A` = `r A <- 1.5` and `B` = `r B <- 0.05`.
+With parameters `A` = `r A <- 1.5` and `B` = `r B <- 0.005`.
 
@@
 
-  z_g <- function() 1+(2*runif(1, 0,  1)-1) * policy_g
-  z_m <- function() 1+(2*runif(1, 0,  1)-1) * policy_m
-  z_i <- function() 1+(2*runif(1, 0,  1)-1) * policy_i
+  z_g <- function() rlnorm(1,0, policy_g)
+  z_m <- function() rlnorm(1,0, policy_m)
+  z_i <- function() rlnorm(1,0,policy_i)
 

### 2012-06-29 inst/examples/bias_table.Rmd
bias table example

--- 2012-06-28 inst/examples/voi_sethi_parameters.Rmd
@@
-`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="voi_sethi_parameters/", verbose=TRUE or`
+`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="bias_table/", verbose=TRUE or`
 
@@
 
-# Calculating the value of information
-
- Implements a numerical version of the SDP described in `r knitcitations::citep("10.1016/j.jeem.2004.11.005")`.
- Compute the optimal solution under different forms of uncertainty.
+# Calculating the bias table
 
@@
 
-With parameters `r` = `r r <- 1` and `K` = `r K <- 100`.
-
-``` {r }
-pars <- c(r, K)
-````
+With `K` = `r K <- 100`, and variable choice of r.
 
@@
 OptTime <- 25
+sigma_g <- .5
 ````
@@
 We will determine the optimal solution over a `r OptTime` time step window with boundary condition for stock at `r xT` and discounting rate of `r delta`.
+The Reed model considers a stochastic growth model
 
-# Scenarios:
+<div> $$ x_{t+1} = z_g f(x_t) $$ </div>
 
-We use Monte Carlo integration over the noise processes to determine the transition matrix.
+for the random variable `z_g`, given by
 
-``` {r beparallel, cache=FALSE}
-require(snowfall)
-sfInit(parallel=TRUE, cpu=16)
+``` {r noise}
+z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
 ````
 
-``` {r policyscenarios}
-scenario <- function(policy_g, policy_m, policy_i){
+No other sources of noise enter into the dynamics.
 
-  z_g <- function() 1+(2*runif(1, 0,  1)-1) * policy_g
-  z_m <- function() 1+(2*runif(1, 0,  1)-1) * policy_m
-  z_i <- function() 1+(2*runif(1, 0,  1)-1) * policy_i
-
-  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=2e4)
-  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
-                       profit, delta, reward=0)
-}
+``` {r othernoise}
+z_m <- function() 1
+z_i <- function() 1
 ````
 
-Determine the policies for each of the scenarios (noise combinations).
+## Scenario 1: low r
 
-``` {r runall}
-lvl <- 0.5
+With parameter `r` = `r r <- 0.5`
+
+``` {r }
+pars <- c(r, K)
 ````
@@
 ``` {r  }
-det <- scenario(0.0, 0.00, 0.00)
+pdfn <- function(P, s){
+  dunif(P, 1 - s, 1 + s)
+}
+SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
 ````
@@
 ``` {r  }
-all_low <- scenario(0.1, 0.1, 0.1)
+opt_low <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
+````
+
+## Scenario 2: medium r
+
+With parameter `r` = `r r <- 1`
+
+``` {r }
+pars <- c(r, K)
 ````
@@
 ``` {r  }
-g   <- scenario(lvl, 0, 0)
+pdfn <- function(P, s){
+  dunif(P, 1 - s, 1 + s)
+}
+SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
 ````
@@
 ``` {r  }
-m   <- scenario(0, lvl, 0)
+opt_med <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
+````
+
+## Scenario 3: high r
+
+With parameter `r` = `r r <- 1.5`
+
+``` {r }
+pars <- c(r, K)
 ````
@@
 ``` {r  }
-i   <- scenario(0, 0, lvl)
+pdfn <- function(P, s){
+  dunif(P, 1 - s, 1 + s)
+}
+SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
 ````
@@
 ``` {r  }
-gm  <- scenario(lvl, lvl, 0)
-````
-
-``` {r }
-gi  <- scenario(lvl, 0, lvl)
-````
-
-``` {r }
-mi  <- scenario(0, lvl, lvl)
-````
-
-``` {r }
-gmi <- scenario(lvl, lvl, lvl)
-````
-
-```{r }
-low <- all_low
+opt_high <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
 ````
@@
 
-``` {r sethiplots}
+``` {r sethiplots, rerun=TRUE}
 require(reshape2)
-policy <- melt(data.frame(stock = x_grid, det = det$D[,1], low=low$D[,1],
-               g = g$D[,1], m = m$D[,1], i= m$D[,1], 
-               gm = gm$D[,1], gi = gi$D[,1], mi = mi$D[,1], gmi = gmi$D[,1]), 
+policy <- melt(data.frame(stock = x_grid, 
+                          low = opt_low$D[,1],
+                          med = opt_med$D[,1],
+                          high = opt_high$D[,1]),
                id = "stock")
@@
 
-value <- melt(data.frame(stock = x_grid, det=det$V, low = low$V, 
-                         g = g$V, m = m$V, gm = gm$V, 
-                         gi = gi$V, mi=mi$V, gmi = gmi$V), id = "stock")
+value <- melt(data.frame(stock = x_grid, 
+                         low=opt_low$V,
+                         med=opt_med$V,
+                         high=opt_high$V),
+              id = "stock")
 
@@
 ``` {r simfn, rerun=TRUE} 
-simulatereps <- function(opt, true_g, true_m, true_i){
-
-  z_g <- function() 1+(2*runif(1, 0,  1)-1) * true_g
-  z_m <- function() 1+(2*runif(1, 0,  1)-1) * true_m
-  z_i <- function() 1+(2*runif(1, 0,  1)-1) * true_i
-
+simulatereps <- function(opt, pars){
   sims <- lapply(1:100, function(i){
@@
   })
-
   sims
@@
 ``` {r runallsims, dependson="simfn"} 
-policyfn <- list(det=det, low=low, g=g, m=m, i=i, gm=gm, gi=gi, mi=mi, gmi=gmi)
-noise <- list( det  = c(0,0,0),        low = c(0.1, .1, .1),  growth = c(lvl, 0, 0),
-               measure  = c(0, lvl, 0),implement = c(0,0,lvl),growth_measure = c(lvl, lvl, 0), 
-               growth_implement = c(lvl, 0, lvl),  measure_implement = c(0, lvl, lvl), all = c(lvl, lvl, lvl)) 
+policyfn <- list(low=opt_low, med=opt_med, high=opt_high)
+par_list <- list(c(0.5, 100), c(1, 100), c(1.5, 100))
+
 allcases <- lapply(policyfn, function(policyfn_i){
-  lapply(noise, function(noise_i){
-    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3])
+  lapply(par_list, function(par){
+    simulatereps(policyfn_i, par)
   })
@@
 dt <- data.table(dat)
-setnames(dt, c("L2", "L1"), c("reps", "uncertainty")) # names are nice
+setnames(dt, c("L2", "L1"), c("reps", "parameter")) # names are nice
 ````
@@
   geom_line(aes(time, harvest), col="darkgreen") + 
-  facet_wrap(~uncertainty) 
+  facet_wrap(~parameter) 
 ````
@@
 p1 <- ggplot(subset(dt, fishstock>0)) 
-p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.1) + facet_wrap(~uncertainty)
+p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.1) + facet_wrap(~parameter)
 ````
@@
 ``` {r profits, fig.cap="the distribution of profits by scenario", dependson="tidyall"}
-profits <-dt[ , sum(profit), by=c("reps", "uncertainty")] 
-ggplot(profits) + geom_histogram(aes(V1)) + facet_wrap(~uncertainty)
+profits <-dt[ , sum(profit), by=c("reps", "parameter")] 
+ggplot(profits) + geom_histogram(aes(V1)) + facet_wrap(~parameter)
 ````
@@
 ``` {r summarystats, cache=FALSE}
-means <- profits[, mean(V1), by=uncertainty]
-sds <- profits[, sd(V1), by=uncertainty]
+means <- profits[, mean(V1), by=parameter]
+sds <- profits[, sd(V1), by=parameter]
 ````
@@
 require(xtable)
-uncertainties <- names(noise) 
-print(xtable(matrix(means$V1, nrow=length(noise), dimnames=list(uncertainties, uncertainties))), type="html")
-print(xtable(matrix(sds$V1, nrow=length(noise), dimnames=list(uncertainties, uncertainties))), type="html")
+scenarios <- names(par_list) 
+print(xtable(matrix(means$V1, nrow=length(scenarios), dimnames=list(scenarios, scenarios))), type="html")
+print(xtable(matrix(sds$V1, nrow=length(scenarios), dimnames=list(scenarios, scenarios))), type="html")
 ````

### 2012-06-29 inst/examples/bias_table.Rmd
bias table updated

@@
 require(xtable)
-scenarios <- names(par_list) 
+scenarios <- c("low", "med", "high")
 print(xtable(matrix(means$V1, nrow=length(scenarios), dimnames=list(scenarios, scenarios))), type="html")

### 2012-06-30 inst/examples/bh_lognormal.Rmd
lognormal noise at sigma=.2, since larger noise crashes stocks
try with nonzero cost

@@
-`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="bh_lognormal/", verbose=TRUE or`
+`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="bh_lognormal_c0/", verbose=TRUE or`
 
@@
 price <- 1
-c0 <- 0.0
+c0 <- 0.01
 c1 <- 0
@@
 ``` {r runall}
-lvl <- 0.5
+lvl <- 0.2
 ````
@@
 policyfn <- list(det=det, low=low, g=g, m=m, i=i, gm=gm, gi=gi, mi=mi, gmi=gmi)
-noise <- list( det  = c(0,0,0),        low = c(0.1, .1, .1),  growth = c(lvl, 0, 0),
-               measure  = c(0, lvl, 0),implement = c(0,0,lvl),growth_measure = c(lvl, lvl, 0), 
-               growth_implement = c(lvl, 0, lvl),  measure_implement = c(0, lvl, lvl), all = c(lvl, lvl, lvl)) 
+noise <- list( det  = c(0,0,0),        low = c(0.1, .1, .1),  gro = c(lvl, 0, 0),
+               meas  = c(0, lvl, 0),imp = c(0,0,lvl),gro_meas = c(lvl, lvl, 0), 
+               gro_imp = c(lvl, 0, lvl),  meas_imp = c(0, lvl, lvl), all = c(lvl, lvl, lvl)) 
 allcases <- lapply(policyfn, function(policyfn_i){

### 2012-06-30 inst/examples/bh_uniform.Rmd
try with nonzero cost

@@
-`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="bh_uniform_fast/", verbose=TRUE or`
+`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="bh_uniform_c0/", verbose=TRUE or`
 

### 2012-06-30 inst/examples/logistic_lognormal.Rmd
lognormal noise at sigma=.2, since larger noise crashes stocks
try with nonzero cost

@@
-`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="logistic_lognormal_fast/", verbose=TRUE or`
+`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="logistic_lognormal_c0/", verbose=TRUE or`
 

### 2012-07-03 inst/examples/logistic_uniform.Rmd

--- 2012-06-28 inst/examples/voi_sethi_parameters.Rmd
@@
-`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="voi_sethi_parameters/", verbose=TRUE or`
+`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="logistic_uniform_c0/", verbose=TRUE or`
 

### 2012-07-03 inst/examples/bias_table.Rmd
low is actually very high now
updated labels
updated

@@
-`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="bias_table/", verbose=TRUE or`
+`ro cache=FALSE, warning=FALSE, comment=NA, message=FALSE, cache.path="bias_table/", verbose=TRUE or`
 
@@
 
-With parameter `r` = `r r <- 0.5`
+With parameter `r` = `r r <- 1`
 
@@
 
-With parameter `r` = `r r <- 1`
+With parameter `r` = `r r <- 1.5`
 
@@
 
-With parameter `r` = `r r <- 1.5`
+With parameter `r` = `r r <- 2`
 
@@
 policyfn <- list(low=opt_low, med=opt_med, high=opt_high)
-par_list <- list(c(0.5, 100), c(1, 100), c(1.5, 100))
+par_list <- list(c(1, 100), c(1.5, 100), c(2, 100))
 

### 2012-07-03 inst/examples/Reed.Rmd
bias table updated with lots more replicates

@@
 ``` {r  find_dp_opt }
-opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
-                     profit, delta=0.05, reward=0)
+opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
+````
+
+## Compare to Clark (noise-free)
+
+``` {r  }
+pdfn2 <- function(P, s){
+  dunif(P, 1 - s, 1 + s)
+}
+SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, 0, pdfn2)
+````
+
+Bellman's algorithm to compute the optimal solution for all possible trajectories.
+
+``` {r  find_dp_opt }
+det <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
 ````
@@
 ``` {r policyfn_plot}
-q1 <- qplot(x_grid, x_grid - x_grid[opt$D[,1]], xlab="stock size", ylab="escapement") + 
-geom_point(aes(x,y), data=data.frame(x=opt$S, y=opt$S), col="red")
+require(reshape2)
+policies <- melt(data.frame(tsock=x_grid, S = x_grid[opt$D[,1]], D = x_grid[det$D[,1]]), id="stock")
+
+q1 <- ggplot(policies, aes(x_grid, x_grid - value)) + xlab("stock size") + ylab=("escapement") 
 q1

### 2012-07-03 inst/examples/bias_table.Rmd
updated bigger grid
bias table updated with lots more replicates

@@
 xmin <- 0
-xmax <- 1.5 * K
-grid_n <- 100
+xmax <- 2.5 * K
+grid_n <- 200
 ````
@@
 simulatereps <- function(opt, pars){
-  sims <- lapply(1:100, function(i){
+  sims <- lapply(1:5000, function(i){
     ForwardSimulate(f, pars, x_grid, h_grid, x0 = K, opt$D, z_g, z_m, z_i, profit)

### 2012-07-04 inst/examples/Reed.Rmd
Reed compared to clark

@@
 
-``` {r  find_dp_opt }
+``` {r  find_dp_optdet }
 det <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
@@
 
-q1 <- ggplot(policies, aes(x_grid, x_grid - value)) + xlab("stock size") + ylab=("escapement") 
+q1 <- ggplot(policies, aes(x_grid, x_grid - value)) + geom_point() + geom_line() + xlab("stock size") + ylab=("escapement") 
 q1

### 2012-07-04 inst/examples/Reed.Rmd
Reed compared to clark

@@
 require(reshape2)
-policies <- melt(data.frame(tsock=x_grid, S = x_grid[opt$D[,1]], D = x_grid[det$D[,1]]), id="stock")
+policies <- melt(data.frame(stock=x_grid, S = x_grid[opt$D[,1]], D = x_grid[det$D[,1]]), id="stock")
 
-q1 <- ggplot(policies, aes(x_grid, x_grid - value)) + geom_point() + geom_line() + xlab("stock size") + ylab=("escapement") 
+q1 <- ggplot(policies, aes(x_grid, x_grid - value, color=variable)) + geom_point() + geom_line() + xlab("stock size") + ylab=("escapement") 
 q1

### 2012-07-04 inst/examples/bias_table.Rmd
bias table, more reps

@@
 xmax <- 2.5 * K
-grid_n <- 200
+grid_n <- 300
 ````
@@
 ``` {r }
-pars <- c(r, K)
+pars1 <- c(r, K)
 ````
@@
 }
-SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
+SDP_Mat1 <- determine_SDP_matrix(f, pars1, x_grid, h_grid, sigma_g, pdfn)
 ````
@@
 ``` {r  }
-opt_low <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
+opt_low <- find_dp_optim(SDP_Mat1, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
 ````
@@
 ``` {r }
-pars <- c(r, K)
+pars2 <- c(r, K)
 ````
@@
 ``` {r  }
-pdfn <- function(P, s){
-  dunif(P, 1 - s, 1 + s)
-}
-SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
+SDP_Mat2 <- determine_SDP_matrix(f, pars2, x_grid, h_grid, sigma_g, pdfn)
 ````
@@
 ``` {r  }
-opt_med <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
+opt_med <- find_dp_optim(SDP_Mat2, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
 ````
@@
 ``` {r }
-pars <- c(r, K)
+pars3 <- c(r, K)
 ````
@@
 ``` {r  }
-pdfn <- function(P, s){
-  dunif(P, 1 - s, 1 + s)
-}
-SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
+SDP_Mat3 <- determine_SDP_matrix(f, pars3, x_grid, h_grid, sigma_g, pdfn)
 ````
@@
 ``` {r  }
-opt_high <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
+opt_high <- find_dp_optim(SDP_Mat3, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
 ````
@@
 policyfn <- list(low=opt_low, med=opt_med, high=opt_high)
-par_list <- list(c(1, 100), c(1.5, 100), c(2, 100))
+par_list <- list(pars1, pars2, pars3)
 
@@
 
-# References
-
-``` {r biblio, echo=FALSE, results="asis"}
-knitcitations::bibliography("html")
-````
+``` {r printvalue}
+k <- which.min(abs(K-x_grid))
+data.frame(low=opt_low$V[k], med=opt_med$V[k], high=opt_high$V[k])
+```

### 2012-07-04 inst/examples/Reed.Rmd
Reed with uniform noise, compare to Clark (degugging)

--- 2012-07-04 inst/examples/Reed.Rmd
@@
 }
-SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, 0, pdfn2)
+SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, 0.01, pdfn2)
 ````
@@
 require(reshape2)
-policies <- melt(data.frame(tsock=x_grid, S = x_grid[opt$D[,1]], D = x_grid[det$D[,1]]), id="stock")
-
-q1 <- ggplot(policies, aes(x_grid, x_grid - value)) + geom_point() + geom_line() + xlab("stock size") + ylab=("escapement") 
+policies <- melt(data.frame(stock=x_grid, S = x_grid[opt$D[,1]], D = x_grid[det$D[,1]]), id="stock")
+q1 <- ggplot(policies, aes(stock, stock - value, color=variable)) + geom_point() + xlab("stock size") + ylab("escapement") 
 q1

### 2012-07-04 inst/examples/Reed.Rmd
Reed lnorm, bev-holt, compare to clark (debug)

@@
 ``` {r }
-f <- function(x,h,p){
-	S = x - h
-	p[1] * S * (1 - S/p[2]) + S
-}
+f <- BevHolt 
 ````
 
-With parameters `r` = `r r <- 1` and `K` = `r K <- 100`.
+With parameters `A` = `r A <- 1.5` and `B` = `r B <- 0.005`.
 
 ``` {r }
-pars <- c(r, K)
+pars <- c(A, B)
 ````
@@
 price <- 1
-c0 <- 0.01
+c0 <- 5
 c1 <- 0
@@
 OptTime <- 25
-sigma_g <- .5
+sigma_g <- .2
 ````
@@
 ``` {r noise}
-z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
+z_g <- function() rlnorm(1,0, sigma_g)  # 1+(2*runif(1, 0,  1)-1) * sigma_g
 ````
@@
 pdfn <- function(P, s){
-  dunif(P, 1 - s, 1 + s)
+  # dunif(P, 1 - s, 1 + s)
+  dlnorm(P, 0, s)
 }
@@
 ``` {r  }
-pdfn2 <- function(P, s){
-  dunif(P, 1 - s, 1 + s)
-}
 SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, 0.01, pdfn2)

### 2012-07-04 R/determine_SDP_matrix.R

@@ -22,21 +22,20 @@
 #' @param sigma_g the variance of the population growth process
 #' @param pdfn the probability density function, taking the proportional
 #' chance of a transition to that state, f(x), and the parameter sigma_g
-#' If NULL (default), will use the log normal density.  
+#' By default it will use the log normal density.  
 #' @return the transition matrix at each value of h in the grid. 
 #' @details this analytical approach doesn't reliably support other 
 #'  sources of variation.  The quality of the analytic approximations 
 #'  (lognormal) can be tested. 
 #' @export
-determine_SDP_matrix <- function(f, p, x_grid, h_grid, sigma_g, pdfn=NULL){
-  if(is.null(pdfn)) 
-    pdfn <- function(P, s) dlnorm(P, 0, s) #logmean of 0 is log(1)
+determine_SDP_matrix <- function(f, p, x_grid, h_grid, sigma_g,
+                                 pdfn=function(P, s) dlnorm(P, 0, s)){
   gridsize <- length(x_grid)
   SDP_Mat <- lapply(h_grid, function(h){
     SDP_matrix <- matrix(0, nrow=gridsize, ncol=gridsize)
     # Cycle over x values
     for(i in 1:gridsize){ ## VECTORIZE ME
-      ## Calculate the 
+      ## Calculate the expected transition  
       x1 <- x_grid[i]
       x2_expected <- f(x1, h, p)
       ## If expected 0, go to 0 with probabilty 1
@@ -45,7 +44,6 @@ determine_SDP_matrix <- function(f, p, x_grid, h_grid, sigma_g, pdfn=NULL){
       else {
         # relative probability of a transition to that state
         ProportionalChance <- x_grid / x2_expected
-        # lognormal due to multiplicative Gaussian noise
         Prob <- pdfn(ProportionalChance, sigma_g)
         # Store normalized probabilities in row
         SDP_matrix[i,] <- Prob/sum(Prob)

### 2012-07-04 inst/examples/Reed.Rmd
Reed debug (cost = 0)

@@
 pars <- c(A, B)
+K <- (A-1)/B
 ````
@@
 price <- 1
-c0 <- 5
+c0 <- 0
 c1 <- 0
@@
 ``` {r  }
-SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, 0.01, pdfn2)
+SDP_Mat2 <- determine_SDP_matrix(f, pars, x_grid, h_grid, 0.01, pdfn)
 ````
@@
 ``` {r  find_dp_optdet }
-det <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
+det <- find_dp_optim(SDP_Mat2, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
 ````
@@
 ````
-
-``` {r cleanup}
-options(device=orig)
-````

### 2012-07-09 inst/examples/monitoring_impact_warning.Rmd
example of the impact that magagement has on ability to detect warning signals

--- 2012-06-21 inst/examples/criticaltransition.Rmd
@@
  * License: [CC0](http://creativecommons.org/publicdomain/zero/1.0/)
- * Description:  Implements a numerical version of the SDP described in `r knitcitations::citet("10.1016/0095-0696(79)90014-7")`, in which the dynamics are slowly moving towards a tipping point.
+ * Description:
 
@@
 ``` {r }
-pars <- c(r = .75, k = 10, a=1, H=1, Q = 3)
+pars <- c(r = .75, k = 10, a=1.7, H=1, Q = 3)
 K <- 8 # approx
 ````
+
+Note that this bifurcates when a increases to 2.
 
@@
 
-Now we'll simulate 100 replicates of this stochastic process, but with the system dynamics gradually changing over time.
-
-``` {r simulationfunction}
-Dt <- 1
-
-ForwardSimulate <- 
-  function(f, pars, x_grid, h_grid, x0, D, z_g,
-         z_m=function(x) 1, z_i = function(x) 1, 
-         profit=NULL){
-
-  OptTime <- dim(D)[2]    # Stopping time
-  x_h <- numeric(OptTime) # population dynamics with harvest
-  h <- numeric(OptTime) # optimal havest level
-  x_h[1] <- x0  # initial values
-  s <- x_h # also track escapement
-  x <- x_h # What would happen with no havest
-  p <- numeric(OptTime)
-
-  ## Simulate through time ##
-  for(t in 1:(OptTime-1)){
-
-    # Move towards collapse
-    pars[3] <- pars[3] + Dt/OptTime
-
-    # Assess stock, with potential measurement error
-    m_t <- x_h[t] * z_m()
-    # Current state (is closest to which grid posititon) 
-    St <- which.min(abs(x_grid - m_t)) 
-    q_t <- h_grid[D[St, (t + 1) ]] 
-    # Implement harvest/(effort) based on quota with noise 
-    h[t] <- q_t * z_i()
-    # Noise in growth 
-    z <- z_g() 
-    # population grows
-    x_h[t+1] <- z * f(x_h[t], h[t], pars) # with havest
-    s[t+1]   <- x_h[t] - q_t # anticipated escapement
-    x[t+1]   <- z * f(x[t], 0, pars) # havest-free dynamics
-    p[t] <- profit(x_h[t], h[t])
-  }
-  data.frame(time = 1:OptTime, fishstock = x_h, harvest = h,
-             unharvested = x, escapement = s, profit = p) 
-}
-
-````
-
-The bifurcation parameter will increase from `r pars[3]` to `r pars[3] + Dt*(OptTime-1)/OptTime`.
-
 ``` {r  simulate }
@@
 ### Plots
-
-Let's begin by looking at the dynamics of a single replicate.
-The line shows Reed's S, the level above which the stock should be harvested (where catch should be the difference between stock and S).
-To confirm that this policy is being followed, note that harvesting only occurs when the stock is above this line, and harvest is proportional to the amount by which it is above.
-Change the replicate `reps==` to see the results from a different replicate.
 
@@
 
-## Calculate warning signals
+## Calculate warning signals on managed system
 
@@
 
-# References
+## Unmanaged warning signals
+Calculate warning signals on the same set of shocks in unfished data
 
-``` {r biblio, echo=FALSE, results="asis"}
-knitcitations::bibliography("html")
+``` {r earlywarning2}
+acor_tau <- dt[unharvested > 1.5, 
+               warningtrend(data.frame(time=time, value=unharvested),
+                            window_autocorr),
+               by=reps]
+
+var_tau <- dt[unharvested > 1.5, 
+              warningtrend(data.frame(time=time, value=unharvested),
+                          window_var),
+              by=reps]
 ````
+
+``` {r modelbased2}
+m <- dt[unharvested > 1.5, 
+        stability_model(data.frame(time=time, value=unharvested),
+                          "LSN")$pars["m"],
+        by=reps]
+````
+
+``` {r summaryplot2}
+signals <- melt(data.frame(var=var_tau$V1, acor=acor_tau$V1, m=m$V1))
+ggplot(signals) + geom_histogram(aes(value)) + facet_wrap(~variable, scales="free")
+````

### 2012-07-28 inst/examples/managed_warning.Rmd
running on zero
debug on managed warning

--- 2012-07-09 inst/examples/monitoring_impact_warning.Rmd
@@
-`ro tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache=TRUE, cache.path="criticaltransition/" or`
+`ro tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache=TRUE, cache.path="managed_warning/" or`
 
@@
 OptTime <- 200
-sigma_g <- .5
+sigma_g <- .1
 ````
@@
 ``` {r noise}
-z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
+z_g <- function() dlnorm(1, 0, sigma_g)
 ````
@@
 ``` {r earlywarning}
-acor_tau <- dt[fishstock > 1.5, 
+acor_tau <- dt[, 
                warningtrend(data.frame(time=time, value=fishstock),
@@
 
-var_tau <- dt[fishstock > 1.5, 
+var_tau <- dt[, 
               warningtrend(data.frame(time=time, value=fishstock),
@@
 ``` {r modelbased}
-m <- dt[fishstock > 1.5, 
+m <- dt[, 
         stability_model(data.frame(time=time, value=fishstock),
@@
 ``` {r earlywarning2}
-acor_tau <- dt[unharvested > 1.5, 
+acor_tau <- dt[, 
                warningtrend(data.frame(time=time, value=unharvested),
@@
 
-var_tau <- dt[unharvested > 1.5, 
+var_tau <- dt[, 
               warningtrend(data.frame(time=time, value=unharvested),
@@
 ``` {r modelbased2}
-m <- dt[unharvested > 1.5, 
+m <- dt[, 
         stability_model(data.frame(time=time, value=unharvested),

### 2012-07-30 inst/examples/managed_warning.Rmd
managed warning debug - rlnorm

@@
-`ro tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache=TRUE, cache.path="managed_warning/" or`
+`ro tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache=TRUE, cache.path="managed_warning2/" or`
 
@@
 OptTime <- 200
-sigma_g <- .1
+sigma_g <- .2
+x0 <- 2
 ````
@@
 ``` {r noise}
-z_g <- function() dlnorm(1, 0, sigma_g)
+z_g <- function() rlnorm(1, 0, sigma_g)
 ````
@@
 sims <- lapply(1:100, function(i){
-  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i)
+  ForwardSimulate(f, pars, x_grid, h_grid, x0=x0, opt$D, z_g, z_m, z_i)
 })

### 2012-07-30 inst/examples/bias_table.Rmd
bias table with measurement error, for issue #17

@@
-`ro cache=FALSE, warning=FALSE, comment=NA, message=FALSE, cache.path="bias_table/", verbose=TRUE or`
+`ro cache=FALSE, warning=FALSE, comment=NA, message=FALSE, cache.path="bias_table_measurement/", verbose=TRUE or`
 
@@
 OptTime <- 25
-sigma_g <- .5
+sigma_g <- .01
+sigma_m <- .5
 ````
@@
 z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
+z_m <- function() 1+(2*runif(1, 0,  1)-1) * sigma_m
 ````
@@
 ``` {r othernoise}
-z_m <- function() 1
 z_i <- function() 1
@@
 
-``` {r  }
-pdfn <- function(P, s){
-  dunif(P, 1 - s, 1 + s)
-}
-SDP_Mat1 <- determine_SDP_matrix(f, pars1, x_grid, h_grid, sigma_g, pdfn)
+``` {r  parallel, cache=FALSE}
+require(snowfall) 
+sfInit(parallel=TRUE, cpu=16)
+````
+
+``` {r sdp_mat}
+SDP_Mat1 <- SDP_by_simulation(f, pars1, x_grid, h_grid, z_g, z_m, z_i, reps=1e4)
 ````
@@
 
-``` {r  }
-SDP_Mat2 <- determine_SDP_matrix(f, pars2, x_grid, h_grid, sigma_g, pdfn)
+``` {r sdp_mat2}
+SDP_Mat2 <- SDP_by_simulation(f, pars2, x_grid, h_grid, z_g, z_m, z_i, reps=1e4)
 ````
@@
 
-``` {r  }
-SDP_Mat3 <- determine_SDP_matrix(f, pars3, x_grid, h_grid, sigma_g, pdfn)
+``` {r sdp_mat3}
+SDP_Mat3 <- SDP_by_simulation(f, pars3, x_grid, h_grid, z_g, z_m, z_i, reps=1e4)
 ````

### 2012-07-30 inst/examples/logistic_uniform.Rmd

@@
-`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="logistic_uniform_c0/", verbose=TRUE or`
+`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="logistic_uniform_c01/", verbose=TRUE or`
 
@@
 price <- 1
-c0 <- 0.01
+c0 <- 0.1
 c1 <- 0
@@
 
-  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=2e4)
+  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=1e4)
   opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 

### 2012-07-30 inst/examples/Reed.Rmd
Reed vs Clark, enforcing the self-sustaining principle #17

@@
 ``` {r }
-f <- BevHolt 
+f <- function (x, h, p) 
+{
+      x <- max(0, x - h)
+          A <- p[1]
+          B <- p[2]
+          sapply(x, function(x) {
+            x <- max(0, x)
+            max(0, A * x/(1 + B * x))
+          })
+}
+
 ````
@@
 ``` {r noise}
-z_g <- function() rlnorm(1,0, sigma_g)  # 1+(2*runif(1, 0,  1)-1) * sigma_g
+z_g <- function() 1 + rlnorm(1,0, sigma_g)  # 1+(2*runif(1, 0,  1)-1) * sigma_g
 ````

### 2012-07-31 inst/examples/Reed.Rmd

@@
   # dunif(P, 1 - s, 1 + s)
-  dlnorm(P, 0, s)
+  1 + dlnorm(P, 0, s)
 }

### 2012-07-31 inst/examples/logistic_uniform.Rmd
replace deterministic with tiny growth noise

@@
-`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="logistic_uniform_c01/", verbose=TRUE or`
+`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="logistic_uniform/", verbose=TRUE or`
 
@@
 price <- 1
-c0 <- 0.1
+c0 <- 0
 c1 <- 0
@@
 ``` {r }
-det <- scenario(0.0, 0.00, 0.00)
+det <- scenario(0.01, 0.00, 0.00)
 ````

### 2012-08-09 inst/examples/Reed.Rmd
replace deterministic with tiny growth noise
policycosts examples

--- 2012-07-04 inst/examples/Reed.Rmd
@@
 ``` {r  echo=FALSE, cache=FALSE}
-opts_knit$set(upload.fun = socialR::flickr.url)
-orig = getOption("device")
-options(device = function(width = 5, height = 5) {
-    pdf(NULL, width = width, height = height)
-})
+#opts_knit$set(upload.fun = socialR::flickr.url)
+#options(device = function(width = 5, height = 5) {
+#    pdf(NULL, width = width, height = height)
+#})
 knitcitations::cleanbib()
@@
 ``` {r }
-f <- BevHolt 
+f <- function (x, h, p) 
+{
+ sapply(x, function(x){
+  	S = max(x - h, 0)
+  	p[1] * S * (1 - S/p[2]) + S
+  })
+}
+
 ````
 
-With parameters `A` = `r A <- 1.5` and `B` = `r B <- 0.005`.
+With parameters `K` = `r K <- 100` and `r` = `r r <- 1`.
 
 ``` {r }
-pars <- c(A, B)
-K <- (A-1)/B
+pars <- c(r, K)
 ````
@@
 xmin <- 0
-xmax <- 1.5 * K
-grid_n <- 100
+xmax <- K
+grid_n <- 200
 ````
@@
 ``` {r noise}
-z_g <- function() rlnorm(1,0, sigma_g)  # 1+(2*runif(1, 0,  1)-1) * sigma_g
+#z_g <- function() 1 + rlnorm(1,0, sigma_g)  
+z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
 ````
@@
 pdfn <- function(P, s){
-  # dunif(P, 1 - s, 1 + s)
-  dlnorm(P, 0, s)
+   dunif(P, 1 - s, 1 + s)
+#  dlnorm(P, 0, s)
 }
@@
 ``` {r  }
-SDP_Mat2 <- determine_SDP_matrix(f, pars, x_grid, h_grid, 0.01, pdfn)
+SDP_Mat2 <- determine_SDP_matrix(f, pars, x_grid, h_grid, 0.001, pdfn)
 ````
@@
 ``` {r biblio, echo=FALSE, results="asis"}
-knitcitations::bibliography("html")
+# knitcitations::bibliography("html")
 ````

### 2012-08-09 inst/examples/policycosts/L1.Rmd
policycosts examples

@@
                     profit, delta, reward, penalty = penalty)
+````
+
+##
+
+Plot the policy function and value function at certain values of previous harvest
+
+``` {r policyfn_plot}
+require(reshape2)
+policies <- melt(data.frame(stock=x_grid, S = x_grid[opt$D[,1]], D = x_grid[det$D[,1]]), id="stock")
+q1 <- ggplot(policies, aes(stock, stock - value, color=variable)) + geom_point() + xlab("stock size") + ylab("escapement") 
+q1
+````
+
+and the value function (at equilibrium):
+
+``` {r valuefn_plot}
+q2 <- qplot(x_grid, opt$V, xlab="stock size", ylab="value") + 
+geom_vline(xintercept=opt$S)
+q2
 ````

### 2012-08-09 inst/doc/policycosts/policycosts.tex
flat file outline/writeup for Paul

\documentclass[review, 12pt]{elsarticle}
\usepackage{amssymb,amsmath,amsfonts,graphicx}
\usepackage{natbib} % already loaded by elsarticle
\bibliographystyle{elsarticle-harv}
\biboptions{sort&compress} % For natbib
\usepackage[hyphens]{url}
\usepackage{hyperref} % already loaded by elsarticle

\usepackage{lineno}
\linenumbers

\usepackage{subfigure}

%\usepackage[nomarkers]{endfloat}
\renewcommand{\listoffigures}{} % but supress these lists
\renewcommand{\listoftables}{} % supress these lists
\hypersetup{breaklinks=true, pdfborder={0 0 0}}

%% Redefines the elsarticle footer
\makeatletter
\def\ps@pprintTitle{%
\let\@oddhead\@empty
\let\@evenhead\@empty
\def\@oddfoot{\it \hfill\today}%
\let\@evenfoot\@oddfoot}
\makeatother

% A modified page layout
\textwidth 6.75in
\oddsidemargin -0.15in
\evensidemargin -0.15in
\textheight 9in
\topmargin -0.5in

\usepackage{microtype}
\usepackage{fancyhdr}
\pagestyle{fancy}
\pagenumbering{arabic}

\begin{document}
\begin{frontmatter}
\title{Policy Costs}
\author[cpb]{C. Boettiger\corref{cor1}}
\author[melbourne]{M. Bode}
\author[esp]{J. Sanchirico}
\author[utk-econ]{J. LaRiviera}
\author[cpb,esp]{A. Hastings}
\author[utk-eeb]{P. Armsworth}
\ead{cboettig@ucdavis.edu}
\cortext[cor1]{Corresponding author, cboettig@ucdavis.edu}
\address[cpb]{Center for Population Biology, University of California, Davis, California 95616, USA}
\address[esp]{Department of Environmental Science \& Policy, University of California, Davis, CA 95616, USA}
\address[utk-econ]{Department of Economics, University of Tennessee, Knoxville, TN 37996, USA}
\address[utk-eeb]{Department of Ecology and Evolutionary Biology, University of Tennessee, Knoxville, TN 37996, USA}
\address[melbourne]{Australian Research Council Centre of Excellence for Environmental Decisions, University of Melbourne, School of Botany,
Parkville, Melbourne, VIC 3010, Australia}

\begin{abstract}
\end{abstract}
\begin{keyword}
  optimal control \sep management \sep stochastic dynamic programming \sep fisheries 
\end{keyword}

\end{frontmatter}

\section{Introduction}

\emph{Could use input from those most familiar with this literature to flush this out more.}

\begin{itemize}
  \item Ecosystem management frequently set in terms of policy of quotas. 
  \item Policy relatively static and costly to change
  \item Meanwhile, the natural world is variable
  \item Optimal solutions tpyically track these shocks, resulting in impractical management recommendations in face of policy costs
\end{itemize}

\emph{see Figure~\ref{fig:1}}

\begin{figure}[ht]
  \begin{center}
    \subfigure[Optimal Policy]{\includegraphics[width=.5\textwidth]{figure/optimal_harvest}\label{fig:1a}}
    \subfigure[Typical Policy]{\includegraphics[width=.5\textwidth]{figure/typical_policy}\label{fig:1b}}
  \end{center}
  \caption{\ref{fig:1a} shows a typical solution found by an optimal
  control solution by stochastic dynamic programming for the optimal catch
  quota in a managed fishery.  Note that the solution tends to track the
  noise, resulting in a highly variable policy.  \ref{fig:1b} shows the
  actual quotas set over the past decade for Bluefin tuna, which show
  great intertia to change despite considerable movement in the stock
  dynamics.  \emph{Conceptual picture illustrating the need to account
  for costs to changing policy. Current images are just placeholders.
  B should be replaced with real data, perhaps tuna quotas from Paul.
  Should stock dynamics actually be shown?}}
  \label{fig:1}
\end{figure}

%Optimal management of ecosystems and natural resources often involves
%frequent adjustment of a control variable in response to the observed
%state of a system. When this control is set in a policy-making process,
%such as determining a fishing quota, it may be more costly to change
%the policy in response to new information than to continue with the
%status quo (Bohm 1974, Xepapadeas 1992).  A management strategy that
%is optimal when adjustment costs are free may be costly and inefficient
%when these costs are present.  Meanwhile, this intertia to policy change
%introduces a two-fold cost to optimal managment solutions that account
%for it: once in direct costs of changing policy, and another in the
%differences from optimality.

\subsection{Types of real world policy costs}

\begin{itemize}
\item A discussion of capital adjustment costs, smoothing Singh, Weninger, and Doyle (2006)
\item Historical context: Discussion of Bohm 1974, Reed 1979, Xepapadeas 1992.
\end{itemize}
\subsection{Stochastic fisheries model}
\begin{itemize}
\item Historical context of the Reed (1979) model.  
\item Disucss the importance and relevance of stochastic, discrete time models, which frequently yield highly variable solutions since the policy tracks the shock.  
\end{itemize}

\section{Methods}

\subsection{Model setup}

\begin{itemize}
  \item   Fish population dynamics / state equation.  We will assume Beverton-Holt dynamics
    \begin{equation} 
      X_{t+1} = Z_t \frac{A X_t}{1 + B X_t} 
    \end{equation}

    where $Z_t$ gives the stochastic shocks.  $Z_t$ may be distributed log-normally \footnote{though this violates the self-sustaining property of~\citet{Reed1979}, such that the optimal constant-escapement level $S$ in the stochastic model is greater than the optimal escapement in the deterministic scenario.}

\item   Fishing profit function 
  \begin{equation} 
    \Pi_0(x,h) = p h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x} \label{profit}
  \end{equation}
  where $h$ is the harvest level, $x$ the stock size, $h/x$ represents fishing effort, $p$ the price per unit harvest.  The coefficient $c_1$ introduces a quadratic cost to effort, a typical way to introduce smoothing~\citep{something}.  For simplicity, we will consider $c_0 = c_1 = 0$.

\item   Policy cost function: L1, L2, fixed fee, asymmetric, are introduced as modifications to the cost function that depend on the action taken in the previous time-step.  (This makes the previous action part of the state space).   All cost functions are characterized in terms of the coupling coefficent $c_2$.  (Because $c_2$ takes different units and strength of interaction under the different functional forms, it is necessary to calibrate the choice of this coefficient such that these penalties can be compared directly, as described in the next section.)

  \begin{align} 
    \Pi_{L_1}(x_t,h_t, h_{t-1}) &= \Pi_0 + c_2 \operatorname{abs}\left( h_t - h_{t-1} \right) \label{L1} \\
    \Pi_{L_2}(x_t,h_t, h_{t-1}) &= \Pi_0 + c_2 \left( h_t - h_{t-1} \right)^2 \label{L2} \\
    \Pi_{\textrm{fixed}}(x_t,h_t, h_{t-1}) &= \Pi_0 + c_2 \mathbb{I}(h_t, h_{t-1})  \label{fixed_fee} \\
    \Pi_{\textrm{asym}}(x_t,h_t, h_{t-1}) &= \Pi_0 + c_2 \operatorname{max}\left( h_t - h_{t-1}, 0 \right) \label{asym}
  \end{align}
  Where $\mathbb{I}(a,b) = 0$ for $a \neq b$ and  $\mathbb{I}(a,b) = 1$ for $a = b$.

\item   Economic discounting, boundary conditions, constraints, Bellman equation, SDP solution method on finite time horizon.  
\item   Choice of model parameters 
\end{itemize}

\subsection{Apples to Apples comparisons: Calibraring the magnitude of the penalty coefficient}

We compare the impact of the different functional forms for the penalty
function at a value of the penalty scaling parameter in each model that
induces an equivalent net present value to the stock when optimally
managed under this penalty. This value represents the expected net
present value before the costs of policy adjustment are paid.

  \begin{figure}
    \begin{center}
\includegraphics[width=.8\textwidth]{figure/7258601130_c2fc0bcfa4_o.png}
\caption{\textbf{Net present value} We compare the impact of the different functional forms for the penalty
function at a value of the penalty scaling parameter in each model that
induces an equivalent net present value to the stock when optimally
managed under this penalty. This value represents the expected net
present value before the costs of policy adjustment are paid.}
\end{center}
\end{figure}

\section{Results}

\begin{itemize}
  \item True cost of the Reed optimum under each of the policy cost scenarios.  (Most severe, least severe).   
  \item How does the choice of penalty function influence the optimal policy? (L2 undershoots, L1 static and then overcompensating)
  \item How are costs partitioned between policy adjustments and deviation from optimality? 
  \item What is the influence of assymetric costs?
  \item Risk sensitivity: does inertia increase or decrease risk to unanticipated shocks?
\end{itemize}

  \begin{figure}
    \begin{center}
 \includegraphics[width=.8\textwidth]{figure/7258516896_5c89f034d5_o.png}
 \caption{L1 example}
  \end{center}
\end{figure}

  \begin{figure}
    \begin{center}
 \includegraphics[width=.8\textwidth]{figure/7258563112_2f5f9ffecd_o.png}
  \end{center}
 \caption{L2 example}
\end{figure}

  \begin{figure}
    \begin{center}
 \includegraphics[width=.8\textwidth]{figure/7258506664_d6235e5f8e_o.png}
  \end{center}
 \caption{Fixed Fee example}
\end{figure}

  \begin{figure}
    \begin{center}
 \includegraphics[width=.8\textwidth]{figure/7258432026_d6f8179f54_o.png}
  \end{center}
 \caption{Asymmetric costs example}
\end{figure}

\subsection{Summary values}

\begin{itemize}
\item  Quantifying the difference between policy costs: mean/sd profit from harvest
\item  mean/sd cost of solution \% reduction in net present value from the  cost (Induced cost)
\item  mean/sd cost of changing policies (Direct costs)
\item  Characterizing response of different policy costs: Plot of variance vs magnitude of penalty, by penalty function.
\item  Plot of autocorrelation vs magnitude of penalty, by penalty function.
\end{itemize}

  \begin{figure}
    \begin{center}
    \includegraphics[width=.8\textwidth]{figure/6850042286_ef81b74acc_o.png}
    \caption{Variance vs magnitude of penalty, by penalty function}
  \end{center}
\end{figure}
  \begin{figure}
    \begin{center}
   \includegraphics[width=.8\textwidth]{figure/6996165783_41c9894bdb_o.png}
    \caption{autocorrelation vs magnitude of penalty, by penalty function}
  \end{center}
\end{figure}

\section{Discussion}

\begin{itemize}
\item   Comparison of the optimal policy solution to the Reed model
\item  Comparison between the different functional forms -- smoothing (L2)
  non-smoothing (L1), and destablizing (fixed).
\item   Induced costs (relative to free adjustment) vs direct costs -- why are
  the induced costs much larger?
\item   Impact of symmetric vs assymetric costs
\item   Comparison to deterministic results
\item   Contrast steady-state results to dynamic solutions under stochastic
  shocks.
\end{itemize}

\section{References}

Bohm, Peter. 1974. ``On the Effects of Policy Costs.'' \emph{The Swedish
Journal of Economics} 76 (mar): 104. doi:10.2307/3439361.

Reed, William J. 1979. ``Optimal escapement levels in stochastic and
deterministic harvesting models.'' \emph{Journal of Environmental
Economics and Management} 6 (dec): 350--363.
doi:10.1016/0095-0696(79)90014-7.

Singh, R., Q. Weninger, and M. Doyle. 2006. ``Fisheries management with
stock growth uncertainty and costly capital adjustment.'' \emph{Journal
of Environmental Economics and Management} 52 (sep): 582--599.
doi:10.1016/j.jeem.2006.02.006.

Xepapadeas, A. P. 1992. ``Environmental policy, adjustment costs, and
behavior of the firm.'' \emph{Journal of Environmental Economics and
Management}: 258--275.

\end{document}

### 2012-08-10 inst/doc/policycosts/policycosts.tex
policycosts compare against Reed under cost reality

@@
 
-\subsection{Apples to Apples comparisons: Calibraring the magnitude of the penalty coefficient}
+\subsection{Apples to apples comparisons}
 
@@
 managed under this penalty. This value represents the expected net
-present value before the costs of policy adjustment are paid.
+present value before the costs of policy adjustment are paid, Figure~\ref{fig:apples}
 
@@
 present value before the costs of policy adjustment are paid.}
+\label{fig:apples}
 \end{center}
@@
     \begin{center}
- \includegraphics[width=.8\textwidth]{figure/7258516896_5c89f034d5_o.png}
- \caption{L1 example}
+      \subfigure[$L_1$]{\includegraphics[width=.45\textwidth]{figure/7258516896_5c89f034d5_o.png}\label{fig:L1}}
+      \subfigure[$L_2$]{\includegraphics[width=.45\textwidth]{figure/7258563112_2f5f9ffecd_o.png}\label{fig:L2}}
+
+      \subfigure[Fixed costs]{\includegraphics[width=.45\textwidth]{figure/7258506664_d6235e5f8e_o.png}\label{fig:fixed}}
+      \subfigure[Asymmetric costs]{\includegraphics[width=.45\textwidth]{figure/7258432026_d6f8179f54_o.png}\label{fig:asym}}
   \end{center}
-\end{figure}
-
-  \begin{figure}
-    \begin{center}
- \includegraphics[width=.8\textwidth]{figure/7258563112_2f5f9ffecd_o.png}
-  \end{center}
- \caption{L2 example}
-\end{figure}
-
-  \begin{figure}
-    \begin{center}
- \includegraphics[width=.8\textwidth]{figure/7258506664_d6235e5f8e_o.png}
-  \end{center}
- \caption{Fixed Fee example}
-\end{figure}
-
-  \begin{figure}
-    \begin{center}
- \includegraphics[width=.8\textwidth]{figure/7258432026_d6f8179f54_o.png}
-  \end{center}
- \caption{Asymmetric costs example}
+ \caption{Individual realizations of management under each stochastic cost}
 \end{figure}
@@
   \begin{center}
-    \includegraphics[width=.8\textwidth]{figure/6850042286_ef81b74acc_o.png}
-    \caption{Variance vs magnitude of penalty, by penalty function}
-  \end{center}
-\end{figure}
-  \begin{figure}
-    \begin{center}
-   \includegraphics[width=.8\textwidth]{figure/6996165783_41c9894bdb_o.png}
-    \caption{autocorrelation vs magnitude of penalty, by penalty function}
+    \subfigure[Variance]{\includegraphics[width=.45\textwidth]{figure/6850042286_ef81b74acc_o.png}\label{fig:var}}
+    \subfigure[Autocorrelation]{\includegraphics[width=.45\textwidth]{figure/6996165783_41c9894bdb_o.png}\label{fig:acor}}
+    \caption{Variance and autocorrelation as a function of the magnitude of penalty, by penalty function}
   \end{center}

### 2012-08-10 inst/examples/policycosts/L1.Rmd
policycosts compare against Reed under cost reality

--- 2012-05-23 inst/examples/policycosts/L1.Rmd
@@
-`ro fig.width=10, fig.height=7, message=FALSE, comment=NA, cache=TRUE, verbose=TRUE, cache.path="L1/" or`
+`ro fig.width=10, fig.height=7, message=FALSE, comment=NA, cache=FALSE, verbose=TRUE, cache.path="L1/" or`
 
@@
 ``` {r policycost_optim }
-c2 <- 1.52
+c2 <- 4 #1.52 is calculated to match, but try bigger!
 penalty <- L1(c2)
@@
 ``` {r policycost}
-costs <- dt[ , sum(policy_cost * (1-delta)^(time-1)), by=reps]
-profits <-dt[ , sum(profit_fishing * (1-delta)^(time-1)), by=reps]
+costs <- dt[, sum(policy_cost * (1 - delta)^(time - 1)), by = reps]$V1
+profits <- dt[, sum(profit_fishing * (1 - delta)^(time - 1)), by = reps]$V1
+costs_alt <- dt[, sum(policy_cost_alt * (1 - delta)^(time - 1)), by = reps]$V1
+profits_alt <- dt[, sum(profit_fishing_alt * (1 - delta)^(time - 1)), by = reps]$V1
 
-qplot(costs$V1)
-qplot(profits$V1)
-qplot(profits$V1-costs$V1)
+qplot(costs)
+qplot(profits)
+qplot(profits-costs)
 ````
@@
 ```{r}
-mean(profits$V1)
-sd(profits$V1)
+mean(profits)-mean(costs)
+mean(profits_alt) - mean(costs_alt)
+
+values <- data.frame(profits= profits, costs=costs, naiive_profit = profits_alt, naiive_costs = costs_alt)
+ggplot(melt(values)) + geom_density(aes(value, fill=variable), alpha=.7) + theme_bw()
+
+npv <- data.frame(policywise = profits-costs, naiive = profits_alt - costs_alt)
+ggplot(melt(npv)) + geom_density(aes(value, fill=variable), alpha=.7) + theme_bw()
 ````
-
-Compare these induced costs to the costs of actual adjustment.  Direct costs:
-
-```{r}
-mean(costs$V1)
-sd(costs$V1)
-````
-
-Induced costs:
-
-```{r}
-380.4 - mean(profits$V1)
-````

### 2012-08-10 R/policy_costs.R

@@ -113,6 +113,7 @@ simulate_optim <- function(f, pars, x_grid, h_grid, x0, D, z_g,
   h <- numeric(OptTime) # optimal havest level
   x_h[1] <- x0  # initial values
   h_prev <- 1 # assume no harvesting happening at start (index of h_grid)
+  h_prev_alt <- 1 # assume no harvesting happening at start (index of h_grid)
   s <- x_h # also track escapement
   x <- x_h # What would happen with no havest
 
@@ -121,6 +122,8 @@ simulate_optim <- function(f, pars, x_grid, h_grid, x0, D, z_g,
   h_alt <- h
   p <- numeric(OptTime)
   fee <- numeric(OptTime)  
+  p_alt <- numeric(OptTime)
+  fee_alt <- numeric(OptTime)  
 
   ## Simulate through time ##
   for(t in 1:(OptTime-1)){
@@ -145,10 +148,13 @@ simulate_optim <- function(f, pars, x_grid, h_grid, x0, D, z_g,
     s[t+1]   <- x_h[t] - q_t # anticipated escapement
     x[t+1]   <- zg * f(x[t], 0, pars) # havest-free dynamics
 
-    p[t] <- profit(x_h[t],h[t])
+    p[t]   <- profit(x_h[t],h[t])
     fee[t] <- penalty(h[t],lastyr)
-    ## Comparison solution
+
+  ## Comparison solution
     if(!is.null(alt_D)){
+   		lastyr_alt <- h_grid[h_prev_alt]
+
       m_alt <- x_alt[t] * zm
       # Current state (is closest to which grid posititon) 
       St_alt <- which.min(abs(x_grid - m_alt)) 
@@ -156,10 +162,18 @@ simulate_optim <- function(f, pars, x_grid, h_grid, x0, D, z_g,
       h_alt[t] <- h_grid[alt_D[St_alt, (t + 1) ]] * zi
       # population grows
       x_alt[t+1] <- zg * f(x_alt[t], h_alt[t], pars) 
+    
+      q_t_alt <- h_grid[D[[h_prev_alt]][St_alt, (t + 1) ]] 
+      h_prev_alt <- which.min(abs(h_grid - q_t_alt))
+
+      p_alt[t]   <- profit(x_alt[t],h_alt[t])
+      fee_alt[t] <- penalty(h_alt[t],lastyr_alt)
+
     }
 }
   # formats output 
   data.frame(time=1:OptTime, fishstock=x_h, harvest=h, 
[…]

### 2012-08-10 inst/examples/policycosts/L1.Rmd
policycosts compared in L1

@@
 profits_alt <- dt[, sum(profit_fishing_alt * (1 - delta)^(time - 1)), by = reps]$V1
-
-qplot(costs)
-qplot(profits)
-qplot(profits-costs)
 ````

### 2012-08-21 inst/doc/policycosts/policycosts.tex
Outline updated

@@
-\documentclass[review, 12pt]{elsarticle}
+\documentclass[authoryear, review, 12pt]{elsarticle}
 \usepackage{amssymb,amsmath,amsfonts,graphicx}
-\usepackage{natbib} % already loaded by elsarticle
 \bibliographystyle{elsarticle-harv}
-\biboptions{sort&compress} % For natbib
+%\usepackage{natbib} % already loaded by elsarticle
+%\biboptions{sort&compress} % For natbib
+%\usepackage{hyperref} % already loaded by elsarticle
+%\hypersetup{breaklinks=true, pdfborder={0 0 0}}
+
 \usepackage[hyphens]{url}
-\usepackage{hyperref} % already loaded by elsarticle
 
@@
 \usepackage{subfigure}
-
 %\usepackage[nomarkers]{endfloat}
-\renewcommand{\listoffigures}{} % but supress these lists
-\renewcommand{\listoftables}{} % supress these lists
-\hypersetup{breaklinks=true, pdfborder={0 0 0}}
+\renewcommand{\listoffigures}{} % but suppress these lists
+\renewcommand{\listoftables}{} % suppress these lists
 
@@
 \makeatother
-
 % A modified page layout
@@
 
+\usepackage[pdftex, usenames]{color}
+\definecolor{darkblue}{rgb}{0,0,0.5}
+\definecolor{darkgreen}{rgb}{0,0.5,0}
+\newcommand{\cdb}[1]{{\it \color{darkgreen} #1}}
+
 \begin{document}
@@
 \author[cpb]{C. Boettiger\corref{cor1}}
+\ead{cboettig@ucdavis.edu}
 \author[melbourne]{M. Bode}
@@
 \author[utk-eeb]{P. Armsworth}
-\ead{cboettig@ucdavis.edu}
-\cortext[cor1]{Corresponding author, cboettig@ucdavis.edu}
+\cortext[cor1]{Corresponding author}
 \address[cpb]{Center for Population Biology, University of California, Davis, California 95616, USA}
@@
 \begin{abstract}
+\cdb{Carl's comments \& questions added in green}
 \end{abstract}
@@
   \item Meanwhile, the natural world is variable
-  \item Optimal solutions tpyically track these shocks, resulting in impractical management recommendations in face of policy costs
+  \item Optimal solutions typically track these shocks, resulting in impractical management recommendations in face of policy costs
 \end{itemize}
 
-\emph{see Figure~\ref{fig:1}}
+(See Figure~\ref{fig:1} which motivates the importance of considering policy costs by comparing a theoretically optimal policy over time to a typical real world policy over time).
 
@@
   great intertia to change despite considerable movement in the stock
-  dynamics.  \emph{Conceptual picture illustrating the need to account
+  dynamics.  \cdb{Conceptual picture illustrating the need to account
   for costs to changing policy. Current images are just placeholders.
@@
 %the policy in response to new information than to continue with the
-%status quo (Bohm 1974, Xepapadeas 1992).  A management strategy that
+%status quo ~\citep{Bohm1974, Xepapadeas1992}.  A management strategy that
 %is optimal when adjustment costs are free may be costly and inefficient
-%when these costs are present.  Meanwhile, this intertia to policy change
-%introduces a two-fold cost to optimal managment solutions that account
+%when these costs are present.  Meanwhile, this inertia to policy change
+%introduces a two-fold cost to optimal management solutions that account
 %for it: once in direct costs of changing policy, and another in the
@@
 \begin{itemize}
-\item A discussion of capital adjustment costs, smoothing Singh, Weninger, and Doyle (2006)
-\item Historical context: Discussion of Bohm 1974, Reed 1979, Xepapadeas 1992.
+  \item A discussion of capital adjustment costs, smoothing, \emph{e.g.} \citet{Singh2006}.
+  \item Historical context, \emph{e.g.} discussion of \citep{Bohm1974, Reed1979, Xepapadeas1992}.  
 \end{itemize}
@@
 \item Historical context of the Reed (1979) model.  
-\item Disucss the importance and relevance of stochastic, discrete time models, which frequently yield highly variable solutions since the policy tracks the shock.  
+\item Discuss the importance and relevance of stochastic, discrete time models, which frequently yield highly variable solutions since the policy tracks the shock.  
 \end{itemize}
@@
 \begin{itemize}
-  \item   Fish population dynamics / state equation.  We will assume Beverton-Holt dynamics
+  \item   Fish population dynamics / state equation.  We will assume Beverton-Holt dynamics,
     \begin{equation} 
-      X_{t+1} = Z_t \frac{A X_t}{1 + B X_t} 
+      X_{t+1} = Z_t \frac{A X_t}{1 + B X_t}, 
     \end{equation}
-
 where $Z_t$ gives the stochastic shocks.
@@
   \end{equation}
-  where $h$ is the harvest level, $x$ the stock size, $h/x$ represents fishing effort, $p$ the price per unit harvest.
-The coefficient $c_1$ introduces a quadratic cost to effort, a typical way to introduce smoothing~\citep{something}.
-For simplicity, we will consider $c_0 = c_1 = 0$.
+  where $h$ is the harvest level, $x$ the stock size, $h/x$ represents
+  fishing effort, $p$ the price per unit harvest.  The coefficient $c_1$
+  introduces a quadratic cost to effort, a typical way to introduce
+  smoothing~\citep[\emph{e.g.}][]{Singh2006}.  For simplicity, we will consider $c_0 =
+  c_1 = 0$.
 
-\item   Policy cost function: L1, L2, fixed fee, asymmetric, are introduced as modifications to the cost function that depend on the action taken in the previous time-step.
-(This makes the previous action part of the state space).
-All cost functions are characterized in terms of the coupling coefficent $c_2$.
-(Because $c_2$ takes different units and strength of interaction under the different functional forms, it is necessary to calibrate the choice of this coefficient such that these penalties can be compared directly, as described in the next section.)
+\item
+Policy cost function: L1, L2, fixed fee, asymmetric, are introduced
+as modifications to the cost function that depend on the action
+taken in the previous time-step.  (This makes the previous action part
+of the state space).   All cost functions are characterized in terms
+of the coupling coefficient $c_2$.  (Because $c_2$ takes different units
+and strength of interaction under the different functional forms, it is
+necessary to calibrate the choice of this coefficient such that these
+penalties can be compared directly, as described in the next section.)
 
@@
     \begin{center}
-\includegraphics[width=.8\textwidth]{figure/7258601130_c2fc0bcfa4_o.png}
-\caption{\textbf{Net present value} We compare the impact of the different functional forms for the penalty
-function at a value of the penalty scaling parameter in each model that
-induces an equivalent net present value to the stock when optimally
-managed under this penalty. This value represents the expected net
-present value before the costs of policy adjustment are paid.}
+\includegraphics[width=.8\textwidth]{figure/npv0.png}
+\caption{\textbf{Net present value by functional form of penalty.} Horizontal axis shows the coefficient $c_2$ governing the magnitude of the policy cost, while vertical axis shows fraction of the stock value dissipated by the policy cost.
+The horizontal line indicates a value of the stock that is 80\% of the adjustment-free value.
+Selecting the coefficient $c_2$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.
+}
 \label{fig:apples}
@@
 \section{Results}
+\subsection{Characterize and compare functional forms of costs}
 
+Figure~\ref{fig:shapes} shows the impact the adjustment cost has on the optimal policy.
+The $L_1$-norm costs tend to avoid small adjustments to the policy, resulting in long periods of constant policy followed by sudden bursts of adjustment.
+In contrast, the $L_2$-norm tracks all of the changes made by the cost-free policy, but with smaller magnitude.
+The fixed fee only makes large adjustments much like the $L_1$, as expected where the adjustment magnitude does not impact the cost.
+Asymmetric ($L_1$) adjustment costs do not appear to show more directional bias than any of the symmetric costs.
+Note that while the cost-free optimal strategy corresponds to a constant-escapement policy as derived in~\citet{Reed1979}, any of the policy-cost scenarios deviate from such a policy.
+    \cdb{
     \begin{itemize}
-  \item True cost of the Reed optimum under each of the policy cost scenarios.  (Most severe, least severe).   
-  \item How does the choice of penalty function influence the optimal policy? (L2 undershoots, L1 static and then overcompensating)
-  \item How are costs partitioned between policy adjustments and deviation from optimality? 
-  \item What is the influence of assymetric costs?
-  \item Risk sensitivity: does inertia increase or decrease risk to unanticipated shocks?
+      \item All of these should use the same sequence of shocks.  
+      \item Don't plot all four curves on the same graph.  
+      \item Omit stock dynamics?
+      \item Consider not violating the self-sustaining property, which should also guarantee that fishing never stops.   
     \end{itemize}
+    }
+
+\cdb{ In terms of a policy set on escapement instead of harvest, our solutions are actually more volatile than~\citet{Reed1979}.
+Maybe this leads to a discussion of what the control policy should be defined in terms of (i.e.
+catch vs escapement)?
+Surely the simplicity of the constant-escapement rule has led to it's popularity in some part due because that simplicity avoids adjustment costs?}
 
@@
   \end{center}
- \caption{Individual realizations of management under each stochastic cost}
+  \caption{Individual realizations of management under the different functional forms of adjustment costs.
+\textbf{Green} lines show the cost-free optimal harvest levels, \textbf{black} lines show the corresponding stock dynamics under that management.
+\textbf{Purple} lines show the optimal harvest level under the specified adjustment cost, under the same sequence of stochastic shocks as in the cost-free policy.
+\textbf{Blue lines} show the resulting stock dynamics.
+  } \label{fig:shapes}
 \end{figure}
 
-\subsection{Summary values}
+\subsection{Responses to increasing costs}
 
-\begin{itemize}
-\item  Quantifying the difference between policy costs: mean/sd profit from harvest
-\item  mean/sd cost of solution \% reduction in net present value from the  cost (Induced cost)
-\item  mean/sd cost of changing policies (Direct costs)
-\item  Characterizing response of different policy costs: Plot of variance vs magnitude of penalty, by penalty function.
-\item  Plot of autocorrelation vs magnitude of penalty, by penalty function.
-\end{itemize}
+The comparisons shown in Figure~\ref{fig:shapes} are made at a fixed magnitude of the policy cost equal to 80\% of the net present value derived from the cost-free optimal strategy.
+The different functional forms may also respond differently to an increasing magnitude of the adjustment cost.
+To quantify the extent to which the policy cost decreases the volatility of the proposed policy, we calculate the variance in the fishing quota over time under each policy.
+While a decrease in variance is typical of smoothing penalties and the $L_2$-norm, the patterns in Figure~\ref{fig:shapes} suggest that other functional forms still involve the same magnitude of variation, but decrease the frequency of adjustments.
+To capture this behavior we calculate the autocorrelation of the policy as the adjustment cost increases.
+These curves van be seen in Figure~\ref{fig:summarystats}.
+
+\cdb{Perhaps not clear what is comparable here and what isn't.
+Certainly we cannot compare the curves at the same value of $c_2$, as discussed in our apples to apples section.
+Not clear that we can even compare the shape of the curves though -- for instance, given the units of $c_2$ for the $L_2$ norm are different than the other norms.
+Perhaps the horizontal axis should be converted into percent of net present value of the adjustment free costs first?}
+
+\cdb{Add additional plot: Is value a linear function of policy cost, or is there a sharp transition? }
+%Must be nonlinear somewhere when adjustment costs exceed profits?
 
@@
     \subfigure[Autocorrelation]{\includegraphics[width=.45\textwidth]{figure/6996165783_41c9894bdb_o.png}\label{fig:acor}}
-    \caption{Variance and autocorrelation as a function of the magnitude of penalty, by penalty function}
+    \caption{Variance and autocorrelation as a function of the magnitude of penalty, by penalty function}\label{fig:summarystats}
   \end{center}
@@
 
+\subsection{Consequences of ignoring policy adjustment costs}
+
+\begin{itemize}
+  \item Distribution of profits and costs under a policy-cost scenario vs profits and costs under Reed solution, by penalty type. Figure~\ref{fig:profits_costs}.
+  \item Distribution of net present value under the policy-cost scenario vs the Reed solution, Figure~\ref{fig:npv_dist}.  
+\end{itemize}
+
+\begin{figure}
+  \begin{center}
+    \subfigure[L1]{\includegraphics[width=.45\textwidth]{figure/7751440758_99645d6e5a_o.png}\label{fig:L1cost}}
+    \caption{Ignoring the cost of policy adjustment results in greater profits from fishing, but even greater costs for adjusting the harvest quotas each year.
+Costs and profits are shown for ignoring the adjustment costs (Reed solution, purple and blue) and accounting for the adjustment (green and red).
+\cdb{Though only L1 shown for the moment, would probably show all four types.
+Possibly a table or box-and-whiskers style plot would be better?}}\label{fig:profits_costs}
+  \end{center}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+    \subfigure[L1]{\includegraphics[width=.45\textwidth]{figure/7751440918_3b54ff2397_o.png}\label{fig:L1npv_dist}}
+    \caption{\textbf{The impact of ignoring policy costs}.
+Distribution of net present value realized over 100 simulations when adjustment costs are ignored (blue), compared to when adjustment costs are optimally accounted for (red).
+\cdb{Though only L1 shown for the moment, would probably show all four types.
+Possibly a table or box-and-whiskers style plot would be better?}}\label{fig:npv_dist}
+  \end{center}
+\end{figure}
+
+Add two-by-two table of net present value accounting for:  ``Adjustment cost in policy calculation'' by ``adjustment cost in reality''?
+
+\cdb{\textbf{Further things to look at?}
+\begin{itemize}
+  \item How are costs partitioned between policy adjustments and deviation from optimality? 
+  \item Risk sensitivity: does policy inertia increase or decrease extinction risk?
+Does accounting for the policy cost increase or decrease extinction risk?
+(only in cases where extinction is possible: \emph{e.g.} in large variance, outside of Reed's self-sustaining range.
+Or Allee model)
+\end{itemize}
+}
+
 \section{Discussion}
-
+\cdb{Some possible things to discuss: could add others, could remove some.}
 \begin{itemize}
@@
 \item  Comparison between the different functional forms -- smoothing (L2)
-  non-smoothing (L1), and destablizing (fixed).
-\item   Induced costs (relative to free adjustment) vs direct costs -- why are
-  the induced costs much larger?
-\item   Impact of symmetric vs assymetric costs
-\item   Comparison to deterministic results
-\item   Contrast steady-state results to dynamic solutions under stochastic
-  shocks.
+  non-smoothing (L1), and de-stablizing (fixed).
+\item   Induced costs (relative to free adjustment) vs direct costs (paid for adjusting) 
+\item   Impact of symmetric vs asymmetric costs
+\item   Contrast steady-state results to dynamic solutions under stochastic shocks.
 \end{itemize}
 
-\section{References}
+\textbf{Key conclusions:}
+\begin{enumerate}
+  \item \textbf{Lesson for modelers}: Ignoring the reality of policy costs leads to less effective management (decreased value)  (increased extinction risk?)
+  \item \textbf{Lesson for policy makers}: Decreasing adjustment costs not only saves direct costs, but permits higher-value solutions.
+\end{enumerate}
 
-Bohm, Peter. 1974. ``On the Effects of Policy Costs.'' \emph{The Swedish
-Journal of Economics} 76 (mar): 104. doi:10.2307/3439361.
-
-Reed, William J. 1979. ``Optimal escapement levels in stochastic and
-deterministic harvesting models.'' \emph{Journal of Environmental
-Economics and Management} 6 (dec): 350--363.
-doi:10.1016/0095-0696(79)90014-7.
-
-Singh, R., Q. Weninger, and M. Doyle. 2006. ``Fisheries management with
-stock growth uncertainty and costly capital adjustment.'' \emph{Journal
-of Environmental Economics and Management} 52 (sep): 582--599.
-doi:10.1016/j.jeem.2006.02.006.
-
-Xepapadeas, A. P. 1992. ``Environmental policy, adjustment costs, and
-behavior of the firm.'' \emph{Journal of Environmental Economics and
-Management}: 258--275.
+\section*{References}
+\bibliography{outline_refs.bib}
 

### 2012-08-23 inst/examples/unmanaged_warning.Rmd
unmanaged warning example calibration

`ro tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache=TRUE, cache.path="managed_warning/" or`

``` {r  echo=FALSE, cache=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
````

# Detecting warning signals in an unmanaged system

This is a precursor exercise to managed_warning.Rmd to calibrate a reasonable set of parameters over which to evaluate the detection.

``` {r  setup, echo=FALSE, cache=FALSE}
# load required libraries
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
rm(list=ls())
````

Simulate from the May population dynamics function

``` {r  simulate }
x <- vector(mode="double", length=n)
a <- x
x[1] <- 8 # positive equilibrium
z <- rlnorm(n, 0, .1)
r = .75; k = 10; a[1]=1.55; H=1; Q = 3
for(t in 1:n){
  x[t+1] = z[t] *  x[t] * exp(r * (1 - x[t] / k) - a[t] * x[t] ^ (Q - 1) / (x[t] ^ Q + H ^ Q)) 
  a[t+1] = a[t] + .01
}
````

### Plot of timeseries

``` {r  p0}
plot(x, type='l')
````

Truncate the timeseries

``` {r truncate}
y <- x[x > 1.5]
````

### Calculate warning signals on the truncated series.

``` {r libs2}
library(earlywarning)
dat <- data.frame(time=1:length(y), value=y)
````

``` {r earlywarning}
acor_tau <- warningtrend(dat, window_autocorr)
var_tau <- warningtrend(dat, window_var)
````

## Model based statistics

Fit the models

``` {r modelbased}
A <- stability_model(dat, "OU")
B <- stability_model(dat, "LSN")
observed <- -2 * (logLik(A) - logLik(B))
m <- model$pars["m"]
````

Set up a parallel environment

``` {r parallel, include=FALSE}
library(snow)
library(methods)
cl <- makeCluster(20, type = "MPI")
clusterEvalQ(cl, library(earlywarning))
```

Evaluate the ROC curve

``` {r roc}
clusterExport(cl, ls())
clusterExport(cl, list = c("A", "B"))
reps <- parLapply(cl, 1:500, function(i) compare(A, B))
lr <- lik_ratios(reps)
roc <- roc_data(lr)
```

Plot results.

``` {r plotroc}
require(ggplot2)
ggplot(lr) + geom_density(aes(value, fill = simulation), alpha = 0.6) + 
    geom_vline(aes(xintercept = observed))
ggplot(roc) + geom_line(aes(False.positives, True.positives))
```

### 2012-08-23 inst/examples/unmanaged_warning.Rmd
launched unmanaged warning, calibration step for issue #21

@@
-`ro tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache=TRUE, cache.path="managed_warning/" or`
+`ro tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache=TRUE, cache.path="unmanaged_warning/" or`
 
 ``` {r  echo=FALSE, cache=FALSE}
-opts_knit$set(upload.fun = socialR::flickr.url)
 options(device = function(width = 5, height = 5) {

### 2012-08-23 inst/examples/unmanaged_warning.Rmd
step by step: initial signals for #21

@@
 ``` {r  simulate }
+n <- 5000
 x <- vector(mode="double", length=n)
@@
   x[t+1] = z[t] *  x[t] * exp(r * (1 - x[t] / k) - a[t] * x[t] ^ (Q - 1) / (x[t] ^ Q + H ^ Q)) 
-  a[t+1] = a[t] + .01
+  a[t+1] = a[t] + .001
 }
@@
 observed <- -2 * (logLik(A) - logLik(B))
-m <- model$pars["m"]
+m <- B$pars["m"]
 ````
-
-Set up a parallel environment
-
-``` {r parallel, include=FALSE}
-library(snow)
-library(methods)
-cl <- makeCluster(20, type = "MPI")
-clusterEvalQ(cl, library(earlywarning))
-```
-
-Evaluate the ROC curve
-
-``` {r roc}
-clusterExport(cl, ls())
-clusterExport(cl, list = c("A", "B"))
-reps <- parLapply(cl, 1:500, function(i) compare(A, B))
-lr <- lik_ratios(reps)
-roc <- roc_data(lr)
-```
-
-Plot results.
-
-``` {r plotroc}
-require(ggplot2)
-ggplot(lr) + geom_density(aes(value, fill = simulation), alpha = 0.6) + 
-    geom_vline(aes(xintercept = observed))
-ggplot(roc) + geom_line(aes(False.positives, True.positives))
-```

### 2012-08-23 inst/examples/unmanaged_warning.Rmd
step by step: initial signals for #21

@@
 z <- rlnorm(n, 0, .1)
-r = .75; k = 10; a[1]=1.55; H=1; Q = 3
+r = .75; k = 10; a[1]=1; H=1; Q = 3
 for(t in 1:n){
   x[t+1] = z[t] *  x[t] * exp(r * (1 - x[t] / k) - a[t] * x[t] ^ (Q - 1) / (x[t] ^ Q + H ^ Q)) 
-  a[t+1] = a[t] + .001
+  a[t+1] = a[t] + 1/5000
 }
@@
 m <- B$pars["m"]
+
+observed
+m
 ````
+
+Set up a parallel environment
+
+``` {r parallel}
+library(snow)
+library(methods)
+cl <- makeCluster(20, type = "MPI")
+clusterEvalQ(cl, library(earlywarning))
+```

### 2012-08-24 inst/examples/unmanaged_warning.Rmd
initial signals for unmanaged case. #21

@@
 
+``` {r  p1}
+plot(y, type='l')
+````
+
 ### Calculate warning signals on the truncated series.
@@
 library(methods)
-cl <- makeCluster(20, type = "MPI")
-clusterEvalQ(cl, library(earlywarning))
+#cl <- makeCluster(20, type = "MPI")
+#clusterEvalQ(cl, library(earlywarning))
+#clusterExport(cl, ls())
+#clusterExport(cl, list = c("A", "B"))
+require(snowfall)
+sfInit(par=T, cpu=12)
+sfLibrary(earlywarning)
+sfExportAll() 
 ```
+
+Evaluate the ROC curve
+
+``` {r roc}
+reps <- sfLapply(1:500, function(i) compare(A, B))
+lr <- lik_ratios(reps)
+roc <- roc_data(lr)
+```
+
+Plot results.
+
+``` {r plotroc}
+require(ggplot2)
+ggplot(lr) + geom_density(aes(value, fill = simulation), alpha = 0.6) + 
+    geom_vline(aes(xintercept = observed))
+ggplot(roc) + geom_line(aes(False.positives, True.positives))
+```

### 2012-08-24 inst/examples/unmanaged_warning.Rmd
added summary stats graphs. #21

@@
 var_tau <- warningtrend(dat, window_var)
+
+acor_tau
+var_tau
 ````
@@
 
+``` {r summarystat_roc} 
+summarystat_roc <- function(A,B, summarystat_functions, reps=200){
+  require(plyr)
+  require(reshape2)
+  Asim <- simulate(A, reps)
+  Bsim <- simulate(B, reps)
+  sim <- melt(Asim, id = "time")
+  Bsim <- melt(Bsim, id = "time")
+  names(Asim)[2] <- "rep"
+  names(Bsim)[2] <- "rep"
+	dat <- lapply(summarystat_functions, function(f){
+	  wsA <- ddply(Asim, "rep", warningtrend, f)
+  	wsB <- ddply(Bsim, "rep", warningtrend, f)
+	  data.frame(null = wsA$tau, test = wsB$tau)
+	})
+	tidy <- melt(dat)
+}
+
+tau_dist <- summarystat_roc(A, B, list(var=window_var, acor=window_autocorr))
+head(tau_dist)
+```
+
 Set up a parallel environment
@@
 ``` {r parallel}
-library(snow)
-library(methods)
-#cl <- makeCluster(20, type = "MPI")
-#clusterEvalQ(cl, library(earlywarning))
-#clusterExport(cl, ls())
-#clusterExport(cl, list = c("A", "B"))
 require(snowfall)

### 2012-09-01 inst/examples/figure3.Rmd
added coarse linear interp

@@
-`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="voi_sethi_parameters_bignoise/", verbose=TRUE or`
+`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="figure3/", verbose=TRUE or`
 
@@
 require(snowfall)
-sfInit(parallel=TRUE, cpu=16)
+sfInit(parallel=TRUE, cpu=4)
 ````
@@
 
-  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=2e5)
+  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=1e3)
   opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
@@
 lvl <- 0.5
-````
-
-``` {r }
-det <- scenario(0.0, 0.00, 0.00)
-````
-
-``` {r }
-all_low <- scenario(0.1, 0.1, 0.1)
-````
-
-``` {r }
+det <- scenario(0.001, 0.00, 0.00)
 g   <- scenario(lvl, 0, 0)
-````
-
-``` {r }
 m   <- scenario(0, lvl, 0)
-````
-
-``` {r }
 i   <- scenario(0, 0, lvl)
-````
-
-``` {r }
-gm  <- scenario(lvl, lvl, 0)
-````
-
-``` {r }
-gi  <- scenario(lvl, 0, lvl)
-````
-
-``` {r }
-mi  <- scenario(0, lvl, lvl)
-````
-
-``` {r }
-gmi <- scenario(lvl, lvl, lvl)
-````
-
-```{r }
-low <- all_low
 ````
@@
 require(reshape2)
-policy <- melt(data.frame(stock = x_grid, det = det$D[,1], low=low$D[,1],
-               g = g$D[,1], m = m$D[,1], i= i$D[,1], 
-               gm = gm$D[,1], gi = gi$D[,1], mi = mi$D[,1], gmi = gmi$D[,1]), 
-               id = "stock")
 policy <- melt(data.frame(stock = x_grid, low=low$D[,1],

### 2012-09-01 inst/examples/figure3.Rmd
cpu settings for farm

@@
 require(snowfall)
-sfInit(parallel=TRUE, cpu=4)
+sfInit(parallel=TRUE, cpu=16)
 ````
@@
 
-  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=1e3)
+  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=1e5)
   opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
@@
 require(reshape2)
-policy <- melt(data.frame(stock = x_grid, low=low$D[,1],
+policy <- melt(data.frame(stock = x_grid, det=det$D[,1],
                g = g$D[,1], m = m$D[,1], i= i$D[,1]), 
@@
 
-ggplot(policy) + 
+ggplot(policy) + geom_line(aes(stock, stock-x_grid[value], color=variable))
+
+linear <- dt[,approx(stock, stock-x_grid[value], xout=seq(1,150, length=20)), by=variable]
+ggplot(linear) + geom_line(aes(x,y,color=variable))
 #  geom_point(aes(stock, stock-x_grid[value], color=variable)) +
-	geom_smooth(aes(stock, stock-x_grid[value], color=variable)) +
-  ylab("escapement") 
+	#geom_smooth(aes(stock, stock-x_grid[value], color=variable)) 
 ```

### 2012-09-01 inst/examples/managed_warning.Rmd

--- 2012-07-28 inst/examples/managed_warning.Rmd
@@
 ``` {r }
-pars <- c(r = .75, k = 10, a=1.7, H=1, Q = 3)
+pars <- c(r = .75, k = 10, a=1, H=1, Q = 3)
 K <- 8 # approx
@@
 ``` {r miscpars}
-delta <- 0.05
+delta <- 0.005
 xT <- 0
-OptTime <- 200
+OptTime <- 5000
 sigma_g <- .1
@@
 ``` {r noise}
-z_g <- function() dlnorm(1, 0, sigma_g)
+z_g <- function() rlnorm(1, 0, sigma_g) 
 ````
@@
 ``` {r  SDP_Mat}
-SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g)
+pdfn <- function(P, s){
+  dunif(P, 1 - s, 1 + s)
+}
+SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
 ````
@@
 
-``` {r  simulate }
-sims <- lapply(1:100, function(i){
-  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i)
-})
+``` {r simulateme}
+Dt <- 1
+
+ForwardSimulate <- 
+  function(f, pars, x_grid, h_grid, x0, D, z_g,
+         z_m=function(x) 1, z_i = function(x) 1, 
+         profit=NULL){
+
+  OptTime <- dim(D)[2]    # Stopping time
+  x_h <- numeric(OptTime) # population dynamics with harvest
+  h <- numeric(OptTime) # optimal havest level
+  x_h[1] <- x0  # initial values
+  s <- x_h # also track escapement
+  x <- x_h # What would happen with no havest
+  p <- numeric(OptTime)
+
+  ## Simulate through time ##
+  for(t in 1:(OptTime-1)){
+
+    # Move towards collapse
+    pars[3] <- pars[3] + Dt/OptTime
+
+    # Assess stock, with potential measurement error
+    m_t <- x_h[t] * z_m()
+    # Current state (is closest to which grid posititon) 
+    St <- which.min(abs(x_grid - m_t)) 
+    q_t <- h_grid[D[St, (t + 1) ]] 
+    # Implement harvest/(effort) based on quota with noise 
+    h[t] <- q_t * z_i()
+    # Noise in growth 
+    z <- z_g() 
+    # population grows
+    x_h[t+1] <- z * f(x_h[t], h[t], pars) # with havest
+    s[t+1]   <- x_h[t] - q_t # anticipated escapement
+    x[t+1]   <- z * f(x[t], 0, pars) # havest-free dynamics
+    p[t] <- profit(x_h[t], h[t])
+  }
+  data.frame(time = 1:OptTime, fishstock = x_h, harvest = h,
+             unharvested = x, escapement = s, profit = p) 
+}
+
+dat <- ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i)
+x <- dat$fishstock
+```
+
+### Plot of timeseries
+
+``` {r  p0}
+plot(x, type='l')
 ````
 
-## Summarize and plot the results
+Truncate the timeseries
 
-R makes it easy to work with this big replicate data set.  We make data tidy (melt), fast (data.tables), and nicely labeled.
-
-``` {r  tidy}
-dat <- melt(sims, id=names(sims[[1]]))  
-dt <- data.table(dat)
-setnames(dt, "L1", "reps") # names are nice
+``` {r truncate}
+y <- x[x > 1.5]
 ````
 
-### Plots
-
-``` {r  p0}
-p0 <- ggplot(subset(dt,reps==1)) +
-  geom_line(aes(time, fishstock)) +
-  geom_abline(intercept=opt$S, slope = 0) +
-  geom_line(aes(time, harvest), col="darkgreen") 
-p0
+``` {r  p1}
+plot(y, type='l')
 ````
 
-This plot summarizes the stock dynamics by visualizing the replicates.
-Reed's S shown again, along with the dotted line showing the allee threshold, below which the stock will go to zero (unless rescued stochastically).
-
-``` {r  p1}
-p1 <- ggplot(dt) + geom_abline(intercept=opt$S, slope = 0) + 
-  geom_abline(intercept=xT, slope = 0, lty=2) 
-p1 <- p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.2)
-p1
-````
-
-## Calculate warning signals on managed system
+### Calculate warning signals on the truncated series.
 
@@
 library(earlywarning)
+dat <- data.frame(time=1:length(y), value=y)
 ````
@@
 ``` {r earlywarning}
-acor_tau <- dt[, 
-               warningtrend(data.frame(time=time, value=fishstock),
-                            window_autocorr),
-               by=reps]
+acor_tau <- warningtrend(dat, window_autocorr)
+var_tau <- warningtrend(dat, window_var)
 
-var_tau <- dt[, 
-              warningtrend(data.frame(time=time, value=fishstock),
-                          window_var),
-              by=reps]
+acor_tau
+var_tau
 ````
 
+## Model based statistics
+
+Fit the models
+
 ``` {r modelbased}
-m <- dt[, 
-        stability_model(data.frame(time=time, value=fishstock),
-                          "LSN")$pars["m"],
-        by=reps]
+A <- stability_model(dat, "OU")
+B <- stability_model(dat, "LSN")
+observed <- -2 * (logLik(A) - logLik(B))
+m <- B$pars["m"]
+
+observed
+m
 ````
 
-``` {r summaryplot}
-signals <- melt(data.frame(var=var_tau$V1, acor=acor_tau$V1, m=m$V1))
-ggplot(signals) + geom_histogram(aes(value)) + facet_wrap(~variable, scales="free")
-````
+Compute summary stat versions
 
-## Unmanaged warning signals
-Calculate warning signals on the same set of shocks in unfished data
+``` {r summarystat_roc} 
+summarystat_roc <- function(A,B, summarystat_functions, reps=200){
+  require(plyr)
+  require(reshape2)
+  Asim <- simulate(A, reps)
+  Bsim <- simulate(B, reps)
+  Asim <- melt(Asim, id = "time")
+  Bsim <- melt(Bsim, id = "time")
+  names(Asim)[2] <- "rep"
+  names(Bsim)[2] <- "rep"
+	dat <- lapply(summarystat_functions, function(f){
+	  wsA <- ddply(Asim, "rep", warningtrend, f)
+  	wsB <- ddply(Bsim, "rep", warningtrend, f)
+	  data.frame(null = wsA$tau, test = wsB$tau)
+	})
+	tidy <- melt(dat)
+}
 
-``` {r earlywarning2}
-acor_tau <- dt[, 
-               warningtrend(data.frame(time=time, value=unharvested),
-                            window_autocorr),
-               by=reps]
+dat <- summarystat_roc(A,B, list(var=window_var, acor=window_autocorr))
+ggplot(dat) + geom_density(aes(value, fill=variable)) + facet_wrap(~L1)
+```
 
-var_tau <- dt[, 
-              warningtrend(data.frame(time=time, value=unharvested),
-                          window_var),
-              by=reps]
-````
+Set up a parallel environment
 
-``` {r modelbased2}
-m <- dt[, 
-        stability_model(data.frame(time=time, value=unharvested),
-                          "LSN")$pars["m"],
-        by=reps]
-````
+``` {r parallel}
+require(snowfall)
+sfInit(par=T, cpu=12)
+sfLibrary(earlywarning)
+sfExportAll() 
+```
 
-``` {r summaryplot2}
-signals <- melt(data.frame(var=var_tau$V1, acor=acor_tau$V1, m=m$V1))
-ggplot(signals) + geom_histogram(aes(value)) + facet_wrap(~variable, scales="free")
-````
+Evaluate the ROC curve
+
+``` {r roc}
+reps <- sfLapply(1:500, function(i) compare(A, B))
+lr <- lik_ratios(reps)
+roc <- roc_data(lr)
+```
+
+Plot results.
+
+``` {r plotroc}
+require(ggplot2)
+ggplot(lr) + geom_density(aes(value, fill = simulation), alpha = 0.6) + 
+    geom_vline(aes(xintercept = observed))
+ggplot(roc) + geom_line(aes(False.positives, True.positives))
+```

### 2012-09-03 inst/examples/figure3.Rmd
figure 3 more reps

@@
 ``` {r  echo=FALSE, cache=FALSE }
-opts_knit$set(upload.fun = socialR::flickr.url)
-options(device = function(width = 5, height = 5) {
-    pdf(NULL, width = width, height = height)
-})
-knitcitations::cleanbib()
+#opts_knit$set(upload.fun = socialR::flickr.url)
+#options(device = function(width = 5, height = 5) {
+#    pdf(NULL, width = width, height = height)
+#})
 ````
@@
 
- Implements a numerical version of the SDP described in `r knitcitations::citep("10.1016/j.jeem.2004.11.005")`.
+ Implements a numerical version of the SDP described in `r #knitcitations::citep("10.1016/j.jeem.2004.11.005")`.
  Compute the optimal solution under different forms of uncertainty.
@@
 ggplot(policy) + geom_line(aes(stock, stock-x_grid[value], color=variable))
-
+dt <- data.table(policy)
 linear <- dt[,approx(stock, stock-x_grid[value], xout=seq(1,150, length=20)), by=variable]

### 2012-09-03 inst/examples/figure3.Rmd
change interpolation

@@
 ggplot(policy) + geom_line(aes(stock, stock-x_grid[value], color=variable))
-dt <- data.table(policy)
-linear <- dt[,approx(stock, stock-x_grid[value], xout=seq(1,150, length=20)), by=variable]
-ggplot(linear) + geom_line(aes(x,y,color=variable))
+dat <- subset(policy, fishstock < 120)
+dt <- data.table(dat)
+linear <- dt[,approx(stock, stock-x_grid[value], xout=seq(1,150, length=15)), by=variable]
+ggplot(linear) + geom_smooth(aes(x,y,color=variable))
 #  geom_point(aes(stock, stock-x_grid[value], color=variable)) +

### 2012-09-03 inst/examples/figure3.Rmd
change interpolation

--- 2012-09-03 inst/examples/figure3.Rmd
@@
 ggplot(policy) + geom_line(aes(stock, stock-x_grid[value], color=variable))
-dt <- data.table(policy)
-linear <- dt[,approx(stock, stock-x_grid[value], xout=seq(1,150, length=20)), by=variable]
-ggplot(linear) + geom_line(aes(x,y,color=variable))
+dat <- subset(policy, stock < 120)
+dt <- data.table(dat)
+linear <- dt[,approx(stock, stock-x_grid[value], xout=seq(1,150, length=15)), by=variable]
+ggplot(linear) + geom_smooth(aes(x,y,color=variable))
 #  geom_point(aes(stock, stock-x_grid[value], color=variable)) +

### 2012-09-03 inst/examples/figure3.Rmd
Formatted figure, closes #26

--- 2012-09-03 inst/examples/figure3.Rmd
@@
 rm(list=ls())
+
+theme_publish <- theme_set(theme_bw(14))
+theme_publish <- 
+  theme_update(axis.line=theme_blank(),
+        axis.text.y=theme_blank(),
+        legend.position=c(.9,.1),
+        panel.grid.major=theme_blank(),panel.grid.minor=theme_blank(),
+        plot.background=theme_blank(), legend.title=theme_blank())
+
 ````
@@
 
-``` {r sethiplots, rerun=TRUE}
+``` {r sethiplots, cache=FALSE}
 require(reshape2)
-policy <- melt(data.frame(stock = x_grid, det=det$D[,1],
-               g = g$D[,1], m = m$D[,1], i= i$D[,1]), 
+policy <- melt(data.frame(stock = x_grid, deterministic=det$D[,1],
+               growth = g$D[,1], measurement = m$D[,1], implementation = i$D[,1]), 
                id = "stock")
 
-ggplot(policy) + geom_line(aes(stock, stock-x_grid[value], color=variable))
-dt <- data.table(policy)
-linear <- dt[,approx(stock, stock-x_grid[value], xout=seq(1,150, length=20)), by=variable]
-ggplot(linear) + geom_line(aes(x,y,color=variable))
+ggplot(policy) + geom_point(aes(stock, stock-x_grid[value], color=variable))
+dat <- subset(policy, stock < 140)
+dt <- data.table(dat)
+linear <- dt[,approx(stock, stock-x_grid[value], xout=seq(1,150, length=15)), by=variable]
+ggplot(linear) + geom_smooth(aes(x,y,color=variable), fill=NA) + xlab("Measured Stock") + ylab("Optimal Expected Escapement")
 #  geom_point(aes(stock, stock-x_grid[value], color=variable)) +
-	#geom_smooth(aes(stock, stock-x_grid[value], color=variable)) 
+# geom_smooth(aes(stock, stock-x_grid[value], color=variable)) 
 ```

### 2012-09-03 inst/examples/figure3.Rmd
updated figure3 for a replicate run

@@
 theme_publish <- 
-  theme_update(axis.line=theme_blank(),
-        axis.text.y=theme_blank(),
-        legend.position=c(.9,.1),
+  theme_update(legend.key = theme_blank(),legend.position=c(.9,.1),
         panel.grid.major=theme_blank(),panel.grid.minor=theme_blank(),
@@
 xmax <- 1.5 * K
-grid_n <- 100
+grid_n <- 200
 ````
@@
 
-  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=1e5)
+  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=2e4)
   opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
@@
 lvl <- 0.5
+low <- scenario(0.1, 0.1, 0.1)
 det <- scenario(0.001, 0.00, 0.00)
@@
 require(reshape2)
-policy <- melt(data.frame(stock = x_grid, deterministic=det$D[,1],
+policy <- melt(data.frame(stock = x_grid, deterministic=det$D[,1], all_low = low$D[,1],
                growth = g$D[,1], measurement = m$D[,1], implementation = i$D[,1]), 

### 2012-09-03 inst/examples/Reed.Rmd
run for figure3_det, doing deterministic exactly #26

@@
    dunif(P, 1 - s, 1 + s)
-#  dlnorm(P, 0, s)
 }

### 2012-09-03 inst/examples/figure3.Rmd
run for figure3_det, doing deterministic exactly #26

@@
-`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="figure3/", verbose=TRUE or`
+`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="figure3_det/", verbose=TRUE or`
 
@@
 
+Do the deterministic exactly,
+
+```{r deterministic}
+pdfn <- function(P, s){
+     dunif(P, 1 - s, 1 + s)
+}
+SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g=0.5, pdfn)
+det <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
+````
+
 Determine the policies for each of the scenarios (noise combinations).
@@
 low <- scenario(0.1, 0.1, 0.1)
-det <- scenario(0.001, 0.00, 0.00)
 g   <- scenario(lvl, 0, 0)

### 2012-09-04 inst/examples/figure3.Rmd
smoothed plot uses first order spline, #26

@@
 
-ggplot(policy) + geom_point(aes(stock, stock-x_grid[value], color=variable))
+ggplot(policy) + geom_point(aes(stock, stock-x_grid[value], color=variable), shape="+")
 dat <- subset(policy, stock < 140)
@@
 linear <- dt[,approx(stock, stock-x_grid[value], xout=seq(1,150, length=15)), by=variable]
-ggplot(linear) + geom_smooth(aes(x,y,color=variable), fill=NA) + xlab("Measured Stock") + ylab("Optimal Expected Escapement")
-#  geom_point(aes(stock, stock-x_grid[value], color=variable)) +
-# geom_smooth(aes(stock, stock-x_grid[value], color=variable)) 
+ggplot(linear) + 
+	stat_smooth(aes(x,y,color=variable), degree=1, se=FALSE, span=.3) + 
+	xlab("Measured Stock") + ylab("Optimal Expected Escapement")
 ```

### 2012-09-06 inst/examples/figure3.Rmd
fix sdp calc: use z_m*z_g*f(y/z_m, q*z_i, p)

@@
-`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="figure3_det/", verbose=TRUE or`
+`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="figure3/", verbose=TRUE or`
 
@@
 
-# Calculating the value of information
-
- Implements a numerical version of the SDP described in `r #knitcitations::citep("10.1016/j.jeem.2004.11.005")`.
- Compute the optimal solution under different forms of uncertainty.
+## Generate Figure 3 of Sethi et al. 2006
 
@@
 rm(list=ls())
-
 theme_publish <- theme_set(theme_bw(14))

### 2012-09-06 R/determine_SDP_matrix.R

@@ -125,7 +125,7 @@ SDP_by_simulation <- function(f, p, x_grid, h_grid, z_g, z_m, z_i, reps = 999){
 
   SDP_Mat <- sfLapply(h_grid, function(h){ 
     mat <- sapply(x_grid, function(x){
-      x_t1 <- replicate(reps, z_g() * z_i() * f(x, z_m() * h, p)) 
+      x_t1 <- replicate(reps, z_g() * z_m() * f(x / z_m(), z_i() * h, p)) 
       a <- mybin( x_t1, binwidth=bw, range=c(lower, upper))$count
       a / sum(a) 
     })

### 2012-09-11 inst/examples/debug_uniform.Rmd
Looking into doing integral analytically and quasi-analytically for the uniform case

--- 2012-09-06 inst/examples/figure3.Rmd
@@
 
-With parameters `r` = `r r <- 1` and `K` = `r K <- 100`.
+With parameters
 
 ``` {r }
+r <- 1
+K <- 100
 pars <- c(r, K)
 ````
+
+`r` = `r r` and `K` = `r K`.
 
@@
 
-We use Monte Carlo integration over the noise processes to determine the transition matrix.
-
-``` {r beparallel, cache=FALSE}
-require(snowfall)
-sfInit(parallel=TRUE, cpu=16)
-````
-
-``` {r policyscenarios}
-scenario <- function(policy_g, policy_m, policy_i){
-
-  z_g <- function() 1+(2*runif(1, 0,  1)-1) * policy_g
-  z_m <- function() 1+(2*runif(1, 0,  1)-1) * policy_m
-  z_i <- function() 1+(2*runif(1, 0,  1)-1) * policy_i
-
-  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=2e4)
-  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
-                       profit, delta, reward=0)
-}
-````
-
 Do the deterministic exactly,
@@
 }
-SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g=0.5, pdfn)
+SDP_Mat <- SDP_uniform(f, pars, x_grid, h_grid, sigma_g=0.5, pdfn, sigma_m=.5, sigma_i=.5)
+
+SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g = 0.5, pdfn)
 det <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)

### 2012-09-11 R/SDP_uniform.R

@@ -1,0 +1,56 @@
+#' Determine the SDP matrix for uniform noise under multiple uncertainty
+#'
+#' Computes the transition matrix under the case of growth noise, 
+#' implementation errors in harvesting, and meaurement errors in 
+#' the stock assessment.  Assumes noise sources are distributed 
+#' by uniform distributions to obtain analytic transition probability densities.
+#'
+#' @param f the growth function of the escapement population (x-h)
+#'   should be a function of f(t, y, p), with parameters p
+#' @param p the parameters of the growth function
+#' @param x_grid the discrete values allowed for the population size, x
+#' @param h_grid the discrete values of harvest levels to optimize over
+#' @param sigma_g is the shape parameter (width) of the multiplicitive growth noise 
+#' @param pdfn is the shape of the growth noise, which need not be uniform (is by default)
+#' @param sigma_m is the half-width of the uniform measurement error (assumes uniform distribution)
+#' @param sigma_i is the half-width of the implementation noise (always assumes uniform distribution)
+#' @param f_int is the function given by the analytic solution,  
+#' $F(x,q) = \frac{1}{4\sigma_i\sigma_m} \int_{q-\sigma_i}^{q+\sigma_i} dh \int_{x-\sigma_m}^{x+\sigma_m} f(y, h)$
+#' For logistic map $f(y,h) = 2 (y-h) \left(1-\frac{y-h}{2K}\right)$, this is: 
+#' F <- function(x,q, m, n) 4*m*n*(6*x*K-6*q*K-3*x^2 + 6*q*x - 3*q^2-n^2-m^2) / (3*K)
+#' (where we've used m = \sigma_m, n = \sigma_i for simplicity of Roman notation)
+#' @export
+SDP_uniform <- function(f, p, x_grid, h_grid, sigma_g,
+                        pdfn=function(P, s) dunif(P, 1-s, 1+s),
+                        sigma_m, sigma_i, 
+                        f_int = function(x,q, m, n, pars){
+                          K <- pars[2]
+                          4*m*n*(6*x*K-6*q*K-3*x^2 + 6*q*x - 3*q^2-n^2-m^2) / (3*K)
+                        }
+                         ){
+  gridsize <- length(x_grid)
+  SDP_Mat <- lapply(h_grid, function(h){
+    SDP_matrix <- matrix(0, nrow=gridsize, ncol=gridsize)
+    # Cycle over x values
[…]

### 2012-09-11 inst/examples/figure3.Rmd
new method added

@@
 }
-SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g=0.5, pdfn)
+SDP_Mat <- SDP_uniform(f, pars, x_grid, h_grid, sigma_g=0.5, pdfn, sigma_m=.5, sigma_i=.5)
 det <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)

### 2012-09-11 inst/examples/debug_uniform.Rmd
Analytic multiple noise, for farm run (figure3.Rmd)

@@
-`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="figure3/", verbose=TRUE or`
+`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="debug/", verbose=TRUE or`
 
@@
 xmax <- 1.5 * K
-grid_n <- 200
+grid_n <- 100
 ````
@@
 OptTime <- 25
+sigma_g <- .5
+sigma_m <- .5
+sigma_i <- .5
 ````
@@
 # Scenarios:
+
+```{r }
+int_f <- function(f, x, q, sigma_m, sigma_i, pars){
+  g <- function(X) f(X[1], X[2], pars)
+  lower <- c(max(x - sigma_m, 0), max(q - sigma_i, 0))
+  upper <- c(x + sigma_m, q + sigma_i)
+  out <- adaptIntegrate(g, lower, upper)
+  out$integral
+}
+
+F <- function(x,q, m, n, pars){
+  K <- pars[2]
+  out <- ((q+n-max(0,q-n))*(x+m-max(0,x-m))*(6*x*K-6*q*K-6*n*K+6*m*K+6*max(0,x-m)*K-6*
+    max(0,q-n)*K-2*x^2+3*q*x+3*n*x-4*m*x-2*max(0,x-m)*x+3*max(0,q-n)*x-2*q^2-4*n*q+3*m*q+3*
+    max(0,x-m)*q-2*max(0,q-n)*q-2*n^2+3*m*n+3*max(0,x-m)*n-2*max(0,q-n)*n-2*m^2-2*max(0,x-m)*m+3*
+    max(0,q-n)*m-2*max(0,x-m)^2+3*max(0,q-n)*max(0,x-m)-2*max(0,q-n)^2))/(6*K)
+  max(out,0)
+}
+```
+
+```{r }
+require(cubature)
+# Confirm that these give the same value, and time performance
+system.time(a <- sapply(x_grid, function(x) int_f(f, x, 1, .1, .1, pars)))
+system.time(b <- sapply(x_grid, function(x) F(x, 1, .1, .1, pars)))
+```
+
+```{r }
+sdp <- SDP_uniform(f, pars, x_grid, h_grid, sigma_g=sigma_g, pdfn=function(P, s) dunif(P, 1-s, 1+s), sigma_m=sigma_m, sigma_i=sigma_i, F)
+```
+
+```{r }
+uniform <- find_dp_optim(sdp, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
+```
 
@@
      }
-SDP_Mat <- SDP_uniform(f, pars, x_grid, h_grid, sigma_g=0.5, pdfn, sigma_m=.5, sigma_i=.5)
-
-SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g = 0.5, pdfn)
+SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g = sigma_g, pdfn)
 det <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
@@
 
-``` {r runall}
-lvl <- 0.5
-low <- scenario(0.1, 0.1, 0.1)
-g   <- scenario(lvl, 0, 0)
-m   <- scenario(0, lvl, 0)
-i   <- scenario(0, 0, lvl)
-````
+```{r}
+  z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
+  z_m <- function() 1+(2*runif(1, 0,  1)-1) * sigma_m
+  z_i <- function() 1+(2*runif(1, 0,  1)-1) * sigma_i
+
+  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=2e4)
+  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
+                       profit, delta, reward=0)
+```
 
@@
 require(reshape2)
-policy <- melt(data.frame(stock = x_grid, deterministic=det$D[,1], all_low = low$D[,1],
-               growth = g$D[,1], measurement = m$D[,1], implementation = i$D[,1]), 
+policy <- melt(data.frame(stock = x_grid, deterministic=det$D[,1], uniform = uniform$D[,1], mc=opt$D[,1]), 
                id = "stock")

### 2012-09-11 inst/examples/figure3.Rmd
Analytic multiple noise, for farm run (figure3.Rmd)

@@
 
-We use Monte Carlo integration over the noise processes to determine the transition matrix.
+--We use Monte Carlo integration over the noise processes to determine the transition matrix.--
 
-``` {r beparallel, cache=FALSE}
+We compute the transition probability analytically, (confirm that this is correct!)
+
+$F(x,q) = \frac{1}{4\sigma_i\sigma_m} \int_{q-\sigma_i}^{q+\sigma_i} dh \int_{x-\sigma_m}^{x+\sigma_m} f(y, h)$
+
+We will use the analytic solution
+
+```{r}
+F <- function(x,q, m, n, pars){
+  K <- pars[2]
+  out <- ((q+n-max(0,q-n))*(x+m-max(0,x-m))*(6*x*K-6*q*K-6*n*K+6*m*K+6*max(0,x-m)*K-6*
+    max(0,q-n)*K-2*x^2+3*q*x+3*n*x-4*m*x-2*max(0,x-m)*x+3*max(0,q-n)*x-2*q^2-4*n*q+3*m*q+3*
+    max(0,x-m)*q-2*max(0,q-n)*q-2*n^2+3*m*n+3*max(0,x-m)*n-2*max(0,q-n)*n-2*m^2-2*max(0,x-m)*m+3*
+    max(0,q-n)*m-2*max(0,x-m)^2+3*max(0,q-n)*max(0,x-m)-2*max(0,q-n)^2))/(6*K)
+  max(out,0)
+}
+```
+
+We can verify our solution is the same as the numerical integral (which is slower to compute)
+
+```{r }
+int_f <- function(f, x, q, sigma_m, sigma_i, pars){
+  g <- function(X) f(X[1], X[2], pars)
+  lower <- c(max(x - sigma_m, 0), max(q - sigma_i, 0))
+  upper <- c(x + sigma_m, q + sigma_i)
+  out <- adaptIntegrate(g, lower, upper)
+  out$integral
+}
+```
+
+```{r }
+require(cubature)
+# Confirm that these give the same value, and time performance
+system.time(a <- sapply(x_grid, function(x) int_f(f, x, 1, .1, .1, pars)))
+system.time(b <- sapply(x_grid, function(x) F(x, 1, .1, .1, pars)))
+```
+
+``` {r beparallel, cache=FALSE, eval=FALSE}
 require(snowfall)
@@
 
-``` {r policyscenarios}
+The policies
+
+```{r}
+stm <- SDP_uniform(f, pars, x_grid, h_grid, sigma_g=0.5, pdfn=function(P, s) dunif(P, 1-s, 1+s), sigma_m=0, sigma_i=0, F)
+g <- find_dp_optim(stm, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
+stm <- SDP_uniform(f, pars, x_grid, h_grid, sigma_g=0, pdfn=function(P, s) dunif(P, 1-s, 1+s), sigma_m=0.5, sigma_i=0, F)
+m <- find_dp_optim(stm, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
+stm <- SDP_uniform(f, pars, x_grid, h_grid, sigma_g=0, pdfn=function(P, s) dunif(P, 1-s, 1+s), sigma_m=0, sigma_i=0.5, F)
+i <- find_dp_optim(stm, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
+stm <- SDP_uniform(f, pars, x_grid, h_grid, sigma_g=0.1, pdfn=function(P, s) dunif(P, 1-s, 1+s), sigma_m=0.1, sigma_i=0.1, F)
+low <- find_dp_optim(stm, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
+```
+
+``` {r policyscenarios, eval=FALSE, include=FALSE} 
+# not run
 scenario <- function(policy_g, policy_m, policy_i){ 
-
   z_g <- function() 1+(2*runif(1, 0,  1)-1) * policy_g
@@
   z_i <- function() 1+(2*runif(1, 0,  1)-1) * policy_i
-
   SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=2e4)
@@
 
-Determine the policies for each of the scenarios (noise combinations).
-
-``` {r runall}
+``` {r runall, eval=FALSE, include=FALSE}
 lvl <- 0.5

### 2012-09-11 R/SDP_uniform.R

@@ -22,9 +22,7 @@
 #' @export
 SDP_uniform <- function(f, p, x_grid, h_grid, sigma_g,
                         pdfn=function(P, s) dunif(P, 1-s, 1+s),
-                        sigma_m, sigma_i, 
-                        f_int = 
-                         ){
+                        sigma_m, sigma_i, f_int){
   gridsize <- length(x_grid)
   SDP_Mat <- lapply(h_grid, function(h){
     SDP_matrix <- matrix(0, nrow=gridsize, ncol=gridsize)
@@ -32,14 +30,15 @@ SDP_uniform <- function(f, p, x_grid, h_grid, sigma_g,
     for(i in 1:gridsize){ 
       ## Calculate the expected transition  
       x1 <- x_grid[i]
-      x2_expected <- f_int(x1, h, sigma_m, sigma_i,p)
+      x2_expected <- f(x1,h,p)
+      P_of_x2 <- f_int(x1, h, sigma_m, sigma_i, p)
       ## If expected 0, go to 0 with probabilty 1
       if( x2_expected == 0) 
         SDP_matrix[i,1] <- 1  
       else {
         # relative probability of a transition to that state
         ProportionalChance <- x_grid / x2_expected
-        Prob <- pdfn(ProportionalChance, sigma_g)
+        Prob <- P_of_x2 * pdfn(ProportionalChance, sigma_g)
 
         # Store normalized probabilities in row
         SDP_matrix[i,] <- Prob/sum(Prob)
@@ -51,12 +50,12 @@ SDP_uniform <- function(f, p, x_grid, h_grid, sigma_g,
 }
 
 
-require(cubature)
 
-f_int <- function(f,x,q,sigma_m, sigma_i, pars){
+
+int_f <- function(f, x, q, sigma_m, sigma_i, pars){
   g <- function(X) f(X[1], X[2], pars)
-  lower <- c(max(x-sigma_m,0), max(q-sigma_i,0))
-  upper <- c(x+sigma_m, q + sigma_i)
+  lower <- c(max(x - sigma_m, 0), max(q - sigma_i, 0))
+  upper <- c(x + sigma_m, q + sigma_i)
[…]

### 2012-09-12 inst/examples/figure3.Rmd
failed to get a agreement in mc and analytic method

@@
 }
-SDP_Mat <- SDP_uniform(f, pars, x_grid, h_grid, sigma_g=0.5, pdfn, sigma_m=.5, sigma_i=.5)
+SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g = 0.5, pdfn)
 det <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)

### 2012-09-12 inst/examples/figure3.sh

@@ -7,7 +7,7 @@
 ## Parallel for MPI
 ##$ -pe mpi 20 
 ## Parallel for openmp:
-#$ -pe threaded 16
+#$ -pe threaded 4
 ## Output file name
 #$ -o det_figure3.log
 

### 2012-09-12 inst/examples/debug_uniform.Rmd
Fixed normalization of uniform integrals

@@
-`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="debug/", verbose=TRUE or`
+`ro cache=FALSE, warning=FALSE, comment=NA, message=FALSE, cache.path="debug/", verbose=TRUE or`
 
@@
 ```{r }
-int_f <- function(f, x, q, sigma_m, sigma_i, pars){
-  g <- function(X) f(X[1], X[2], pars)
-  lower <- c(max(x - sigma_m, 0), max(q - sigma_i, 0))
-  upper <- c(x + sigma_m, q + sigma_i)
-  out <- adaptIntegrate(g, lower, upper)
-  out$integral
-}
-
-F <- function(x,q, m, n, pars){
-  K <- pars[2]
-  out <- ((q+n-max(0,q-n))*(x+m-max(0,x-m))*(6*x*K-6*q*K-6*n*K+6*m*K+6*max(0,x-m)*K-6*
-    max(0,q-n)*K-2*x^2+3*q*x+3*n*x-4*m*x-2*max(0,x-m)*x+3*max(0,q-n)*x-2*q^2-4*n*q+3*m*q+3*
-    max(0,x-m)*q-2*max(0,q-n)*q-2*n^2+3*m*n+3*max(0,x-m)*n-2*max(0,q-n)*n-2*m^2-2*max(0,x-m)*m+3*
-    max(0,q-n)*m-2*max(0,x-m)^2+3*max(0,q-n)*max(0,x-m)-2*max(0,q-n)^2))/(6*K)
-  max(out,0)
-}
-```
-
-```{r }
 require(cubature)
@@
 
-```{r}
+```{r eval=FALSE, include=FALSE}
   z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
@@
 require(reshape2)
-policy <- melt(data.frame(stock = x_grid, deterministic=det$D[,1], uniform = uniform$D[,1], mc=opt$D[,1]), 
-               id = "stock")
+#policy <- melt(data.frame(stock = x_grid, deterministic=det$D[,1], uniform = uniform$D[,1], mc=opt$D[,1]), id = "stock")
+policy <- melt(data.frame(stock = x_grid, deterministic=det$D[,1], uniform = uniform$D[,1]), id = "stock")
 
-ggplot(policy) + geom_point(aes(stock, stock-x_grid[value], color=variable), shape="+")
+ggplot(policy) + geom_jitter(aes(stock, stock-x_grid[value], color=variable), shape="+")
 dat <- subset(policy, stock < 140)

### 2012-09-12 inst/examples/figure3.Rmd
minor edits
Fixed normalization of uniform integrals

@@
 
-We will use the analytic solution
-
-```{r}
-F <- function(x,q, m, n, pars){
-  K <- pars[2]
-  out <- ((q+n-max(0,q-n))*(x+m-max(0,x-m))*(6*x*K-6*q*K-6*n*K+6*m*K+6*max(0,x-m)*K-6*
-    max(0,q-n)*K-2*x^2+3*q*x+3*n*x-4*m*x-2*max(0,x-m)*x+3*max(0,q-n)*x-2*q^2-4*n*q+3*m*q+3*
-    max(0,x-m)*q-2*max(0,q-n)*q-2*n^2+3*m*n+3*max(0,x-m)*n-2*max(0,q-n)*n-2*m^2-2*max(0,x-m)*m+3*
-    max(0,q-n)*m-2*max(0,x-m)^2+3*max(0,q-n)*max(0,x-m)-2*max(0,q-n)^2))/(6*K)
-  max(out,0)
-}
-```
-
-We can verify our solution is the same as the numerical integral (which is slower to compute)
-
-```{r }
-int_f <- function(f, x, q, sigma_m, sigma_i, pars){
-  g <- function(X) f(X[1], X[2], pars)
-  lower <- c(max(x - sigma_m, 0), max(q - sigma_i, 0))
-  upper <- c(x + sigma_m, q + sigma_i)
-  out <- adaptIntegrate(g, lower, upper)
-  out$integral
-}
-```
-
 ```{r }

### 2012-09-12 R/SDP_uniform.R

@@ -50,22 +50,59 @@ SDP_uniform <- function(f, p, x_grid, h_grid, sigma_g,
 }
 
 
-
-
+#' Integrate against uniform distributions of measurement and implementation uncertainty
+#' 
+#' @export
 int_f <- function(f, x, q, sigma_m, sigma_i, pars){
-  g <- function(X) f(X[1], X[2], pars)
-  lower <- c(max(x - sigma_m, 0), max(q - sigma_i, 0))
-  upper <- c(x + sigma_m, q + sigma_i)
-  out <- adaptIntegrate(g, lower, upper)
-  out$integral
+  K <- pars[2]
+  sigma_m <- K*sigma_m
+  sigma_i <- K*sigma_i # scale noise into units of K
+  
+  if(sigma_m > 0 && sigma_i > 0){
+    g <- function(X) f(X[1], X[2], pars)
+    lower <- c(max(x - sigma_m, 0), max(q - sigma_i, 0))
+    upper <- c(x + sigma_m, q + sigma_i)
+    A <- adaptIntegrate(g, lower, upper)
+    out <- A$integral/(2 * sigma_m*  2 * sigma_i)
+  } else if(sigma_m == 0){ 
+    g <- function(h) f(x, h, pars)
+    lower <- max(q - sigma_i, 0)
+    upper <- q + sigma_i
+    A <- adaptIntegrate(g, lower, upper)
+    out <- A$integral/(2 * sigma_i)
+  } else if(sigma_i == 0){ 
+    g <- function(y) f(y, q, pars)
+    lower <- max(x - sigma_m, 0)
+    upper <- x + sigma_m
+    A <- adaptIntegrate(g, lower, upper)
+    out <- A$integral/(2 * sigma_m)
+  } else {
+    stop("distribution widths cannot be negative")
+  }
+  out
 }
 
-
+#' Analytic solution to int_f for logistic model
+#' @export
 F <- function(x,q, m, n, pars){
   K <- pars[2]
+  m <- K*m
+  n <- K*n # scale noise by K
[…]

### 2012-09-14 inst/examples/debug_uniform.Rmd
debug unifrom from strata

@@
 
-``` {r  echo=FALSE, cache=FALSE }
-#opts_knit$set(upload.fun = socialR::flickr.url)
-#options(device = function(width = 5, height = 5) {
-#    pdf(NULL, width = width, height = height)
-#})
-````
-
-## Generate Figure 3 of Sethi et al. 2006
-
 ``` {r  setup, echo=FALSE, cache=FALSE}
-# load required libraries
 require(pdgControl)
@@
 theme_publish <- theme_set(theme_bw(14))
-theme_publish <- 
-  theme_update(legend.key = theme_blank(),legend.position=c(.9,.1),
+theme_publish <- theme_update(legend.key = theme_blank(),legend.position=c(.9,.1),
         panel.grid.major=theme_blank(),panel.grid.minor=theme_blank(),
         plot.background=theme_blank(), legend.title=theme_blank())
-
 ````
 
-Chose the state equation / population dynamics function
+``` {r  echo=FALSE, cache=FALSE }
+opts_knit$set(upload.fun = socialR::flickr.url)
+#options(device = function(width = 5, height = 5) {
+#    pdf(NULL, width = width, height = height)
+#})
+````
+
+We consider adding additional sources of noise through observation error and implementation error to the orginal model of Reed (1979), which considers only growth error.
+This follows in the line of exploration taken by Clark and Kirkwood (1987), Roughgarden (1996) and Sethi (2006).
+
+In adding these two sources of error, our state variable becomes our *measured* (or believed) stock $x$, rather than the true stock size $y$, and our control variable becomes the quota $q$ set, rather than the realized harvest $h$.
+
+## Analytical integrals for Sethi (2006) calcuations
+
+The central calculation to accomodating additional sources of uncertainty is the determination of the transition matrix; the probability of going from state $x_t$ at time $t$ to state $x_{t+1}$ in the next interval, for each possible value of the control variable (quota).
+We discritize the statespace onto a fine grid of values $x$ and $h$ to seek a stochastic dynamic programming solution.
+
+``` {r }
+xmin <- 0
+xmax <- 150
+grid_n <- 100
+````
+
+We seek a harvest policy which maximizes the discounted profit from the fishery using a stochastic dynamic programming approach over a discrete grid of stock sizes from `r xmin` to `r xmax` on a grid of `r grid_n` points, and over an identical discrete grid of possible harvest values.
+
+``` {r  grid}
+x_grid <- seq(xmin, xmax, length = grid_n)  
+h_grid <- x_grid  
+````
+
+With purely growth noise, a row of the matrix is given by the probability density of the growth noise with mean $f(x,h)$, that is, the probability of tranistion from $x$ to $x_{t+1}$ at harvest $h$ is given by the function $P(x_t+1, f(x,h))$ for some probability density function $P$.
+In the case of uncertainty in stock $y$ and harvest $h$, we must integrate over the probability distributions for possible harvests and possible stock sizes,
+
+<div> $$ \int dh \int dy P(x_{t+1}, f(y, h))P(y)P(h) $$</div>
+
+In general this convolution can be non-trivial to compute, but in the case of uniformly distributed harvest error of $\pm \sigma_i$ around some quota $q$, and uniform measurement error of $\pm \sigma_m$ around the true stock size $x$, the integrals can be written as,
+
+<div> $$ \frac{1}{(q+\sigma_i) - \max(q-\sigma_i,0)} \frac{1}{(x+\sigma_m) - \max(x-\sigma_m,0)} \int_{\max(q-\sigma_i,0)}^{q+\sigma_i} dh \int_{\max(y-\sigma_h,0)}^{y+\sigma_h} dy P(x_{t+1}, f(y, h)) $$ </div>
+
+Note we enforce the simple non-negative boundary on stock and harvest.
+
+So now we are left to merely integrate the $f(y,h)$ over these finite intervals.
+We can do this for arbitrary $f$ through multidimensional numerical integration (In fact we could have done this in the first place, but it is too slow for the convolutions of arbitrary probability densities)
+
+```{r}
+int_f
+```
+
+If we assume a simple function like logistic growth, \\(f(s) = r s (1-s/K) + s \\), where \\(s = x - h\\),
 
@@
 
+Following Sethi et al, we can do this in closed form,
+
+```r
+F
+```
+
+We can compare timing and equivalence of these two expressions:
+
+```{r }
+require(cubature)
+# Confirm that these give the same value, and time performance
+system.time(a <- sapply(x_grid, function(x) int_f(f, x, 1, .1, .1, pars)))
+system.time(b <- sapply(x_grid, function(x) F(x, 1, .1, .1, pars)))
+ggplot(data.frame(x=x_grid,a=a,b=b)) + geom_line(aes(x,a), col="red") + geom_line(aes(x,b), lty=2)
+```
+
+Note that as the uncertainy gets small, we recover the original transition probability $f$:
+
+```{r }
+F(50, 4, .1, .1, pars)
+F(50, 4, .0001, .0001, pars)
+f(50,4,pars)
+```
+
+When the noise width is much smaller than the bin width we may have trouble, particularly with the uniform distribution, since part of the bin corresponds to zero density, part to high density.
+
+## Numerical implementation
+
 We consider a profits from fishing to be a function of harvest `h` and stock size `x`,  \\( \Pi(x,h) = h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x} \\), conditioned on \\( h > x \\) and \\(x > 0 \\),
@@
 
-``` {r }
-xmin <- 0
-xmax <- 1.5 * K
-grid_n <- 100
-````
-
-We seek a harvest policy which maximizes the discounted profit from the fishery using a stochastic dynamic programming approach over a discrete grid of stock sizes from `r xmin` to `r xmax` on a grid of `r grid_n` points, and over an identical discrete grid of possible harvest values.
-
-``` {r  grid}
-x_grid <- seq(xmin, xmax, length = grid_n)  
-h_grid <- x_grid  
-````
+Additional parameters
 
@@
 OptTime <- 25
-sigma_g <- .5
+sigma_g <- .1
 sigma_m <- .5
@@
 ````
+
+The uniform distribution must be careful for noise sizes smaller than binwidth
+
+```{r }
+pdfn <- function(P, s) dunif(P, 1 - s, 1 + s)
+#pdfn <- function(P, s) dlnorm(P, 0, s)
+```
 
@@
 ```{r }
-require(cubature)
-# Confirm that these give the same value, and time performance
-system.time(a <- sapply(x_grid, function(x) int_f(f, x, 1, .1, .1, pars)))
-system.time(b <- sapply(x_grid, function(x) F(x, 1, .1, .1, pars)))
-```
-
-```{r }
-sdp <- SDP_uniform(f, pars, x_grid, h_grid, sigma_g=sigma_g, pdfn=function(P, s) dunif(P, 1-s, 1+s), sigma_m=sigma_m, sigma_i=sigma_i, F)
+sdp <- SDP_uniform(f, pars, x_grid, h_grid, sigma_g=sigma_g, pdfn, sigma_m=sigma_m, sigma_i=sigma_i, F)
 ```
@@
 ```{r deterministic}
-pdfn <- function(P, s){
-     dunif(P, 1 - s, 1 + s)
-     }
+
 SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g = sigma_g, pdfn)

### 2012-10-01 inst/examples/multiple_uncertainty.Rmd
attempting multiple uncertainties using matrix approach -- Example on growth-noise alone

--- 2012-09-14 inst/examples/debug_uniform.Rmd
@@
 ``` {r  echo=FALSE, cache=FALSE }
-opts_knit$set(upload.fun = socialR::flickr.url)
-#options(device = function(width = 5, height = 5) {
-#    pdf(NULL, width = width, height = height)
-#})
+#opts_knit$set(upload.fun = socialR::flickr.url)
+#options(device = function(width = 5, height = 5) 
+#                   pdf(NULL, width = width, height = height))
 ````
@@
 xmax <- 150
-grid_n <- 100
+grid_n <- 20
 ````
@@
 With purely growth noise, a row of the matrix is given by the probability density of the growth noise with mean $f(x,h)$, that is, the probability of tranistion from $x$ to $x_{t+1}$ at harvest $h$ is given by the function $P(x_t+1, f(x,h))$ for some probability density function $P$.
-In the case of uncertainty in stock $y$ and harvest $h$, we must integrate over the probability distributions for possible harvests and possible stock sizes,
 
-<div> $$ \int dh \int dy P(x_{t+1}, f(y, h))P(y)P(h) $$</div>
-
-In general this convolution can be non-trivial to compute, but in the case of uniformly distributed harvest error of $\pm \sigma_i$ around some quota $q$, and uniform measurement error of $\pm \sigma_m$ around the true stock size $x$, the integrals can be written as,
-
-<div> $$ \frac{1}{(q+\sigma_i) - \max(q-\sigma_i,0)} \frac{1}{(x+\sigma_m) - \max(x-\sigma_m,0)} \int_{\max(q-\sigma_i,0)}^{q+\sigma_i} dh \int_{\max(y-\sigma_h,0)}^{y+\sigma_h} dy P(x_{t+1}, f(y, h)) $$ </div>
-
-Note we enforce the simple non-negative boundary on stock and harvest.
-
-So now we are left to merely integrate the $f(y,h)$ over these finite intervals.
-We can do this for arbitrary $f$ through multidimensional numerical integration (In fact we could have done this in the first place, but it is too slow for the convolutions of arbitrary probability densities)
-
-```{r}
-int_f
-```
-
-If we assume a simple function like logistic growth, \\(f(s) = r s (1-s/K) + s \\), where \\(s = x - h\\),
+We assume a simple function like logistic growth, \\(f(s) = r s (1-s/K) + s \\), where \\(s = x - h\\),
 
@@
 
-Following Sethi et al, we can do this in closed form,
-
-```r
-F
-```
-
-We can compare timing and equivalence of these two expressions:
-
-```{r }
-require(cubature)
-# Confirm that these give the same value, and time performance
-system.time(a <- sapply(x_grid, function(x) int_f(f, x, 1, .1, .1, pars)))
-system.time(b <- sapply(x_grid, function(x) F(x, 1, .1, .1, pars)))
-ggplot(data.frame(x=x_grid,a=a,b=b)) + geom_line(aes(x,a), col="red") + geom_line(aes(x,b), lty=2)
-```
-
-Note that as the uncertainy gets small, we recover the original transition probability $f$:
-
-```{r }
-F(50, 4, .1, .1, pars)
-F(50, 4, .0001, .0001, pars)
-f(50,4,pars)
-```
-
-When the noise width is much smaller than the bin width we may have trouble, particularly with the uniform distribution, since part of the bin corresponds to zero density, part to high density.
-
 ## Numerical implementation
 
-We consider a profits from fishing to be a function of harvest `h` and stock size `x`,  \\( \Pi(x,h) = h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x} \\), conditioned on \\( h > x \\) and \\(x > 0 \\),
+We consider a profits from fishing to be a function of harvest `h` and stock size `x`,  $\Pi(x,h) = h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x}$, conditioned on $h > x$ and $x > 0$
 
@@
 sigma_g <- .1
-sigma_m <- .5
-sigma_i <- .5
+sigma_m <- 0
+sigma_i <- 0
 ````
@@
 ```{r }
-pdfn <- function(P, s) dunif(P, 1 - s, 1 + s)
-#pdfn <- function(P, s) dlnorm(P, 0, s)
+pdfn=function(P, mu, s){
+                          if(mu==0)
+                            if(P == 0)
+                              1
+                            else 
+                              0
+                          else 
+                          dunif(P,mu*(1-s),mu*(1+s))
+}
+
+ln <- function(P, mu, s) dlnorm(P, log(mu), s)
 ```
@@
 ```{r }
-sdp <- SDP_uniform(f, pars, x_grid, h_grid, sigma_g=sigma_g, pdfn, sigma_m=sigma_m, sigma_i=sigma_i, F)
+sdp <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, sigma_g, pdfn, sigma_m, sigma_i)
 ```
@@
 ```{r }
-uniform <- find_dp_optim(sdp, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
+mult <- find_dp_optim(sdp, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
 ```
 
-Do the deterministic exactly,
+Compare to the former method:
 
 ```{r deterministic}
-
-SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g = sigma_g, pdfn)
+pdfn_old <- function(P,s) dunif(P, 1-s, 1+s)
+SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g = sigma_g, pdfn_old)
 det <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
 ````
-
-Determine the policies for each of the scenarios (noise combinations).
-
-```{r eval=FALSE, include=FALSE}
-  z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
-  z_m <- function() 1+(2*runif(1, 0,  1)-1) * sigma_m
-  z_i <- function() 1+(2*runif(1, 0,  1)-1) * sigma_i
-
-  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=2e4)
-  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
-                       profit, delta, reward=0)
-```
 
@@
 require(reshape2)
-#policy <- melt(data.frame(stock = x_grid, deterministic=det$D[,1], uniform = uniform$D[,1], mc=opt$D[,1]), id = "stock")
-policy <- melt(data.frame(stock = x_grid, deterministic=det$D[,1], uniform = uniform$D[,1]), id = "stock")
 
-ggplot(policy) + geom_jitter(aes(stock, stock-x_grid[value], color=variable), shape="+")
-dat <- subset(policy, stock < 140)
+policy <- melt(data.frame(stock = x_grid, deterministic=det$D[,1], new = mult$D[,1]), id = "stock")
+ggplot(subset(policy, stock < 120)) + geom_jitter(aes(stock, stock-x_grid[value], color=variable), shape="+")
+
+dat <- subset(policy, stock < 120)
 dt <- data.table(dat)
-linear <- dt[,approx(stock, stock-x_grid[value], xout=seq(1,150, length=15)), by=variable]
+linear <- dt[,approx(stock, stock-x_grid[value], xout=seq(1,120, length=15)), by=variable]
 ggplot(linear) + 

### 2012-10-01 R/SDP_multiple_uncertainty.R
small multiple uncertainty: working example! Uses matrix approach in R/SDP_multiple_uncertainty.R

@@ -24,7 +24,7 @@ SDP_multiple_uncertainty <- function(f, p, x_grid, h_grid, sigma_g,
                           else 
                           dunif(P,mu*(1-s),mu*(1+s))
                           },
-                        sigma_m, sigma_i){
+                        sigma_m, sigma_i, debug=FALSE){
   
     gridsize <- length(x_grid)
     
@@ -55,18 +55,19 @@ SDP_multiple_uncertainty <- function(f, p, x_grid, h_grid, sigma_g,
                        MoreArgs = list(sigma=sigma_i, g=function(x) max(x-h, 0), pdfn=pdfn)), nrow = gridsize)
     for(i in 1:gridsize)
       I[i,] = I[i,]/sum(I[i,])
-    out <- F %*% M %*% I
+    out <- I %*% M %*% F
     for(i in 1:gridsize)
       out[i,] = out[i,]/sum(out[i,])
     
     
     ## Debug Testing!
+    if(debug){
     F <- matrix(mapply(transition, m_grid$x, m_grid$y, 
                        MoreArgs = list(sigma=sigma_g, g=function(x) f(x,h,p), pdfn=pdfn)), nrow = gridsize)
     for(i in 1:gridsize) # normalize
       F[i,] = F[i,]/sum(F[i,])
     out <- F 
-    
+    }
     
     out
   })

### 2012-10-02 inst/examples/Reed.Rmd

@@
 xmin <- 0
-xmax <- K
+xmax <- K*1.5
 grid_n <- 200
@@
 OptTime <- 25
-sigma_g <- .2
+sigma_g <- .1
 ````
@@
 ``` {r noise}
-#z_g <- function() 1 + rlnorm(1,0, sigma_g)  
-z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
-````
+z_g <- function() 1 + rlnorm(1,0, sigma_g)  
+pdfn <- function(P, s) dlnorm(P, 0, s)
 
-No other sources of noise enter into the dynamics.
-
-``` {r othernoise}
-z_m <- function() 1
-z_i <- function() 1
+#z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
+#pdfn <- function(P, s)  dunif(P, 1 - s, 1 + s)
 ````
@@
 ``` {r  SDP_Mat}
-pdfn <- function(P, s){
-   dunif(P, 1 - s, 1 + s)
-}
 SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
@@
 
+No other sources of noise enter into the dynamics.
+
+``` {r othernoise}
+z_m <- function() 1
+z_i <- function() 1
+````
+
 ``` {r  simulate }

### 2012-10-02 inst/examples/multiple_uncertainty.Rmd
small multiple uncertainty: working example! Uses matrix approach in R/SDP_multiple_uncertainty.R

@@
-`ro cache=FALSE, warning=FALSE, comment=NA, message=FALSE, cache.path="debug/", verbose=TRUE or`
+`ro cache=FALSE, warning=FALSE, comment=NA, message=FALSE, cache.path="cache/multiple_uncertainty/", verbose=TRUE or`
 
@@
 theme_publish <- theme_set(theme_bw(14))
-theme_publish <- theme_update(legend.key = theme_blank(),legend.position=c(.9,.1),
-        panel.grid.major=theme_blank(),panel.grid.minor=theme_blank(),
-        plot.background=theme_blank(), legend.title=theme_blank())
+theme_publish <- theme_update(
+        # panel.grid.major=theme_blank(),panel.grid.minor=theme_blank(),
+        legend.title=theme_blank(), 
+        panel.background = theme_rect(fill = "transparent",colour = NA), 
+        plot.background = theme_rect(fill = "transparent",colour = NA))
 ````
@@
 xmax <- 150
-grid_n <- 20
+grid_n <- 150
 ````
@@
 OptTime <- 25
-sigma_g <- .1
-sigma_m <- 0
-sigma_i <- 0
+sigma_g <- 0.5
+sigma_m <- 0.5
+sigma_i <- 0.5
 ````
@@
 ```{r deterministic}
-pdfn_old <- function(P,s) dunif(P, 1-s, 1+s)
-SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g = sigma_g, pdfn_old)
-det <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
+det_mat <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, 0, pdfn, 0, 0)
+det <- find_dp_optim(det_mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
 ````

### 2012-10-04 inst/examples/multiple_uncertainty.Rmd
trying larger grid to remove edge effects
testing `SDP_multiple_uncertainty` function (3-matrices based approach)
Comparing source of noise (coarse grid)

@@
 ``` {r  echo=FALSE, cache=FALSE }
-#opts_knit$set(upload.fun = socialR::flickr.url)
+opts_knit$set(upload.fun = socialR::flickr.url)
 #options(device = function(width = 5, height = 5) 
@@
 xmin <- 0
-xmax <- 150
-grid_n <- 150
+xmax <- 200
+grid_n <- 40
 ````
@@
 OptTime <- 25
-sigma_g <- 0.5
-sigma_m <- 0.5
-sigma_i <- 0.5
 ````
@@
 ```{r }
-sdp <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, sigma_g, pdfn, sigma_m, sigma_i)
-```
-
-```{r }
-mult <- find_dp_optim(sdp, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
+sdp_g <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, .5, pdfn, 0, 0)
+sdp_m <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, 0, pdfn, .5, 0)
+sdp_i <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, 0, pdfn, 0, .5)
+opt_g <- find_dp_optim(sdp_g, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
+opt_m <- find_dp_optim(sdp_m, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
+opt_i <- find_dp_optim(sdp_i, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
 ```
@@
 require(reshape2)
+XMAX <- 140
+policy <- melt(data.frame(stock = x_grid, deterministic=det$D[,1], growth = opt_g$D[,1], meas = opt_m$D[,1], imp = opt_i$D[,1]), id = "stock")
+ggplot(subset(policy, stock < XMAX)) + geom_jitter(aes(stock, stock-x_grid[value], color=variable))
 
-policy <- melt(data.frame(stock = x_grid, deterministic=det$D[,1], new = mult$D[,1]), id = "stock")
-ggplot(subset(policy, stock < 120)) + geom_jitter(aes(stock, stock-x_grid[value], color=variable), shape="+")
-
-dat <- subset(policy, stock < 120)
+dat <- subset(policy, stock < XMAX)
 dt <- data.table(dat)
-linear <- dt[,approx(stock, stock-x_grid[value], xout=seq(1,120, length=15)), by=variable]
+linear <- dt[,approx(stock, stock-x_grid[value], xout=seq(1,XMAX, length=15)), by=variable]
 ggplot(linear) + 
 	stat_smooth(aes(x,y,color=variable), degree=1, se=FALSE, span=.3) + 
+	geom_jitter(aes(x,y, color=variable), shpae='+') +
   xlab("Measured Stock") + ylab("Optimal Expected Escapement")

### 2012-10-23 inst/doc/policycosts/policycosts.tex
added Jake's write-up to section 2.2

@@
 
+% From Jake:
+
+The fact that there is no uniform metric for comparing different functional forms of the penalty function complicates identifying the implications of various penalty functions on optimal management.
+Put another way, it is unclear what parameter values should be used for each functional form in order to compare the relative effect of each penalty function on optimal management.
+To address this issue, consider the following rule for comparing functional forms inspired by Bovenberg, Goulder and Gurnery (2005) and Bovenberg, Goulder and Jacobsen (2008).
+By definition, adding a constraint, in the form of a penalty function, to the social planner’s objective function will reduce the NPV of the resource in addition to affecting the optimal management policy.
+For example, each individual penalty function equation (3)-(6) is multiplied by a constant C2.
+As the magnitude of the penalty function increases (e.g., C2 increases), the NPV value of the resource decreases.
+Importantly, though, the rate at which the NPV is affected by a given increase in magnitude of the penalty function is different for different penalty functions.
+One way to compare the relative impact of penalty functions on optimal management is to choose parameters for the penalty function that imply the same level of NPV conditional on optimal management.
+
+Figure 2 shows this comparison criterion graphically.
+Each curve plots the percentage change in NPV relative to the unconstrained problem for a given penalty function over different magnitudes of that penalty function, C2, given optimal management.
+There are two important features in Figure 2.
+First, the optimal management policy is not constant across penalty function.
+This will be discussed in detail below.
+Second, the rate of change in NPV as a function of the magnitude of the penalty function varies both within and across policies.
+For example, the existence of a relatively small L2 penalty function dramatically affects the resource’s value initially but there is little marginal effect on NPV for relatively large L2 penalty functions.
+Conversely, the rate of change in NPV for the fixed penalty function is roughly constant over all ranges of penalty function magnitudes.
+
+To compare the impact of penalty functions on optimal management, we select penalty magnitudes that make the resource worth 80\% of its unconstrained value.
+The dashed vertical lines in Figure 2 map the needed penalty function magnitude, C2, to each penalty function such that the resource is worth 80\% of its unconstrained value when optimally managed.
+We choose 80\% somewhat arbitrarily but the method is applicable to any NPV level and the qualitative effects on management are robust for other levels.
+
+Bovenberg, AL, Goulder LH, and Gurney DJ (2005).  “Efficiency Costs of Meeting Industry-Distributional  Constraints Under Environmental Permits and Taxes” RAND Journal of Economics. 36(4): 951-  971.
+
+Bovenberg, AL, Goulder LH, and Jacobsen MR (2008).  “Costs of Alternative Policy Instruments in the    Presence of Industry Compensation Requirements” Journal of Public Economics. 92: 1236-1253.
+
+%% end-Jake
+
 We compare the impact of the different functional forms for the penalty

### 2012-10-23 inst/examples/multiple_uncertainty.Rmd
added Jake's write-up to section 2.2

@@
 
-We assume a simple function like logistic growth, \\(f(s) = r s (1-s/K) + s \\), where \\(s = x - h\\),
+We assume a simple function like logistic growth, $f(s) = r s (1-s/K) + s$, where $s = x - h$,
 
@@
 ggplot(subset(policy, stock < XMAX)) + geom_jitter(aes(stock, stock-x_grid[value], color=variable))
-
 dat <- subset(policy, stock < XMAX)

### 2012-10-23 R/SDP_multiple_uncertainty.R

@@ -53,8 +53,11 @@ SDP_multiple_uncertainty <- function(f, p, x_grid, h_grid, sigma_g,
     
   # Cycle over action space (harvest level)
   SDP_Mat <- lapply(h_grid, function(h){
+
+    ## I is incorrect, it isn't x-h that experiences the noise, but h 
     I <- matrix(mapply(transition, m_grid$x, m_grid$y, 
                        MoreArgs = list(sigma=sigma_i, g=function(x) max(x-h, 0), pdfn=pdfn)), nrow = gridsize)
+
     for(i in 1:gridsize)
       I[i,] = I[i,]/sum(I[i,])
     out <- I %*% M %*% F

### 2012-11-05 inst/examples/mult_uncertainty_test.Rmd
update

Test multiple uncertainty function

```{r  setup, echo=FALSE, cache=FALSE}
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
````

``` {r  echo=FALSE, cache=FALSE }
opts_knit$set(upload.fun = rfigshare::fs_embed)
````

## Current version of the multiple uncertainty function

```{r}
#' SDP under multiple uncertainty
#'
#' Computes the SDP solution under the case of growth noise, 
#' implementation errors in harvesting, and meaurement errors in 
#' the stock assessment.  
#'
#' @param f the growth function of the escapement population (x-h)
#'   should be a function of f(t, y, p), with parameters p
#' @param p the parameters of the growth function
#' @param x_grid the discrete values allowed for the population size, x
#' @param h_grid the discrete values of harvest levels to optimize over
#' @param sigma is the shape parameters for noise distribution (sigma_g, sigma_m, sigma_i) (default is no noise)
#' @param pdfn is the probability density function (same functional form is used for growth, measure, implement).  (Default is uniform)
#' @param profit is the profit function (defaults to the realized harvest)
#' @return The D matrix giving the optimal harvest for each possible state in each timestep.  
#' Hence the optimal policy at time t is given by the policy function D[,t].  
#' Values of D[,t] correspond to the index of h_grid.  Indices of of D[,t] correspond to states in y_grid.  
#' @export
SDP_multiple_uncertainty <- function(f, p, x_grid, h_grid, Tmax = 25,
                                     sigmas =c(sigma_g=0, sigma_m=0, sigma_i=0), 
                                     pdfn = pdfn, profit = function(x,h) pmin(x, h)){

    ## Initialize stuff
    sigma_g <- sigmas['sigma_g']      
    sigma_m <- sigmas['sigma_m']
    sigma_i <- sigmas['sigma_i']
    n_x <- length(x_grid)
    n_h <- length(h_grid)
    D <- matrix(NA, nrow=n_x, ncol=Tmax)

    ## Compute the transition matrices 
    P <-  outer(x_grid, h_grid, profit) 
    M <- rownorm( outer(x_grid, x_grid, pdfn, sigma_m) )
    I <- rownorm( outer(h_grid, h_grid, pdfn, sigma_i) )

    # integrate over uncertainty in I and X 
    F <- lapply(1:n_h, function(q){  
      t(sapply(1:n_x, function(y){
        out <- numeric(n_x)
        mu <- sum(sapply(1:n_x, function(x)
          f(x_grid[x],h_grid,p) %*% I[q,] *  M[x,y])) # Implementation & Measurement error
        if(mu==0)
          out[1] <- 1
        else 
          out <- dlnorm(x_grid/mu, 0, sigma_g)
        out/sum(out)
      }))
    })

    Ep <- M %*% P %*% I
    V <- Ep
    for(t in 1:Tmax){
      D[,(Tmax-t+1)] <- apply(V, 1, which.max)
      v_t <- apply(V, 1, max) # vector of current values
      V <- sapply(1:n_h, function(j){ # updated value matrix
        Ep[,j] + (1-delta) * M %*% F[[j]] %*% v_t
      })
    }
    list(D=D, M=M, I=I, P=P, Ep=Ep, V=V, F=F)
}

# row-normalize the probability distribution
rownorm <- function(M) t(apply(M, 1, function(x) x/sum(x)))
# binning routine (vectorized)
snap_to_grid <- function(x, grid) sapply(x, function(x) grid[which.min(abs(grid - x))])   
```

``` {r stateeq}
f <- function(x, h, p){
  A <- p[1] 
  B <- p[2] 
  s <- pmax(x-h, 0)
  A * s/(1 + B * s)
}
profit = function(x,h) pmin(x, h)

pars <- c(1.5, 0.05)
K <- (pars[1] - 1)/pars[2]
xmin <- 0
xmax <- 1.5 * K
n_x <- 20
n_h <- n_x
x_grid <- seq(xmin, xmax, length = n_x)  
h_grid <- seq(xmin, xmax, length = n_h)
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- 0.5
````

Old school way:

``` {r  SDP_Mat}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g)
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
````

New way:

```{r}
# Uniform pdf where width scales with mean (probably better way to do that)
# And handles degenerate/delta fn cases such as no width and zero mean
FUN <- function(P, mu, s){
  if(mu == 0){
    as.integer(P == 0)
  } else if(s > 0){
    if(mu > 0) dunif(P, mu * (1 - s), mu * (1 + s))
  }
  else { # delta spike
    P <- snap_to_grid(P, x_grid)
    mu <- snap_to_grid(mu, x_grid)
    as.integer(P == mu)
  }
}
pdfn <- Vectorize(FUN)
```

```{r mult_uncertainty}
new <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=sigma_g, sigma_m=0, sigma_i=0), pdfn=pdfn)  
m <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=sigma_g, sigma_m=0.1, sigma_i=0), pdfn=pdfn)
i <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=sigma_g, sigma_m=0, sigma_i=0.1), pdfn=pdfn)
```

Plot the policy function (in terms of escapement, `x-h`, rather than harvest `h`) at equilibrium (first time-step):

```{r policyfn_data}
require(reshape2)
policies <- melt(data.frame(stock=x_grid, old = x_grid[opt$D[,1]], new = x_grid[new$D[,1]], meas = x_grid[m$D[,1]], imp = x_grid[i$D[,1]]), id="stock")
```

```{r policyfunctions}
q1 <- ggplot(policies, aes(stock, stock - value, color=variable)) + geom_point() + xlab("stock size") + ylab("escapement") 
q1
```

```{r}
rbind(opt$D[,1], new$D[,1], m$D[,1], i$D[,1])
```

### 2012-11-09 inst/examples/mult_uncertainty_test.Rmd
updated with finer grid, still shows strange pattern

@@
 require(data.table)
-````
-
-``` {r  echo=FALSE, cache=FALSE }
-opts_knit$set(upload.fun = rfigshare::fs_embed)
 ````
@@
 xmax <- 1.5 * K
-n_x <- 20
+n_x <- 120
 n_h <- n_x

### 2012-11-17 inst/examples/mult_uncertainty_test.Rmd
successful example of implementation uncertainty

@@
 
-    ## Initialize stuff
+Tmax = 25
+sigmas =c (sigma_g=.3, sigma_m=0.3, sigma_i=0.3)
+
     sigma_g <- sigmas['sigma_g']      
@@
         mu <- sum(sapply(1:n_x, function(x)
-          f(x_grid[x],h_grid,p) %*% I[q,] *  M[x,y])) # Implementation & Measurement error
+          f(x_grid[x],h_grid,p) %*% I[q,] *  M[y,x])) # Implementation & Measurement error
         if(mu==0)
-          out[1] <- 1
+          out[1] <- 1 ## Wow, really? should we be applying noise to the f*I*M product or the f?  
         else 
@@
 
-    Ep <- M %*% P %*% I
+    Ep <- M %*% P %*% t(I)
     V <- Ep

### 2012-11-17 inst/examples/mult_uncertainty_test.Rmd
Comparison of each type of uncertainty (e.g. Figure 3)

@@
 
-Tmax = 25
-sigmas =c (sigma_g=.3, sigma_m=0.3, sigma_i=0.3)
-
     sigma_g <- sigmas['sigma_g']      
@@
         if(mu==0)
-          out[1] <- 1 ## Wow, really? should we be applying noise to the f*I*M product or the f?  
+          out[1] <- 1   
         else 
@@
 ```{r mult_uncertainty}
-new <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=sigma_g, sigma_m=0, sigma_i=0), pdfn=pdfn)  
-m <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=sigma_g, sigma_m=0.1, sigma_i=0), pdfn=pdfn)
-i <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=sigma_g, sigma_m=0, sigma_i=0.1), pdfn=pdfn)
+out <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.3, sigma_m=0.3, sigma_i=0.3), pdfn=pdfn)  
+```
+
+```{r noisetypes}
+new <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.3, sigma_m=0, sigma_i=0), pdfn=pdfn)  
+m <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.3, sigma_m=0.3, sigma_i=0), pdfn=pdfn)  
+i <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.3, sigma_m=0, sigma_i=0.3), pdfn=pdfn)  
 ```
@@
 ```
-
-```{r}
-rbind(opt$D[,1], new$D[,1], m$D[,1], i$D[,1])
-```

### 2012-11-22 inst/examples/mult_uncertainty_test.Rmd
numerical instabilities in uniform noise case?

@@
 ````
+
+```{r plotting, include=FALSE}
+theme_publish <- theme_set(theme_bw(14))
+theme_publish <- theme_update(
+        # panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
+        legend.title=element_blank(), 
+        panel.background = element_rect(fill = "transparent",colour = NA), 
+        plot.background = element_rect(fill = "transparent",colour = NA))
+```
 
@@
 SDP_multiple_uncertainty <- function(f, p, x_grid, h_grid, Tmax = 25,
-                                     sigmas =c(sigma_g=0, sigma_m=0, sigma_i=0), 
+                                     sigmas =c(sigma_g=0.3, sigma_m=0, sigma_i=0), 
                                      pdfn = pdfn, profit = function(x,h) pmin(x, h)){
@@
           out[1] <- 1   
-        else 
-          out <- dlnorm(x_grid/mu, 0, sigma_g)
+        else {
+         out <- pdfn(x_grid, mu, sigma_g)
+         if(sum(out) == 0)
+           out[1] = 1
+         out
+        }
         out/sum(out)
@@
 xmax <- 1.5 * K
-n_x <- 120
+n_x <- 200
 n_h <- n_x

### 2012-11-22 inst/examples/mult_uncertainty_test.Rmd
Whoops, not preventing negative harvest values can lead to some weird results.

@@
   } else if(s > 0){
-    if(mu > 0) dunif(P, mu * (1 - s), mu * (1 + s))
+    if(mu > 0){
+      dlnorm(P, mu, s)
+      #dunif(P, mu * (1 - s), mu * (1 + s))
+    }
   }

### 2012-11-22 inst/examples/mult_uncertainty_test.Rmd
A few small tweaks to probability calculations
Handle the case of mu = grid zero, not just exactly zero, to avoid introducing NAs

Calculate dlnorm as (x_grid/mu, 0, sigma), rather than as (x_grid, mu, sigma).

Transpose of measurement error in M %*% F.  Because now we want to treat x as given, integrate over range of y?  (no, probably not?)

standardize noise level between old and g

--- 2012-11-22 inst/examples/mult_uncertainty_test.Rmd
@@
 
-    sigma_g <- sigmas['sigma_g']      
-    sigma_m <- sigmas['sigma_m']
-    sigma_i <- sigmas['sigma_i']
+# sigmas = c(0.2, 0.2, .0)
+    sigma_g <- sigmas[1]      
+    sigma_m <- sigmas[2]
+    sigma_i <- sigmas[3]
     n_x <- length(x_grid)
@@
 
-    # integrate over uncertainty in I and X 
     F <- lapply(1:n_h, function(q){  
@@
           f(x_grid[x],h_grid,p) %*% I[q,] *  M[y,x])) # Implementation & Measurement error
-        if(mu==0)
+        # Handle special cases
+        if(snap_to_grid(mu,x_grid)==0){
           out[1] <- 1   
-        else {
+        } else {
          out <- pdfn(x_grid, mu, sigma_g)
-         if(sum(out) == 0)
-           out[1] = 1
-         out
         }
@@
 
+    # n_y by n_x, given y %*% n_x by n_h %*% n_h by n_q, given q
     Ep <- M %*% P %*% t(I)
@@
       D[,(Tmax-t+1)] <- apply(V, 1, which.max) 
+      ## q can often exceed y, if fishing is free, there might be more x than you think.  
+      #if(any(pmin(D[,(Tmax-t+1)], 1:n_h) !=  D[,(Tmax-t+1)])) stop()
+      #v_t <- sapply(1:n_h, function(i) V[i,D[i,(Tmax-t+1)]]) # Look-up value given by which.max
       v_t <- apply(V, 1, max) # vector of current values 
       V <- sapply(1:n_h, function(j){ # updated value matrix
-        Ep[,j] + (1-delta) * M %*% F[[j]] %*% v_t
+        Ep[,j] + (1-delta) * t(M) %*% F[[j]] %*% v_t
       })
@@
 profit = function(x,h) pmin(x, h)
+#profit <- profit_harvest(price=1, c0 = 0, c1=0)
 
@@
 xmax <- 1.5 * K
-n_x <- 200
+n_x <- 100
 n_h <- n_x
@@
 OptTime <- 25
-sigma_g <- 0.5
+
+sigma_g=0.1
 ````
@@
   } else if(s > 0){
-    if(mu > 0) dunif(P, mu * (1 - s), mu * (1 + s))
+    if(mu > 0){
+      dlnorm(P/mu, 0, s)
+      #dunif(P, mu * (1 - s), mu * (1 + s))
+    }
   }
@@
     mu <- snap_to_grid(mu, x_grid)
-    as.integer(P == mu)
+    as.numeric(as.integer(P == mu))
   }
@@
 
-```{r mult_uncertainty}
-out <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.3, sigma_m=0.3, sigma_i=0.3), pdfn=pdfn)  
-```
-
 ```{r noisetypes}
-new <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.3, sigma_m=0, sigma_i=0), pdfn=pdfn)  
-m <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.3, sigma_m=0.3, sigma_i=0), pdfn=pdfn)  
-i <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.3, sigma_m=0, sigma_i=0.3), pdfn=pdfn)  
+g <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=sigma_g, sigma_m=0, sigma_i=0), pdfn=pdfn)  
+m <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.03, sigma_m=0.1, sigma_i=0), pdfn=pdfn)  
+i <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.03, sigma_m=0, sigma_i=0.1), pdfn=pdfn)  
 ```
@@
 require(reshape2)
-policies <- melt(data.frame(stock=x_grid, old = x_grid[opt$D[,1]], new = x_grid[new$D[,1]], meas = x_grid[m$D[,1]], imp = x_grid[i$D[,1]]), id="stock")
+policies <- melt(data.frame(stock=x_grid, old = x_grid[opt$D[,1]], g = x_grid[g$D[,1]], meas = x_grid[m$D[,1]], imp = x_grid[i$D[,1]]), id="stock")
 ```

### 2012-11-22 inst/examples/mult_uncertainty_test.Rmd
Larger (log-normal in all variables) noise, weirder results.

@@
 ```{r plotting, include=FALSE}
-theme_publish <- theme_set(theme_bw(14))
-theme_publish <- theme_update(
-        # panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
-        legend.title=element_blank(), 
-        panel.background = element_rect(fill = "transparent",colour = NA), 
-        plot.background = element_rect(fill = "transparent",colour = NA))
+opts_knit$set(upload.fun = socialR::notebook.url)
+opts_chunk$set(dev.args=list(bg="transparent"))
 ```
@@
         # Handle special cases
-        if(snap_to_grid(mu,x_grid)==0){
+        if(snap_to_grid(mu,x_grid)==0){ # 
           out[1] <- 1   
@@
       V <- sapply(1:n_h, function(j){ # updated value matrix
-        Ep[,j] + (1-delta) * t(M) %*% F[[j]] %*% v_t
+        Ep[,j] + (1-delta) * M %*% F[[j]] %*% v_t
       })
@@
 
-sigma_g=0.1
+sigma_g=0.3
 ````
@@
 g <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=sigma_g, sigma_m=0, sigma_i=0), pdfn=pdfn)  
-m <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.03, sigma_m=0.1, sigma_i=0), pdfn=pdfn)  
-i <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.03, sigma_m=0, sigma_i=0.1), pdfn=pdfn)  
+m <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.03, sigma_m=0.3, sigma_i=0), pdfn=pdfn)  
+i <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.03, sigma_m=0, sigma_i=0.3), pdfn=pdfn)  
 ```

### 2012-11-22 inst/examples/mult_uncertainty_test.Rmd
Changes improving performance of F calculation (rate-limiting step)
1. vectorized calculation of mu.
2. matrix-based calc of deterministic part of growth rate

@@
 
+    # Much faster to fill out f calls as a matrix ahead of time.  
+    f_matrix <- outer(x_grid, h_grid, f, p)
+
     F <- lapply(1:n_h, function(q){  
@@
         out <- numeric(n_x)
-        mu <- sum(sapply(1:n_x, function(x)
-          f(x_grid[x],h_grid,p) %*% I[q,] *  M[y,x])) # Implementation & Measurement error
+        mu <- M[y,] %*% f_matrix %*% I[q,] 
         # Handle special cases
@@
         } else {
-         out <- pdfn(x_grid, mu, sigma_g)
+         # snap mu to grid first?  then do this by table look-up?
+         out <- pdfn(x_grid, mu, sigma_g)  ## All computational time spent here.  could be done by look-up?
         }
@@
 xmax <- 1.5 * K
-n_x <- 100
+n_x <- 200
 n_h <- n_x
@@
     if(mu > 0){
-      dlnorm(P/mu, 0, s)
-      #dunif(P, mu * (1 - s), mu * (1 + s))
+      #dlnorm(P/mu, 0, s)
+      dunif(P, mu * (1 - s), mu * (1 + s))
     }

### 2012-11-26 inst/examples/mult_uncertainty_test.Rmd
transparent plots

@@
 opts_chunk$set(dev.args=list(bg="transparent"))
+theme_update(plot.background = element_rect(fill = "transparent",colour = NA))
 ```
@@
     f_matrix <- outer(x_grid, h_grid, f, p)
+    # Fill out uncertainty in transitions first
+    G <- outer(x_grid, x_grid, pdfn, sigma_g)
 
@@
         } else {
-         # snap mu to grid first?  then do this by table look-up?
-         out <- pdfn(x_grid, mu, sigma_g)  ## All computational time spent here.  could be done by look-up?
+        #out <- pdfn(x_grid, mu, sigma_g)  ## All computational time spent here.  could be done by look-up:
+         mu_i <- which.min(abs(x_grid - mu)) ## snap mu to grid first
+         out <- G[,mu_i]   ## then do this by table look-up
+         ## Not identical but very close.  
         }
@@
       D[,(Tmax-t+1)] <- apply(V, 1, which.max) 
-      ## q can often exceed y, if fishing is free, there might be more x than you think.  
+      ## q can often exceed y: if fishing is free, there might be more x than you think.  
       #if(any(pmin(D[,(Tmax-t+1)], 1:n_h) !=  D[,(Tmax-t+1)])) stop()
@@
 xmax <- 1.5 * K
-n_x <- 200
+n_x <- 150
 n_h <- n_x
@@
 
-```{r noisetypes}
+```{r }
 g <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=sigma_g, sigma_m=0, sigma_i=0), pdfn=pdfn)
+```
+
+```{r}
 m <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.03, sigma_m=0.3, sigma_i=0), pdfn=pdfn)  
+```
+
+```{r}
 i <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.03, sigma_m=0, sigma_i=0.3), pdfn=pdfn)  

### 2012-11-27 inst/examples/policycosts/policycosts_writeup.Rmd
exploring graphical representations for policycosts

``` {r setupsource}
rm(list=ls())   
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
```

```{r}
opts_knit$set(upload.fun = socialR::notebook.url)
opts_chunk$set(dev.args=list(bg="transparent"))
theme_set(theme_bw())
theme_update(panel.background = element_rect(fill = "transparent",colour = NA),
             plot.background = element_rect(fill = "transparent",colour = NA))
```

```{r}
delta <- 0.05     # economic discounting rate
OptTime <- 50     # stopping time
gridsize <- 50   # gridsize (discretized population)
sigma_g <- 0.2    # Noise in population growth
reward <- 0       # bonus for satisfying the boundary condition
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1 # measurement noise, none, but part of simulation routine
z_i <- function() 1
f <- BevHolt                # Select the state equation
pars <- c(1.5, 0.05)             # parameters for the state equation
K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
xT <- 0                     # boundary conditions
x0 <- K
profit <- profit_harvest(price = 10, c0 = 30, c1 = 0)
x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
h_grid <- seq(0.01, 0.8 * K, length = gridsize)  
````

```{r}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                     profit, delta, reward=reward)
````

``` {r fees}
L1 <- function(c2) function(h, h_prev)  c2 * abs(h - h_prev) 
free_increase <- function(c2) function(h, h_prev)  c2 * abs(min(h - h_prev, 0)) # increasing harvest is free
free_decrease <- function(c2) function(h, h_prev)  c2 * max(h - h_prev, 0) # decreasing harvest is free
fixed <-  function(c2) function(h, h_prev) c2 * as.numeric( !(h == h_prev) )
L2 <- function(c2) function(h, h_prev)  c2 * (h - h_prev) ^ 2
````

Solve the policy cost for the specified penalty function

``` {r L2}
L2_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                    profit, delta, reward, penalty = L2(0.7586))
````

```{r fixed}
fixed_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
    profit, delta, reward, penalty = fixed(9.103))
```

``` {r L1}
L1_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward, penalty = L1(1.52))
````

```{r free_increase}
free_increase_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward, penalty =  free_increase(3.04))
````

```{r free_decrease}
free_decrease_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward, penalty = free_decrease(3.04))
````

``` {r simulate_policy}
sims <- list(
  L1 = simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L1_policy$D, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L1(1.52), seed=111), 
  L2 = simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L2_policy$D, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L2(0.7586), seed=111),
  fixed = simulate_optim(f, pars, x_grid, h_grid, x0, 
                         fixed_policy$D, z_g, z_m, z_i, 
                         opt$D, profit=profit, penalty=fixed(9.103), seed=111),
  increase = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            free_decrease_policy$D, z_g, z_m, z_i, 
                            opt$D, profit=profit, penalty= free_increase(1.52), seed=111),
  decrease = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            free_decrease_policy$D, z_g, z_m, z_i, 
                            opt$D, profit=profit, penalty= free_decrease(1.52), seed=111)
)
````

Make data tidy (melt), fast (data.tables), and nicely labeled.

``` {r tidy}
dat <- melt(sims, id=names(sims[[1]]))  
dt <- data.table(dat)
setnames(dt, "L1", "penalty_fn") # names are nice
````

# Plots

``` {r}
p0 <- ggplot(dt) +
  geom_line(aes(time, alternate), col="grey20", lwd=1) +
  geom_line(aes(time, fishstock, col=penalty_fn, lty=penalty_fn))+ 
  labs(x="time", y="stock size", title = "Stock Dynamics")
p0
```

```{r}
p1 <- ggplot(dt) +
  geom_line(aes(time, alternate), col="grey20", lwd=1) +
  geom_line(aes(time, fishstock), col=rgb(0,0,1,.8)) + facet_wrap(~penalty_fn) + 
  labs(x="time", y="stock size", title = "Stock Dynamics")
p1
```

```{r}
p2 <- ggplot(dt) +
  geom_line(aes(time, harvest_alt), col="grey20", lwd=1)  +
  geom_line(aes(time, harvest), col=rgb(0,0,1,.8)) + 
  facet_wrap(~penalty_fn) + 
  labs(x="time", y="havest intensity (fish taken)", title = "Harvest Policy Dynamics")
p2
````

### 2012-11-27 inst/examples/multiple_uncertainty.Rmd

--- 2012-10-04 inst/examples/multiple_uncertainty.Rmd
@@
 xmax <- 200
-grid_n <- 40
+grid_n <- 200
 ````
@@
 ```{r }
+sdp_low <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, .1, pdfn, 0, 0)
 sdp_g <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, .5, pdfn, 0, 0)
@@
 sdp_i <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, 0, pdfn, 0, .5)
+opt_low <- find_dp_optim(sdp_low, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
 opt_g <- find_dp_optim(sdp_g, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
@@
 XMAX <- 140
-policy <- melt(data.frame(stock = x_grid, deterministic=det$D[,1], growth = opt_g$D[,1], meas = opt_m$D[,1], imp = opt_i$D[,1]), id = "stock")
+policy <- melt(data.frame(stock = x_grid, det=det$D[,1], low_g = opt_low$D[,1], growth = opt_g$D[,1], meas = opt_m$D[,1], imp = opt_i$D[,1]), id = "stock")
 ggplot(subset(policy, stock < XMAX)) + geom_jitter(aes(stock, stock-x_grid[value], color=variable))
@@
 	stat_smooth(aes(x,y,color=variable), degree=1, se=FALSE, span=.3) + 
-	geom_jitter(aes(x,y, color=variable), shpae='+') +
+	geom_jitter(aes(x,y, color=variable), shape='+') +
   xlab("Measured Stock") + ylab("Optimal Expected Escapement")

### 2012-11-27 inst/doc/policycosts/policycosts.tex

@@
 \newcommand{\cdb}[1]{{\it \color{darkgreen} #1}}
+\newcommand{\pa}[1]{{\it \color{darkblue} #1}}
 
@@
 
+\pa{
+   
+  \textbf{Option 1.}
+
+  We don’t include do a section 3.3. I’m not convinced the paper needs one. Some of this I think is a tension between a focus in the paper on :
+
+  A.      ``What are the effects of including policy adjustment costs on optimal policy recommendations at all?''
+
+  Vs.
+
+  B.      ``Given that there will be costs to adjusting policies but we don’t know just what form these will take, what are the consequences of different cost formulations''
+
+  If we focus the paper on question B there is less need for a section 3.3 at least as Carl has that section currently entitled (``Consequences of ignoring policy adjustment costs'' – which is not really a statement about functional forms).
+
+  \textbf{Option 2.}
+
+  We include a version of the results Carl currently shows in his Fig 5 and 6 for the L1 penalty, but we include it also for the other penalty function forms – e.g.
+using Carl’s suggestion of a box-whisker plot.
+   
+  Reminder - The two figures compare the performance of the optimal policy when accounting for the policy adjustment costs (maximizing $\Pi_{L_1}$) with what the optimal policy recommendation one would arrive if ignoring these costs (maximizing $\Pi_0$) WHEN scoring the performance of the two control recommendations against $\Pi_{L_1}$.
+   
+  Fig.
+5 shows the breakdown into how the gross yield (ph) and adjustment cost ($c_2 abs(h_t-h_{t-1})$) separately.
+The policy ignoring costs of policy adjustment gets higher gross yields by tracking the variations more closely but also incurs (even) higher policy adjustment costs.
+Fig 6 combines the two bits to show the effect on net present value.
+   
+  This option would let one answer:
+
+  i)                    What is the consequence of ignoring policy adjustment costs when they are present?
+
+  ii)                   It also answers Jim’s suggested reversal of that question, I think, namely: what is the consequence of assuming adjustment costs are present when in fact they are absent?
+(I think this is just the difference between the gross yields / the turquoise and red shaded areas in Fig 5).
+
+  iii)                 And then how do these things vary for each of the different functional forms?
+
+  \textbf{Option 3}
+
+  We populate a table that organizes columns by the ``Actual functional form of adjustment costs'' and the rows into ``Assumed functional form of adjustment costs.'' The types of functional form in both columns and rows would then run ``None, $L_1$, $L_2$ etc.''
+   
+  IF we denote the optimal control for objective function $NPV_i$ as being $h^*_i$, then I would populate the Table with the proportions
+  $NPV_i(h^*_j) / NPV_i(h^*_i)$
+  (i.e. what proportion of the available NPV you still get if assuming the wrong functional form for the adjustment costs).
+   
+  The inclusion of the comparison against None means that all of what was being talked about for Option 2 would be captured.
+In addition it would provide a robustness check on a policy recommendation if uncertain of either the presence of policy adjustment costs or functional form that they should adopt.
+Specifically, by comparing across rows one could ascertain whether assuming one choice of functional form was likely to lead to large efficiency costs should other assumptions about adjustment costs prove correct.
+Similarly one could compare across columns to see if one form were particularly problematic in reality.
+   
+  I don’t know if those are clear – you need to get mired into the document once again a bit to parse it out. I’ll happily discuss with anyone in a bid to shed more light.
+   
+  Discussion of these options and alternative suggestions invited.
+}
+
 \begin{itemize}

### 2012-11-27 inst/examples/bad_outcome_good_policy.Rmd

--- 2012-06-21 inst/examples/criticaltransition.Rmd
@@
-`ro cache=FALSE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE or`
+`ro tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache=TRUE, cache.path="badoutcome/" or`
 
@@
 ``` {r  p0}
-p0 <- ggplot(subset(dt,reps==1)) +
+p0 <- ggplot(subset(dt,reps==3)) +
   geom_line(aes(time, fishstock)) +
-  geom_abline(intercept=opt$S, slope = 0) +
-  geom_line(aes(time, harvest), col="darkgreen") 
+  geom_line(aes(time, harvest), col="darkgreen") + ylab("Fish population/harvest (tons)") + theme_bw()
+
+df <- subset(dt, reps==30)
+df$harvest <- df$harvest * 0.5
+df <- melt(df, id="time")
+df <- subset(df, variable %in% c("fishstock", "harvest"))
+p0 <- ggplot(df) +  geom_line(aes(time, value, lty=variable)) +
+    ylab("Fish population/harvest (tons)") + theme_bw()
 p0

### 2012-11-27 inst/examples/mult_uncertainty_test.Rmd

@@
 opts_chunk$set(dev.args=list(bg="transparent"))
-theme_update(plot.background = element_rect(fill = "transparent",colour = NA))
 ```

### 2012-11-27 inst/examples/policycosts/L2.Rmd
minor changes, housekeeping

@@
 ``` {r setup, include=FALSE, cache=FALSE}
-opts_knit$set(upload.fun = socialR::flickr.url)
+opts_knit$set(upload.fun = socialR::notebook.url)
+opts_chunk$set(dev.args=list(bg="transparent"))
+theme_update(plot.background = element_rect(fill = "transparent",colour = NA))
 options(device = function(width=5, height=5) pdf(NULL, width = width, height = height))

### 2012-11-27 inst/examples/policycosts/exact_npv.Rmd

@@
 OptTime <- 50     # stopping time
-gridsize <- 100   # gridsize (discretized population)
+gridsize <- 50   # gridsize (discretized population)
 sigma_g <- 0.2    # Noise in population growth
@@
 z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
-z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
+z_m <- function() 1
+z_i <- function() 1
 ````
@@
 penaltyfns <- list(L2=L2, L1=L1, asy=asymmetric, fixed=fixed, asy2=free_increase)
-c2 <- seq(0, 22, length.out = 30)
+c2 <- seq(0, 10, length.out = 30)
 ````
@@
 require(snowfall)
-sfInit(cpu=16, parallel=T)
+sfInit(cpu=3, parallel=T)
 sfLibrary(pdgControl)

### 2012-11-27 inst/examples/policycosts/policycosts_writeup.Rmd

@@
-``` {r setupsource}
+`ro warning=FALSE, message=FALSE, comment=NA, cache=TRUE, cache.path="policycost-cache/" or`
+
+``` {r libraries, include=FALSE}
 rm(list=ls())   
@@
 
-```{r}
+```{r graphing-options, include=FALSE}
 opts_knit$set(upload.fun = socialR::notebook.url)
@@
 
-```{r}
+```{r setup}
+seed <- 123                 # Random seed (replicable results)
 delta <- 0.05               # economic discounting rate
-OptTime <- 50     # stopping time
-gridsize <- 50   # gridsize (discretized population)
+OptTime <- 100              # stopping time
+gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
 sigma_g <- 0.2              # Noise in population growth
@@
 z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() 1 # measurement noise, none, but part of simulation routine
-z_i <- function() 1
+z_m <- function() 1         # No measurement noise, 
+z_i <- function() 1         # No implemenation noise
 f <- BevHolt                # Select the state equation
@@
 x0 <- K
-profit <- profit_harvest(price = 10, c0 = 30, c1 = 0)
+profit <- profit_harvest(price = 10, c0 = 0, c1 = 0)
 x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
@@
 
-```{r}
+```{r reed, dependson="setup"}
 SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
@@
 L2 <- function(c2) function(h, h_prev)  c2 * (h - h_prev) ^ 2
+none <- function(h, h_prev)  0
+penaltyfns <- list(L2=L2, L1=L1, asy=asymmetric, fixed=fixed, asy2=free_increase)
+c2 <- seq(0, 10, length.out = 30)
 ````
+
+## Apples to Apples levels
+
+This can take a while, so we use explicit parallelization, 
+``` {r  parallel}
+require(snowfall)
+sfInit(cpu=8, parallel=T)
+sfLibrary(pdgControl)
+sfExportAll()
+````
+
+## Loop over penalty functions and magnitudes
+
+``` {r  bigloop, dependson=c("setup", "reed", "fees")}
+policies <- 
+sfSapply(penaltyfns, function(penalty){
+  policies <- 
+  sapply(c2, function(c2){
+      policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
+                        profit, delta, reward, penalty = penalty(c2))
+      i <- which(x_grid > K)[1]
+      max(policycost$penalty_free_V[i,]) 
+  })
+})
+````
+
+Note that `optim_policy` has been updated to return the equilibrium value of profits from fish harvests before the adjustment costs have been paid, `penalty_free_V`.
+This containst the values for all possible states, we simply evaluate it at the carrying capacity (which is our initial condition.)  The index in `x_grid` that corresponds to the carrying capacity (initial condition) `i` indicates this.
+
+Quadratic costs on fishing effort have to be done separately,
+
+``` {r  quadcosts, dependson="bigloop"}
+quad <- 
+  sapply(c2, function(c2){
+  effort_penalty = function(x,h) .1*c2*h/x
+  policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
+                        profit, delta, reward, penalty = fixed(0), 
+                        effort_penalty)
+      i <- which(x_grid > K)[1]
+      max(policycost$penalty_free_V[i,]) # chooses the most sensible harvest in t=1
+})
+dat <- cbind(policies, quad)
+````
+
+Tidy up the data and plot the net present value (before the penalty has been paid) relative to that achieved when managed without a penalty.
+
+``` {r npv-plot, dependson="quadcosts"}
+npv0 <- dat[1,3] 
+npv0
+dat <- data.frame(c2=c2,dat)
+dat <- melt(dat, id="c2")
+ggplot(dat, aes(c2, value, col=variable)) + geom_point() + geom_line()
+````
+
+Find the value of `c2` that brings each penalty closest to 75% of the cost-free adjustment value:
+
+```{r apples_plot, dependson="quadcosts"}
+ggplot(dat, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
+````
+
+```{r apples, dependson="quadcosts"}
+closest <- function(x, v){
+  which.min(abs(v-x))
+}
+dt <- data.table(dat)
+index <- dt[,closest(.25, (npv0-value)/value), by=variable]
+apples <- c2[index$V1]
+names(apples) = index$variable
+apples
+````
+
+## Results
 
@@
 
-``` {r L2}
+``` {r L2, dependson="apples"}
 L2_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
-                    profit, delta, reward, penalty = L2(0.7586))
+                    profit, delta, reward, penalty = L2(apples["L2"]))
 ````
 
-```{r fixed}
+```{r fixed, dependson="apples"}
 fixed_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
-    profit, delta, reward, penalty = fixed(9.103))
+    profit, delta, reward, penalty = fixed(apples["fixed"]))
 ```
 
-``` {r L1}
-L1_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward, penalty = L1(1.52))
+``` {r L1, dependson="apples"}
+L1_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward, penalty = L1(apples["L1"]))
 ````
 
-```{r free_increase}
-free_increase_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward, penalty =  free_increase(3.04))
+```{r free_increase, dependson="apples"}
+free_increase_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward, penalty =  free_increase(apples["free_increase"]))
 ````
 
-```{r free_decrease}
-free_decrease_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward, penalty = free_decrease(3.04))
+```{r free_decrease, dependson="apples"}
+free_decrease_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward, penalty = free_decrease(apples["free_decrease"]))
 ````
 
-``` {r simulate_policy}
+We also compare to the case in which costs of harvesting increase quadratically with effort; a common approach to create smoother policies.
+
+```{r quad_costs, dependson="apples"}
+quad_profit <- profit_harvest(price = 10, c0 = 30, c1 = apples["quad"]) 
+quad_costs <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, quad_profit, delta, reward, penalty =  none)
+```
+
+``` {r simulate_policy, dependson=c(-1,-2,-3,-4,-5,-6)}
 sims <- list(
@@
                       L1_policy$D, z_g, z_m, z_i, 
-                      opt$D, profit=profit, penalty=L1(1.52), seed=111), 
+                      opt$D, profit=profit, penalty=L1(apples["L1"]), seed=seed), 
   L2 = simulate_optim(f, pars, x_grid, h_grid, x0, 
                       L2_policy$D, z_g, z_m, z_i, 
-                      opt$D, profit=profit, penalty=L2(0.7586), seed=111),
+                      opt$D, profit=profit, penalty=L2(apples["L2"]), seed=seed),
   fixed = simulate_optim(f, pars, x_grid, h_grid, x0, 
                          fixed_policy$D, z_g, z_m, z_i, 
-                         opt$D, profit=profit, penalty=fixed(9.103), seed=111),
+                         opt$D, profit=profit, penalty=fixed(apples["fixed"]), seed=seed),
   increase = simulate_optim(f, pars, x_grid, h_grid, x0, 
-                            free_decrease_policy$D, z_g, z_m, z_i, 
-                            opt$D, profit=profit, penalty= free_increase(1.52), seed=111),
+                            free_increase_policy$D, z_g, z_m, z_i, 
+                            opt$D, profit=profit, penalty= free_increase(apples["increase"]), seed=seed),
   decrease = simulate_optim(f, pars, x_grid, h_grid, x0, 
                             free_decrease_policy$D, z_g, z_m, z_i, 
-                            opt$D, profit=profit, penalty= free_decrease(1.52), seed=111)
+                            opt$D, profit=profit, penalty= free_decrease(apples["decrease"]), seed=seed),
+  quad = simulate_optim(f, pars, x_grid, h_grid, x0, 
+                            free_decrease_policy$D, z_g, z_m, z_i, 
+                            opt$D, profit=quad_profit, penalty= none, seed=seed)
 )
@@
 
-Make data tidy (melt), fast (data.tables), and nicely labeled.
-
-``` {r tidy}
+``` {r tidy, dependson="simulate_policy"}
+#Make data tidy (melt), fast (data.tables), and nicely labeled.
 dat <- melt(sims, id=names(sims[[1]]))  
@@
 
-``` {r}
+``` {r p0, dependson="tidy"}
 p0 <- ggplot(dt) +
@@
 
-```{r}
+```{r p1, dependson="tidy"}
 p1 <- ggplot(dt) +
@@
 
-```{r}
+```{r p2, dependson="tidy"}
 p2 <- ggplot(dt) +

### 2012-11-28 inst/examples/policycosts/policycosts_writeup.Rmd
fixed dependson (negative indexing not supported on CRAN version of knitr?)

@@
 require(snowfall)
-sfInit(cpu=8, parallel=T)
+sfInit(cpu=2, parallel=T)
 sfLibrary(pdgControl)
@@
 
-``` {r simulate_policy, dependson=c(-1,-2,-3,-4,-5,-6)}
+``` {r simulate_policy, dependson=c("L1", "L2", "free_increase", "free_decrease", "fixed", "quad_costs")}
 sims <- list(

### 2012-11-28 inst/examples/policycosts/policycosts_writeup.Rmd
cpu settings for zero

@@
 require(snowfall)
-sfInit(cpu=2, parallel=T)
+sfInit(cpu=8, parallel=T)
 sfLibrary(pdgControl)

### 2012-11-28 inst/examples/policycosts/policycosts_writeup.Rmd
consistent names required for penalty fns!

@@
 none <- function(h, h_prev)  0
-penaltyfns <- list(L2=L2, L1=L1, asy=asymmetric, fixed=fixed, asy2=free_increase)
+penaltyfns <- list(L2=L2, L1=L1, free_decrease=free_decrease, fixed=fixed, free_increase=free_increase)
 c2 <- seq(0, 10, length.out = 30)

### 2012-11-29 inst/examples/policycosts/policycosts_writeup_c0_30.Rmd
Runs from zero

--- 2012-11-28 inst/examples/policycosts/policycosts_writeup.Rmd
@@
 ```{r graphing-options, include=FALSE}
-opts_knit$set(upload.fun = socialR::notebook.url)
+#opts_knit$set(upload.fun = socialR::notebook.url)
 opts_chunk$set(dev.args=list(bg="transparent"))
@@
 x0 <- K
-profit <- profit_harvest(price = 10, c0 = 0, c1 = 0)
+profit <- profit_harvest(price = 10, c0 = 30, c1 = 0)
 x_grid <- seq(0.01, 1.2 * K, length = gridsize)  

### 2012-11-29 inst/examples/policycosts/policycosts_writeup.Rmd
minor tweaks

@@
 ```{r graphing-options, include=FALSE}
-opts_knit$set(upload.fun = socialR::notebook.url)
+#opts_knit$set(upload.fun = socialR::notebook.url)
 opts_chunk$set(dev.args=list(bg="transparent"))
-theme_set(theme_bw())
 theme_update(panel.background = element_rect(fill = "transparent",colour = NA),
-             plot.background = element_rect(fill = "transparent",colour = NA))
+             panel.grid.major=element_line(colour="transparent"),
+             panel.grid.minor=element_line(colour="transparent")
+             )
 ```
@@
 require(snowfall)
-sfInit(cpu=8, parallel=T)
+sfInit(cpu=3, parallel=T)
 sfLibrary(pdgControl)
@@
 p0 <- ggplot(dt) +
-  geom_line(aes(time, alternate), col="grey20", lwd=1) +
-  geom_line(aes(time, fishstock, col=penalty_fn, lty=penalty_fn))+ 
+  geom_line(aes(time, harvest_alt), col="grey20", lwd=1) +
+  geom_line(aes(time, harvest, col=penalty_fn, lty=penalty_fn))+ 
   labs(x="time", y="stock size", title = "Stock Dynamics")
@@
 
-```{r p1, dependson="tidy"}
+```{r p1, dependson="tidy", fig.width=12}
 p1 <- ggplot(dt) +
@@
 
-```{r p2, dependson="tidy"}
+```{r p2, dependson="tidy", fig.width=12}
 p2 <- ggplot(dt) +

### 2012-11-29 inst/examples/policycosts/policycosts_writeup_c0_30.Rmd
minor tweaks

@@
 opts_chunk$set(dev.args=list(bg="transparent"))
-theme_set(theme_bw())
 theme_update(panel.background = element_rect(fill = "transparent",colour = NA),
-             plot.background = element_rect(fill = "transparent",colour = NA))
+             panel.grid.major=element_line(colour="transparent"),
+             panel.grid.minor=element_line(colour="transparent")
+             )
 ```

### 2012-11-30 inst/examples/policycosts/policycosts.Rmd
tidy up and rerun on zero

--- 2012-11-28 inst/examples/policycosts/policycosts_writeup.Rmd
@@
-`ro warning=FALSE, message=FALSE, comment=NA, cache=TRUE, cache.path="policycost-cache/" or`
-
 ``` {r libraries, include=FALSE}
-rm(list=ls())   
 require(pdgControl)
@@
 ```{r graphing-options, include=FALSE}
-opts_knit$set(upload.fun = socialR::notebook.url)
-opts_chunk$set(dev.args=list(bg="transparent"))
-theme_set(theme_bw())
-theme_update(panel.background = element_rect(fill = "transparent",colour = NA),
-             plot.background = element_rect(fill = "transparent",colour = NA))
+#opts_knit$set(upload.fun = socialR::notebook.url)
+opts_chunk$set(dev.args=list(bg="transparent"), tidy=FALSE, comment=NA, message=FALSE)
+theme_notebook <- theme_grey() + 
+                  theme(plot.background = element_rect(fill = "transparent",colour = NA),
+                        panel.grid.minor=element_line(colour="transparent"))
+theme_set(theme_notebook)
 ```
+
+``` {r  parallel}
+require(snowfall)
+sfInit(cpu=16, parallel=T)
+sfLibrary(pdgControl)
+sfExportAll()
+````
 
@@
 seed <- 123                 # Random seed (replicable results)
-delta <- 0.05               # economic discounting rate
+delta <- 0.01               # economic discounting rate
 OptTime <- 100              # stopping time
-gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
+gridsize <- 100              # grid size for fish stock and harvest rate (discretized population)
 sigma_g <- 0.2              # Noise in population growth
@@
 x0 <- K
-profit <- profit_harvest(price = 10, c0 = 0, c1 = 0)
 x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
@@
 penaltyfns <- list(L2=L2, L1=L1, free_decrease=free_decrease, fixed=fixed, free_increase=free_increase)
-c2 <- seq(0, 10, length.out = 30)
 ````
@@
 
-This can take a while, so we use explicit parallelization, 
-``` {r  parallel}
-require(snowfall)
-sfInit(cpu=8, parallel=T)
-sfLibrary(pdgControl)
-sfExportAll()
-````
-
-## Loop over penalty functions and magnitudes
+### Loop over penalty functions and magnitudes
 
@@
 p0 <- ggplot(dt) +
-  geom_line(aes(time, alternate), col="grey20", lwd=1) +
-  geom_line(aes(time, fishstock, col=penalty_fn, lty=penalty_fn))+ 
+  geom_line(aes(time, harvest_alt), col="grey20", lwd=1) +
+  geom_line(aes(time, harvest, col=penalty_fn, lty=penalty_fn))+ 
   labs(x="time", y="stock size", title = "Stock Dynamics")
-p0
 ```
 
-```{r p1, dependson="tidy"}
+```{r p1, dependson="tidy", fig.width=12}
 p1 <- ggplot(dt) +
@@
   labs(x="time", y="stock size", title = "Stock Dynamics")
-p1
 ```
 
-```{r p2, dependson="tidy"}
+```{r p2, dependson="tidy", fig.width=12}
 p2 <- ggplot(dt) +
@@
   labs(x="time", y="havest intensity (fish taken)", title = "Harvest Policy Dynamics")
-p2
 ````

### 2012-11-30 inst/examples/policycosts/policycosts_writeup.Rmd
tidy up and rerun on zero

--- 2012-11-28 inst/examples/policycosts/policycosts_writeup.Rmd
@@
-`ro warning=FALSE, message=FALSE, comment=NA, cache=TRUE, cache.path="policycost-cache/" or`
-
-``` {r libraries, include=FALSE}
-rm(list=ls())   
-require(pdgControl)
-require(reshape2)
-require(ggplot2)
-require(data.table)
+```{r cache-options, include=FALSE}
+opts_chunk$set(cache=TRUE, cache.path="policycosts-cache-c0-0/")
 ```
 
-```{r graphing-options, include=FALSE}
-opts_knit$set(upload.fun = socialR::notebook.url)
-opts_chunk$set(dev.args=list(bg="transparent"))
-theme_set(theme_bw())
-theme_update(panel.background = element_rect(fill = "transparent",colour = NA),
-             plot.background = element_rect(fill = "transparent",colour = NA))
+```{r}
+profit <- profit_harvest(price = 10, c0 = 0, c1 = 0)
+c2 <- seq(0, 20, length.out = 30)
 ```
 
-```{r setup}
-seed <- 123                 # Random seed (replicable results)
-delta <- 0.05               # economic discounting rate
-OptTime <- 100              # stopping time
-gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
-sigma_g <- 0.2              # Noise in population growth
-reward <- 0                 # bonus for satisfying the boundary condition
-z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() 1         # No measurement noise, 
-z_i <- function() 1         # No implemenation noise
-f <- BevHolt                # Select the state equation
-pars <- c(1.5, 0.05)        # parameters for the state equation
-K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
-xT <- 0                     # boundary conditions
-x0 <- K
-profit <- profit_harvest(price = 10, c0 = 0, c1 = 0)
-x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
-h_grid <- seq(0.01, 0.8 * K, length = gridsize)  
-````
+```{r run, results="hide"}
+knit("policycosts.Rmd", "policycosts_c0_0.md")
+```
 
-```{r reed, dependson="setup"}
-SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
-opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
-                     profit, delta, reward=reward)
-````
+## Results
 
-``` {r fees}
-L1 <- function(c2) function(h, h_prev)  c2 * abs(h - h_prev) 
-free_increase <- function(c2) function(h, h_prev)  c2 * abs(min(h - h_prev, 0)) # increasing harvest is free
-free_decrease <- function(c2) function(h, h_prev)  c2 * max(h - h_prev, 0) # decreasing harvest is free
-fixed <-  function(c2) function(h, h_prev) c2 * as.numeric( !(h == h_prev) )
-L2 <- function(c2) function(h, h_prev)  c2 * (h - h_prev) ^ 2
-none <- function(h, h_prev)  0
-penaltyfns <- list(L2=L2, L1=L1, asy=asymmetric, fixed=fixed, asy2=free_increase)
-c2 <- seq(0, 10, length.out = 30)
-````
-
-## Apples to Apples levels
-
-This can take a while, so we use explicit parallelization, 
-``` {r  parallel}
-require(snowfall)
-sfInit(cpu=8, parallel=T)
-sfLibrary(pdgControl)
-sfExportAll()
-````
-
-## Loop over penalty functions and magnitudes
-
-``` {r  bigloop, dependson=c("setup", "reed", "fees")}
-policies <- 
-sfSapply(penaltyfns, function(penalty){
-  policies <- 
-  sapply(c2, function(c2){
-      policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
-                        profit, delta, reward, penalty = penalty(c2))
-      i <- which(x_grid > K)[1]
-      max(policycost$penalty_free_V[i,]) 
-  })
-})
-````
-
-Note that `optim_policy` has been updated to return the equilibrium value of profits from fish harvests before the adjustment costs have been paid, `penalty_free_V`.
-This containst the values for all possible states, we simply evaluate it at the carrying capacity (which is our initial condition.)  The index in `x_grid` that corresponds to the carrying capacity (initial condition) `i` indicates this.
-
-Quadratic costs on fishing effort have to be done separately,
-
-``` {r  quadcosts, dependson="bigloop"}
-quad <- 
-  sapply(c2, function(c2){
-  effort_penalty = function(x,h) .1*c2*h/x
-  policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
-                        profit, delta, reward, penalty = fixed(0), 
-                        effort_penalty)
-      i <- which(x_grid > K)[1]
-      max(policycost$penalty_free_V[i,]) # chooses the most sensible harvest in t=1
-})
-dat <- cbind(policies, quad)
-````
-
-Tidy up the data and plot the net present value (before the penalty has been paid) relative to that achieved when managed without a penalty.
-
-``` {r npv-plot, dependson="quadcosts"}
-npv0 <- dat[1,3] 
-npv0
-dat <- data.frame(c2=c2,dat)
-dat <- melt(dat, id="c2")
-ggplot(dat, aes(c2, value, col=variable)) + geom_point() + geom_line()
-````
-
-Find the value of `c2` that brings each penalty closest to 75% of the cost-free adjustment value:
-
-```{r apples_plot, dependson="quadcosts"}
+```{r }
 ggplot(dat, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
@@
 
-```{r apples, dependson="quadcosts"}
-closest <- function(x, v){
-  which.min(abs(v-x))
-}
-dt <- data.table(dat)
-index <- dt[,closest(.25, (npv0-value)/value), by=variable]
-apples <- c2[index$V1]
-names(apples) = index$variable
-apples
-````
-
-## Results
-
-Solve the policy cost for the specified penalty function
-
-``` {r L2, dependson="apples"}
-L2_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
-                    profit, delta, reward, penalty = L2(apples["L2"]))
-````
-
-```{r fixed, dependson="apples"}
-fixed_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
-    profit, delta, reward, penalty = fixed(apples["fixed"]))
+```{r}
+as.table(apples)
 ```
 
-``` {r L1, dependson="apples"}
-L1_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward, penalty = L1(apples["L1"]))
-````
-
-```{r free_increase, dependson="apples"}
-free_increase_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward, penalty =  free_increase(apples["free_increase"]))
-````
-
-```{r free_decrease, dependson="apples"}
-free_decrease_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward, penalty = free_decrease(apples["free_decrease"]))
-````
-
-We also compare to the case in which costs of harvesting increase quadratically with effort; a common approach to create smoother policies.
-
-```{r quad_costs, dependson="apples"}
-quad_profit <- profit_harvest(price = 10, c0 = 30, c1 = apples["quad"]) 
-quad_costs <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, quad_profit, delta, reward, penalty =  none)
-```
-
-``` {r simulate_policy, dependson=c("L1", "L2", "free_increase", "free_decrease", "fixed", "quad_costs")}
-sims <- list(
-  L1 = simulate_optim(f, pars, x_grid, h_grid, x0, 
-                      L1_policy$D, z_g, z_m, z_i, 
-                      opt$D, profit=profit, penalty=L1(apples["L1"]), seed=seed), 
-  L2 = simulate_optim(f, pars, x_grid, h_grid, x0, 
-                      L2_policy$D, z_g, z_m, z_i, 
-                      opt$D, profit=profit, penalty=L2(apples["L2"]), seed=seed),
-  fixed = simulate_optim(f, pars, x_grid, h_grid, x0, 
-                         fixed_policy$D, z_g, z_m, z_i, 
-                         opt$D, profit=profit, penalty=fixed(apples["fixed"]), seed=seed),
-  increase = simulate_optim(f, pars, x_grid, h_grid, x0, 
-                            free_increase_policy$D, z_g, z_m, z_i, 
-                            opt$D, profit=profit, penalty= free_increase(apples["increase"]), seed=seed),
-  decrease = simulate_optim(f, pars, x_grid, h_grid, x0, 
-                            free_decrease_policy$D, z_g, z_m, z_i, 
-                            opt$D, profit=profit, penalty= free_decrease(apples["decrease"]), seed=seed),
-  quad = simulate_optim(f, pars, x_grid, h_grid, x0, 
-                            free_decrease_policy$D, z_g, z_m, z_i, 
-                            opt$D, profit=quad_profit, penalty= none, seed=seed)
-)
-````
-
-``` {r tidy, dependson="simulate_policy"}
-#Make data tidy (melt), fast (data.tables), and nicely labeled.
-dat <- melt(sims, id=names(sims[[1]]))  
-dt <- data.table(dat)
-setnames(dt, "L1", "penalty_fn") # names are nice
-````
-
-# Plots
-
-``` {r p0, dependson="tidy"}
-p0 <- ggplot(dt) +
-  geom_line(aes(time, alternate), col="grey20", lwd=1) +
-  geom_line(aes(time, fishstock, col=penalty_fn, lty=penalty_fn))+ 
-  labs(x="time", y="stock size", title = "Stock Dynamics")
+``` {r }
 p0
@@
 
-```{r p1, dependson="tidy"}
-p1 <- ggplot(dt) +
-  geom_line(aes(time, alternate), col="grey20", lwd=1) +
-  geom_line(aes(time, fishstock), col=rgb(0,0,1,.8)) + facet_wrap(~penalty_fn) + 
-  labs(x="time", y="stock size", title = "Stock Dynamics")
+```{r fig.width=12}
 p1 
+p2
 ```
-
-```{r p2, dependson="tidy"}
-p2 <- ggplot(dt) +
-  geom_line(aes(time, harvest_alt), col="grey20", lwd=1)  +
-  geom_line(aes(time, harvest), col=rgb(0,0,1,.8)) + 
-  facet_wrap(~penalty_fn) + 
-  labs(x="time", y="havest intensity (fish taken)", title = "Harvest Policy Dynamics")
-p2
-````

### 2012-12-03 inst/examples/policycosts/policycosts_writeup_c0_30.Rmd
run on zero

--- 2012-11-28 inst/examples/policycosts/policycosts_writeup.Rmd
@@
-`ro warning=FALSE, message=FALSE, comment=NA, cache=TRUE, cache.path="policycost-cache/" or`
-
-``` {r libraries, include=FALSE}
-rm(list=ls())   
-require(pdgControl)
-require(reshape2)
-require(ggplot2)
-require(data.table)
+```{r cache-options, include=FALSE}
+opts_chunk$set(cache=TRUE, cache.path="policycosts-cache-c0-30/")
 ```
 
-```{r graphing-options, include=FALSE}
-opts_knit$set(upload.fun = socialR::notebook.url)
-opts_chunk$set(dev.args=list(bg="transparent"))
-theme_set(theme_bw())
-theme_update(panel.background = element_rect(fill = "transparent",colour = NA),
-             plot.background = element_rect(fill = "transparent",colour = NA))
+```{r}
+profit <- profit_harvest(price = 10, c0 = 30, c1 = 0)
+c2 <- seq(0, 20, length.out = 40)
 ```
 
-```{r setup}
-seed <- 123                 # Random seed (replicable results)
-delta <- 0.05               # economic discounting rate
-OptTime <- 100              # stopping time
-gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
-sigma_g <- 0.2              # Noise in population growth
-reward <- 0                 # bonus for satisfying the boundary condition
-z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() 1         # No measurement noise, 
-z_i <- function() 1         # No implemenation noise
-f <- BevHolt                # Select the state equation
-pars <- c(1.5, 0.05)        # parameters for the state equation
-K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
-xT <- 0                     # boundary conditions
-x0 <- K
-profit <- profit_harvest(price = 10, c0 = 0, c1 = 0)
-x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
-h_grid <- seq(0.01, 0.8 * K, length = gridsize)  
-````
+```{r run, results="hide"}
+knit("policycosts.Rmd", "policycosts_c0_30.md")
+```
 
-```{r reed, dependson="setup"}
-SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
-opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
-                     profit, delta, reward=reward)
-````
+## Results
 
-``` {r fees}
-L1 <- function(c2) function(h, h_prev)  c2 * abs(h - h_prev) 
-free_increase <- function(c2) function(h, h_prev)  c2 * abs(min(h - h_prev, 0)) # increasing harvest is free
-free_decrease <- function(c2) function(h, h_prev)  c2 * max(h - h_prev, 0) # decreasing harvest is free
-fixed <-  function(c2) function(h, h_prev) c2 * as.numeric( !(h == h_prev) )
-L2 <- function(c2) function(h, h_prev)  c2 * (h - h_prev) ^ 2
-none <- function(h, h_prev)  0
-penaltyfns <- list(L2=L2, L1=L1, free_decrease=free_decrease, fixed=fixed, free_increase=free_increase)
-c2 <- seq(0, 10, length.out = 30)
-````
-
-## Apples to Apples levels
-
-This can take a while, so we use explicit parallelization, 
-``` {r  parallel}
-require(snowfall)
-sfInit(cpu=8, parallel=T)
-sfLibrary(pdgControl)
-sfExportAll()
-````
-
-## Loop over penalty functions and magnitudes
-
-``` {r  bigloop, dependson=c("setup", "reed", "fees")}
-policies <- 
-sfSapply(penaltyfns, function(penalty){
-  policies <- 
-  sapply(c2, function(c2){
-      policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
-                        profit, delta, reward, penalty = penalty(c2))
-      i <- which(x_grid > K)[1]
-      max(policycost$penalty_free_V[i,]) 
-  })
-})
-````
-
-Note that `optim_policy` has been updated to return the equilibrium value of profits from fish harvests before the adjustment costs have been paid, `penalty_free_V`.
-This containst the values for all possible states, we simply evaluate it at the carrying capacity (which is our initial condition.)  The index in `x_grid` that corresponds to the carrying capacity (initial condition) `i` indicates this.
-
-Quadratic costs on fishing effort have to be done separately,
-
-``` {r  quadcosts, dependson="bigloop"}
-quad <- 
-  sapply(c2, function(c2){
-  effort_penalty = function(x,h) .1*c2*h/x
-  policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
-                        profit, delta, reward, penalty = fixed(0), 
-                        effort_penalty)
-      i <- which(x_grid > K)[1]
-      max(policycost$penalty_free_V[i,]) # chooses the most sensible harvest in t=1
-})
-dat <- cbind(policies, quad)
-````
-
-Tidy up the data and plot the net present value (before the penalty has been paid) relative to that achieved when managed without a penalty.
-
-``` {r npv-plot, dependson="quadcosts"}
-npv0 <- dat[1,3] 
-npv0
-dat <- data.frame(c2=c2,dat)
-dat <- melt(dat, id="c2")
-ggplot(dat, aes(c2, value, col=variable)) + geom_point() + geom_line()
-````
-
-Find the value of `c2` that brings each penalty closest to 75% of the cost-free adjustment value:
-
-```{r apples_plot, dependson="quadcosts"}
+```{r }
 ggplot(dat, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()

### 2012-12-03 inst/examples/policycosts/quick_examples.Rmd
running code for policy costs: Figure 3 using fixed rather than algorithmic values for coefficients, taken to match http://www.carlboettiger.info/2012/11/27/polict-costs-work.html

--- 2012-11-30 inst/examples/policycosts/policycosts.Rmd
@@
 ```{r graphing-options, include=FALSE}
-#opts_knit$set(upload.fun = socialR::notebook.url)
+opts_knit$set(upload.fun = socialR::notebook.url)
 opts_chunk$set(dev.args=list(bg="transparent"), tidy=FALSE, comment=NA, message=FALSE)
@@
 
-``` {r  parallel}
-require(snowfall)
-sfInit(cpu=16, parallel=T)
-sfLibrary(pdgControl)
-sfExportAll()
-````
+``` {r}
+profit <- profit_harvest(price = 10, c0 = 30, c1 = 0)
+```
 
@@
 
-## Apples to Apples levels
-
-### Loop over penalty functions and magnitudes
-
-``` {r  bigloop, dependson=c("setup", "reed", "fees")}
-policies <- 
-sfSapply(penaltyfns, function(penalty){
-  policies <- 
-  sapply(c2, function(c2){
-      policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
-                        profit, delta, reward, penalty = penalty(c2))
-      i <- which(x_grid > K)[1]
-      max(policycost$penalty_free_V[i,]) 
-  })
-})
-````
-
-Note that `optim_policy` has been updated to return the equilibrium value of profits from fish harvests before the adjustment costs have been paid, `penalty_free_V`.
-This containst the values for all possible states, we simply evaluate it at the carrying capacity (which is our initial condition.)  The index in `x_grid` that corresponds to the carrying capacity (initial condition) `i` indicates this.
-
-Quadratic costs on fishing effort have to be done separately,
-
-``` {r  quadcosts, dependson="bigloop"}
-quad <- 
-  sapply(c2, function(c2){
-  effort_penalty = function(x,h) .1*c2*h/x
-  policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
-                        profit, delta, reward, penalty = fixed(0), 
-                        effort_penalty)
-      i <- which(x_grid > K)[1]
-      max(policycost$penalty_free_V[i,]) # chooses the most sensible harvest in t=1
-})
-dat <- cbind(policies, quad)
-````
-
-Tidy up the data and plot the net present value (before the penalty has been paid) relative to that achieved when managed without a penalty.
-
-``` {r npv-plot, dependson="quadcosts"}
-npv0 <- dat[1,3] 
-npv0
-dat <- data.frame(c2=c2,dat)
-dat <- melt(dat, id="c2")
-ggplot(dat, aes(c2, value, col=variable)) + geom_point() + geom_line()
-````
-
-Find the value of `c2` that brings each penalty closest to 75% of the cost-free adjustment value:
-
-```{r apples_plot, dependson="quadcosts"}
-ggplot(dat, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
-````
-
-```{r apples, dependson="quadcosts"}
-closest <- function(x, v){
-  which.min(abs(v-x))
-}
-dt <- data.table(dat)
-index <- dt[,closest(.25, (npv0-value)/value), by=variable]
-apples <- c2[index$V1]
-names(apples) = index$variable
-apples
+```{r apples}
+apples <- c(L2=1.034, L1=1.724, free_decrease=1.724, fixed=8.276, free_increase=1.724)
+xtable(apples)
 ````
@@
 
-# Plots
+## Plots
 
@@
   labs(x="time", y="stock size", title = "Stock Dynamics")
+p0
 ```
@@
   labs(x="time", y="stock size", title = "Stock Dynamics")
+p1
 ```
@@
   labs(x="time", y="havest intensity (fish taken)", title = "Harvest Policy Dynamics")
+p2
 ````

### 2012-12-03 inst/examples/policycosts/figure4.Rmd
figure4 run on farm

--- 2012-11-30 inst/examples/policycosts/policycosts.Rmd
@@
 
+```{r cache-options, include=FALSE}
+opts_chunk$set(cache=TRUE, cache.path="figure4/")
+```
+
+``` {r}
+profit <- profit_harvest(price = 10, c0 = 30, c1 = 0)
+c2 <- seq(0, 20, length.out = 40)
+```
+
 ```{r graphing-options, include=FALSE}
 #opts_knit$set(upload.fun = socialR::notebook.url)
-opts_chunk$set(dev.args=list(bg="transparent"), tidy=FALSE, comment=NA, message=FALSE)
+opts_chunk$set(dev.args=list(bg="transparent"),
+               tidy=FALSE, comment=NA, message=FALSE)
 theme_notebook <- theme_grey() + 
-                  theme(plot.background = element_rect(fill = "transparent",colour = NA),
-                        panel.grid.minor=element_line(colour="transparent"))
+                  theme(plot.background = 
+                          element_rect(fill = "transparent",colour = NA),
+                        panel.grid.minor = 
+                          element_line(colour = "transparent"))
 theme_set(theme_notebook)
@@
 ``` {r  bigloop, dependson=c("setup", "reed", "fees")}
-policies <- 
-sfSapply(penaltyfns, function(penalty){
-  policies <- 
-  sapply(c2, function(c2){
-      policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
+policies <- lapply(penaltyfns, function(penalty){
+  sfLapply(c2, function(c2)
+      optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                    profit, delta, reward, penalty = penalty(c2))
-      i <- which(x_grid > K)[1]
-      max(policycost$penalty_free_V[i,]) 
-  })
+  )
 })
@@
 quad <- 
-  sapply(c2, function(c2){
-  effort_penalty = function(x,h) .1*c2*h/x
+  sfLapply(c2, function(c2){
+  effort_penalty = function(x,h) c2 * h / x
   policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
-                        profit, delta, reward, penalty = fixed(0), 
+                        profit, delta, reward, penalty = none, 
                         effort_penalty)
-      i <- which(x_grid > K)[1]
-      max(policycost$penalty_free_V[i,]) # chooses the most sensible harvest in t=1
 })

### 2012-12-04 inst/examples/policycosts/policycosts.Rmd

@@
+This file is called by `policycosts_writeup.Rmd`.
+First it calibrates the apples-to-apples comparison level for each penalty function, and then generates sample plots by penalty function, illustrating the resulting stock dynamics and harvest quota dynamics.
+The file needs a `profit` function to be specified and the grid of `c2` values over which we search to find the coefficient introducing the 25% reduction in Net Present Value (npv).
+
 ``` {r libraries, include=FALSE}
@@
 policies <- 
-sfSapply(penaltyfns, function(penalty){
+sapply(penaltyfns, function(penalty){
   policies <- 
-  sapply(c2, function(c2){
+  sfSapply(c2, function(c2){
       policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
@@
   sapply(c2, function(c2){
-  effort_penalty = function(x,h) .1*c2*h/x
+  effort_penalty = function(x,h) .1 * c2 * h / x
   policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 

### 2012-12-04 inst/examples/policycosts/quick_examples.Rmd
caching for quick_examples, run on one
code for variance and autocorrelation, as per Fig 4

@@
 
+```{r cache-options, include=FALSE}
+opts_chunk$set(cache=TRUE, cache.path="quick_examples/")
+```
+
 ```{r graphing-options, include=FALSE}
@@
 theme_notebook <- theme_grey() + 
-                  theme(plot.background = element_rect(fill = "transparent",colour = NA),
-                        panel.grid.minor=element_line(colour="transparent"))
+                  theme(plot.background = 
+                          element_rect(fill = "transparent",colour = NA),
+                        panel.grid.minor = 
+                          element_line(colour = "transparent"))
 theme_set(theme_notebook)
@@
 
+Actually, we'll want to draw these from the table in figure4 data at different levels.  
+Ideally we can draw the policy out rather than running that again.
+
 ```{r apples}
 apples <- c(L2=1.034, L1=1.724, free_decrease=1.724, fixed=8.276, free_increase=1.724)
-xtable(apples)
 ````
@@
 
-Solve the policy cost for the specified penalty function
+Solve the policy cost for the specified penalty function.
 
@@
 ``` {r simulate_policy, dependson=c("L1", "L2", "free_increase", "free_decrease", "fixed", "quad_costs")}
+seed
 sims <- list(
@@
   labs(x="time", y="stock size", title = "Stock Dynamics")
+
 p0
@@
   labs(x="time", y="stock size", title = "Stock Dynamics")
+
 p1
@@
   labs(x="time", y="havest intensity (fish taken)", title = "Harvest Policy Dynamics")
+
 p2
 ````
+
+Calculate statistics of the kind used in figure 4.
+
+```{r}
+dt[,var(harvest), by=penalty_fn]
+dt[,acf(harvest, lag.max=1, plot=F)$acf[2], by=penalty_fn]
+```

### 2012-12-04 inst/examples/policycosts/figure4.Rmd
figure4 set up for run on farm

@@
 ``` {r libraries, include=FALSE}
+rm(list=ls())
 require(pdgControl)
@@
 
-``` {r  parallel}
-require(snowfall)
-sfInit(cpu=16, parallel=T)
-sfLibrary(pdgControl)
-sfExportAll()
-````
-
 ```{r setup}
 seed <- 123                 # Random seed (replicable results)
-delta <- 0.01               # economic discounting rate
-OptTime <- 100              # stopping time
-gridsize <- 100              # grid size for fish stock and harvest rate (discretized population)
+delta <- 0.05               # economic discounting rate
+OptTime <- 20               # stopping time
+gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
 sigma_g <- 0.2              # Noise in population growth
@@
 
+``` {r  parallel}
+require(snowfall)
+sfInit(cpu=16, parallel=T)
+sfLibrary(pdgControl)
+sfExportAll()
+````
+
 ### Loop over penalty functions and magnitudes
@@
 policies <- lapply(penaltyfns, function(penalty){
-  sfLapply(c2, function(c2)
-      optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
+  sfLapply(c2, function(c2){
+      policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                    profit, delta, reward, penalty = penalty(c2))
+      }
   )

### 2012-12-04 inst/examples/policycosts/figure4.Rmd
farm fast figure4
index by npv0 fraction (fixes typo)

@@
 dt <- data.table(dat)
-index <- dt[,closest(.25, (npv0-value)/value), by=variable]
+index <- dt[,closest(.25, (npv0-value)/npv0), by=variable]
 apples <- c2[index$V1]

### 2012-12-04 inst/examples/policycosts/policycosts.Rmd
index by npv0 fraction (fixes typo)

@@
 seed <- 123                 # Random seed (replicable results)
-delta <- 0.01               # economic discounting rate
-OptTime <- 100              # stopping time
-gridsize <- 100              # grid size for fish stock and harvest rate (discretized population)
+delta <- 0.05               # economic discounting rate
+OptTime <- 20              # stopping time
+gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
 sigma_g <- 0.2              # Noise in population growth
@@
   sapply(c2, function(c2){
-  effort_penalty = function(x,h) .1 * c2 * h / x
+  effort_penalty = function(x,h) c2 * h / x
   policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
@@
 ````
+
+```{r}
+save(list=ls(), file="policycosts.rda")
+```
 
@@
 ````
+
+Calculate statistics of variance and autocorrelation for Figure 4.
+
+```{r}
+v <- dt[,var(harvest), by=penalty_fn]
+a <- dt[,acf(harvest, lag.max=1, plot=F)$acf[2], by=penalty_fn]
+v
+a
+```

### 2012-12-04 inst/examples/policycosts/quick_examples.Rmd

@@
 
-Actually, we'll want to draw these from the table in figure4 data at different levels.  
-Ideally we can draw the policy out rather than running that again.
-
 ```{r apples}
 apples <- c(L2=1.034, L1=1.724, free_decrease=1.724, fixed=8.276, free_increase=1.724)
+xtable(apples)
 ````
@@
 
-Solve the policy cost for the specified penalty function.
+Solve the policy cost for the specified penalty function
 
@@
 ````
-
-Calculate statistics of the kind used in figure 4.
-
-```{r}
-dt[,var(harvest), by=penalty_fn]
-dt[,acf(harvest, lag.max=1, plot=F)$acf[2], by=penalty_fn]
-```

### 2012-12-04 inst/examples/policycosts/quick_examples.Rmd
policycosts quick example from one

@@
 seed <- 123                 # Random seed (replicable results)
-delta <- 0.01               # economic discounting rate
-OptTime <- 100              # stopping time
-gridsize <- 100              # grid size for fish stock and harvest rate (discretized population)
+delta <- 0.05               # economic discounting rate
+OptTime <- 20            # stopping time
+gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
 sigma_g <- 0.2              # Noise in population growth
@@
 ````
+
+```{r}
+dt[,var(harvest), by="penalty_fn"]
+dt[,acf(harvest, plot=F)$acf[2], by="penalty_fn"]
+```

### 2012-12-04 inst/examples/policycosts/figure4.Rmd
fixed figure4 -- extract policycost separately from bigloop

@@
 profit <- profit_harvest(price = 10, c0 = 30, c1 = 0)
-c2 <- seq(0, 20, length.out = 40)
+c2 <- exp(seq(0, log(21), length.out = 20))-1
 ```
@@
 })
-dat <- cbind(policies, quad)
+policies <- c(policies, quad=list(quad))
 ````
+
+Extract the policy cost
+
+```{r}
+i <- which(x_grid > K)[1]
+dat <- 
+lapply(policies, function(penalty) 
+  sapply(penalty, function(c2_run)
+    max(c2_run$penalty_free_V[i,]) 
+  )
+)
+```
 

### 2012-12-04 inst/examples/policycosts/policycosts_writeup_c0_30.Rmd
example c0_30 from farm (images)

@@
 ```{r cache-options, include=FALSE}
-opts_chunk$set(cache=TRUE, cache.path="policycosts-cache-c0-30/")
+opts_chunk$set(cache=TRUE, cache.path="policycosts-cache-c0-30/", fig.path="figure/c30-")
 ```
@@
 ```{r}
-profit <- profit_harvest(price = 10, c0 = 30, c1 = 0)
-c2 <- seq(0, 20, length.out = 40)
+price = 1
+c0 = 30
+c1 = 0
 ```
@@
 ```{r }
-ggplot(dat, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
+apples_plot
 ````
@@
 ```{r}
-as.table(apples)
-```
-
-``` {r }
-p0
+apples
 ```

### 2012-12-04 inst/examples/policycosts/policycosts.Rmd
accompanying main source file for previous 3 commits

@@
 First it calibrates the apples-to-apples comparison level for each penalty function, and then generates sample plots by penalty function, illustrating the resulting stock dynamics and harvest quota dynamics.
-The file needs a `profit` function to be specified and the grid of `c2` values over which we search to find the coefficient introducing the 25% reduction in Net Present Value (npv).
 
@@
 
-``` {r  parallel}
-require(snowfall)
-sfInit(cpu=16, parallel=T)
-sfLibrary(pdgControl)
-sfExportAll()
-````
+```{r}
+profit <- profit_harvest(price = price, c0 = c0, c1 = c1)
+c2 <- exp(seq(0, log(21), length.out = 20))-1
+```
 
@@
 ## Apples to Apples levels
+
+``` {r  parallel}
+require(snowfall)
+sfInit(cpu=16, parallel=T)
+sfLibrary(pdgControl)
+sfExportAll()
+````
 
@@
 dat <- melt(dat, id="c2")
-ggplot(dat, aes(c2, value, col=variable)) + geom_point() + geom_line()
 ````
@@
 ```{r apples_plot, dependson="quadcosts"}
-ggplot(dat, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
+apples_plot <- ggplot(dat, aes(c2, (max(value)-value)/max(value), col=variable)) + geom_point() + geom_line()
 ````
@@
 ```{r quad_costs, dependson="apples"}
-quad_profit <- profit_harvest(price = 10, c0 = 30, c1 = apples["quad"]) 
+quad_profit <- profit_harvest(price = 10, c0 = c0, c1 = apples["quad"]) 
 quad_costs <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, quad_profit, delta, reward, penalty =  none)

### 2012-12-04 inst/examples/policycosts/policycosts.Rmd
use price=10 for better scaling

@@
 profit <- profit_harvest(price = price, c0 = c0, c1 = c1)
-c2 <- exp(seq(0, log(21), length.out = 20))-1
+c2 <- exp(seq(0, log(price), length.out = 32))-1
 ```
@@
   sapply(c2, function(c2){
-  effort_penalty = function(x,h) c2 * h / x
+  effort_penalty = function(x,h) ( c2 * h / x) / price
   policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 

### 2012-12-04 inst/examples/policycosts/figure4.Rmd

--- 2012-12-04 inst/examples/policycosts/figure4.Rmd
@@
 ``` {r}
-profit <- profit_harvest(price = 10, c0 = 30, c1 = 0)
-c2 <- seq(0, 20, length.out = 40)
+price = 10
+c0 = 30
+profit <- profit_harvest(price = price, c0 = c0, c1 = 0)
+c2 <- exp(seq(0, log(21), length.out = 20))-1
 ```
@@
 require(snowfall)
-sfInit(cpu=16, parallel=T)
+sfInit(cpu=8, parallel=T)
 sfLibrary(pdgControl)
@@
   sfLapply(c2, function(c2){
-  effort_penalty = function(x,h) c2 * h / x
+  effort_penalty = function(x,h) (c2 * h / x) / price
   policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
@@
 ``` {r npv-plot, dependson="quadcosts"}
-npv0 <- dat[1,3] 
+npv0 <- max(dat$L1) # all have same max, at c2=0 
 npv0
@@
 index <- dt[,closest(.25, (npv0-value)/npv0), by=variable]
+apples_index <- index$V1
+names(apples_index) = index$variable
 apples <- c2[index$V1]
@@
 
-``` {r L2, dependson="apples"}
-L2_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
-                    profit, delta, reward, penalty = L2(apples["L2"]))
-````
-
-```{r fixed, dependson="apples"}
-fixed_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
-    profit, delta, reward, penalty = fixed(apples["fixed"]))
+``` {r policynames}
+L2_policy <- policies$L2[[apples_index["L2"]]]$D
+L1_policy <- policies$L1[[apples_index["L1"]]]$D
+fixed_policy <- policies$fixed[[apples_index["fixed"]]]$D
+free_increase_policy <- policies$free_increase[[apples_index["free_increase"]]]$D
+free_decrease_policy <- policies$free_decrease[[apples_index["free_decrease"]]]$D
+quad_policy <- policies$quad[[apples_index["quad"]]]$D
 ```
 
-``` {r L1, dependson="apples"}
-L1_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward, penalty = L1(apples["L1"]))
-````
-
-```{r free_increase, dependson="apples"}
-free_increase_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward, penalty =  free_increase(apples["free_increase"]))
-````
-
-```{r free_decrease, dependson="apples"}
-free_decrease_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward, penalty = free_decrease(apples["free_decrease"]))
-````
-
-We also compare to the case in which costs of harvesting increase quadratically with effort; a common approach to create smoother policies.
-
-```{r quad_costs, dependson="apples"}
-quad_profit <- profit_harvest(price = 10, c0 = 30, c1 = apples["quad"]) 
-quad_costs <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, quad_profit, delta, reward, penalty =  none)
-```
-
-``` {r simulate_policy, dependson=c("L1", "L2", "free_increase", "free_decrease", "fixed", "quad_costs")}
+``` {r simulate_policy, dependson="policynames"}
+quad_profit <- profit_harvest(price = price, c0 = c0, c1 = apples["quad"]) 
 sims <- list(
   L1 = simulate_optim(f, pars, x_grid, h_grid, x0, 
-                      L1_policy$D, z_g, z_m, z_i, 
+                      L1_policy, z_g, z_m, z_i, 
                       opt$D, profit=profit, penalty=L1(apples["L1"]), seed=seed), 
   L2 = simulate_optim(f, pars, x_grid, h_grid, x0, 
-                      L2_policy$D, z_g, z_m, z_i, 
+                      L2_policy, z_g, z_m, z_i, 
                       opt$D, profit=profit, penalty=L2(apples["L2"]), seed=seed),
   fixed = simulate_optim(f, pars, x_grid, h_grid, x0, 
-                         fixed_policy$D, z_g, z_m, z_i, 
+                         fixed_policy, z_g, z_m, z_i, 
                          opt$D, profit=profit, penalty=fixed(apples["fixed"]), seed=seed),
   increase = simulate_optim(f, pars, x_grid, h_grid, x0, 
-                            free_increase_policy$D, z_g, z_m, z_i, 
+                            free_increase_policy, z_g, z_m, z_i, 
                             opt$D, profit=profit, penalty= free_increase(apples["increase"]), seed=seed),
   decrease = simulate_optim(f, pars, x_grid, h_grid, x0, 
-                            free_decrease_policy$D, z_g, z_m, z_i, 
+                            free_decrease_policy, z_g, z_m, z_i, 
                             opt$D, profit=profit, penalty= free_decrease(apples["decrease"]), seed=seed),
   quad = simulate_optim(f, pars, x_grid, h_grid, x0, 
-                            free_decrease_policy$D, z_g, z_m, z_i, 
+                            quad_policy, z_g, z_m, z_i, 
                             opt$D, profit=quad_profit, penalty= none, seed=seed)
@@
 
-``` {r p0, dependson="tidy"}
-p0 <- ggplot(dt) +
-  geom_line(aes(time, harvest_alt), col="grey20", lwd=1) +
-  geom_line(aes(time, harvest, col=penalty_fn, lty=penalty_fn))+ 
-  labs(x="time", y="stock size", title = "Stock Dynamics")
-```
-
 ```{r p1, dependson="tidy", fig.width=12}
@@
 
-```{r p2, dependson="tidy", fig.width=12}
+```{r Figure3, dependson="tidy", fig.width=12}
 p2 <- ggplot(dt) +

### 2012-12-04 inst/examples/policycosts/figure4.Rmd
working example of Figures 3 & 4
Still need to fully understand why asymmetric costs appear to be able to realize NPV0 policies, even though they cannot.

@@
 i <- which(x_grid > K)[1]
-dat <- 
+fees <- 
 lapply(policies, function(penalty) 
@@
 ``` {r npv-plot, dependson="quadcosts"}
-npv0 <- max(dat$L1) # all have same max, at c2=0 
+npv0 <- max(fees$L1) # all have same max, at c2=0 
 npv0
-dat <- data.frame(c2=c2,dat)
-dat <- melt(dat, id="c2")
-ggplot(dat, aes(c2, value, col=variable)) + geom_point() + geom_line()
+fees <- data.frame(c2=c2,fees)
+fees <- melt(fees, id="c2")
+ggplot(fees, aes(c2, value, col=variable)) + geom_point() + geom_line()
 ````
@@
 ```{r apples_plot, dependson="quadcosts"}
-ggplot(dat, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
+ggplot(fees, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
 ````
@@
 }
-dt <- data.table(dat)
-index <- dt[,closest(.25, (npv0-value)/npv0), by=variable]
+dt_npv <- data.table(fees)
+index <- dt_npv[,closest(0.25, (npv0-value)/npv0), by=variable]
 apples_index <- index$V1
@@
 ````
-
-## Results
 
@@
 
+```{r}
+v <- dt[,var(harvest), by="penalty_fn"]
+var <- v$V1
+names(var) <- v$penalty_fn
+acor <- dt[,acf(harvest, plot=F)$acf[2], by="penalty_fn"]$V1
+names(acor) <- names(var)
+out <- rbind(var=var, a=acor)
+out
+```
+
 # Plots
@@
 ````
+
+```{r}
+source("fig4_helper_fun.R")
+frac_lost <- seq(0,1, length=5)
+out <- lapply(frac_lost, fig4, ls())
+out <- melt(out)
+colnames(out) = c("statistic", "penalty", "value", "index")
+out <- cbind(out[1:3], fraction = frac_lost[out$index])
+Figure4 <- ggplot(out) + geom_line(aes(fraction, value, col=penalty)) + facet_wrap(~statistic)
+Figure4
+````

### 2012-12-04 inst/examples/policycosts/writeup.Rmd

--- 2012-12-04 inst/examples/policycosts/figure4.Rmd
@@
 ```{r cache-options, include=FALSE}
-opts_chunk$set(cache=TRUE, cache.path="figure4/")
+opts_chunk$set(cache=TRUE, cache.path="writeup/")
 ```
@@
 ```{r graphing-options, include=FALSE}
-#opts_knit$set(upload.fun = socialR::notebook.url)
+opts_knit$set(upload.fun = socialR::notebook.url)
 opts_chunk$set(dev.args=list(bg="transparent"),
@@
 
-```{r}
-source("fig4_helper_fun.R")
-frac_lost <- seq(0,1, length=5)
-out <- lapply(frac_lost, fig4, ls())
+```{r Figure4}
+frac_lost <- seq(0.1,0.9, length=5)
+out <- lapply(frac_lost, pdgControl:::fig4, ls())
 out <- melt(out)
 colnames(out) = c("statistic", "penalty", "value", "index")
-out <- cbind(out[1:3], fraction = frac_lost[out$index])
-Figure4 <- ggplot(out) + geom_line(aes(fraction, value, col=penalty)) + facet_wrap(~statistic)
+out <- cbind(out[1:3], fraction__npv_lost = frac_lost[out$index])
+Figure4 <- ggplot(out) + geom_point(aes(fraction_npv_lost, value, col=penalty)) + geom_line(aes(fraction, value, col=penalty)) + facet_wrap(~statistic, scales="free_y")
 Figure4

### 2012-12-04 inst/examples/policycosts/writeup.Rmd
updated writeup Fig4 graphs

@@
 ```{r Figure4}
-frac_lost <- seq(0.1,0.9, length=5)
-out <- lapply(frac_lost, pdgControl:::fig4, ls())
-out <- melt(out)
-colnames(out) = c("statistic", "penalty", "value", "index")
-out <- cbind(out[1:3], fraction__npv_lost = frac_lost[out$index])
-Figure4 <- ggplot(out) + geom_point(aes(fraction_npv_lost, value, col=penalty)) + geom_line(aes(fraction, value, col=penalty)) + facet_wrap(~statistic, scales="free_y")
-Figure4
+frac_lost <- seq(0,1, length=20)
+tmp <- lapply(frac_lost, fig4, ls())
+out <- melt(tmp, id=c("reps", "var", "acor"))
+colnames(out) = c("reps", "var", "acor", "nothing", "penalty", "index")
+out <- cbind(out[c(1,2,3,5)], fraction = frac_lost[out$index])
+out <- data.table(out)
+
+Ev = out[,mean(var),by=c('penalty', 'fraction')]
+SDv = out[,sd(var),by=c('penalty', 'fraction')]
+Ea = out[,mean(acor),by=c('penalty', 'fraction')]
+SDa = out[,sd(acor),by=c('penalty', 'fraction')]
+
+tmp2 <- data.table(penalty = Ev$penalty, fraction = Ev$fraction, Ev = Ev$V1, Ea = Ea$V1, SDv=SDv$V1, SDa = SDa$V1)
+
+Fig4a <- ggplot(tmp2, aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
+  #geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.1) + 
+  geom_line() + xlab("Fraction of NPV lost to costs")
+Fig4a
+Fig4b <- ggplot(tmp2, aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
+  #geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.1) + 
+  geom_line() + xlab("Fraction of NPV lost to costs")
+Fig4b
 ````

### 2012-12-04 R/fig4_helper_fn.R

@@ -1,4 +1,5 @@
 
+#' @export
 fig4 <- function(fraction_lost, ...){
 closest <- function(x, v){
   which.min(abs(v-x))
@@ -9,7 +10,6 @@ apples_index <- index$V1
 names(apples_index) = index$variable
 apples <- c2[index$V1]
 names(apples) = index$variable
-apples
 
 L2_policy <- policies$L2[[apples_index["L2"]]]$D
 L1_policy <- policies$L1[[apples_index["L1"]]]$D
@@ -19,38 +19,44 @@ free_decrease_policy <- policies$free_decrease[[apples_index["free_decrease"]]]$
 quad_policy <- policies$quad[[apples_index["quad"]]]$D
 
 quad_profit <- profit_harvest(price = price, c0 = c0, c1 = apples["quad"]) 
-sims <- list(
+sims <- lapply(1:10, function(reps) list(
   L1 = simulate_optim(f, pars, x_grid, h_grid, x0, 
                       L1_policy, z_g, z_m, z_i, 
-                      opt$D, profit=profit, penalty=L1(apples["L1"]), seed=seed), 
+                      opt$D, profit=profit, penalty=L1(apples["L1"])), 
   L2 = simulate_optim(f, pars, x_grid, h_grid, x0, 
                       L2_policy, z_g, z_m, z_i, 
-                      opt$D, profit=profit, penalty=L2(apples["L2"]), seed=seed),
+                      opt$D, profit=profit, penalty=L2(apples["L2"])),
   fixed = simulate_optim(f, pars, x_grid, h_grid, x0, 
                          fixed_policy, z_g, z_m, z_i, 
-                         opt$D, profit=profit, penalty=fixed(apples["fixed"]), seed=seed),
+                         opt$D, profit=profit, penalty=fixed(apples["fixed"])),
   increase = simulate_optim(f, pars, x_grid, h_grid, x0, 
                             free_increase_policy, z_g, z_m, z_i, 
-                            opt$D, profit=profit, penalty= free_increase(apples["increase"]), seed=seed),
-  decrease = simulate_optim(f, pars, x_grid, h_girpdgd, x0, 
+                            opt$D, profit=profit, penalty= free_increase(apples["increase"])),
+  decrease = simulate_optim(f, pars, x_grid, h_grid, x0, 
[…]

### 2012-12-04 inst/examples/policycosts/writeup.Rmd
finalized version of writeup.md

@@
 Fig4a <- ggplot(tmp2, aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
-  #geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.1) + 
+  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
+  geom_line() + xlab("Fraction of NPV lost to costs")
+
+Fig4b <- ggplot(tmp2, aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
+  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
   geom_line() + xlab("Fraction of NPV lost to costs")
 Fig4a
-Fig4b <- ggplot(tmp2, aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
-  #geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.1) + 
-  geom_line() + xlab("Fraction of NPV lost to costs")
 Fig4b

### 2012-12-04 inst/examples/policycosts/costfree.Rmd
cleanup

--- 2012-12-04 inst/examples/policycosts/writeup.Rmd
@@
 ```{r cache-options, include=FALSE}
-opts_chunk$set(cache=TRUE, cache.path="writeup/")
+opts_chunk$set(cache=TRUE, cache.path="costfree/")
 ```
@@
 price = 10
-c0 = 30
+c0 = 0
 profit <- profit_harvest(price = price, c0 = c0, c1 = 0)

### 2012-12-04 inst/doc/policycosts/policycosts.tex
writing writing

@@
 
-To compare the impact of penalty functions on optimal management, we select penalty magnitudes that make the resource worth 80\% of its unconstrained value.
-The dashed vertical lines in Figure 2 map the needed penalty function magnitude, C2, to each penalty function such that the resource is worth 80\% of its unconstrained value when optimally managed.
-We choose 80\% somewhat arbitrarily but the method is applicable to any NPV level and the qualitative effects on management are robust for other levels.
-
-Bovenberg, AL, Goulder LH, and Gurney DJ (2005).  “Efficiency Costs of Meeting Industry-Distributional  Constraints Under Environmental Permits and Taxes” RAND Journal of Economics. 36(4): 951-  971.
-
-Bovenberg, AL, Goulder LH, and Jacobsen MR (2008).  “Costs of Alternative Policy Instruments in the    Presence of Industry Compensation Requirements” Journal of Public Economics. 92: 1236-1253.
+To compare the impact of penalty functions on optimal management, we select penalty magnitudes that make the resource worth 75\% of its unconstrained value.
+The dashed vertical lines in Figure 2 map the needed penalty function magnitude, C2, to each penalty function such that the resource is worth 75\% of its unconstrained value when optimally managed.
+We choose 75\% somewhat arbitrarily but the method is applicable to any NPV level and the qualitative effects on management are robust for other levels.
 
@@
 Figure~\ref{fig:shapes} shows the impact the adjustment cost has on the optimal policy.
-The $L_1$-norm costs tend to avoid small adjustments to the policy, resulting in long periods of constant policy followed by sudden bursts of adjustment.
+Each panel is generated against the same sequence of random shocks so that they can be compared directly.
+In each case, the optimal solution without any adjustment cost is shown in black and the policy induced by optimization under the given adjustment penalty is overlaid in blue.
+The $L_1$ panel of Figure~\ref{fig:shapes} shows a pattern typical of the $L_1$-norm, which tends to avoid small adjustments to the policy, resulting in long periods of constant policy followed by sudden bursts of adjustment.
+This results in a relatively step-like policy pattern.
 In contrast, the $L_2$-norm tracks all of the changes made by the cost-free policy, but with smaller magnitude.
-The fixed fee only makes large adjustments much like the $L_1$, as expected where the adjustment magnitude does not impact the cost.
-Asymmetric ($L_1$) adjustment costs do not appear to show more directional bias than any of the symmetric costs.
-Note that while the cost-free optimal strategy corresponds to a constant-escapement policy as derived in~\citet{Reed1979}, any of the policy-cost scenarios deviate from such a policy.
-    \cdb{
-    \begin{itemize}
-      \item All of these should use the same sequence of shocks.  
-      \item Don't plot all four curves on the same graph.  
-      \item Omit stock dynamics?
-      \item Consider not violating the self-sustaining property, which should also guarantee that fishing never stops.   
-    \end{itemize}
-    }
+This results in a smoother curve that undershoots the larger oscillations seen in the cost-free optimum, but results in a policy that changes incrementally each interval.
+The fixed fee only makes large adjustments $L_1$, as expected where the adjustment magnitude does not impact the cost.
+Where the $L_1$ norm attempts to accomidate the large oscillations at the end with a constant quota in between the extremes, the fixed cost takes the opposite approach of one very large swing.
+Asymmetric ($L_1$) adjustment costs attempt to track the optimal solution, and can end up with larger fees than anticipated.
+\cdb{Not quite sure why we get this pattern in the asymmetrics!}
+
+The resulting stock dynamics are more similar to the optimal solution (Figure S1).
 
@@
 catch vs escapement)?
-Surely the simplicity of the constant-escapement rule has led to it's popularity in some part due because that simplicity avoids adjustment costs?}
+Surely the simplicity of the constant-escapement rule has led to it's popularity in some part due because that simplicity avoids adjustment costs?
+We should consider a parameter range where the solution has less chatter?
+Parameters that actually satisify the \citet{Reed1979} self-sustaining condition?}
 
@@
     \begin{center}
-      \subfigure[$L_1$]{\includegraphics[width=.45\textwidth]{figure/7258516896_5c89f034d5_o.png}\label{fig:L1}}
-      \subfigure[$L_2$]{\includegraphics[width=.45\textwidth]{figure/7258563112_2f5f9ffecd_o.png}\label{fig:L2}}
-
-      \subfigure[Fixed costs]{\includegraphics[width=.45\textwidth]{figure/7258506664_d6235e5f8e_o.png}\label{fig:fixed}}
-      \subfigure[Asymmetric costs]{\includegraphics[width=.45\textwidth]{figure/7258432026_d6f8179f54_o.png}\label{fig:asym}}
+      \includegraphics[width=\textwidth]{figure/2012-12-04-8f1e7b92fa-Figure3.png}
   \end{center}
-  \caption{Individual realizations of management under the different functional forms of adjustment costs.
-\textbf{Green} lines show the cost-free optimal harvest levels, \textbf{black} lines show the corresponding stock dynamics under that management.
-\textbf{Purple} lines show the optimal harvest level under the specified adjustment cost, under the same sequence of stochastic shocks as in the cost-free policy.
-\textbf{Blue lines} show the resulting stock dynamics.
-  } \label{fig:shapes}
+  \caption{Individual realizations of management under the different functional forms of adjustment costs.} \label{fig:shapes}
 \end{figure}
@@
 
-The comparisons shown in Figure~\ref{fig:shapes} are made at a fixed magnitude of the policy cost equal to 80\% of the net present value derived from the cost-free optimal strategy.
+The comparisons shown in Figure~\ref{fig:shapes} are made at a fixed magnitude of the policy cost equal to 25\% of the net present value derived from the cost-free optimal strategy.
 The different functional forms may also respond differently to an increasing magnitude of the adjustment cost.
 To quantify the extent to which the policy cost decreases the volatility of the proposed policy, we calculate the variance in the fishing quota over time under each policy.
-While a decrease in variance is typical of smoothing penalties and the $L_2$-norm, the patterns in Figure~\ref{fig:shapes} suggest that other functional forms still involve the same magnitude of variation, but decrease the frequency of adjustments.
-To capture this behavior we calculate the autocorrelation of the policy as the adjustment cost increases.
-These curves van be seen in Figure~\ref{fig:summarystats}.
+The variance is averaged over 50 replicates, and recalculated at each of 20 different intensities ranging from 0 (no cost) to 1 (NPV reduced to zero by the adjustment costs)The variance is averaged over 50 replicates, and recalculated at each of 20 different intensities ranging from 0 (no cost) to 1 (NPV reduced to zero, by the adjustment costs), shown in Figure~\ref{fig:summarystats}.
+\cdb{Correction: not actually zero, just to max reduction (usually what is obtained by constant quota).
+Should indicate where this asymptote has occurred)}.
 
-\cdb{Perhaps not clear what is comparable here and what isn't.
-Certainly we cannot compare the curves at the same value of $c_2$, as discussed in our apples to apples section.
-Not clear that we can even compare the shape of the curves though -- for instance, given the units of $c_2$ for the $L_2$ norm are different than the other norms.
-Perhaps the horizontal axis should be converted into percent of net present value of the adjustment free costs first?}
+The variance is always smallest in $L_2$, which creates relatively smooth policies, and largest in the fixed cost, which creates highly volatile adjustments (Figure~\ref{fig:var}).
+Stronger penalties further shrink the variance of the $L_2$ norm and the smoothing quadratic costs on effort, while provoking even higher variance in the fixed cost solution.
+The $L_1$ solution does not become either more or less variable as costs increase.
+
+The autocorrelation of the policies also captures the qualitative pattern observed in the individual replicates (Figure~\ref{fig:acor}).
+The $L_2$ norm shows postively auto-correlated patterns, since a series of small increases is often required in lieu of a single large adjustment in the cost-free solution.
+The other penalties tend to have more oscillatory solutions, leading to a negative autocorrelation.
 
@@
   \begin{center}
-    \subfigure[Variance]{\includegraphics[width=.45\textwidth]{figure/6850042286_ef81b74acc_o.png}\label{fig:var}}
-    \subfigure[Autocorrelation]{\includegraphics[width=.45\textwidth]{figure/6996165783_41c9894bdb_o.png}\label{fig:acor}}
+    \subfigure[Variance]{\includegraphics[width=.45\textwidth]{figure/2012-12-04-8f1e7b92fa-Figure41.png}\label{fig:var}}
+    \subfigure[Autocorrelation]{\includegraphics[width=.45\textwidth]{figure/2012-12-04-8f1e7b92fa-Figure42.png}\label{fig:acor}}
     \caption{Variance and autocorrelation as a function of the magnitude of penalty, by penalty function}\label{fig:summarystats}
@@
 \section*{References}
+
+Bovenberg, AL, Goulder LH, and Gurney DJ (2005).  “Efficiency Costs of Meeting Industry-Distributional  Constraints Under Environmental Permits and Taxes” RAND Journal of Economics. 36(4): 951-  971.
+
+Bovenberg, AL, Goulder LH, and Jacobsen MR (2008).  “Costs of Alternative Policy Instruments in the    Presence of Industry Compensation Requirements” Journal of Public Economics. 92: 1236-1253.
 \bibliography{outline_refs.bib}

### 2012-12-05 inst/examples/policycosts/writeup.Rmd
writeup generates plots for fishstock now as well as harvest

--- 2012-12-04 inst/examples/policycosts/writeup.Rmd
@@
 
+# Figure 4
+
+```{r helperfn1}
+fig4 <- function(fraction_lost){
+closest <- function(x, v){
+  which.min(abs(v-x))
+}
+dt_npv <- data.table(fees)
+index <- dt_npv[,closest(fraction_lost, (npv0-value)/npv0), by=variable]
+apples_index <- index$V1
+names(apples_index) = index$variable
+apples <- c2[index$V1]
+names(apples) = index$variable
+L2_policy <- policies$L2[[apples_index["L2"]]]$D
+L1_policy <- policies$L1[[apples_index["L1"]]]$D
+fixed_policy <- policies$fixed[[apples_index["fixed"]]]$D
+free_increase_policy <- policies$free_increase[[apples_index["free_increase"]]]$D
+free_decrease_policy <- policies$free_decrease[[apples_index["free_decrease"]]]$D
+quad_policy <- policies$quad[[apples_index["quad"]]]$D
+
+quad_profit <- profit_harvest(price = price, c0 = c0, c1 = apples["quad"]) 
+sims <- lapply(1:50, function(reps) list(
+  L1 = simulate_optim(f, pars, x_grid, h_grid, x0, 
+                      L1_policy, z_g, z_m, z_i, 
+                      opt$D, profit=profit, penalty=L1(apples["L1"])), 
+  L2 = simulate_optim(f, pars, x_grid, h_grid, x0, 
+                      L2_policy, z_g, z_m, z_i, 
+                      opt$D, profit=profit, penalty=L2(apples["L2"])),
+  fixed = simulate_optim(f, pars, x_grid, h_grid, x0, 
+                         fixed_policy, z_g, z_m, z_i, 
+                         opt$D, profit=profit, penalty=fixed(apples["fixed"])),
+  increase = simulate_optim(f, pars, x_grid, h_grid, x0, 
+                            free_increase_policy, z_g, z_m, z_i, 
+                            opt$D, profit=profit, penalty= free_increase(apples["increase"])),
+  decrease = simulate_optim(f, pars, x_grid, h_grid, x0, 
+                            free_decrease_policy, z_g, z_m, z_i, 
+                            opt$D, profit=profit, penalty= free_decrease(apples["decrease"])),
+  quad = simulate_optim(f, pars, x_grid, h_grid, x0, 
+                            quad_policy, z_g, z_m, z_i, 
+                            opt$D, profit=quad_profit, penalty= none)
+  ))
+
+  #Make data tidy (melt), fast (data.tables), and nicely labeled.
+  dat <- melt(sims, id=names(sims[[1]][[1]]))  
+  dt <- data.table(dat)
+  setnames(dt, "L1", "reps") # names are nice
+  setnames(dt, "L2", "penalty_fn") # names are nice
+
+  dt
+}
+```
+
+```{r} 
+# Helper functions to extract the summary stats in different variables
+stats_harvest <- function(dt){
+v <- dt[,var(harvest), by=c("penalty_fn", "reps")]
+acor <- dt[,acf(harvest, plot=F)$acf[2], by=c("penalty_fn", "reps")]
+df <- cbind(v, acor$V1)
+setnames(df, c("V1", "V2"), c("var", "acor")) # names are nice
+df
+}
+
+stats_fishstock <- function(dt){
+v <- dt[,var(fishstock), by=c("penalty_fn", "reps")]
+acor <- dt[,acf(fishstock, plot=F)$acf[2], by=c("penalty_fn", "reps")]
+df <- cbind(v, acor$V1)
+setnames(df, c("V1", "V2"), c("var", "acor")) # names are nice
+df
+}
+```
+
+```{r helper2}
+#' a simple function for reorganizing the data over the different "faction-lost" levels
+get_trends <- function(tmp2){
+  out <- melt(tmp2, id=c("reps", "var", "acor"))
+  colnames(out) = c("reps", "var", "acor", "nothing", "penalty", "index")
+  out <- cbind(out[c(1,2,3,5)], fraction = frac_lost[out$index])
+  out <- data.table(out)
+  Ev = out[,mean(var),by=c('penalty', 'fraction')]
+  SDv = out[,sd(var),by=c('penalty', 'fraction')]
+  Ea = out[,mean(acor),by=c('penalty', 'fraction')]
+  SDa = out[,sd(acor),by=c('penalty', 'fraction')]
+  harvest_trends <- data.table(penalty = Ev$penalty, 
+                               fraction = Ev$fraction, 
+                               Ev = Ev$V1, Ea = Ea$V1, 
+                               SDv=SDv$V1, SDa = SDa$V1)
+}
+```
+
 ```{r Figure4}
-frac_lost <- seq(0.1,0.9, length=5)
-out <- lapply(frac_lost, pdgControl:::fig4, ls())
-out <- melt(out)
-colnames(out) = c("statistic", "penalty", "value", "index")
-out <- cbind(out[1:3], fraction__npv_lost = frac_lost[out$index])
-Figure4 <- ggplot(out) + geom_point(aes(fraction_npv_lost, value, col=penalty)) + geom_line(aes(fraction, value, col=penalty)) + facet_wrap(~statistic, scales="free_y")
-Figure4
+frac_lost <- seq(0,1, length=20)
+sims_at_each_apple <- lapply(frac_lost, fig4)
+harvest_stats <- lapply(sims_at_each_apple, stats_harvest)
+havest_trends <- get_trends(harvest_stats)
+
+Fig4a <- ggplot(harvest_trends, 
+                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
+  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
+  geom_line() + xlab("Fraction of NPV lost to costs")
+
+Fig4b <- ggplot(harvest_trends, 
+                aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
+  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
+  geom_line() + xlab("Fraction of NPV lost to costs")
+Fig4a
+Fig4b
 ````
+
+```{r}
+fishstock_stats <- lapply(sims_at_each_apple, stats_fishstock)
+fishstock_trends <- get_trends(fishstock_stats)
+
+FigS4a <- ggplot(fishstock_trends, 
+                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
+  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
+  geom_line() + xlab("Fraction of NPV lost to costs")
+
+FigS4b <- ggplot(fishstock_trends, 
+                aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
+  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
+  geom_line() + xlab("Fraction of NPV lost to costs")
+FigS4a
+FigS4b
+```

### 2012-12-05 inst/examples/policycosts/writeup.Rmd
added fishstock plots to example

@@
 
-```{r helperfn1}
+```{r}
+frac_lost <- seq(0,1, length=20)
+```
+
+```{r helper_fn_1}
 fig4 <- function(fraction_lost){
@@
 names(apples) = index$variable
+
 L2_policy <- policies$L2[[apples_index["L2"]]]$D
@@
 
-```{r} 
+```{r helper_fn_2} 
 # Helper functions to extract the summary stats in different variables
@@
 
-```{r helper2}
+```{r helper_fn_3}
 #' a simple function for reorganizing the data over the different "faction-lost" levels
@@
 
-```{r Figure4}
-frac_lost <- seq(0,1, length=20)
+```{r Figure4_harvest}
 sims_at_each_apple <- lapply(frac_lost, fig4)
 harvest_stats <- lapply(sims_at_each_apple, stats_harvest)
-havest_trends <- get_trends(harvest_stats)
+harvest_trends <- get_trends(harvest_stats)
+```
 
+```{r Figure4}
 Fig4a <- ggplot(harvest_trends, 
@@
 
-```{r}
+```{r Figure4S}
 fishstock_stats <- lapply(sims_at_each_apple, stats_fishstock)

### 2012-12-27 R/find_dp_optim.R
multi-dimensional population dynamics examples

@@ -53,7 +53,9 @@ find_dp_optim <- function(SDP_Mat, x_grid, h_grid, OptTime, xT, profit,
     V <- out[1,]                        # The new value-to-go
     D[,OptTime-time+1] <- out[2,]       # The index positions
   }
-
+  # check for convergence in V
+  
+  
   # Reed derives a const escapement policy saying to fish the pop down to
   # the largest population for which you shouldn't harvest: 
   ReedThreshold <- x_grid[max(which(D[,1] == 1))]

### 2012-12-27 R/population_models.R

@@ -159,14 +159,48 @@ Ricker <- function(x,h,p){
 #' @param h harvesting effort on parrotfish
 #' @param p c(a, g, T, gamma, r, d, s, K)
 #'            1  2  3     4   5  6  7  8
+#' @references Blackwood et al. (2011) doi:10.1890/10-2195.1
+#' @details 
+#' $$\begin{align}
+#' \frac{dM}{dt} = aMC - \frac{g(P) M}{M+T} + \gamma M T \\
+#' \frac{dC}{dt} = rTC - dC - a M C \\
+#' \frac{dP}{dt} = sP \left( 1- \frac{P}{\beta K(C) } \right) - h P 
+#' \end{align}$$
 #' @export
-coral <- function(x, h, p){
+coral <- function(x, h, p = c(a = 0.1, g = 1, T = , gamma = 0.8, r = 1, d = 0.44, s= 0.49, K = 1)){
  x_t1 <- p[1] * x[1] * x[2] + p[2] * x[3] * x[1] / (x[1] + p[3]) + p[4] * p[3] * x[1]
  x_t2 <- (p[5] * p[3] - p[6] - p[1] * x[1]  ) * x[2] 
  x_t3 <- p[7] * x[3] * (1 - x[3] / (p[8] * x[2])) - h * x[3]
  c(x_t1, x_t2, x_t3)
 }
+                  
 
+
+#' Coral-Parrotfish model
+#' @param x vector of population levels: macroalgae, coral, parrotfish
+#' @param h harvesting effort on parrotfish
+#' @param p c(a, g, gamma, r, d)
+#' @param dt descrization scale
+#' @references Mumby et al. (2007) doi:10.1038/nature06252
+#' Blackwood et al. (2011) doi:10.1890/10-2195.1
+#' @details 
+#' $$\begin{align}
+#' \frac{dM}{dt} = aMC - \frac{(g-h) M}{M+T} + \gamma M T \\
+#' \frac{dC}{dt} = rTC - dC - a M C \\
+#' T = 1 - M - C
+#' \end{align}$$
+#' @export
+mumby <- function(x, h, p= c(a = 0.1, g = .5, gamma = 0.8, r = 1, d = 0.44), dt=0.025){
+  M <- x[1] # Macroalgae
+  C <- x[2] # Corals
+  a <- p[1] # algal growth rate
+  g <- p[2] # grazing rate (reduced by harvesting)
[…]

### 2012-12-27 inst/examples/mult_uncertainty_test.Rmd
multi-dimensional population dynamics examples
initialized multiple_uncertainty as separate project (branched from pdg_control

@@
-Test multiple uncertainty function
+Compare multiple uncertainties
 
 ```{r  setup, echo=FALSE, cache=FALSE}
-require(pdgControl)
+require(multipleuncertainty)
 require(reshape2)
@@
 
-## Current version of the multiple uncertainty function
-
-```{r}
-#' SDP under multiple uncertainty
-#'
-#' Computes the SDP solution under the case of growth noise, 
-#' implementation errors in harvesting, and meaurement errors in 
-#' the stock assessment.  
-#'
-#' @param f the growth function of the escapement population (x-h)
-#'   should be a function of f(t, y, p), with parameters p
-#' @param p the parameters of the growth function
-#' @param x_grid the discrete values allowed for the population size, x
-#' @param h_grid the discrete values of harvest levels to optimize over
-#' @param sigma is the shape parameters for noise distribution (sigma_g, sigma_m, sigma_i) (default is no noise)
-#' @param pdfn is the probability density function (same functional form is used for growth, measure, implement).  (Default is uniform)
-#' @param profit is the profit function (defaults to the realized harvest)
-#' @return The D matrix giving the optimal harvest for each possible state in each timestep.  
-#' Hence the optimal policy at time t is given by the policy function D[,t].  
-#' Values of D[,t] correspond to the index of h_grid.  Indices of of D[,t] correspond to states in y_grid.  
-#' @export
-SDP_multiple_uncertainty <- function(f, p, x_grid, h_grid, Tmax = 25,
-                                     sigmas =c(sigma_g=0.3, sigma_m=0, sigma_i=0), 
-                                     pdfn = pdfn, profit = function(x,h) pmin(x, h)){
-
-# sigmas = c(0.2, 0.2, .0)
-    sigma_g <- sigmas[1]      
-    sigma_m <- sigmas[2]
-    sigma_i <- sigmas[3]
-    n_x <- length(x_grid)
-    n_h <- length(h_grid)
-    D <- matrix(NA, nrow=n_x, ncol=Tmax)
-
-    ## Compute the transition matrices 
-    P <-  outer(x_grid, h_grid, profit) 
-    M <- rownorm( outer(x_grid, x_grid, pdfn, sigma_m) )
-    I <- rownorm( outer(h_grid, h_grid, pdfn, sigma_i) )
-
-    # Much faster to fill out f calls as a matrix ahead of time.  
-    f_matrix <- outer(x_grid, h_grid, f, p)
-    # Fill out uncertainty in transitions first
-    G <- outer(x_grid, x_grid, pdfn, sigma_g)
-
-    F <- lapply(1:n_h, function(q){  
-      t(sapply(1:n_x, function(y){
-        out <- numeric(n_x)
-        mu <- M[y,] %*% f_matrix %*% I[q,] 
-        # Handle special cases
-        if(snap_to_grid(mu,x_grid)==0){ # 
-          out[1] <- 1   
-        } else {
-        #out <- pdfn(x_grid, mu, sigma_g)  ## All computational time spent here.  could be done by look-up:
-         mu_i <- which.min(abs(x_grid - mu)) ## snap mu to grid first
-         out <- G[,mu_i]   ## then do this by table look-up
-         ## Not identical but very close.  
-        }
-        out/sum(out)
-      }))
-    })
-
-    # n_y by n_x, given y %*% n_x by n_h %*% n_h by n_q, given q
-    Ep <- M %*% P %*% t(I)
-    V <- Ep
-    for(t in 1:Tmax){
-      D[,(Tmax-t+1)] <- apply(V, 1, which.max) 
-      ## q can often exceed y: if fishing is free, there might be more x than you think.  
-      #if(any(pmin(D[,(Tmax-t+1)], 1:n_h) !=  D[,(Tmax-t+1)])) stop()
-      #v_t <- sapply(1:n_h, function(i) V[i,D[i,(Tmax-t+1)]]) # Look-up value given by which.max
-      v_t <- apply(V, 1, max) # vector of current values 
-      V <- sapply(1:n_h, function(j){ # updated value matrix
-        Ep[,j] + (1-delta) * M %*% F[[j]] %*% v_t
-      })
-    }
-    list(D=D, M=M, I=I, P=P, Ep=Ep, V=V, F=F)
-}
-
-# row-normalize the probability distribution
-rownorm <- function(M) t(apply(M, 1, function(x) x/sum(x)))
-# binning routine (vectorized)
-snap_to_grid <- function(x, grid) sapply(x, function(x) grid[which.min(abs(grid - x))])   
-```
-
 ``` {r stateeq}
@@
 profit = function(x,h) pmin(x, h)
-#profit <- profit_harvest(price=1, c0 = 0, c1=0)
+```
 
+```{r }
 pars <- c(1.5, 0.05)
@@
 OptTime <- 25
-
 sigma_g=0.3
 ````
-
-Old school way:
-
-``` {r  SDP_Mat}
-SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g)
-opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
-````
-
-New way:
-
-```{r}
-# Uniform pdf where width scales with mean (probably better way to do that)
-# And handles degenerate/delta fn cases such as no width and zero mean
-FUN <- function(P, mu, s){
-  if(mu == 0){
-    as.integer(P == 0)
-  } else if(s > 0){
-    if(mu > 0){
-      #dlnorm(P/mu, 0, s)
-      dunif(P, mu * (1 - s), mu * (1 + s))
-    }
-  }
-  else { # delta spike
-    P <- snap_to_grid(P, x_grid)
-    mu <- snap_to_grid(mu, x_grid)
-    as.numeric(as.integer(P == mu))
-  }
-}
-pdfn <- Vectorize(FUN)
-```
 
@@
 require(reshape2)
-policies <- melt(data.frame(stock=x_grid, old = x_grid[opt$D[,1]], g = x_grid[g$D[,1]], meas = x_grid[m$D[,1]], imp = x_grid[i$D[,1]]), id="stock")
+policies <- melt(data.frame(stock=x_grid, g = x_grid[g$D[,1]], meas = x_grid[m$D[,1]], imp = x_grid[i$D[,1]]), id="stock")
 ```

### 2012-12-27 R/ForwardSimulate.R

@@ -1,60 +1,0 @@
-## Note: See policy_costs.R for another simulation algorithm 
-
-
-#' Forward simulate given the optimal havesting policy, D
-#' @param f the growth function of the escapement population (x-h)
-#'   should be a function of f(y, p), with parameters p
-#' @param p the parameters of the growth function
-#' @param x_grid the discrete values allowed for the population size, x
-#' @param h_grid the discrete values of harvest levels to optimize over
-#' @param Xo initial stock size
-#' @param D the optimal solution indices on h_grid, 
-#'  given for each possible state at each timestep
-#' @param z_g a function which returns a random multiple for population growth 
-#' @param z_m a function which returns the measurement uncertainty in the 
-#'  assessment of stock size
-#' @param z_i a function which returns a random number from a distribution 
-#' for the implementation uncertainty in quotas 
-#' @param profit function, if known
-#' @return a data frame with the time, fishstock, harvested amount,
-#'  and what the escapement ("unharvested"). 
-#' @export
-ForwardSimulate <- function(f, pars, x_grid, h_grid, x0, D, z_g,
-                            z_m=function(x) 1, z_i = function(x) 1, 
-                            profit=NULL){
-  # initialize variables with initial conditions
-  OptTime <- dim(D)[2]    # Stopping time
-  x_h <- numeric(OptTime) # population dynamics with harvest
-  h <- numeric(OptTime) # optimal havest level
-  x_h[1] <- x0  # initial values
-  
-  s <- x_h # also track escapement
-  x <- x_h # What would happen with no havest
-  p <- numeric(OptTime)
- 
-    
-  ## Simulate through time ##
-  for(t in 1:(OptTime-1)){
-    # Assess stock, with potential measurement error
-    m_t <- x_h[t] * z_m()
-    # Current state (is closest to which grid posititon) 
-    St <- which.min(abs(x_grid - m_t)) 
-    q_t <- h_grid[D[St, (t + 1) ]] 
-    # Implement harvest/(effort) based on quota with noise 
-    h[t] <- q_t * z_i()
-    # Noise in growth 
-    z <- z_g() 
-    # population grows
-    x_h[t+1] <- z * f(x_h[t], h[t], pars) # with havest
-    s[t+1]   <- x_h[t] - q_t # anticipated escapement
-    x[t+1]   <- z * f(x[t], 0, pars) # havest-free dynamics
[…]

### 2012-12-27 R/SDP_uniform.R

@@ -1,108 +1,0 @@
-#' Determine the SDP matrix for uniform noise under multiple uncertainty
-#'
-#' Computes the transition matrix under the case of growth noise, 
-#' implementation errors in harvesting, and meaurement errors in 
-#' the stock assessment.  Assumes noise sources are distributed 
-#' by uniform distributions to obtain analytic transition probability densities.
-#'
-#' @param f the growth function of the escapement population (x-h)
-#'   should be a function of f(t, y, p), with parameters p
-#' @param p the parameters of the growth function
-#' @param x_grid the discrete values allowed for the population size, x
-#' @param h_grid the discrete values of harvest levels to optimize over
-#' @param sigma_g is the shape parameter (width) of the multiplicitive growth noise 
-#' @param pdfn is the shape of the growth noise, which need not be uniform (is by default)
-#' @param sigma_m is the half-width of the uniform measurement error (assumes uniform distribution)
-#' @param sigma_i is the half-width of the implementation noise (always assumes uniform distribution)
-#' @param f_int is the function given by the analytic solution,  
-#' @export
-SDP_uniform <- function(f, p, x_grid, h_grid, sigma_g,
-                        pdfn=function(P, s) dunif(P, 1-s, 1+s),
-                        sigma_m, sigma_i, f_int){
-  gridsize <- length(x_grid)
-  SDP_Mat <- lapply(h_grid, function(h){
-    SDP_matrix <- matrix(0, nrow=gridsize, ncol=gridsize)
-    # Cycle over x values
-    for(i in 1:gridsize){ 
-      ## Calculate the expected transition  
-      x1 <- x_grid[i]
-      x2_expected <- f_int(x1, h, sigma_m, sigma_i, p)
-      ## If expected 0, go to 0 with probabilty 1
-      if( x2_expected == 0) 
[…]

### 2012-12-27 R/determine_SDP_matrix.R

@@ -1,205 +1,0 @@
-# file determine_SDP_matrix.R 
-# author Carl Boettiger <cboettig@gmail.com>
-# date 2011-11-07
-# licence BSD
-# SDP solution adapted from SDP.m by Michael Bode
-# 
-# Contains three different functions for determining the 
-# Stochastic Transition Matrix used in the Dynamic Programming solution
-#
-
-
-#########################################################################
-# A function to generate the transition matrix used for the SDP routine #
-#########################################################################
-
-#' Determine the Stochastic Dynamic Programming matrix.
-#' @param f the growth function of the escapement population (x-h)
-#'   should be a function of f(t, y, p), with parameters p
-#' @param p the parameters of the growth function
-#' @param x_grid the discrete values allowed for the population size, x
-#' @param h_grid the discrete values of harvest levels to optimize over
-#' @param sigma_g the variance of the population growth process
-#' @param pdfn the probability density function, taking the proportional
-#' chance of a transition to that state, f(x), and the parameter sigma_g
-#' By default it will use the log normal density.  
-#' @return the transition matrix at each value of h in the grid. 
-#' @details this analytical approach doesn't reliably support other 
-#'  sources of variation.  The quality of the analytic approximations 
-#'  (lognormal) can be tested. 
-#' @export
-determine_SDP_matrix <- function(f, p, x_grid, h_grid, sigma_g,
-                                 pdfn=function(P, s) dlnorm(P, 0, s)){
-  gridsize <- length(x_grid)
-  SDP_Mat <- lapply(h_grid, function(h){
-    SDP_matrix <- matrix(0, nrow=gridsize, ncol=gridsize)
-    # Cycle over x values
-    for(i in 1:gridsize){ ## VECTORIZE ME
-      ## Calculate the expected transition  
-      x1 <- x_grid[i]
-      x2_expected <- f(x1, h, p)
-      ## If expected 0, go to 0 with probabilty 1
-      if( x2_expected == 0) 
-        SDP_matrix[i,1] <- 1  
-      else {
-        # relative probability of a transition to that state
-        ProportionalChance <- x_grid / x2_expected
[…]

### 2012-12-27 R/fig4_helper_fn.R

@@ -1,62 +1,0 @@
-
-#' @export
-fig4 <- function(fraction_lost, ...){
-closest <- function(x, v){
-  which.min(abs(v-x))
-}
-dt_npv <- data.table(fees)
-index <- dt_npv[,closest(fraction_lost, (npv0-value)/npv0), by=variable]
-apples_index <- index$V1
-names(apples_index) = index$variable
-apples <- c2[index$V1]
-names(apples) = index$variable
-
-L2_policy <- policies$L2[[apples_index["L2"]]]$D
-L1_policy <- policies$L1[[apples_index["L1"]]]$D
-fixed_policy <- policies$fixed[[apples_index["fixed"]]]$D
-free_increase_policy <- policies$free_increase[[apples_index["free_increase"]]]$D
-free_decrease_policy <- policies$free_decrease[[apples_index["free_decrease"]]]$D
-quad_policy <- policies$quad[[apples_index["quad"]]]$D
-
-quad_profit <- profit_harvest(price = price, c0 = c0, c1 = apples["quad"]) 
-sims <- lapply(1:50, function(reps) list(
-  L1 = simulate_optim(f, pars, x_grid, h_grid, x0, 
-                      L1_policy, z_g, z_m, z_i, 
-                      opt$D, profit=profit, penalty=L1(apples["L1"])), 
-  L2 = simulate_optim(f, pars, x_grid, h_grid, x0, 
-                      L2_policy, z_g, z_m, z_i, 
-                      opt$D, profit=profit, penalty=L2(apples["L2"])),
-  fixed = simulate_optim(f, pars, x_grid, h_grid, x0, 
-                         fixed_policy, z_g, z_m, z_i, 
-                         opt$D, profit=profit, penalty=fixed(apples["fixed"])),
-  increase = simulate_optim(f, pars, x_grid, h_grid, x0, 
-                            free_increase_policy, z_g, z_m, z_i, 
-                            opt$D, profit=profit, penalty= free_increase(apples["increase"])),
-  decrease = simulate_optim(f, pars, x_grid, h_grid, x0, 
-                            free_decrease_policy, z_g, z_m, z_i, 
-                            opt$D, profit=profit, penalty= free_decrease(apples["decrease"])),
-  quad = simulate_optim(f, pars, x_grid, h_grid, x0, 
[…]

### 2012-12-27 R/find_dp_cautious.R

@@ -1,70 +1,0 @@
-
-#' Identify the best policy which harvests at P percent of optimum harvest
-#' @param SDP_Mat the stochastic transition matrix at each h value
-#' @param x_grid the discrete values allowed for the population size, x
-#' @param h_grid the discrete values of harvest levels to optimize over
-#' @param OptTime the stopping time 
-#' @param xT the boundary condition population size at OptTime
-#' @param c the cost/profit function, a function of harvested level
-#' @param delta the exponential discounting rate
-#' @param reward  the profit for finishing with >= Xt fish at the end 
-#' (i.e. enforces the boundary condition)
-#' @param P fraction of optimal harvest to use as the policy.  
-#' @return list containing the matrices D and V.  D is an x_grid by OptTime
-#'  matrix with the indices of h_grid giving the optimal h at each value x
-#'  as the columns, with a column for each time.  
-#'  V is a matrix of x_grid by x_grid, which is used to store the value 
-#'  function at each point along the grid at each point in time.  
-#'  The returned V gives the value matrix at the first (last) time. 
-#' @export
-find_dp_cautious <- function(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, 
-                          delta, reward=0, P=1){
-
- 
-  ## Initialize space for the matrices
-  gridsize <- length(x_grid)
-  HL <- length(h_grid)
-  D <- matrix(NA, nrow=gridsize, ncol=OptTime)
-  V <- rep(0,gridsize) # initialize BC,
-
-  ## give a fixed reward for having value larger than xT at the end. 
-  V[x_grid >= xT] <- reward # a "scrap value" for x(T) >= xT
-
-  ## loop through time  
-  for(time in 1:OptTime){ 
-    ## try all potential havest rates
-    V1 <- sapply(1:HL, function(i){
-      ## Transition matrix times V gives dist in next time
-      SDP_Mat[[i]] %*% V + 
-      ## then (add) harvested amount times discount
-       profit(x_grid, h_grid[i]) * (1 - delta) 
-    })
-
-    ## find havest, h that gives the maximum value
-    out <- sapply(1:gridsize, function(j){
-      
-      ## Optimal harvest solution is:
-      best_index <- which.max(V1[j,])  
-
-      ## Set policy to harvest level closest to fraction P of optimal harvest
-      index <- which.min(abs(h_grid -  P * h_grid[best_index]))
[…]

### 2012-12-27 R/find_dp_optim.R

@@ -1,68 +1,0 @@
-########################################################################
-# A function to identify the dynamic optimum using backward iteration  #
-########################################################################
-
-#' Identify the dynamic optimum using backward iteration (dynamic programming)
-#' @param SDP_Mat the stochastic transition matrix at each h value
-#' @param x_grid the discrete values allowed for the population size, x
-#' @param h_grid the discrete values of harvest levels to optimize over
-#' @param OptTime the stopping time 
-#' @param xT the boundary condition population size at OptTime
-#' @param c the cost/profit function, a function of harvested level
-#' @param delta the exponential discounting rate
-#' @param reward  the profit for finishing with >= Xt fish at the end 
-#' (i.e. enforces the boundary condition)
-#' @return list containing the matrices D and V.  D is an x_grid by OptTime
-#'  matrix with the indices of h_grid giving the optimal h at each value x
-#'  as the columns, with a column for each time.  
-#'  V is a matrix of x_grid by x_grid, which is used to store the value 
-#'  function at each point along the grid at each point in time.  
-#'  The returned V gives the value matrix at the first (last) time. 
-#' @export
-find_dp_optim <- function(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, 
-                          delta, reward=0){
-
- 
-  ## Initialize space for the matrices
-  gridsize <- length(x_grid)
-  HL <- length(h_grid)
-  D <- matrix(NA, nrow=gridsize, ncol=OptTime)
-  V <- rep(0,gridsize) # initialize BC,
-
-  # give a fixed reward for having value larger than xT at the end. 
-  V[x_grid >= xT] <- reward # a "scrap value" for x(T) >= xT
-
-  # loop through time  
-  for(time in 1:OptTime){ 
-    # try all potential havest rates
-    V1 <- sapply(1:HL, function(i){
-      # Transition matrix times V gives dist in next time
-      SDP_Mat[[i]] %*% V + 
-      # then (add) harvested amount times discount
-       profit(x_grid, h_grid[i]) * (1 - delta) 
-    })
-
-    # find havest, h that gives the maximum value
-    out <- sapply(1:gridsize, function(j){
-      value <- max(V1[j,], na.rm = T) # each col is a diff h, max over these
-      index <- which.max(V1[j,])  # store index so we can recover h's 
-      c(value, index) # returns both profit value & index of optimal h.  
-    })
-
[…]

### 2012-12-27 R/multiple_uncertainty.R

@@ -17,13 +17,12 @@
 #' Values of D[,t] correspond to the index of h_grid.  Indices of of D[,t] correspond to states in y_grid.  
 #' @export
 SDP_multiple_uncertainty <- function(f, p, x_grid, h_grid, Tmax = 25,
-                                     sigmas =c(sigma_g=0, sigma_m=0, sigma_i=0), 
+                                     sigmas =c(sigma_g=0.3, sigma_m=0, sigma_i=0), 
                                      pdfn = pdfn, profit = function(x,h) pmin(x, h)){
   
-    ## Initialize stuff
-    sigma_g <- sigmas['sigma_g']      
-    sigma_m <- sigmas['sigma_m']
-    sigma_i <- sigmas['sigma_i']
+    sigma_g <- sigmas[1]      
+    sigma_m <- sigmas[2]
+    sigma_i <- sigmas[3]
     n_x <- length(x_grid)
     n_h <- length(h_grid)
     D <- matrix(NA, nrow=n_x, ncol=Tmax)  
@@ -31,34 +30,47 @@ SDP_multiple_uncertainty <- function(f, p, x_grid, h_grid, Tmax = 25,
     ## Compute the transition matrices 
     P <-  outer(x_grid, h_grid, profit) 
     M <- rownorm( outer(x_grid, x_grid, pdfn, sigma_m) )
-    I <- rownorm( outer(h_grid, h_grid, pdfn, sigma_i) )
+    I <- rownorm( outer(h_grid, h_grid, pdfn, sigma_i) )  
     
-    # integrate over uncertainty in I and X 
+
+    
+    # Much faster to fill out f calls as a matrix ahead of time.  
+    f_matrix <- outer(x_grid, h_grid, f, p)
+    # Fill out uncertainty in transitions first
+    G <- outer(x_grid, x_grid, pdfn, sigma_g)
+    
     F <- lapply(1:n_h, function(q){  
       t(sapply(1:n_x, function(y){
         out <- numeric(n_x)
-        mu <- sum(sapply(1:n_x, function(x)
-          f(x_grid[x],h_grid,p) %*% 
-            I[q,] *  # Implementation error
-            M[x,y])) # Measurement error
-        if(mu==0)
-          out[1] <- 1
-        else 
-          out <- dlnorm(x_grid/mu, 0, sigma_g)
+        mu <- M[y,] %*% f_matrix %*% I[q,] 
+        # Handle special cases
+        if(snap_to_grid(mu,x_grid)==0){ # 
[…]

### 2012-12-27 R/plots.R

@@ -1,83 +1,0 @@
-#' Show the ensemble fishstock and harvest dynamics
-#' @param sims simulation results
-#' @param S Reed's S, from opt$S, where opt <- find_dp_optim(...)
-#' @param allee the allee threshold (defaults to 0)
-#' @param fish_reps logical - show replicate trajectories of fish stocks?
-#' @param fish_sd logical - show ribbon of SD of fishstock?
-#' @param fish_mean logical - show mean fishstock?
-#' @param harvest - include harvest level on the same plot?
-#' @param harvest_reps - show individual reps for harvest?
-#' @param harvest_mean - show mean harvest level over time?
-#' @param harvest_sd - show harvest SD
-#' @param crash_count - count the number of reps that have fallen below allee
-#' @return a ggplot object (display with print(object)) 
-#' @details if line values for any S, allee, e_star are not specified 
-#' then these are omitted from the plot.
-#' @import ggplot2
-#' @import reshape2
-#' @import Hmisc
-#' @export 
-plot_replicates <- function(sims, S = NULL, allee = 0, e_star = NULL,
-                            fish_reps = TRUE, fish_sd = TRUE, 
-                            fish_mean = TRUE, harvest = TRUE, 
-                            harvest_reps = TRUE, harvest_mean = TRUE,
-                            harvest_sd = TRUE, crash_count=TRUE){
-
-  require(ggplot2)
-
-  ## Should rewrite this to be act like a proper ggplot2 extension 
-
-  dat <- melt(sims, id="time") # reshapes the data matrix to "long" form
-  dat <<- dat
-  # some stats on the replicates, (stat_sumary can do this instead)
-  m <- dcast(dat, time ~ variable, mean) # mean population
-  m <<- m
-  err <- dcast(dat, time ~ variable, sd) # sd population
-  err <<- err
-  
-  ## Create the ggplot object with this data
-  p1 <- ggplot(dat) 
-
-  ## Add the layers requested 
-  if(fish_reps) # Replicate harvested dynamics
-    p1 <- p1+ geom_line(aes(time, value, group = L1), data = 
-                  subset(dat, variable == "fishstock"), alpha = 0.2)
-  if(fish_sd) 
-    p1 <- p1 + geom_ribbon(aes(x = time, 
-                           ymin = m$fishstock - err$fishstock,
-                           ymax = m$fishstock + err$fishstock),
[…]

### 2012-12-27 R/policy_costs.R

@@ -1,181 +1,0 @@
-## Modified optimization and simulation techniques that allow for a cost to policy 
-
-#' Optimum policy when changing harvest level has an adjustment cost
-#' 
-#' Identify the dynamic optimum using backward iteration (dynamic programming)
-#' @param SDP_Mat the stochastic transition matrix at each h value
-#' @param x_grid the discrete values allowed for the population size, x
-#' @param h_grid the discrete values of harvest levels to optimize over
-#' @param OptTime the stopping time 
-#' @param xT the boundary condition population size at OptTime
-#' @param c the cost/profit function, a function of harvested level
-#' @param delta the exponential discounting rate
-#' @param reward the profit for finishing with >= Xt fish at the end 
-#' (i.e. enforces the boundary condition)
-#' @param penalty the kind of penalty applied: currently L1, L2, or assymetric
-#' @return list containing the matrices D and V.  D is an x_grid by OptTime
-#'  matrix with the indices of h_grid giving the optimal h at each value x
-#'  as the columns, with a column for each time.  
-#'  V is a matrix of x_grid by x_grid, which is used to store the value 
-#'  function at each point along the grid at each point in time.  
-#'  The returned V gives the value matrix at the first (last) time. 
-#' @import expm
-#' @export
-optim_policy <- function(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, 
-                          delta, reward=0, penalty, effort_penalty=function(x,h) 0){
-           
-  ## Initialize space for the matrices
-  gridsize <- length(x_grid)
-  HL <- length(h_grid)
-  D <- lapply(1:HL, function(i) matrix(NA, nrow=gridsize, ncol=OptTime))
-  V <- sapply(1:HL, function(i){ 
-    Vi <- rep(0,gridsize)  
-    # give a fixed reward for having value larger than xT at the end. 
-    Vi[x_grid >= xT] <- reward # a "scrap value" for x(T) >= xT
-    Vi
-  })
-  
-  penalty_free_V <- V
-
-  profit_matrix <- sapply(h_grid, function(h) profit(x_grid, h))
-  penalty_matrix <- sapply(h_grid, function(h) 
-                           sapply(h_grid, function(h_prev) penalty(h, h_prev)))
-
-  quadratic_penalty <- 
[…]

### 2012-12-27 R/population_models.R

@@ -1,209 +1,0 @@
-# file population_models.R
-# author Carl Boettiger <cboettig@gmail.com>
-# date 2011-11-16
-# license BSD
-# common population dynamics models with fishing
-
-
-
-################################################################
-# Library of some possible population dynamics state equations #
-################################################################
-
-
-# temporal variation in f is possible, but increases the memory required, 
-# though not the time for the optimization(?)
-
-#' Harvested Beverton Holt growth model
-#' @param x fish population 
-#' @param h havest level
-#' @param p parameters of the growth function, c(A, B), where
-#'  A is the maximum growth rate and B the half-maximum in Beverton-Holt.  
-#' @return population next year
-#' @details Harvesting takes place before reproduction in ths model.
-#'  The carrying capacity is K <- (pars[1]-1)/pars[2]
-#'  Try with pars <- c(2,4)
-#' @export
-BevHolt <- function(x, h, p){
-  x <- max(0, x - h)
-  A <- p[1] 
-  B <- p[2] 
-  sapply(x, function(x){ # use sapply so fn accepts vector-valued x
-    x <- max(0, x)
-    max(0, A * x/(1 + B * x))
-  })
-}
-
-
-
-
-#' Beverton Holt growth model with fishing-effort based control
-#' @param x fish population 
-#' @param h fishing effort (harvest is effort times fish population)
-#' @param p parameters of the growth function, c(A, B), where
-#'  A is the maximum growth rate and B the half-maximum in Beverton-Holt.  
-#' @return population next year
-#' @details Harvesting takes place before reproduction in ths model.
-#'  The carrying capacity is K <- (pars[1]-1)/pars[2]
-#'  Try with pars <- c(2,4)
-#' @export
-BevHolt_effort <- function(x, h, p){
-  S <- max(0, x - x*h) # Escapement from harvest
-  A <- p[1] 
-  B <- p[2] 
-  sapply(S, function(x){ # use sapply so fn accepts vector-valued x
-    x <- max(0, x)
[…]

### 2012-12-27 R/profit_functions.R

@@ -1,37 +1,0 @@
-#' Define a profit function, price minus cost
-#' @param price market price (Note, optimal will scrap xT if price is
-#' high enough!) 
-#' @param cost_stock_effect fishing extraction costs (per unit effort)
-#' @param operating_cost costs of having a given harvest level (must
-#' be less than price) 
-##' @return a function computing profit at effort intensity h_i over
-#' possible stock values x_grid, profit(x_grid, h_i)
-#' @export
-profit_effort <-  function(price = 1, c0 = .1, c1 = 0.0){
-    function(x_grid, e_i){ 
-      sapply(x_grid, function(x_i){
-        price * min(e_i * x_i, x_i) -  (c0 + c1 * e_i ) * e_i
-    })
-  }
-}
-
-#' Define a profit function, price minus cost
-#' @param price market price (Note, optimal will scrap xT if price is
-#' high enough!) 
-#' @param c0 Cost, linear with effort (cost = (c0 + c1*E)*E
-#' @param c1 Cost, quadratic with effort (cost = (c0 + c1*E)*E
-#' @return a function computing profit at harvest intensity h_i over
-#' possible stock values x_grid, profit(x_grid, h_i)
-#' @export
-profit_harvest  <- function(price = 1, c0 = .1, c1 = 0.0){
-  function(x_grid, h_i){
-    sapply(x_grid, function(x_i){
-      effort <- h_i / (x_i + 1e-12) 
-      price * min(h_i, x_i) -  (c0 + c1 * effort ) * effort
-      # 1e-12 to avoid NaNs at zero stock condition
-    })
-  }
-}
-
-
-

### 2012-12-27 inst/examples/figure3.sh

@@ -1,17 +1,0 @@
-## Use the current working directory
-#$ -cwd
-## use bash commands
-#$ -S /bin/bash
-## combine error and output files
-#$ -j y
-## Parallel for MPI
-##$ -pe mpi 20 
-## Parallel for openmp:
-#$ -pe threaded 16
-## Output file name
-#$ -o figure3.log
-
-module load gcc openmpi R 
-Rscript -e "source('~/.Rprofile'); library('knitr'); knit('figure3.Rmd')" 
-
-

### 2013-04-08 inst/examples/Reed.Rmd
add value iteration termination to package functions, example shown in Reed.md

@@
 ``` {r  echo=FALSE, cache=FALSE}
-#opts_knit$set(upload.fun = socialR::flickr.url)
-#options(device = function(width = 5, height = 5) {
-#    pdf(NULL, width = width, height = height)
-#})
-knitcitations::cleanbib()
+opts_knit$set(upload.fun = socialR::flickr.url)
 ````
@@
 }
-
 ````
 
-With parameters `K` = `r K <- 100` and `r` = `r r <- 1`.
-
 ``` {r }
+r <- 1
+K <- 100
 pars <- c(r, K)
 ````
+
+With parameters `K` = `r K` and `r` = `r r`.
 
@@
 
+Stationary optimal policy:
+
+``` {r value_iteration }
+s_opt <- value_iteration(SDP_Mat, x_grid, h_grid, OptTime=1000, xT, profit, delta)
+````
+
 ## Compare to Clark (noise-free)
@@
 require(reshape2)
-policies <- melt(data.frame(stock=x_grid, S = x_grid[opt$D[,1]], D = x_grid[det$D[,1]]), id="stock")
-q1 <- ggplot(policies, aes(stock, stock - value, color=variable)) + geom_point() + xlab("stock size") + ylab("escapement") 
+policies <- melt(data.frame(stock=x_grid, S = x_grid[opt$D[,1]], D = x_grid[det$D[,1]], Stationary = x_grid[s_opt$D]), id="stock")
+q1 <- ggplot(policies, aes(stock, stock - value, color=variable)) + geom_point(alpha=.5) + xlab("stock size") + ylab("escapement") 
 q1

### 2013-04-08 R/find_dp_optim.R

@@ -1,7 +1,6 @@
 ########################################################################
 # A function to identify the dynamic optimum using backward iteration  #
-########################################################################
-
+#
 #' Identify the dynamic optimum using backward iteration (dynamic programming)
 #' @param SDP_Mat the stochastic transition matrix at each h value
 #' @param x_grid the discrete values allowed for the population size, x
@@ -59,6 +58,74 @@ find_dp_optim <- function(SDP_Mat, x_grid, h_grid, OptTime, xT, profit,
   # Reed derives a const escapement policy saying to fish the pop down to
   # the largest population for which you shouldn't harvest: 
   ReedThreshold <- x_grid[max(which(D[,1] == 1))]
+
+  # Format the output 
+  list(D=D, V=V, S=ReedThreshold)
+}
+#######################################################################
+
+#' Identify the dynamic optimum using backward iteration (dynamic programming)
+#' @param SDP_Mat the stochastic transition matrix at each h value
+#' @param x_grid the discrete values allowed for the population size, x
+#' @param h_grid the discrete values of harvest levels to optimize over
+#' @param OptTime the stopping time 
+#' @param xT the boundary condition population size at OptTime
+#' @param c the cost/profit function, a function of harvested level
+#' @param delta the discounting rate (1-delta)
+#' @param epsilon value iteration tolerance
+
+#' (i.e. enforces the boundary condition)
+#' @return list containing the matrices D and V.  D is an x_grid by OptTime
+#'  matrix with the indices of h_grid giving the optimal h at each value x
+#'  as the columns, with a column for each time.  
+#'  V is a matrix of x_grid by x_grid, which is used to store the value 
+#'  function at each point along the grid at each point in time.  
+#'  The returned V gives the value matrix at the first (last) time. 
+#' @export
+value_iteration <- function(SDP_Mat, x_grid, h_grid, OptTime=100, xT, profit, 
+                          delta, epsilon = 1e-4){
+
+ 
+  ## Initialize space for the matrices
+  gridsize <- length(x_grid)
+  HL <- length(h_grid)
+  D <- matrix(NA, nrow=gridsize, ncol=1)
+  V <- rep(0,gridsize) # initialize BC,
+  Vp <- rep(10, gridsize) # initialize previous value (not equal to current value)
+
+  # loop through time  
+  #for(time in 1:OptTime){
+  time <- 1
[…]

### 2013-05-01 inst/examples/Reed.Rmd
parameter uncertainty SDP methods added

@@
 ``` {r }
-f <- function (x, h, p) 
-{
- sapply(x, function(x){
-  	S = max(x - h, 0)
-  	p[1] * S * (1 - S/p[2]) + S
-  })
-}
+f <- RickerAllee
+K <- 10
+pars <- c(2, K, 5)
 ````
-
-``` {r }
-r <- 1
-K <- 100
-pars <- c(r, K)
-````
-
-With parameters `K` = `r K` and `r` = `r r`.
 
@@
 ``` {r  SDP_Mat}
-SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
+p <- c(.2,7.5,5)
+SDP_Mat <- determine_SDP_matrix(f, p, x_grid, h_grid, sigma_g, pdfn)
 ````
@@
 opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
+opt$S
 ````

### 2013-05-01 R/parameter_uncertainty_SDP.R

@@ -1,0 +1,43 @@
+#' Computes the transition matrix under the case of parametric uncertainty
+#'
+#' @param f the growth function of the escapement population (x-h)
+#'   should be a function of f(t, y, p), with parameters p
+#' @param p the parameters of the growth function
+#' @param x_grid the discrete values allowed for the population size, x
+#' @param h_grid the discrete values of harvest levels to optimize over
+#' @param pardist a matrix with columns as variables and rows as the 
+#' Monte Carlo samples from the posterior
+#' @export
+#' #FIXME: pardist should be in "long" format of par_posterior, allow for variable parameter numbers
+parameter_uncertainty_SDP <- function(f, p, x_grid, h_grid, pardist, n_mc = 100){
+  lapply(h_grid, function(h){ # for each h
+    # Set up monte carlo sampling 
+    d <- dim(pardist)
+    indices <- round(runif(n_mc,1, d[1]))
+    # Compute the transition matrix
+    F_true <- 
+      sapply(x_grid, function(x_t){           # For each x_t  
+        bypar <- sapply(indices, function(i){ # For each parameter value
+          p <- unname(pardist[i,c(2,1,3)])    # Parameters for the mean, at current sample 
+          mu <- f(x_t,h,p)                    # expected x_{t+1} 
+          est_sigma_g <- pardist[i,4]         # Variance parameter         
+          # Calculate the probability density
+          if(snap_to_grid(mu,x_grid) < x_grid[2]){ # handle the degenerate case 
+            out <- numeric(length(x_grid))
+            out[1] <- 1
+            out
+          } else { # Calculate the transition density based on log-normal
+            # FIXME handle normally distributed measurement error additionally 
+            out <- dlnorm(x_grid/mu, 0, est_sigma_g) 
+          }
+        })  
+        # Average over parameter distributions and normalize
+        ave_over_pars <- apply(bypar, 1, sum) 
+        ave_over_pars / sum(ave_over_pars)
+      })
+    F_true <- t(F_true)
+  })
+}
+
+
+snap_to_grid <- function(x, grid) sapply(x, function(x) grid[which.min(abs(grid - x))])   

### 2013-05-13 inst/doc/policycosts/policycosts_PRA.tex
Tex version with comments from Paul

--- 2012-12-04 inst/doc/policycosts/policycosts.tex
@@
 \bibliographystyle{elsarticle-harv}
-%\usepackage{natbib} % already loaded by elsarticle
-%\biboptions{sort&compress} % For natbib
-%\usepackage{hyperref} % already loaded by elsarticle
-%\hypersetup{breaklinks=true, pdfborder={0 0 0}}
+\usepackage{natbib} % already loaded by elsarticle
+\biboptions{sort&compress} % For natbib
+\usepackage{hyperref} % already loaded by elsarticle
+\hypersetup{breaklinks=true, pdfborder={0 0 0}}
 
-\usepackage[hyphens]{url}
+%\usepackage[hyphens]{url}
 
@@
 \usepackage[pdftex, usenames]{color}
+\definecolor{darkred}{rgb}{0.5,0,0}
 \definecolor{darkblue}{rgb}{0,0,0.5}
@@
 \newcommand{\pa}[1]{{\it \color{darkblue} #1}}
+\newcommand{\jr}[1]{{\it \color{darkred} #1}}
 
@@
 \begin{frontmatter}
-\title{Policy Costs}
+\title{Policy Costs \\ \pa{
+Target Journals: Ecological Applications, Journal of Applied Ecology, some discussion of whether scope for PNAS}}
 \author[cpb]{C. Boettiger\corref{cor1}}
@@
 \author[melbourne]{M. Bode}
-\author[esp]{J. Sanchirico}
-\author[utk-econ]{J. LaRiviera}
-\author[cpb,esp]{A. Hastings}
-\author[utk-eeb]{P. Armsworth}
-\cortext[cor1]{Corresponding author}
+\author[esp]{J. N. Sanchirico}
+\author[utk-econ]{J. LaRiviere}
+\author[cpb,esp]{A.M. Hastings}
+\author[utk-eeb]{P. R Armsworth}
+\cortext[cor1]{Corresponding author, present address: XXX}
 \address[cpb]{Center for Population Biology, University of California, Davis, California 95616, USA}
+\address[melbourne]{Australian Research Council Centre of Excellence for Environmental Decisions, University of Melbourne, School of Botany,
+Parkville, Melbourne, VIC 3010, Australia}
 \address[esp]{Department of Environmental Science \& Policy, University of California, Davis, CA 95616, USA}
@@
 \address[utk-eeb]{Department of Ecology and Evolutionary Biology, University of Tennessee, Knoxville, TN 37996, USA}
-\address[melbourne]{Australian Research Council Centre of Excellence for Environmental Decisions, University of Melbourne, School of Botany,
-Parkville, Melbourne, VIC 3010, Australia}
 
 \begin{abstract}
-\cdb{Carl's comments \& questions added in green}
+\cdb{Carl's comments \& questions added in green} \\
+\pa{Paul's comments \& questions added in blue} \\
+\jr{Jake's comments \& questions added in red}
 \end{abstract}
@@
 
-(See Figure~\ref{fig:1} which motivates the importance of considering policy costs by comparing a theoretically optimal policy over time to a typical real world policy over time).
+(See Figure~\ref{fig:1} which motivates the importance of considering policy costs by comparing a theoretically optimal policy over time to a typical real world policy over time.
+Possible candidates - bluefin tuna vs.
+halibut comparison to show variation).
 
@@
 
+\pa{
+ Problem description resolved in Meeting 3 - note the list of possible causal mechanisms here (reaching agreement to processor plants) was negotiated with some not being acceptable suggestions:
+
+ Empirics suggest not always as responsive as Reed solution.
+Explore conditions under which that makes sense.
+Idea is that regulator’s objective sometimes may not be `raw' NPV, but rather NPV with some penalties on fast changes.
+Possible reasons pure administrative transaction cost of changing policies (reaching agreement), fishermens' preferences for less variable quotas, processing plants' preferences for less variable quotas especially if tied into contracts for canning and so forth.
+But we do not know what the functional form is and will be a lot of work to estimate it.
+Here we explore several plausible candidates that each reflect different ways these costs could work.
+Would be good to know if differences between functional forms is particularly important.
+}
+
 \subsection{Types of real world policy costs}
@@
 
-\begin{itemize}
-  \item   Fish population dynamics / state equation.  We will assume Beverton-Holt dynamics,
+  Fish population dynamics / state equation.  We will assume Beverton-Holt dynamics,
     \begin{equation} 
@@
 
-\item   Fishing profit function 
+\pa{
+
+Resolved in Meeting 3: Base case for all analyses $ph-c_0E$ where $h=qEx$ and $c_0>0$.
+
+Resolved in Meeting 3: The economic smoothing formulation: $ph - (c_0 E+c_4 E^2)$ will ONLY appear in SI with some figures for comparison. We do not make a big play out of comparing one with the other
+}
+
 \begin{equation} 
@@
 \end{equation}
+
 where $h$ is the harvest level, $x$ the stock size, $h/x$ represents
@@
 introduces a quadratic cost to effort, a typical way to introduce
-  smoothing~\citep[\emph{e.g.}][]{Singh2006}.  For simplicity, we will consider $c_0 =
-  c_1 = 0$.
+smoothing~\citep[\emph{e.g.}][]{Singh2006}.  For simplicity, we will consider $c_0 = c_1 = 0$.
 
-\item
 Policy cost function: L1, L2, fixed fee, asymmetric, are introduced
@@
 
+\pa{
+Resolved in Meeting 3: We will only do comparisons described last time as $L_1$, $L_2$ and fixed.
+They have new and more descriptive names now.
+$c_0>0$ in all comparisons please.
+We do not present the asymmetric comparison.
+
+Resolved in Meeting 3: penalties to apply to h(t) NOT E(t)
+}
+
   \begin{align} 
@@
 
-\item   Economic discounting, boundary conditions, constraints, Bellman equation, SDP solution method on finite time horizon.  
-\item   Choice of model parameters 
-\end{itemize}
+ Economic discounting, boundary conditions, constraints, Bellman equation, SDP solution method on finite time horizon.
+
+Choice of model parameters
+
+\pa{
+  Suggested from Meeting 3:
+
+ Give them more meaningful names.   we suggested
+
+$L_1$ - Variable cost with extent of policy change, case 1 / linear
+
+$L_2$ - Variable cost with extent of policy change, case 2 / quadratic
+
+fixed -  Fixed cost associated with any policy change
+
+ My own suggestion is that rather than calling ALL of the relevant parameters $c_2$, that you than call them $c_1$, $c_2$, $c_3$ and when seeking to refer to them collectively you call them $c_i$
+
+ That is why the suggested parameter on $E^2$ penalties for the SI was $c_4$  This section needs also to introduce the NPV function including discounting.
+We also resolved in Meeting 3 that we should use a positive discount rate.
+}
 
@@
 
-% From Jake:
+\jr{
 
+Resolved in meeting 3.
+
+Let $h_0^*$ be the optimal control path for the base case $\Pi_0$ version of the NPV function, $NPV_0$.
+
+Let $h_i^*$ be the optimal control path for one comparator case $\Pi_i$ version of the NPV function, $NPV_i$, e.g. $\Pi_i$ might now be what we called the L1 penalty.
+
+Then our independent variable in Fig. 4 for example is the fraction: $1 - NPV_i(h_i^*) / NPV_0(h_0^*)$
+
+By solving that and using the approach outlined in Figure 2, we obtain the $c_i$ value that we use for a given comparison.
+
+Given what is shown in Figure 2, we should make the focal range of fraction be 0-30\% of the $NPV_0(h_0^*)$ value to avoid a blow-up on $c_i$ for some penalty function forms
+
+Resolved in Meeting 3: we would do this instead of a dimensionality argument OR trying to calibrate on costs arising only from induced changes to controls.
+}
+
+\jr{
 The fact that there is no uniform metric for comparing different functional forms of the penalty function complicates identifying the implications of various penalty functions on optimal management.
@@
 
+}
 %% end-Jake
@@
 
+\pa{ 
+  Figure 3 stays largely as is.  But we also need to see the corresponding x trajectories in a way that makes for easy comparisons but not cluttered axes
+}
+
 \subsection{Responses to increasing costs}
+
+\pa{ 
+ A version of Figure 4 to go in.
+But limit the range of the fraction on the horizontal axis more.
+We need to see the corresponding variance and autocorrelation for x as well as h.
+Also suggested we might want a panel showing cross-correlation statistic as well x to h variation although depending on what it shows it could perhaps go to SI.
+}
 
@@
 \cdb{Add additional plot: Is value a linear function of policy cost, or is there a sharp transition? }
-%Must be nonlinear somewhere when adjustment costs exceed profits?
+\pa{ Must be nonlinear somewhere when adjustment costs exceed profits? }
 
@@
 
-  We include a version of the results Carl currently shows in his Fig 5 and 6 for the L1 penalty, but we include it also for the other penalty function forms – e.g.
+  We include a version of the results Carl currently shows in his Fig 5 and 6 for the L1 penalty, but we include it also for the other penalty function forms - e.g.
 using Carl’s suggestion of a box-whisker plot.
@@
 Fig 6 combines the two bits to show the effect on net present value.
+Distribution of profits and costs under a policy-cost scenario vs profits and costs under Reed solution, by penalty type.
+Figure~\ref{fig:profits_costs}.
+}
+
+\begin{figure}
+  \begin{center}
+    \subfigure[L1]{\includegraphics[width=.45\textwidth]{figure/7751440758_99645d6e5a_o.png}\label{fig:L1cost}}
+    \caption{Ignoring the cost of policy adjustment results in greater profits from fishing, but even greater costs for adjusting the harvest quotas each year.
+Costs and profits are shown for ignoring the adjustment costs (Reed solution, purple and blue) and accounting for the adjustment (green and red).
+\cdb{Though only L1 shown for the moment, would probably show all four types.
+Possibly a table or box-and-whiskers style plot would be better?}}\label{fig:profits_costs}
+  \end{center}
+\end{figure}
+
+\pa{ Keep Figure 5 or its equivalent for one penalty function formulation and talk through what it means and how to interpret it.
+
+Underneath lay out
+
+$$ NPV_i(h_{it}^*) = \sum \frac{p h^*_{it}-c_0E^*_{it}-c(h^*_{it})}{(1+\delta)^t} $$
+
+ALL MINUS
+
+$$ NPV_i(h_{0t}^*) = \sum \frac{p h^*_{0t}-c_0E^*_{0t}-c(h^*_{0t})}{(1+\delta)^t} $$
+
+}
+
+\pa{
+
+ Use labelling on the equations to label:
+
+$p h^*_{it}-c_0E^*_{it} $  as contribution (1 - red in Figure 5)
+and $c(h^*_{it})$ as contribution (3 - green in Figure 5) in the first expression
+
+ and then
+
+$p h^*_{0t}-c_0E^*_{0t}$ as contribution (2 - blue )
+$c(h^*_{0t}$ as contribution (4 - mauve) in the second expression
+
+Then cost of assuming penalties when they are not actually there, i.e.
+induced cost of controls is (2) - (1),  blue - red cost of assuming no penalties when they are present is [1-3] - [2-4].
+Finally tabulate separately for each of $\Pi_1$, $\Pi_2$, $\Pi_3$
+
+rows: $\sigma_{\epsilon}$ low, medium, high
+
+columns: $c_i$ values corresponding to fraction NPV or 90\%, 80\%, 70\%
+
+Cells: (2)-(1) AND [1-3]-[2-4] all divided by $NPV_0(h^*_{0t})$ to make them dimensionless
+
+(alternatively just draw three versions of Fig. 5 if not much is going on as we scope parameter space in this way.)
 
@@
 
-  I don’t know if those are clear – you need to get mired into the document once again a bit to parse it out. I’ll happily discuss with anyone in a bid to shed more light.
+  I don't know if those are clear – you need to get mired into the document once again a bit to parse it out. I’ll happily discuss with anyone in a bid to shed more light.
 
@@
 \end{itemize}
-
-\begin{figure}
-  \begin{center}
-    \subfigure[L1]{\includegraphics[width=.45\textwidth]{figure/7751440758_99645d6e5a_o.png}\label{fig:L1cost}}
-    \caption{Ignoring the cost of policy adjustment results in greater profits from fishing, but even greater costs for adjusting the harvest quotas each year.
-Costs and profits are shown for ignoring the adjustment costs (Reed solution, purple and blue) and accounting for the adjustment (green and red).
-\cdb{Though only L1 shown for the moment, would probably show all four types.
-Possibly a table or box-and-whiskers style plot would be better?}}\label{fig:profits_costs}
-  \end{center}
-\end{figure}
 
@@
 \begin{itemize}
-\item   Comparison of the optimal policy solution to the Reed model
+\item From Meeting 3: Interest in how the inclusion of these costs would operationally put a population at greater risk of extinction (e.g.
+if including the transaction costs increases the variance and autocorrelation of N when subject to the optimal policy).
+Should expect this, because (AH) as the transaction costs become infinite, you would never change your policy which puts you in the world of open loop control; TAC fixed for all time, which we know puts the stock at greater risk of extinction.
+\item Alan on the Table looking at the impacts of $\sigma_{\epsilon}$ should flag that might also be good to look at autocorrelated environmental noise and how that affects thing.
+Here we look at how the optimal policy induces more color in the stock size EVEN though the environmental variability going into it is white noise.
+\item (JL) Interpreting  (1), (2), (3), and (4) in terms of how much you would have available to pay the Japanese and Canadians to convince them to participate in an expedited process to change TACs.
+\item   Comparison of the optimal policy solution to the Reed model, traditional economic smoothing penalty - which now appears in SI
 \item  Comparison between the different functional forms -- smoothing (L2)
@@
 \item   Induced costs (relative to free adjustment) vs direct costs (paid for adjusting) 
-\item   Impact of symmetric vs asymmetric costs
+%\item   Impact of symmetric vs asymmetric costs
 \item   Contrast steady-state results to dynamic solutions under stochastic shocks.

### 2013-05-17 inst/examples/policycosts/writeup.Rmd
Working out the Apples-to-Apples case based on total costs, #35

@@
-``` {r libraries, include=FALSE}
-rm(list=ls())
-require(pdgControl)
-require(reshape2)
-require(ggplot2)
-require(data.table)
-```
-
 ```{r cache-options, include=FALSE}
@@
 ```
+
+Define the parameters of our cost function. We will 
+consider a fixed price and fixed $c_0$ cost per unit effort.  
+An additional "policy cost" is introduced through the $c_2$
+coefficient, which can take a range of values. We will loop
+over this range for each of the functional forms of the policy
+cost, in order to choose coefficients $c_2$ in each case
+that are comparable.
 
@@
 
+Clean the workspace and load the required libraries.
+
+``` {r libraries}
+rm(list=ls())
+require(pdgControl)
+require(reshape2)
+require(ggplot2)
+require(data.table)
+```
+
 ```{r graphing-options, include=FALSE}
-opts_knit$set(upload.fun = socialR::notebook.url)
+opts_knit$set(upload.fun = socialR::flickr.url)
 opts_chunk$set(dev.args=list(bg="transparent"),
@@
 ```
+
+This block defines the various parameters 
+and nuisance parameters we need to specify our
+optimal control problem.
 
@@
 
+Given these parameters, we can determine the optimal solution under the classic assumption of "adjustment-free" costs, where there is no penalty for adjusting the value of the control (harvest) at each decision step (year).
+
 ```{r reed, dependson="setup"}
@@
 ````
+
+Now we introduce the functional forms for each of the adjustment costs,
 
@@
 ## Apples to Apples levels
+
+Before we can start comparing solutions induced
+under each of these costs, we need to scale them
+appropriately (e.g. the coefficient $c_2$ has 
+different units and a different magnitude of 
+effect when multiplied by quadratic differences
+$(h_{t} - h_{t-1})^2$ then when multiplied by 
+linear differences $h_{t} - h_{t-1}$.
+
+To do so we loop over a grid of $c_2$ values and
+determine the net present value under each functional 
+form of adjustment costs for each $c_2$ in our grid.
 
@@
 Note that `optim_policy` has been updated to return the equilibrium value of profits from fish harvests before the adjustment costs have been paid, `penalty_free_V`.
-This containst the values for all possible states, we simply evaluate it at the carrying capacity (which is our initial condition.)  The index in `x_grid` that corresponds to the carrying capacity (initial condition) `i` indicates this.
+This contains the values for all possible states, we simply evaluate it at the carrying capacity (which is our initial condition.)  The index in `x_grid` that corresponds to the carrying capacity (initial condition) `i` indicates this.
 
-Quadratic costs on fishing effort have to be done separately,
+We also do the the classical quadratic costs on fishing effort separately,
 

### 2013-05-17 inst/examples/policycosts/writeup.Rmd
writeup run using NPV apples-to-apples #35

@@
+``` {r libraries, message=FALSE, warning=FALSE}
+rm(list=ls())
+require(pdgControl)
+require(reshape2)
+require(ggplot2)
+require(data.table)
+```
+
 ```{r cache-options, include=FALSE}
@@
 
-Clean the workspace and load the required libraries.
-
-``` {r libraries}
-rm(list=ls())
-require(pdgControl)
-require(reshape2)
-require(ggplot2)
-require(data.table)
-```
-
 ```{r graphing-options, include=FALSE}
-opts_knit$set(upload.fun = socialR::flickr.url)
+#opts_knit$set(upload.fun = socialR::flickr.url)
 opts_chunk$set(dev.args=list(bg="transparent"),
-               tidy=FALSE, comment=NA, message=FALSE)
+               tidy=FALSE, comment=NA, message=FALSE, warning=FALSE)
 theme_notebook <- theme_grey() + 
@@
 
-This block defines the various parameters 
-and nuisance parameters we need to specify our
-optimal control problem.
+This block defines the various parameters and nuisance parameters we
+need to specify our optimal control problem.
 
@@
 
-Given these parameters, we can determine the optimal solution under the classic assumption of "adjustment-free" costs, where there is no penalty for adjusting the value of the control (harvest) at each decision step (year).
+Given these parameters, we can determine the optimal solution under the
+classic assumption of "adjustment-free" costs, where there is no penalty
+for adjusting the value of the control (harvest) at each decision step
+(year).
 
@@
 
-Before we can start comparing solutions induced
-under each of these costs, we need to scale them
-appropriately (e.g. the coefficient $c_2$ has 
-different units and a different magnitude of 
-effect when multiplied by quadratic differences
-$(h_{t} - h_{t-1})^2$ then when multiplied by 
+Before we can start comparing solutions induced under each of these
+costs, we need to scale them appropriately (e.g. the coefficient $c_2$
+has different units and a different magnitude of effect when multiplied
+by quadratic differences $(h_{t} - h_{t-1})^2$ then when multiplied by
 linear differences $h_{t} - h_{t-1}$.
 
-To do so we loop over a grid of $c_2$ values and
-determine the net present value under each functional 
-form of adjustment costs for each $c_2$ in our grid.
+To do so we loop over a grid of $c_2$ values and determine the net
+present value under each functional form of adjustment costs for each
+$c_2$ in our grid.
 
@@
 require(snowfall)
-sfInit(cpu=2, parallel=T)
+sfInit(cpu=16, parallel=T)
 sfLibrary(pdgControl)
@@
 
-Note that `optim_policy` has been updated to return the equilibrium value of profits from fish harvests before the adjustment costs have been paid, `penalty_free_V`.
-This contains the values for all possible states, we simply evaluate it at the carrying capacity (which is our initial condition.)  The index in `x_grid` that corresponds to the carrying capacity (initial condition) `i` indicates this.
+Note that `optim_policy` has been updated to return the equilibrium value
+of profits from fish harvests before the adjustment costs have been paid,
+`penalty_free_V`, as well as the total value `V`. Initially we based the 
+comparison on matching `penalty_free_V`, now the economists recommend we
+simply use the total net present value resulting, `V`.
+
+The value matrices returned in either case contain the values for all possible states,
+we simply evaluate it at the carrying capacity (which is our initial
+condition.)  The index in `x_grid` that corresponds to the carrying
+capacity (initial condition) `i` indicates this.
 
@@
   sapply(penalty, function(c2_run)
-    max(c2_run$penalty_free_V[i,]) 
+    max(c2_run$V[i,]) # Would be penalty_free_V originally 
   )
@@
 
-Tidy up the data and plot the net present value (before the penalty has been paid) relative to that achieved when managed without a penalty.
+Tidy up the data and plot the net present value (before the penalty has
+been paid) relative to that achieved when managed without a penalty.
 

### 2013-05-18 inst/examples/policycosts/writeup.Rmd
Provide a table of c2 values
- also allow varying the comparison point.  set to 50% npv

@@
 
-``` {r}
+``` {r profit_model}
 price = 10
@@
 profit <- profit_harvest(price = price, c0 = c0, c1 = 0)
-c2 <- exp(seq(0, log(21), length.out = 20))-1
 ```
+
+```{r c2_grid}
+c2 <- exp(seq(0, log(41), length.out = 40))-1
+c2 <- seq(0, 40, length.out=100)
+```
+
+```{r reduction}
+reduction <- 0.5 
+```
+
+We will compare when transaction costs have reduced the value to `(1-reduction) * adjustment_cost_free_value`
 
@@
 
-```{r reed, dependson="setup"}
+```{r reed, dependson=c("setup", "profit_model")}
 SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
@@
 L1 <- function(c2) function(h, h_prev)  c2 * abs(h - h_prev) 
-free_increase <- function(c2) function(h, h_prev)  c2 * abs(min(h - h_prev, 0)) # increasing harvest is free
-free_decrease <- function(c2) function(h, h_prev)  c2 * max(h - h_prev, 0) # decreasing harvest is free
+free_increase <- function(c2) function(h, h_prev)  c2 * abs(pmin(h - h_prev, 0)) # increasing harvest is free
+free_decrease <- function(c2) function(h, h_prev)  c2 * pmax(h - h_prev, 0) # decreasing harvest is free
 fixed <-  function(c2) function(h, h_prev) c2 * as.numeric( !(h == h_prev) )
@@
 
-``` {r  bigloop, dependson=c("setup", "reed", "fees")}
+``` {r  bigloop, dependson=c("setup", "reed", "fees", "profit_model", "c2_grid")}
 policies <- lapply(penaltyfns, function(penalty){
@@
 
-```{r}
+```{r, dependson="quadcosts"}
 i <- which(x_grid > K)[1]
@@
   sapply(penalty, function(c2_run)
-    max(c2_run$V[i,]) # Would be penalty_free_V originally 
+    max(c2_run$V[i,]) # Would be penalty_free_V originally   ## this isn't correct for asym cases
   )
@@
 
-Tidy up the data and plot the net present value (before the penalty has
-been paid) relative to that achieved when managed without a penalty.
+Tidy up the data and plot the net present value relative to that achieved when managed without a penalty.
 
@@
 
-Find the value of `c2` that brings each penalty closest to 75% of the cost-free adjustment value:
+Alternative version of plot, showing a ratio
 
@@
 
-```{r apples, dependson="quadcosts"}
+Find the value of `c2` that brings each penalty closest to 75% of the cost-free adjustment value:
+
+```{r apples, dependson=c("quadcosts", "reduction")}
 closest <- function(x, v){
@@
 dt_npv <- data.table(fees)
-index <- dt_npv[,closest(0.25, (npv0-value)/npv0), by=variable]
+index <- dt_npv[,closest(reduction, (npv0-value)/npv0), by=variable]
 apples_index <- index$V1
@@
 ````
+
+How close has each of these actually gotten to `r 100*reduction`% reduction to NPV0 (which is `r (1-reduction) * npv0`)?
+
+```{r print_npv, dependson="apples"}
+setkey(dt_npv, variable)
+values <- apply(index, 1, function(x) dt_npv[x[1], ][as.integer(x[2]), ]$value)
+
+percent.error <- (values - ((1-reduction)*npv0)) / ((1-reduction)*npv0)* 100
+
+print_npv <- data.frame(model=index$variable, "value realized"=values, 
+                        "percent of npv0" = 100*values/npv0, "percent error"=percent.error)
+
+```
+
+```{r npv_table, dependson="print_npv"} 
+library(xtable)
+print(xtable(print_npv), type="html")
+#pandoc.table(print_npv)
+```
 
@@
 
-``` {r simulate_policy, dependson="policynames"}
+``` {r simulate_policy, dependson=c("policynames", "apples")}
 quad_profit <- profit_harvest(price = price, c0 = c0, c1 = apples["quad"]) 

### 2013-10-31 inst/examples/policycosts/table.Rmd
script to generate data for building table (issue #41)

``` {r libraries, include=FALSE}
rm(list=ls())
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
```

```{r cache-options, include=FALSE}
opts_chunk$set(cache=TRUE, cache.path="table/")
```

```{r graphing-options, include=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
opts_chunk$set(dev.args=list(bg="transparent"),
               tidy=FALSE, comment=NA, message=FALSE)
```

``` {r}
fees_fn <- function(sigma_g){

price = 10
c0 = 30
profit <- profit_harvest(price = price, c0 = c0, c1 = 0)
c2 <- exp(seq(0, log(21), length.out = 20))-1  # range of c2 values to try
seed <- 123                 # Random seed (replicable results)
delta <- 0.05               # economic discounting rate
OptTime <- 20               # stopping time
gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
reward <- 0                 # bonus for satisfying the boundary condition
#sigma_g <- 0.2              # Noise in population growth
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1         # No measurement noise, 
z_i <- function() 1         # No implemenation noise
f <- BevHolt                # Select the state equation
pars <- c(1.5, 0.05)        # parameters for the state equation
K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
xT <- 0                     # boundary conditions
x0 <- K
x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
h_grid <- x_grid # seq(0.01, 0.8 * K, length = gridsize)

SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                     profit, delta, reward=reward)

L1 <- function(c2) function(h, h_prev)  c2 * abs(h - h_prev) 
free_increase <- function(c2) function(h, h_prev)  c2 * abs(min(h - h_prev, 0)) # increasing harvest is free
free_decrease <- function(c2) function(h, h_prev)  c2 * max(h - h_prev, 0) # decreasing harvest is free
fixed <-  function(c2) function(h, h_prev) c2 * as.numeric( !(h == h_prev) )
L2 <- function(c2) function(h, h_prev)  c2 * (h - h_prev) ^ 2
none <- function(h, h_prev)  0
penaltyfns <- list(L2=L2, L1=L1, free_decrease=free_decrease, fixed=fixed, free_increase=free_increase)

require(snowfall)
sfInit(cpu=8, parallel=T)
sfLibrary(pdgControl)
sfExportAll()

policies <- lapply(penaltyfns, function(penalty){
  sfLapply(c2, function(c2){
      policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                   profit, delta, reward, penalty = penalty(c2))
      }
  )
})

#Note that `optim_policy` has been updated to return the equilibrium value of profits from fish harvests before the adjustment costs have been paid, `penalty_free_V`.  This containst the values for all possible states, we simply evaluate it at the carrying capacity (which is our initial condition.)  The index in `x_grid` that corresponds to the carrying capacity (initial condition) `i` indicates this.

#Quadratic costs on fishing effort have to be done separately,

quad <- 
  sfLapply(c2, function(c2){
  effort_penalty = function(x,h) (c2 * h / x) / price
  policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                        profit, delta, reward, penalty = none, 
                        effort_penalty)
})
policies <- c(policies, quad=list(quad))

#`policies` is a list with an entry for each model.  For each model we have `r length(c2)` different values of the `c_2` coefficient.  For each `c_2` value, we have the `r length(x_grid)` policy function in the vector `D`, giving the harvest index number in `h_grid` optimal for the corresponding stock size in `x_grid`, and the `r length(h_grid)` by `r length(x_grid)` matrices corresponding to the realized value and penalty-free value of harvesting.

#Extract the policy cost.  Values are expected total (net) discounted (present) value given the optimal decision under the given cost model.  That value is computed for all possible previous states.

#We return a value matrix giving the npv for each possible $x_0$ for each possible h.  of course we don't care for each possible h, only the one that is optimal given that starting condition.

fees <- 
lapply(policies, function(penalty){
  i_vals <- 1:length(x_grid)
  names(i_vals) <- as.character(x_grid) #prettyNum(x_grid, 3)
  lapply(i_vals, function(i){
    names(penalty) <- as.character(c2)  #prettyNum(c2, digits=4)
    lapply(penalty, function(c2_run){
      max(c2_run$V[i,])    # 
      #max(c2_run$penalty_free_V[i,])  
    })
  })
})
fees <- melt(fees)
names(fees) <- c("value", "c2", "stock_size", "model")
fees$stock_size <- as.numeric(fees$stock_size)
fees$c2 <- as.numeric(fees$c2)

## some subsetting
dt <- subset(subset(fees, stock_size > x_grid[1]), model %in% c("L1", "L2", "fixed"))
x = as.numeric(levels(as.factor(dt$stock_size))[8])
y = as.numeric(levels(as.factor(dt$stock_size))[42])

## Add npv0 as a column:
fees <- data.table(fees)
npv0 <- fees[,max(value), by=stock_size]
fees <- merge(fees, npv0, "stock_size")
setnames(fees, "V1", "npv0")

fees1 <- subset(subset(fees, stock_size == y), model %in% c("L1", "L2", "fixed"))
fees1 <- data.frame(fees1, sigma_g = sigma_g)
}
````

```{r}
low_noise <- fees_fn(0.05)
med_noise <- fees_fn(0.2)
high_noise <- fees_fn(0.5)

fees <- rbind(low_noise, med_noise, high_noise)
```

```{r}
fees$model <- as.factor(fees$model)
col.defs = c("the initial stock size, (arbitrary units)", 
             "Expected net present value", 
             "the coefficient scaling the magnitude of the adjustment costs",
             "the model",
             "the net present value of the stock size if there where no adjustment costs",
             "the environmental noise level (sigma parameter in multiplicative log-normal noise)")
unit.defs = list("tonnes", 
              "dollar/dollar", 
              "model dependent units", 
              c(L1 = "linear adjustment costs model", 
                L2 = "quadratic adjustment costs model", 
                fixed = "fixed transaction fee for every adjustment"),
              "dollar/dollar",
              "tonnes")
require(reml)
eml_write(data.set(fees, col.defs = col.defs, unit.defs = unit.defs), creator = "Carl Boettiger <cboettig@ropensci.org>")
```

```{r}

fees <- data.table(fees)
ratio <- function(npv0, value){ 
  x = 0.25
  v = (npv0-value)/npv0
  which.min(abs(v-x))
  }

fees[,ratio(npv0, value), by="model"]

a = ddply(fees, .(npv0, value), ratio)

```

```{r}
fees <- med_noise 
```

Obviously the expected net present value (ENPV) increases monotonically with starting stock size, and decreases with larger penalties (successively lower curves in the same model).

```{r}
ggplot(subset(subset(fees, stock_size > x_grid[1]), model %in% c("L1", "L2", "fixed"))) + 
  geom_line(aes(stock_size, value, group=interaction(c2,model), color=model), alpha=.7) +
  facet_wrap(~model)

```

We need overlapping region of c2 values to be able to find apples-to-apples comparisons.

Different starting stock sizes are just a vertical translation of the value vs penalty curve.  The exponential-like decline of value with penalty magnitude motivates our sampling of the c2 values (indicated by dots)

```{r}
ggplot(subset(dt, stock_size %in% c(x,y))) + 
  geom_line(aes(c2, value, group=interaction(stock_size, model), color=model)) + 
  facet_wrap(~stock_size) +
  geom_point(data= data.frame(c2 = c2, y=0), aes(c2,y)) # + scale_x_log10()
```

```{r}
ggplot(subset(fees, stock_size > x_grid[2] )) + 
  geom_line(aes(stock_size, value, group=interaction(c2,model), color=model), alpha=.7) +
  facet_wrap(~model)

```

Tidy up the data and plot the net present value (before the penalty has been paid) relative to that achieved when managed without a penalty.

Find the value of `c2` that brings each penalty closest to 75% of the cost-free adjustment value:

```{r apples_plot, dependson="quadcosts"}
ggplot(subset(fees, stock_size == y), 
       aes(c2, (npv0-value)/npv0, col=model, group = interaction(model, stock_size)))  +
  geom_line()
````

Write fees out along with nusiance variables.  We will subset on a specific starting stock size since this is just a constant shift to the value curve.

### 2013-10-31 inst/doc/policycosts/policycosts_tmp.tex

--- 2013-05-13 inst/doc/policycosts/policycosts_PRA.tex
@@
 \begin{frontmatter}
-\title{Policy Costs \\ \pa{
-Target Journals: Ecological Applications, Journal of Applied Ecology, some discussion of whether scope for PNAS}}
+\title{Policy Costs }
 \author[cpb]{C. Boettiger\corref{cor1}}
@@
 \begin{abstract}
-\cdb{Carl's comments \& questions added in green} \\
-\pa{Paul's comments \& questions added in blue} \\
-\jr{Jake's comments \& questions added in red}
 \end{abstract}
@@
   great intertia to change despite considerable movement in the stock
-  dynamics.  \cdb{Conceptual picture illustrating the need to account
+  dynamics.  {\color{green}Conceptual picture illustrating the need to account
   for costs to changing policy. Current images are just placeholders.
@@
 
-\pa{
+{\color{blue}
  Problem description resolved in Meeting 3 - note the list of possible causal mechanisms here (reaching agreement to processor plants) was negotiated with some not being acceptable suggestions:
@@
 
-\pa{
+{\color{blue}
 
@@
 
-\pa{
+{\color{blue}
 Resolved in Meeting 3: We will only do comparisons described last time as $L_1$, $L_2$ and fixed.
@@
 
-\pa{
+{\color{blue}
   Suggested from Meeting 3:
@@
 
-\jr{
+{\color{red}
 
@@
 
-\jr{
+{\color{red}
 The fact that there is no uniform metric for comparing different functional forms of the penalty function complicates identifying the implications of various penalty functions on optimal management.
@@
 Asymmetric ($L_1$) adjustment costs attempt to track the optimal solution, and can end up with larger fees than anticipated.
-\cdb{Not quite sure why we get this pattern in the asymmetrics!}
+{\color{green}Not quite sure why we get this pattern in the asymmetrics!}
 
@@
 
-\cdb{ In terms of a policy set on escapement instead of harvest, our solutions are actually more volatile than~\citet{Reed1979}.
+{\color{green} In terms of a policy set on escapement instead of harvest, our solutions are actually more volatile than~\citet{Reed1979}.
 Maybe this leads to a discussion of what the control policy should be defined in terms of (i.e.
@@
 
-\pa{ 
+{\color{blue} 
   Figure 3 stays largely as is.  But we also need to see the corresponding x trajectories in a way that makes for easy comparisons but not cluttered axes
@@
 
-\pa{ 
+{\color{blue} 
  A version of Figure 4 to go in.
@@
 The variance is averaged over 50 replicates, and recalculated at each of 20 different intensities ranging from 0 (no cost) to 1 (NPV reduced to zero by the adjustment costs)The variance is averaged over 50 replicates, and recalculated at each of 20 different intensities ranging from 0 (no cost) to 1 (NPV reduced to zero, by the adjustment costs), shown in Figure~\ref{fig:summarystats}.
-\cdb{Correction: not actually zero, just to max reduction (usually what is obtained by constant quota).
+{\color{green}Correction: not actually zero, just to max reduction (usually what is obtained by constant quota).
 Should indicate where this asymptote has occurred)}.
@@
 
-\cdb{Add additional plot: Is value a linear function of policy cost, or is there a sharp transition? }
-\pa{ Must be nonlinear somewhere when adjustment costs exceed profits? }
+{\color{green}Add additional plot: Is value a linear function of policy cost, or is there a sharp transition? }
+{\color{blue} Must be nonlinear somewhere when adjustment costs exceed profits? }
 
@@
 Costs and profits are shown for ignoring the adjustment costs (Reed solution, purple and blue) and accounting for the adjustment (green and red).
-\cdb{Though only L1 shown for the moment, would probably show all four types.
+{\color{green}Though only L1 shown for the moment, would probably show all four types.
 Possibly a table or box-and-whiskers style plot would be better?}}\label{fig:profits_costs}
@@
 
-\pa{ Keep Figure 5 or its equivalent for one penalty function formulation and talk through what it means and how to interpret it.
+{\color{blue} Keep Figure 5 or its equivalent for one penalty function formulation and talk through what it means and how to interpret it.
 
@@
 Distribution of net present value realized over 100 simulations when adjustment costs are ignored (blue), compared to when adjustment costs are optimally accounted for (red).
-\cdb{Though only L1 shown for the moment, would probably show all four types.
+{\color{green}Though only L1 shown for the moment, would probably show all four types.
 Possibly a table or box-and-whiskers style plot would be better?}}\label{fig:npv_dist}
@@
 
-\cdb{\textbf{Further things to look at?}
+{\color{green}\textbf{Further things to look at?}
 \begin{itemize}
@@
 \section{Discussion}
-\cdb{Some possible things to discuss: could add others, could remove some.}
+{\color{green}Some possible things to discuss: could add others, could remove some.}
 \begin{itemize}

### 2013-10-31 inst/examples/policycosts/writeup.Rmd
exploring table relative costs

@@
 ```{r graphing-options, include=FALSE}
-#opts_knit$set(upload.fun = socialR::flickr.url)
+opts_knit$set(upload.fun = socialR::flickr.url)
 opts_chunk$set(dev.args=list(bg="transparent"),
@@
 quad_profit <- profit_harvest(price = price, c0 = c0, c1 = apples["quad"])
+
+reps <- 1:10
+names(reps) = paste("rep", 1:10, sep="_")
 sims <- list(
-  L1 = simulate_optim(f, pars, x_grid, h_grid, x0, 
+  L1 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                       L1_policy, z_g, z_m, z_i, 
-                      opt$D, profit=profit, penalty=L1(apples["L1"]), seed=seed), 
-  L2 = simulate_optim(f, pars, x_grid, h_grid, x0, 
+                      opt$D, profit=profit, penalty=L1(apples["L1"]), seed=seed)), 
+  L2 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                       L2_policy, z_g, z_m, z_i, 
-                      opt$D, profit=profit, penalty=L2(apples["L2"]), seed=seed),
-  fixed = simulate_optim(f, pars, x_grid, h_grid, x0, 
+                      opt$D, profit=profit, penalty=L2(apples["L2"]), seed=seed)),
+  fixed = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                          fixed_policy, z_g, z_m, z_i, 
-                         opt$D, profit=profit, penalty=fixed(apples["fixed"]), seed=seed),
-  increase = simulate_optim(f, pars, x_grid, h_grid, x0, 
-                            free_increase_policy, z_g, z_m, z_i, 
-                            opt$D, profit=profit, penalty= free_increase(apples["increase"]), seed=seed),
-  decrease = simulate_optim(f, pars, x_grid, h_grid, x0, 
-                            free_decrease_policy, z_g, z_m, z_i, 
-                            opt$D, profit=profit, penalty= free_decrease(apples["decrease"]), seed=seed),
-  quad = simulate_optim(f, pars, x_grid, h_grid, x0, 
-                            quad_policy, z_g, z_m, z_i, 
-                            opt$D, profit=quad_profit, penalty= none, seed=seed)
+                         opt$D, profit=profit, penalty=fixed(apples["fixed"]), seed=seed))
+
 )
@@
 #Make data tidy (melt), fast (data.tables), and nicely labeled.
-dat <- melt(sims, id=names(sims[[1]]))  
+dat <- melt(sims, id=names(sims[[1]][[1]]))  
 dt <- data.table(dat)
+setnames(dt, "L2", "replicate") # names are nice
 setnames(dt, "L1", "penalty_fn") # names are nice
 ````
+
+```{r }
+sims_free <- list(
+  L1 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
+                      L1_policy, z_g, z_m, z_i, 
+                      opt$D, profit=profit, penalty=none, seed=seed)), 
+  L2 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
+                      L2_policy, z_g, z_m, z_i, 
+                      opt$D, profit=profit, penalty=none, seed=seed)),
+  fixed = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
+                         fixed_policy, z_g, z_m, z_i, 
+                         opt$D, profit=profit, penalty=none, seed=seed))
+)
+````
+
+``` {r }
+#Make data tidy (melt), fast (data.tables), and nicely labeled.
+free <- melt(sims_free, id=names(sims_free[[1]][[1]]))  
+dt_free <- data.table(free)
+setnames(dt_free, "L2", "replicate") # names are nice
+setnames(dt_free, "L1", "penalty_fn") # names are nice
+````
+
+```{r}
+
+# Profit when accounting for penalty when present
+optimal_cost <- dt[, sum(profit_fishing), by=penalty_fn ] 
+# Profit when ignoring penalty when present
+ignore_when_present <- dt[, sum(profit_fishing_alt), by=penalty_fn] 
+# Profit when assuming penalty when it is absent
+assume_when_absent <- dt_free[, sum(profit_fishing), by=penalty_fn]
+# Profit when ignoring penalty when it is absent
+optimal_free <- dt_free[, sum(profit_fishing_alt), by=penalty_fn]
+
+# Normalize by the optimal 
+ignore_when_present$V1 <- ignore_when_present$V1/optimal_cost$V1
+assume_when_absent$V1 <- assume_when_absent$V1/optimal_free$V1
+
+# Name and merge columns
+setnames(ignore_when_present, "V1", "ignore_cost")
+setnames(assume_when_absent, "V1", "assume_cost")
+error_costs = merge(ignore_when_present, assume_when_absent, "penalty_fn")
+
+error_costs
+
+```
+
+### additional plots based on simulations under the correct model
 

### 2013-11-01 inst/examples/policycosts/writeup.Rmd
more reps

@@
 ```{r reduction}
-reduction <- 0.5 
+reduction <- 0.25 
 ```
@@
 
-Find the value of `c2` that brings each penalty closest to 75% of the cost-free adjustment value:
+Find the value of `c2` that brings each penalty closest to `r reduction*100`% of the cost-free adjustment value:
 
@@
 
-reps <- 1:10
+reps <- 1:100
 names(reps) = paste("rep", 1:10, sep="_")
@@
 # Profit when accounting for penalty when present
-optimal_cost <- dt[, sum(profit_fishing), by=penalty_fn ] 
+optimal_cost <- dt[, sum(profit_fishing - policy_cost), by=penalty_fn ] 
 # Profit when ignoring penalty when present
-ignore_when_present <- dt[, sum(profit_fishing_alt), by=penalty_fn] 
+ignore_when_present <- dt[, sum(profit_fishing_alt - policy_cost_alt), by=penalty_fn] 
 # Profit when assuming penalty when it is absent
-assume_when_absent <- dt_free[, sum(profit_fishing), by=penalty_fn]
+assume_when_absent <- dt_free[, sum(profit_fishing - policy_cost), by=penalty_fn]
 # Profit when ignoring penalty when it is absent
-optimal_free <- dt_free[, sum(profit_fishing_alt), by=penalty_fn]
+optimal_free <- dt_free[, sum(profit_fishing_alt - policy_cost_alt), by=penalty_fn]
 
 # Normalize by the optimal 
-ignore_when_present$V1 <- ignore_when_present$V1/optimal_cost$V1
-assume_when_absent$V1 <- assume_when_absent$V1/optimal_free$V1
+#ignore_when_present$V1 <- ignore_when_present$V1/optimal_cost$V1
+#assume_when_absent$V1 <- assume_when_absent$V1/optimal_free$V1
 
@@
 
+print_npv # theoretically acheivable profits under these costs
+optimal_cost$V1/optimal_free$V1 # actually realized
+
 error_costs
 
+```
+
+```{r error_costs_table} 
+print(xtable(error_costs), type="html")
+#pandoc.table(print_npv)
 ```

### 2013-11-05 inst/examples/policycosts/plot_table.Rmd
plottable

```{r}
opts_knit$set(upload.fun = socialR::flickr.url)
```

```{r}
require(ggplot2)
df <- read.csv("output.csv")
df <- df[2:8]

require(reshape2)
who <- c("penalty_fn", "ignore_fraction", "assume_fraction", "sigma_g", "reduction")
df2 <- melt(df, id=who)
who <- c("penalty_fn", "sigma_g", "reduction", "variable", "value")
df3 <- melt(df2, id=who)
names(df3) <- c("penalty_fn", "sigma_g", "reduction", "variable", "value", "fraction_variable", "fraction")

df3$reduction <- as.factor(df3$reduction)
#ggplot(df3) + geom_line(aes(sigma_g, value, col=penalty_fn, lty=variable)) + facet_wrap(~reduction) 
ggplot(df3) + geom_line(aes(sigma_g, value, col=reduction, lty=variable)) + facet_wrap(~penalty_fn) 
```

```{r results="asis"}
print(xtable::xtable(df3), type="html")
```

### 2013-11-05 inst/examples/policycosts/errors_table.Rmd

``` {r libraries, message=FALSE, warning=FALSE}
rm(list=ls())
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
```

```{r cache-options, include=FALSE}
opts_chunk$set(cache=TRUE, cache.path="errors_table/", tidy=FALSE)
```

```{r}
start <- Sys.time()
```

``` {r profit_model}
compute_error_table <- function(reduction = 0.25, sigma = 0.2){
reduction <- reduction

price = 10
c0 = 30
profit <- profit_harvest(price = price, c0 = c0, c1 = 0)
c2 <- seq(0, 50, length.out=100)

seed <- 123                 # Random seed (replicable results)
delta <- 0.05               # economic discounting rate
OptTime <- 20               # stopping time
gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
sigma_g <- sigma              # Noise in population growth
reward <- 0                 # bonus for satisfying the boundary condition
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1         # No measurement noise, 
z_i <- function() 1         # No implemenation noise
f <- BevHolt                # Select the state equation
pars <- c(1.5, 0.05)        # parameters for the state equation
K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
xT <- 0                     # boundary conditions
x0 <- K
x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
h_grid <- seq(0.01, 0.8 * K, length = gridsize)

SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                     profit, delta, reward=reward)

L1 <- function(c2) function(h, h_prev)  c2 * abs(h - h_prev) 
free_increase <- function(c2) function(h, h_prev)  c2 * abs(pmin(h - h_prev, 0)) # increasing harvest is free
free_decrease <- function(c2) function(h, h_prev)  c2 * pmax(h - h_prev, 0) # decreasing harvest is free
fixed <-  function(c2) function(h, h_prev) c2 * as.numeric( !(h == h_prev) )
L2 <- function(c2) function(h, h_prev)  c2 * (h - h_prev) ^ 2
none <- function(h, h_prev)  0
penaltyfns <- list(L2=L2, L1=L1, free_decrease=free_decrease, fixed=fixed, free_increase=free_increase)

require(snowfall)
sfInit(cpu=8, parallel=T)
sfLibrary(pdgControl)
sfExportAll()

policies <- lapply(penaltyfns, function(penalty){
  sfLapply(c2, function(c2){
      policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                   profit, delta, reward, penalty = penalty(c2))
      }
  )
})

quad <- 
  sfLapply(c2, function(c2){
  effort_penalty = function(x,h) (c2 * h / x) / price
  policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                        profit, delta, reward, penalty = none, 
                        effort_penalty)
})
policies <- c(policies, quad=list(quad))

i <- which(x_grid > K)[1]
fees <- 
lapply(policies, function(penalty) 
  sapply(penalty, function(c2_run)
    max(c2_run$V[i,]) # Would be penalty_free_V originally   ## this isn't correct for asym cases
  )
)

npv0 <- max(fees$L1) # all have same max, at c2=0 
npv0
fees <- data.frame(c2=c2,fees)
fees <- melt(fees, id="c2")
#ggplot(fees, aes(c2, value, col=variable)) + geom_point() + geom_line()

closest <- function(x, v){
  which.min(abs(v-x))
}
dt_npv <- data.table(fees)
index <- dt_npv[,closest(reduction, (npv0-value)/npv0), by=variable]
apples_index <- index$V1
names(apples_index) = index$variable
apples <- c2[index$V1]
names(apples) = index$variable
apples

setkey(dt_npv, variable)
values <- apply(index, 1, function(x) dt_npv[x[1], ][as.integer(x[2]), ]$value)

percent.error <- (values - ((1-reduction)*npv0)) / ((1-reduction)*npv0)* 100

print_npv <- data.frame(model=index$variable, "value realized"=values, 
                        "percent of npv0" = 100*values/npv0, "percent error"=percent.error)

L2_policy <- policies$L2[[apples_index["L2"]]]$D
L1_policy <- policies$L1[[apples_index["L1"]]]$D
fixed_policy <- policies$fixed[[apples_index["fixed"]]]$D
free_increase_policy <- policies$free_increase[[apples_index["free_increase"]]]$D
free_decrease_policy <- policies$free_decrease[[apples_index["free_decrease"]]]$D
quad_policy <- policies$quad[[apples_index["quad"]]]$D

quad_profit <- profit_harvest(price = price, c0 = c0, c1 = apples["quad"])

reps <- 1:100
names(reps) = paste("rep", 1:10, sep="_")
sims <- list(
  L1 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L1_policy, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L1(apples["L1"]), seed=seed)), 
  L2 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L2_policy, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L2(apples["L2"]), seed=seed)),
  fixed = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                         fixed_policy, z_g, z_m, z_i, 
                         opt$D, profit=profit, penalty=fixed(apples["fixed"]), seed=seed))

)

#Make data tidy (melt), fast (data.tables), and nicely labeled.
dat <- melt(sims, id=names(sims[[1]][[1]]))  
dt <- data.table(dat)
setnames(dt, "L2", "replicate") # names are nice
setnames(dt, "L1", "penalty_fn") # names are nice

sims_free <- list(
  L1 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L1_policy, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=none, seed=seed)), 
  L2 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L2_policy, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=none, seed=seed)),
  fixed = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                         fixed_policy, z_g, z_m, z_i, 
                         opt$D, profit=profit, penalty=none, seed=seed))
)

#Make data tidy (melt), fast (data.tables), and nicely labeled.
free <- melt(sims_free, id=names(sims_free[[1]][[1]]))  
dt_free <- data.table(free)
setnames(dt_free, "L2", "replicate") # names are nice
setnames(dt_free, "L1", "penalty_fn") # names are nice

# Profit when accounting for penalty when present
optimal_cost <- dt[, sum(profit_fishing - policy_cost), by=penalty_fn ] 
# Profit when ignoring penalty when present
ignore_when_present <- dt[, sum(profit_fishing_alt - policy_cost_alt), by=penalty_fn] 
# Profit when assuming penalty when it is absent
assume_when_absent <- dt_free[, sum(profit_fishing - policy_cost), by=penalty_fn]
# Profit when ignoring penalty when it is absent
optimal_free <- dt_free[, sum(profit_fishing_alt - policy_cost_alt), by=penalty_fn]

# Normalize by the optimal 
ignore_fraction <- ignore_when_present$V1/optimal_cost$V1
assume_fraction <- assume_when_absent$V1/optimal_free$V1
assume_when_absent <- cbind(assume_when_absent, assume_fraction = assume_fraction)
ignore_when_present <- cbind(ignore_when_present, ignore_fraction = ignore_fraction)

# Name and merge columns
setnames(ignore_when_present, "V1", "ignore_cost")
setnames(assume_when_absent, "V1", "assume_cost")
error_costs = merge(ignore_when_present, assume_when_absent, "penalty_fn")

print_npv # theoretically acheivable profits under these costs
optimal_cost$V1/optimal_free$V1 # actually realized

error_costs <- cbind(error_costs, sigma_g = sigma_g, reduction = reduction)

error_costs 
}

```

```{r}
sigmas <- c(0.05, 0.2, 0.5)
reductions <- c(0.1, 0.2, 0.3)
out <- lapply(sigmas, function(s){
  lapply(reductions, function(r){
    compute_error_table(r = r, sigma = s)    
  })
})

who <- names(out[[1]][[1]])
df <- melt(out, id=who)              
df
```

```{r}
#df <- df[1:5]
library(xtable)
print(xtable(df), type="html")
writeLines(print(xtable(df)), "output.md")
system("pandoc output.md -o output.pdf")
```

```{r}
Sys.time() - start 
```

### 2013-11-05 inst/examples/policycosts/plot_table.Rmd
update plot, smaller table

@@
 df3$reduction <- as.factor(df3$reduction)
-#ggplot(df3) + geom_line(aes(sigma_g, value, col=penalty_fn, lty=variable)) + facet_wrap(~reduction) 
-ggplot(df3) + geom_line(aes(sigma_g, value, col=reduction, lty=variable)) + facet_wrap(~penalty_fn) 
+ggplot(df3) + geom_line(aes(sigma_g, value, col=reduction, lty=variable)) + facet_wrap(~penalty_fn, scales="free_y") 
 ```
@@
 ```{r results="asis"}
-print(xtable::xtable(df3), type="html")
+print(xtable::xtable(df), type="html")
 ```

### 2013-11-05 inst/examples/policycosts/plot_table.Rmd
update plot, smaller table
hide code

@@
-```{r}
+```{r settings, include=FALSE}
 opts_knit$set(upload.fun = socialR::flickr.url)
@@
 
-```{r}
+```{r fig.width=12, echo=FALSE}
 require(ggplot2)
@@
 
-```{r results="asis"}
+```{r results="asis", echo=FALSE}
 print(xtable::xtable(df), type="html")

### 2013-11-06 inst/examples/policycosts/errors_table.Rmd
updated writeup with tweaks to figures

@@
 
-```{r}
+```{r results="asis"}
 #df <- df[1:5]
@@
 system("pandoc output.md -o output.pdf")
+write.csv(df, "output.csv")
 ```

### 2013-11-06 inst/doc/policycosts/StochAdjCost_051713.tex
Paul's edits

\documentclass[12pt]{article}

\usepackage{epsfig}

\begin{document}

\title{Optimal management of a stochastically varying population when policy adjustment is costly}

%\titlerunning{Short form of title}        % if too long for running head

\author{Carl Boettiger    \\
       Michael Bode      \\
        James N. Sanchirico \\
Jacob LaRiviere \\
Alan M. Hastings\\
Paul R. Armsworth
}

\maketitle

\section{Introduction}

\begin{itemize}
  \item Ecosystem management frequently set in terms of policy of quotas. 
  \item Policy relatively static and costly to change
  \item Meanwhile, the natural world is variable
  \item Optimal solutions typically track these shocks, resulting in impractical management recommendations in face of policy costs
\end{itemize}

\emph{Develop a figure to insert here comparing quotas that were set to the stock size estimated at that time in the stock assessment for two different fish stocks. We choose the two stocks to highlight variation in how responsive management can be. Suggested halibut and bluefin tuna.}

Empirics suggest not always as responsive as Reed solution. Explore conditions under which that makes sense. Idea is that regulator’s objective sometimes may not be `raw' NPV, but rather NPV with some penalties on fast changes. Possible reasons: pure administrative transaction cost of changing policies (reaching agreement), fishermens' preferences for less variable quotas, processing plants' preferences for less variable quotas especially if tied into contracts for canning and so forth. But we do not know what functional form of any such policy adjustment costs takes and it will be a lot of work to estimate it. Here we explore several plausible candidate functional forms that each reflect different ways these policy adjustment costs could work. Would be good to know if differences between functional forms is particularly important.

\section{Methods}

 Fish population dynamics / state equation.  We will assume Beverton-Holt dynamics with multiplicative environmental noise
    \begin{equation} 
      N_{t+1} = Z_t \frac{A N_t}{1 + B N_t}, 
\label{eq:state_equation}
    \end{equation}
where $N_t$ the stock size, $Z_t$ gives the stochastic shocks, which we assume are lognormally distributed and $A$ and $B$ are positive constants. HARVESTING SHOULD APPEAR IN THIS EQUATION.

We assume managers set an annual quota for harvesting $h_t$ (the control variable) after observing the stock size that year $N_t$ (the state variable), but while still being uncertain about future environmental conditions and stock sizes. Through time, this gives a time path of management actions ${\bf h}=(h_1,h_2,\dots)$ that depend on the stock sizes that were observed (a state dependent control rule).

We assume that managers choose annual quotas to maximize the expected net present value (NPV) of the fishery. We take as a base case the situation where there are no costs associated with policy adjustment and the managers' objective is
\begin{equation}
\max_{{\bf h}}\mathbf{ E} ( NPV_{0} )=\max_{{\bf h}} \sum_0^\infty \mathbf{E} \left( \displaystyle \frac{\Pi_0(N_t,h_t)}{(1+\delta)^{t+1}} \right)
\label{eq:objective}
\end{equation}
where $\mathbf{E}$ is the expectation operator, $\delta>0$ is the discount rate and $\Pi_0$ is the net revenue from operating the fishery in a given year. In this base case, we assume the annual net revenue from fishing is 
  \begin{equation} 
    \Pi_0(N_t,h_t) = p h_t -  c_0 E_t
\label{eq:annual_netrevenue}
  \end{equation}
  where $E_t$ represents
  fishing effort. We assume catch is proportional to stock size and effort expended fishing that year, $h_t=qE_tN_t$ and constant $q>0$ is the catchability coefficient. In Eqn.~\ref{eq:annual_netrevenue}, $p$ is the price per unit harvest and $c_0$ the cost of fishing and we assume $p>0$ and $c_0>0$.

Taken together this objective function (\ref{eq:objective}) and the state equation (\ref{eq:state_equation}) define a stochastic dynamic programming problem that we solve using backwards recursion via Bellman's equation. We denote the resulting state-dependent, optimal control as ${\bf h_0^*}$. PRESUMABLY YOU USED A FINITE TERMINAL TIME IN WHICH CASE WE NEED TO REVISE TO REFLECT HOW YOU HANDLED THAT.

\subsection*{Costs of policy adjustment}
We compare this base case to three alternative problem formulations, each reflecting different plausible functional forms that costs of policy adjustment could take. In each, we assume managers can adjust the quota set in the fishery $h_t$ in a given year and that any policy adjustment costs are associated with changes to this control variable.

First we assume that policy adjustment costs are directly proportional to the magnitude of the change in policy being proposed, such that larger changes to annual harvesting quotas incur greater policy adjustment penalties. Specifically, we replace $\Pi_0$ in the $NPV_0$ equation with 
\begin{equation}
  \Pi_{1}(N_t,h_t, h_{t-1}) = \Pi_0 - c_1  |  h_t - h_{t-1} | \,.
\end{equation}

Next we continue to assume that policy adjustment costs depend on the magnitude of the change in policy being proposed. However, we consider a case where this dependence is nonlinear with big changes in policy being disproportionately expensive:
\begin{equation}
  \Pi_{2}(N_t,h_t, h_{t-1}) = \Pi_0 - c_2 (  h_t - h_{t-1})^2 \,.
\end{equation}

Finally, we assume instead that there is a fixed cost associated with any adjustment of policy, regardless of how large that adjustment might be
\begin{equation}
  \Pi_{3}(N_t,h_t, h_{t-1}) = \Pi_0 - c_3 (1-\mathbf{I}(h_t, h_{t-1}))  \,,
\end{equation}
where indicator function $\mathbf{I}(h_t, h_{t-1})$ takes the value 1 if $h_t=h_{t-1}$ and zero otherwise. For each $\Pi_i$, we can then define a new objective function $NPV_i$ similar to that in Eqn.~\ref{eq:objective}.

Taken together with the state equation (Eqn.~\ref{eq:state_equation}), each of these new objective functions defines a different stochastic dynamic programming problem. Again, we solve them numerically using backwards recursion.  To include costs of policy adjustment, we expand the state space to include both the current stock size and the management action taken on the previous time step $(N_t,h_{t-1})$. For each new objective function $\max NPV_i$, we denote the corresponding optimal control policy $ {\bf h_i^*} $.

In addition in the Supplementary Material, we compare our results with a more conventional fisheries economic formulation in which additional costs are applied to the control variables themselves, as opposed to adjustments to the controls: $ \Pi_4 (N_t,h_t) = p h_t -  c_0 E_t-c_4E_t^2$. Additional costs of this form tend to have  a smoothing effect on optimal quotas, but also change the long-term average stock size or quota size that is optimal.

\subsection*{Choice of parameters}

Each of the policy adjustment cost function is characterized in terms
of a cost coefficient $c_i$.  However, $c_i$ takes different units for each  functional form. Therefore, if seeking to compare the relative effect of each penalty function on optimal management, it is unclear what parameter values should be used. To address this issue, we calibrate choices of $c_i$ so that each has a comparable impact on the optimal net present value of fishery, broadly following the example of Bovenberg, Goulder and Gurnery (2005) and Bovenberg, Goulder and Jacobsen (2008).

Figure 1 shows the calibration graphically.  Each curve plots the change in maximum expected NPV for a given penalty function as the penalty cost parameter is increased. In each case, the figure shows maximum expected NPV with policy adjustment costs as a proportion of the maximum expected NPV available in the basic problem $NPV_0({\bf h_0^*})$ without policy adjustment costs.

To compare the impact of penalty functions on optimal management across the different functional forms, we select penalty cost coefficients that induce the same reduction in maximum expected NPV. For example, the dashed vertical lines in Figure 1 map the needed cost coefficient $c_i$, for each penalty function, such that the fishery is worth 80\% of its unconstrained value when optimally managed.

Other parameters in the model are chosen - HOW?

\begin{figure}
\epsfig{figure=npv0.eps,width=5in}
\caption{\textbf{Expected net present value by functional form of penalty.} Horizontal axis shows the coefficient $c_i$ governing the magnitude of the policy cost, while vertical axis shows fraction of the maximum expected net present value dissipated by the policy cost.  The horizontal line indicates a value of the stock that is 80\% of the maximum expected value in the absence of policy adjustment costs, $NPV_0({\bf h_0^*})$. Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.  }
\end{figure}

\section{Results}
\subsection*{Effect of policy adjustment costs on optimal quotas and stock sizes}
Figure 2 shows the impact that the adjustment cost has on the optimal policy.   Each panel is generated against the same sequence of random shocks so that they can be compared directly. Figure 3 (TO COME) shows the corresponding stock sizes.  In each case, the optimal solution without any adjustment cost is shown in black and the policy induced by optimization under the given adjustment penalty (equivalent to a 25\% reduction in maximum expected NPV) is overlaid in blue.

When considering the first formulation of policy adjustment costs ($\Pi_1$), the first  panel of Figure 2 shows a typical pattern, in which the optimal policy tends to avoid small policy adjustments, resulting in long periods of constant policy followed by sudden bursts of adjustment. This results in a relatively step-like policy pattern.  In contrast, the second formulation $\Pi_2$ disproportionately penalizes large policy adjustments. The corresponding optimal policy tracks all of the changes made by the cost-free policy, but with smaller magnitude.  This results in a smoother $h_t$ curve, one that undershoots the larger oscillations seen in the cost-free optimum in favor of a policy that changes incrementally each yearl.  Finally, the optimal policy for the third, `fixed fee' formulation ($\Pi_3$) only makes large adjustments, as one might expect, because the magnitude of the adjustment made is not reflected in the resulting penalty.  Whereas the optimal solution for $\Pi_1$ attempts to accommodate the large oscillations at the end of the period shown (time steps $t=47-49$) with a constant quota in between the extremes, the fixed fee version takes the opposite approach of one very large swing. MORE DETAILING TO COME WHEN WE HAVE THE FIGURES

\begin{figure}
%\epsfig{figure=optimalcontrols.eps,width=6 in}
  \caption{Individual realizations of optimal harvesting strategy under the different functional forms of adjustment costs. WILL ONLY SHOW THREE PANELS (PANELS 1,2 AND 4). NEED TO SHOW COMPARABLE STOCK DYNAMICS. PANEL 6 GOES TO SI ALONG WITH CORRESPONDING STOCK DYNAMICS}
\end{figure}

The comparisons shown in Figure 2 are for one realization (i.e. a particular sequence of random number draws representing environmental variability) and are made for a particular magnitude of policy adjustment costs equal to 25\% of the maximum expected net present value in the base case ($NPV_0({\bf h_0^*})$). Figure 4 generalizes to show how optimal harvest levels and corresponding optimal stock sizes are affected by the magnitude of the costs of policy adjustment. This time we show summary statistics across 50 replicate sets of environmental conditions. We show the impact of policy adjustment costs on the variance of both harvests and stock sizes through time; on the autocorrelation of harvests and stock sizes through time; and on the cross-correlation of harvests and stock sizes through time.  (COMPARABLE FIGURES FOR OPTIMAL STOCK SIZES AND CROSS-CORRELATIONS OF THE TWO TO COME.)

We see that TO COME WHEN WE HAVE THE FIGURES

\begin{figure}
%\epsfig{figure=Harvestvariance.eps,width=4in}
\caption*{Figure 4a: Variance of optimal harvest rates through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs. RANGE OF HORIZONTAL AXIS MORE LIKE 0-0.35 GIVEN FIGURE 1. DROP THE THREE UNUSED CURVES. ADD COMPARABLE FIGURE FOR STOCK SIZES}
\end{figure}

\begin{figure}
%\epsfig{figure=Harvestautocorrelation.eps,width=4in}
\caption*{Figure 4b: Autocorrelation of optimal harvest rates through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs. RANGE OF HORIZONTAL AXIS MORE LIKE 0-0.35 GIVEN FIGURE 1. DROP THE THREE UNUSED CURVES. ADD COMPARABLE FIGURE FOR STOCK SIZES AND CROSS-CORRELATIONS}
\end{figure}

\subsection*{Consequences of policy adjustment costs}

Next we examine the consequences either of ignoring policy adjustment costs when they are present or assuming they are present when they are not. To do so, it helps to break-down the different contributions to the maximum expected $NPV_i$ when employing the optimal policy $\bf{h_i}^*$ versus when employing the policy that would be optimal were there no costs to policy adjustment $\bf{h_0}^*$. For example, if we take the first of the adjustment penalty forms, $\Pi_1$
\begin{equation}
 NPV_i( \mathbf{h_1^*} ) = \sum_{t=0}^\infty (\overbrace{ p h^*_{1,t}-c_0E^*_{1t}}^{[1]}-\overbrace{c_1 | h^*_{1,t}- h^*_{1,t-1}|}^{[2]} ) \displaystyle \frac{1}{(1+\delta)^t}
\end{equation}
and 
\begin{equation}
 NPV_i( \mathbf{h_0^*} ) = \sum_{t=0}^\infty (\underbrace{ p h^*_{0,t}-c_0E^*_{0t}}_{[3]}-\underbrace{c_1 | h^*_{0,t}- h^*_{0,t-1}|}_{[4]} ) \displaystyle \frac{1}{(1+\delta)^t}
\end{equation}
Histograms for the different contributions labelled $[1]-[4]$ here when taken across XXX replicate runs are shown are shown in Figure 5 (contribution $[1]$ red, $[2]$ green, $[3]$ blue, and $[4]$ mauve). The cost of assuming policy adjustments are present when in fact they are absent is given by subtracting the contribution to the first infinite sum from term $[1]$ from the contribution to the second infinite sum of term $[3]$ (red-blue in the Figure). (Note that convergence properties required to do this are met because we assume a positive discount rate). This cost is positive because the optimal controls recommended when assuming policy adjustment costs are present do not track variations in stock size as closely. Therefore, this harvesting strategy provides lower net revenue dockside.

In contrast, the cost of ignoring policy adjustment costs when in fact they are present is given by subtracting the second infinite sum from the first (contributions $([1]-[2])-([3]-[4]))$ in the equations or (red-green)-(blue-mauve) in the Figure). These costs are positive because the lost revenues from not tracking stock variations as closely are smaller than the penalties of policy adjustment that are incurred if managers try to track stock variations more tightly.

\begin{figure}
%\epsfig{figure=Figure5.eps,width=4in}
\caption{Ignoring the cost of policy adjustment results in greater profits from fishing, but even greater costs for adjusting the harvest quotas each year.}
\end{figure}

Table 1 compares these different contributions, namely the $NPV$ lost by assuming policy adjustment costs when none are present (first entry in each cell, $[1]-[3]$ in the equations)) and the $NPV$ lost when ignoring policy adjustment costs when they are present (second entry in each cell of the table, contributions $([1]-[2])-([3]-[4]))$ in the equations) across the three different functional forms. Specifically, the table shows how these values change as we vary the severity of policy adjustment costs and the underlying environmental variability. In each case, values are shown as percentages of the maximum expected $NPV$ in the base case where no policy adjustment costs apply or are assumed to apply $NPV_0({\bf h_0^*})$.

\begin{table}
\begin{tabular}{l|l l|rr|rr|rr}
 \multicolumn{1}{c|}{Penalty}& \multicolumn{2}{c|}{Environmental}&\multicolumn{6}{c}{Adjusment cost ($\% NPV_0 ({\bf h_0^*})$)}  \\ 
\multicolumn{1}{c|}{Function}& \multicolumn{2}{c|}{Variability}& \multicolumn{2}{c}{$90\%$} &\multicolumn{2}{c}{$80\%$} & \multicolumn{2}{c}{$70\%$} \\ \hline 
Linear, $\Pi_1$ & Low & $\sigma_Z=XX$ & Val & Val & Val & Val & Val & Val \\ 
 &  Medium & $\sigma_Z=XX$ & Val & Val & Val & Val & Val & Val \\  
&  High & $\sigma_Z=XX$ & Val & Val & Val & Val & Val & Val \\ 
&  &  &  &  &  &  &  &  \\ 
Quadratic, $\Pi_2$  & Low & $\sigma_Z=XX$ & Val & Val & Val & Val & Val & Val \\ 
 &  Medium & $\sigma_Z=XX$ & Val & Val & Val & Val & Val & Val \\  
&  High & $\sigma_Z=XX$ & Val & Val & Val & Val & Val & Val \\ 
&  &  &  &  &  &  &  &  \\ 
Fixed fee, $\Pi_3$  & Low & $\sigma_Z=XX$ & Val & Val & Val & Val & Val & Val \\ 
 &  Medium & $\sigma_Z=XX$ & Val & Val & Val & Val & Val & Val \\  
&  High & $\sigma_Z=XX$ & Val & Val & Val & Val & Val & Val 
\end{tabular}
\caption{Overall cost of assuming policy adjustment costs apply when they are absent (first value) or from ignoring them when they are present (second value). These overall costs are shown for different severities of policy adjustment costs (columns) and levels of environmental variability (rows) and for three different functional forms for policy adjustment costs ($\Pi_i$ for $ i=1-3$). Values expressed as percentages of the maximum expected net present value when no policy adjustment costs apply and this is known to managers ($ NPV_0 ({\bf h_0^*}) $). }
\end{table}

MORE DETAILING WHEN WE HAVE THE TABLE.

\section{Discussion}
TO COME PENDING WHAT THE RESULTS SHOW.
\begin{itemize}
\item From Meeting 3: Interest in how the inclusion of these costs would operationally put a population at greater risk of extinction (e.g. if including the transaction costs increases the variance and autocorrelation of $N$ when subject to the optimal policy). Should expect this, because as the transaction costs become infinite, you would never change your policy which puts you in the world of open loop control - TAC fixed for all time, which we know puts the stock at greater risk of extinction.
\item On Table 1 should flag that might also be good to look at autocorrelated environmental noise and how that affects thing. Here we look at how the optimal policy induces more color in the stock size EVEN though the environmental variability going into it is white noise. - QUERY - HOW MUCH AUTOCORRELATION INDUCED BY STOCK DYNAMICS IN THE ABSENCE OF HARVESTING
\item for case of bluefin, interpreting  (1), (2), (3), and (4) in terms of how much you would have available to pay the Japanese and Canadians to convince them to participate in an expedited process to change TACs. Similarly for other contexts.
\item   Comparison of the optimal policy solution to the Reed model, traditional economic smoothing penalty - which now appears in SI
\item  Comparison between the different functional forms -- smoothing (L2)
  non-smoothing (L1), and de-stablizing (fixed).
\item   Induced costs (relative to free adjustment) vs direct costs (paid for adjusting) 
\item   Contrast steady-state results to dynamic solutions under stochastic shocks.
\end{itemize}

\textbf{Key conclusions:}
\begin{enumerate}
  \item \textbf{Lesson for modelers}: Ignoring the reality of policy costs leads to less effective management (decreased value)  (increased extinction risk?)
  \item \textbf{Lesson for policy makers}: Decreasing adjustment costs not only saves direct costs, but permits higher-value solutions.
\end{enumerate}

\end{document}

dvips -o temp.ps temp

### 2013-11-07 inst/examples/policycosts/writeup.Rmd
writeup updated
combine code and text

@@
 opts_chunk$set(cache=TRUE, cache.path="writeup/")
+opts_knit$set(upload.fun=socialR::flickr.url)
 ```
@@
 
-```{r graphing-options, include=FALSE}
+```{r graphing-options, include=TRUE}
 opts_knit$set(upload.fun = socialR::flickr.url)
@@
                tidy=FALSE, comment=NA, message=FALSE, warning=FALSE)
-theme_notebook <- theme_grey() + 
-                  theme(plot.background = 
-                          element_rect(fill = "transparent",colour = NA),
-                        panel.grid.minor = 
-                          element_line(colour = "transparent"))
-theme_set(theme_notebook)
+opts_chunk$set(echo=FALSE)
+theme_set(theme_bw())
 ```
@@
 L1 <- function(c2) function(h, h_prev)  c2 * abs(h - h_prev) 
-free_increase <- function(c2) function(h, h_prev)  c2 * abs(pmin(h - h_prev, 0)) # increasing harvest is free
-free_decrease <- function(c2) function(h, h_prev)  c2 * pmax(h - h_prev, 0) # decreasing harvest is free
 fixed <-  function(c2) function(h, h_prev) c2 * as.numeric( !(h == h_prev) )
@@
 none <- function(h, h_prev)  0
-penaltyfns <- list(L2=L2, L1=L1, free_decrease=free_decrease, fixed=fixed, free_increase=free_increase)
+penaltyfns <- list(L2=L2, L1=L1, fixed=fixed)
 ````
@@
 fees <- melt(fees, id="c2")
+
+fees <- subset(fees, variable %in% c("L1", "L2", "fixed"))
 ggplot(fees, aes(c2, value, col=variable)) + geom_point() + geom_line()
@@
 values <- apply(index, 1, function(x) dt_npv[x[1], ][as.integer(x[2]), ]$value)
-
 percent.error <- (values - ((1-reduction)*npv0)) / ((1-reduction)*npv0)* 100
-
 print_npv <- data.frame(model=index$variable, "value realized"=values, 
@@
 
-```{r npv_table, dependson="print_npv"} 
+```{r npv_table, dependson="print_npv", results='asis'} 
 library(xtable)
@@
 fixed_policy <- policies$fixed[[apples_index["fixed"]]]$D
-free_increase_policy <- policies$free_increase[[apples_index["free_increase"]]]$D
-free_decrease_policy <- policies$free_decrease[[apples_index["free_decrease"]]]$D
-quad_policy <- policies$quad[[apples_index["quad"]]]$D
 ```
@@
 ``` {r simulate_policy, dependson=c("policynames", "apples")}
-quad_profit <- profit_harvest(price = price, c0 = c0, c1 = apples["quad"])
 
 reps <- 1:100
-names(reps) = paste("rep", 1:10, sep="_")
+names(reps) = paste("rep", 1:length(reps), sep="_") # treat as a factor
+seeds <- 1:100
+
 sims <- list(
@@
                       L1_policy, z_g, z_m, z_i, 
-                      opt$D, profit=profit, penalty=L1(apples["L1"]), seed=seed)), 
+                      opt$D, profit=profit, penalty=L1(apples["L1"]), seed=seeds[x])), 
   L2 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                       L2_policy, z_g, z_m, z_i, 
-                      opt$D, profit=profit, penalty=L2(apples["L2"]), seed=seed)),
+                      opt$D, profit=profit, penalty=L2(apples["L2"]), seed=seeds[x])),
   fixed = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                          fixed_policy, z_g, z_m, z_i, 
-                         opt$D, profit=profit, penalty=fixed(apples["fixed"]), seed=seed))
+                         opt$D, profit=profit, penalty=fixed(apples["fixed"]), seed=seeds[x]))
 
@@
                       L1_policy, z_g, z_m, z_i, 
-                      opt$D, profit=profit, penalty=none, seed=seed)), 
+                      opt$D, profit=profit, penalty=none, seed=seeds[x])), 
   L2 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                       L2_policy, z_g, z_m, z_i, 
-                      opt$D, profit=profit, penalty=none, seed=seed)),
+                      opt$D, profit=profit, penalty=none, seed=seeds[x])),
   fixed = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                          fixed_policy, z_g, z_m, z_i, 
-                         opt$D, profit=profit, penalty=none, seed=seed))
+                         opt$D, profit=profit, penalty=none, seed=seeds[x]))
 )
@@
 
-error_costs
+cbind(error_costs, sigma_g = sigma_g, reduction = reduction)
 
@@
 
-```{r error_costs_table} 
+```{r error_costs_table, results='asis'} 
 print(xtable(error_costs), type="html")
@@
 ```{r p1, dependson="tidy", fig.width=12}
-p1 <- ggplot(dt) +
+p1 <- ggplot(subset(dt, replicate %in% names(reps)[1:5])) +
   geom_line(aes(time, alternate), col="grey20", lwd=1) +
-  geom_line(aes(time, fishstock), col=rgb(0,0,1,.8)) + facet_wrap(~penalty_fn) + 
+  geom_line(aes(time, fishstock), col=rgb(0,0,1,.8)) + 
+  facet_grid(replicate~penalty_fn) + 
   labs(x="time", y="stock size", title = "Stock Dynamics")
@@
 ```{r Figure3, dependson="tidy", fig.width=12}
-p2 <- ggplot(dt) +
+p2 <- ggplot(subset(dt, replicate %in% names(reps)[1:5])) +
   geom_line(aes(time, harvest_alt), col="grey20", lwd=1)  +
   geom_line(aes(time, harvest), col=rgb(0,0,1,.8)) + 
-  facet_wrap(~penalty_fn) + 
+  facet_grid(replicate~penalty_fn) + 
   labs(x="time", y="havest intensity (fish taken)", title = "Harvest Policy Dynamics")
@@
                          fixed_policy, z_g, z_m, z_i, 
-                         opt$D, profit=profit, penalty=fixed(apples["fixed"])),
-  increase = simulate_optim(f, pars, x_grid, h_grid, x0, 
-                            free_increase_policy, z_g, z_m, z_i, 
-                            opt$D, profit=profit, penalty= free_increase(apples["increase"])),
-  decrease = simulate_optim(f, pars, x_grid, h_grid, x0, 
-                            free_decrease_policy, z_g, z_m, z_i, 
-                            opt$D, profit=profit, penalty= free_decrease(apples["decrease"])),
-  quad = simulate_optim(f, pars, x_grid, h_grid, x0, 
-                            quad_policy, z_g, z_m, z_i, 
-                            opt$D, profit=quad_profit, penalty= none)
+                         opt$D, profit=profit, penalty=fixed(apples["fixed"]))
+#  increase = simulate_optim(f, pars, x_grid, h_grid, x0, 
+#                            free_increase_policy, z_g, z_m, z_i, 
+#                            opt$D, profit=profit, penalty= free_increase(apples["increase"])),
+#  decrease = simulate_optim(f, pars, x_grid, h_grid, x0, 
+#                            free_decrease_policy, z_g, z_m, z_i, 
+#                            opt$D, profit=profit, penalty= free_decrease(apples["decrease"])),
+#  quad = simulate_optim(f, pars, x_grid, h_grid, x0, 
+#                            quad_policy, z_g, z_m, z_i, 
+#                            opt$D, profit=quad_profit, penalty= none)
   ))
@@
   geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
-  geom_line() + xlab("Fraction of NPV lost to costs")
+  geom_line() + 
+  xlab("Fraction of NPV lost to costs") +
+  scale_x_continuous(limits=c(0, 0.4))
 
@@
   geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
-  geom_line() + xlab("Fraction of NPV lost to costs")
+  geom_line() + xlab("Fraction of NPV lost to costs")+
+  scale_x_continuous(limits=c(0, 0.4)) 
 Fig4a
@@
   geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
-  geom_line() + xlab("Fraction of NPV lost to costs")
+  geom_line() + xlab("Fraction of NPV lost to costs")+
+  scale_x_continuous(limits=c(0, 0.4))
 
@@
   geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
-  geom_line() + xlab("Fraction of NPV lost to costs")
+  geom_line() + xlab("Fraction of NPV lost to costs") +
+  scale_x_continuous(limits=c(0, 0.4)) 
 FigS4a

### 2013-11-07 inst/doc/policycosts/policycosts.tex
pdf

--- 2012-10-23 inst/doc/policycosts/policycosts.tex
@@
-\documentclass[authoryear, review, 12pt]{elsarticle}
-\usepackage{amssymb,amsmath,amsfonts,graphicx}
-\bibliographystyle{elsarticle-harv}
-%\usepackage{natbib} % already loaded by elsarticle
-%\biboptions{sort&compress} % For natbib
-%\usepackage{hyperref} % already loaded by elsarticle
-%\hypersetup{breaklinks=true, pdfborder={0 0 0}}
+\documentclass{article}\usepackage{graphicx, color}
+%% maxwidth is the original width if it is less than linewidth
+%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
 
-\usepackage[hyphens]{url}
+\definecolor{fgcolor}{rgb}{0.2, 0.2, 0.2}
+\newcommand{\hlnumber}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlfunctioncall}[1]{\textcolor[rgb]{0.501960784313725,0,0.329411764705882}{\textbf{#1}}}%
+\newcommand{\hlstring}[1]{\textcolor[rgb]{0.6,0.6,1}{#1}}%
+\newcommand{\hlkeyword}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
+\newcommand{\hlargument}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
+\newcommand{\hlcomment}[1]{\textcolor[rgb]{0.180392156862745,0.6,0.341176470588235}{#1}}%
+\newcommand{\hlroxygencomment}[1]{\textcolor[rgb]{0.43921568627451,0.47843137254902,0.701960784313725}{#1}}%
+\newcommand{\hlformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
+\newcommand{\hleqformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
+\newcommand{\hlassignement}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
+\newcommand{\hlpackage}[1]{\textcolor[rgb]{0.588235294117647,0.709803921568627,0.145098039215686}{#1}}%
+\newcommand{\hlslot}[1]{\textit{#1}}%
+\newcommand{\hlsymbol}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlprompt}[1]{\textcolor[rgb]{0.2,0.2,0.2}{#1}}%
 
-\usepackage{lineno}
-\linenumbers
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
 
-\usepackage{subfigure}
-%\usepackage[nomarkers]{endfloat}
-\renewcommand{\listoffigures}{} % but suppress these lists
-\renewcommand{\listoftables}{} % suppress these lists
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
 
-%% Redefines the elsarticle footer
-\makeatletter
-\def\ps@pprintTitle{%
-\let\@oddhead\@empty
-\let\@evenhead\@empty
-\def\@oddfoot{\it \hfill\today}%
-\let\@evenfoot\@oddfoot}
-\makeatother
-% A modified page layout
-\textwidth 6.75in
-\oddsidemargin -0.15in
-\evensidemargin -0.15in
-\textheight 9in
-\topmargin -0.5in
-
-\usepackage{microtype}
-\usepackage{fancyhdr}
-\pagestyle{fancy}
-\pagenumbering{arabic}
-
-\usepackage[pdftex, usenames]{color}
-\definecolor{darkblue}{rgb}{0,0,0.5}
-\definecolor{darkgreen}{rgb}{0,0.5,0}
-\newcommand{\cdb}[1]{{\it \color{darkgreen} #1}}
+\usepackage{alltt}
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 
 \begin{document}
-\begin{frontmatter}
-\title{Policy Costs}
-\author[cpb]{C. Boettiger\corref{cor1}}
-\ead{cboettig@ucdavis.edu}
-\author[melbourne]{M. Bode}
-\author[esp]{J. Sanchirico}
-\author[utk-econ]{J. LaRiviera}
-\author[cpb,esp]{A. Hastings}
-\author[utk-eeb]{P. Armsworth}
-\cortext[cor1]{Corresponding author}
-\address[cpb]{Center for Population Biology, University of California, Davis, California 95616, USA}
-\address[esp]{Department of Environmental Science \& Policy, University of California, Davis, CA 95616, USA}
-\address[utk-econ]{Department of Economics, University of Tennessee, Knoxville, TN 37996, USA}
-\address[utk-eeb]{Department of Ecology and Evolutionary Biology, University of Tennessee, Knoxville, TN 37996, USA}
-\address[melbourne]{Australian Research Council Centre of Excellence for Environmental Decisions, University of Melbourne, School of Botany,
-Parkville, Melbourne, VIC 3010, Australia}
 
-\begin{abstract}
-\cdb{Carl's comments \& questions added in green}
-\end{abstract}
-\begin{keyword}
-  optimal control \sep management \sep stochastic dynamic programming \sep fisheries 
-\end{keyword}
+\title{Optimal management of a stochastically varying population when policy adjustment is costly}
 
-\end{frontmatter}
+%\titlerunning{Short form of title}        % if too long for running head
+
+\author{Carl Boettiger    \\
+       Michael Bode      \\
+        James N. Sanchirico \\
+Jacob LaRiviere \\
+Alan M. Hastings\\
+Paul R. Armsworth
+}
+
+\maketitle
 
 \section{Introduction}
-
-\emph{Could use input from those most familiar with this literature to flush this out more.}
 
@@
 
-(See Figure~\ref{fig:1} which motivates the importance of considering policy costs by comparing a theoretically optimal policy over time to a typical real world policy over time).
+\emph{Develop a figure to insert here comparing quotas that were set to the stock size estimated at that time in the stock assessment for two different fish stocks.
+We choose the two stocks to highlight variation in how responsive management can be.
+Suggested halibut and bluefin tuna.}
 
-\begin{figure}[ht]
-  \begin{center}
-    \subfigure[Optimal Policy]{\includegraphics[width=.5\textwidth]{figure/optimal_harvest}\label{fig:1a}}
-    \subfigure[Typical Policy]{\includegraphics[width=.5\textwidth]{figure/typical_policy}\label{fig:1b}}
-  \end{center}
-  \caption{\ref{fig:1a} shows a typical solution found by an optimal
-  control solution by stochastic dynamic programming for the optimal catch
-  quota in a managed fishery.  Note that the solution tends to track the
-  noise, resulting in a highly variable policy.  \ref{fig:1b} shows the
-  actual quotas set over the past decade for Bluefin tuna, which show
-  great intertia to change despite considerable movement in the stock
-  dynamics.  \cdb{Conceptual picture illustrating the need to account
-  for costs to changing policy. Current images are just placeholders.
-  B should be replaced with real data, perhaps tuna quotas from Paul.
-  Should stock dynamics actually be shown?}}
-  \label{fig:1}
-\end{figure}
-
-%Optimal management of ecosystems and natural resources often involves
-%frequent adjustment of a control variable in response to the observed
-%state of a system. When this control is set in a policy-making process,
-%such as determining a fishing quota, it may be more costly to change
-%the policy in response to new information than to continue with the
-%status quo ~\citep{Bohm1974, Xepapadeas1992}.  A management strategy that
-%is optimal when adjustment costs are free may be costly and inefficient
-%when these costs are present.  Meanwhile, this inertia to policy change
-%introduces a two-fold cost to optimal management solutions that account
-%for it: once in direct costs of changing policy, and another in the
-%differences from optimality.
-
-\subsection{Types of real world policy costs}
-
-\begin{itemize}
-  \item A discussion of capital adjustment costs, smoothing, \emph{e.g.} \citet{Singh2006}.
-  \item Historical context, \emph{e.g.} discussion of \citep{Bohm1974, Reed1979, Xepapadeas1992}.  
-\end{itemize}
-\subsection{Stochastic fisheries model}
-\begin{itemize}
-\item Historical context of the Reed (1979) model.  
-\item Discuss the importance and relevance of stochastic, discrete time models, which frequently yield highly variable solutions since the policy tracks the shock.  
-\end{itemize}
+Empirics suggest not always as responsive as Reed solution.
+Explore conditions under which that makes sense.
+Idea is that regulator’s objective sometimes may not be `raw' NPV, but rather NPV with some penalties on fast changes.
+Possible reasons: pure administrative transaction cost of changing policies (reaching agreement), fishermens' preferences for less variable quotas, processing plants' preferences for less variable quotas especially if tied into contracts for canning and so forth.
+But we do not know what functional form of any such policy adjustment costs takes and it will be a lot of work to estimate it.
+Here we explore several plausible candidate functional forms that each reflect different ways these policy adjustment costs could work.
+Would be good to know if differences between functional forms is particularly important.
 
@@
 
-\subsection{Model setup}
+ Fish population dynamics / state equation.  We will assume Beverton-Holt dynamics with multiplicative environmental noise
+    \begin{equation} 
+      N_{t+1} = Z_t \frac{A N_t}{1 + B N_t}, 
+\label{eq:state_equation}
+    \end{equation}
+where $N_t$ the stock size, $Z_t$ gives the stochastic shocks, which we assume are lognormally distributed and $A$ and $B$ are positive constants. HARVESTING SHOULD APPEAR IN THIS EQUATION.
 
-\begin{itemize}
-  \item   Fish population dynamics / state equation.  We will assume Beverton-Holt dynamics,
+We assume managers set an annual quota for harvesting $h_t$ (the control variable) after observing the stock size that year $N_t$ (the state variable), but while still being uncertain about future environmental conditions and stock sizes.
+Through time, this gives a time path of management actions ${\bf h}=(h_1,h_2,\dots)$ that depend on the stock sizes that were observed (a state dependent control rule).
+
+We assume that managers choose annual quotas to maximize the expected net present value (NPV) of the fishery.
+We take as a base case the situation where there are no costs associated with policy adjustment and the managers' objective is
 \begin{equation}
-      X_{t+1} = Z_t \frac{A X_t}{1 + B X_t}, 
+\max_{{\bf h}}\mathbf{ E} ( NPV_{0} )=\max_{{\bf h}} \sum_0^\infty \mathbf{E} \left( \displaystyle \frac{\Pi_0(N_t,h_t)}{(1+\delta)^{t+1}} \right)
+\label{eq:objective}
 \end{equation}
-where $Z_t$ gives the stochastic shocks.
-$Z_t$ may be distributed log-normally \footnote{though this violates the self-sustaining property of~\citet{Reed1979}, such that the optimal constant-escapement level $S$ in the stochastic model is greater than the optimal escapement in the deterministic scenario.}
+where $\mathbf{E}$ is the expectation operator, $\delta>0$ is the discount rate and $\Pi_0$ is the net revenue from operating the fishery in a given year.
+In this base case, we assume the annual net revenue from fishing is
+  \begin{equation} 
+    \Pi_0(N_t,h_t) = p h_t -  c_0 E_t
+\label{eq:annual_netrevenue}
+  \end{equation}
+  where $E_t$ represents
+  fishing effort.
+We assume catch is proportional to stock size and effort expended fishing that year, $h_t=qE_tN_t$ and constant $q>0$ is the catchability coefficient.
+In Eqn.~\ref{eq:annual_netrevenue}, $p$ is the price per unit harvest and $c_0$ the cost of fishing and we assume $p>0$ and $c_0>0$.
 
-\item   Fishing profit function 
+Taken together this objective function (\ref{eq:objective}) and the state equation (\ref{eq:state_equation}) define a stochastic dynamic programming problem that we solve using backwards recursion via Bellman's equation.
+We denote the resulting state-dependent, optimal control as ${\bf h_0^*}$.
+PRESUMABLY YOU USED A FINITE TERMINAL TIME IN WHICH CASE WE NEED TO REVISE TO REFLECT HOW YOU HANDLED THAT.
+
+\subsection*{Costs of policy adjustment}
+We compare this base case to three alternative problem formulations, each reflecting different plausible functional forms that costs of policy adjustment could take.
+In each, we assume managers can adjust the quota set in the fishery $h_t$ in a given year and that any policy adjustment costs are associated with changes to this control variable.
+
+First we assume that policy adjustment costs are directly proportional to the magnitude of the change in policy being proposed, such that larger changes to annual harvesting quotas incur greater policy adjustment penalties.
+Specifically, we replace $\Pi_0$ in the $NPV_0$ equation with
 \begin{equation}
-    \Pi_0(x,h) = p h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x} \label{profit}
+  \Pi_{1}(N_t,h_t, h_{t-1}) = \Pi_0 - c_1  |  h_t - h_{t-1} | \,.
 \end{equation}
-  where $h$ is the harvest level, $x$ the stock size, $h/x$ represents
-  fishing effort, $p$ the price per unit harvest.  The coefficient $c_1$
-  introduces a quadratic cost to effort, a typical way to introduce
-  smoothing~\citep[\emph{e.g.}][]{Singh2006}.  For simplicity, we will consider $c_0 =
-  c_1 = 0$.
 
-\item
-Policy cost function: L1, L2, fixed fee, asymmetric, are introduced
-as modifications to the cost function that depend on the action
-taken in the previous time-step.  (This makes the previous action part
-of the state space).   All cost functions are characterized in terms
-of the coupling coefficient $c_2$.  (Because $c_2$ takes different units
-and strength of interaction under the different functional forms, it is
-necessary to calibrate the choice of this coefficient such that these
-penalties can be compared directly, as described in the next section.)
+Next we continue to assume that policy adjustment costs depend on the magnitude of the change in policy being proposed.
+However, we consider a case where this dependence is nonlinear with big changes in policy being disproportionately expensive:
+\begin{equation}
+  \Pi_{2}(N_t,h_t, h_{t-1}) = \Pi_0 - c_2 (  h_t - h_{t-1})^2 \,.
+\end{equation}
 
-  \begin{align} 
-    \Pi_{L_1}(x_t,h_t, h_{t-1}) &= \Pi_0 + c_2 \operatorname{abs}\left( h_t - h_{t-1} \right) \label{L1} \\
-    \Pi_{L_2}(x_t,h_t, h_{t-1}) &= \Pi_0 + c_2 \left( h_t - h_{t-1} \right)^2 \label{L2} \\
-    \Pi_{\textrm{fixed}}(x_t,h_t, h_{t-1}) &= \Pi_0 + c_2 \mathbb{I}(h_t, h_{t-1})  \label{fixed_fee} \\
-    \Pi_{\textrm{asym}}(x_t,h_t, h_{t-1}) &= \Pi_0 + c_2 \operatorname{max}\left( h_t - h_{t-1}, 0 \right) \label{asym}
-  \end{align}
-  Where $\mathbb{I}(a,b) = 0$ for $a \neq b$ and  $\mathbb{I}(a,b) = 1$ for $a = b$.
+Finally, we assume instead that there is a fixed cost associated with any adjustment of policy, regardless of how large that adjustment might be
+\begin{equation}
+  \Pi_{3}(N_t,h_t, h_{t-1}) = \Pi_0 - c_3 (1-\mathbf{I}(h_t, h_{t-1}))  \,,
+\end{equation}
+where indicator function $\mathbf{I}(h_t, h_{t-1})$ takes the value 1 if $h_t=h_{t-1}$ and zero otherwise.
+For each $\Pi_i$, we can then define a new objective function $NPV_i$ similar to that in Eqn.~\ref{eq:objective}.
 
-\item   Economic discounting, boundary conditions, constraints, Bellman equation, SDP solution method on finite time horizon.  
-\item   Choice of model parameters 
-\end{itemize}
+Taken together with the state equation (Eqn.~\ref{eq:state_equation}), each of these new objective functions defines a different stochastic dynamic programming problem.
+Again, we solve them numerically using backwards recursion.
+To include costs of policy adjustment, we expand the state space to include both the current stock size and the management action taken on the previous time step $(N_t,h_{t-1})$.
+For each new objective function $\max NPV_i$, we denote the corresponding optimal control policy $ {\bf h_i^*} $.
 
-\subsection{Apples to apples comparisons}
+In addition in the Supplementary Material, we compare our results with a more conventional fisheries economic formulation in which additional costs are applied to the control variables themselves, as opposed to adjustments to the controls: $ \Pi_4 (N_t,h_t) = p h_t -  c_0 E_t-c_4E_t^2$.
+Additional costs of this form tend to have  a smoothing effect on optimal quotas, but also change the long-term average stock size or quota size that is optimal.
 
-% From Jake:
+\subsection*{Choice of parameters}
 
-The fact that there is no uniform metric for comparing different functional forms of the penalty function complicates identifying the implications of various penalty functions on optimal management.
-Put another way, it is unclear what parameter values should be used for each functional form in order to compare the relative effect of each penalty function on optimal management.
-To address this issue, consider the following rule for comparing functional forms inspired by Bovenberg, Goulder and Gurnery (2005) and Bovenberg, Goulder and Jacobsen (2008).
-By definition, adding a constraint, in the form of a penalty function, to the social planner’s objective function will reduce the NPV of the resource in addition to affecting the optimal management policy.
-For example, each individual penalty function equation (3)-(6) is multiplied by a constant C2.
-As the magnitude of the penalty function increases (e.g., C2 increases), the NPV value of the resource decreases.
-Importantly, though, the rate at which the NPV is affected by a given increase in magnitude of the penalty function is different for different penalty functions.
-One way to compare the relative impact of penalty functions on optimal management is to choose parameters for the penalty function that imply the same level of NPV conditional on optimal management.
+Each of the policy adjustment cost function is characterized in terms
+of a cost coefficient $c_i$.
+However, $c_i$ takes different units for each  functional form.
+Therefore, if seeking to compare the relative effect of each penalty function on optimal management, it is unclear what parameter values should be used.
+To address this issue, we calibrate choices of $c_i$ so that each has a comparable impact on the optimal net present value of fishery, broadly following the example of Bovenberg, Goulder and Gurnery (2005) and Bovenberg, Goulder and Jacobsen (2008).
 
-Figure 2 shows this comparison criterion graphically.
-Each curve plots the percentage change in NPV relative to the unconstrained problem for a given penalty function over different magnitudes of that penalty function, C2, given optimal management.
-There are two important features in Figure 2.
-First, the optimal management policy is not constant across penalty function.
-This will be discussed in detail below.
-Second, the rate of change in NPV as a function of the magnitude of the penalty function varies both within and across policies.
-For example, the existence of a relatively small L2 penalty function dramatically affects the resource’s value initially but there is little marginal effect on NPV for relatively large L2 penalty functions.
-Conversely, the rate of change in NPV for the fixed penalty function is roughly constant over all ranges of penalty function magnitudes.
+Figure 1 shows the calibration graphically.
+Each curve plots the change in maximum expected NPV for a given penalty function as the penalty cost parameter is increased.
+In each case, the figure shows maximum expected NPV with policy adjustment costs as a proportion of the maximum expected NPV available in the basic problem $NPV_0({\bf h_0^*})$ without policy adjustment costs.
 
-To compare the impact of penalty functions on optimal management, we select penalty magnitudes that make the resource worth 80\% of its unconstrained value.
-The dashed vertical lines in Figure 2 map the needed penalty function magnitude, C2, to each penalty function such that the resource is worth 80\% of its unconstrained value when optimally managed.
-We choose 80\% somewhat arbitrarily but the method is applicable to any NPV level and the qualitative effects on management are robust for other levels.
+To compare the impact of penalty functions on optimal management across the different functional forms, we select penalty cost coefficients that induce the same reduction in maximum expected NPV.
+For example, the dashed vertical lines in Figure 1 map the needed cost coefficient $c_i$, for each penalty function, such that the fishery is worth 80\% of its unconstrained value when optimally managed.
 
-Bovenberg, AL, Goulder LH, and Gurney DJ (2005).  “Efficiency Costs of Meeting Industry-Distributional  Constraints Under Environmental Permits and Taxes” RAND Journal of Economics. 36(4): 951-  971.
-
-Bovenberg, AL, Goulder LH, and Jacobsen MR (2008).  “Costs of Alternative Policy Instruments in the    Presence of Industry Compensation Requirements” Journal of Public Economics. 92: 1236-1253.
-
-%% end-Jake
-
-We compare the impact of the different functional forms for the penalty
-function at a value of the penalty scaling parameter in each model that
-induces an equivalent net present value to the stock when optimally
-managed under this penalty. This value represents the expected net
-present value before the costs of policy adjustment are paid, Figure~\ref{fig:apples}
+Other parameters in the model are chosen - HOW?
 
 \begin{figure}
-    \begin{center}
-\includegraphics[width=.8\textwidth]{figure/npv0.png}
-\caption{\textbf{Net present value by functional form of penalty.} Horizontal axis shows the coefficient $c_2$ governing the magnitude of the policy cost, while vertical axis shows fraction of the stock value dissipated by the policy cost.
-The horizontal line indicates a value of the stock that is 80\% of the adjustment-free value.
-Selecting the coefficient $c_2$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/Figure_1}
+
+\end{knitrout}
+
+\caption{\textbf{Expected net present value by functional form of penalty.} Horizontal axis shows the coefficient $c_i$ governing the magnitude of the policy cost, while vertical axis shows fraction of the maximum expected net present value dissipated by the policy cost.
+The horizontal line indicates a value of the stock that is 80\% of the maximum expected value in the absence of policy adjustment costs, $NPV_0({\bf h_0^*})$.
+Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.
 }
-\label{fig:apples}
-\end{center}
 \end{figure}
@@
 \section{Results}
-\subsection{Characterize and compare functional forms of costs}
+\subsection*{Effect of policy adjustment costs on optimal quotas and stock sizes}
+Figure 2 shows the impact that the adjustment cost has on the optimal policy.
+Each panel is generated against the same sequence of random shocks so that they can be compared directly.
+Figure 3 (TO COME) shows the corresponding stock sizes.
+In each case, the optimal solution without any adjustment cost is shown in black and the policy induced by optimization under the given adjustment penalty (equivalent to a 25\% reduction in maximum expected NPV) is overlaid in blue.
 
-Figure~\ref{fig:shapes} shows the impact the adjustment cost has on the optimal policy.
-The $L_1$-norm costs tend to avoid small adjustments to the policy, resulting in long periods of constant policy followed by sudden bursts of adjustment.
-In contrast, the $L_2$-norm tracks all of the changes made by the cost-free policy, but with smaller magnitude.
-The fixed fee only makes large adjustments much like the $L_1$, as expected where the adjustment magnitude does not impact the cost.
-Asymmetric ($L_1$) adjustment costs do not appear to show more directional bias than any of the symmetric costs.
-Note that while the cost-free optimal strategy corresponds to a constant-escapement policy as derived in~\citet{Reed1979}, any of the policy-cost scenarios deviate from such a policy.
-    \cdb{
-    \begin{itemize}
-      \item All of these should use the same sequence of shocks.  
-      \item Don't plot all four curves on the same graph.  
-      \item Omit stock dynamics?
-      \item Consider not violating the self-sustaining property, which should also guarantee that fishing never stops.   
-    \end{itemize}
-    }
-
-\cdb{ In terms of a policy set on escapement instead of harvest, our solutions are actually more volatile than~\citet{Reed1979}.
-Maybe this leads to a discussion of what the control policy should be defined in terms of (i.e.
-catch vs escapement)?
-Surely the simplicity of the constant-escapement rule has led to it's popularity in some part due because that simplicity avoids adjustment costs?}
+When considering the first formulation of policy adjustment costs ($\Pi_1$), the first  panel of Figure 2 shows a typical pattern, in which the optimal policy tends to avoid small policy adjustments, resulting in long periods of constant policy followed by sudden bursts of adjustment.
+This results in a relatively step-like policy pattern.
+In contrast, the second formulation $\Pi_2$ disproportionately penalizes large policy adjustments.
+The corresponding optimal policy tracks all of the changes made by the cost-free policy, but with smaller magnitude.
+This results in a smoother $h_t$ curve, one that undershoots the larger oscillations seen in the cost-free optimum in favor of a policy that changes incrementally each yearl.
+Finally, the optimal policy for the third, `fixed fee' formulation ($\Pi_3$) only makes large adjustments, as one might expect, because the magnitude of the adjustment made is not reflected in the resulting penalty.
+Whereas the optimal solution for $\Pi_1$ attempts to accommodate the large oscillations at the end of the period shown (time steps $t=47-49$) with a constant quota in between the extremes, the fixed fee version takes the opposite approach of one very large swing.
+MORE DETAILING TO COME WHEN WE HAVE THE FIGURES
 
 \begin{figure}
-    \begin{center}
-      \subfigure[$L_1$]{\includegraphics[width=.45\textwidth]{figure/7258516896_5c89f034d5_o.png}\label{fig:L1}}
-      \subfigure[$L_2$]{\includegraphics[width=.45\textwidth]{figure/7258563112_2f5f9ffecd_o.png}\label{fig:L2}}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/Figure_2}
 
-      \subfigure[Fixed costs]{\includegraphics[width=.45\textwidth]{figure/7258506664_d6235e5f8e_o.png}\label{fig:fixed}}
-      \subfigure[Asymmetric costs]{\includegraphics[width=.45\textwidth]{figure/7258432026_d6f8179f54_o.png}\label{fig:asym}}
-  \end{center}
-  \caption{Individual realizations of management under the different functional forms of adjustment costs.
-\textbf{Green} lines show the cost-free optimal harvest levels, \textbf{black} lines show the corresponding stock dynamics under that management.
-\textbf{Purple} lines show the optimal harvest level under the specified adjustment cost, under the same sequence of stochastic shocks as in the cost-free policy.
-\textbf{Blue lines} show the resulting stock dynamics.
-  } \label{fig:shapes}
-\end{figure}
+\end{knitrout}
 
-\subsection{Responses to increasing costs}
-
-The comparisons shown in Figure~\ref{fig:shapes} are made at a fixed magnitude of the policy cost equal to 80\% of the net present value derived from the cost-free optimal strategy.
-The different functional forms may also respond differently to an increasing magnitude of the adjustment cost.
-To quantify the extent to which the policy cost decreases the volatility of the proposed policy, we calculate the variance in the fishing quota over time under each policy.
-While a decrease in variance is typical of smoothing penalties and the $L_2$-norm, the patterns in Figure~\ref{fig:shapes} suggest that other functional forms still involve the same magnitude of variation, but decrease the frequency of adjustments.
-To capture this behavior we calculate the autocorrelation of the policy as the adjustment cost increases.
-These curves van be seen in Figure~\ref{fig:summarystats}.
-
-\cdb{Perhaps not clear what is comparable here and what isn't.
-Certainly we cannot compare the curves at the same value of $c_2$, as discussed in our apples to apples section.
-Not clear that we can even compare the shape of the curves though -- for instance, given the units of $c_2$ for the $L_2$ norm are different than the other norms.
-Perhaps the horizontal axis should be converted into percent of net present value of the adjustment free costs first?}
-
-\cdb{Add additional plot: Is value a linear function of policy cost, or is there a sharp transition? }
-%Must be nonlinear somewhere when adjustment costs exceed profits?
-
-\begin{figure}
-  \begin{center}
-    \subfigure[Variance]{\includegraphics[width=.45\textwidth]{figure/6850042286_ef81b74acc_o.png}\label{fig:var}}
-    \subfigure[Autocorrelation]{\includegraphics[width=.45\textwidth]{figure/6996165783_41c9894bdb_o.png}\label{fig:acor}}
-    \caption{Variance and autocorrelation as a function of the magnitude of penalty, by penalty function}\label{fig:summarystats}
-  \end{center}
-\end{figure}
-
-\subsection{Consequences of ignoring policy adjustment costs}
-
-\begin{itemize}
-  \item Distribution of profits and costs under a policy-cost scenario vs profits and costs under Reed solution, by penalty type. Figure~\ref{fig:profits_costs}.
-  \item Distribution of net present value under the policy-cost scenario vs the Reed solution, Figure~\ref{fig:npv_dist}.  
-\end{itemize}
-
-\begin{figure}
-  \begin{center}
-    \subfigure[L1]{\includegraphics[width=.45\textwidth]{figure/7751440758_99645d6e5a_o.png}\label{fig:L1cost}}
-    \caption{Ignoring the cost of policy adjustment results in greater profits from fishing, but even greater costs for adjusting the harvest quotas each year.
-Costs and profits are shown for ignoring the adjustment costs (Reed solution, purple and blue) and accounting for the adjustment (green and red).
-\cdb{Though only L1 shown for the moment, would probably show all four types.
-Possibly a table or box-and-whiskers style plot would be better?}}\label{fig:profits_costs}
-  \end{center}
+  \caption{Individual realizations of optimal harvesting strategy under the different functional forms of adjustment costs.}
 \end{figure}
@@
 \begin{figure}
-  \begin{center}
-    \subfigure[L1]{\includegraphics[width=.45\textwidth]{figure/7751440918_3b54ff2397_o.png}\label{fig:L1npv_dist}}
-    \caption{\textbf{The impact of ignoring policy costs}.
-Distribution of net present value realized over 100 simulations when adjustment costs are ignored (blue), compared to when adjustment costs are optimally accounted for (red).
-\cdb{Though only L1 shown for the moment, would probably show all four types.
-Possibly a table or box-and-whiskers style plot would be better?}}\label{fig:npv_dist}
-  \end{center}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/Figure_3}
+
+\end{knitrout}
+
+  \caption{Individual realizations of optimal stock size strategy under the different functional forms of adjustment costs.}
 \end{figure}
 
-Add two-by-two table of net present value accounting for:  ``Adjustment cost in policy calculation'' by ``adjustment cost in reality''?
+The comparisons shown in Figure 2 are for one realization (i.e.
+a particular sequence of random number draws representing environmental variability) and are made for a particular magnitude of policy adjustment costs equal to 25\% of the maximum expected net present value in the base case ($NPV_0({\bf h_0^*})$).
+Figure 4 generalizes to show how optimal harvest levels and corresponding optimal stock sizes are affected by the magnitude of the costs of policy adjustment.
+This time we show summary statistics across 50 replicate sets of environmental conditions.
+We show the impact of policy adjustment costs on the variance of both harvests and stock sizes through time; on the autocorrelation of harvests and stock sizes through time; and on the cross-correlation of harvests and stock sizes through time.
+(COMPARABLE FIGURES FOR OPTIMAL STOCK SIZES AND CROSS-CORRELATIONS OF THE TWO TO COME.)
 
-\cdb{\textbf{Further things to look at?}
-\begin{itemize}
-  \item How are costs partitioned between policy adjustments and deviation from optimality? 
-  \item Risk sensitivity: does policy inertia increase or decrease extinction risk?
-Does accounting for the policy cost increase or decrease extinction risk?
-(only in cases where extinction is possible: \emph{e.g.} in large variance, outside of Reed's self-sustaining range.
-Or Allee model)
-\end{itemize}
+We see that TO COME WHEN WE HAVE THE FIGURES
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/Figure_4a}
+
+\end{knitrout}
+
+\caption*{Figure 4a: Variance of optimal harvest rates through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.
 }
+\end{figure}
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/Figure_4b}
+
+\end{knitrout}
+
+\caption*{Figure 4b: Autocorrelation of optimal harvest rates through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.
+}
+\end{figure}
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/Figure_5a}
+
+\end{knitrout}
+
+\caption*{Figure 5a: Variance of optimal stock sizes through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.
+}
+\end{figure}
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/Figure_5b}
+
+\end{knitrout}
+
+\caption*{Figure 5b: Autocorrelation of optimal stock sizes through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.
+}
+\end{figure}
+
+\subsection*{Consequences of policy adjustment costs}
+
+Next we examine the consequences either of ignoring policy adjustment costs when they are present or assuming they are present when they are not.
+To do so, it helps to break-down the different contributions to the maximum expected $NPV_i$ when employing the optimal policy $\bf{h_i}^*$ versus when employing the policy that would be optimal were there no costs to policy adjustment $\bf{h_0}^*$.
+For example, if we take the first of the adjustment penalty forms, $\Pi_1$
+\begin{equation}
+ NPV_i( \mathbf{h_1^*} ) = \sum_{t=0}^\infty (\overbrace{ p h^*_{1,t}-c_0E^*_{1t}}^{[1]}-\overbrace{c_1 | h^*_{1,t}- h^*_{1,t-1}|}^{[2]} ) \displaystyle \frac{1}{(1+\delta)^t}
+\end{equation}
+and 
+\begin{equation}
+ NPV_i( \mathbf{h_0^*} ) = \sum_{t=0}^\infty (\underbrace{ p h^*_{0,t}-c_0E^*_{0t}}_{[3]}-\underbrace{c_1 | h^*_{0,t}- h^*_{0,t-1}|}_{[4]} ) \displaystyle \frac{1}{(1+\delta)^t}
+\end{equation}
+
+Histograms for the different contributions labelled $[1]-[4]$ here when taken across XXX replicate runs are shown are shown in Figure 5 (contribution $[1]$ red, $[2]$ green, $[3]$ blue, and $[4]$ mauve).
+The cost of assuming policy adjustments are present when in fact they are absent is given by subtracting the contribution to the first infinite sum from term $[1]$ from the contribution to the second infinite sum of term $[3]$ (red-blue in the Figure).
+(Note that convergence properties required to do this are met because we assume a positive discount rate).
+This cost is positive because the optimal controls recommended when assuming policy adjustment costs are present do not track variations in stock size as closely.
+Therefore, this harvesting strategy provides lower net revenue dockside.
+
+In contrast, the cost of ignoring policy adjustment costs when in fact they are present is given by subtracting the second infinite sum from the first (contributions $([1]-[2])-([3]-[4]))$ in the equations.
+These costs are positive because the lost revenues from not tracking stock variations as closely are smaller than the penalties of policy adjustment that are incurred if managers try to track stock variations more tightly.
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+
+{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Using\ \ as id variables}}\end{kframe}
+\includegraphics[width=\maxwidth]{figure/Figure_6}
+
+\end{knitrout}
+
+\caption{Ignoring the cost of policy adjustment results in greater profits from fishing, but even greater costs for adjusting the harvest quotas each year.}
+\end{figure}
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/Figure_7}
+
+\end{knitrout}
+
+\end{figure}
+
+Table 1 compares these different contributions, namely the $NPV$ lost by assuming policy adjustment costs when none are present (first entry in each cell, $[1]-[3]$ in the equations)) and the $NPV$ lost when ignoring policy adjustment costs when they are present (second entry in each cell of the table, contributions $([1]-[2])-([3]-[4]))$ in the equations) across the three different functional forms.
+Specifically, the table shows how these values change as we vary the severity of policy adjustment costs and the underlying environmental variability.
+In each case, values are shown as percentages of the maximum expected $NPV$ in the base case where no policy adjustment costs apply or are assumed to apply $NPV_0({\bf h_0^*})$.
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{rlrrrrrr}
+  \hline
+ & penalty\_fn & ignore\_cost & ignore\_fraction & assume\_cost & assume\_fraction & sigma\_g & reduction \\ 
+  \hline
+1 & L1 & 14536.09 & 1.00 & 16857.61 & 1.00 & 0.05 & 0.10 \\ 
+  2 & L2 & 11020.10 & 0.76 & 15538.44 & 0.92 & 0.05 & 0.10 \\ 
+  3 & fixed & 13584.97 & 0.92 & 17582.78 & 1.05 & 0.05 & 0.10 \\ 
+  4 & L1 & 9273.66 & 1.09 & 17561.81 & 1.04 & 0.05 & 0.20 \\ 
+  5 & L2 & 11020.10 & 0.76 & 15538.44 & 0.92 & 0.05 & 0.20 \\ 
+  6 & fixed & 8332.45 & 0.84 & 17401.82 & 1.03 & 0.05 & 0.20 \\ 
+  7 & L1 & -641.78 & 0.21 & 15451.25 & 0.92 & 0.05 & 0.30 \\ 
+  8 & L2 & -272586.11 & -24.90 & 11567.12 & 0.69 & 0.05 & 0.30 \\ 
+  9 & fixed & -1213.01 & -0.46 & 15519.95 & 0.92 & 0.05 & 0.30 \\ 
+  10 & L1 & 18281.97 & 1.01 & 20973.56 & 0.99 & 0.20 & 0.10 \\ 
+  11 & L2 & 12462.51 & 0.72 & 19392.85 & 0.91 & 0.20 & 0.10 \\ 
+  12 & fixed & 16691.94 & 1.03 & 20143.80 & 0.95 & 0.20 & 0.10 \\ 
+  13 & L1 & 12788.95 & 0.96 & 20663.21 & 0.97 & 0.20 & 0.20 \\ 
+  14 & L2 & 12462.51 & 0.72 & 19392.85 & 0.91 & 0.20 & 0.20 \\ 
+  15 & fixed & 12399.01 & 0.88 & 21289.21 & 1.00 & 0.20 & 0.20 \\ 
+  16 & L1 & 9099.48 & 0.73 & 19999.07 & 0.94 & 0.20 & 0.30 \\ 
+  17 & L2 & -6337.76 & -0.39 & 17765.33 & 0.83 & 0.20 & 0.30 \\ 
+  18 & fixed & 7399.01 & 0.62 & 21969.84 & 1.03 & 0.20 & 0.30 \\ 
+  19 & L1 & 30227.43 & 1.07 & 31377.07 & 0.94 & 0.50 & 0.10 \\ 
+  20 & L2 & 33472.18 & 1.00 & 33472.18 & 1.00 & 0.50 & 0.10 \\ 
+  21 & fixed & 28926.73 & 1.09 & 30500.85 & 0.91 & 0.50 & 0.10 \\ 
+  22 & L1 & 24157.93 & 1.10 & 31767.92 & 0.95 & 0.50 & 0.20 \\ 
+  23 & L2 & 19091.31 & 0.93 & 29225.46 & 0.87 & 0.50 & 0.20 \\ 
+  24 & fixed & 23573.19 & 1.02 & 30069.80 & 0.90 & 0.50 & 0.20 \\ 
+  25 & L1 & 21086.12 & 1.12 & 32035.93 & 0.96 & 0.50 & 0.30 \\ 
+  26 & L2 & 19091.31 & 0.93 & 29225.46 & 0.87 & 0.50 & 0.30 \\ 
+  27 & fixed & 17209.56 & 0.85 & 32946.24 & 0.98 & 0.50 & 0.30 \\ 
+   \hline
+\end{tabular}
+
+\caption{Overall cost of assuming policy adjustment costs apply when they are absent (first value) or from ignoring them when they are present (second value).
+These overall costs are shown for different severities of policy adjustment costs (columns) and levels of environmental variability (rows) and for three different functional forms for policy adjustment costs ($\Pi_i$ for $ i=1-3$).
+Values expressed as percentages of the maximum expected net present value when no policy adjustment costs apply and this is known to managers ($ NPV_0 ({\bf h_0^*}) $).
+}
+\end{table}
+
+MORE DETAILING WHEN WE HAVE THE TABLE.
 
 \section{Discussion}
-\cdb{Some possible things to discuss: could add others, could remove some.}
+TO COME PENDING WHAT THE RESULTS SHOW.
 \begin{itemize}
-\item   Comparison of the optimal policy solution to the Reed model
+\item From Meeting 3: Interest in how the inclusion of these costs would operationally put a population at greater risk of extinction (e.g.
+if including the transaction costs increases the variance and autocorrelation of $N$ when subject to the optimal policy).
+Should expect this, because as the transaction costs become infinite, you would never change your policy which puts you in the world of open loop control - TAC fixed for all time, which we know puts the stock at greater risk of extinction.
+\item On Table 1 should flag that might also be good to look at autocorrelated environmental noise and how that affects thing.
+Here we look at how the optimal policy induces more color in the stock size EVEN though the environmental variability going into it is white noise.
+- QUERY - HOW MUCH AUTOCORRELATION INDUCED BY STOCK DYNAMICS IN THE ABSENCE OF HARVESTING
+\item for case of bluefin, interpreting  (1), (2), (3), and (4) in terms of how much you would have available to pay the Japanese and Canadians to convince them to participate in an expedited process to change TACs.
+Similarly for other contexts.
+\item   Comparison of the optimal policy solution to the Reed model, traditional economic smoothing penalty - which now appears in SI
 \item  Comparison between the different functional forms -- smoothing (L2)
@@
 \item   Induced costs (relative to free adjustment) vs direct costs (paid for adjusting) 
-\item   Impact of symmetric vs asymmetric costs
 \item   Contrast steady-state results to dynamic solutions under stochastic shocks.
@@
 
-\section*{References}
-\bibliography{outline_refs.bib}
-
 \end{document}

### 2013-11-07 inst/doc/policycosts/policycosts.Rnw
update pdf

--- 2013-11-07 inst/doc/policycosts/policycosts.tex
@@
-\documentclass{article}\usepackage{graphicx, color}
-%% maxwidth is the original width if it is less than linewidth
-%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
-\makeatletter
-\def\maxwidth{ %
-  \ifdim\Gin@nat@width>\linewidth
-    \linewidth
-  \else
-    \Gin@nat@width
-  \fi
-}
-\makeatother
-
-\definecolor{fgcolor}{rgb}{0.2, 0.2, 0.2}
-\newcommand{\hlnumber}[1]{\textcolor[rgb]{0,0,0}{#1}}%
-\newcommand{\hlfunctioncall}[1]{\textcolor[rgb]{0.501960784313725,0,0.329411764705882}{\textbf{#1}}}%
-\newcommand{\hlstring}[1]{\textcolor[rgb]{0.6,0.6,1}{#1}}%
-\newcommand{\hlkeyword}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
-\newcommand{\hlargument}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
-\newcommand{\hlcomment}[1]{\textcolor[rgb]{0.180392156862745,0.6,0.341176470588235}{#1}}%
-\newcommand{\hlroxygencomment}[1]{\textcolor[rgb]{0.43921568627451,0.47843137254902,0.701960784313725}{#1}}%
-\newcommand{\hlformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
-\newcommand{\hleqformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
-\newcommand{\hlassignement}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
-\newcommand{\hlpackage}[1]{\textcolor[rgb]{0.588235294117647,0.709803921568627,0.145098039215686}{#1}}%
-\newcommand{\hlslot}[1]{\textit{#1}}%
-\newcommand{\hlsymbol}[1]{\textcolor[rgb]{0,0,0}{#1}}%
-\newcommand{\hlprompt}[1]{\textcolor[rgb]{0.2,0.2,0.2}{#1}}%
-
-\usepackage{framed}
-\makeatletter
-\newenvironment{kframe}{%
- \def\at@end@of@kframe{}%
- \ifinner\ifhmode%
-  \def\at@end@of@kframe{\end{minipage}}%
-  \begin{minipage}{\columnwidth}%
- \fi\fi%
- \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
- \colorbox{shadecolor}{##1}\hskip-\fboxsep
-     % There is no \\@totalrightmargin, so:
-     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
- \MakeFramed {\advance\hsize-\width
-   \@totalleftmargin\z@ \linewidth\hsize
-   \@setminipage}}%
- {\par\unskip\endMakeFramed%
- \at@end@of@kframe}
-\makeatother
-
-\definecolor{shadecolor}{rgb}{.97, .97, .97}
-\definecolor{messagecolor}{rgb}{0, 0, 0}
-\definecolor{warningcolor}{rgb}{1, 0, 1}
-\definecolor{errorcolor}{rgb}{1, 0, 0}
-\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
-
-\usepackage{alltt}
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\documentclass{article}
 
 \begin{document}
+%\SweaveOpts{concordance=TRUE, echo=FALSE}
 
@@
 
+<<settings, echo=FALSE, warning=FALSE>>=
+require(knitr)
+opts_chunk$set(echo=FALSE, dev="pdf", cache=FALSE, warning=FALSE)
+require(pdgControl)
+require(reshape2)
+require(ggplot2)
+require(data.table)
+require(plyr)
+require(xtable)
+load("writeup.rda")
+theme_set(theme_bw())
+@
+
 \begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/Figure_1}
-
-\end{knitrout}
+<<Figure_1>>=
+ggplot(fees, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
+@
 
@@
 \begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/Figure_2}
-
-\end{knitrout}
-
+<<Figure_2, fig.width=12>>=
+p2 <- ggplot(subset(dt, replicate %in% names(reps)[1:5])) +
+  geom_line(aes(time, harvest_alt), col="grey20", lwd=1)  +
+  geom_line(aes(time, harvest), col=rgb(0,0,1,.8)) + 
+  facet_grid(replicate~penalty_fn) + 
+  labs(x="time", y="havest intensity (fish taken)", title = "Harvest Policy Dynamics")
+p2
+@
   \caption{Individual realizations of optimal harvesting strategy under the different functional forms of adjustment costs.}
@@
 \begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/Figure_3}
-
-\end{knitrout}
-
+<<Figure_3, fig.width=12>>=
+p1 <- ggplot(subset(dt, replicate %in% names(reps)[1:5])) +
+  geom_line(aes(time, alternate), col="grey20", lwd=1) +
+  geom_line(aes(time, fishstock), col=rgb(0,0,1,.8)) + 
+  facet_grid(replicate~penalty_fn) + 
+  labs(x="time", y="stock size", title = "Stock Dynamics")
+p1
+@
   \caption{Individual realizations of optimal stock size strategy under the different functional forms of adjustment costs.}
@@
 \begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/Figure_4a}
+<<Figure_4a>>=
+Fig4a <- ggplot(harvest_trends, 
+                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
+  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
+  geom_line() + 
+  xlab("Fraction of NPV lost to costs") +
+  scale_x_continuous(limits=c(0, 0.4))
 
-\end{knitrout}
+Fig4b <- ggplot(harvest_trends, 
+                aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
+  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
+  geom_line() + xlab("Fraction of NPV lost to costs")+
+  scale_x_continuous(limits=c(0, 0.4)) 
+Fig4a
+
+@
 
@@
 \begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/Figure_4b}
-
-\end{knitrout}
-
+<<Figure_4b>>=
+Fig4b
+@
 \caption*{Figure 4b: Autocorrelation of optimal harvest rates through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.
@@
 \begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/Figure_5a}
+<<Figure_5a>>=
+fishstock_stats <- lapply(sims_at_each_apple, stats_fishstock)
+fishstock_trends <- get_trends(fishstock_stats)
 
-\end{knitrout}
+Fig5a <- ggplot(fishstock_trends, 
+                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
+  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
+  geom_line() + xlab("Fraction of NPV lost to costs")+
+  scale_x_continuous(limits=c(0, 0.4))
+
+Fig5b <- ggplot(fishstock_trends, 
+                aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
+  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
+  geom_line() + xlab("Fraction of NPV lost to costs") +
+  scale_x_continuous(limits=c(0, 0.4)) 
+Fig5a
+
+@
 
@@
 \begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/Figure_5b}
-
-\end{knitrout}
-
+<<Figure_5b>>=
+Fig5b
+@
 \caption*{Figure 5b: Autocorrelation of optimal stock sizes through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.
@@
 \begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-
-{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Using\ \ as id variables}}\end{kframe}
-\includegraphics[width=\maxwidth]{figure/Figure_6}
-
-\end{knitrout}
+<<Figure_6>>=
+totals <- data.frame(
+profit_under_penalty = dt[,sum(profit_fishing), by='replicate']$V1,
+cost_under_penalty = dt[,sum(policy_cost), by='replicate']$V1,
+profit_without_penalty = dt[,sum(profit_fishing_alt), by='replicate']$V1,
+costs_ignoring_penalty = dt[,sum(policy_cost_alt), by='replicate']$V1)
+totals <- melt(totals)
+ggplot(totals) + geom_density(aes(value, fill=variable), alpha=.7)
+@
 
@@
 \begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/Figure_7}
+<<Figure_7>>=
+require(ggplot2)
+df <- read.csv("output.csv")
+df <- df[2:8]
+require(reshape2)
+who <- c("penalty_fn", "ignore_fraction", "assume_fraction", "sigma_g", "reduction")
+df2 <- melt(df, id=who)
+who <- c("penalty_fn", "sigma_g", "reduction", "variable", "value")
+df3 <- melt(df2, id=who)
+names(df3) <- c("penalty_fn", "sigma_g", "reduction", "variable", "value", "fraction_variable", "fraction")
 
-\end{knitrout}
-
+df3$reduction <- as.factor(df3$reduction)
+ggplot(df3) + geom_line(aes(sigma_g, value, col=reduction, lty=variable)) + facet_wrap(~penalty_fn, scales="free_y") 
+@
 \end{figure}
@@
 
-\begin{table}[ht]
-\centering
-\begin{tabular}{rlrrrrrr}
-  \hline
- & penalty\_fn & ignore\_cost & ignore\_fraction & assume\_cost & assume\_fraction & sigma\_g & reduction \\ 
-  \hline
-1 & L1 & 14536.09 & 1.00 & 16857.61 & 1.00 & 0.05 & 0.10 \\ 
-  2 & L2 & 11020.10 & 0.76 & 15538.44 & 0.92 & 0.05 & 0.10 \\ 
-  3 & fixed & 13584.97 & 0.92 & 17582.78 & 1.05 & 0.05 & 0.10 \\ 
-  4 & L1 & 9273.66 & 1.09 & 17561.81 & 1.04 & 0.05 & 0.20 \\ 
-  5 & L2 & 11020.10 & 0.76 & 15538.44 & 0.92 & 0.05 & 0.20 \\ 
-  6 & fixed & 8332.45 & 0.84 & 17401.82 & 1.03 & 0.05 & 0.20 \\ 
-  7 & L1 & -641.78 & 0.21 & 15451.25 & 0.92 & 0.05 & 0.30 \\ 
-  8 & L2 & -272586.11 & -24.90 & 11567.12 & 0.69 & 0.05 & 0.30 \\ 
-  9 & fixed & -1213.01 & -0.46 & 15519.95 & 0.92 & 0.05 & 0.30 \\ 
-  10 & L1 & 18281.97 & 1.01 & 20973.56 & 0.99 & 0.20 & 0.10 \\ 
-  11 & L2 & 12462.51 & 0.72 & 19392.85 & 0.91 & 0.20 & 0.10 \\ 
-  12 & fixed & 16691.94 & 1.03 & 20143.80 & 0.95 & 0.20 & 0.10 \\ 
-  13 & L1 & 12788.95 & 0.96 & 20663.21 & 0.97 & 0.20 & 0.20 \\ 
-  14 & L2 & 12462.51 & 0.72 & 19392.85 & 0.91 & 0.20 & 0.20 \\ 
-  15 & fixed & 12399.01 & 0.88 & 21289.21 & 1.00 & 0.20 & 0.20 \\ 
-  16 & L1 & 9099.48 & 0.73 & 19999.07 & 0.94 & 0.20 & 0.30 \\ 
-  17 & L2 & -6337.76 & -0.39 & 17765.33 & 0.83 & 0.20 & 0.30 \\ 
-  18 & fixed & 7399.01 & 0.62 & 21969.84 & 1.03 & 0.20 & 0.30 \\ 
-  19 & L1 & 30227.43 & 1.07 & 31377.07 & 0.94 & 0.50 & 0.10 \\ 
-  20 & L2 & 33472.18 & 1.00 & 33472.18 & 1.00 & 0.50 & 0.10 \\ 
-  21 & fixed & 28926.73 & 1.09 & 30500.85 & 0.91 & 0.50 & 0.10 \\ 
-  22 & L1 & 24157.93 & 1.10 & 31767.92 & 0.95 & 0.50 & 0.20 \\ 
-  23 & L2 & 19091.31 & 0.93 & 29225.46 & 0.87 & 0.50 & 0.20 \\ 
-  24 & fixed & 23573.19 & 1.02 & 30069.80 & 0.90 & 0.50 & 0.20 \\ 
-  25 & L1 & 21086.12 & 1.12 & 32035.93 & 0.96 & 0.50 & 0.30 \\ 
-  26 & L2 & 19091.31 & 0.93 & 29225.46 & 0.87 & 0.50 & 0.30 \\ 
-  27 & fixed & 17209.56 & 0.85 & 32946.24 & 0.98 & 0.50 & 0.30 \\ 
-   \hline
-\end{tabular}
+<<Table_1, results="asis">>=
+df4 <- df[c(1,2,4,6,7)]
+df4 <- plyr::arrange(df4, penalty_fn)
+print(xtable::xtable(df))
+@
 
-\caption{Overall cost of assuming policy adjustment costs apply when they are absent (first value) or from ignoring them when they are present (second value).
+Overall cost of assuming policy adjustment costs apply when they are absent (first value) or from ignoring them when they are present (second value).
 These overall costs are shown for different severities of policy adjustment costs (columns) and levels of environmental variability (rows) and for three different functional forms for policy adjustment costs ($\Pi_i$ for $ i=1-3$).
 Values expressed as percentages of the maximum expected net present value when no policy adjustment costs apply and this is known to managers ($ NPV_0 ({\bf h_0^*}) $).
-}
-\end{table}
 

### 2013-11-07 inst/doc/policycosts/policycosts.Rnw
update figures (again)

@@
 <<Figure_1>>=
-ggplot(fees, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
+ggplot(fees, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()+theme_bw()
 @
@@
   labs(x="time", y="havest intensity (fish taken)", title = "Harvest Policy Dynamics")
-p2
+p2+theme_bw()
 @
@@
   labs(x="time", y="stock size", title = "Stock Dynamics")
-p1
+p1+theme_bw()
 @
@@
 df3$reduction <- as.factor(df3$reduction)
-ggplot(df3) + geom_line(aes(sigma_g, value, col=reduction, lty=variable)) + facet_wrap(~penalty_fn, scales="free_y") 
+ggplot(df3) + geom_line(aes(sigma_g, value, col=reduction, lty=variable)) + facet_wrap(~penalty_fn, scales="free_y", ncol=1) 
 @

### 2013-11-07 inst/doc/policycosts/policycosts.tex
update figures (again)

@@
 \begin{document}
+%\SweaveOpts{concordance=TRUE, echo=FALSE}
 
@@
 
+% latex table generated in R 3.0.2 by xtable 1.7-1 package
+% Wed Nov  6 20:50:41 2013
 \begin{table}[ht]
@@
 \end{tabular}
+\end{table}
 
-\caption{Overall cost of assuming policy adjustment costs apply when they are absent (first value) or from ignoring them when they are present (second value).
+Overall cost of assuming policy adjustment costs apply when they are absent (first value) or from ignoring them when they are present (second value).
 These overall costs are shown for different severities of policy adjustment costs (columns) and levels of environmental variability (rows) and for three different functional forms for policy adjustment costs ($\Pi_i$ for $ i=1-3$).
 Values expressed as percentages of the maximum expected net present value when no policy adjustment costs apply and this is known to managers ($ NPV_0 ({\bf h_0^*}) $).
-}
-\end{table}
 

### 2013-11-08 inst/doc/policycosts/policycosts.Rnw
updates

@@
 \begin{figure}
-<<Figure_1>>=
+<<Figure_1, cache=FALSE>>=
 ggplot(fees, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()+theme_bw()
@@
 df <- read.csv("output.csv")
-df <- df[2:8]
-require(reshape2)
-who <- c("penalty_fn", "ignore_fraction", "assume_fraction", "sigma_g", "reduction")
-df2 <- melt(df, id=who)
-who <- c("penalty_fn", "sigma_g", "reduction", "variable", "value")
-df3 <- melt(df2, id=who)
-names(df3) <- c("penalty_fn", "sigma_g", "reduction", "variable", "value", "fraction_variable", "fraction")
+df2 <- df[c("penalty_fn", "ignore_cost", "assume_cost", "sigma_g", "reduction")] # subset
+df3 <- reshape2::melt(df2, id = c("penalty_fn", "sigma_g", "reduction")) 
+df3$reduction <- as.factor(df3$reduction)
+ggplot(df3) + 
+  geom_line(aes(sigma_g, value, col=reduction, lty=variable)) +
+  #facet_grid(reduction~penalty_fn, scales="free")
+  facet_wrap(~penalty_fn, scales="free_y", ncol=1) +
+  scale_y_continuous(limits=c(-3e4,3e4))
 
-df3$reduction <- as.factor(df3$reduction)
-ggplot(df3) + geom_line(aes(sigma_g, value, col=reduction, lty=variable)) + facet_wrap(~penalty_fn, scales="free_y", ncol=1) 
   @

### 2013-11-08 inst/examples/policycosts/errors_table.Rmd
updates

@@
 
-``` {r profit_model}
-compute_error_table <- function(reduction = 0.25, sigma = 0.2){
-reduction <- reduction
+``` {r defs}
+compute_error_table <- function(r = 2, sigma = 0.2){
+reduction_range = c(.1, .2, .3)
+reduction <- reduction_range[r]
 
 price = 10
-c0 = 30
+c0 = 0
 profit <- profit_harvest(price = price, c0 = c0, c1 = 0)
@@
 
+sigma_g <- 0.3
 SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
@@
 
+tmp <- lapply(1:100, function(i){ 
+  set.seed(i)
+  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i)
+  })
+tmp <- melt(tmp, id = names(tmp[[1]]))
+sum(tmp$profit)
+
 L1 <- function(c2) function(h, h_prev)  c2 * abs(h - h_prev) 
-free_increase <- function(c2) function(h, h_prev)  c2 * abs(pmin(h - h_prev, 0)) # increasing harvest is free
-free_decrease <- function(c2) function(h, h_prev)  c2 * pmax(h - h_prev, 0) # decreasing harvest is free
 fixed <-  function(c2) function(h, h_prev) c2 * as.numeric( !(h == h_prev) )
@@
 none <- function(h, h_prev)  0
-penaltyfns <- list(L2=L2, L1=L1, free_decrease=free_decrease, fixed=fixed, free_increase=free_increase)
 
-require(snowfall)
-sfInit(cpu=8, parallel=T)
-sfLibrary(pdgControl)
-sfExportAll()
+reduction_table <- read.csv('reduction_table.csv', row.names=1)
+apples <-   reduction_table[[r]]
+names(apples) <- rownames(reduction_table)
 
-policies <- lapply(penaltyfns, function(penalty){
-  sfLapply(c2, function(c2){
-      policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
-                   profit, delta, reward, penalty = penalty(c2))
-      }
-  )
-})
-
-quad <- 
-  sfLapply(c2, function(c2){
-  effort_penalty = function(x,h) (c2 * h / x) / price
-  policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
-                        profit, delta, reward, penalty = none, 
-                        effort_penalty)
-})
-policies <- c(policies, quad=list(quad))
-
-i <- which(x_grid > K)[1]
-fees <- 
-lapply(policies, function(penalty) 
-  sapply(penalty, function(c2_run)
-    max(c2_run$V[i,]) # Would be penalty_free_V originally   ## this isn't correct for asym cases
-  )
-)
-
-npv0 <- max(fees$L1) # all have same max, at c2=0 
-npv0
-fees <- data.frame(c2=c2,fees)
-fees <- melt(fees, id="c2")
-#ggplot(fees, aes(c2, value, col=variable)) + geom_point() + geom_line()
-
-closest <- function(x, v){
-  which.min(abs(v-x))
-}
-dt_npv <- data.table(fees)
-index <- dt_npv[,closest(reduction, (npv0-value)/npv0), by=variable]
-apples_index <- index$V1
-names(apples_index) = index$variable
-apples <- c2[index$V1]
-names(apples) = index$variable
-apples
-
-setkey(dt_npv, variable)
-values <- apply(index, 1, function(x) dt_npv[x[1], ][as.integer(x[2]), ]$value)
-
-percent.error <- (values - ((1-reduction)*npv0)) / ((1-reduction)*npv0)* 100
-
-print_npv <- data.frame(model=index$variable, "value realized"=values, 
-                        "percent of npv0" = 100*values/npv0, "percent error"=percent.error)
-
-L2_policy <- policies$L2[[apples_index["L2"]]]$D
-L1_policy <- policies$L1[[apples_index["L1"]]]$D
-fixed_policy <- policies$fixed[[apples_index["fixed"]]]$D
-free_increase_policy <- policies$free_increase[[apples_index["free_increase"]]]$D
-free_decrease_policy <- policies$free_decrease[[apples_index["free_decrease"]]]$D
-quad_policy <- policies$quad[[apples_index["quad"]]]$D
-
-quad_profit <- profit_harvest(price = price, c0 = c0, c1 = apples["quad"])
+L2_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
+                   profit, delta, reward, penalty = L2(apples[["L2"]]))
+L1_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
+                   profit, delta, reward, penalty = L1(apples[["L1"]]))
+fixed_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
+                   profit, delta, reward, penalty = fixed(apples[["fixed"]]))
 
 reps <- 1:100
-names(reps) = paste("rep", 1:10, sep="_")
+names(reps) = paste("rep", 1:100, sep="_")
+seeds <- 1:100
 sims <- list(
   L1 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
-                      L1_policy, z_g, z_m, z_i, 
-                      opt$D, profit=profit, penalty=L1(apples["L1"]), seed=seed)), 
+                      L1_policy$D, z_g, z_m, z_i, 
+                      opt$D, profit=profit, penalty=L1(apples[["L1"]]), seed=seeds[x])), 
   L2 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
-                      L2_policy, z_g, z_m, z_i, 
-                      opt$D, profit=profit, penalty=L2(apples["L2"]), seed=seed)),
+                      L2_policy$D, z_g, z_m, z_i, 
+                      opt$D, profit=profit, penalty=L2(apples[["L2"]]), seed=seeds[x])),
   fixed = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
-                         fixed_policy, z_g, z_m, z_i, 
-                         opt$D, profit=profit, penalty=fixed(apples["fixed"]), seed=seed))
+                         fixed_policy$D, z_g, z_m, z_i, 
+                         opt$D, profit=profit, penalty=fixed(apples[["fixed"]]), seed=seeds[x]))
 
@@
 
-sims_free <- list(
-  L1 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
-                      L1_policy, z_g, z_m, z_i, 
-                      opt$D, profit=profit, penalty=none, seed=seed)), 
-  L2 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
-                      L2_policy, z_g, z_m, z_i, 
-                      opt$D, profit=profit, penalty=none, seed=seed)),
-  fixed = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
-                         fixed_policy, z_g, z_m, z_i, 
-                         opt$D, profit=profit, penalty=none, seed=seed))
-)
-
-#Make data tidy (melt), fast (data.tables), and nicely labeled.
-free <- melt(sims_free, id=names(sims_free[[1]][[1]]))  
-dt_free <- data.table(free)
-setnames(dt_free, "L2", "replicate") # names are nice
-setnames(dt_free, "L1", "penalty_fn") # names are nice
-
 # Profit when accounting for penalty when present
@@
 # Profit when assuming penalty when it is absent
-assume_when_absent <- dt_free[, sum(profit_fishing - policy_cost), by=penalty_fn]
+assume_when_absent <- dt[, sum(profit_fishing), by=penalty_fn]
 # Profit when ignoring penalty when it is absent
-optimal_free <- dt_free[, sum(profit_fishing_alt - policy_cost_alt), by=penalty_fn]
+optimal_free <- dt[, sum(profit_fishing_alt), by=penalty_fn]
 
 # Normalize by the optimal 
-ignore_fraction <- ignore_when_present$V1/optimal_cost$V1
+ignore_fraction <- ignore_when_present$V1/optimal_free$V1 # common normalization
 assume_fraction <- assume_when_absent$V1/optimal_free$V1
-assume_when_absent <- cbind(assume_when_absent, assume_fraction = assume_fraction)
+assume_when_absent <- cbind(assume_when_absent, assume_fraction = assume_fraction, normalize_optimal_free=optimal_free$V1, normalize_optimal_cost = optimal_cost$V1)
 ignore_when_present <- cbind(ignore_when_present, ignore_fraction = ignore_fraction)
@@
 
-print_npv # theoretically acheivable profits under these costs
 optimal_cost$V1/optimal_free$V1 # actually realized
@@
 
-```{r}
-sigmas <- c(0.05, 0.2, 0.5)
-reductions <- c(0.1, 0.2, 0.3)
+```{r compute_table}
+sigmas <- c(0.01, 0.1, 0.2)
+reductions <- 1:3
 out <- lapply(sigmas, function(s){

### 2013-11-08 inst/examples/policycosts/test.Rmd
updates

--- 2013-11-07 inst/examples/policycosts/writeup.Rmd
@@
 ```{r cache-options, include=FALSE}
-opts_chunk$set(cache=TRUE, cache.path="writeup/")
+opts_chunk$set(cache=TRUE, cache.path="test/")
 opts_knit$set(upload.fun=socialR::flickr.url)
@@
 gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
-sigma_g <- 0.2              # Noise in population growth
+sigma_g <- 0.5            # Noise in population growth
 reward <- 0                 # bonus for satisfying the boundary condition
@@
 
-We also do the the classical quadratic costs on fishing effort separately,
-
-``` {r  quadcosts, dependson="bigloop"}
-quad <- 
-  sfLapply(c2, function(c2){
-  effort_penalty = function(x,h) (c2 * h / x) / price
-  policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
-                        profit, delta, reward, penalty = none, 
-                        effort_penalty)
-})
-policies <- c(policies, quad=list(quad))
-````
-
 Extract the policy cost
@@
 apples
+````
+
+```{r reductions}
+reduction_table <- sapply(c("0.10" = 0.10, "0.20" = 0.20, "0.30" = 0.30), function(reduction){
+index <- dt_npv[,closest(reduction, (npv0-value)/npv0), by=variable]
+apples <- c2[index$V1]
+names(apples) = index$variable
+apples })
+write.csv(reduction_table, "reduction_table.csv")
 ````
@@
 
-```{r }
-sims_free <- list(
-  L1 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
-                      L1_policy, z_g, z_m, z_i, 
-                      opt$D, profit=profit, penalty=none, seed=seeds[x])), 
-  L2 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
-                      L2_policy, z_g, z_m, z_i, 
-                      opt$D, profit=profit, penalty=none, seed=seeds[x])),
-  fixed = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
-                         fixed_policy, z_g, z_m, z_i, 
-                         opt$D, profit=profit, penalty=none, seed=seeds[x]))
-)
-````
-
-``` {r }
-#Make data tidy (melt), fast (data.tables), and nicely labeled.
-free <- melt(sims_free, id=names(sims_free[[1]][[1]]))  
-dt_free <- data.table(free)
-setnames(dt_free, "L2", "replicate") # names are nice
-setnames(dt_free, "L1", "penalty_fn") # names are nice
-````
-
 ```{r}
@@
 # Profit when assuming penalty when it is absent
-assume_when_absent <- dt_free[, sum(profit_fishing - policy_cost), by=penalty_fn]
+assume_when_absent <- dt[, sum(profit_fishing), by=penalty_fn]
 # Profit when ignoring penalty when it is absent
-optimal_free <- dt_free[, sum(profit_fishing_alt - policy_cost_alt), by=penalty_fn]
+optimal_free <- dt[, sum(profit_fishing_alt), by=penalty_fn]
 
 # Normalize by the optimal 
-#ignore_when_present$V1 <- ignore_when_present$V1/optimal_cost$V1
-#assume_when_absent$V1 <- assume_when_absent$V1/optimal_free$V1
+ignore_fraction <- ignore_when_present$V1/optimal_free$V1 # common normalization
+assume_fraction <- assume_when_absent$V1/optimal_free$V1
+assume_when_absent <- cbind(assume_when_absent, assume_fraction = assume_fraction, normalize_optimal_free=optimal_free$V1, normalize_optimal_cost = optimal_cost$V1)
+ignore_when_present <- cbind(ignore_when_present, ignore_fraction = ignore_fraction)
 
@@
 
-cbind(error_costs, sigma_g = sigma_g, reduction = reduction)
+error_costs <- cbind(error_costs, sigma_g = sigma_g, reduction = reduction)
 
-```
-
-```{r error_costs_table, results='asis'} 
-print(xtable(error_costs), type="html")
-#pandoc.table(print_npv)
 ```

### 2013-11-12 inst/examples/noise_effects.Rmd
add noise table, updated files

```{r}
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
rm(list=ls())

delta <- 0.05               # economic discounting rate
OptTime <- 20               # stopping time
gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
reward <- 0                 # bonus for satisfying the boundary condition
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1         # No measurement noise, 
z_i <- function() 1         # No implemenation noise
f <- BevHolt                # Select the state equation
pars <- c(1.5, 0.05)        # parameters for the state equation
K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
xT <- 0                     # boundary conditions
x0 <- K
x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
h_grid <- seq(0.01, 0.8 * K, length = gridsize)  
```

With profits linear in price (no cost)

```{r}
profit <- profit_harvest(price = 1, c0 = 0, c1 = 0)

sigma_g <- 0.03
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                     profit, delta, reward=reward)

p1 <- opt$D[,1]
p1 = sapply(1:length(p1), function(x) p1)
#s_opt <- value_iteration(SDP_Mat, x_grid, h_grid, OptTime=1000, xT, profit, delta)

tmp <- lapply(1:100, function(i){ 
  set.seed(i)
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i)
  })
tmp <- melt(tmp, id = names(tmp[[1]]))

sigma_g <- 0.1
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                     profit, delta, reward=reward)

p2 <- opt$D[,1]
p2 = sapply(1:length(p2), function(x) p2)

tmp2 <- lapply(1:100, function(i){ 
  set.seed(i)
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, p2, z_g, z_m, z_i)
  })
tmp2 <- melt(tmp2, id = names(tmp2[[1]]))

tmp <- data.table(tmp)
tmp2 <- data.table(tmp2)

discounted = tmp[, sum(profit/((1+delta)^time)), by=L1]$V1
profit = tmp[, sum(profit), by=L1]$V1
#ggplot(tmp, aes(time, fishstock, group=L1)) + geom_line(alpha=0.1)
#ggplot(tmp2, aes(time, fishstock, group=L1)) + geom_line(alpha=0.1)
```

The control strategies are identical but the net present values differ.

```{r}
identical(p1,p2)

c(low_noise = sum(tmp$profit), high_noise = sum(tmp2$profit))
```

### 2013-12-04 inst/doc/policycosts/policycosts.Rnw
source in scripts to Rnw manuscript

@@
 %\SweaveOpts{concordance=TRUE, echo=FALSE}
+<<settings, echo=FALSE, warning=FALSE>>=
+require(knitr)
+opts_chunk$set(echo=FALSE, dev="pdf", cache=FALSE, warning=FALSE)
+require(pdgControl)
+require(reshape2)
+require(ggplot2)
+require(data.table)
+require(plyr)
+require(xtable)
+#load("writeup.rda")
+theme_set(theme_bw())
+@
+
+<<maincode, echo=FALSE, warning=FALSE>>=
+source("writeup.R")
+@
+<<errortable, echo=FALSE, warning=FALSE>>=
+source("errors_table.R")
+@
 
@@
 Other parameters in the model are chosen - HOW?
-
-<<settings, echo=FALSE, warning=FALSE>>=
-require(knitr)
-opts_chunk$set(echo=FALSE, dev="pdf", cache=FALSE, warning=FALSE)
-require(pdgControl)
-require(reshape2)
-require(ggplot2)
-require(data.table)
-require(plyr)
-require(xtable)
-load("writeup.rda")
-theme_set(theme_bw())
-@
 

### 2013-12-04 inst/doc/policycosts/errors_table.R

@@ -1,22 +1,21 @@
 
-``` {r libraries, message=FALSE, warning=FALSE}
+## ----libraries, message=FALSE, warning=FALSE-----------------------------
 rm(list=ls())
 require(pdgControl)
 require(reshape2)
 require(ggplot2)
 require(data.table)
-```
 
 
-```{r cache-options, include=FALSE}
+## ----cache-options, include=FALSE----------------------------------------
 opts_chunk$set(cache=TRUE, cache.path="errors_table/", tidy=FALSE)
-```
 
-```{r}
+
+## ------------------------------------------------------------------------
 start <- Sys.time()
-```
 
-``` {r defs}
+
+## ----defs----------------------------------------------------------------
 compute_error_table <- function(r, sigma){
 reduction_range = c(.1, .2, .3)
 reduction <- reduction_range[r]
@@ -121,9 +120,9 @@ error_costs <- cbind(error_costs, sigma_g = sigma_g, reduction = reduction)
 error_costs 
 }
 
-```
 
-```{r compute_table}
+
+## ----compute_table-------------------------------------------------------
 sigmas <- c(0.01, 0.1, 0.2)
 reductions <- 1:3
 out <- lapply(sigmas, function(s){
@@ -135,17 +134,18 @@ out <- lapply(sigmas, function(s){
 who <- names(out[[1]][[1]])
 df <- melt(out, id=who)              
 df
-```
 
-```{r results="asis"}
+
+## ----results="asis"------------------------------------------------------
 #df <- df[1:5]
 library(xtable)
 print(xtable(df), type="html")
 writeLines(print(xtable(df)), "output.md")
 system("pandoc output.md -o output.pdf")
 write.csv(df, "output.csv")
-```
 
-```{r}
+
+## ------------------------------------------------------------------------
 Sys.time() - start 
-```
+
+

### 2013-12-04 inst/doc/policycosts/writeup.R

@@ -1,0 +1,375 @@
+
+## ----libraries, message=FALSE, warning=FALSE-----------------------------
+rm(list=ls())
+require(pdgControl)
+require(reshape2)
+require(ggplot2)
+require(data.table)
+
+
+## ----cache-options, include=FALSE----------------------------------------
+opts_chunk$set(cache=TRUE, cache.path="writeup/")
+opts_knit$set(upload.fun=socialR::flickr.url)
+
+
+## ----profit_model--------------------------------------------------------
+price = 10
+c0 = 30
+profit <- profit_harvest(price = price, c0 = c0, c1 = 0)
+
+
+## ----c2_grid-------------------------------------------------------------
+c2 <- exp(seq(0, log(41), length.out = 40))-1
+c2 <- seq(0, 40, length.out=100)
+
+
+## ----reduction-----------------------------------------------------------
+reduction <- 0.25 
+
+
+## ----graphing-options, include=TRUE--------------------------------------
+opts_knit$set(upload.fun = socialR::flickr.url)
+opts_chunk$set(dev.args=list(bg="transparent"),
+               tidy=FALSE, comment=NA, message=FALSE, warning=FALSE)
+opts_chunk$set(echo=FALSE)
+theme_set(theme_bw())
+
+
+## ----setup---------------------------------------------------------------
+seed <- 123                 # Random seed (replicable results)
+delta <- 0.05               # economic discounting rate
+OptTime <- 20               # stopping time
+gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
+sigma_g <- 0.2              # Noise in population growth
+reward <- 0                 # bonus for satisfying the boundary condition
+z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
+z_m <- function() 1         # No measurement noise, 
+z_i <- function() 1         # No implemenation noise
+f <- BevHolt                # Select the state equation
+pars <- c(1.5, 0.05)        # parameters for the state equation
+K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
+xT <- 0                     # boundary conditions
+x0 <- K
+x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
[…]

### 2014-01-30 inst/examples/Reed.Rmd
Beverton Holt example

@@
-`ro cache=FALSE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE or`
-
 ``` {r  echo=FALSE, cache=FALSE}
 opts_knit$set(upload.fun = socialR::flickr.url)
+opts_chunk$set(cache=FALSE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE)
 ````
@@
 ``` {r }
-f <- RickerAllee
-K <- 10
-pars <- c(2, K, 5)
+#f <- RickerAllee
+#pars <- c(2, K, 5)
+f <- BevHolt
+pars <- c(2,4)
+K <- (pars[1]-1)/pars[2]
+
+#K <- 100
+#pars <- c(1,K)
+#f <- function(x,h,p){
+#  sapply(x, function(x){
+ #   S = max(x - h, 0)
+#    p[1] * S * (1 - S/p[2]) + S
+#  })
+#}
+
 ````
@@
 ``` {r noise}
-z_g <- function() 1 + rlnorm(1,0, sigma_g)  
+#z_g <- function() 1 + rlnorm(1,0, sigma_g)  
 pdfn <- function(P, s) dlnorm(P, 0, s)
@@
 ``` {r  SDP_Mat}
-p <- c(.2,7.5,5)
-SDP_Mat <- determine_SDP_matrix(f, p, x_grid, h_grid, sigma_g, pdfn)
+SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
 ````
@@
 require(reshape2)
-policies <- melt(data.frame(stock=x_grid, S = x_grid[opt$D[,1]], D = x_grid[det$D[,1]], Stationary = x_grid[s_opt$D]), id="stock")
-q1 <- ggplot(policies, aes(stock, stock - value, color=variable)) + geom_point(alpha=.5) + xlab("stock size") + ylab("escapement") 
+policies <- melt(data.frame(stock=x_grid, 
+                            S = x_grid[opt$D[,1]], 
+                            D = x_grid[det$D[,1]], 
+                            Stationary = x_grid[s_opt$D]
+                            ), id="stock")
+q1 <- ggplot(policies, aes(stock, stock - value, color=variable)) + geom_point(alpha=.4) + xlab("stock size") + ylab("escapement") 
 q1

### 2014-01-30 inst/examples/Reed.Rmd
Logistic (uniform noise), shows steps in deterministic policy (but not the stochastic).

@@
 #pars <- c(2, K, 5)
-f <- BevHolt
-pars <- c(2,4)
-K <- (pars[1]-1)/pars[2]
 
-#K <- 100
-#pars <- c(1,K)
-#f <- function(x,h,p){
-#  sapply(x, function(x){
- #   S = max(x - h, 0)
-#    p[1] * S * (1 - S/p[2]) + S
-#  })
-#}
+#f <- BevHolt
+#pars <- c(2,4)
+#K <- (pars[1]-1)/pars[2]
+
+K <- 100
+pars <- c(1,K)
+f <- function(x,h,p){
+  sapply(x, function(x){
+    S = max(x - h, 0)
+    p[1] * S * (1 - S/p[2]) + S
+  })
+}
 
@@
 #z_g <- function() 1 + rlnorm(1,0, sigma_g)  
-pdfn <- function(P, s) dlnorm(P, 0, s)
+#pdfn <- function(P, s) dlnorm(P, 0, s)
 
-#z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
-#pdfn <- function(P, s)  dunif(P, 1 - s, 1 + s)
+z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
+pdfn <- function(P, s)  dunif(P, 1 - s, 1 + s)
 ````
@@
 
+<!--
+
 ### Simulate 
@@
 ````
+
+-->

### 2014-03-18 inst/doc/policycosts/policycosts.Rnw
updates from previous runs

--- 2013-11-08 inst/doc/policycosts/policycosts.Rnw
@@
 %\SweaveOpts{concordance=TRUE, echo=FALSE}
+<<settings, echo=FALSE, warning=FALSE>>=
+require(knitr)
+opts_chunk$set(echo=FALSE, dev="pdf", cache=FALSE, warning=FALSE)
+require(pdgControl)
+require(reshape2)
+require(ggplot2)
+require(data.table)
+require(plyr)
+require(xtable)
+
+theme_set(theme_bw())
+@
+
+<<maincode, echo=FALSE, warning=FALSE>>=
+#source("writeup.R")
+load("writeup.rda")
+@
+<<errortable, echo=FALSE, warning=FALSE>>=
+#source("errors_table.R")
+NULL
+@
 
@@
 
-\begin{figure}
-<<Figure_7>>=
-require(ggplot2)
+<<reshapedata, echo=FALSE>>=
 df <- read.csv("output.csv")
@@
 df3$reduction <- as.factor(df3$reduction)
-ggplot(df3) + 
-  geom_line(aes(sigma_g, value, col=reduction, lty=variable)) +
-  #facet_grid(reduction~penalty_fn, scales="free")
-  facet_wrap(~penalty_fn, scales="free_y", ncol=1) +
-  scale_y_continuous(limits=c(-3e4,3e4))
-
+reduction_table <- read.csv('reduction_table.csv', row.names=1)
+reduction_coefs <- melt(data.frame(penalty_fn = rownames(reduction_table), reduction_table), id = "penalty_fn")[c(1,3)]
+names(reduction_coefs) <- c("penalty_fn", "coefficient")
 @
-\end{figure}
 
@@
 <<Table_1, results="asis">>=
-df4 <- df[c(1,2,4,6,7)]
-df4 <- plyr::arrange(df4, penalty_fn)
-print(xtable::xtable(df))
+df4 <- df[c(2,4,6,9,10)]
+df4 <- plyr::arrange(df4, reduction)
+df5 <- subset(df4, sigma_g == 0.20)[-4]
+df5 <- cbind(df5, reduction_coefs[2])
+df5 <- plyr::arrange(df5, penalty_fn)
+names(df5) <- c("penalty fn", "ignoring", "assuming", "percent reduction", "c2")
+print(xtable::xtable(df5, caption="Column 'ignoring' shows the results of ignoring a adjustment penalty when it is present, Column 'assuming' shows the results of assuming an adjustment cost when it is absent.
+Values (ignoring, assuming) are given as the expected net present value (ENPV) as a fraction of that when no penalty is present, ENPV0.
+Percent reduction refers to penalty coefficient being calibrated to achieve the given percent reduction relative to ENPV0 when the penalty is optimally accounted for.
+Column c2 shows the coefficient chosen to achieve that reduction.
+Comparing the second and third columns shows that ignoring a real cost is a significantly graver error, particularly in the case of quadratic (L2) costs."))
 @

### 2014-03-18 inst/doc/policycosts/policycosts.tex
updates
updates from previous runs

@@
-\documentclass{article}\usepackage{graphicx, color}
+\documentclass{article}\usepackage[]{graphicx}\usepackage[]{color}
 %% maxwidth is the original width if it is less than linewidth
@@
 
-\definecolor{fgcolor}{rgb}{0.2, 0.2, 0.2}
-\newcommand{\hlnumber}[1]{\textcolor[rgb]{0,0,0}{#1}}%
-\newcommand{\hlfunctioncall}[1]{\textcolor[rgb]{0.501960784313725,0,0.329411764705882}{\textbf{#1}}}%
-\newcommand{\hlstring}[1]{\textcolor[rgb]{0.6,0.6,1}{#1}}%
-\newcommand{\hlkeyword}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
-\newcommand{\hlargument}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
-\newcommand{\hlcomment}[1]{\textcolor[rgb]{0.180392156862745,0.6,0.341176470588235}{#1}}%
-\newcommand{\hlroxygencomment}[1]{\textcolor[rgb]{0.43921568627451,0.47843137254902,0.701960784313725}{#1}}%
-\newcommand{\hlformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
-\newcommand{\hleqformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
-\newcommand{\hlassignement}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
-\newcommand{\hlpackage}[1]{\textcolor[rgb]{0.588235294117647,0.709803921568627,0.145098039215686}{#1}}%
-\newcommand{\hlslot}[1]{\textit{#1}}%
-\newcommand{\hlsymbol}[1]{\textcolor[rgb]{0,0,0}{#1}}%
-\newcommand{\hlprompt}[1]{\textcolor[rgb]{0.2,0.2,0.2}{#1}}%
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
 
@@
 %\SweaveOpts{concordance=TRUE, echo=FALSE}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+
+{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Loading required package: pdgControl\\\#\# Loading required package: reshape2\\\#\# Loading required package: ggplot2\\\#\# Loading required package: data.table\\\#\# Loading required package: plyr\\\#\# Loading required package: xtable}}\end{kframe}
+\end{knitrout}
 
@@
 
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/Figure_7}
-
-\end{knitrout}
-
-\end{figure}
-
 Table 1 compares these different contributions, namely the $NPV$ lost by assuming policy adjustment costs when none are present (first entry in each cell, $[1]-[3]$ in the equations)) and the $NPV$ lost when ignoring policy adjustment costs when they are present (second entry in each cell of the table, contributions $([1]-[2])-([3]-[4]))$ in the equations) across the three different functional forms.
@@
 
-% latex table generated in R 3.0.2 by xtable 1.7-1 package
-% Wed Nov  6 20:50:41 2013
 \begin{table}[ht]
-\centering
-\begin{tabular}{rlrrrrrr}
+\begin{center}
+\begin{tabular}{rlrrrr}
   \hline
- & penalty\_fn & ignore\_cost & ignore\_fraction & assume\_cost & assume\_fraction & sigma\_g & reduction \\ 
+ & penalty fn & ignoring & assuming & percent reduction & c2 \\ 
   \hline
-1 & L1 & 14536.09 & 1.00 & 16857.61 & 1.00 & 0.05 & 0.10 \\ 
-  2 & L2 & 11020.10 & 0.76 & 15538.44 & 0.92 & 0.05 & 0.10 \\ 
-  3 & fixed & 13584.97 & 0.92 & 17582.78 & 1.05 & 0.05 & 0.10 \\ 
-  4 & L1 & 9273.66 & 1.09 & 17561.81 & 1.04 & 0.05 & 0.20 \\ 
-  5 & L2 & 11020.10 & 0.76 & 15538.44 & 0.92 & 0.05 & 0.20 \\ 
-  6 & fixed & 8332.45 & 0.84 & 17401.82 & 1.03 & 0.05 & 0.20 \\ 
-  7 & L1 & -641.78 & 0.21 & 15451.25 & 0.92 & 0.05 & 0.30 \\ 
-  8 & L2 & -272586.11 & -24.90 & 11567.12 & 0.69 & 0.05 & 0.30 \\ 
-  9 & fixed & -1213.01 & -0.46 & 15519.95 & 0.92 & 0.05 & 0.30 \\ 
-  10 & L1 & 18281.97 & 1.01 & 20973.56 & 0.99 & 0.20 & 0.10 \\ 
-  11 & L2 & 12462.51 & 0.72 & 19392.85 & 0.91 & 0.20 & 0.10 \\ 
-  12 & fixed & 16691.94 & 1.03 & 20143.80 & 0.95 & 0.20 & 0.10 \\ 
-  13 & L1 & 12788.95 & 0.96 & 20663.21 & 0.97 & 0.20 & 0.20 \\ 
-  14 & L2 & 12462.51 & 0.72 & 19392.85 & 0.91 & 0.20 & 0.20 \\ 
-  15 & fixed & 12399.01 & 0.88 & 21289.21 & 1.00 & 0.20 & 0.20 \\ 
-  16 & L1 & 9099.48 & 0.73 & 19999.07 & 0.94 & 0.20 & 0.30 \\ 
-  17 & L2 & -6337.76 & -0.39 & 17765.33 & 0.83 & 0.20 & 0.30 \\ 
-  18 & fixed & 7399.01 & 0.62 & 21969.84 & 1.03 & 0.20 & 0.30 \\ 
-  19 & L1 & 30227.43 & 1.07 & 31377.07 & 0.94 & 0.50 & 0.10 \\ 
-  20 & L2 & 33472.18 & 1.00 & 33472.18 & 1.00 & 0.50 & 0.10 \\ 
-  21 & fixed & 28926.73 & 1.09 & 30500.85 & 0.91 & 0.50 & 0.10 \\ 
-  22 & L1 & 24157.93 & 1.10 & 31767.92 & 0.95 & 0.50 & 0.20 \\ 
-  23 & L2 & 19091.31 & 0.93 & 29225.46 & 0.87 & 0.50 & 0.20 \\ 
-  24 & fixed & 23573.19 & 1.02 & 30069.80 & 0.90 & 0.50 & 0.20 \\ 
-  25 & L1 & 21086.12 & 1.12 & 32035.93 & 0.96 & 0.50 & 0.30 \\ 
-  26 & L2 & 19091.31 & 0.93 & 29225.46 & 0.87 & 0.50 & 0.30 \\ 
-  27 & fixed & 17209.56 & 0.85 & 32946.24 & 0.98 & 0.50 & 0.30 \\ 
+1 & L1 & 0.81 & 1.00 & 0.10 & 0.40 \\ 
+  2 & L1 & 0.62 & 0.99 & 0.20 & 0.81 \\ 
+  3 & L1 & 0.35 & 0.97 & 0.30 & 2.02 \\ 
+  4 & L2 & 0.68 & 0.95 & 0.10 & 0.81 \\ 
+  5 & L2 & 0.44 & 0.89 & 0.20 & 1.62 \\ 
+  6 & L2 & -0.28 & 0.81 & 0.30 & 2.83 \\ 
+  7 & fixed & 0.78 & 1.00 & 0.10 & 3.64 \\ 
+  8 & fixed & 0.56 & 0.99 & 0.20 & 8.08 \\ 
+  9 & fixed & 0.31 & 0.97 & 0.30 & 12.93 \\ 
    \hline
 \end{tabular}
+\caption{Column 'ignoring' shows the results of ignoring a adjustment penalty when it is present, Column 'assuming' shows the results of assuming an adjustment cost when it is absent.
+Values (ignoring, assuming) are given as the expected net present value (ENPV) as a fraction of that when no penalty is present, ENPV0.
+Percent reduction refers to penalty coefficient being calibrated to achieve the given percent reduction relative to ENPV0 when the penalty is optimally accounted for.
+Column c2 shows the coefficient chosen to achieve that reduction.
+Comparing the second and third columns shows that ignoring a real cost is a significantly graver error, particularly in the case of quadratic (L2) costs.}
+\end{center}
 \end{table}

### 2014-03-18 inst/examples/Reed.Rmd
Ricker dynamic shows steps in deterministic case
updates from previous runs

--- 2013-05-01 inst/examples/Reed.Rmd
@@
 ``` {r }
-f <- RickerAllee
-K <- 10
-pars <- c(2, K, 5)
+#f <- RickerAllee
+#pars <- c(2, K, 5)
+K <- 100
+pars <- c(1,100)
+f <- function(x,h,p){
+  sapply(x, function(x){
+    S = max(x - h, 0)
+  	p[1] * S * (1 - S/p[2]) + S
+  })
+}
+
 ````

### 2014-03-18 inst/doc/policycosts/writeup.Rmd
probably an old writeup, current one is in examples/policycosts

--- 2013-11-07 inst/examples/policycosts/writeup.Rmd
@@
 L1 <- function(c2) function(h, h_prev)  c2 * abs(h - h_prev) 
+free_increase <- function(c2) function(h, h_prev)  c2 * abs(pmin(h - h_prev, 0)) # increasing harvest is free
+free_decrease <- function(c2) function(h, h_prev)  c2 * pmax(h - h_prev, 0) # decreasing harvest is free
 fixed <-  function(c2) function(h, h_prev) c2 * as.numeric( !(h == h_prev) )
@@
 none <- function(h, h_prev)  0
-penaltyfns <- list(L2=L2, L1=L1, fixed=fixed)
+penaltyfns <- list(L2=L2, L1=L1, free_decrease=free_decrease, fixed=fixed, free_increase=free_increase)
 ````
@@
 values <- apply(index, 1, function(x) dt_npv[x[1], ][as.integer(x[2]), ]$value)
+
 percent.error <- (values - ((1-reduction)*npv0)) / ((1-reduction)*npv0)* 100
+
 print_npv <- data.frame(model=index$variable, "value realized"=values, 
@@
 fixed_policy <- policies$fixed[[apples_index["fixed"]]]$D
+#free_increase_policy <- policies$free_increase[[apples_index["free_increase"]]]$D
+#free_decrease_policy <- policies$free_decrease[[apples_index["free_decrease"]]]$D
+#quad_policy <- policies$quad[[apples_index["quad"]]]$D
 ```
@@
 ``` {r simulate_policy, dependson=c("policynames", "apples")}
+quad_profit <- profit_harvest(price = price, c0 = c0, c1 = apples["quad"])
 
 reps <- 1:100
-names(reps) = paste("rep", 1:length(reps), sep="_") # treat as a factor
-seeds <- 1:100
-
+names(reps) = paste("rep", 1:10, sep="_")
 sims <- list(
@@
                       L1_policy, z_g, z_m, z_i, 
-                      opt$D, profit=profit, penalty=L1(apples["L1"]), seed=seeds[x])), 
+                      opt$D, profit=profit, penalty=L1(apples["L1"]), seed=seed)), 
   L2 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                       L2_policy, z_g, z_m, z_i, 
-                      opt$D, profit=profit, penalty=L2(apples["L2"]), seed=seeds[x])),
+                      opt$D, profit=profit, penalty=L2(apples["L2"]), seed=seed)),
   fixed = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                          fixed_policy, z_g, z_m, z_i, 
-                         opt$D, profit=profit, penalty=fixed(apples["fixed"]), seed=seeds[x]))
+                         opt$D, profit=profit, penalty=fixed(apples["fixed"]), seed=seed))
 
@@
                       L1_policy, z_g, z_m, z_i, 
-                      opt$D, profit=profit, penalty=none, seed=seeds[x])), 
+                      opt$D, profit=profit, penalty=none, seed=seed)), 
   L2 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                       L2_policy, z_g, z_m, z_i, 
-                      opt$D, profit=profit, penalty=none, seed=seeds[x])),
+                      opt$D, profit=profit, penalty=none, seed=seed)),
   fixed = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                          fixed_policy, z_g, z_m, z_i, 
-                         opt$D, profit=profit, penalty=none, seed=seeds[x]))
+                         opt$D, profit=profit, penalty=none, seed=seed))
 )
@@
 ```{r p1, dependson="tidy", fig.width=12}
-p1 <- ggplot(subset(dt, replicate %in% names(reps)[1:5])) +
+p1 <- ggplot(dt) +
   geom_line(aes(time, alternate), col="grey20", lwd=1) +
-  geom_line(aes(time, fishstock), col=rgb(0,0,1,.8)) + 
-  facet_grid(replicate~penalty_fn) + 
+  geom_line(aes(time, fishstock), col=rgb(0,0,1,.8)) + facet_wrap(~penalty_fn) + 
   labs(x="time", y="stock size", title = "Stock Dynamics")
@@
 ```{r Figure3, dependson="tidy", fig.width=12}
-p2 <- ggplot(subset(dt, replicate %in% names(reps)[1:5])) +
+p2 <- ggplot(dt) +
   geom_line(aes(time, harvest_alt), col="grey20", lwd=1)  +
   geom_line(aes(time, harvest), col=rgb(0,0,1,.8)) + 
-  facet_grid(replicate~penalty_fn) + 
+  facet_wrap(~penalty_fn) + 
   labs(x="time", y="havest intensity (fish taken)", title = "Harvest Policy Dynamics")

### 2014-03-19 inst/doc/policycosts/policycosts.Rmd
synthesize paul's docs

----
title: Optimal management of a stochastically varying population when policy adjustment is costly
abstract: |
          Ecological systems are dynamic and policies to manage them need to
          respond to that variation. However, policy adjustments will sometimes
          be costly, which means that fine-tuning a policy to track variability in
          the environment very tightly will only sometimes be worthwhile. We use a
          classic fisheries management question – how to manage a stochastically
          varying population using annually varying quotas in order to maximize
          profit  - to examine how costs of policy adjustment change optimal
          management recommendations. Costs of policy adjustment (here changes in
          fishing quotas through time) could take different forms. For example,
          these costs may respond to the size of the change being implemented or
          there could be a fixed cost any time a quota change is made. We show
          how different forms of policy costs have contrasting implications for
          optimal policies. While some types of cost act to smooth out variation in
          quotas and stock sizes, as one might have expected, others can actually
          increase variation in stock sizes and quotas through time. We also show
          that the potential economic impact on the fishery of managers assuming
          policy adjustment costs are present when in fact they are absent is much
          smaller than the impact of managers assuming such costs are absent if
          they are present.
---

Introduction
============

Ecosystems are dynamic and exhibit rich patterns of variability in
both time and space. In designing management policies for ecosystems,
managers need to decide how much of that variation to respond to. Managers
could try to track variations in ecosystem dynamics very closely by
setting policies that are extremely responsive to the environment. Many
theoretical studies that seek to identify optimal policies for exploited
populations and communities adopt this approach and largely ignore the
challenges that would be involved in implementing such recommendations
(e.g., Reed 1979, Neubert 2003, Sethi et al. 2005, Halpern et
al. 2011). However, the policy process can often be much more sluggish
to respond to variations in ecosystem dynamics (Walters 1978, Armsworth
et al. 2012). Moreover, stakeholders impacted by ecosystem management
may prefer some stability and not want to deal with continually changing
management recommendations (Biais 1995, Armsworth and Roughgarden 2003,
Patterson 2007, Patterson & Resimont 2007, Sanchirico et al. 2008).
In other words, whatever gains are available from fine-tuning a
policy prescription to reflect environmental variation more closely
should be traded off against potential costs associated with the more
interventionist approach to management this would require.

To illustrate these concepts, Figure 1 show an example from fisheries
management. On the left axis, the figure shows a time series for the
estimated population size, represented as spawning stock biomass, of
west Atlantic bluefin tuna (Thunnus thynnus, henceforth bluefin) from
a recent stock assessment (ICCAT 20XX).  On the right axis the figure
also shows the catch quota for the stock that was set by the relevant
management agency (ICCAT 20XX). Despite the estimated population size
declining by XX% between YYYY and ZZZZ, the quota was not changed during
this period. Instead, the quota only changed occasionally and in between
times was left unaltered. Fishery management decisions regarding this
species can be highly contentious (Safina 1998, Sissenwine et al. 1998,
Porch 2005). Moreover, the stock is fished by fleets from many nations
with quotas being set by a multilaterial management agency through a
process of negotiation. As such, we might reasonably anticipate that
for this species there could be substantial transaction costs involved
in reaching agreement over any quota change, which could contribute to
the observed quota stability. More generally, reviews by Biais (1995) and
Patterson and Resimont (2007) document many cases where changes in catch
quotas that a management agency set were more modest than changes that
would be recommended just by considering variations in stock abundance.

We use a classic fisheries management question to examine how accounting
for costs of policy adjustment can change optimal policies (see also
Ludwig 1980, Feichtinger et al. 1994, Wirl 1999). We focus on how
harvest quotas for a stochastically varying fish population can be
chosen to maximize the net present value of a fishery. Our formulation
and solution method largely follow Reed’s classic treatment on this
question, a treatment repeated widely in bioeconomic textbooks. With
his formulation, Reed showed that a constant escapement policy could be
optimal under certain conditions. Such a policy involves choosing annual
quotas that are perfectly responsive to recruitment variation in a fish
stock. In poor recruitment years, the quota is set to zero and no fishing
is allowed. But any time there is a good recruitment pulse, a quota is
set that allows the fishery to exactly compensate through harvesting,
thereby maintaining the optimal escapement level. However, in that
analysis, Reed did not account for any costs of policy adjustment, which
for such a responsive management strategy potentially could be large.

As the example in Figure 1 makes clear, management policies will rarely be
as responsive as this constant escapement policy assumes. In this paper,
we explore conditions under which this lack of responsiveness may be a
rationale response on the part of managers. Specifically, we consider a
case where managers seek to balance the benefits in terms of increased
profits from fishing from more finely tracking recruitment variations
with the growing costs associated with adjusting policies quickly to do
so. The policy adjustment costs involved could reflect pure administrative
transaction costs or preferences held by fishermen, fish processing plants
or other stakeholders, for less variable quotas. In seeking to account
for these policy adjustment costs, we recognize that we do not know just
what functional form they should take and that it will require a lot of
empirical work to estimate that. Therefore, we scope three candidate
functional forms that represent different assumptions about how these
costs operate to determine whether the results we obtain are sensitive
to such differences.

-   Ecosystem management frequently set in terms of policy of quotas.

-   Policy relatively static and costly to change

-   Meanwhile, the natural world is variable

-   Optimal solutions typically track these shocks, resulting in
    impractical management recommendations in face of policy costs

*Develop a figure to insert here comparing quotas that were set to the
stock size estimated at that time in the stock assessment for two
different fish stocks. We choose the two stocks to highlight variation
in how responsive management can be. Suggested halibut and bluefin
tuna.*

Empirics suggest not always as responsive as Reed solution. Explore
conditions under which that makes sense. Idea is that regulator’s
objective sometimes may not be ‘raw’ NPV, but rather NPV with some
penalties on fast changes. Possible reasons: pure administrative
transaction cost of changing policies (reaching agreement), fishermens’
preferences for less variable quotas, processing plants’ preferences for
less variable quotas especially if tied into contracts for canning and
so forth. But we do not know what functional form of any such policy
adjustment costs takes and it will be a lot of work to estimate it. Here
we explore several plausible candidate functional forms that each
reflect different ways these policy adjustment costs could work. Would
be good to know if differences between functional forms is particularly
important.

Methods
=======

Fish population dynamics / state equation. We will assume Beverton-Holt
dynamics with multiplicative environmental noise

$$N_{t+1} = Z_t \frac{A (N_t - h_t)}{1 + B (N_t - h_t)}, 
\label{eq:state_equation}$$

where $N_t$ the stock size, $h_t$ the harvested level, 
$Z_t$ gives the stochastic shocks, which we
assume are lognormally distributed and $A$ and $B$ are positive
constants.

We assume managers set an annual quota for harvesting $h_t$ (the control
variable) after observing the stock size that year $N_t$ (the state
variable), but while still being uncertain about future environmental
conditions and stock sizes. Through time, this gives a time path of
management actions ${\bf h}=(h_1,h_2,\dots)$ that depend on the stock
sizes that were observed (a state dependent control rule).

We assume that managers choose annual quotas to maximize the expected
net present value (NPV) of the fishery. We take as a base case the
situation where there are no costs associated with policy adjustment and
the managers’ objective is

$$\max_{{\bf h}}\mathbf{ E} ( NPV_{0} )=\max_{{\bf h}} \sum_0^\infty \mathbf{E} \left( \displaystyle \frac{\Pi_0(N_t,h_t)}{(1+\delta)^{t+1}} \right)
\label{eq:objective}$$

where $\mathbf{E}$ is the expectation operator, $\delta>0$ is the
discount rate and $\Pi_0$ is the net revenue from operating the fishery
in a given year. In this base case, we assume the annual net revenue
from fishing is

$$\Pi_0(N_t,h_t) = p h_t -  c_0 E_t
\label{eq:annual_netrevenue}$$

where $E_t$ represents fishing effort. We assume catch is proportional
to stock size and effort expended fishing that year, $h_t=qE_tN_t$ and
constant $q>0$ is the catchability coefficient. In
Eqn. [eq:annual~n~etrevenue], $p$ is the price per unit harvest and
$c_0$ the cost of fishing and, to simplify the presentation of results,
we assume that these are constants with $p>0$ and $c_0>0$.

Taken together this objective function ([eq:objective]) and the state
equation ([eq:state~e~quation]) define a stochastic dynamic programming
problem that we solve using backwards recursion via Bellman’s equation.
We denote the resulting state-dependent, optimal control as
${\bf h_0^*}$. PRESUMABLY YOU USED A FINITE TERMINAL TIME IN WHICH CASE
WE NEED TO REVISE TO REFLECT HOW YOU HANDLED THAT.

Costs of policy adjustment {#costs-of-policy-adjustment .unnumbered}
--------------------------

We compare this base case to three alternative problem formulations,
each reflecting different plausible functional forms that costs of
policy adjustment could take. In each, we assume managers can adjust the
quota set in the fishery $h_t$ in a given year and that any policy
adjustment costs are associated with changes to this control variable.

First we assume that policy adjustment costs are directly proportional
to the magnitude of the change in policy being proposed, such that
larger changes to annual harvesting quotas incur greater policy
adjustment penalties. Specifically, we replace $\Pi_0$ in the $NPV_0$
equation with

$$\Pi_{1}(N_t,h_t, h_{t-1}) = \Pi_0 - c_1  |  h_t - h_{t-1} | \,.$$

Next we continue to assume that policy adjustment costs depend on the
magnitude of the change in policy being proposed. However, we consider a
case where this dependence is nonlinear with big changes in policy being
disproportionately expensive:

$$\Pi_{2}(N_t,h_t, h_{t-1}) = \Pi_0 - c_2 (  h_t - h_{t-1})^2 \,.$$

Finally, we assume instead that there is a fixed cost associated with
any adjustment of policy, regardless of how large that adjustment might
be

$$\Pi_{3}(N_t,h_t, h_{t-1}) = \Pi_0 - c_3 (1-\mathbf{I}(h_t, h_{t-1}))  \,,$$

where indicator function $\mathbf{I}(h_t, h_{t-1})$ takes the value 1 if
$h_t=h_{t-1}$ and zero otherwise. For each $\Pi_i$, we can then define a
new objective function $NPV_i$ similar to that in Eqn. [eq:objective].

Taken together with the state equation (Eqn. [eq:state~e~quation]), each
of these new objective functions defines a different stochastic dynamic
programming problem. Again, we solve them numerically using backwards
recursion. To include costs of policy adjustment, we expand the state
space to include both the current stock size and the management action
taken on the previous time step $(N_t,h_{t-1})$. For each new objective
function $\max NPV_i$, we denote the corresponding optimal control
policy $ {\bf h_i^*} $.

<!-- NOTE Will need to do the runs and generate the figures for that one  -->
In addition in the Supplementary Material, we compare our results with a
more conventional fisheries economic formulation in which additional
costs are applied to the control variables themselves, as opposed to
adjustments to the controls:
$ \Pi_4 (N_t,h_t) = p h_t -  c_0 E_t-c_4E_t^2$. Additional costs of this
form tend to have a smoothing effect on optimal quotas, but also change
the long-term average stock size or quota size that is optimal.

Choice of parameters {#choice-of-parameters .unnumbered}
--------------------

Each of the policy adjustment cost function is characterized in terms of
a cost coefficient $c_i$. However, $c_i$ takes different units for each
functional form. Therefore, if seeking to compare the relative effect of
each penalty function on optimal management, it is unclear what
parameter values should be used. To address this issue, we calibrate
choices of $c_i$ so that each has a comparable impact on the optimal net
present value of fishery, broadly following the example of Bovenberg,
Goulder and Gurnery (2005) and Bovenberg, Goulder and Jacobsen (2008).
<!--NOTE Jake to confirm these are still relevant and needed. We are using a less sophisticated normalization than was once discussed and may or may not need the citations now. -->

Figure 1 shows the calibration graphically. Each curve plots the change
in maximum expected NPV for a given penalty function as the penalty cost
parameter is increased. In each case, the figure shows maximum expected
NPV with policy adjustment costs as a proportion of the maximum expected
NPV available in the basic problem $NPV_0({\bf h_0^*})$ without policy
adjustment costs.

To compare the impact of penalty functions on optimal management across
the different functional forms, we select penalty cost coefficients that
induce the same reduction in maximum expected NPV. For example, the
dashed vertical lines in Figure 1 map the needed cost coefficient $c_i$,
for each penalty function, such that the fishery is worth 80% of its
unconstrained value when optimally managed.

We focus our examination of the models on how the type and severity of
policy adjustment costs affects the optimal management strategy. To
simplify presentation of the results, we will illustrate cases where the
growth parameters are chosen so that the intrinsic rate of increase of
the fish population is 1 and the equilibrium biomass for the equivalent
deterministic model without harvesting is 100; specifically, $A=2$ and
$B=0.01$ in Eqn. (1)). To characterize environmental variability, we
assume multiplicative shock $Z_t$ is distributed HOW? In addition, we
show cases where $p=1$, $\delta=0.05$ and $c_0$ is chosen such that the
optimal stock size in the analogous deterministic problem is 5% larger
than that corresponding to the maximum sustainable yield in biomass
($c_0=XXX$).

![**Expected net present value by functional form of penalty.** Horizontal axis shows the coefficient $c_i$ governing the magnitude of the policy cost, while vertical axis shows fraction of the maximum expected net present value dissipated by the policy cost.  The horizontal line indicates a value of the stock that is 80\% of the maximum expected value in the absence of policy adjustment costs, $NPV_0({\bf h_0^*})$. Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs. ](figure/Figure_1.pdf)

<!-- NOTE
Figure needs tidying up to be submission ready. Resize it – can be smaller, no color needed, bigger TickLabels, no background shading or grid. It also need the relevant horizontal and vertical lines marking to show the calibration. Choose a % reduction that corresponds to that you are choosing for what is currently labeled Figs 2&3 (sample paths) and Fig 8 – histograms. We should then adjust the text to talk to what is shown in the figure consistently – e.g. is is 25% loss or 75% of the value, etc. -->

Results
=======

Effect of policy adjustment costs on optimal quotas and stock sizes {#effect-of-policy-adjustment-costs-on-optimal-quotas-and-stock-sizes .unnumbered}
-------------------------------------------------------------------

<!-- If, as discussed over email, we are going to go with just one in the main text blown up a bit bigger to make it more visible, I need to have that figure to be able to write this text around it. Note I would still present the full set in the SI. Rather than trying to recover old random seeds if not stored. Just run one anew. -->
<!-- 
For the figure in the main text, I would make a single figure with six plates – the three different adjustment costs are the columns. One row is the effect on optimal harvests and one the effect on optimal stock sizes. -->

Figure 2 illustrates how the different forms of adjustment cost can
impact the optimal policy. Each panel is generated against the same
sequence of random shocks so that they can be compared directly. Figure
3 shows the corresponding stock sizes, which are measured here WHEN

<!-- At what time relative to the dynamics in equation 1, and I would be setting up a comment why they don’t see something similar to the constant escapement policy – this is just a census time issue, but I would say it explicitly given the attention we shine on the REED result upfront.
-->

. In 
each case, the optimal solution without any adjustment cost is shown in
black and the policy induced by optimization under the given adjustment
penalty (equivalent to a 25% reduction in maximum expected NPV) is
overlaid in blue.

When considering the first formulation of policy adjustment costs
($\Pi_1$), the first panel of Figure 2 shows a typical pattern, in which
the optimal policy tends to avoid small policy adjustments, resulting in
long periods of constant policy followed by sudden bursts of adjustment.
This results in a relatively step-like policy pattern. In contrast, the
second formulation $\Pi_2$ disproportionately penalizes large policy
adjustments. The corresponding optimal policy tracks all of the changes
made by the cost-free policy, but with smaller magnitude. This results
in a smoother $h_t$ curve, one that undershoots the larger oscillations
seen in the cost-free optimum in favor of a policy that changes
incrementally each year. Finally, the optimal policy for the third,
‘fixed fee’ formulation ($\Pi_3$) only makes large adjustments, as one
might expect, because the magnitude of the adjustment made is not
reflected in the resulting penalty. Whereas the optimal solution for
$\Pi_1$ attempts to accommodate the large oscillations at the end of the
period shown (time steps $t=47-49$) with a constant quota in between the
extremes, the fixed fee version takes the opposite approach of one very
large swing. MORE DETAILING TO COME WHEN WE HAVE THE FIGURES

<!-- Flush out details in Figure captions-->
![Individual realizations of optimal harvesting strategy under the different functional forms of adjustment costs.](figure/Figure_2)

![Individual realizations of optimal stock size strategy under the different functional forms of adjustment costs](figure/Figure_3)

The comparisons shown in Figure 2 are for one realization (i.e. a
particular sequence of random number draws representing environmental
variability) and are made for a particular magnitude of policy
adjustment costs equal to 25% of the maximum expected net present value <!-- Match to that shown in Figure 1. -->
in the base case ($NPV_0({\bf h_0^*})$). Figure 4 generalizes to show
how optimal harvest levels and corresponding optimal stock sizes are
affected by the magnitude of the costs of policy adjustment. This time
we show summary statistics across 50 replicate sets of environmental
conditions. We show the impact of policy adjustment costs on the
variance of both harvests and stock sizes through time; on the
autocorrelation of harvests and stock sizes through time; and on the
cross-correlation of harvests and stock sizes through time. <!-- Are we showing cross-correlations or not?-->

For example, when small policy adjustment costs cost little but large
adjustments are expensive ($\Pi_2$), we see the smoothing signal that we
might have expected (see also Ludwig 1980 for this particular case). As
cost penalties increase in severity (i.e., $c_2$ increases), the
variance in quotas through time decreases and the autocorrelation of
quotas through time increases. This smoothing of the harvest quotas
through time has knock-on effects for the corresponding optimal stock
sizes, which also become more autocorrelated as the scaling on policy
adjustment costs ($c_2$) is increased. The autocorrelation in stock
sizes here reflects the lag involved in a more modest increase in
harvests taking longer to eliminate the signal of strong recruitment
events, when compared to a more immediately responsive constant
escapement policy.

Interestingly, as suggested by the realization in Fig. 3, including a
fixed cost of policy adjustment increases the variation in harvests
through time. This is the opposite of a smoothing effect. Follow-on
consequences for the other statistics are not as clear in this case.

Finally, the case where policy adjustment costs scale linearly with the
size of the adjustment ($\Pi_1$ in Eqn. 4) appear to be something of a
middle of the road strategy, in that increasing the severity of policy
adjustment costs (increasing $c_1$ has little effect on the variance or
autocorrelation of optimal harvest rates or stock sizes. To reveal the
particular impact of policy adjustment costs of this type requires a
more targeted summary statistic. Specifically, for each run we
calculated the frequency with which the optimal policy involved
maintaining a positive quota across multiple time steps unaltered. This
type of policy is arguably the most commonly observed behavior in TAC
management, but is one that is almost never observed to be part of the
optimal management strategy in the basic model without policy adjustment
costs (Eqn. 3) or when optimizing against $\Pi_2$ or $\Pi_3$. While
still not common for the particular parameter combinations we examine,
we find that positive unaltered quotas through time are much more likely
to occur when optimizing against $\Pi_1$ where policy adjustment costs
scale linearly with the size of proposed policy changes (STATISTIC).
Moreover, these occurrences increase in frequency as the severity of
these costs ($c_1$) increases (STATISTIC).

<!--
Assuming we aren’t showing cross-correlations, I think we can probably fit these into a single four subplot figure. Cross-correlations would be a little harder but just using 5 subplots from what could have been a 6 subplot figure would also work, because a journal could just put the caption into the empty space.

Same comments as before on labeling the curves and detailing in the figure captions. Axis labels and things all also need work.
-->

![Figure 4a: Variance of optimal harvest rates through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.](figure/Figure_4a.pdf)

![Figure 4b: Autocorrelation of optimal harvest rates through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs](figure/Figure_4b.pdf)

![Figure 5a: Variance of optimal stock sizes through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.](figure/Figure_5a.pdf)

![Figure 5b: Autocorrelation of optimal stock sizes through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.](figure/Figure_5b.pdf)

Consequences of policy adjustment costs {#consequences-of-policy-adjustment-costs .unnumbered}
---------------------------------------

Next we examine the consequences either of ignoring policy adjustment
costs when they are present or assuming they are present when they are
not. To do so, it helps to break-down the different contributions to the
maximum expected $NPV_i$ when employing the optimal policy $\bf{h_i}^*$
versus when employing the policy that would be optimal were there no
costs to policy adjustment $\bf{h_0}^*$. For example, if we take the
first of the adjustment penalty forms, $\Pi_1$

$$NPV_i( \mathbf{h_1^*} ) = \sum_{t=0}^\infty (\overbrace{ p h^*_{1,t}-c_0E^*_{1t}}^{[1]}-\overbrace{c_1 | h^*_{1,t}- h^*_{1,t-1}|}^{[2]} ) \displaystyle \frac{1}{(1+\delta)^t}$$

and

$$NPV_i( \mathbf{h_0^*} ) = \sum_{t=0}^\infty (\underbrace{ p h^*_{0,t}-c_0E^*_{0t}}_{[3]}-\underbrace{c_1 | h^*_{0,t}- h^*_{0,t-1}|}_{[4]} ) \displaystyle \frac{1}{(1+\delta)^t}$$

Histograms for the different contributions labelled $[1]-[4]$ here when
taken across XXX replicate runs are shown are shown in Figure 5
(contribution $[1]$ red, $[2]$ green, $[3]$ blue, and $[4]$ mauve). The
cost of assuming policy adjustments are present when in fact they are
absent is given by subtracting the contribution to the first infinite
sum from term $[1]$ from the contribution to the second infinite sum of
term $[3]$ (blue - red in the Figure). (Note that convergence properties
required to do this are met because we assume a positive discount rate).
This cost is positive because the optimal controls recommended when
assuming policy adjustment costs are present do not track variations in
stock size as closely. Therefore, this harvesting strategy provides
lower net revenue dockside.

In contrast, the cost of ignoring policy adjustment costs when in fact
they are present is given by subtracting the second infinite sum from
the first (contributions $([1]-[2])-([3]-[4]))$ in the equations. These
costs are positive because the lost revenues from not tracking stock
variations as closely are smaller than the penalties of policy
adjustment that are incurred if managers try to track stock variations
more tightly.

**

![image](figure/Figure_6)

Table 1 compares these different contributions, namely the $NPV$ lost by
assuming policy adjustment costs when none are present (first entry in
each cell, $ [3]-[1]$ in the equations)) and the $NPV$ lost when
ignoring policy adjustment costs when they are present (second entry in
each cell of the table, contributions $([1]-[2])-([3]-[4]))$ in the
equations) across the three different functional forms. Specifically,
the table shows how these values change as we vary the severity of
policy adjustment costs. In each case, values are shown as percentages
of the maximum expected $NPV$ in the base case where no policy
adjustment costs apply or are assumed to apply $NPV_0({\bf h_0^*})$. For
a sensitivity test where we draw similar comparisons for different
amounts of environmental variation, see Supplementary Information X.X.

We find a pronounced asymmetry when comparing the impact on the net
present value of the fishery of assuming policy adjustment costs are
present when they are absent with the impact of assuming they are absent
when they are present. For all three types of policy adjustment cost,
the impact on NPV of ignoring these costs if they are in fact present is
much bigger than that incurred by fallaciously managing as if they are
present when they do not occur. This asymmetry arises, because there is
less difference in the dockside revenue under the two management
recommendations than there is in the potential policy adjustment costs
themselves, as is evident in for the particular parameters shown in
Figure 5.

We also see that the impacts on net present value of the fishery of
incorrectly assuming or ignoring policy adjustment costs are most severe
when these costs are assumed to scale quadratically with the size of the
policy change being implemented ($\Pi_2$).

<!--
Obviously we have presentation choices to make here. I think there is plenty of scope either to compact this table somehow (rows are penalty functions)  x columns are percent reduction.

There would also be lots of scope for showing the same info visually as a simple bar chart
-->

      penalty fn     ignoring   assuming   percent reduction      c2
  --- ------------ ---------- ---------- ------------------- -------
    1 L1                 0.81       1.00                0.10    0.40
    2 L1                 0.62       0.99                0.20    0.81
    3 L1                 0.35       0.97                0.30    2.02
    4 L2                 0.68       0.95                0.10    0.81
    5 L2                 0.44       0.89                0.20    1.62
    6 L2                -0.28       0.81                0.30    2.83
    7 fixed              0.78       1.00                0.10    3.64
    8 fixed              0.56       0.99                0.20    8.08
    9 fixed              0.31       0.97                0.30   12.93

  Table 1: Column 'ignoring' shows the results of ignoring a adjustment penalty when it is present, Column 'assuming' shows the results of assuming an adjustment cost when it is absent. Values (ignoring, assuming) are given as the expected net present value (ENPV) as a fraction of that when no penalty is present, ENPV0.  Percent reduction refers to penalty coefficient being calibrated to achieve the given percent reduction relative to ENPV0 when the penalty is optimally accounted for.  Column c2 shows the coefficient chosen to achieve that reduction. Comparing the second and third columns shows that ignoring a real cost is a significantly graver error, particularly in the case of quadratic (L2) costs.

Discussion
==========

TO COME PENDING WHAT THE RESULTS SHOW.

-   From Meeting 3: Interest in how the inclusion of these costs would
    operationally put a population at greater risk of extinction (e.g.
    if including the transaction costs increases the variance and
    autocorrelation of $N$ when subject to the optimal policy). Should
    expect this, because as the transaction costs become infinite, you
    would never change your policy which puts you in the world of open
    loop control - TAC fixed for all time, which we know puts the stock
    at greater risk of extinction.

-   On Table 1 should flag that might also be good to look at
    autocorrelated environmental noise and how that affects thing. Here
    we look at how the optimal policy induces more color in the stock
    size EVEN though the environmental variability going into it is
    white noise. - QUERY - HOW MUCH AUTOCORRELATION INDUCED BY STOCK
    DYNAMICS IN THE ABSENCE OF HARVESTING

-   for case of bluefin, interpreting (1), (2), (3), and (4) in terms of
    how much you would have available to pay the Japanese and Canadians
    to convince them to participate in an expedited process to change
    TACs. Similarly for other contexts.

-   Comparison of the optimal policy solution to the Reed model,
    traditional economic smoothing penalty - which now appears in SI

-   Comparison between the different functional forms – smoothing (L2)
    non-smoothing (L1), and de-stablizing (fixed).

-   Induced costs (relative to free adjustment) vs direct costs (paid
    for adjusting)

-   Contrast steady-state results to dynamic solutions under stochastic
    shocks.

**Key conclusions:**

1.  **Lesson for modelers**: Ignoring the reality of policy costs leads
    to less effective management (decreased value) (increased extinction
    risk?)

2.  **Lesson for policy makers**: Decreasing adjustment costs not only
    saves direct costs, but permits higher-value solutions.

### 2014-05-23 manuscripts/manuscript.Rmd
reorganize following current template

--- 2014-03-19 inst/doc/policycosts/policycosts.Rmd
@@
 title: Optimal management of a stochastically varying population when policy adjustment is costly
+author: 
+  - name: Carl Boettiger
+    affiliation: cstar
+    email: cboettig@gmail.com
+    footnote: Corresponding author
+  - name: Michael Bode
+    affiliation: melbourne
+  - name: Jacob LaRiviera
+    affiliation: UTK
+  - name: James Sanchirico
+    affiliation: UCD
+  - name: Alan Hastings
+    affiliation: UCD
+  - name: Paul Armsworth 
+    affiliation: UTK
+
+address: 
+  - code: cstar
+    address: | 
+      Center for Stock Assessment Research,
+      110 Shaffer Rd,
+      Santa Cruz, CA 95050, USA 
+  - code: UCD
+    address: Department of Environmental Science and Policy, University of California, Davis
+  - code: melbourne
+    address: University of Melbourne, Australia 
+  - code: UTK
+    address: University of Tennessee, Knoxville
+
 abstract: |
@@
           they are present.
+
+layout: preprint      # review, 11pt
 ---
@@
 challenges that would be involved in implementing such recommendations
-(e.g., Reed 1979, Neubert 2003, Sethi et al. 2005, Halpern et
-al. 2011). However, the policy process can often be much more sluggish
-to respond to variations in ecosystem dynamics (Walters 1978, Armsworth
-et al. 2012). Moreover, stakeholders impacted by ecosystem management
+[e.g., @Reed1979; @Neubert2003; @Sethi2005; @Halpern2011]. However, 
+the policy process can often be much more sluggish
+to respond to variations in ecosystem dynamics [@Walters1978; @Armsworth2012]. 
+Moreover, stakeholders impacted by ecosystem management
 may prefer some stability and not want to deal with continually changing
-management recommendations (Biais 1995, Armsworth and Roughgarden 2003,
-Patterson 2007, Patterson & Resimont 2007, Sanchirico et al. 2008).
+management recommendations [@Biais1995; @Armsworth2003;
+@Patterson2007; @PattersonResimont2007; @Sanchirico2008].
 In other words, whatever gains are available from fine-tuning a
@@
 estimated population size, represented as spawning stock biomass, of
-west Atlantic bluefin tuna (Thunnus thynnus, henceforth bluefin) from
-a recent stock assessment (ICCAT 20XX).  On the right axis the figure
+west Atlantic bluefin tuna (_Thunnus thynnus_, henceforth bluefin) from
+a recent stock assessment [@ICCAT20XX].  On the right axis the figure
 also shows the catch quota for the stock that was set by the relevant
-management agency (ICCAT 20XX). Despite the estimated population size
+management agency [@ICCAT20XX]. Despite the estimated population size
 declining by XX% between YYYY and ZZZZ, the quota was not changed during
@@
 times was left unaltered. Fishery management decisions regarding this
-species can be highly contentious (Safina 1998, Sissenwine et al. 1998,
-Porch 2005). Moreover, the stock is fished by fleets from many nations
+species can be highly contentious (@Safina1998, @Sissenwine1998,
+@Porch2005). Moreover, the stock is fished by fleets from many nations
 with quotas being set by a multilaterial management agency through a
@@
 in reaching agreement over any quota change, which could contribute to
-the observed quota stability. More generally, reviews by Biais (1995) and
-Patterson and Resimont (2007) document many cases where changes in catch
+the observed quota stability. More generally, reviews by @Biais1995 and
+@Patterson2007 document many cases where changes in catch
 quotas that a management agency set were more modest than changes that
@@
 for costs of policy adjustment can change optimal policies (see also
-Ludwig 1980, Feichtinger et al. 1994, Wirl 1999). We focus on how
+@Ludwig1980, @Feichtinger1994, @Wirl1999). We focus on how
 harvest quotas for a stochastically varying fish population can be
@@
 
-$$N_{t+1} = Z_t \frac{A (N_t - h_t)}{1 + B (N_t - h_t)}, 
-\label{eq:state_equation}$$
+$$N_{t+1} = Z_t \frac{A (N_t - h_t)}{1 + B (N_t - h_t)}, \label{eq:state_equation}$$
 
@@
 
-$$\max_{{\bf h}}\mathbf{ E} ( NPV_{0} )=\max_{{\bf h}} \sum_0^\infty \mathbf{E} \left( \displaystyle \frac{\Pi_0(N_t,h_t)}{(1+\delta)^{t+1}} \right)
-\label{eq:objective}$$
+$$\max_{{\bf h}}\mathbf{ E} ( NPV_{0} )=\max_{{\bf h}} \sum_0^\infty \mathbf{E} \left( \displaystyle \frac{\Pi_0(N_t,h_t)}{(1+\delta)^{t+1}} \right) \label{eq:objective}$$
 
@@
 
-$$\Pi_0(N_t,h_t) = p h_t -  c_0 E_t
-\label{eq:annual_netrevenue}$$
+$$\Pi_0(N_t,h_t) = p h_t -  c_0 E_t \label{eq:annual_netrevenue}$$
 
@@
 constant $q>0$ is the catchability coefficient. In
-Eqn. [eq:annual~n~etrevenue], $p$ is the price per unit harvest and
+Eqn. [eq:annual_netrevenue], $p$ is the price per unit harvest and
 $c_0$ the cost of fishing and, to simplify the presentation of results,
@@
 Taken together this objective function ([eq:objective]) and the state
-equation ([eq:state~e~quation]) define a stochastic dynamic programming
+equation ([eq:state_equation]) define a stochastic dynamic programming
 problem that we solve using backwards recursion via Bellman’s equation.
-We denote the resulting state-dependent, optimal control as
-${\bf h_0^*}$. PRESUMABLY YOU USED A FINITE TERMINAL TIME IN WHICH CASE
-WE NEED TO REVISE TO REFLECT HOW YOU HANDLED THAT.
+We denote the resulting state-dependent, optimal control as $h_0^{\ast}$.
+
+<!--PRESUMABLY YOU USED A FINITE TERMINAL TIME IN WHICH CASE
+WE NEED TO REVISE TO REFLECT HOW YOU HANDLED THAT.-->
 
@@
 
-Taken together with the state equation (Eqn. [eq:state~e~quation]), each
+Taken together with the state equation (Eqn. [eq:state_equation]), each
 of these new objective functions defines a different stochastic dynamic
@@
 function $\max NPV_i$, we denote the corresponding optimal control
-policy $ {\bf h_i^*} $.
+policy $h_i^*$.
 
@@
 costs are applied to the control variables themselves, as opposed to
-adjustments to the controls:
-$ \Pi_4 (N_t,h_t) = p h_t -  c_0 E_t-c_4E_t^2$. Additional costs of this
+adjustments to the controls: $\Pi_4 (N_t,h_t) = p h_t -  c_0 E_t-c_4E_t^2$. Additional costs of this
 form tend to have a smoothing effect on optimal quotas, but also change
@@
 
-![**Expected net present value by functional form of penalty.** Horizontal axis shows the coefficient $c_i$ governing the magnitude of the policy cost, while vertical axis shows fraction of the maximum expected net present value dissipated by the policy cost.
+<!-- ![**Expected net present value by functional form of penalty.** Horizontal axis shows the coefficient $c_i$ governing the magnitude of the policy cost, while vertical axis shows fraction of the maximum expected net present value dissipated by the policy cost.
 The horizontal line indicates a value of the stock that is 80\% of the maximum expected value in the absence of policy adjustment costs, $NPV_0({\bf h_0^*})$.
@@
 ](figure/Figure_1.pdf)
+
+-->
 
@@
 
-<!-- Flush out details in Figure captions-->
+<!--
 ![Individual realizations of optimal harvesting strategy under the different functional forms of adjustment costs.](figure/Figure_2)
@@
 ![Individual realizations of optimal stock size strategy under the different functional forms of adjustment costs](figure/Figure_3)
+-->
 
@@
 
+<!--
 ![Figure 4a: Variance of optimal harvest rates through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.](figure/Figure_4a.pdf)
@@
 ![Figure 5b: Autocorrelation of optimal stock sizes through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.](figure/Figure_5b.pdf)
+-->
 
@@
 
-![image](figure/Figure_6)
+<!-- ![image](figure/Figure_6) -->
 
@@
 assuming policy adjustment costs when none are present (first entry in
-each cell, $ [3]-[1]$ in the equations)) and the $NPV$ lost when
+each cell, $[3]-[1]$ in the equations)) and the $NPV$ lost when
 ignoring policy adjustment costs when they are present (second entry in

### 2014-05-23 manuscripts/components/knit.R

@@ -1,0 +1,26 @@
+#!/usr/bin/Rscript
+args <- commandArgs(TRUE)
+file <- args[1]
+
+## FIXME add second argument to handle figure types
+
+## Set the paths for cache and figure
+library("methods")
+library("knitr")
+basename <- gsub(".Rmd", "", file) # knitr:::knit_concord$get('infile')) 
+opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
+               cache.path = paste("components/cache/", basename, "/", sep=""))
+opts_chunk$set(cache = 2)
+opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, comment = NA, verbose = TRUE)
+
+# PDF-based figures
+opts_chunk$set(dev='pdf')
+
+# Better to use a temporary markdown file (best to not overwrite basename.md since that can be used to display on GitHub)
+# For now use basename, since pandoc function in knitr 1.5 doesn't respect output name from config (fixed in knitr 1.5.32)
+output <- paste(basename, ".md", sep="")
+
+## Knit
+knit(file, output)
+
+

### 2014-05-23 manuscripts/components/restore-cache.R

@@ -1,0 +1,19 @@
+#!/usr/bin/R
+setwd("components")
+archive <- "template-manuscript-cache.tar.gz"
+
+
+library("utils")
+library("httr")
+# restore cache file
+target <- paste0("http://two.ucdavis.edu/~cboettig/data/", archive)
+cache <- GET(target)
+if(cache$status_code != 404){
+  writeBin(content(cache, "raw"), archive)
+  untar(archive)
+  unlink(archive)
+}
+
+setwd("..")
+
+

### 2014-05-23 manuscripts/manuscript.Rmd
avoid printing unnecessary outputs

@@
-----
+---
 title: Optimal management of a stochastically varying population when policy adjustment is costly
@@
     affiliation: UTK
-
 address: 
@@
     address: University of Tennessee, Knoxville
-
 abstract: |
@@
           they are present.
-
 layout: preprint      # review, 11pt
 ---
+
+<!-- CODE -->
+
+```{r libraries, output="hide", include=FALSE, cache=FALSE}
+rm(list=ls())
+library("pdgControl")
+library("reshape2")
+library("ggplot2")
+library("data.table")
+library("pander")
+theme_set(theme_bw())
+```
+
+``` {r profit_model}
+price = 10
+c0 = 30
+profit <- profit_harvest(price = price, c0 = c0, c1 = 0)
+```
+
+```{r c2_grid}
+c2 <- exp(seq(0, log(41), length.out = 40))-1
+c2 <- seq(0, 40, length.out=100)
+```
+
+```{r reduction}
+reduction <- 0.25 
+```
+
+```{r setup}
+seed <- 123                 # Random seed (replicable results)
+delta <- 0.05               # economic discounting rate
+OptTime <- 20               # stopping time
+gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
+sigma_g <- 0.2              # Noise in population growth
+reward <- 0                 # bonus for satisfying the boundary condition
+z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
+z_m <- function() 1         # No measurement noise, 
+z_i <- function() 1         # No implemenation noise
+f <- BevHolt                # Select the state equation
+pars <- c(1.5, 0.05)        # parameters for the state equation
+K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
+xT <- 0                     # boundary conditions
+x0 <- K
+x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
+h_grid <- seq(0.01, 0.8 * K, length = gridsize)  
+````
+
+```{r reed, dependson=c("setup", "profit_model")}
+SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
+opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
+                     profit, delta, reward=reward)
+````
+
+```{r fees}
+L1 <- function(c2) function(h, h_prev)  c2 * abs(h - h_prev) 
+fixed <-  function(c2) function(h, h_prev) c2 * as.numeric( !(h == h_prev) )
+L2 <- function(c2) function(h, h_prev)  c2 * (h - h_prev) ^ 2
+none <- function(h, h_prev)  0
+penaltyfns <- list(L2=L2, L1=L1, fixed=fixed)
+````
+
+```{r parallel, include=FALSE}
+require(snowfall)
+sfInit(cpu=4, parallel=T)
+sfLibrary(pdgControl)
+sfExportAll()
+````
+
+``` {r bigloop, dependson=c("setup", "reed", "fees", "profit_model", "c2_grid")}
+policies <- lapply(penaltyfns, function(penalty){
+  sfLapply(c2, function(c2){
+      policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
+                   profit, delta, reward, penalty = penalty(c2))
+      }
+  )
+})
+````
+
+```{r, dependson="quadcosts"}
+i <- which(x_grid > K)[1]
+fees <- 
+lapply(policies, function(penalty) 
+  sapply(penalty, function(c2_run)
+    max(c2_run$V[i,]) # Would be penalty_free_V originally   ## this isn't correct for asym cases
+  )
+)
+```
+
+``` {r npv-plot, dependson="quadcosts"}
+npv0 <- max(fees$L1) # all have same max, at c2=0 
+fees <- data.frame(c2=c2,fees)
+fees <- melt(fees, id="c2")
+
+fees <- subset(fees, variable %in% c("L1", "L2", "fixed"))
+ggplot(fees, aes(c2, value, col=variable)) + geom_point() + geom_line()
+````
+
+```{r apples_plot, dependson="quadcosts"}
+ggplot(fees, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
+````
+
+```{r apples, dependson=c("quadcosts", "reduction")}
+closest <- function(x, v){
+  which.min(abs(v-x))
+}
+dt_npv <- data.table(fees)
+index <- dt_npv[,closest(reduction, (npv0-value)/npv0), by=variable]
+apples_index <- index$V1
+names(apples_index) = index$variable
+apples <- c2[index$V1]
+````
+
+```{r reductions}
+reduction_table <- sapply(c("0.10" = 0.10, "0.20" = 0.20, "0.30" = 0.30), function(reduction){
+index <- dt_npv[,closest(reduction, (npv0-value)/npv0), by=variable]
+apples <- c2[index$V1]
+names(apples) = index$variable
+apples })
+write.csv(reduction_table, "reduction_table.csv")
+````
+
+```{r print_npv, dependson="apples"}
+setkey(dt_npv, variable)
+values <- apply(index, 1, function(x) dt_npv[x[1], ][as.integer(x[2]), ]$value)
+percent.error <- (values - ((1-reduction)*npv0)) / ((1-reduction)*npv0)* 100
+print_npv <- data.frame(model=index$variable, "value realized"=values, 
+                        "percent of npv0" = 100*values/npv0, "percent error"=percent.error)
+
+```
+
+```{r npv_table, dependson="print_npv", results='asis'} 
+pandoc.table(print_npv)
+```
+
+```{r policynames}
+L2_policy <- policies$L2[[apples_index["L2"]]]$D
+L1_policy <- policies$L1[[apples_index["L1"]]]$D
+fixed_policy <- policies$fixed[[apples_index["fixed"]]]$D
+```
+
+```{r simulate_policy, dependson=c("policynames", "apples")}
+reps <- 1:100
+names(reps) = paste("rep", 1:length(reps), sep="_") # treat as a factor
+seeds <- 1:100
+sims <- list(
+  L1 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
+                      L1_policy, z_g, z_m, z_i, 
+                      opt$D, profit=profit, penalty=L1(apples["L1"]), seed=seeds[x])), 
+  L2 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
+                      L2_policy, z_g, z_m, z_i, 
+                      opt$D, profit=profit, penalty=L2(apples["L2"]), seed=seeds[x])),
+  fixed = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
+                         fixed_policy, z_g, z_m, z_i, 
+                         opt$D, profit=profit, penalty=fixed(apples["fixed"]), seed=seeds[x]))
+
+)
+```
+
+```{r tidy, dependson="simulate_policy"}
+#Make data tidy (melt), fast (data.tables), and nicely labeled.
+dat <- melt(sims, id=names(sims[[1]][[1]]))  
+dt <- data.table(dat)
+setnames(dt, "L2", "replicate") # names are nice
+setnames(dt, "L1", "penalty_fn") # names are nice
+```
+
+```{r profit_calcs, dependson="tidy"}
+# Profit when accounting for penalty when present
+optimal_cost <- dt[, sum(profit_fishing - policy_cost), by=penalty_fn ]
+
+# Profit when ignoring penalty when present
+ignore_when_present <- dt[, sum(profit_fishing_alt - policy_cost_alt), by=penalty_fn]
+
+# Profit when assuming penalty when it is absent
+assume_when_absent <- dt[, sum(profit_fishing), by=penalty_fn]
+
+# Profit when ignoring penalty when it is absent
+optimal_free <- dt[, sum(profit_fishing_alt), by=penalty_fn]
+
+# Normalize by the optimal 
+ignore_fraction <- ignore_when_present$V1/optimal_free$V1 # common normalization
+assume_fraction <- assume_when_absent$V1/optimal_free$V1
+assume_when_absent <- cbind(assume_when_absent, assume_fraction = assume_fraction, normalize_optimal_free=optimal_free$V1, normalize_optimal_cost = optimal_cost$V1)
+ignore_when_present <- cbind(ignore_when_present, ignore_fraction = ignore_fraction)
+
+# Name and merge columns
+setnames(ignore_when_present, "V1", "ignore_cost")
+setnames(assume_when_absent, "V1", "assume_cost")
+error_costs <- merge(ignore_when_present, assume_when_absent, "penalty_fn")
+
+# print_npv                             # theoretically acheivable profits under these costs
+# optimal_cost$V1/optimal_free$V1       # actually realized
+
+error_costs <- cbind(error_costs, sigma_g = sigma_g, reduction = reduction)
+
+```
+
+```{r}
+v <- dt[,var(harvest), by="penalty_fn"]
+var <- v$V1
+names(var) <- v$penalty_fn
+acor <- dt[,acf(harvest, plot=F)$acf[2], by="penalty_fn"]$V1
+names(acor) <- names(var)
+out <- rbind(var=var, a=acor)
+```
+
+```{r p1, dependson="tidy", fig.width=12}
+p1 <- ggplot(subset(dt, replicate %in% names(reps)[1:5])) +
+  geom_line(aes(time, alternate), col="grey20", lwd=1) +
+  geom_line(aes(time, fishstock), col=rgb(0,0,1,.8)) + 
+  facet_grid(replicate~penalty_fn) + 
+  labs(x="time", y="stock size", title = "Stock Dynamics")
+p1
+```
+
+```{r Figure3, dependson="tidy", fig.width=12}
+p2 <- ggplot(subset(dt, replicate %in% names(reps)[1:5])) +
+  geom_line(aes(time, harvest_alt), col="grey20", lwd=1)  +
+  geom_line(aes(time, harvest), col=rgb(0,0,1,.8)) + 
+  facet_grid(replicate~penalty_fn) + 
+  labs(x="time", y="havest intensity (fish taken)", title = "Harvest Policy Dynamics")
+p2
+````
+
+```{r}
+frac_lost <- seq(0,1, length=20)
+```
+
+```{r helper_fn_1}
+fig4 <- function(fraction_lost){
+closest <- function(x, v){
+  which.min(abs(v-x))
+}
+dt_npv <- data.table(fees)
+index <- dt_npv[,closest(fraction_lost, (npv0-value)/npv0), by=variable]
+apples_index <- index$V1
+names(apples_index) = index$variable
+apples <- c2[index$V1]
+names(apples) = index$variable
+
+L2_policy <- policies$L2[[apples_index["L2"]]]$D
+L1_policy <- policies$L1[[apples_index["L1"]]]$D
+fixed_policy <- policies$fixed[[apples_index["fixed"]]]$D
+free_increase_policy <- policies$free_increase[[apples_index["free_increase"]]]$D
+free_decrease_policy <- policies$free_decrease[[apples_index["free_decrease"]]]$D
+quad_policy <- policies$quad[[apples_index["quad"]]]$D
+
+quad_profit <- profit_harvest(price = price, c0 = c0, c1 = apples["quad"]) 
+sims <- lapply(1:50, function(reps) list(
+  L1 = simulate_optim(f, pars, x_grid, h_grid, x0, 
+                      L1_policy, z_g, z_m, z_i, 
+                      opt$D, profit=profit, penalty=L1(apples["L1"])), 
+  L2 = simulate_optim(f, pars, x_grid, h_grid, x0, 
+                      L2_policy, z_g, z_m, z_i, 
+                      opt$D, profit=profit, penalty=L2(apples["L2"])),
+  fixed = simulate_optim(f, pars, x_grid, h_grid, x0, 
+                         fixed_policy, z_g, z_m, z_i, 
+                         opt$D, profit=profit, penalty=fixed(apples["fixed"]))
+#  increase = simulate_optim(f, pars, x_grid, h_grid, x0, 
+#                            free_increase_policy, z_g, z_m, z_i, 
+#                            opt$D, profit=profit, penalty= free_increase(apples["increase"])),
+#  decrease = simulate_optim(f, pars, x_grid, h_grid, x0, 
+#                            free_decrease_policy, z_g, z_m, z_i, 
+#                            opt$D, profit=profit, penalty= free_decrease(apples["decrease"])),
+#  quad = simulate_optim(f, pars, x_grid, h_grid, x0, 
+#                            quad_policy, z_g, z_m, z_i, 
+#                            opt$D, profit=quad_profit, penalty= none)
+  ))
+
+  #Make data tidy (melt), fast (data.tables), and nicely labeled.
+  dat <- melt(sims, id=names(sims[[1]][[1]]))  
+  dt <- data.table(dat)
+  setnames(dt, "L1", "reps") # names are nice
+  setnames(dt, "L2", "penalty_fn") # names are nice
+
+  dt
+}
+```
+
+```{r helper_fn_2} 
+# Helper functions to extract the summary stats in different variables
+stats_harvest <- function(dt){
+v <- dt[,var(harvest), by=c("penalty_fn", "reps")]
+acor <- dt[,acf(harvest, plot=F)$acf[2], by=c("penalty_fn", "reps")]
+df <- cbind(v, acor$V1)
+setnames(df, c("V1", "V2"), c("var", "acor")) # names are nice
+df
+}
+
+stats_fishstock <- function(dt){
+v <- dt[,var(fishstock), by=c("penalty_fn", "reps")]
+acor <- dt[,acf(fishstock, plot=F)$acf[2], by=c("penalty_fn", "reps")]
+df <- cbind(v, acor$V1)
+setnames(df, c("V1", "V2"), c("var", "acor")) # names are nice
+df
+}
+```
+
+```{r helper_fn_3}
+#' a simple function for reorganizing the data over the different "faction-lost" levels
+get_trends <- function(tmp2){
+  out <- melt(tmp2, id=c("reps", "var", "acor"))
+  colnames(out) = c("reps", "var", "acor", "nothing", "penalty", "index")
+  out <- cbind(out[c(1,2,3,5)], fraction = frac_lost[out$index])
+  out <- data.table(out)
+  Ev = out[,mean(var),by=c('penalty', 'fraction')]
+  SDv = out[,sd(var),by=c('penalty', 'fraction')]
+  Ea = out[,mean(acor),by=c('penalty', 'fraction')]
+  SDa = out[,sd(acor),by=c('penalty', 'fraction')]
+  harvest_trends <- data.table(penalty = Ev$penalty, 
+                               fraction = Ev$fraction, 
+                               Ev = Ev$V1, Ea = Ea$V1, 
+                               SDv=SDv$V1, SDa = SDa$V1)
+}
+```
+
+```{r Figure4_harvest}
+sims_at_each_apple <- lapply(frac_lost, fig4)
+harvest_stats <- lapply(sims_at_each_apple, stats_harvest)
+harvest_trends <- get_trends(harvest_stats)
+```
+
+```{r Figure4}
+Fig4a <- ggplot(harvest_trends, 
+                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
+  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
+  geom_line() + 
+  xlab("Fraction of NPV lost to costs") +
+  scale_x_continuous(limits=c(0, 0.4))
+
+Fig4b <- ggplot(harvest_trends, 
+                aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
+  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
+  geom_line() + xlab("Fraction of NPV lost to costs")+
+  scale_x_continuous(limits=c(0, 0.4)) 
+Fig4a
+Fig4b
+````
+
+```{r Figure4S}
+fishstock_stats <- lapply(sims_at_each_apple, stats_fishstock)
+fishstock_trends <- get_trends(fishstock_stats)
+
+FigS4a <- ggplot(fishstock_trends, 
+                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
+  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
+  geom_line() + xlab("Fraction of NPV lost to costs")+
+  scale_x_continuous(limits=c(0, 0.4))
+
+FigS4b <- ggplot(fishstock_trends, 
+                aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
+  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
+  geom_line() + xlab("Fraction of NPV lost to costs") +
+  scale_x_continuous(limits=c(0, 0.4)) 
+FigS4a
+FigS4b
+```
+
+<!-- ENDCODE -->
 

### 2014-05-23 manuscripts/components/knit.R

@@ -2,6 +2,13 @@
 args <- commandArgs(TRUE)
 file <- args[1]
 
+if(!is.na(args[1])){
+  file <- args[1]
+} else if(!is.character(file)) {
+  file <- 'manuscript.Rmd'
+}
+
+
 ## FIXME add second argument to handle figure types
 
 ## Set the paths for cache and figure
@@ -11,7 +18,7 @@ basename <- gsub(".Rmd", "", file) # knitr:::knit_concord$get('infile'))
 opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
                cache.path = paste("components/cache/", basename, "/", sep=""))
 opts_chunk$set(cache = 2)
-opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, comment = NA, verbose = TRUE)
+opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, comment = NA, verbose = TRUE, echo=FALSE)
 
 # PDF-based figures
 opts_chunk$set(dev='pdf')

### 2014-05-26 manuscripts/manuscript.Rmd
update references and figures

@@
     affiliation: melbourne
+  - name: James Sanchirico
+    affiliation: UCD
   - name: Jacob LaRiviera
     affiliation: UTK
-  - name: James Sanchirico
-    affiliation: UCD
   - name: Alan Hastings
@@
           the environment very tightly will only sometimes be worthwhile. We use a
-          classic fisheries management question – how to manage a stochastically
+          classic fisheries management question -- how to manage a stochastically
           varying population using annually varying quotas in order to maximize
@@
 library("pander")
+library("cboettigR")
 theme_set(theme_bw())
@@
 fees <- melt(fees, id="c2")
+fees <- subset(fees, variable %in% c("L1", "L2", "fixed"))
 
-fees <- subset(fees, variable %in% c("L1", "L2", "fixed"))
-ggplot(fees, aes(c2, value, col=variable)) + geom_point() + geom_line()
+#ggplot(fees, aes(c2, value, col=variable)) + geom_point() + geom_line()
 ````
@@
 ```{r apples_plot, dependson="quadcosts"}
-ggplot(fees, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
+#ggplot(fees, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
 ````
@@
 
-```{r p1, dependson="tidy", fig.width=12}
-p1 <- ggplot(subset(dt, replicate %in% names(reps)[1:5])) +
-  geom_line(aes(time, alternate), col="grey20", lwd=1) +
-  geom_line(aes(time, fishstock), col=rgb(0,0,1,.8)) + 
-  facet_grid(replicate~penalty_fn) + 
-  labs(x="time", y="stock size", title = "Stock Dynamics")
-p1
-```
-
-```{r Figure3, dependson="tidy", fig.width=12}
-p2 <- ggplot(subset(dt, replicate %in% names(reps)[1:5])) +
-  geom_line(aes(time, harvest_alt), col="grey20", lwd=1)  +
-  geom_line(aes(time, harvest), col=rgb(0,0,1,.8)) + 
-  facet_grid(replicate~penalty_fn) + 
-  labs(x="time", y="havest intensity (fish taken)", title = "Harvest Policy Dynamics")
-p2
-````
-
 ```{r}
@@
 
-```{r Figure4}
-Fig4a <- ggplot(harvest_trends, 
-                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
-  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
-  geom_line() + 
-  xlab("Fraction of NPV lost to costs") +
-  scale_x_continuous(limits=c(0, 0.4))
-
-Fig4b <- ggplot(harvest_trends, 
-                aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
-  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
-  geom_line() + xlab("Fraction of NPV lost to costs")+
-  scale_x_continuous(limits=c(0, 0.4)) 
-Fig4a
-Fig4b
-````
-
-```{r Figure4S}
+```{r fishstock_trends}
 fishstock_stats <- lapply(sims_at_each_apple, stats_fishstock)
 fishstock_trends <- get_trends(fishstock_stats)
-
-FigS4a <- ggplot(fishstock_trends, 
-                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
-  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
-  geom_line() + xlab("Fraction of NPV lost to costs")+
-  scale_x_continuous(limits=c(0, 0.4))
-
-FigS4b <- ggplot(fishstock_trends, 
-                aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
-  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
-  geom_line() + xlab("Fraction of NPV lost to costs") +
-  scale_x_continuous(limits=c(0, 0.4)) 
-FigS4a
-FigS4b
 ```
@@
 management recommendations [@Biais1995; @Armsworth2003;
-@Patterson2007; @PattersonResimont2007; @Sanchirico2008].
+@Patterson2007a; @Patterson2007b; @Sanchirico2008].
 In other words, whatever gains are available from fine-tuning a
@@
 the observed quota stability. More generally, reviews by @Biais1995 and
-@Patterson2007 document many cases where changes in catch
+@Patterson2007a document many cases where changes in catch
 quotas that a management agency set were more modest than changes that
@@
 chosen to maximize the net present value of a fishery. Our formulation
-and solution method largely follow Reed’s classic treatment on this
+and solution method largely follow Reed's classic treatment on this
 question, a treatment repeated widely in bioeconomic textbooks. With
@@
 Empirics suggest not always as responsive as Reed solution. Explore
-conditions under which that makes sense. Idea is that regulator’s
-objective sometimes may not be ‘raw’ NPV, but rather NPV with some
+conditions under which that makes sense. Idea is that regulator's
+objective sometimes may not be 'raw' NPV, but rather NPV with some
 penalties on fast changes. Possible reasons: pure administrative
-transaction cost of changing policies (reaching agreement), fishermens’
-preferences for less variable quotas, processing plants’ preferences for
+transaction cost of changing policies (reaching agreement), fishermens'
+preferences for less variable quotas, processing plants' preferences for
 less variable quotas especially if tied into contracts for canning and
@@
 situation where there are no costs associated with policy adjustment and
-the managers’ objective is
+the managers' objective is
 
@@
 equation ([eq:state_equation]) define a stochastic dynamic programming
-problem that we solve using backwards recursion via Bellman’s equation.
+problem that we solve using backwards recursion via Bellman's equation.
 We denote the resulting state-dependent, optimal control as $h_0^{\ast}$.
@@
 
-<!-- ![**Expected net present value by functional form of penalty.** Horizontal axis shows the coefficient $c_i$ governing the magnitude of the policy cost, while vertical axis shows fraction of the maximum expected net present value dissipated by the policy cost.
-The horizontal line indicates a value of the stock that is 80\% of the maximum expected value in the absence of policy adjustment costs, $NPV_0({\bf h_0^*})$.
-Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.
-](figure/Figure_1.pdf)
+```{r Figure_1, fig.cap="Expected net present value by functional form of penalty.
+Horizontal axis shows the coefficient $c_i$ governing the magnitude of the policy cost, while vertical axis shows fraction of the maximum expected net present value dissipated by the policy cost.
+The horizontal line indicates a value of the stock that is 80% of the maximum expected value in the absence of policy adjustment costs, $NPV_0({\\bf h_0^*})$.
+Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.", dependson="quadcosts", fig.width=5, fig.height=3}
+ggplot(fees, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
 
--->
+```
 
@@
 Figure needs tidying up to be submission ready.
-Resize it – can be smaller, no color needed, bigger TickLabels, no background shading or grid.
+Resize it - can be smaller, no color needed, bigger TickLabels, no background shading or grid.
 It also need the relevant horizontal and vertical lines marking to show the calibration.
-Choose a % reduction that corresponds to that you are choosing for what is currently labeled Figs 2&3 (sample paths) and Fig 8 – histograms.
-We should then adjust the text to talk to what is shown in the figure consistently – e.g.
+Choose a % reduction that corresponds to that you are choosing for what is currently labeled Figs 2&3 (sample paths) and Fig 8 - histograms.
+We should then adjust the text to talk to what is shown in the figure consistently - e.g.
 is is 25% loss or 75% of the value, etc.
@@
 <!-- 
-For the figure in the main text, I would make a single figure with six plates – the three different adjustment costs are the columns.
+For the figure in the main text, I would make a single figure with six plates - the three different adjustment costs are the columns.
 One row is the effect on optimal harvests and one the effect on optimal stock sizes.
@@
 
-<!-- At what time relative to the dynamics in equation 1, and I would be setting up a comment why they don’t see something similar to the constant escapement policy – this is just a census time issue, but I would say it explicitly given the attention we shine on the REED result upfront.
+<!-- At what time relative to the dynamics in equation 1, and I would be setting up a comment why they don't see something similar to the constant escapement policy -- this is just a census time issue, but I would say it explicitly given the attention we shine on the REED result upfront.
 -->
@@
 incrementally each year. Finally, the optimal policy for the third,
-‘fixed fee’ formulation ($\Pi_3$) only makes large adjustments, as one
+'fixed fee' formulation ($\Pi_3$) only makes large adjustments, as one
 might expect, because the magnitude of the adjustment made is not
@@
 
-<!--
-![Individual realizations of optimal harvesting strategy under the different functional forms of adjustment costs.](figure/Figure_2)
+```{r Figure_2, dependson="tidy", fig.cap="Individual realizations of optimal harvesting strategy under the different functional forms of adjustment costs.", fig.height=3, fig.width=8}
+ggplot(subset(dt, replicate %in% names(reps)[1:5])) +
+  geom_line(aes(time, alternate), col="grey20", lwd=1) +
+  geom_line(aes(time, fishstock), col=rgb(0,0,1,.8)) + 
+  facet_grid(replicate~penalty_fn) + 
+  labs(x="time", y="stock size", title = "Stock Dynamics") +
+  theme_bw()
 
-![Individual realizations of optimal stock size strategy under the different functional forms of adjustment costs](figure/Figure_3)
--->
+```
+
+```{r Figure_3, dependson="tidy", fig.cap="Individual realizations of optimal stock size strategy under the different functional forms of adjustment costs.", fig.height=3, fig.width=8}
+ggplot(subset(dt, replicate %in% names(reps)[1:5])) +
+  geom_line(aes(time, harvest_alt), col="grey20", lwd=1)  +
+  geom_line(aes(time, harvest), col=rgb(0,0,1,.8)) + 
+  facet_grid(replicate~penalty_fn) + 
+  labs(x="time", y="havest intensity (fish taken)", title = "Harvest Policy Dynamics") + 
+  theme_bw()
+
+```
 
@@
 <!--
-Assuming we aren’t showing cross-correlations, I think we can probably fit these into a single four subplot figure.
+Assuming we aren't showing cross-correlations, I think we can probably fit these into a single four subplot figure.
 Cross-correlations would be a little harder but just using 5 subplots from what could have been a 6 subplot figure would also work, because a journal could just put the caption into the empty space.
@@
 
-<!--
-![Figure 4a: Variance of optimal harvest rates through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.](figure/Figure_4a.pdf)
+```{r Figure_4, fig.cap="(a) Variance of optimal harvest rates through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.
+(b) Autocorrelation of optimal harvest rates through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=3, fig.width=8}
+Fig4a <- ggplot(harvest_trends, 
+                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
+  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
+  geom_line() + 
+  xlab("Fraction of NPV lost to costs") +
+  scale_x_continuous(limits=c(0, 0.4))
 
-![Figure 4b: Autocorrelation of optimal harvest rates through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs](figure/Figure_4b.pdf)
+Fig4b <- ggplot(harvest_trends, 
+                aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
+  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
+  geom_line() + xlab("Fraction of NPV lost to costs")+
+  scale_x_continuous(limits=c(0, 0.4))
 
-![Figure 5a: Variance of optimal stock sizes through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.](figure/Figure_5a.pdf)
+multiplot(Fig4a, Fig4b, cols=2)
+```
 
-![Figure 5b: Autocorrelation of optimal stock sizes through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.](figure/Figure_5b.pdf)
--->
+```{r Figure_5, fig.cap = "(a) Variance of optimal stock sizes through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.
+(b) Autocorrelation of optimal stock sizes through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=3, fig.width=8}
+Fig5a <- ggplot(fishstock_trends, 
+                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
+  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
+  geom_line() + xlab("Fraction of NPV lost to costs")+
+  scale_x_continuous(limits=c(0, 0.4))
+
+Fig5b <- ggplot(fishstock_trends, 
+                aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
+  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
+  geom_line() + xlab("Fraction of NPV lost to costs") +
+  scale_x_continuous(limits=c(0, 0.4))
+
+multiplot(Fig5a, Fig5b, cols=2)
+
+```
 
@@
 
--   Comparison between the different functional forms – smoothing (L2)
+-   Comparison between the different functional forms -- smoothing (L2)
     non-smoothing (L1), and de-stablizing (fixed).

### 2014-05-26 manuscripts/components/restore-cache.R

@@ -1,6 +1,6 @@
 #!/usr/bin/R
 setwd("components")
-archive <- "template-manuscript-cache.tar.gz"
+archive <- "pdg_controlcache.tar.gz"
 
 
 library("utils")

### 2014-05-26 manuscripts/manuscript.Rmd
start to tune plotting

@@
 library("cboettigR")
-theme_set(theme_bw())
+library("ggthemes")
+theme_set(theme_tufte())
 ```
@@
 the policy process can often be much more sluggish
-to respond to variations in ecosystem dynamics [@Walters1978; @Armsworth2012]. 
+to respond to variations in ecosystem dynamics [@Walters1978; @Armsworth2010]. 
 Moreover, stakeholders impacted by ecosystem management
@@
 Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.", dependson="quadcosts", fig.width=5, fig.height=3}
-ggplot(fees, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
+ggplot(fees, aes(c2, (npv0-value)/npv0, lty=variable)) + geom_line() + theme_tufte()
 
@@
   facet_grid(replicate~penalty_fn) + 
-  labs(x="time", y="stock size", title = "Stock Dynamics") +
-  theme_bw()
+  labs(x="time", y="stock size", title = "Stock Dynamics")  + theme_tufte()
 
@@
   facet_grid(replicate~penalty_fn) + 
-  labs(x="time", y="havest intensity (fish taken)", title = "Harvest Policy Dynamics") + 
-  theme_bw()
+  labs(x="time", y="havest intensity (fish taken)", title = "Harvest Policy Dynamics")  + theme_tufte()
 
@@
   xlab("Fraction of NPV lost to costs") +
-  scale_x_continuous(limits=c(0, 0.4))
+  scale_x_continuous(limits=c(0, 0.4)) + theme_tufte()
 
@@
   geom_line() + xlab("Fraction of NPV lost to costs")+
-  scale_x_continuous(limits=c(0, 0.4))
+  scale_x_continuous(limits=c(0, 0.4)) + theme_tufte()
 
@@
   geom_line() + xlab("Fraction of NPV lost to costs")+
-  scale_x_continuous(limits=c(0, 0.4))
+  scale_x_continuous(limits=c(0, 0.4))  + theme_tufte()
 
@@
   geom_line() + xlab("Fraction of NPV lost to costs") +
-  scale_x_continuous(limits=c(0, 0.4))
+  scale_x_continuous(limits=c(0, 0.4))  + theme_tufte()
 

### 2014-05-27 May.Rmd
create gh-pages branch

--- 2012-06-21 inst/examples/May.Rmd
@@
 
-``` {r  find_dp_opt }
+``` {r  find_dp_opt, dependson="SDP_Mat"}
 opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=OptTime, xT=xT, 
@@
 p1
+````
+
+``` {r profits, fig.cap="the distribution of profits by scenario", dependson="tidy"}
+profits <-dt[ , sum(profit), by="reps"] 
+ggplot(profits) + geom_histogram(aes(V1)) 
 ````

### 2014-05-27 bh_lognormal.Rmd
create gh-pages branch

--- 2012-06-30 inst/examples/bh_lognormal.Rmd
@@
-`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="bh_lognormal_c0/", verbose=TRUE or`
+`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="bh_lognormal_c01", verbose=TRUE or`
 

### 2014-05-27 bh_uniform.Rmd
create gh-pages branch

--- 2012-06-30 inst/examples/bh_uniform.Rmd
@@
-`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="bh_uniform_c0/", verbose=TRUE or`
+`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="bh_uniform_c01/", verbose=TRUE or`
 

### 2014-05-27 logistic_lognormal.Rmd
create gh-pages branch

--- 2012-06-30 inst/examples/logistic_lognormal.Rmd
@@
-`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="logistic_lognormal_c0/", verbose=TRUE or`
+`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="logistic_lognormal_c01/", verbose=TRUE or`
 

### 2014-05-27 logistic_uniform.Rmd
create gh-pages branch

--- 2012-07-31 inst/examples/logistic_uniform.Rmd
@@
 policyfn <- list(det=det, low=low, g=g, m=m, i=i, gm=gm, gi=gi, mi=mi, gmi=gmi)
-noise <- list( det  = c(0,0,0),        low = c(0.1, .1, .1),  growth = c(lvl, 0, 0),
+noise <- list( det  = c(0.01,0,0),        low = c(0.1, .1, .1),  growth = c(lvl, 0, 0),
                measure  = c(0, lvl, 0),implement = c(0,0,lvl),growth_measure = c(lvl, lvl, 0), 

### 2014-05-27 policycosts/costfree.Rmd
create gh-pages branch

--- 2012-12-04 inst/examples/policycosts/costfree.Rmd
@@
 
-```{r Figure4}
+# Figure 4
+
+```{r}
 frac_lost <- seq(0,1, length=20)
-tmp <- lapply(frac_lost, fig4, ls())
-out <- melt(tmp, id=c("reps", "var", "acor"))
+```
+
+```{r helper_fn_1}
+fig4 <- function(fraction_lost){
+closest <- function(x, v){
+  which.min(abs(v-x))
+}
+dt_npv <- data.table(fees)
+index <- dt_npv[,closest(fraction_lost, (npv0-value)/npv0), by=variable]
+apples_index <- index$V1
+names(apples_index) = index$variable
+apples <- c2[index$V1]
+names(apples) = index$variable
+
+L2_policy <- policies$L2[[apples_index["L2"]]]$D
+L1_policy <- policies$L1[[apples_index["L1"]]]$D
+fixed_policy <- policies$fixed[[apples_index["fixed"]]]$D
+free_increase_policy <- policies$free_increase[[apples_index["free_increase"]]]$D
+free_decrease_policy <- policies$free_decrease[[apples_index["free_decrease"]]]$D
+quad_policy <- policies$quad[[apples_index["quad"]]]$D
+
+quad_profit <- profit_harvest(price = price, c0 = c0, c1 = apples["quad"]) 
+sims <- lapply(1:50, function(reps) list(
+  L1 = simulate_optim(f, pars, x_grid, h_grid, x0, 
+                      L1_policy, z_g, z_m, z_i, 
+                      opt$D, profit=profit, penalty=L1(apples["L1"])), 
+  L2 = simulate_optim(f, pars, x_grid, h_grid, x0, 
+                      L2_policy, z_g, z_m, z_i, 
+                      opt$D, profit=profit, penalty=L2(apples["L2"])),
+  fixed = simulate_optim(f, pars, x_grid, h_grid, x0, 
+                         fixed_policy, z_g, z_m, z_i, 
+                         opt$D, profit=profit, penalty=fixed(apples["fixed"])),
+  increase = simulate_optim(f, pars, x_grid, h_grid, x0, 
+                            free_increase_policy, z_g, z_m, z_i, 
+                            opt$D, profit=profit, penalty= free_increase(apples["increase"])),
+  decrease = simulate_optim(f, pars, x_grid, h_grid, x0, 
+                            free_decrease_policy, z_g, z_m, z_i, 
+                            opt$D, profit=profit, penalty= free_decrease(apples["decrease"])),
+  quad = simulate_optim(f, pars, x_grid, h_grid, x0, 
+                            quad_policy, z_g, z_m, z_i, 
+                            opt$D, profit=quad_profit, penalty= none)
+  ))
+
+  #Make data tidy (melt), fast (data.tables), and nicely labeled.
+  dat <- melt(sims, id=names(sims[[1]][[1]]))  
+  dt <- data.table(dat)
+  setnames(dt, "L1", "reps") # names are nice
+  setnames(dt, "L2", "penalty_fn") # names are nice
+
+  dt
+}
+```
+
+```{r helper_fn_2} 
+# Helper functions to extract the summary stats in different variables
+stats_harvest <- function(dt){
+v <- dt[,var(harvest), by=c("penalty_fn", "reps")]
+acor <- dt[,acf(harvest, plot=F)$acf[2], by=c("penalty_fn", "reps")]
+df <- cbind(v, acor$V1)
+setnames(df, c("V1", "V2"), c("var", "acor")) # names are nice
+df
+}
+
+stats_fishstock <- function(dt){
+v <- dt[,var(fishstock), by=c("penalty_fn", "reps")]
+acor <- dt[,acf(fishstock, plot=F)$acf[2], by=c("penalty_fn", "reps")]
+df <- cbind(v, acor$V1)
+setnames(df, c("V1", "V2"), c("var", "acor")) # names are nice
+df
+}
+```
+
+```{r helper_fn_3}
+#' a simple function for reorganizing the data over the different "faction-lost" levels
+get_trends <- function(tmp2){
+  out <- melt(tmp2, id=c("reps", "var", "acor"))
   colnames(out) = c("reps", "var", "acor", "nothing", "penalty", "index")
@@
   out <- data.table(out)
-
   Ev = out[,mean(var),by=c('penalty', 'fraction')]
@@
   SDa = out[,sd(acor),by=c('penalty', 'fraction')]
+  harvest_trends <- data.table(penalty = Ev$penalty, 
+                               fraction = Ev$fraction, 
+                               Ev = Ev$V1, Ea = Ea$V1, 
+                               SDv=SDv$V1, SDa = SDa$V1)
+}
+```
 
-tmp2 <- data.table(penalty = Ev$penalty, fraction = Ev$fraction, Ev = Ev$V1, Ea = Ea$V1, SDv=SDv$V1, SDa = SDa$V1)
+```{r Figure4_harvest}
+sims_at_each_apple <- lapply(frac_lost, fig4)
+harvest_stats <- lapply(sims_at_each_apple, stats_harvest)
+harvest_trends <- get_trends(harvest_stats)
+```
 
-Fig4a <- ggplot(tmp2, aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
+```{r Figure4}
+Fig4a <- ggplot(harvest_trends, 
+                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
   geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
@@
 
-Fig4b <- ggplot(tmp2, aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
+Fig4b <- ggplot(harvest_trends, 
+                aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
   geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
@@
 ````
+
+```{r Figure4S}
+fishstock_stats <- lapply(sims_at_each_apple, stats_fishstock)
+fishstock_trends <- get_trends(fishstock_stats)
+
+FigS4a <- ggplot(fishstock_trends, 
+                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
+  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
+  geom_line() + xlab("Fraction of NPV lost to costs")
+
+FigS4b <- ggplot(fishstock_trends, 
+                aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
+  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
+  geom_line() + xlab("Fraction of NPV lost to costs")
+FigS4a
+FigS4b
+```

### 2014-05-27 policycosts/errors_table.Rmd
create gh-pages branch

--- 2013-11-08 inst/examples/policycosts/errors_table.Rmd
@@
 ``` {r defs}
-compute_error_table <- function(r = 2, sigma = 0.2){
+compute_error_table <- function(r, sigma){
 reduction_range = c(.1, .2, .3)
@@
 
-seed <- 123                 # Random seed (replicable results)
 delta <- 0.05               # economic discounting rate
@@
 
-sigma_g <- 0.3
 SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
@@
                      profit, delta, reward=reward)
-
-tmp <- lapply(1:100, function(i){ 
-  set.seed(i)
-  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i)
-  })
-tmp <- melt(tmp, id = names(tmp[[1]]))
-sum(tmp$profit)
 
@@
 setnames(dt, "L1", "penalty_fn") # names are nice
+
+dt$profit <- dt$profit_fishing/(1+delta)^dt$time
+dt$profit_fishing_alt <- dt$profit_fishing_alt/(1+delta)^dt$time
+dt$policy_cost <- dt$policy_cost/(1+delta)^dt$time
+dt$policy_cost_alt <- dt$policy_cost_alt/(1+delta)^dt$time
 

### 2014-05-27 policycosts/writeup.Rmd
create gh-pages branch

--- 2013-11-08 inst/examples/policycosts/test.Rmd
@@
 ```{r cache-options, include=FALSE}
-opts_chunk$set(cache=TRUE, cache.path="test/")
+opts_chunk$set(cache=TRUE, cache.path="writeup/")
 opts_knit$set(upload.fun=socialR::flickr.url)
@@
 gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
-sigma_g <- 0.5            # Noise in population growth
+sigma_g <- 0.2              # Noise in population growth
 reward <- 0                 # bonus for satisfying the boundary condition

### 2014-05-27 resilience_assessment.Rmd
create gh-pages branch

--- 2012-06-21 inst/examples/criticaltransition.Rmd
@@
-`ro cache=FALSE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE or`
+`ro tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache=TRUE, cache.path="resilience_assessment/" or`
 
 ``` {r  echo=FALSE, cache=FALSE}
-opts_knit$set(upload.fun = socialR::flickr.url)
-options(device = function(width = 5, height = 5) {
-    pdf(NULL, width = width, height = height)
-})
+#opts_knit$set(upload.fun = socialR::flickr.url)
+#options(device = function(width = 5, height = 5) {
+#    pdf(NULL, width = width, height = height)
+#})
 knitcitations::cleanbib()
@@
 
+    # Track the location of the stable and unstable points?
+
     # Assess stock, with potential measurement error
@@
 
+### Warning signal assessment
+
+1. Simulate timeseries before management begins, use this data to compute warning signals.  
+2. Calculate the ROC curve
+3. Calculate the expected profits remaining under the hypothesis that the system is not going to collapse. "D"
+4. Calculate the expected profits under the assumption that the system collapses (in the next timestep?)  "C" == 0
+5. Calculate the profits expected under a response to the signal.  (Say, 50% reduction in harvest). "A", "B"
+
+Ideal response with complete information: determine the optimal policy under temporally changing f.
+
 This plot summarizes the stock dynamics by visualizing the replicates.

### 2014-05-27 unmanaged_warning.Rmd
create gh-pages branch

--- 2012-08-24 inst/examples/unmanaged_warning.Rmd
@@
 
+Compute summary stat versions
+
 ``` {r summarystat_roc} 
@@
   Bsim <- simulate(B, reps)
-  sim <- melt(Asim, id = "time")
+  Asim <- melt(Asim, id = "time")
   Bsim <- melt(Bsim, id = "time")
@@
 
-tau_dist <- summarystat_roc(A, B, list(var=window_var, acor=window_autocorr))
-head(tau_dist)
+dat <- summarystat_roc(A,B, list(var=window_var, acor=window_autocorr))
+ggplot(dat) + geom_density(aes(value, fill=variable)) + facet_wrap(~L1)
 ```

### 2014-05-27 voi_May.Rmd
create gh-pages branch

--- 2012-06-25 inst/examples/voi_May.Rmd
@@
 policyfn <- list(det=det, low=low, g=g, m=m, i=i, gm=gm, gi=gi, mi=mi, gmi=gmi)
-noise <- list( det  = c(0,0,0),        low = c(0.1, .1, .1),  growth = c(lvl, 0, 0),
-               measure  = c(0, lvl, 0),implement = c(0,0,lvl),growth_measure = c(lvl, lvl, 0), 
-               growth_implement = c(lvl, 0, lvl),  measure_implement = c(0, lvl, lvl), all = c(lvl, lvl, lvl)) 
+noise <- list(det  = c(0,0,0), 
+							low = c(0.1, .1, .1),  
+							grow = c(lvl, 0, 0),
+              meas  = c(0, lvl, 0), 
+							imp = c(0,0,lvl), 
+							gro_meas = c(lvl, lvl, 0),  
+							gro_imp = c(lvl, 0, lvl),  
+							meas_imp = c(0, lvl, lvl), 
+							all = c(lvl, lvl, lvl))
+````
+
+``` {r loopoverall}
  allcases <- lapply(policyfn, function(policyfn_i){
   lapply(noise, function(noise_i){
-    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3])
+    try(simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3]))
   })

### 2014-05-27 R/ForwardSimulate.R

@@ -1,64 +1,0 @@
-## Note: See policy_costs.R for another simulation algorithm 
-
-
-#' Forward simulate given the optimal havesting policy, D
-#' @param f the growth function of the escapement population (x-h)
-#'   should be a function of f(y, p), with parameters p
-#' @param p the parameters of the growth function
-#' @param x_grid the discrete values allowed for the population size, x
-#' @param h_grid the discrete values of harvest levels to optimize over
-#' @param Xo initial stock size
-#' @param D the optimal solution indices on h_grid, 
-#'  given for each possible state at each timestep
-#' @param z_g a function which returns a random multiple for population growth 
-#' @param z_m a function which returns the measurement uncertainty in the 
-#'  assessment of stock size
-#' @param z_i a function which returns a random number from a distribution 
-#' for the implementation uncertainty in quotas 
-#' @param profit function, if known
-#' @return a data frame with the time, fishstock, harvested amount,
-#'  and what the escapement ("unharvested"). 
-#' @export
-ForwardSimulate <- function(f, pars, x_grid, h_grid, x0, D, z_g,
-                            z_m = function(x) 1, z_i = function(x) 1, 
-                            profit = NULL, OptTime = NULL){
-  # initialize variables with initial conditions
-  if(is.null(OptTime)) 
-    OptTime <- dim(D)[2]    # Stopping time
-  x_h <- numeric(OptTime) # population dynamics with harvest
-  h <- numeric(OptTime)   # optimal havest level
-  x_h[1] <- x0            # initial values
-  
-  s <- x_h # also track escapement
-  x <- x_h # What would happen with no havest
-  p <- numeric(OptTime)
- 
-  ## If given a stationary policy, replicate it throughout.  
-  if(!is.matrix(D))
-    D <- sapply(1:OptTime, function(i) D)
-    
-  ## Simulate through time ##
-  for(t in 1:(OptTime-1)){
-    # Assess stock, with potential measurement error
-    m_t <- x_h[t] * z_m()
-    # Current state (is closest to which grid posititon) 
-    St <- which.min(abs(x_grid - m_t)) 
-    q_t <- h_grid[D[St, (t + 1) ]] 
-    # Implement harvest/(effort) based on quota with noise 
-    h[t] <- q_t * z_i()
-    # Noise in growth 
-    z <- z_g() 
-    # population grows
[…]

### 2014-05-27 R/SDP_by_simulation.R

@@ -1,105 +1,0 @@
-
-#' Determine the transtion matrix using stochastic simulation
-#' @param f the growth function of the escapement population (x-h)
-#'   should be a function of f(t, y, p), with parameters p
-#' @param p the parameters of the growth function
-#' @param x_grid the discrete values allowed for the population size, x
-#' @param h_grid the discrete values of harvest levels to optimize over
-#' @param z_g a function determing the probability distrubtion for the 
-#'  stochastic population growth process (draws a random variable z_g)
-#' @param z_m a function determining the porbability distribution for
-#'  measurement uncertainty in the assessment of stock size (random variable)
-#' @param z_i function for implementation uncertainty in quotas 
-#' @return the transition matrix at each value of h in the grid.  
-#' @import snowfall
-#' @import ggplot2
-#' @import Hmisc
-#' @export
-SDP_by_simulation <- function(f, p, x_grid, h_grid, z_g, z_m, z_i, reps = 999){
-  require(snowfall) # support parallelization of this
-  sfExportAll()
-  sfLibrary(ggplot2) # for the bin function 
-  
-  bw <- x_grid[2] - x_grid[1]
-  lower <-x_grid[1]
-  upper <- x_grid[length(x_grid)] + bw
-  
-  SDP_Mat <- sfLapply(h_grid, function(h){ 
-    mat <- sapply(x_grid, function(x){
-      x_t1 <- replicate(reps, z_g() * z_m() * f(x / z_m(), z_i() * h, p)) 
-      a <- mybin( x_t1, binwidth=bw, range=c(lower, upper))$count
-      a / sum(a) 
-    })
-    t(mat)
-  })
-  SDP_Mat
-}
-
-
-
-
-
-# Bin data from old version of ggplot2
-# This function powers \code{\link{stat_bin}}R
-#
-# @keyword internal
-mybin <- function(x, weight=NULL, binwidth=NULL, origin=NULL, breaks=NULL, range=NULL, width=0.9, drop = FALSE) {
-  
-  if (is.null(weight))  weight <- rep(1, length(x))
-  weight[is.na(weight)] <- 0
-  
-  if (is.null(range))    range <- range(x, na.rm = TRUE, finite=TRUE)
-  if (is.null(binwidth)) binwidth <- diff(range) / 30
-  
-  if (is.integer(x)) {
-    bins <- x
-    x <- sort(unique(bins))
-    width <- width    
[…]

### 2014-05-27 R/active_adaptive_simulate.R

@@ -1,162 +1,0 @@
-#' @export
-setmodel <- function(f, pars){
-  function(x_t1, x_t0){
-    mu = f(x_t0, 0, pars)
-    (mu <= 0) * (x_t1 == 0) +
-    (mu > 0) * dlnorm(x_t1, log(mu), sigma_g)
-  }
-}
-
-# internal function
-bin <- function(v, v_grid){
-  v_grid[which.min(abs(v_grid - v))]
-#  i = 1
-#  n = length(v_grid)
-#  while(v_grid[i] < v & i < n)
-#    i = i+1
-#  v_grid[i]  
-}
-
-#' @export
-update_belief = function(f1,f2){
-  function(x_t0, p_t0, x_t1, p_grid){
-    y1 = p_t0 * f1(x_t1, x_t0)
-    y2 = (1-p_t0) * f2(x_t1, x_t0)
-    P1 = y1 / (y1 + y2)
-    if(is.na(P1) || x_t0 == 0)
-      P1 = p_t0
-    else{
-      P1 = bin(P1, p_grid)
-   }
-   P1
-  }
-}
-
-
-# internal function
-transition = function(p_grid, f1, f2){
-  function(x_t0, p_t0, x_t1, p_t1){
-    np = length(p_grid)
-    y1 = p_t0 * f1(x_t1, x_t0)
-    y2 = (1-p_t0) * f2(x_t1, x_t0)
-    P1 = y1 / (y1 + y2)
-    if(is.na(P1) || x_t0 == 0)
-      P1 = p_t0
-    else
-      P1 = bin(P1, p_grid)
-   (y1+y2) * ( p_t1 == P1)
-  }
-}
-
-#' @export
-model_uncertainty <- function(f1, f2, x_grid, p_grid, h_grid){
-  f <- transition(p_grid, f1, f2)
-  lapply(h_grid, function(h){
-    x_minus_h <- (x_grid-h) * as.integer( (x_grid-h)>0 )
-    d = expand.grid(x_t0 = x_minus_h, p_t0 = p_grid, x_t1 = x_grid, p_t1 = p_grid)
-    M = matrix(mapply(f, d$x_t0, d$p_t0, d$x_t1, d$p_t1), nrow = length(p_grid) * length(x_grid) )
-    for(i in 1:dim(M)[1]) # normalize
-      M[i,] = M[i,]/sum(M[i,])
-    M
-  })
-}
-
-
-#' @export
[…]

### 2014-05-27 R/determine_SDP_matrix.R

@@ -1,59 +1,0 @@
-# file determine_SDP_matrix.R 
-# author Carl Boettiger <cboettig@gmail.com>
-# date 2011-11-07
-# licence BSD
-# SDP solution adapted from SDP.m by Michael Bode
-# 
-# Contains three different functions for determining the 
-# Stochastic Transition Matrix used in the Dynamic Programming solution
-#
-
-
-#########################################################################
-# A function to generate the transition matrix used for the SDP routine #
-#########################################################################
-
-#' Determine the Stochastic Dynamic Programming matrix.
-#' @param f the growth function of the escapement population (x-h)
-#'   should be a function of f(t, y, p), with parameters p
-#' @param p the parameters of the growth function
-#' @param x_grid the discrete values allowed for the population size, x
-#' @param h_grid the discrete values of harvest levels to optimize over
-#' @param sigma_g the variance of the population growth process
-#' @param pdfn the probability density function, taking the proportional
-#' chance of a transition to that state, f(x), and the parameter sigma_g
-#' By default it will use the log normal density.  
-#' @return the transition matrix at each value of h in the grid. 
-#' @details this analytical approach doesn't reliably support other 
-#'  sources of variation.  The quality of the analytic approximations 
-#'  (lognormal) can be tested. 
-#' @export
-determine_SDP_matrix <- function(f, p, x_grid, h_grid, sigma_g,
-                                 pdfn=function(P, s) dlnorm(P, 0, s)){
-  gridsize <- length(x_grid)
-  SDP_Mat <- lapply(h_grid, function(h){
-    SDP_matrix <- matrix(0, nrow=gridsize, ncol=gridsize)
-    # Cycle over x values
-    for(i in 1:gridsize){ ## VECTORIZE ME
-      ## Calculate the expected transition  
-      x1 <- x_grid[i]
-      x2_expected <- f(x1, h, p)
-      ## If expected 0, go to 0 with probabilty 1
-      if( x2_expected == 0) 
-        SDP_matrix[i,1] <- 1  
-      else {
-        # relative probability of a transition to that state
-        ProportionalChance <- x_grid / x2_expected
-        Prob <- pdfn(ProportionalChance, sigma_g)
-        # Store normalized probabilities in row
-        SDP_matrix[i,] <- Prob/sum(Prob)
-      }
-    }
-    SDP_matrix
-  })
-  SDP_Mat
-}
-
-
-
-

### 2014-05-27 R/find_dp_optim.R

@@ -1,65 +1,0 @@
-########################################################################
-# A function to identify the dynamic optimum using backward iteration  #
-#
-#' Identify the dynamic optimum using backward iteration (dynamic programming)
-#' @param SDP_Mat the stochastic transition matrix at each h value
-#' @param x_grid the discrete values allowed for the population size, x
-#' @param h_grid the discrete values of harvest levels to optimize over
-#' @param OptTime the stopping time 
-#' @param xT the boundary condition population size at OptTime
-#' @param c the cost/profit function, a function of harvested level
-#' @param delta the exponential discounting rate
-#' @param reward  the profit for finishing with >= Xt fish at the end 
-#' (i.e. enforces the boundary condition)
-#' @return list containing the matrices D and V.  D is an x_grid by OptTime
-#'  matrix with the indices of h_grid giving the optimal h at each value x
-#'  as the columns, with a column for each time.  
-#'  V is a matrix of x_grid by x_grid, which is used to store the value 
-#'  function at each point along the grid at each point in time.  
-#'  The returned V gives the value matrix at the first (last) time. 
-#' @export
-find_dp_optim <- function(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, 
-                          delta, reward=0){
-
- 
-  ## Initialize space for the matrices
-  gridsize <- length(x_grid)
-  HL <- length(h_grid)
-  D <- matrix(NA, nrow=gridsize, ncol=OptTime)
-  V <- rep(0,gridsize) # initialize BC,
-
-  # give a fixed reward for having value larger than xT at the end. 
-  V[x_grid >= xT] <- reward # a "scrap value" for x(T) >= xT
-
-  # loop through time  
-  for(time in 1:OptTime){ 
-    # try all potential havest rates
-    V1 <- sapply(1:HL, function(i){
-      # Transition matrix times V gives dist in next time
-      SDP_Mat[[i]] %*% V + 
-      # then (add) harvested amount times discount
-       profit(x_grid, h_grid[i]) * (1 - delta) 
-    })
-
-    # find havest, h that gives the maximum value
-    out <- sapply(1:gridsize, function(j){
-      value <- max(V1[j,], na.rm = T) # each col is a diff h, max over these
-      index <- which.max(V1[j,])  # store index so we can recover h's 
-      c(value, index) # returns both profit value & index of optimal h.  
-    })
-
-    # Sets V[t+1] = max_h V[t] at each possible state value, x
[…]

### 2014-05-27 R/integrate_SDP_matrix.R

@@ -1,42 +1,0 @@
-
-#' Determine the Stochastic Dynamic Programming matrix.
-#'
-#' Integrate the multidimensional function using the cubature package
-#' @param f the growth function of the escapement population (x-h)
-#'   should be a function of f(t, y, p), with parameters p
-#' @param p the parameters of the growth function
-#' @param x_grid the discrete values allowed for the population size, x
-#' @param h_grid the discrete values of harvest levels to optimize over
-#' @param sigma_g the variance of the population growth process
-#' @param sigma_m noise in stock assessment (currently assumes lognormal)
-#' @param sigma_i noise in implementing the quota (lognormal)
-#' @return the transition matrix at each value of h in the grid. 
-#' @import cubature
-#' @export
-integrate_SDP_matrix  <- function(f, p, x_grid, h_grid, sigma_g, sigma_m, sigma_i){
-  gridsize <- length(x_grid)
-  SDP_Mat <- lapply(h_grid, function(h){
-    mat <- sapply(x_grid, function(y){
-      # Handle the case of 0 expectation seperately, maps 100% to extinction
-      expected <- f(y,h,p)
-      if(expected==0){
-        Prob <- numeric(gridsize)
-        Prob[1] <- 1
-      } else {
-        # dividing x by the expected value is same as scaling distribution to mean 1
-        pdf_zg <- function(x, expected) dlnorm(x/expected, 0, sigma_g)
-        pdf_zm <- function(x) dlnorm(x, 0, sigma_m)
-        pdf_zi <- function(x,q) dlnorm(x, log(q), sigma_i)
-        Prob <- sapply(x_grid, function(y){
-          F <- function(x) 
-            pdf_zg(y, f(x[1], x[2], p)) * pdf_zm(x[1]) * pdf_zi(x[2], h)
-          int <- adaptIntegrate(F, c(0, 0), c(10*K, 10*K))
-          int$integral
-        })   
-      }
-      Prob/sum(Prob)
-    })
-    t(mat)
-  })
-  SDP_Mat
-}

### 2014-05-27 R/parameter_uncertainty_SDP.R

@@ -1,44 +1,0 @@
-#' Computes the transition matrix under the case of parametric uncertainty
-#'
-#' @param f the growth function of the escapement population (x-h)
-#'   should be a function of f(t, y, pardist[i,]), with parameters
-#' @param x_grid the discrete values allowed for the population size, x
-#' @param h_grid the discrete values of harvest levels to optimize over
-#' @param pardist a matrix with columns as variables and rows as the 
-#' Monte Carlo samples from the posterior
-#' @param sigma_g_index column number containing growth noise
-#' @param n_mc number of monte carlo replicates to sample
-#' @export
-parameter_uncertainty_SDP <- function(f, x_grid, h_grid, pardist, sigma_g_index, n_mc = 100){
-  lapply(h_grid, function(h){ # for each h
-    # Set up monte carlo sampling 
-    d <- dim(pardist)
-    indices <- round(runif(n_mc,1, d[1]))
-    # Compute the transition matrix
-    F_true <- 
-      sapply(x_grid, function(x_t){           # For each x_t  
-        bypar <- sapply(indices, function(i){ # For each parameter value
-          
-          mu <- f(x_t, h, pardist[i,])                    # expected x_{t+1} 
-          est_sigma_g <- pardist[i,sigma_g_index]         # Variance parameter
-          
-          # Calculate the probability density
-          if(snap_to_grid(mu,x_grid) < x_grid[2]){ # handle the degenerate case 
-            out <- numeric(length(x_grid))
-            out[1] <- 1
-            out
-          } else { # Calculate the transition density based on log-normal
-            # FIXME handle normally distributed measurement error additionally 
-            out <- dlnorm(x_grid/mu, 0, est_sigma_g) 
-          }
-        })  
-        # Average over parameter distributions and normalize
-        ave_over_pars <- apply(bypar, 1, sum) 
-        ave_over_pars / sum(ave_over_pars)
-      })
-    F_true <- t(F_true)
-  })
-}
-
-
-snap_to_grid <- function(x, grid) sapply(x, function(x) grid[which.min(abs(grid - x))])   

### 2014-05-27 R/population_models.R

@@ -1,209 +1,0 @@
-# file population_models.R
-# author Carl Boettiger <cboettig@gmail.com>
-# date 2011-11-16
-# license BSD
-# common population dynamics models with fishing
-
-
-
-################################################################
-# Library of some possible population dynamics state equations #
-################################################################
-
-
-# temporal variation in f is possible, but increases the memory required, 
-# though not the time for the optimization(?)
-
-#' Harvested Beverton Holt growth model
-#' @param x fish population 
-#' @param h havest level
-#' @param p parameters of the growth function, c(A, B), where
-#'  A is the maximum growth rate and B the half-maximum in Beverton-Holt.  
-#' @return population next year
-#' @details Harvesting takes place before reproduction in ths model.
-#'  The carrying capacity is K <- (pars[1]-1)/pars[2]
-#'  Try with pars <- c(2,4)
-#' @export
-BevHolt <- function(x, h, p){
-  x <- max(0, x - h)
-  A <- p[1] 
-  B <- p[2] 
-  sapply(x, function(x){ # use sapply so fn accepts vector-valued x
-    x <- pmax(0, x)
-    pmax(0, A * x/(1 + B * x))
-  })
-}
-
-
-
-
-#' Beverton Holt growth model with fishing-effort based control
-#' @param x fish population 
-#' @param h fishing effort (harvest is effort times fish population)
-#' @param p parameters of the growth function, c(A, B), where
-#'  A is the maximum growth rate and B the half-maximum in Beverton-Holt.  
-#' @return population next year
-#' @details Harvesting takes place before reproduction in ths model.
-#'  The carrying capacity is K <- (pars[1]-1)/pars[2]
-#'  Try with pars <- c(2,4)
-#' @export
-BevHolt_effort <- function(x, h, p){
-  S <- max(0, x - x*h) # Escapement from harvest
-  A <- p[1] 
-  B <- p[2] 
-  sapply(S, function(x){ # use sapply so fn accepts vector-valued x
-    x <- pmax(0, x)
[…]

### 2014-05-27 R/value_iteration.R

@@ -1,69 +1,0 @@
-
-#' Identify the dynamic optimum using backward iteration (dynamic programming)
-#' @param SDP_Mat the stochastic transition matrix at each h value
-#' @param x_grid the discrete values allowed for the population size, x
-#' @param h_grid the discrete values of harvest levels to optimize over
-#' @param OptTime the stopping time 
-#' @param xT the boundary condition population size at OptTime
-#' @param c the cost/profit function, a function of harvested level
-#' @param delta the discounting rate (1-delta)
-#' @param epsilon value iteration tolerance
-
-#' (i.e. enforces the boundary condition)
-#' @return list containing the matrices D and V.  D is an x_grid by OptTime
-#'  matrix with the indices of h_grid giving the optimal h at each value x
-#'  as the columns, with a column for each time.  
-#'  V is a matrix of x_grid by x_grid, which is used to store the value 
-#'  function at each point along the grid at each point in time.  
-#'  The returned V gives the value matrix at the first (last) time. 
-#' @export
-value_iteration <- function(SDP_Mat, x_grid, h_grid, OptTime=100, xT, profit, 
-                            delta, epsilon = 1e-4){
-  
-  
-  ## Initialize space for the matrices
-  gridsize <- length(x_grid)
-  HL <- length(h_grid)
-  D <- matrix(NA, nrow=gridsize, ncol=1)
-  V <- rep(0,gridsize) # initialize BC,
-  Vp <- rep(10, gridsize) # initialize previous value (not equal to current value)
-  
-  # loop through time  
-  #for(time in 1:OptTime){
-  time <- 1
-  while(max(abs(Vp - V)) >= (delta * epsilon / (2 - 2 * delta)) && time < OptTime){
-    # try all potential havest rates
-    V1 <- sapply(1:HL, function(i){
-      # Transition matrix times V gives dist in next time
-      SDP_Mat[[i]] %*% V + 
-        # then (add) harvested amount times discount
-        profit(x_grid, h_grid[i]) * (1 - delta) 
-    })
-    
-    # find havest, h that gives the maximum value
-    out <- sapply(1:gridsize, function(j){
-      value <- max(V1[j,], na.rm = T) # each col is a diff h, max over these
-      index <- which.max(V1[j,])  # store index so we can recover h's 
-      c(value, index) # returns both profit value & index of optimal h.  
-    })
-    
[…]

### 2014-05-27 demo/likelihood_estimators.R

@@ -1,45 +1,0 @@
-require(pdgControl)
-
-sigma_g <- 0.8    # Noise in population growth
-z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-f <- BevHolt                # Select the state equation
-pars <- c(2, 4)             # parameters for the state equation
-K <- (pars[1] - 1)/pars[2]  # Carrying capacity 
-
-
-x <- numeric(1000)
-x[1] <- .01
-for(t in 1:(length(x)-1)){
-  x[t+1] = z_g()*f(x,0,pars)
-}
-
-likelihood_estimator <- function(f, x, guess_p = NULL){
-  loglikfn <- function(pars){
-    probs <- sapply(1:(length(x)-1), function(i){
-      mu <- f(x[i],0,pars)
-      sigma <-  
-      dlnorm(x[i+1], meanlog=log(mu+sigma_g^2/2), sdlog=sigma_g, log=TRUE)
-    })
-    -sum(probs)
-  }
-  o <- optim(guess_p, loglikfn)
-}
-
-out <- likelihood_estimator(f, x, pars)
-out
-
-
-X <- 5 * rlnorm(10000, 0, 1)
--sum(dlnorm(X, log(5), 1))
-
-
-
-  loglik_noise <- function(pars){
-    probs <- sapply(1:(length(x)-1), function(i){
-      p <- pars[-1]    # estimate noise parameter too?
-      sigma <- pars[1]
-      dlnorm(x[i+1], logmean=log(f(x[i],0,p)), sdlog=log(sigma), log=TRUE)
-    })
-    -sum(probs)
-  }
-

### 2014-05-27 demo/noise_dists.R

@@ -1,36 +1,0 @@
-#########################################################################
-# A library of distribution functions for sources of stohcasticity      #
-#########################################################################
-
-# z_g is the stochasticity in the growth process, x_{t+1} = z_g f(x_t)
-# z_m is the measurement error in the stock assessment, m_t = z_m x_t
-# z_i is the implementation error in the harvest quota: h_t = z_i q_t
-
-# Normal random vars -- an unusual choice given the negative domain support
-#z_g <- function() rnorm(1,1, sigma_g)
-#z_m <- function() rnorm(1,1, sigma_m)
-#z_i <- function() rnorm(1,1, sigma_i)
-
-# Log-normal distribution -- perhaps the most natural, at least for z_g
-# mean is 1 = exp(mu + sigma^2/2), then
-# log(1) - sigma^2/2 = mu
-#z_g <- function() rlnorm(1,  log(1)-sigma_g^2/2, sigma_g) # mean 1
-#z_m <- function() rlnorm(1,  log(1)-sigma_m^2/2, sigma_m) # mean 1
-#z_i <- function() rlnorm(1,  log(1)-sigma_i^2/2, sigma_i) # mean 1
-
-z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
-z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
-
-# Uniform distribution
-#z_g <- function() runif(1, max(0,1-sigma_g), 1+sigma_g)
-#z_m <- function() runif(1, max(0,1-sigma_m), 1+sigma_m)
-#z_i <- function() runif(1, max(0,1-sigma_i), 1+sigma_i)
-
-
-# No noise
-#z_g <- function() 1
-#z_m <- function() 1
-#z_i <- function() 1
-
-

### 2014-05-27 demo/policy_costs.R

@@ -1,79 +1,0 @@
-# file Reed.R
-# author Carl Boettiger, <cboettig@gmail.com>
-# date 2011-11-02
-# license BSD
-rm(list=ls())   # Start wtih clean workspace 
-require(pdgControl)
-
-# we'll be using these libraries directly, so we load them up
-require(ggplot2)
-require(reshape2)
-require(Hmisc)
-
-## consider defaults for these
-# Define all parameters 
-delta <- 0.04      # economic discounting rate
-OptTime <- 50     # stopping time
-gridsize <- 40   # gridsize (discretized population)
-sigma_g <- 0.2    # Noise in population growth
-sigma_m <- 0.     # noise in stock assessment measurement
-sigma_i <- 0.     # noise in implementation of the quota
-
-# Define noise distributions  
-z_g <- function() rlnorm(1,  0, sigma_g) # growth noise
-z_m <- function() 1 # no measurement (stock assessment) noise
-z_i <- function() 1 # no implementation (quota) noise
-
-## Chose the state equation / population dynamics function
-f <- BevHolt                # Select the state equation
-pars <- c(2, 4)             # parameters for the state equation
-K <- (pars[1] - 1)/pars[2]  # Carrying capacity 
-xT <- 0                     # boundary conditions
-scrap_value <- 0            # reward profit offered for finishing >= xT stock
-e_star <- 0                 # model's bifurcation point (just for reference)
-control <- "harvest"        # control variable is total harvest, h = e * x
-x0 <- K / 2                 # initial condition
-# use a harvest-based profit function with default parameters
-profit <- profit_harvest() # functions defined in stochastic_dynamic_programming.R
-
-# Set up the discrete grids
-x_grid <- seq(0, 2 * K, length = gridsize)  # population size
-h_grid <- x_grid  # vector of havest levels, use same resolution as for stock
-
-SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g)
-
-## solution with policy cost P: 
-opt <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, .25*K, 
-                    profit, delta, reward=0, P=.3, penalty="asym")
-
-# Calculate the Reed optimum (e.g. no cost to policy adjustment):
-reed <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, .25*K, 
[…]

### 2014-05-27 inst/archive/JimExamples/run_collocation.R

@@ -1,75 +1,0 @@
-# file: training_prob2_collocation.R
-# author: Carl Boettiger, \url{http://carlboettiger.info}
-# date: 2011-11-24
-
-# Libraries
-require(bvpSolve)
-
-# load the functions
-source("training_prob2_collocation.R")
-
-##################################################################
-# Set up model and parameters                                    #
-##################################################################
-
-
-## Biological Parameters (state equation)
-# alpha - population growth rate
-# K - carrying capacity
-# C - allee theshold
-## Economic Parameters 
-# gamma - utility function (diminishing returns) 
-# rho - economic discounting
-pars <- c(alpha=1, K=1, C=0.2, gamma=-2, rho=0.5)
-
-
-## Boundary Conditions
-X0 <- K     # Starting population size
-XT <- C     # Ending population size
-
-y0 <- c(0.5*K, 0) # 
-t <- seq(0, 10, by=0.1)
-out <- lsoda(y=y0, times=t, func=fish, parms=p, rtol=1e-4, jacfun=jac)
-plot(out[,1], out[,2], type="l", xlab="t", ylab="fish stock", lwd=3)
-
-
-## Solve by shooting  ##
-t <- seq(0, 10, by=.1)
-sol1 <- bvpshoot(yini = c(X0,NA), yend = c(XT, NA),
-                 x = t, func = fun, guess = 0, parms=pars)
-
-## Solve by collocation ##
-## (using the shooting solution as the guess)
-sol3 <- bvpcol(yini = c(X0, NA), yend = c(XT, NA),
-               x = t, func = fun, parms=pars, 
-               xguess = sol1[,1], yguess=t(sol1[,-1]))
-
-## check solution quality 
-diagnostics(sol3)
-
-## save output to file
-png("collocation.png")
-  time <- sol3[,1]
-  fishstock <- sol3[,2] 
-  harvesteff <- sol3[,3] 
-
-  ylim <- c(min(fishstock, harvesteff), max(fishstock, harvesteff)) 
-  plot(time, fishstock, type="l", lwd=3, 
-       ylim=ylim, xlab="time", ylab="fraction of K")
-  lines(sol3[,1], harvesteff, col="red", lwd=3)
-  legend("topright", c("fish stock", "harvest effort"), lty=1, 
-         col=c("black", "red"))
-
-mtext(expression(bold("Optimal Harvest for:")), 
-       line=2.5,cex=1.15)
[…]

### 2014-05-27 inst/archive/JimExamples/stochastic_growth.R

@@ -1,147 +1,0 @@
-###############################################
-#
-# stochastic_growth.R: An R program to solve a simple stochastic
-# growth model via eitehr value function or policy function 
-# iteration, which is also known as Howard's Policy Improvement 
-# Algorithm.
-#
-# Characteristics of the problem are:
-#   (1) Infinite horizon
-#   (2) Continuous state space and discrete time
-#   (3) Income shock takes on two discrete states
-#
-#   \max_u
-#
-# Assumptions are:
-#   (1) Utility function: U(c) = c^(1-g)/(1-g)
-#   (2) discount rate, b = 10% 
-#   (3) Consumption function: c = F(K) = (1/a)*K^a.  AKA the law of motion
-#
-# Based on code written by George Hall, July 2001
-# 
-
-function <- stochastic_growth(){
-  value_iteration <-0
-  if(value_iteration==1)
-    print("Value Function Iteration")
-  else 
-    print("Policy Function Iteration")
-
-# Economic parameter values
-
-a <- 0.20     # production parameter for f(K)
-b <- 0.10     # discount rate
-b <- 1/(1+b)  # discount factor
-g <- 1.5      # g>=1 in U(c) function
-
-
-
-# Transition probability matrix
-P <- matrix(c(.8,.2,.2,.8), nrow=2, byrow=T) # 
-A_high <- 1.250 # high value for technology
-A_low <- 0.50   # low value for technology
-
-# Discretizing the continuous state variable, Capital
-N <- 1501 # N is the grid-size, slower fro larger N
-
-#########
-# Typically, you would solve for the steady-state level and 
-# use that to determine the range.  I know for this problem
-# the steady-state is around K=1 in setting this range:
-########
-MaxK <- 1.5
-MinK <- 0.1
-K <- seq(MinK, MaxK, length.out = N) # uniform grid
-
-
-#=========================================================#
-# Tabulating consumption and utility for all combinations #
-# K, K(t+1) for the grid                                  #
-#=========================================================#
-# R needs a meshgrid function. 
-meshgrid <- function(a,b) {
-    list(
-           x=outer(b*0,a,FUN="+"),
-           y=outer(b,a*0,FUN="+")
-        )
-} 
-grid <- meshgrid(K, K)
-Kt <- grid$x
-Kt1 <- grid$y
-
[…]

### 2014-05-27 inst/archive/JimExamples/training_prob2_collocation.R

@@ -1,40 +1,0 @@
-# file: training_prob2_collocation.R
-# author: Carl Boettiger, \url{http://carlboettiger.info}
-# date: 2011-11-24
-
-# Libraries
-require(bvpSolve)
-
-##################################################################
-# Solve the ODE system of fish dynamics at fixed harvest level   #
-##################################################################
-fish <- function(t,y,p){
-  dy1 <- f(t, y, p) 
-  dy2 <- 0                # constant harvest level 
-  list(c(dy1, dy2), NULL)
-}
-jac <- function(t,y,p){
-  matrix(c(df(t, y, p), 0,
-           0,           0),
-         2,2, byrow=T)
-}
-
-##################################################################
-# Specify & solve the Boundary Value Problem                     #
-##################################################################
-
-#' fun defines the bvp system to be solved
-#' @param t time variable 
-#' @param y a vector of the system state y[1],y[2] = (x,h)
-#' @param p parameters: c(alpha, K, C, gamma, rho)
-fun <- function(t,y,p){
-  gamma <- p[4]
-  rho <- p[5]
-
-  dy1 <- f(t, y, p) 
-  dy2 <- (1 / gamma) * (rho - df(t,y,p))
-
-  list(c(dy1, dy2))
-}
-
-

### 2014-05-27 inst/matlab/Reed_SDP_with_changecosts.m

@@ -1,121 +1,0 @@
-function [D,SDP_Mat,xt_h] = Reed_SDP_with_changecosts(DISCRETISE,SIM,ChangeCost,OptTime)
-% REED_SDP_with_changecosts implements a numerical version of a variant of the SDP described in:
-%       Reed, W.J., 1979. Optimal Escapement Levels in Stochastic and
-%       Deterministic Harvesting Models. Journal of Environmental Economics
-%       and Management. 6: 350-363.
-%
-%       Reed's original formulation has been changed to include a cost
-%       associated with increasing or decreasing the harvest.
-%
-%       Updated: December 7 2011
-% 
-%   [D,SDP_Mat,xt_h,xt,x_ph] = REED_SDP_with_changecosts(DISCRETISE,SIM,ChangeCost,OptTime)
-%   
-%   Inputs are:
-%           DISCRETISE  - the resolution at which the state space (i.e., the 
-%                         number of fish in the population) is discretised.
-%           SIM         - a binary stating whether a stochastic forward simulation
-%                         of the population should be run and outputted. 
-%           ChangeCost  - the cost of changing the harvest rate. Value is
-%                         in the units of harvest, and is per-unit-harvest-change. 
-%           OptTime     - length of the project period 
-%
-%   % Outputs 
-%           D           - The #States x Tmax state-dependent optimal decision matrix
-%           SDP_Mat     - The markovian state transition matrix
-%           xt_h        - The population level through time
-% 
-
-if nargin < 3; DISCRETISE = 30; SIM = 1; ChangeCost = 0.05; OptTime = 25; disp('Running defaults'); end
-A = 1.5; B = 4; % Beverton-Holt parameters
-K = (A-1)/B; % K is the equilibrium population in the absence of stochasticity and harvest
-delta = 0.05; % The economic discount rate
-dev = 0.1; % Standard deviation of the noise process
-n_vec = linspace(0,1.75*K,DISCRETISE); % Vector of population sizes
-
[…]

### 2014-05-27 inst/matlab/draw_plots.m

@@ -1,37 +1,0 @@
-function out = draw_plots(HVec, n_vec, V1, D, xt_h, xt, x_ph, OptTime)
-% Draw the plots associated with REED_SDP.m
-
-  figure(1), clf % PLOTTING FUNCTIONS
-  subplot(2,2,1), hold on, set(gca,'fontsize',14)
-  P=pcolor(HVec,n_vec,V1); set(P,'edgecolor','none'), colorbar, ylim([0 75])
-  title('Reward in 1st timestep','fontsize',14)
-  xlabel('Alternative harvest rates','fontsize',14)
-  ylabel('Population','fontsize',14), axis tight
-  subplot(2,2,2), cla, hold on, xlim([1 OptTime]), set(gca,'fontsize',14)
-  ZZ = HVec(D);
-  ZZ(ZZ==0)=nan;
-  P=pcolor([OptTime:-1:1],n_vec,ZZ(:,end:-1:1));
-  set(P,'edgecolor','none'), colorbar, ylim([0 75])
-
-  title('Optimal decision (no scrap value)','fontsize',14)
-  xlabel('Management timeline (years)','fontsize',14)
-  ylabel('Population','fontsize',14), axis tight
-  subplot(2,2,[3,4]), hold on, set(gca,'fontsize',14)
-
-  ReedThreshold = n_vec(sum(D(:,1)==1));
-  plot([0 OptTime],[ReedThreshold ReedThreshold],'r:')
-  MixX = [1:length(xt);
-  1:length(xt)];
-  MixX = MixX(1:end-1);
-  Mix = [xt;xt_h];
-  Mix = Mix(1:end-1);
-  plot(MixX,Mix,'g--','linewidth',2)
-  plot([1:OptTime],xt_h,'linewidth',2)
-  plot([1:OptTime],[x_ph xt_h(end)],'m--','linewidth',2), ylim([0 1.1*max([xt_h,xt])])
-  xlabel('Management timeline (years)','fontsize',16)
-  ylabel('Population','fontsize',16), axis tight
-  legend('Reed''s S','N(t) without harvest','N(t)','Post-harvest population',2);
-  %set(L,'fontsize',12)
-  out = 0;
-end
-

### 2014-05-27 manuscripts/components/install.R

@@ -1,8 +1,0 @@
-#!/usr/bin/Rscript
-
-if(!require("pdgControl")){
-#  install.packages("devtools")
-#  library("devtools")
-#  install_github("reshape")
-  install.packages("..", repos =NULL, dependencies = c("Depends", "Imports", "Suggests"))
-}

### 2014-05-27 manuscripts/components/restore-cache.R

@@ -1,19 +1,0 @@
-#!/usr/bin/R
-setwd("components")
-archive <- "pdg_controlcache.tar.gz"
-
-
-library("utils")
-library("httr")
-# restore cache file
-target <- paste0("http://two.ucdavis.edu/~cboettig/data/", archive)
-cache <- GET(target)
-if(cache$status_code != 404){
-  writeBin(content(cache, "raw"), archive)
-  untar(archive)
-  unlink(archive)
-}
-
-setwd("..")
-
-

### 2014-05-28 inst/examples/policycosts/noise_effects.Rmd

--- 2013-11-12 inst/examples/noise_effects.Rmd
@@
                      profit, delta, reward=reward)
-
+value1 <- opt$V[42]*100
 p1 <- opt$D[,1]
@@
 tmp <- lapply(1:100, function(i){ 
-  set.seed(i)
+  #set.seed(i)
   ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i)
@@
                      profit, delta, reward=reward)
-
+value2 <- opt$V[42]*100
 p2 <- opt$D[,1]
@@
 tmp2 <- lapply(1:100, function(i){ 
-  set.seed(i)
+  #set.seed(i)
   ForwardSimulate(f, pars, x_grid, h_grid, x0=K, p2, z_g, z_m, z_i)
@@
 
-tmp <- data.table(tmp)
-tmp2 <- data.table(tmp2)
+# adjust by discount rate
+tmp$profit <- tmp$profit/(1+delta)^tmp$time
+tmp2$profit <- tmp2$profit/(1+delta)^tmp2$time
 
-discounted = tmp[, sum(profit/((1+delta)^time)), by=L1]$V1
-profit = tmp[, sum(profit), by=L1]$V1
 #ggplot(tmp, aes(time, fishstock, group=L1)) + geom_line(alpha=0.1)
@@
 identical(p1,p2)
-
-c(low_noise = sum(tmp$profit), high_noise = sum(tmp2$profit))
+c(low_noise = sum(tmp$profit), high_noise = sum(tmp2$profit), low_theory = value1, high_theory=value2)
 ```

### 2014-05-28 manuscripts/manuscript.Rmd

@@
 
-<!--PRESUMABLY YOU USED A FINITE TERMINAL TIME IN WHICH CASE
-WE NEED TO REVISE TO REFLECT HOW YOU HANDLED THAT.-->
+<!--NOTE presumably you used a finite terminal time in which case
+we need to revise to reflect how you handled that.-->
 
@@
 ```{r Figure_1, fig.cap="Expected net present value by functional form of penalty.
-Horizontal axis shows the coefficient $c_i$ governing the magnitude of the policy cost, while vertical axis shows fraction of the maximum expected net present value dissipated by the policy cost.
-The horizontal line indicates a value of the stock that is 80% of the maximum expected value in the absence of policy adjustment costs, $NPV_0({\\bf h_0^*})$.
-Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.", dependson="quadcosts", fig.width=5, fig.height=3}
-ggplot(fees, aes(c2, (npv0-value)/npv0, lty=variable)) + geom_line() + theme_tufte()
+Horizontal axis shows the coefficient $c_i$ governing the magnitude of the policy cost, while vertical axis shows fraction of the maximum expected net present value dissipated by the policy cost, $\\tfrac{NPV_0 - NPV_i}{NPV_0}$.
+The horizontal line indicates a value of the stock that is reduced by `r reduction * 100`% from the maximum expected value in the absence of policy adjustment costs, $NPV_0({\\bf h_0^*})$.
+Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.", dependson="quadcosts", fig.width=4, fig.height=3}
+
+ggplot(fees, aes(c2, (npv0-value)/npv0, lty=variable)) + 
+  geom_line() + 
+  geom_hline(aes(hintercept=reduction), linetype=4) + 
+  xlab("penalty coefficient") +
+  ylab("Reduction in net present value") + 
+  theme_tufte()
 
 ```
-
-<!-- NOTE
-Figure needs tidying up to be submission ready.
-Resize it - can be smaller, no color needed, bigger TickLabels, no background shading or grid.
-It also need the relevant horizontal and vertical lines marking to show the calibration.
-Choose a % reduction that corresponds to that you are choosing for what is currently labeled Figs 2&3 (sample paths) and Fig 8 - histograms.
-We should then adjust the text to talk to what is shown in the figure consistently - e.g.
-is is 25% loss or 75% of the value, etc.
--->
 
@@
 
-<!-- If, as discussed over email, we are going to go with just one in the main text blown up a bit bigger to make it more visible, I need to have that figure to be able to write this text around it.
-Note I would still present the full set in the SI.
-Rather than trying to recover old random seeds if not stored.
-Just run one anew.
--->
-<!-- 
-For the figure in the main text, I would make a single figure with six plates - the three different adjustment costs are the columns.
-One row is the effect on optimal harvests and one the effect on optimal stock sizes.
--->
-
 Figure 2 illustrates how the different forms of adjustment cost can
@@
 sequence of random shocks so that they can be compared directly. Figure
-3 shows the corresponding stock sizes, which are measured here WHEN
+3 shows the corresponding stock sizes, which are measured here before 
+harvest ($h_t$ being determined after observing stock size $x_t$).
+Because stock sizes are measured before harvests, the effect of the 
+penalty on the stock size is not very pronounced, while the effect
+on the harvest chosen shows a systematic deviations from the penalty
+free optimum, depending on the nature of the cost.
 
-<!-- At what time relative to the dynamics in equation 1, and I would be setting up a comment why they don't see something similar to the constant escapement policy -- this is just a census time issue, but I would say it explicitly given the attention we shine on the REED result upfront.
--->
-
-. In 
-each case, the optimal solution without any adjustment cost is shown in
-black and the policy induced by optimization under the given adjustment
-penalty (equivalent to a 25% reduction in maximum expected NPV) is
-overlaid in blue.
+In each case, the optimal solution without any adjustment cost is shown in
+against the policy induced by optimization under the given adjustment
+penalty (equivalent to a `r 100*reduction`% reduction in maximum expected NPV) 
+is overlaid in blue.
 
@@
 
-```{r Figure_2, dependson="tidy", fig.cap="Individual realizations of optimal harvesting strategy under the different functional forms of adjustment costs.", fig.height=3, fig.width=8}
-ggplot(subset(dt, replicate %in% names(reps)[1:5])) +
-  geom_line(aes(time, alternate), col="grey20", lwd=1) +
-  geom_line(aes(time, fishstock), col=rgb(0,0,1,.8)) + 
-  facet_grid(replicate~penalty_fn) + 
-  labs(x="time", y="stock size", title = "Stock Dynamics")  + theme_tufte()
+```{r Figure_2, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=3, fig.width=8}
 
-```
+fig2_df <- as.data.frame(subset(dt, replicate=='rep_2'))
+fig2_df <- fig2_df[c("time", "fishstock", "alternate", "harvest", "harvest_alt", "penalty_fn")]
+fig2_df <- melt(fig2_df, id = c("time", "penalty_fn"))
+fig2_df <- data.frame(fig2_df, baseline = fig2_df$variable)
+variable_map <- c(fishstock = "fish_stock", alternate = "fish_stock", harvest = "harvest", harvest_alt = "harvest")
+baseline_map <- c(fishstock = "penalty", alternate = "no_penalty", harvest = "penalty", harvest_alt = "no_penalty")
+fig2_df$variable <- variable_map[fig2_df$variable]
+fig2_df$baseline <- baseline_map[fig2_df$baseline]
 
-```{r Figure_3, dependson="tidy", fig.cap="Individual realizations of optimal stock size strategy under the different functional forms of adjustment costs.", fig.height=3, fig.width=8}
-ggplot(subset(dt, replicate %in% names(reps)[1:5])) +
-  geom_line(aes(time, harvest_alt), col="grey20", lwd=1)  +
-  geom_line(aes(time, harvest), col=rgb(0,0,1,.8)) + 
-  facet_grid(replicate~penalty_fn) + 
-  labs(x="time", y="havest intensity (fish taken)", title = "Harvest Policy Dynamics")  + theme_tufte()
+ggplot(fig2_df, aes(time, value, col=baseline)) +
+  geom_line() +
+  facet_grid(variable~penalty_fn) + 
+  labs(x="time", y="stock size", title = "Example Stock & Harvest Dynamics")  + 
+  theme_tufte()
 
@@
 variability) and are made for a particular magnitude of policy
-adjustment costs equal to 25% of the maximum expected net present value <!-- Match to that shown in Figure 1. -->
+adjustment costs equal to `r reduction`% of the maximum expected net present value 
 in the base case ($NPV_0({\bf h_0^*})$). Figure 4 generalizes to show
@@
 autocorrelation of harvests and stock sizes through time; and on the
-cross-correlation of harvests and stock sizes through time. <!-- Are we showing cross-correlations or not?-->
+cross-correlation of harvests and stock sizes through time. <!-- NOTE Are we showing cross-correlations or not?-->
 
@@
 
-<!--
+<!-- NOTE 
 Assuming we aren't showing cross-correlations, I think we can probably fit these into a single four subplot figure.
@@
 <!--
-Obviously we have presentation choices to make here. I think there is plenty of scope either to compact this table somehow (rows are penalty functions)  x columns are percent reduction.
+NOTE Obviously we have presentation choices to make here. I think there is plenty of scope either to compact this table somehow (rows are penalty functions)  x columns are percent reduction.
 
@@
     saves direct costs, but permits higher-value solutions.
+
+Supplementary material
+======================
+
+```{r Figure_1S, dependson="tidy", fig.cap="Multiple realizations of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.
+Note that while fish stock dynamics appear similar in penalty and non-penalty scenarios, the harvest dyanmics show clear patterns depending on the type of penalty.", fig.height=3, fig.width=8}
+
+fig1s_df <- as.data.frame(subset(dt, replicate %in% paste0('rep_', 1:5)))
+fig1s_df <- fig1s_df[c("time", "fishstock", "alternate", "harvest", "harvest_alt", "penalty_fn", "replicate")]
+fig1s_df <- melt(fig1s_df, id = c("time", "penalty_fn", "replicate"))
+fig1s_df <- data.frame(fig1s_df, baseline = fig1s_df$variable)
+variable_map <- c(fishstock = "fish_stock", alternate = "fish_stock", harvest = "harvest", harvest_alt = "harvest")
+baseline_map <- c(fishstock = "penalty", alternate = "no_penalty", harvest = "penalty", harvest_alt = "no_penalty")
+fig1s_df$variable <- variable_map[fig1s_df$variable]
+fig1s_df$baseline <- baseline_map[fig1s_df$baseline]
+
+ggplot(fig1s_df, aes(time, value, col=baseline, lty=replicate)) +
+  geom_line() +
+  facet_grid(variable~penalty_fn) + 
+  labs(x="time", y="stock size", title = "Example Stock & Harvest Dynamics")  + 
+  theme_tufte()
+
+```

### 2014-05-28 manuscripts/manuscript.Rmd
update documentation, add rmarkdown header info

@@
 layout: preprint      # review, 11pt
+output:
+  pdf_document:
+    keep_tex: true
+    template: components/elsarticle.latex
+    pandoc_args: [
+      "--biblio", "components/references.bib",
+      "--csl", "components/ecology.csl",
+      "--metadata", "fontsize[:11]"
+      ]
 ---
@@
 <!-- CODE -->
+
+```{r caching, include=FALSE, output="hide"}
+library("methods")
+library("knitr")
+basename <- "manuscript"
+opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
+               cache.path = paste("components/cache/", basename, "/", sep=""))
+opts_chunk$set(cache = 2)
+opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, 
+               comment = NA, verbose = TRUE, echo=FALSE)
+
+# PDF-based figures
+opts_chunk$set(dev='pdf')
+```
 

### 2014-05-28 manuscripts/components/install.R

@@ -1,8 +1,12 @@
 #!/usr/bin/Rscript
 
 if(!require("pdgControl")){
-#  install.packages("devtools")
-#  library("devtools")
-#  install_github("reshape")
-  install.packages("..", repos =NULL, dependencies = c("Depends", "Imports", "Suggests"))
+  install.packages("devtools")
+  library("devtools")
+  install_github("reshape")
+  install_github("rmarkdown", "rstudio")
+  install_github("cboettig/cboettigR")
+
+
+  install.packages("..", repos = NULL, dependencies = c("Depends", "Imports", "Suggests"))
 }

### 2014-05-28 manuscripts/manuscript.Rmd
use render instead of makefile

@@
     affiliation: cstar
-    email: cboettig@gmail.com
+    email: 
     footnote: Corresponding author

### 2014-05-28 manuscripts/manuscript.Rmd
tweak and clean up

@@
 title: Optimal management of a stochastically varying population when policy adjustment is costly
+
 author: 
@@
     affiliation: UTK
+
 address: 
@@
     address: University of Tennessee, Knoxville
+
 abstract: |
@@
           they are present.
-layout: preprint      # review, 11pt
+
+layout: preprint, 11pt
+
+bibliography: components/references.bib
+csl: components/ecology.csl
+
 output:
@@
     template: components/elsarticle.latex
-    pandoc_args: [
-      "--biblio", "components/references.bib",
-      "--csl", "components/ecology.csl",
-      "--metadata", "fontsize[:11]"
-      ]
 ---
@@
 apples })
-write.csv(reduction_table, "reduction_table.csv")
+write.csv(reduction_table, "../data/reduction_table.csv")
 ````
@@
 ```
+
+# References

### 2014-05-29 manuscripts/manuscript.Rmd
updated packrat configuration

@@
 
-layout: preprint, 11pt
+layout: preprint
 
@@
 csl: components/ecology.csl
+documentclass: components/elsarticle
 
@@
 
-```{r caching, include=FALSE, output="hide"}
+```{r dependencies, include=FALSE}
+source("components/install.R")
+```
+
+```{r caching, include=FALSE}
 library("methods")
@@
 
-```{r libraries, output="hide", include=FALSE, cache=FALSE}
+```{r libraries, include=FALSE, cache=FALSE}
 rm(list=ls())
+library("rmarkdown")
 library("pdgControl")
@@
 library("ggthemes")
+library("snowfall")
 theme_set(theme_tufte())
+ncpu = 1
 ```
@@
 ```{r parallel, include=FALSE}
-require(snowfall)
-sfInit(cpu=4, parallel=T)
+sfInit(cpu=ncpu, parallel=T)
 sfLibrary(pdgControl)

### 2014-05-29 manuscripts/components/install.R

@@ -1,10 +1,14 @@
 #!/usr/bin/Rscript
+library("methods")
 
-if(!require("pdgControl")){
-  install.packages("devtools")
-  library("devtools")
-  install_github("reshape")
-  install_github("rmarkdown", "rstudio")
-  install_github("cboettig/cboettigR")
-  install_github("cboettig/pdg_control", dependencies = c("Depends", "Imports", "Suggests"))
-}
+# Install packrat if not available
+if(!require("devtools")) install.packages("devtools")
+if(!require("packrat")) devtools::install_github("rstudio/packrat")
+
+# Let packrat set up the manuscript dependencies
+packrat::packify()
+source(".Rprofile"); readRenviron(".Renviron")
+packrat::restore()
+source(".Rprofile"); readRenviron(".Renviron")
+
+

### 2014-05-29 manuscripts/components/restore-cache.R

@@ -1,10 +1,10 @@
 #!/usr/bin/R
+library("methods")
+library("utils")
+library("httr")
 setwd("components")
 archive <- "pdg_controlcache.tar.gz"
 
-
-library("utils")
-library("httr")
 # restore cache file
 target <- paste0("http://two.ucdavis.edu/~cboettig/data/", archive)
 cache <- GET(target)

### 2014-06-02 manuscripts/manuscript.Rmd
tweaks to manuscript; makefile does not restore cache by default

@@
 ```{r npv_table, dependson="print_npv", results='asis'} 
-pandoc.table(print_npv)
+# verify that we have fine enough c_2 sampling to hit about 75% NPV0 on each penalty form
+# pandoc.table(print_npv)
 ```
@@
 
-$$\max_{{\bf h}}\mathbf{ E} ( NPV_{0} )=\max_{{\bf h}} \sum_0^\infty \mathbf{E} \left( \displaystyle \frac{\Pi_0(N_t,h_t)}{(1+\delta)^{t+1}} \right) \label{eq:objective}$$
+$$
+\begin{equation}
+\max_{{\bf h}}\mathbf{ E} ( NPV_{0} )=\max_{{\bf h}} \sum_0^\infty \mathbf{E} \left( \displaystyle \frac{\Pi_0(N_t,h_t)}{(1+\delta)^{t+1}} \right) \label{eq:objective}
+\end{equation}
+$$
 
@@
 
-$$\Pi_0(N_t,h_t) = p h_t -  c_0 E_t \label{eq:annual_netrevenue}$$
+$$\begin{equation}
+\Pi_0(N_t,h_t) = p h_t -  c_0 E_t \label{eq:annual_netrevenue}
+\end{equation}
+$$
 
 where $E_t$ represents fishing effort. We assume catch is proportional
-to stock size and effort expended fishing that year, $h_t=qE_tN_t$ and
+to stock size and effort expended fishing that year, $h_t = q E_t N_t$ and
 constant $q>0$ is the catchability coefficient. In
-Eqn. [eq:annual_netrevenue], $p$ is the price per unit harvest and
+Eqn. \eqref{eq:annual_netrevenue}, $p$ is the price per unit harvest and
 $c_0$ the cost of fishing and, to simplify the presentation of results,
-we assume that these are constants with $p>0$ and $c_0>0$.
+we assume that these are constants with $p>0$ and $c_0>0$. (Examples 
+shown here use $p$= `r p` and $c_0$ = `r_c0`.) 
+<!-- Mention R code provided to test other values? Do we need to test other values?
+(i.e. the c0 = 0 case?) Word about units?-->
 
-Taken together this objective function ([eq:objective]) and the state
-equation ([eq:state_equation]) define a stochastic dynamic programming
+Taken together this objective function \eqref{eq:objective} and the state
+equation \eqref{eq:state_equation} define a stochastic dynamic programming
 problem that we solve using backwards recursion via Bellman's equation.
@@
 
-<!--NOTE presumably you used a finite terminal time in which case
-we need to revise to reflect how you handled that.-->
+We solve this problem on a finite time horizon of $T =$ `r OptTime` using
+value iteration [@Mangel1988; @Clark2000].
 
@@
 $h_t=h_{t-1}$ and zero otherwise. For each $\Pi_i$, we can then define a
-new objective function $NPV_i$ similar to that in Eqn. [eq:objective].
+new objective function $NPV_i$ similar to that in Eqn. \eqref{eq:objective}.
 
-Taken together with the state equation (Eqn. [eq:state_equation]), each
+Taken together with the state equation Eqn. \eqref{eq:state_equation}, each
 of these new objective functions defines a different stochastic dynamic
@@
 
-<!-- NOTE Will need to do the runs and generate the figures for that one  -->
-In addition in the Supplementary Material, we compare our results with a
+In addition in the Supplementary Material, we compare our results with 
 more conventional fisheries economic formulation in which additional
 costs are applied to the control variables themselves, as opposed to
-adjustments to the controls: $\Pi_4 (N_t,h_t) = p h_t -  c_0 E_t-c_4E_t^2$. Additional costs of this
-form tend to have a smoothing effect on optimal quotas, but also change
+adjustments to the controls: $\Pi_4 (N_t,h_t) = p h_t -  c_0 E_t-c_4E_t^2$. Additional costs of this form tend to have a smoothing effect on optimal quotas, but also change
 the long-term average stock size or quota size that is optimal.
@@
 
+<!--NOTE c_i notation is confusing because it does not usually refer to c_0 or c_4 -->
 Each of the policy adjustment cost function is characterized in terms of
@@
 adjustment costs.
+
+```{r Figure_1, fig.cap="Expected net present value by functional form of penalty.
+Horizontal axis shows the coefficient $c_i$ governing the magnitude of the policy cost, while vertical axis shows fraction of the maximum expected net present value dissipated by the policy cost, $\\tfrac{NPV_0 - NPV_i}{NPV_0}$.
+The horizontal line indicates a value of the stock that is reduced by `r reduction * 100`% from the maximum expected value in the absence of policy adjustment costs, $NPV_0({\\bf h_0^*})$.
+Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.", dependson="quadcosts", fig.width=4, fig.height=3}
+
+ggplot(fees, aes(c2, (npv0-value)/npv0, lty=variable)) + 
+  geom_line() + 
+  geom_hline(aes(hintercept=reduction), linetype=4) + 
+  xlab("penalty coefficient") +
+  ylab("Reduction in net present value") + 
+  theme_tufte()
+
+```
 
@@
 ($c_0=XXX$).
-
-```{r Figure_1, fig.cap="Expected net present value by functional form of penalty.
-Horizontal axis shows the coefficient $c_i$ governing the magnitude of the policy cost, while vertical axis shows fraction of the maximum expected net present value dissipated by the policy cost, $\\tfrac{NPV_0 - NPV_i}{NPV_0}$.
-The horizontal line indicates a value of the stock that is reduced by `r reduction * 100`% from the maximum expected value in the absence of policy adjustment costs, $NPV_0({\\bf h_0^*})$.
-Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.", dependson="quadcosts", fig.width=4, fig.height=3}
-
-ggplot(fees, aes(c2, (npv0-value)/npv0, lty=variable)) + 
-  geom_line() + 
-  geom_hline(aes(hintercept=reduction), linetype=4) + 
-  xlab("penalty coefficient") +
-  ylab("Reduction in net present value") + 
-  theme_tufte()
-
-```
 

### 2014-06-02 manuscripts/components/install.R

@@ -1,14 +1,17 @@
 #!/usr/bin/Rscript
 library("methods")
-
-# Install packrat if not available
-if(!require("devtools")) install.packages("devtools")
-if(!require("packrat")) devtools::install_github("rstudio/packrat")
-
 # Let packrat set up the manuscript dependencies
-packrat::packify()
-source(".Rprofile"); readRenviron(".Renviron")
-packrat::restore()
-source(".Rprofile"); readRenviron(".Renviron")
-
-
+if(file.exists("packrat.sources") && file.exists(".Rprofile") && file.exists(".Renviron")){
+  if(exists("initPackrat"))
+    initPackrat()
+  else 
+    NULL
+} else {
+# Install packrat if not available
+  if(!require("devtools")) install.packages("devtools")
+  if(!require("packrat")) devtools::install_github("rstudio/packrat")
+  packrat::packify()
+  source(".Rprofile"); readRenviron(".Renviron")
+  packrat::restore()
+  source(".Rprofile"); readRenviron(".Renviron")
+}

### 2014-06-03 manuscripts/manuscript.Rmd
rebuild cache
add code for crosscor

@@
 ```{r npv_table, dependson="print_npv", results='asis'} 
-# verify that we have fine enough c_2 sampling to hit about 75% NPV0 on each penalty form
-# pandoc.table(print_npv)
+#pandoc.table(print_npv)
 ```
@@
 }
+```
+
+```{r cross-correlations}
+#stats_xcor <- dt[, xcor(fishstock, harvest), by=c("penalty_fn", "reps")]
 ```

### 2014-06-03 manuscripts/manuscript.Rmd
fix inline code chunk

@@
 
-```{r cross-correlations}
-#stats_xcor <- dt[, xcor(fishstock, harvest), by=c("penalty_fn", "reps")]
-```
-
 ```{r helper_fn_3}
@@
 
-$$
 \begin{equation}
@@
 \end{equation}
-$$
 
@@
 
-$$\begin{equation}
+\begin{equation}
 \Pi_0(N_t,h_t) = p h_t -  c_0 E_t \label{eq:annual_netrevenue}
 \end{equation}
-$$
 
@@
 we assume that these are constants with $p>0$ and $c_0>0$. (Examples 
-shown here use $p$= `r p` and $c_0$ = `r_c0`.) 
+shown here use $p$= `r price` and $c_0$ = `r c0`.) 
 <!-- Mention R code provided to test other values? Do we need to test other values?

### 2014-06-03 manuscripts/manuscript.Rmd
edits to Fig4, working on code for table 1

@@
 apples })
-write.csv(reduction_table, "../data/reduction_table.csv")
+write.csv(reduction_table, "components/data/reduction_table.csv")
 ````
@@
 
-```{r helper_fn_2} 
-# Helper functions to extract the summary stats in different variables
-stats_harvest <- function(dt){
-v <- dt[,var(harvest), by=c("penalty_fn", "reps")]
-acor <- dt[,acf(harvest, plot=F)$acf[2], by=c("penalty_fn", "reps")]
-df <- cbind(v, acor$V1)
-setnames(df, c("V1", "V2"), c("var", "acor")) # names are nice
-df
-}
+```{r fig4-stats}
+summary_stats <- function(dt){
+ harvest_var <- dt[,var(harvest), by=c("penalty_fn", "reps")]$V1
+ harvest_acor <- dt[,acf(harvest, plot=F)$acf[2], by=c("penalty_fn", "reps")]$V1
+ stock_var <- dt[,var(fishstock), by=c("penalty_fn", "reps")]$V1
+ stock_acor <- dt[,acf(fishstock, plot=F)$acf[2], by=c("penalty_fn", "reps")]$V1
+ xcor <- dt[, ccf(fishstock, harvest, plot=FALSE)$acf[2], by=c("penalty_fn", "reps")]
+ setnames(xcor, "V1", "cross-correlation")
 
-stats_fishstock <- function(dt){
-v <- dt[,var(fishstock), by=c("penalty_fn", "reps")]
-acor <- dt[,acf(fishstock, plot=F)$acf[2], by=c("penalty_fn", "reps")]
-df <- cbind(v, acor$V1)
-setnames(df, c("V1", "V2"), c("var", "acor")) # names are nice
-df
+ df <- data.frame('stock.variance' = stock_var, 
+                  'stock.autocorrelation' = stock_acor, 
+                  'harvest.variance' = harvest_var, 
+                  'harvest.autocorrelation' = harvest_acor, 
+                  xcor)
+
+ # long format
+ melt(df, id=c("penalty_fn", "reps"))
  }
@@
 
-```{r helper_fn_3}
-#' a simple function for reorganizing the data over the different "faction-lost" levels
-get_trends <- function(tmp2){
-  out <- melt(tmp2, id=c("reps", "var", "acor"))
-  colnames(out) = c("reps", "var", "acor", "nothing", "penalty", "index")
-  out <- cbind(out[c(1,2,3,5)], fraction = frac_lost[out$index])
-  out <- data.table(out)
-  Ev = out[,mean(var),by=c('penalty', 'fraction')]
-  SDv = out[,sd(var),by=c('penalty', 'fraction')]
-  Ea = out[,mean(acor),by=c('penalty', 'fraction')]
-  SDa = out[,sd(acor),by=c('penalty', 'fraction')]
-  harvest_trends <- data.table(penalty = Ev$penalty, 
-                               fraction = Ev$fraction, 
-                               Ev = Ev$V1, Ea = Ea$V1, 
-                               SDv=SDv$V1, SDa = SDa$V1)
-}
+```{r summary-stat-calc}
+stats_summaries <- lapply(sims_at_each_apple, summary_stats)
+# reformat list of data-frames as data frame with apple coef as a factor
+stats_df <- melt(stats_summaries, id=names(stats_summaries[[1]]))
+stats_df$L1 <- frac_lost[stats_df$L1]
+names(stats_df) <- c("penalty_fn", "reps", "variable", "value", "penalty_fraction")
 ```
 
-```{r Figure4_harvest}
-sims_at_each_apple <- lapply(frac_lost, fig4)
-harvest_stats <- lapply(sims_at_each_apple, stats_harvest)
-harvest_trends <- get_trends(harvest_stats)
+```{r split-factors}
+# make statistic and timeseries separate factors
+figure4_df <- stats_df
+figure4_df$statistic <- figure4_df$variable
+figure4_df$timeseries <- figure4_df$variable
+stat_map <- c(harvest.variance = 'variance', stock.variance='variance', stock.autocorrelation='autocor',harvest.autocorrelation='autocor', cross.correlation='cross.correlation')
+series_map <- c(harvest.variance = 'harvest', stock.variance='stock', stock.autocorrelation='stock',harvest.autocorrelation='harvest', cross.correlation='both')
+
+figure4_df$statistic <- stat_map[figure4_df$statistic]
+figure4_df$timeseries <- series_map[figure4_df$timeseries]
 ```
 
-```{r fishstock_trends}
-fishstock_stats <- lapply(sims_at_each_apple, stats_fishstock)
-fishstock_trends <- get_trends(fishstock_stats)
+```{r table-calc}
+source("componetns/compute_error_table.R")
+sigmas <- c(0.01, 0.1, 0.2)
+reductions <- 1:3
+out <- lapply(sigmas, function(s){
+  lapply(reductions, function(r){
+    compute_error_table(r = r, sigma = s)    
+  })
+})
+
+who <- names(out[[1]][[1]])
+error_df <- melt(out, id=who)              
+```
+
+```{r clean-table}
+df <- error_df[2:8]
+who <- c("penalty_fn", "ignore_fraction", "assume_fraction", "sigma_g", "reduction")
+df2 <- melt(df, id=who)
+who <- c("penalty_fn", "sigma_g", "reduction", "variable", "value")
+df3 <- melt(df2, id=who)
+names(df3) <- c("penalty_fn", "sigma_g", "reduction", "variable", "value", "fraction_variable", "fraction")
+df3$reduction <- as.factor(df3$reduction)
+
+#ggplot(df3) + geom_line(aes(sigma_g, value, col=reduction, lty=variable)) + facet_wrap(~penalty_fn, scales="free_y") 
 ```
@@
 autocorrelation of harvests and stock sizes through time; and on the
-cross-correlation of harvests and stock sizes through time. <!-- NOTE Are we showing cross-correlations or not?-->
+cross-correlation of harvests and stock sizes through time. <!-- NOTE Are we showing cross-correlations or not? --> <!-- See figure 4, probably not-->
 
@@
 
-Interestingly, as suggested by the realization in Fig. 3, including a
+Interestingly, as suggested by the realization in Fig. 2, including a
 fixed cost of policy adjustment increases the variation in harvests
@@
 
-Same comments as before on labeling the curves and detailing in the figure captions. Axis labels and things all also need work.
+Same comments as before on labeling the curves and detailing in the figure captions. Axis labels and things all also need work. - Paul
+-->
+<!--
+Added cross-correlations but shows no pattern.  Also have version with 2x2 as single plot.  feedback on aesthetics welcome.  - CB
 -->
 
-```{r Figure_4, fig.cap="(a) Variance of optimal harvest rates through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.
-(b) Autocorrelation of optimal harvest rates through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=3, fig.width=8}
-Fig4a <- ggplot(harvest_trends, 
-                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
-  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
-  geom_line() + 
-  xlab("Fraction of NPV lost to costs") +
-  scale_x_continuous(limits=c(0, 0.4)) + theme_tufte()
+```{r Figure_4, fig.cap="Variance and autocorrelation of stock dynamics and harvest dynamics, as well as cross-correlation between stock and harvest dynamics, as a function of the penalty coefficient.
+Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8}
 
-Fig4b <- ggplot(harvest_trends, 
-                aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
-  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
-  geom_line() + xlab("Fraction of NPV lost to costs")+
-  scale_x_continuous(limits=c(0, 0.4)) + theme_tufte()
+with_xcor_plot <- 
+ggplot(figure4_df, aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn)) + 
+  facet_wrap(~variable, scales = "free_y") +
+  stat_summary(fun.y = mean, 
+               fun.ymin = function(x) mean(x) - sd(x), 
+               fun.ymax = function(x) mean(x) + sd(x), 
+               geom = "ribbon", alpha=0.3, colour=NA) +
+  stat_summary(fun.y = mean, geom = "line")
+with_xcor_plot
 
-multiplot(Fig4a, Fig4b, cols=2)
-```
-
-```{r Figure_5, fig.cap = "(a) Variance of optimal stock sizes through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.
-(b) Autocorrelation of optimal stock sizes through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=3, fig.width=8}
-Fig5a <- ggplot(fishstock_trends, 
-                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
-  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
-  geom_line() + xlab("Fraction of NPV lost to costs")+
-  scale_x_continuous(limits=c(0, 0.4))  + theme_tufte()
-
-Fig5b <- ggplot(fishstock_trends, 
-                aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
-  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
-  geom_line() + xlab("Fraction of NPV lost to costs") +
-  scale_x_continuous(limits=c(0, 0.4))  + theme_tufte()
-
-multiplot(Fig5a, Fig5b, cols=2)
+ggplot(subset(figure4_df, statistic != "cross.correlation"), aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn))  +
+  stat_summary(fun.y = mean, 
+               fun.ymin = function(x) mean(x) - sd(x), 
+               fun.ymax = function(x) mean(x) + sd(x), 
+               geom = "ribbon", alpha=0.3, colour=NA) +
+  stat_summary(fun.y = mean, geom = "line") + 
+  facet_grid(statistic ~ timeseries, scale="free") + theme_bw()
 
@@
 policy change being implemented ($\Pi_2$).
+
+```{r Table1, results="asis", echo=FALSE}
+df4 <- error_df[c(1,2,4,6,7)]
+plyr::arrange(df4, penalty_fn)
+pandoc.table(df4)
+```
 

### 2014-06-03 manuscripts/components/compute_error_table.R

@@ -1,0 +1,103 @@
+compute_error_table <- function(r, sigma){
+  reduction_range = c(.1, .2, .3)
+  reduction <- reduction_range[r]
+  
+  price = 10
+  c0 = 0
+  profit <- profit_harvest(price = price, c0 = c0, c1 = 0)
+  c2 <- seq(0, 50, length.out=100)
+  
+  
+  delta <- 0.05               # economic discounting rate
+  OptTime <- 20               # stopping time
+  gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
+  sigma_g <- sigma              # Noise in population growth
+  reward <- 0                 # bonus for satisfying the boundary condition
+  z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
+  z_m <- function() 1         # No measurement noise, 
+  z_i <- function() 1         # No implemenation noise
+  f <- BevHolt                # Select the state equation
+  pars <- c(1.5, 0.05)        # parameters for the state equation
+  K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
+  xT <- 0                     # boundary conditions
+  x0 <- K
+  x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
+  h_grid <- seq(0.01, 0.8 * K, length = gridsize)  
+  
+  
+  SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
+  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
+                       profit, delta, reward=reward)
+  
+  L1 <- function(c2) function(h, h_prev)  c2 * abs(h - h_prev) 
+  fixed <-  function(c2) function(h, h_prev) c2 * as.numeric( !(h == h_prev) )
+  L2 <- function(c2) function(h, h_prev)  c2 * (h - h_prev) ^ 2
+  none <- function(h, h_prev)  0
+  
+  
+  reduction_table <- read.csv('reduction_table.csv', row.names=1)
+  apples <-   reduction_table[[r]]
+  names(apples) <- rownames(reduction_table)
+  
+  L2_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
+                            profit, delta, reward, penalty = L2(apples[["L2"]]))
+  L1_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
[…]

### 2014-06-03 manuscripts/manuscript.Rmd
ugh, error table already computed. try clean

@@
     affiliation: cstar
-    email: 
+    email: cboettig (at) gmail.com
     footnote: Corresponding author
@@
 ```{r dependencies, include=FALSE}
-source("components/install.R")
+#source("components/install.R")
 ```
@@
 library("reshape2")
+library("plyr")
 library("ggplot2")
@@
 #ggplot(fees, aes(c2, value, col=variable)) + geom_point() + geom_line()
-````
-
-```{r apples_plot, dependson="quadcosts"}
-#ggplot(fees, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
 ````
@@
 
-```{r}
-v <- dt[,var(harvest), by="penalty_fn"]
-var <- v$V1
-names(var) <- v$penalty_fn
-acor <- dt[,acf(harvest, plot=F)$acf[2], by="penalty_fn"]$V1
-names(acor) <- names(var)
-out <- rbind(var=var, a=acor)
-```
-
-```{r}
-frac_lost <- seq(0,1, length=20)
-```
-
 ```{r helper_fn_1}
@@
 
-```{r fig4-stats}
+```{r sim_at_each_apple}
+frac_lost <- seq(0,1, length=20)
+sims_at_each_apple <- lapply(frac_lost, fig4)
+```
+
+```{r stats-defs}
 summary_stats <- function(dt){
@@
 
-```{r summary-stat-calc}
+```{r summary-stat-calc, dependson="sim_at_each_apple"}
 stats_summaries <- lapply(sims_at_each_apple, summary_stats)
@@
 figure4_df$timeseries <- series_map[figure4_df$timeseries]
-```
-
-```{r table-calc}
-source("componetns/compute_error_table.R")
-sigmas <- c(0.01, 0.1, 0.2)
-reductions <- 1:3
-out <- lapply(sigmas, function(s){
-  lapply(reductions, function(r){
-    compute_error_table(r = r, sigma = s)    
-  })
-})
-
-who <- names(out[[1]][[1]])
-error_df <- melt(out, id=who)              
-```
-
-```{r clean-table}
-df <- error_df[2:8]
-who <- c("penalty_fn", "ignore_fraction", "assume_fraction", "sigma_g", "reduction")
-df2 <- melt(df, id=who)
-who <- c("penalty_fn", "sigma_g", "reduction", "variable", "value")
-df3 <- melt(df2, id=who)
-names(df3) <- c("penalty_fn", "sigma_g", "reduction", "variable", "value", "fraction_variable", "fraction")
-df3$reduction <- as.factor(df3$reduction)
-
-#ggplot(df3) + geom_line(aes(sigma_g, value, col=reduction, lty=variable)) + facet_wrap(~penalty_fn, scales="free_y") 
 ```
@@
 
-```{r Table1, results="asis", echo=FALSE}
-df4 <- error_df[c(1,2,4,6,7)]
-plyr::arrange(df4, penalty_fn)
-pandoc.table(df4)
+```{r table-caption}
+caption = "Table 1: Column 'ignoring' shows the results of ignoring a adjustment penalty when it is present, Column 'assuming' shows the results of assuming an adjustment cost when it is absent.
+Values (ignoring, assuming) are given as the expected net present value (ENPV) as a fraction of that when no penalty is present, ENPV0.
+Percent reduction refers to penalty coefficient being calibrated to achieve the given percent reduction relative to ENPV0 when the penalty is optimally accounted for.
+Column c2 shows the coefficient chosen to achieve that reduction.
+Comparing the second and third columns shows that ignoring a real cost is a significantly graver error, particularly in the case of quadratic (L2) costs."
+```
+
+```{r clean-table}
+who <- c("penalty_fn", "ignore_fraction", "assume_fraction", "reduction")
+table1 <- arrange(subset(error_df, sigma_g == 0.01)[who], penalty_fn) 
+pandoc.table(table1, caption=caption)
+
+table1_long <- melt(table1, id = c('penalty_fn', 'reduction'))
+table1_long$reduction <- as.factor(table1_long$reduction)
+ggplot(table1_long, aes(penalty_fn, value, fill = variable)) + geom_bar(stat="identity", position="dodge") + facet_wrap(~ reduction) + theme_bw()
 ```
@@
 -->
-
-      penalty fn     ignoring   assuming   percent reduction      c2
-  --- ------------ ---------- ---------- ------------------- -------
-    1 L1                 0.81       1.00                0.10    0.40
-    2 L1                 0.62       0.99                0.20    0.81
-    3 L1                 0.35       0.97                0.30    2.02
-    4 L2                 0.68       0.95                0.10    0.81
-    5 L2                 0.44       0.89                0.20    1.62
-    6 L2                -0.28       0.81                0.30    2.83
-    7 fixed              0.78       1.00                0.10    3.64
-    8 fixed              0.56       0.99                0.20    8.08
-    9 fixed              0.31       0.97                0.30   12.93
-
-  Table 1: Column 'ignoring' shows the results of ignoring a adjustment penalty when it is present, Column 'assuming' shows the results of assuming an adjustment cost when it is absent.
-Values (ignoring, assuming) are given as the expected net present value (ENPV) as a fraction of that when no penalty is present, ENPV0.
-Percent reduction refers to penalty coefficient being calibrated to achieve the given percent reduction relative to ENPV0 when the penalty is optimally accounted for.
-Column c2 shows the coefficient chosen to achieve that reduction.
-Comparing the second and third columns shows that ignoring a real cost is a significantly graver error, particularly in the case of quadratic (L2) costs.
 

### 2014-06-03 manuscripts/components/compute_error_table.R

@@ -1,103 +1,0 @@
-compute_error_table <- function(r, sigma){
-  reduction_range = c(.1, .2, .3)
-  reduction <- reduction_range[r]
-  
-  price = 10
-  c0 = 0
-  profit <- profit_harvest(price = price, c0 = c0, c1 = 0)
-  c2 <- seq(0, 50, length.out=100)
-  
-  
-  delta <- 0.05               # economic discounting rate
-  OptTime <- 20               # stopping time
-  gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
-  sigma_g <- sigma              # Noise in population growth
-  reward <- 0                 # bonus for satisfying the boundary condition
-  z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-  z_m <- function() 1         # No measurement noise, 
-  z_i <- function() 1         # No implemenation noise
-  f <- BevHolt                # Select the state equation
-  pars <- c(1.5, 0.05)        # parameters for the state equation
-  K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
-  xT <- 0                     # boundary conditions
-  x0 <- K
-  x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
-  h_grid <- seq(0.01, 0.8 * K, length = gridsize)  
-  
-  
-  SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
-  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
-                       profit, delta, reward=reward)
-  
-  L1 <- function(c2) function(h, h_prev)  c2 * abs(h - h_prev) 
-  fixed <-  function(c2) function(h, h_prev) c2 * as.numeric( !(h == h_prev) )
-  L2 <- function(c2) function(h, h_prev)  c2 * (h - h_prev) ^ 2
-  none <- function(h, h_prev)  0
-  
-  
-  reduction_table <- read.csv('reduction_table.csv', row.names=1)
-  apples <-   reduction_table[[r]]
-  names(apples) <- rownames(reduction_table)
-  
-  L2_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
-                            profit, delta, reward, penalty = L2(apples[["L2"]]))
-  L1_policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
[…]

### 2014-06-03 manuscripts/manuscript.Rmd
fixed table data and figure

@@
 theme_set(theme_tufte())
-ncpu = 1
+ncpu = 24
 ```
@@
 apples_index <- index$V1
-names(apples_index) = index$variable
+names(apples_index) <- index$variable
 apples <- c2[index$V1]
-````
-
-```{r reductions}
-reduction_table <- sapply(c("0.10" = 0.10, "0.20" = 0.20, "0.30" = 0.30), function(reduction){
-index <- dt_npv[,closest(reduction, (npv0-value)/npv0), by=variable]
-apples <- c2[index$V1]
-names(apples) = index$variable
-apples })
-write.csv(reduction_table, "components/data/reduction_table.csv")
+names(apples) <- index$variable
 ````
@@
 ```
+
+```{r errors-table}
+
+source("components/compute_error_table.R")
+
+reduction_list <- c(.1, .15, .2, .25, .3)
+out <- lapply(reduction_list, function(r)
+    compute_error_table(r = r))   
+who <- names(out[[1]])
+error_df <- melt(out, id=who)
+
+````
 
@@
 Percent reduction refers to penalty coefficient being calibrated to achieve the given percent reduction relative to ENPV0 when the penalty is optimally accounted for.
-Column c2 shows the coefficient chosen to achieve that reduction.
 Comparing the second and third columns shows that ignoring a real cost is a significantly graver error, particularly in the case of quadratic (L2) costs."
@@
 
-```{r clean-table}
+```{r Table1}
 who <- c("penalty_fn", "ignore_fraction", "assume_fraction", "reduction")
-table1 <- arrange(subset(error_df, sigma_g == 0.01)[who], penalty_fn) 
+table1 <- arrange(error_df[who], reduction) 
+names(table1) = c("penalty.fn", "ignoring", "assuming", "reduction")
 pandoc.table(table1, caption=caption)
+```
 
-table1_long <- melt(table1, id = c('penalty_fn', 'reduction'))
+```{r Table1-Figure, fig.cap="Relative cost of ignoring adjustment costs when they are present ('ignoring', red) vs assuming the adjustment costs when they are absent ('assuming', blue), shown by penalty function over increasing magnitudes of cost.
+All values are relative to the cost-free adjustment optimum, NPV0.
+In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present.
+The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs."}
+table1_long <- melt(table1, id = c('penalty.fn', 'reduction'))
 table1_long$reduction <- as.factor(table1_long$reduction)
-ggplot(table1_long, aes(penalty_fn, value, fill = variable)) + geom_bar(stat="identity", position="dodge") + facet_wrap(~ reduction) + theme_bw()
+ggplot(table1_long, aes(penalty.fn, value, fill = variable)) + geom_bar(stat="identity", position="dodge") + facet_wrap(~ reduction) + theme_bw()
 ```

### 2014-06-03 manuscripts/components/compute_error_table.R

@@ -1,0 +1,57 @@
+compute_error_table <- function(r){
+  
+  index <- dt_npv[,closest(r, (npv0-value)/npv0), by=variable]
+  apples_index <- index$V1
+  names(apples_index) <- index$variable
+  
+  L2_policy <- policies$L2[[apples_index["L2"]]]$D
+  L1_policy <- policies$L1[[apples_index["L1"]]]$D
+  fixed_policy <- policies$fixed[[apples_index["fixed"]]]$D
+
+  reps <- 1:100
+  names(reps) = paste("rep", 1:length(reps), sep="_") # treat as a factor
+  seeds <- 1:100
+  sims <- list(
+    L1 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
+                                                 L1_policy, z_g, z_m, z_i, 
+                                                 opt$D, profit=profit, penalty=L1(c2[apples_index["L1"]]), seed=seeds[x])), 
+    L2 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
+                                                 L2_policy, z_g, z_m, z_i, 
+                                                 opt$D, profit=profit, penalty=L2(c2[apples_index["L2"]]), seed=seeds[x])),
+    fixed = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
+                                                    fixed_policy, z_g, z_m, z_i, 
+                                                    opt$D, profit=profit, penalty=fixed(c2[apples_index["fixed"]]), seed=seeds[x]))
+    
+  )
+
+
+#Make data tidy (melt), fast (data.tables), and nicely labeled.
+  dat <- melt(sims, id=names(sims[[1]][[1]]))  
+  dt <- data.table(dat)
+  setnames(dt, "L2", "replicate") # names are nice
+  setnames(dt, "L1", "penalty_fn") # names are nice
+  
+  
+  
+  optimal_cost <- dt[, sum(profit_fishing - policy_cost), by=penalty_fn ] 
+  ignore_when_present <- dt[, sum(profit_fishing_alt - policy_cost_alt), by=penalty_fn] 
+  assume_when_absent <- dt[, sum(profit_fishing), by=penalty_fn]
+  optimal_free <- dt[, sum(profit_fishing_alt), by=penalty_fn]
+  
+  # Normalize by the optimal 
+  ignore_fraction <- ignore_when_present$V1/optimal_free$V1 # common normalization
[…]

### 2014-06-04 manuscripts/manuscript.Rmd
source code externally (easier for collaborators to edit)

@@
     template: components/elsarticle.latex
+    fig_caption: true
 ---
 
-<!-- CODE -->
-
-```{r dependencies, include=FALSE}
+```{r dependencies, include=FALSE, cache=FALSE}
 #source("components/install.R")
 ```
-
-```{r caching, include=FALSE}
-library("methods")
-library("knitr")
-basename <- "manuscript"
-opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
-               cache.path = paste("components/cache/", basename, "/", sep=""))
-opts_chunk$set(cache = 2)
-opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, 
-               comment = NA, verbose = TRUE, echo=FALSE)
-
-# PDF-based figures
-opts_chunk$set(dev='pdf')
+```{r analysis, include=FALSE}
+source("components/analysis.R")
 ```
-
-```{r libraries, include=FALSE, cache=FALSE}
-rm(list=ls())
-library("rmarkdown")
-library("pdgControl")
-library("reshape2")
-library("plyr")
-library("ggplot2")
-library("data.table")
-library("pander")
-library("cboettigR")
-library("ggthemes")
-library("snowfall")
-theme_set(theme_tufte())
-ncpu = 24
-```
-
-``` {r profit_model}
-price = 10
-c0 = 30
-profit <- profit_harvest(price = price, c0 = c0, c1 = 0)
-```
-
-```{r c2_grid}
-c2 <- exp(seq(0, log(41), length.out = 40))-1
-c2 <- seq(0, 40, length.out=100)
-```
-
-```{r reduction}
-reduction <- 0.25 
-```
-
-```{r setup}
-seed <- 123                 # Random seed (replicable results)
-delta <- 0.05               # economic discounting rate
-OptTime <- 20               # stopping time
-gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
-sigma_g <- 0.2              # Noise in population growth
-reward <- 0                 # bonus for satisfying the boundary condition
-z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() 1         # No measurement noise, 
-z_i <- function() 1         # No implemenation noise
-f <- BevHolt                # Select the state equation
-pars <- c(1.5, 0.05)        # parameters for the state equation
-K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
-xT <- 0                     # boundary conditions
-x0 <- K
-x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
-h_grid <- seq(0.01, 0.8 * K, length = gridsize)  
-````
-
-```{r reed, dependson=c("setup", "profit_model")}
-SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
-opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
-                     profit, delta, reward=reward)
-````
-
-```{r fees}
-L1 <- function(c2) function(h, h_prev)  c2 * abs(h - h_prev) 
-fixed <-  function(c2) function(h, h_prev) c2 * as.numeric( !(h == h_prev) )
-L2 <- function(c2) function(h, h_prev)  c2 * (h - h_prev) ^ 2
-none <- function(h, h_prev)  0
-penaltyfns <- list(L2=L2, L1=L1, fixed=fixed)
-````
-
-```{r parallel, include=FALSE}
-sfInit(cpu=ncpu, parallel=T)
-sfLibrary(pdgControl)
-sfExportAll()
-````
-
-``` {r bigloop, dependson=c("setup", "reed", "fees", "profit_model", "c2_grid")}
-policies <- lapply(penaltyfns, function(penalty){
-  sfLapply(c2, function(c2){
-      policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
-                   profit, delta, reward, penalty = penalty(c2))
-      }
-  )
-})
-````
-
-```{r, dependson="quadcosts"}
-i <- which(x_grid > K)[1]
-fees <- 
-lapply(policies, function(penalty) 
-  sapply(penalty, function(c2_run)
-    max(c2_run$V[i,]) # Would be penalty_free_V originally   ## this isn't correct for asym cases
-  )
-)
-```
-
-``` {r npv-plot, dependson="quadcosts"}
-npv0 <- max(fees$L1) # all have same max, at c2=0 
-fees <- data.frame(c2=c2,fees)
-fees <- melt(fees, id="c2")
-fees <- subset(fees, variable %in% c("L1", "L2", "fixed"))
-
-#ggplot(fees, aes(c2, value, col=variable)) + geom_point() + geom_line()
-````
-
-```{r apples, dependson=c("quadcosts", "reduction")}
-closest <- function(x, v){
-  which.min(abs(v-x))
-}
-dt_npv <- data.table(fees)
-index <- dt_npv[,closest(reduction, (npv0-value)/npv0), by=variable]
-apples_index <- index$V1
-names(apples_index) <- index$variable
-apples <- c2[index$V1]
-names(apples) <- index$variable
-````
-
-```{r print_npv, dependson="apples"}
-setkey(dt_npv, variable)
-values <- apply(index, 1, function(x) dt_npv[x[1], ][as.integer(x[2]), ]$value)
-percent.error <- (values - ((1-reduction)*npv0)) / ((1-reduction)*npv0)* 100
-print_npv <- data.frame(model=index$variable, "value realized"=values, 
-                        "percent of npv0" = 100*values/npv0, "percent error"=percent.error)
-
-```
-
-```{r npv_table, dependson="print_npv", results='asis'} 
-#pandoc.table(print_npv)
-```
-
-```{r policynames}
-L2_policy <- policies$L2[[apples_index["L2"]]]$D
-L1_policy <- policies$L1[[apples_index["L1"]]]$D
-fixed_policy <- policies$fixed[[apples_index["fixed"]]]$D
-```
-
-```{r simulate_policy, dependson=c("policynames", "apples")}
-reps <- 1:100
-names(reps) = paste("rep", 1:length(reps), sep="_") # treat as a factor
-seeds <- 1:100
-sims <- list(
-  L1 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
-                      L1_policy, z_g, z_m, z_i, 
-                      opt$D, profit=profit, penalty=L1(apples["L1"]), seed=seeds[x])), 
-  L2 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
-                      L2_policy, z_g, z_m, z_i, 
-                      opt$D, profit=profit, penalty=L2(apples["L2"]), seed=seeds[x])),
-  fixed = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
-                         fixed_policy, z_g, z_m, z_i, 
-                         opt$D, profit=profit, penalty=fixed(apples["fixed"]), seed=seeds[x]))
-
-)
-```
-
-```{r tidy, dependson="simulate_policy"}
-#Make data tidy (melt), fast (data.tables), and nicely labeled.
-dat <- melt(sims, id=names(sims[[1]][[1]]))  
-dt <- data.table(dat)
-setnames(dt, "L2", "replicate") # names are nice
-setnames(dt, "L1", "penalty_fn") # names are nice
-```
-
-```{r profit_calcs, dependson="tidy"}
-# Profit when accounting for penalty when present
-optimal_cost <- dt[, sum(profit_fishing - policy_cost), by=penalty_fn ]
-
-# Profit when ignoring penalty when present
-ignore_when_present <- dt[, sum(profit_fishing_alt - policy_cost_alt), by=penalty_fn]
-
-# Profit when assuming penalty when it is absent
-assume_when_absent <- dt[, sum(profit_fishing), by=penalty_fn]
-
-# Profit when ignoring penalty when it is absent
-optimal_free <- dt[, sum(profit_fishing_alt), by=penalty_fn]
-
-# Normalize by the optimal 
-ignore_fraction <- ignore_when_present$V1/optimal_free$V1 # common normalization
-assume_fraction <- assume_when_absent$V1/optimal_free$V1
-assume_when_absent <- cbind(assume_when_absent, assume_fraction = assume_fraction, normalize_optimal_free=optimal_free$V1, normalize_optimal_cost = optimal_cost$V1)
-ignore_when_present <- cbind(ignore_when_present, ignore_fraction = ignore_fraction)
-
-# Name and merge columns
-setnames(ignore_when_present, "V1", "ignore_cost")
-setnames(assume_when_absent, "V1", "assume_cost")
-error_costs <- merge(ignore_when_present, assume_when_absent, "penalty_fn")
-
-# print_npv                             # theoretically acheivable profits under these costs
-# optimal_cost$V1/optimal_free$V1       # actually realized
-
-error_costs <- cbind(error_costs, sigma_g = sigma_g, reduction = reduction)
-
-```
-
-```{r helper_fn_1}
-fig4 <- function(fraction_lost){
-closest <- function(x, v){
-  which.min(abs(v-x))
-}
-dt_npv <- data.table(fees)
-index <- dt_npv[,closest(fraction_lost, (npv0-value)/npv0), by=variable]
-apples_index <- index$V1
-names(apples_index) = index$variable
-apples <- c2[index$V1]
-names(apples) = index$variable
-
-L2_policy <- policies$L2[[apples_index["L2"]]]$D
-L1_policy <- policies$L1[[apples_index["L1"]]]$D
-fixed_policy <- policies$fixed[[apples_index["fixed"]]]$D
-free_increase_policy <- policies$free_increase[[apples_index["free_increase"]]]$D
-free_decrease_policy <- policies$free_decrease[[apples_index["free_decrease"]]]$D
-quad_policy <- policies$quad[[apples_index["quad"]]]$D
-
-quad_profit <- profit_harvest(price = price, c0 = c0, c1 = apples["quad"]) 
-sims <- lapply(1:50, function(reps) list(
-  L1 = simulate_optim(f, pars, x_grid, h_grid, x0, 
-                      L1_policy, z_g, z_m, z_i, 
-                      opt$D, profit=profit, penalty=L1(apples["L1"])), 
-  L2 = simulate_optim(f, pars, x_grid, h_grid, x0, 
-                      L2_policy, z_g, z_m, z_i, 
-                      opt$D, profit=profit, penalty=L2(apples["L2"])),
-  fixed = simulate_optim(f, pars, x_grid, h_grid, x0, 
-                         fixed_policy, z_g, z_m, z_i, 
-                         opt$D, profit=profit, penalty=fixed(apples["fixed"]))
-#  increase = simulate_optim(f, pars, x_grid, h_grid, x0, 
-#                            free_increase_policy, z_g, z_m, z_i, 
-#                            opt$D, profit=profit, penalty= free_increase(apples["increase"])),
-#  decrease = simulate_optim(f, pars, x_grid, h_grid, x0, 
-#                            free_decrease_policy, z_g, z_m, z_i, 
-#                            opt$D, profit=profit, penalty= free_decrease(apples["decrease"])),
-#  quad = simulate_optim(f, pars, x_grid, h_grid, x0, 
-#                            quad_policy, z_g, z_m, z_i, 
-#                            opt$D, profit=quad_profit, penalty= none)
-  ))
-
-  #Make data tidy (melt), fast (data.tables), and nicely labeled.
-  dat <- melt(sims, id=names(sims[[1]][[1]]))  
-  dt <- data.table(dat)
-  setnames(dt, "L1", "reps") # names are nice
-  setnames(dt, "L2", "penalty_fn") # names are nice
-
-  dt
-}
-```
-
-```{r sim_at_each_apple}
-frac_lost <- seq(0,1, length=20)
-sims_at_each_apple <- lapply(frac_lost, fig4)
-```
-
-```{r stats-defs}
-summary_stats <- function(dt){
- harvest_var <- dt[,var(harvest), by=c("penalty_fn", "reps")]$V1
- harvest_acor <- dt[,acf(harvest, plot=F)$acf[2], by=c("penalty_fn", "reps")]$V1
- stock_var <- dt[,var(fishstock), by=c("penalty_fn", "reps")]$V1
- stock_acor <- dt[,acf(fishstock, plot=F)$acf[2], by=c("penalty_fn", "reps")]$V1
- xcor <- dt[, ccf(fishstock, harvest, plot=FALSE)$acf[2], by=c("penalty_fn", "reps")]
- setnames(xcor, "V1", "cross-correlation")
-
- df <- data.frame('stock.variance' = stock_var, 
-                  'stock.autocorrelation' = stock_acor, 
-                  'harvest.variance' = harvest_var, 
-                  'harvest.autocorrelation' = harvest_acor, 
-                  xcor)
-
- # long format
- melt(df, id=c("penalty_fn", "reps"))
- }
-```
-
-```{r summary-stat-calc, dependson="sim_at_each_apple"}
-stats_summaries <- lapply(sims_at_each_apple, summary_stats)
-# reformat list of data-frames as data frame with apple coef as a factor
-stats_df <- melt(stats_summaries, id=names(stats_summaries[[1]]))
-stats_df$L1 <- frac_lost[stats_df$L1]
-names(stats_df) <- c("penalty_fn", "reps", "variable", "value", "penalty_fraction")
-```
-
-```{r split-factors}
-# make statistic and timeseries separate factors
-figure4_df <- stats_df
-figure4_df$statistic <- figure4_df$variable
-figure4_df$timeseries <- figure4_df$variable
-stat_map <- c(harvest.variance = 'variance', stock.variance='variance', stock.autocorrelation='autocor',harvest.autocorrelation='autocor', cross.correlation='cross.correlation')
-series_map <- c(harvest.variance = 'harvest', stock.variance='stock', stock.autocorrelation='stock',harvest.autocorrelation='harvest', cross.correlation='both')
-
-figure4_df$statistic <- stat_map[figure4_df$statistic]
-figure4_df$timeseries <- series_map[figure4_df$timeseries]
-```
-
-```{r errors-table}
-
-source("components/compute_error_table.R")
-
-reduction_list <- c(.1, .15, .2, .25, .3)
-out <- lapply(reduction_list, function(r)
-    compute_error_table(r = r))   
-who <- names(out[[1]])
-error_df <- melt(out, id=who)
-
-````
-
-<!-- ENDCODE -->
 
@@
 The horizontal line indicates a value of the stock that is reduced by `r reduction * 100`% from the maximum expected value in the absence of policy adjustment costs, $NPV_0({\\bf h_0^*})$.
-Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.", dependson="quadcosts", fig.width=4, fig.height=3}
-
+Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.", dependson="quadcosts", fig.width=4, fig.height=3, cache=FALSE}
 ggplot(fees, aes(c2, (npv0-value)/npv0, lty=variable)) + 
   geom_line() + 
-  geom_hline(aes(hintercept=reduction), linetype=4) + 
+  geom_hline(aes(yintercept=reduction), linetype=4) + 
   xlab("penalty coefficient") +
-  ylab("Reduction in net present value") + 
-  theme_tufte()
+  ylab("Reduction in net present value")
 
@@
   facet_grid(variable~penalty_fn) + 
-  labs(x="time", y="stock size", title = "Example Stock & Harvest Dynamics")  + 
-  theme_tufte()
+  labs(x="time", y="stock size", title = "Example Stock & Harvest Dynamics")
 
@@
   stat_summary(fun.y = mean, geom = "line") + 
-  facet_grid(statistic ~ timeseries, scale="free") + theme_bw()
+  facet_grid(statistic ~ timeseries, scale="free_y")
 
@@
 
-```{r Table1}
+```{r Table1, results="asis"}
 who <- c("penalty_fn", "ignore_fraction", "assume_fraction", "reduction")
@@
 table1_long$reduction <- as.factor(table1_long$reduction)
-ggplot(table1_long, aes(penalty.fn, value, fill = variable)) + geom_bar(stat="identity", position="dodge") + facet_wrap(~ reduction) + theme_bw()
+ggplot(table1_long, aes(penalty.fn, value, fill = variable)) + geom_bar(stat="identity", position="dodge") + facet_wrap(~reduction) 
 ```

### 2014-06-04 manuscripts/components/analysis.R

@@ -1,0 +1,312 @@
+
+## ----caching, include=FALSE----------------------------------------------
+library("methods")
+library("knitr")
+basename <- "manuscript"
+opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
+               cache.path = paste("components/cache/", basename, "/", sep=""))
+opts_chunk$set(cache = 2)
+opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, 
+               comment = NA, verbose = TRUE, echo=FALSE)
+
+# PDF-based figures
+opts_chunk$set(dev='pdf')
+
+
+## ----libraries, include=FALSE, cache=FALSE-------------------------------
+rm(list=ls())
+library("rmarkdown")
+library("pdgControl")
+library("reshape2")
+library("plyr")
+library("ggplot2")
+library("data.table")
+library("pander")
+library("cboettigR")
+library("ggthemes")
+library("snowfall")
+theme_set(theme_tufte())
+ncpu = 24
+
+
+## ----profit_model--------------------------------------------------------
+price = 10
+c0 = 30
+profit <- profit_harvest(price = price, c0 = c0, c1 = 0)
+
+
+## ----c2_grid-------------------------------------------------------------
+c2 <- exp(seq(0, log(41), length.out = 40))-1
+c2 <- seq(0, 40, length.out=100)
+
+
+## ----reduction-----------------------------------------------------------
+reduction <- 0.25 
+
+
+## ----setup---------------------------------------------------------------
+seed <- 123                 # Random seed (replicable results)
+delta <- 0.05               # economic discounting rate
+OptTime <- 20               # stopping time
+gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
+sigma_g <- 0.2              # Noise in population growth
+reward <- 0                 # bonus for satisfying the boundary condition
+z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
+z_m <- function() 1         # No measurement noise, 
+z_i <- function() 1         # No implemenation noise
+f <- BevHolt                # Select the state equation
+pars <- c(1.5, 0.05)        # parameters for the state equation
+K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
[…]

### 2014-06-04 manuscripts/manuscript.Rmd
caching commands must be in a prior chunk.

@@
 
-```{r dependencies, include=FALSE, cache=FALSE}
+```{r configure, include=FALSE, cache=FALSE}
 #source("components/install.R")
+
+library("methods")
+library("knitr")
+basename <- "manuscript"
+opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
+               cache.path = paste("components/cache/", basename, "/", sep=""))
+opts_chunk$set(cache = 2)
+opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, 
+               comment = NA, verbose = TRUE, echo=FALSE)
+# PDF-based figures
+opts_chunk$set(dev='pdf')
 ```
+
 ```{r analysis, include=FALSE}
@@
 The horizontal line indicates a value of the stock that is reduced by `r reduction * 100`% from the maximum expected value in the absence of policy adjustment costs, $NPV_0({\\bf h_0^*})$.
-Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.", dependson="quadcosts", fig.width=4, fig.height=3, cache=FALSE}
+Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.", dependson="quadcosts", fig.width=4, fig.height=3}
 ggplot(fees, aes(c2, (npv0-value)/npv0, lty=variable)) + 
@@
 
-ggplot(subset(figure4_df, statistic != "cross.correlation"), aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn))  +
+ggplot(subset(figure4_df, statistic != "cross.correlation"), 
+       aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn))  +
   stat_summary(fun.y = mean, 
@@
 **
-
-<!-- ![image](figure/Figure_6) -->
 
@@
 table1_long$reduction <- as.factor(table1_long$reduction)
-ggplot(table1_long, aes(penalty.fn, value, fill = variable)) + geom_bar(stat="identity", position="dodge") + facet_wrap(~reduction) 
+ggplot(table1_long, aes(penalty.fn, value, fill = variable)) + 
+  geom_bar(stat="identity", position="dodge") + facet_wrap(~reduction) 
 ```

### 2014-06-04 manuscripts/components/analysis.R

@@ -1,17 +1,4 @@
 
-## ----caching, include=FALSE----------------------------------------------
-library("methods")
-library("knitr")
-basename <- "manuscript"
-opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
-               cache.path = paste("components/cache/", basename, "/", sep=""))
-opts_chunk$set(cache = 2)
-opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, 
-               comment = NA, verbose = TRUE, echo=FALSE)
-
-# PDF-based figures
-opts_chunk$set(dev='pdf')
-
 
 ## ----libraries, include=FALSE, cache=FALSE-------------------------------
 rm(list=ls())

### 2014-06-05 manuscripts/manuscript.Rmd
no need to keep tex
use facet_wrap for better scaling

@@
   pdf_document:
-    keep_tex: true
     template: components/elsarticle.latex
@@
 with_xcor_plot
+```
 
+```{r Figure_4_alt, fig.cap="Variance and autocorrelation of stock dynamics and harvest dynamics, as a function of the penalty coefficient.
+Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8}
 ggplot(subset(figure4_df, statistic != "cross.correlation"), 
@@
   stat_summary(fun.y = mean, geom = "line") + 
-  facet_grid(statistic ~ timeseries, scale="free_y")
+  facet_wrap(~ timeseries + statistic, scale="free_y")
 

### 2014-06-17 manuscripts/manuscript.Rmd
add cache rules on images

@@
 opts_chunk$set(dev='pdf')
+
+fig.cache <- TRUE
 ```
@@
 
-Figure 1 shows the calibration graphically. Each curve plots the change
+Figure 2 shows the calibration graphically. Each curve plots the change
 in maximum expected NPV for a given penalty function as the penalty cost
@@
 
-```{r Figure_1, fig.cap="Expected net present value by functional form of penalty.
+```{r Figure_2, fig.cap="Expected net present value by functional form of penalty.
 Horizontal axis shows the coefficient $c_i$ governing the magnitude of the policy cost, while vertical axis shows fraction of the maximum expected net present value dissipated by the policy cost, $\\tfrac{NPV_0 - NPV_i}{NPV_0}$.
 The horizontal line indicates a value of the stock that is reduced by `r reduction * 100`% from the maximum expected value in the absence of policy adjustment costs, $NPV_0({\\bf h_0^*})$.
-Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.", dependson="quadcosts", fig.width=4, fig.height=3}
+Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.", dependson="quadcosts", fig.width=4, fig.height=3, cache = fig.cache}
 ggplot(fees, aes(c2, (npv0-value)/npv0, lty=variable)) + 
@@
 
-```{r Figure_2, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=3, fig.width=8}
+```{r Figure_3, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=3, fig.width=8, cache = fig.cache}
 
@@
 
-<!-- NOTE 
-Assuming we aren't showing cross-correlations, I think we can probably fit these into a single four subplot figure.
-Cross-correlations would be a little harder but just using 5 subplots from what could have been a 6 subplot figure would also work, because a journal could just put the caption into the empty space.
-
-Same comments as before on labeling the curves and detailing in the figure captions. Axis labels and things all also need work. - Paul
--->
 <!--
 Added cross-correlations but shows no pattern.  Also have version with 2x2 as single plot.  feedback on aesthetics welcome.  - CB
--->
 
 ```{r Figure_4, fig.cap="Variance and autocorrelation of stock dynamics and harvest dynamics, as well as cross-correlation between stock and harvest dynamics, as a function of the penalty coefficient.
-Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8}
+Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8, cache=fig.cache}
 
@@
 
+-->
+
 ```{r Figure_4_alt, fig.cap="Variance and autocorrelation of stock dynamics and harvest dynamics, as a function of the penalty coefficient.
-Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8}
+Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8, cache=fig.cache}
 ggplot(subset(figure4_df, statistic != "cross.correlation"), 
@@
 ```{r Figure_1S, dependson="tidy", fig.cap="Multiple realizations of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.
-Note that while fish stock dynamics appear similar in penalty and non-penalty scenarios, the harvest dyanmics show clear patterns depending on the type of penalty.", fig.height=3, fig.width=8}
+Note that while fish stock dynamics appear similar in penalty and non-penalty scenarios, the harvest dyanmics show clear patterns depending on the type of penalty.", fig.height=3, fig.width=8, cache=fig.cache}
 

### 2014-06-17 manuscripts/manuscript.Rmd
add additional figures: - histograms of costs and profits - cross-comparisons of managing with wrong policy

@@
 opts_chunk$set(dev='pdf')
+fig.cache <- FALSE
 
-fig.cache <- TRUE
+library("rmarkdown")
+library("pdgControl")
+library("reshape2")
+library("plyr")
+library("ggplot2")
+library("data.table")
+library("pander")
+library("cboettigR")
+library("ggthemes")
+library("snowfall")
+
+theme_set(theme_tufte())
 ```
@@
 variance of both harvests and stock sizes through time; on the
-autocorrelation of harvests and stock sizes through time; and on the
-cross-correlation of harvests and stock sizes through time. <!-- NOTE Are we showing cross-correlations or not? --> <!-- See figure 4, probably not-->
+autocorrelation of harvests and stock sizes through time. <!-- NOTE Are we showing cross-correlations or not? --> <!-- See figure 4, probably not-->
 
@@
 
+```{r histogram-calc}
+profits <- dt[, sum(profit_fishing), by=c('penalty_fn', 'replicate') ]
+costs <- dt[, sum(policy_cost), by=c('penalty_fn', 'replicate') ]
+reed_profits <- dt[, sum(profit_fishing_alt), by=c('penalty_fn', 'replicate') ]
+reed_costs <- dt[, sum(policy_cost_alt), by=c('penalty_fn', 'replicate') ]
+setnames(profits, "V1", "profits")
+hist_dat <- melt(cbind(profits, costs = costs$V1, 
+                       reed_profits = reed_profits$V1, reed_costs = reed_costs$V1),
+                 id = c("penalty_fn", "replicate"))
+````
+
+```{r Figure_5}
+ggplot(hist_dat) + geom_density(aes(value, fill=variable), alpha=0.6)+facet_wrap(~penalty_fn)
+```
 Next we examine the consequences either of ignoring policy adjustment
@@
 
+When policy costs are present, assuming the wrong functional form may or may not be worse than ignoring the presence of policy costs all together.
+Figure S2 considers several such cases.
+The X axis labels indicate first which policy is being used to drive the harvest decisions, and then which penalty is actually being applied.
+Thus `L1_L2` indicates a policy calculated under the linear $L_1$ costs, when the reality involves quadratic $L_2$ costs.
+Though the coefficients of the $L_2$ costs have been scaled such that the net effect is the same, the inferred policies differ.
+As a result, the value is slightly more than half of the optimal free solution when the expected reduction should only be 10% less than optimal free.
+In this case, ignoring the costs all together is still worse than using L1 costs -- the red bar is lower than the blue.
+
+For fixed costs, the reverse is true.
+Because fixed costs increase the volatility of the optimal solution while L2 costs decrease it, simply ignoring the cost of adjustment all together results in a higher value than either assuming costs are quadratic $L_2$ when they are fixed, or assuming they are fixed when they are quadratic.
+
+Nevertheless, assuming quadaratic costs is always the most conservative option -- scenarios in which true costs are quadratic (regardless of what cost structure is assumed by the policy) do significantly worse than those that are not (i.e.
+all cases that assume quadratic but actually have linear or fixed costs).
+
+These patterns hold across the different size reductions shown (from 10% to 25%), though net present value becomes negative under the quadratic form for the larger penalties as costs paid for adjustments exceed profits derived from harvest.
+(Though optimal solutions will always avoid negative net present values, these scenarios in which policies are applied under conditions other than assumed in the optimality calculation have no such guarentee.) For each scenario, results are averaged over 100 replicates.
+
+```{r mismatches, fig.cap="Mismatches.
+X axis labels indicate the model used to derive the policy, followed by the model used to simulate the penalty.
+Blue bars show the net present value of that scenario.
+Compare to red bars, which show the consequence of using a policy that ignores costs all together in the same scenario (i.e.
+costs as indicated by second code), rather than assuming the policy indicated by the first code in the pair.
+All values are scaled to a fraction of the adjustment free net present value.
+Successive panels show increasing reduction of the net present value by increasing penalty coefficients: e.g.
+a policy in the first panel should lose only 10% of its net present value to adjustment costs if it had the correct form of those costs."}
+who <- c("penalty_fn", "ignore_fraction", "mismatched_fraction", "reduction")
+table2 <- arrange(mismatches_df[who], reduction) 
+names(table2) = c("penalty.fn", "ignoring", "mismatched", "reduction")
+table2_long <- melt(table2, id = c('penalty.fn', 'reduction'))
+table2_long$reduction <- as.factor(table2_long$reduction)
+
+ggplot(table2_long, aes(penalty.fn, value, fill = variable)) + 
+  geom_bar(stat="identity", position="dodge") + 
+  facet_wrap(~reduction, scales="free_y") 
+```
+
 <!--

### 2014-06-17 manuscripts/components/analysis.R

@@ -1,18 +1,6 @@
 
 
-## ----libraries, include=FALSE, cache=FALSE-------------------------------
-rm(list=ls())
-library("rmarkdown")
-library("pdgControl")
-library("reshape2")
-library("plyr")
-library("ggplot2")
-library("data.table")
-library("pander")
-library("cboettigR")
-library("ggthemes")
-library("snowfall")
-theme_set(theme_tufte())
+
 ncpu = 24
 
 
@@ -285,6 +273,16 @@ figure4_df$statistic <- stat_map[figure4_df$statistic]
 figure4_df$timeseries <- series_map[figure4_df$timeseries]
 
 
+## ----histograms----------------------------------------------------------
+profits <- dt[, sum(profit_fishing), by=c('penalty_fn', 'replicate') ]
+costs <- dt[, sum(policy_cost), by=c('penalty_fn', 'replicate') ]
+reed_profits <- dt[, sum(profit_fishing_alt), by=c('penalty_fn', 'replicate') ]
+reed_costs <- dt[, sum(policy_cost_alt), by=c('penalty_fn', 'replicate') ]
+setnames(profits, "V1", "profits")
+hist_dat <- melt(cbind(profits, costs = costs$V1, 
+                       reed_profits = reed_profits$V1, reed_costs = reed_costs$V1),
+                 id = c("penalty_fn", "replicate"))
+
 ## ----errors-table--------------------------------------------------------
 
 source("components/compute_error_table.R")
@@ -296,4 +294,13 @@ who <- names(out[[1]])
 error_df <- melt(out, id=who)       
 
 
+## ----mismatches--------------------------------------------------------
+
+source("components/compute_mismatches.R")
+
+reduction_list <- c(.1, .15, .2, .25)
+out <- lapply(reduction_list, function(r)
+  compute_mismatches(r = r))   
+who <- names(out[[1]])
+mismatches_df <- melt(out, id=who)       
 

### 2014-06-17 manuscripts/manuscript.Rmd
manuscript updated, add compute_mismatches code.

@@
 
-<!--NOTE c_i notation is confusing because it does not usually refer to c_0 or c_4 -->
+<!--NOTE ci notation is confusing because it does not usually refer to c0 or c4 -->
+
 Each of the policy adjustment cost function is characterized in terms of
@@
 
-Figure 2 illustrates how the different forms of adjustment cost can
-impact the optimal policy. Each panel is generated against the same
-sequence of random shocks so that they can be compared directly. Figure
-3 shows the corresponding stock sizes, which are measured here before 
-harvest ($h_t$ being determined after observing stock size $x_t$).
-Because stock sizes are measured before harvests, the effect of the 
-penalty on the stock size is not very pronounced, while the effect
-on the harvest chosen shows a systematic deviations from the penalty
-free optimum, depending on the nature of the cost.
-
-In each case, the optimal solution without any adjustment cost is shown in
-against the policy induced by optimization under the given adjustment
-penalty (equivalent to a `r 100*reduction`% reduction in maximum expected NPV) 
-is overlaid in blue.
-
-When considering the first formulation of policy adjustment costs
-($\Pi_1$), the first panel of Figure 2 shows a typical pattern, in which
-the optimal policy tends to avoid small policy adjustments, resulting in
-long periods of constant policy followed by sudden bursts of adjustment.
-This results in a relatively step-like policy pattern. In contrast, the
-second formulation $\Pi_2$ disproportionately penalizes large policy
-adjustments. The corresponding optimal policy tracks all of the changes
-made by the cost-free policy, but with smaller magnitude. This results
-in a smoother $h_t$ curve, one that undershoots the larger oscillations
-seen in the cost-free optimum in favor of a policy that changes
-incrementally each year. Finally, the optimal policy for the third,
-'fixed fee' formulation ($\Pi_3$) only makes large adjustments, as one
-might expect, because the magnitude of the adjustment made is not
-reflected in the resulting penalty. Whereas the optimal solution for
-$\Pi_1$ attempts to accommodate the large oscillations at the end of the
-period shown (time steps $t=47-49$) with a constant quota in between the
-extremes, the fixed fee version takes the opposite approach of one very
-large swing. MORE DETAILING TO COME WHEN WE HAVE THE FIGURES
-
 ```{r Figure_3, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=3, fig.width=8, cache = fig.cache}
 
-fig2_df <- as.data.frame(subset(dt, replicate=='rep_2'))
+fig2_df <- as.data.frame(subset(dt, replicate=='rep_1'))
 fig2_df <- fig2_df[c("time", "fishstock", "alternate", "harvest", "harvest_alt", "penalty_fn")]
@@
 
-The comparisons shown in Figure 2 are for one realization (i.e. a
+Figure 3 illustrates how the different forms of adjustment cost can
+impact the optimal policy (lower row) and corresponding stock sizes,
+which are measured here before harvest ($h_t$ being determined after
+observing stock size $x_t$). Each panel is generated against the same
+sequence of random shocks so that they can be compared directly.
+Because stock sizes are measured before harvests, the effect of the 
+penalty on the stock size is not very pronounced, while the effect
+on the harvest chosen shows a systematic deviations from the penalty
+free optimum, depending on the nature of the cost.
+
+In each case, the optimal solution without any adjustment cost is shown in
+against the policy induced by optimization under the given adjustment
+penalty (equivalent to a `r 100*reduction`% reduction in maximum expected NPV) 
+is overlaid in blue.
+
+When considering the first formulation of policy adjustment costs
+(linear costs, $\Pi_1$), the bottom-left panel of Figure 3 shows a typical pattern, in which
+the optimal policy tends to avoid small policy adjustments, resulting in
+periods of constant policy followed by sudden bursts of adjustment.
+This results in a relatively step-like policy pattern. In contrast, the
+second formulation (quadratic costs, $\Pi_2$) disproportionately penalizes large policy
+adjustments. The corresponding optimal policy tracks all of the changes
+made by the cost-free policy, but with smaller magnitude. This results
+in a smoother $h_t$ curve, one that undershoots the larger oscillations
+seen in the cost-free optimum in favor of a policy that changes
+incrementally each year. Finally, the optimal policy for the third,
+'fixed fee' formulation ($\Pi_3$) only makes large adjustments, as one
+might expect, because the magnitude of the adjustment made is not
+reflected in the resulting penalty. Whereas the optimal solution for
+$\Pi_1$ attempts to accommodate the large oscillations at the end of the
+period shown (time steps $t=47-49$) with a constant quota in between the
+extremes, the fixed fee version takes the opposite approach of one very
+large swing.
+
+The comparisons shown in Figure 3 are for one realization (i.e. a
 particular sequence of random number draws representing environmental
@@
 adjustments are expensive ($\Pi_2$), we see the smoothing signal that we
-might have expected (see also Ludwig 1980 for this particular case). As
+might have expected (see also @Ludwig1980 for this particular case). As
 cost penalties increase in severity (i.e., $c_2$ increases), the
@@
 
-Interestingly, as suggested by the realization in Fig. 2, including a
+Interestingly, as suggested by the realization in Fig. 3, including a
 fixed cost of policy adjustment increases the variation in harvests
@@
 optimal management strategy in the basic model without policy adjustment
-costs (Eqn. 3) or when optimizing against $\Pi_2$ or $\Pi_3$. While
-still not common for the particular parameter combinations we examine,
+costs (Eqn. 3) or when optimizing against $\Pi_2$ or $\Pi_3$.
+
+```{r}
+fraction_no_shift <- function(x)
+ sum(x[2:length(x)] - x[1:length(x)-1] == 0)/length(x)
+
+shifts <- dt[, fraction_no_shift(harvest), by=c("penalty_fn", "replicate")]
+ave <- shifts[, mean(V1), by=penalty_fn]
+
+no_shifts <- ave$V1
+names(no_shifts) <- ave$penalty_fn
+```
+
+While still not common for the particular parameter combinations we examine,
 we find that positive unaltered quotas through time are much more likely
 to occur when optimizing against $\Pi_1$ where policy adjustment costs
-scale linearly with the size of proposed policy changes (STATISTIC).
-Moreover, these occurrences increase in frequency as the severity of
-these costs ($c_1$) increases (STATISTIC).
+scale linearly with the size of proposed policy changes: in the 100 replicates
+of data presented above the harvest policy is identical in conecutive intevals
+only `r no_shifts[["L2"]] * 100`% of the time for quadratic costs $\Pi_2$, compared with
+`r no_shifts[["L1"]] * 100`$ with linear costs $Pi_1$ and `r no_shifts[["fixed"]]*100`%
+for fixed costs $\Pi_3$. Moreover, these occurrences increase in frequency as the severity of
+these costs ($c_1$) increases.
 
-<!--
-Added cross-correlations but shows no pattern.  Also have version with 2x2 as single plot.  feedback on aesthetics welcome.  - CB
-
-```{r Figure_4, fig.cap="Variance and autocorrelation of stock dynamics and harvest dynamics, as well as cross-correlation between stock and harvest dynamics, as a function of the penalty coefficient.
-Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8, cache=fig.cache}
-
-with_xcor_plot <- 
-ggplot(figure4_df, aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn)) + 
-  facet_wrap(~variable, scales = "free_y") +
-  stat_summary(fun.y = mean, 
-               fun.ymin = function(x) mean(x) - sd(x), 
-               fun.ymax = function(x) mean(x) + sd(x), 
-               geom = "ribbon", alpha=0.3, colour=NA) +
-  stat_summary(fun.y = mean, geom = "line")
-with_xcor_plot
-```
-
--->
+<!-- to include cross.correlation, drop subset call and facet_wrap by variable. But shows no pattern-->
 
@@
   stat_summary(fun.y = mean, geom = "line") + 
+  coord_cartesian(xlim = c(0, .3)) + 
   facet_wrap(~ timeseries + statistic, scale="free_y")
@@
 ```
+
 Next we examine the consequences either of ignoring policy adjustment
@@
 Histograms for the different contributions labelled $[1]-[4]$ here when
-taken across XXX replicate runs are shown are shown in Figure 5
+taken across 100 replicate runs are shown are shown in Figure 5
 (contribution $[1]$ red, $[2]$ green, $[3]$ blue, and $[4]$ mauve). The
@@
 
-**
+```{r Figure_6, fig.cap="Relative cost of ignoring adjustment costs when they are present ('ignoring', red) vs assuming the adjustment costs when they are absent ('assuming', blue), shown by penalty function over increasing magnitudes of cost.
+All values are relative to the cost-free adjustment optimum, NPV0.
+In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present.
+The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs."}
+table1_long <- melt(table1, id = c('penalty.fn', 'reduction'))
+table1_long$reduction <- as.factor(table1_long$reduction)
+ggplot(table1_long, aes(penalty.fn, value, fill = variable)) + 
+  geom_bar(stat="identity", position="dodge") + facet_wrap(~reduction) 
+```
 
-Table 1 compares these different contributions, namely the $NPV$ lost by
+Figure 6 compares these different contributions, namely the $NPV$ lost by
 assuming policy adjustment costs when none are present (first entry in
@@
 of the maximum expected $NPV$ in the base case where no policy
-adjustment costs apply or are assumed to apply $NPV_0({\bf h_0^*})$. For
-a sensitivity test where we draw similar comparisons for different
-amounts of environmental variation, see Supplementary Information X.X.
+adjustment costs apply or are assumed to apply $NPV_0({\bf h_0^*})$.
 
@@
 
-```{r table-caption}
-caption = "Table 1: Column 'ignoring' shows the results of ignoring a adjustment penalty when it is present, Column 'assuming' shows the results of assuming an adjustment cost when it is absent.
-Values (ignoring, assuming) are given as the expected net present value (ENPV) as a fraction of that when no penalty is present, ENPV0.
-Percent reduction refers to penalty coefficient being calibrated to achieve the given percent reduction relative to ENPV0 when the penalty is optimally accounted for.
-Comparing the second and third columns shows that ignoring a real cost is a significantly graver error, particularly in the case of quadratic (L2) costs."
-```
-
-```{r Table1, results="asis"}
-who <- c("penalty_fn", "ignore_fraction", "assume_fraction", "reduction")
-table1 <- arrange(error_df[who], reduction) 
-names(table1) = c("penalty.fn", "ignoring", "assuming", "reduction")
-pandoc.table(table1, caption=caption)
-```
-
-```{r Table1-Figure, fig.cap="Relative cost of ignoring adjustment costs when they are present ('ignoring', red) vs assuming the adjustment costs when they are absent ('assuming', blue), shown by penalty function over increasing magnitudes of cost.
-All values are relative to the cost-free adjustment optimum, NPV0.
-In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present.
-The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs."}
-table1_long <- melt(table1, id = c('penalty.fn', 'reduction'))
-table1_long$reduction <- as.factor(table1_long$reduction)
-ggplot(table1_long, aes(penalty.fn, value, fill = variable)) + 
-  geom_bar(stat="identity", position="dodge") + facet_wrap(~reduction) 
-```
-
 When policy costs are present, assuming the wrong functional form may or may not be worse than ignoring the presence of policy costs all together.
-Figure S2 considers several such cases.
+Figure 7 considers several such cases.
 The X axis labels indicate first which policy is being used to drive the harvest decisions, and then which penalty is actually being applied.
@@
 
-```{r mismatches, fig.cap="Mismatches.
+```{r Figure_7, fig.cap="Mismatches.
 X axis labels indicate the model used to derive the policy, followed by the model used to simulate the penalty.
@@
 
-<!--
-NOTE Obviously we have presentation choices to make here. I think there is plenty of scope either to compact this table somehow (rows are penalty functions)  x columns are percent reduction.
-
-There would also be lots of scope for showing the same info visually as a simple bar chart
--->
-
 Discussion
 ==========
+
+<!--
 
@@
     saves direct costs, but permits higher-value solutions.
+-->
+
+<!-- Pasted from external word doc, see Boettiger_Discussion_draft.docx for latest version of discussion -->
+
+Policy-makers managing ecological systems that vary in space and time must evaluate how much of that variation to reflect in management recommendations in order to achieve a desirable management outcome.
+Fine-tuning a policy to respond to frequent variations in ecological dynamics may incur increased transaction costs associated with constantly revisiting past policy decisions.
+A more pragmatic approach might be one that balances benefits from responding to frequent variations in ecological conditions with the increased transactions costs involved.
+As a first step towards exploring these ideas, we revisited a classic problem from bioeconomics concerning the optimal management of a fish stock subject to stochastically varying recruitment (Reed, Clark).
+We examined how optimal policy recommendations, here annual catch quotas, changed when accounting for costs associated with policy adjustment and what the implications of following these policy recommendations would be for the exploited population.
+We also compared how the value of the fishery is affected by managers either under- or over-estimating the importance of policy adjustment costs of this type.
+
+Estimating policy adjustment costs and how they respond to the size of proposed policy changes would be empirically challenging.
+Recognizing this fact, in our analyses, we compared different plausible forms that these costs might take.
+We compared two cost structures where we assumed the magnitude of policy adjustment costs increased with the magnitude of the change in policy being proposed with an alternative formulation in which we assumed there was a fixed cost associated with making any change to current policy.
+While each formulation clearly provides only a very phenomenological representation of the policy setting environment, we believe that each enables us to explore meaningful differences in how policy adjustment costs might operate.
+That being said, in the real-world we might expect the different types of adjustment cost to operate in combination.
+Interestingly, there are analogues between how we have represented different types of policy adjustment costs in our models and regularization techniques (e.g.
+ridge or lasso regression approaches) that are sometimes in model fitting to address concerns about over-specifying models (REFERENCES).
+
+The biggest differences between the different representations of policy adjustment cost that we consider are between those that have a smoothing effect on annual quotas and those that do not.
+The few past studies that incorporate policy adjustment costs in models of fisheries management (e.g.
+Ludwig, Feichtinger, Wirl) assumed costs of policy adjustment increased as a quadratic function of the magnitude of the policy change being proposed (our $\Pi_2$ formulation in Eqn.) In effect, this means that small changes to annual quotas incur little extra cost, but large changes to annual quotas become disproportionately expensive to make.
+Including costs of this form smoothes inter-annual variation in the catch quotas that would be recommended.
+However, as catches become less variable through time, the variability in the fish population itself increases.
+In essence, the optimal policy no longer soaks up as much of the natural variability in recruitment that is affecting the population.
+Also, the catches and remaining stock sizes corresponding to optimal management become more autocorrelated in time, because it takes the fishery longer to fish down peaks in abundance that follow large recruitment pulses.
+The effects of smoothing here are similar to those predicted when assuming the cost per unit effort is increasing in the amount of effort expended, as is common in many fisheries bioeconomics models (references).
+Note this assumption is different from associating extra costs with changes to policy per se (see Supporting Information for the relevant results).
+Moreover, smoothing effects of this type are what one would have expected when including policy adjustment costs.
+
+Therefore, standing in sharp contrast to these smoothing predictions is our finding that including policy adjustment costs can actually increase the variability of quotas through time if there is a fixed cost associated with making any changes to current policy (e.g.
+costs of running relevant stakeholder meetings and public consultations on proposed policy changes, $\Pi_3$).
+With this formulation, as stock sizes vary in response to recruitment, the fishery manager must balance the cost of brokering a policy change with the cost in forgone fisheries revenue from not responding to favorable recruitment pulses.
+The optimal policy involves ignoring small variations in recruitment, but then assigns a larger quota when particularly strong recruitment years arise than would have been the case in the absence of policy adjustment costs.
+The other functional form we consider, in which the costs of policy adjustment scale linearly with the size of the adjustment ($Pi_1$), has less obvious effects on optimal policies.
+But interestingly, it is the only formulation for which we observed positive unchanging quotas of the type most commonly encountered in real-world applications.
+
+That the different representations of policy adjustment costs result in such different dynamics suggests that researchers constructing fisheries economics models should proceed cautiously when choosing how to represent these costs.
+However, in our own experience, we have found that while modeling studies sometimes mention policy adjustment costs when motivating model assumptions (references), they rarely provide much justification for the choice of functional form used or test the sensitivity of any conclusions drawn to alternative specifications.
+That we found such clear differences between the functional forms is perhaps also surprising, because one might anticipate that the limiting case of increasing policy adjustment costs within each functional form should be the same, namely a constant annual quota that does not change through time (open-loop control).
+
+We also compared the efficiency costs that would result from failing to account for policy adjustment cost if they are present with those involved in assuming them when in fact they are absent.
+The results of this comparison were not sensitive to the particular form of policy adjustment costs assumed.
+Instead, we always found the efficiency costs of ignoring policy adjustment costs when they were present to be much larger than the efficiency costs of assuming policy adjustment costs applied when they were in fact absent.
+Policy adjustment costs affect the overall value of the fishery in two ways here.
+First, there is the direct cost associated with each quota change.
+Second there is a cost in foregone revenue from missed catches when not following what would be the optimal policy if quotas were free to track recruitment variability.
+Our finding that it is more costly to ignore policy adjustment costs when they are present arises because the first, more direct, cost contribution here is larger than the second.
+
+As with any modeling analysis, our formulation makes many assumptions.
+For example, we assume that the fishery in question is being optimally managed by a policy-maker who acts as the 'sole owner' of the stock.
+This approach is different to models that assume fisheries are not well-managed, e.g.
+by assuming open access conditions (references), or ones that derive policy recommendations endogenously by modeling interactions between different stakeholders (game theory references).
+As such, we anticipate that our approach will be more relevant to some fisheries, particularly domestic fisheries in developed countries that are subject to relatively strong regulatory regimes, than to others (e.g., artisanal fisheries that are subject to weaker regulation).
+A second important assumption we made is that the fishery manager observes the current stock size correctly when setting the annual quota (see Clark and Kirkwood, Williams + more for alternative specifications).
+However, stock assessments struggle to predict current cohort sizes based as they are on observing past catch history (Ralston et al).
+We might anticipate that when uncertainty regarding reported recruitment pulses is included, we see the tendency for an optimizing manager to moderate their policy responses to initial reports of particularly good recruitment years increase yet further.
+
+One obvious research avenue suggested by our models is that of empirically estimating costs of policy adjustment.
+A direct estimation approach could quantify some sources of policy adjustment costs, e.g.
+costs to processing plants that arise from having more variable catches.
+However, other more intangible sources of policy adjustment costs, e.g.
+preferences of policy-makers or different stakeholders for less variable quotas, might be missed.
+An alternative, more holistic, approach would be to apply revealed preference methods to fisheries management agencies themselves, in the tradition of McFadden (1975, 1976).
+Such an analysis would involve comparing quotas that were set relative to stock sizes as they were estimated at the time each management decision was taken to try to infer what objective managers were maximizing.
+Some stocks are assessed and some quotas revisited more frequently than others, which provides relevant patterns of variation in policy environments that econometric analyses of this type could try to exploit.
+
+A worthwhile modeling extension suggested by our results would be to examine the implications of policy adjustment costs for risks of stock collapse.
+Examining risks of stock collapse is not possible with the Reed model-formulation that we followed here.
+But using an alternative approach also would be worthwhile in light of our finding that the variance and autocorrelation in stock sizes through time can be affected when accounting for costs of policy adjustment.
+Both are properties known in other modeling settings to be associated with changes to the risk of extinction or of transitions between alternative stable states.
+In such an analysis, it would be interesting to explore more complicated patterns of environmental variability than we have here (e.g., colored environmental noise).
+Another obvious extension would be to combine the different functional forms that we consider rather than studying them in isolation as we have here.
+Finally, a third would be to consider how policy adjustment costs affect approach paths to the long-run management outcomes, which provide the focus for this study.
+
+Conclusions
+===========
+
+Lessons for modelers - ignoring reality of policy costs leads to less effective management (decreased value)
+
+Lesons for policy makers - decreasing adjustment costs not only saves direct costs but permits higher value solutions.
 
@@
 
+```{r table-caption}
+caption = "Table 1: Column 'ignoring' shows the results of ignoring a adjustment penalty when it is present, Column 'assuming' shows the results of assuming an adjustment cost when it is absent.
+Values (ignoring, assuming) are given as the expected net present value (ENPV) as a fraction of that when no penalty is present, ENPV0.
+Percent reduction refers to penalty coefficient being calibrated to achieve the given percent reduction relative to ENPV0 when the penalty is optimally accounted for.
+Comparing the second and third columns shows that ignoring a real cost is a significantly graver error, particularly in the case of quadratic (L2) costs."
+```
+
+```{r Table1, results="asis"}
+who <- c("penalty_fn", "ignore_fraction", "assume_fraction", "reduction")
+table1 <- arrange(error_df[who], reduction) 
+names(table1) = c("penalty.fn", "ignoring", "assuming", "reduction")
+pandoc.table(table1, caption=caption)
+```
+
 # References

### 2014-06-17 manuscripts/components/compute_mismatches.R

@@ -1,0 +1,66 @@
+compute_mismatches <- function(r){
+    
+  index <- dt_npv[,closest(r, (npv0-value)/npv0), by=variable]
+  apples_index <- index$V1
+  names(apples_index) <- index$variable
+  
+  L2_policy <- policies$L2[[apples_index["L2"]]]$D
+  L1_policy <- policies$L1[[apples_index["L1"]]]$D
+  fixed_policy <- policies$fixed[[apples_index["fixed"]]]$D
+
+  reps <- 1:100
+  names(reps) = paste("rep", 1:length(reps), sep="_") # treat as a factor
+  seeds <- 1:100
+  sims <- list(
+    L1_L2 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
+                                                 L1_policy, z_g, z_m, z_i, 
+                                                 opt$D, profit=profit, 
+                                                 penalty=L2(c2[apples_index["L2"]]), seed=seeds[x])), 
+    L2_L1 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
+                                                 L2_policy, z_g, z_m, z_i, 
+                                                 opt$D, profit=profit, 
+                                                 penalty=L1(c2[apples_index["L1"]]), seed=seeds[x])),
+    
+    L2_fixed = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
+                                                       L2_policy, z_g, z_m, z_i, 
+                                                       opt$D, profit=profit, 
+                                                       penalty=fixed(c2[apples_index["fixed"]]), seed=seeds[x])),
+    
+    fixed_L2 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
+                                                    fixed_policy, z_g, z_m, z_i, 
+                                                    opt$D, profit=profit, 
+                                                    penalty=L2(c2[apples_index["L2"]]), seed=seeds[x]))
+    
+  )
+
+
+#Make data tidy (melt), fast (data.tables), and nicely labeled.
+  dat <- melt(sims, id=names(sims[[1]][[1]]))  
+  dt <- data.table(dat)
+  setnames(dt, "L2", "replicate") # names are nice
+  setnames(dt, "L1", "penalty_fn") # names are nice
+  
+  
+  
[…]

### 2014-06-17 manuscripts/manuscript.Rmd
update manuscript to write out figure data

@@
 opts_chunk$set(dev='pdf')
-fig.cache <- FALSE
+fig.cache <- TRUE
 
@@
 
+write.csv(dt, "components/data/100reps.csv")
+write.csv(fees, "components/data/figure2.csv")
+
 ```
@@
 
-fig2_df <- as.data.frame(subset(dt, replicate=='rep_1'))
-fig2_df <- fig2_df[c("time", "fishstock", "alternate", "harvest", "harvest_alt", "penalty_fn")]
-fig2_df <- melt(fig2_df, id = c("time", "penalty_fn"))
-fig2_df <- data.frame(fig2_df, baseline = fig2_df$variable)
+fig3_df <- as.data.frame(subset(dt, replicate=='rep_1'))
+fig3_df <- fig3_df[c("time", "fishstock", "alternate", "harvest", "harvest_alt", "penalty_fn")]
+fig3_df <- melt(fig3_df, id = c("time", "penalty_fn"))
+fig3_df <- data.frame(fig3_df, baseline = fig3_df$variable)
 variable_map <- c(fishstock = "fish_stock", alternate = "fish_stock", harvest = "harvest", harvest_alt = "harvest")
 baseline_map <- c(fishstock = "penalty", alternate = "no_penalty", harvest = "penalty", harvest_alt = "no_penalty")
-fig2_df$variable <- variable_map[fig2_df$variable]
-fig2_df$baseline <- baseline_map[fig2_df$baseline]
+fig3_df$variable <- variable_map[fig3_df$variable]
+fig3_df$baseline <- baseline_map[fig3_df$baseline]
 
-ggplot(fig2_df, aes(time, value, col=baseline)) +
+ggplot(fig3_df, aes(time, value, col=baseline)) +
   geom_line() +
@@
 
+write.csv(fig3_df, "components/data/figure3.csv")
 ```
@@
 
+write.csv(figure4_df, "components/data/figure4.csv")
 ```
@@
 ggplot(hist_dat) + geom_density(aes(value, fill=variable), alpha=0.6)+facet_wrap(~penalty_fn)
+write.csv(hist_dat, "components/data/figure5.csv")
 ```
@@
   geom_bar(stat="identity", position="dodge") + facet_wrap(~reduction) 
+write.csv(table1_long, "components/data/figure6.csv")
 ```
@@
   facet_wrap(~reduction, scales="free_y")
+
+write.csv(table2_long, "components/data/figure7.csv")
 ```

### 2014-06-17 manuscripts/manuscript.Rmd
update refs

@@
 choices of $c_i$ so that each has a comparable impact on the optimal net
-present value of fishery, broadly following the example of Bovenberg,
-Goulder and Gurnery (2005) and Bovenberg, Goulder and Jacobsen (2008).
+present value of fishery, broadly following the example of  @Bovenberg_2008.
+
 <!--NOTE Jake to confirm these are still relevant and needed. We are using a less sophisticated normalization than was once discussed and may or may not need the citations now. -->

### 2014-07-17 manuscripts/manuscript.Rmd
rerun manuscript

@@
 ```{r}
-fraction_no_shift <- function(x)
+fraction_no_shift <- function(x){
+ nonzeros <- which(x > 0)
+ x <- x[nonzeros]
  sum(x[2:length(x)] - x[1:length(x)-1] == 0)/length(x)
+}
 
@@
 scale linearly with the size of proposed policy changes: in the 100 replicates
-of data presented above the harvest policy is identical in conecutive intevals
+of data presented above the harvest policy is strictly positive and identical in consecutive intervals
 only `r no_shifts[["L2"]] * 100`% of the time for quadratic costs $\Pi_2$, compared with
-`r no_shifts[["L1"]] * 100`$ with linear costs $Pi_1$ and `r no_shifts[["fixed"]]*100`%
+`r no_shifts[["L1"]] * 100` with linear costs $\Pi_1$ and `r no_shifts[["fixed"]]*100`%
 for fixed costs $\Pi_3$. Moreover, these occurrences increase in frequency as the severity of
@@
 The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs."}
+
+who <- c("penalty_fn", "ignore_fraction", "assume_fraction", "reduction")
+table1 <- arrange(error_df[who], reduction) 
+names(table1) = c("penalty.fn", "ignoring", "assuming", "reduction")
+
 table1_long <- melt(table1, id = c('penalty.fn', 'reduction'))
@@
 ```{r Table1, results="asis"}
-who <- c("penalty_fn", "ignore_fraction", "assume_fraction", "reduction")
-table1 <- arrange(error_df[who], reduction) 
-names(table1) = c("penalty.fn", "ignoring", "assuming", "reduction")
 pandoc.table(table1, caption=caption)

### 2014-07-22 manuscripts/manuscript.Rmd
pasted in Paul's discussion update

@@
 for such a responsive management strategy potentially could be large.
+
+```{r Figure_1, fig.cap="Quota on Blue Fin Tuna Catch "}
+tuna <- read.csv("components/data/tuna.csv")
+ggplot(tuna, aes(year, quota)) + geom_point()
+```
 
@@
 fraction_no_shift <- function(x){
- nonzeros <- which(x > 0)
- x <- x[nonzeros]
- sum(x[2:length(x)] - x[1:length(x)-1] == 0)/length(x)
+
+noshift <- x[2:length(x)] - x[1:length(x)-1] == 0
+strictly_positive <- (x > 0.01 )[-1] # drop first point, 
+who <- noshift & strictly_positive # True whenever consecutive pairs did not shift and the second in the pair was nonzero harvest
+ sum(who)/length(who)
 }
@@
 
-Policy-makers managing ecological systems that vary in space and time must evaluate how much of that variation to reflect in management recommendations in order to achieve a desirable management outcome.
+Policy-makers managing ecological systems that vary in space and time must evaluate how much of that variation to reflect in management recommendations.
 Fine-tuning a policy to respond to frequent variations in ecological dynamics may incur increased transaction costs associated with constantly revisiting past policy decisions.
-A more pragmatic approach might be one that balances benefits from responding to frequent variations in ecological conditions with the increased transactions costs involved.
-As a first step towards exploring these ideas, we revisited a classic problem from bioeconomics concerning the optimal management of a fish stock subject to stochastically varying recruitment (Reed, Clark).
+A more pragmatic approach would be one that balances benefits from responding to frequent variations in ecological conditions with the increased transaction costs involved.
+As a first step towards exploring these ideas, we revisited a classic problem from bioeconomics concerning the optimal management of a fish stock subject to stochastically varying recruitment (Reed 1979, Clark 2010).
 We examined how optimal policy recommendations, here annual catch quotas, changed when accounting for costs associated with policy adjustment and what the implications of following these policy recommendations would be for the exploited population.
@@
 That being said, in the real-world we might expect the different types of adjustment cost to operate in combination.
-Interestingly, there are analogues between how we have represented different types of policy adjustment costs in our models and regularization techniques (e.g.
-ridge or lasso regression approaches) that are sometimes in model fitting to address concerns about over-specifying models (REFERENCES).
+Interestingly, there are analogues between how we have represented different types of policy adjustment costs in our models and regularization techniques that are sometimes used in model fitting to address concerns about over-specifying models (e.g.
+ridge or lasso regression (James et al., 2013) or total variation denoising approaches (Rudin et al.
+1992)).
 
-The biggest differences between the different representations of policy adjustment cost that we consider are between those that have a smoothing effect on annual quotas and those that do not.
+<!-- NOTE
+
+Have wondered about cutting this, but does broaden things out a bit from just econ referencing and context.
+
+Also more people will have heard about ridge and lasso, but I actually think they’re not as relevant as the total variation suggestion, because it applies to the gradient whereas they do not.
+So really a more accurate statement is that the difference between lasso and ridge and the total variation approach is in some ways analogous to the difference between costs on h or E and costs on dh/dt or dE/dt.
+But that’s way too many words now
+
+Carl B – when it comes to references, you may have others you would prefer here
+
+-->
+
+The biggest differences between the representations of policy adjustment cost that we consider are between those that have a smoothing effect on annual quotas and those that do not.
 The few past studies that incorporate policy adjustment costs in models of fisheries management (e.g.
-Ludwig, Feichtinger, Wirl) assumed costs of policy adjustment increased as a quadratic function of the magnitude of the policy change being proposed (our $\Pi_2$ formulation in Eqn.) In effect, this means that small changes to annual quotas incur little extra cost, but large changes to annual quotas become disproportionately expensive to make.
+Ludwig 1980, Feichtinger et al.
+1994, Wirl 1999) assumed costs of policy adjustment increased as a quadratic function of the magnitude of the policy change being proposed (our $\Pi_2$ formulation in Eqn.) In effect, this means that small changes to annual quotas incur little extra cost, but large changes to annual quotas become disproportionately expensive to make.
 Including costs of this form smoothes inter-annual variation in the catch quotas that would be recommended.
@@
 In essence, the optimal policy no longer soaks up as much of the natural variability in recruitment that is affecting the population.
-Also, the catches and remaining stock sizes corresponding to optimal management become more autocorrelated in time, because it takes the fishery longer to fish down peaks in abundance that follow large recruitment pulses.
-The effects of smoothing here are similar to those predicted when assuming the cost per unit effort is increasing in the amount of effort expended, as is common in many fisheries bioeconomics models (references).
-Note this assumption is different from associating extra costs with changes to policy per se (see Supporting Information for the relevant results).
-Moreover, smoothing effects of this type are what one would have expected when including policy adjustment costs.
+Also, the catches and remaining stock sizes corresponding to optimal management become more autocorrelated in time, because it takes the fishery longer to harvest down peaks in abundance that follow large recruitment pulses.
+The effects of smoothing here are similar to those predicted when assuming the cost per unit effort is increasing in the amount of effort expended (e.g., Lewis 1981, McGough et al.
+2009; see Supporting Information for a summary of the relevant results) as opposed to associating extra costs with changes to policy {\em per se}.
+Smoothing effects of this type are what one mightd have expected when including policy adjustment costs.
 
-Therefore, standing in sharp contrast to these smoothing predictions is our finding that including policy adjustment costs can actually increase the variability of quotas through time if there is a fixed cost associated with making any changes to current policy (e.g.
+Standing in sharp contrast to these smoothing predictions is our finding that including policy adjustment costs can actually increase the variability of quotas through time if there is a fixed cost associated with making any changes to current policy (e.g.
 costs of running relevant stakeholder meetings and public consultations on proposed policy changes, $\Pi_3$).
@@
 
-That the different representations of policy adjustment costs result in such different dynamics suggests that researchers constructing fisheries economics models should proceed cautiously when choosing how to represent these costs.
-However, in our own experience, we have found that while modeling studies sometimes mention policy adjustment costs when motivating model assumptions (references), they rarely provide much justification for the choice of functional form used or test the sensitivity of any conclusions drawn to alternative specifications.
-That we found such clear differences between the functional forms is perhaps also surprising, because one might anticipate that the limiting case of increasing policy adjustment costs within each functional form should be the same, namely a constant annual quota that does not change through time (open-loop control).
+<!-- NOTE These paragraphs will need revamping if the new results on mismatch are going in. -->
+
+That the different representations of policy adjustment costs result in such different dynamics suggests that researchers constructing fisheries economics models should proceed cautiously when choosing how to represent these costs.
+However, in our own experience, we have found that while modeling studies sometimes mention policy adjustment costs when motivating model assumptions (references), they rarely provide much justification for the choice of functional form used or test the sensitivity of any conclusions drawn to alternative specifications.
+Indeed, we were surprised to find such clear differences between the functional forms, because we anticipated that the limiting case of increasing policy adjustment costs within each functional form should be the same, namely a constant annual quota that does not change through time (open-loop control).
 
@@
 This approach is different to models that assume fisheries are not well-managed, e.g.
-by assuming open access conditions (references), or ones that derive policy recommendations endogenously by modeling interactions between different stakeholders (game theory references).
+by assuming open access conditions (references),
+
+<!-- NOTE Would be good to give an open access model in a fluctuating environment here.
+From Andersen and Sutinen’s review (Mar Res Econ 1, 117-136) it looks like one basal citation is Andersen 1981 The exploitation of fish resources under stock uncertainty.
+But it is a “staff paper”.
+Our library don’t hold it.
+Has anyone else got it?-->
+
+or ones that derive policy recommendations endogenously by modeling interactions between different stakeholders (Kaitala 1993, Laukkanen 2003).
 As such, we anticipate that our approach will be more relevant to some fisheries, particularly domestic fisheries in developed countries that are subject to relatively strong regulatory regimes, than to others (e.g., artisanal fisheries that are subject to weaker regulation).
-A second important assumption we made is that the fishery manager observes the current stock size correctly when setting the annual quota (see Clark and Kirkwood, Williams + more for alternative specifications).
-However, stock assessments struggle to predict current cohort sizes based as they are on observing past catch history (Ralston et al).
-We might anticipate that when uncertainty regarding reported recruitment pulses is included, we see the tendency for an optimizing manager to moderate their policy responses to initial reports of particularly good recruitment years increase yet further.
+To focus on the effects of policy adjustment costs, we focused narrowly on the basic model specification of Reed (1979) and examined how the predictions of this classic problem were changed by introducing policy adjustment costs of different forms.
+However, there have been many elaborations on Reed’s basic approach that increase the realism of the optimization models involved by relaxing other assumptions (see for example Sethi et al.
+2005; Singh et al.
+2006; McGough et al.
+2009).
+For example, in following Reed’s approach closely another important assumption we made is that the fishery manager observes the current stock size correctly when setting the annual quota (see Clark and Kirkwood 1986, Williams 2001 for alternative specifications).
+However, predictions of current cohort sizes from stock assessments are subject to uncertainty (Ralston et al.
+2011).
+Were uncertainty regarding reported recruitment pulses also included, an optimizing manager might moderate their policy responses to initial reports of particularly good recruitment years increase yet further.
+<!-- NOTE Might be worth saying something like this upfront in the Methods to head off the obvious referee comment from the obvious referees.-->
 
@@
 Such an analysis would involve comparing quotas that were set relative to stock sizes as they were estimated at the time each management decision was taken to try to infer what objective managers were maximizing.
-Some stocks are assessed and some quotas revisited more frequently than others, which provides relevant patterns of variation in policy environments that econometric analyses of this type could try to exploit.
 
 A worthwhile modeling extension suggested by our results would be to examine the implications of policy adjustment costs for risks of stock collapse.
-Examining risks of stock collapse is not possible with the Reed model-formulation that we followed here.
-But using an alternative approach also would be worthwhile in light of our finding that the variance and autocorrelation in stock sizes through time can be affected when accounting for costs of policy adjustment.
-Both are properties known in other modeling settings to be associated with changes to the risk of extinction or of transitions between alternative stable states.
+Examining risks of stock collapse is not possible with the Reed model-formulation that we followed here but would be worthwhile in light of our finding that the variance and autocorrelation in stock sizes through time can be affected when accounting for costs of policy adjustment.
+Both are properties known in other modeling settings to be associated with changes to the risk of extinction or of transitions between alternative stable states (references).
+
+<!--NOTE: Carl – pick your faves and I suggest you highlight things you’ve written! -->
+
+<!-- 
 In such an analysis, it would be interesting to explore more complicated patterns of environmental variability than we have here (e.g., colored environmental noise).
-Another obvious extension would be to combine the different functional forms that we consider rather than studying them in isolation as we have here.
-Finally, a third would be to consider how policy adjustment costs affect approach paths to the long-run management outcomes, which provide the focus for this study.
+Another obvious extension would be to combine the different functional forms that we consider rather than studying them in isolation as we have here.
+Finally, a third would be to consider how policy adjustment costs affect approach paths to the long-run management outcomes, which provide the focus for this study.
+-->
 
-Conclusions
-===========
+<!-- Too many extensions being suggested now -->
 
-Lessons for modelers - ignoring reality of policy costs leads to less effective management (decreased value)
+When facing highly variable ecological systems, how often should natural resource managers respond?
+A highly interventionist strategy would track ecosystem variation very closely.
+Alternatively, a manager might choose only to take action or change policy only when conditions look very different to those previously experienced.
+We took a modeling approach to begin to explore these ideas.
+Specifically, we focused on a well-known problem from fisheries management and examined how optimal management recommendations changed when we accounted for costs associated with frequently changing management decisions.
+While we focused on a fisheries context, our findings would be relevant to many other settings where natural resource managers revisit management decisions through time in light of ecological variability, including game management, management of instream flow rates, fire management, habitat restoration, and managing for endangered species.
+In some ways, the analyses that we present can also be thought of as providing a temporal counter-part to discussions about the optimal spatial scale over which ecosystem management should be conducted.
 
-Lesons for policy makers - decreasing adjustment costs not only saves direct costs but permits higher value solutions.
+<!--Paul writes:
+I can provide some references on this paragraph.
+But would suggest that I wait and let you and others overhaul it first.
+I am not sure it really adds much of value, but it does give us a dismount.
+Moreover,  I’m trying to help you hit your desire to broaden out beyond a fisheries context.
+The key barometer is we should be able to point at a suitable sdp application which we could have used just as easily as the fisheries management context.
+I think we can probably do that for the list provided here.
+-->
+
+Additional references
+
+Clark, C.W. 2010. Mathematical Bioeconomics: The Mathematics of Conservation. 3rd edition. Wiley, Hoboken, NJ.
+
+Clark, C.W., Kirkwood, G.P. 1986. On uncertain renewable resource stocks: optimal harvest policies and the value of stock surveys. J. Environmental Economics and Manage. 13:235-244.
+
+James, G., Witten, D., Hastie, T., Tibshirani, R. 2013. An Introduction to Statistical Learning with Applications in R. Springer, New York.
+
+Kaitala V. 1993. Equilibria in a stochastic resource management game under imperfect information. European Journal of Operational Research 71, 439-453.
+
+Laukkanen, M. 2003. Cooperative and non-cooperative harvesting in a stochastic sequential fishery. J Environmental Economics and Management 45, 454-473.
+
+Lewis, T.R. 1981. Exploitation of a renewable resource under uncertainty. Canadian Journal of Economics 14, 422-439.
+
+McFadden, D. 1975. The revealed preference of a government bureaucracy: theory. Bell Journal of economics 6, 401-416.
+
+McFadden D. 1976. The revealed preference of a government bureaucracy: empirical evidence. Bell Journal of Economics 7, 55-72.
+
+McGough, B., Plantinga, A.J., Costello, C. 2009. Optimally managing a stochastic renewable resource under general economic conditions. B.E. Journal of Economic Analysis & Policy 9, Iss 1, Article 56.
+
+Ralston S., Punt, A.E., Hamel, O.S., DeVore, J.D., Conser, R.J. 2011. A meta-analytic approach to quantifying scientific uncertainty in stock assessments. Fish. Bull. 109: 217-231.
+[NOTE WE CAN CITE STEVE’S PAPER FOR THIS POINT + I LIKE THE PAPER. BUT THE POINT IS PRETTY BEING CLAIMED IS PRETTY ELEMENTARY AND IT’S POSSIBLE WE COULD CITE A STOCK ASSESSMENT TEXTBOOK INSTEAD.]
+
+Rudin, L.I., Osher, S., Fatemi, E. 1992. Nonlinear total variation based noise removal algorithms. Physica D 60, 259-268.
+
+Williams, B.K. 2001. Uncertainty, learning and the optimal management of wildlife> Environmental and Ecological Statistics 8, 269-288.
+
+ALSO REFERENCE TO ADD TO METHODS SECTION
+
+When introducing fixed fee – conceptual analogues to the set-up cost of Reef (1974) and Spulber (1982) but here the fee is associated with a change in harvesting ($h_t\neq h_{t-1}$) and not with harvesting {\em per se} ($h_t>0$) as in those studies.
+
+Reed, W.J. 1974. A stochastic model for the economic management of a renewable animal resource. Mathematical Biosciences 22, 313-337.
+
+Spulber, D.F.
+1982.
+Adaptive harvesting of a renewable resource and stable equilibrium.
+In: Essays in the Economics of Renewable Resources.
+L.J.
+Mirman and D.F.
+Spulber (eds.) North-Holland Publishing, Amsterdam.
+pp.
+117-139.
 

### 2014-07-24 manuscripts/manuscript.Rmd
updated manuscript, draft sent to paul

--- 2014-07-17 manuscripts/manuscript.Rmd
@@
 title: Optimal management of a stochastically varying population when policy adjustment is costly
-
 author: 
@@
 
-layout: preprint
+layout: review,12pt
+linenumbers: true
 
@@
 
+```{r Figure_1, fig.cap="Quota on Blue Fin Tuna Catch", fig.width=4, fig.height=4}
+tuna <- read.csv("components/data/tuna.csv")
+ggplot(tuna, aes(year, quota)) + geom_point()
+```
+
 To illustrate these concepts, Figure 1 show an example from fisheries
@@
 and solution method largely follow Reed's classic treatment on this
-question, a treatment repeated widely in bioeconomic textbooks. With
-his formulation, Reed showed that a constant escapement policy could be
+question, a treatment repeated widely in bioeconomic textbooks. We 
+note that while later work has extended this treatment to deal with 
+a variety of other issues (e.g. @Sethi2005; @Singh2006; @McGough2009),
+we start from the classical model for simplicity of presentation and analysis.
+
+With his formulation, Reed showed that a constant escapement policy could be
 optimal under certain conditions. Such a policy involves choosing annual
@@
 for such a responsive management strategy potentially could be large.
+
+<!-- NOTE perhaps comment on the deviation from constant escapement !-->
 
@@
 
--   Ecosystem management frequently set in terms of policy of quotas.
-
--   Policy relatively static and costly to change
-
--   Meanwhile, the natural world is variable
-
--   Optimal solutions typically track these shocks, resulting in
-    impractical management recommendations in face of policy costs
-
-*Develop a figure to insert here comparing quotas that were set to the
-stock size estimated at that time in the stock assessment for two
-different fish stocks. We choose the two stocks to highlight variation
-in how responsive management can be. Suggested halibut and bluefin
-tuna.*
-
-Empirics suggest not always as responsive as Reed solution. Explore
-conditions under which that makes sense. Idea is that regulator's
-objective sometimes may not be 'raw' NPV, but rather NPV with some
-penalties on fast changes. Possible reasons: pure administrative
-transaction cost of changing policies (reaching agreement), fishermens'
-preferences for less variable quotas, processing plants' preferences for
-less variable quotas especially if tied into contracts for canning and
-so forth. But we do not know what functional form of any such policy
-adjustment costs takes and it will be a lot of work to estimate it. Here
-we explore several plausible candidate functional forms that each
-reflect different ways these policy adjustment costs could work. Would
-be good to know if differences between functional forms is particularly
-important.
-
 Methods
@@
 
-Fish population dynamics / state equation. We will assume Beverton-Holt
-dynamics with multiplicative environmental noise
+Fish population dynamics (state equation)
+-----------------------------------------
+
+We will assume Beverton-Holt dynamics with multiplicative environmental noise
 
@@
 we assume that these are constants with $p>0$ and $c_0>0$. (Examples
-shown here use $p$= `r price` and $c_0$ = `r c0`.) 
-<!-- Mention R code provided to test other values? Do we need to test other values?
-(i.e. the c0 = 0 case?) Word about units?-->
+shown here use $p$= `r price` and $c_0$ = `r c0`, complete code is
+provided in the supplementary materials to re-run these analyses with
+arbitrarily specified values and replot the figures shown).
 
@@
 
-Costs of policy adjustment {#costs-of-policy-adjustment .unnumbered}
+Costs of policy adjustment 
 --------------------------
@@
 
+We note that the fixed cost has conceptual analogues to the set-up cost of
+@Reed1974 and @Spulber1982 but here the fee is associated with a change
+in harvesting ($h_t\neq h_{t-1}$) and not with harvesting *per se*
+($h_t>0$) as in those studies.
+
 Taken together with the state equation Eqn. \eqref{eq:state_equation}, each
@@
 costs are applied to the control variables themselves, as opposed to
-adjustments to the controls: $\Pi_4 (N_t,h_t) = p h_t -  c_0 E_t-c_4E_t^2$. Additional costs of this form tend to have a smoothing effect on optimal quotas, but also change
+adjustments to the controls: $\Pi_4 (N_t,h_t) = p h_t -  c_0 E_t-c_4E_t^2$. 
+Additional costs of this form tend to have a smoothing effect on optimal quotas, but also change
 the long-term average stock size or quota size that is optimal.
 
-Choice of parameters {#choice-of-parameters .unnumbered}
+Choice of parameters 
 --------------------
@@
 choices of $c_i$ so that each has a comparable impact on the optimal net
-present value of fishery, broadly following the example of  @Bovenberg_2008.
+present value of fishery, broadly following the example of @Bovenberg2008.
 
-<!--NOTE Jake to confirm these are still relevant and needed. We are using a less sophisticated normalization than was once discussed and may or may not need the citations now. -->
+<!--NOTE Jake to confirm these are still relevant and needed. 
+        We are using a less sophisticated normalization than was 
+        once discussed and may or may not need the citations now. -->
 
@@
 Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.", dependson="quadcosts", fig.width=4, fig.height=3, cache = fig.cache}
+
+relabel <- c(L1 = substitute(paste(Pi[1])),
+             L2 = substitute(paste(Pi[2])),
+             fixed = substitute(paste(Pi[3])))
+
 ggplot(fees, aes(c2, (npv0-value)/npv0, lty=variable)) + 
@@
   geom_hline(aes(yintercept=reduction), linetype=4) + 
-  xlab("penalty coefficient") +
-  ylab("Reduction in net present value")
+  xlab("Penalty coefficient") +
+  ylab("Reduction in net present value") + 
+  scale_linetype_discrete(labels=relabel)
 
@@
 dashed vertical lines in Figure 1 map the needed cost coefficient $c_i$,
-for each penalty function, such that the fishery is worth 80% of its
+for each penalty function, such that the fishery is worth `r 100*(1-reduction)`% of its
 unconstrained value when optimally managed.
@@
 the fish population is 1 and the equilibrium biomass for the equivalent
-deterministic model without harvesting is 100; specifically, $A=2$ and
-$B=0.01$ in Eqn. (1)). To characterize environmental variability, we
-assume multiplicative shock $Z_t$ is distributed HOW? In addition, we
-show cases where $p=1$, $\delta=0.05$ and $c_0$ is chosen such that the
+deterministic model without harvesting is 10; (specifically, $A=$ `r pars[1]` and
+$B=$ `r pars[2]` in Eqn. (1)). To characterize environmental variability, we
+assume multiplicative shock $Z_t$ is distributed log-normally with 
+log standard deviation $\sigma_g$ = `r sigma_g`. In addition, we
+show cases where $p=$ `r price`, $\delta=$ `r delta` and $c_0=$ `r c0`.
+
+<!-- is chosen such that the
 optimal stock size in the analogous deterministic problem is 5% larger
 than that corresponding to the maximum sustainable yield in biomass
-($c_0=XXX$).
+($c_0=XXX$). -->
 
@@
 
-Effect of policy adjustment costs on optimal quotas and stock sizes {#effect-of-policy-adjustment-costs-on-optimal-quotas-and-stock-sizes .unnumbered}
+Effect of policy adjustment costs on optimal quotas and stock sizes 
 -------------------------------------------------------------------
 
-```{r Figure_3, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=3, fig.width=8, cache = fig.cache}
+```{r Figure_3, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=3, fig.width=5, cache = fig.cache}
 
-fig3_df <- as.data.frame(subset(dt, replicate=='rep_1'))
+fig3_df <- as.data.frame(subset(dt, replicate=='rep_17'))
 fig3_df <- fig3_df[c("time", "fishstock", "alternate", "harvest", "harvest_alt", "penalty_fn")]
@@
 
-ggplot(fig3_df, aes(time, value, col=baseline)) +
-  geom_line() +
-  facet_grid(variable~penalty_fn) + 
+harvest_fig3 <- subset(fig3_df, variable=="harvest")
+fishstock_fig3 <- subset(fig3_df, variable=="fish_stock")
+
+labeller <- function(variable,value){
+    return(relabel[value])
+}
+
+ggplot(harvest_fig3, aes(time, value, col=baseline)) +
+  geom_line(lwd=1) +
+  facet_grid(penalty_fn~., labeller = labeller) + 
   labs(x="time", y="stock size", title = "Example Stock & Harvest Dynamics")
 
-write.csv(fig3_df, "components/data/figure3.csv")
+write.csv(harvest_fig3, "components/data/figure3.csv")
 ```
 
-Figure 3 illustrates how the different forms of adjustment cost can
-impact the optimal policy (lower row) and corresponding stock sizes,
-which are measured here before harvest ($h_t$ being determined after
-observing stock size $x_t$). Each panel is generated against the same
-sequence of random shocks so that they can be compared directly.
-Because stock sizes are measured before harvests, the effect of the 
-penalty on the stock size is not very pronounced, while the effect
-on the harvest chosen shows a systematic deviations from the penalty
-free optimum, depending on the nature of the cost.
+Figure 3 illustrates how the different forms of adjustment cost can impact
+the optimal harvest policy. Corresponding stock sizes, which are measured
+here before harvest ($h_t$ being determined after observing stock size
+$x_t$) and thus show less influence of the policy cost can be seen in the
+supplement.  Each panel is generated against the same sequence of random
+shocks so that they can be compared directly.  The harvest policy chosen
+shows a systematic deviations from the penalty free optimum, depending on
+the nature of the cost.  In each case, the optimal solution without any
+adjustment cost is shown in against the policy induced by optimization
+under the given adjustment penalty (equivalent to a `r 100*reduction`%
+reduction in maximum expected NPV) is overlaid in blue.
 
-In each case, the optimal solution without any adjustment cost is shown in
-against the policy induced by optimization under the given adjustment
-penalty (equivalent to a `r 100*reduction`% reduction in maximum expected NPV) 
-is overlaid in blue.
+<!-- NOTE FIXME make this consistent! -->
 
 When considering the first formulation of policy adjustment costs
-(linear costs, $\Pi_1$), the bottom-left panel of Figure 3 shows a typical pattern, in which
+(linear costs, $\Pi_1$), the first panel of Figure 3 shows a typical pattern, in which
 the optimal policy tends to avoid small policy adjustments, resulting in
@@
 might expect, because the magnitude of the adjustment made is not
-reflected in the resulting penalty. Whereas the optimal solution for
-$\Pi_1$ attempts to accommodate the large oscillations at the end of the
-period shown (time steps $t=47-49$) with a constant quota in between the
-extremes, the fixed fee version takes the opposite approach of one very
-large swing.
+reflected in the resulting penalty.
 
@@
 
-```{r Figure_4_alt, fig.cap="Variance and autocorrelation of stock dynamics and harvest dynamics, as a function of the penalty coefficient.
+```{r Figure_4, fig.cap="Variance and autocorrelation of stock dynamics and harvest dynamics, as a function of the penalty coefficient.
 Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8, cache=fig.cache}
@@
   coord_cartesian(xlim = c(0, .3)) + 
-  facet_wrap(~ timeseries + statistic, scale="free_y")
+  facet_wrap(~ timeseries + statistic, scale="free_y") + 
+  scale_color_discrete(labels=relabel, name="Penalty function") + 
+  xlab("Penalty size (as fraction of NPV0)")
 
@@
 
-Consequences of policy adjustment costs {#consequences-of-policy-adjustment-costs .unnumbered}
+Consequences of policy adjustment costs 
 ---------------------------------------
@@
 setnames(profits, "V1", "profits")
-hist_dat <- melt(cbind(profits, costs = costs$V1, 
-                       reed_profits = reed_profits$V1, reed_costs = reed_costs$V1),
-                 id = c("penalty_fn", "replicate"))
+setnames(reed_profits, "V1", "profits")
+
+Reed <- cbind(reed_profits, costs = reed_costs$V1, Assumption = "Reed") 
+Adj <- cbind(profits, costs = costs$V1, Assumption = "Adjustment penalty")
+
+hist_dat <- melt(rbind(Adj, Reed), id=c("penalty_fn", "replicate", "Assumption"))
 ````
 
-```{r Figure_5}
-ggplot(hist_dat) + geom_density(aes(value, fill=variable), alpha=0.6)+facet_wrap(~penalty_fn)
+```{r Figure_5, fig.cap="Distribution of profits from fishing and costs paid to adjustment.
+Distributions are shown when managing a system in which the adjustment costs present are determined by the model indicated, and compared to the same costs and profits of managing the same system using a Reed model, which ignores adjustment costs, and thus tends to pay much higher fees for adjustment.
+In contrast, the difference in profit after accounting for costs is only marginally less than the value derived by managing the population to optimize profits when ignoring adjustment costs (Reed model).", fig.width=6, fig.height=5, dependson="histogram-calc"}
+
+assume <- levels(as.factor(hist_dat$Assumption))
+labeller <- function(variable,value){
+if (variable=='penalty_fn') {
+    return(relabel[value])
+  } else {
+    return(assume[value])
+  }
+}
+
+ggplot(hist_dat) + 
+  geom_density(aes(value, fill=variable, color=variable), alpha=0.8)+
+  facet_grid(Assumption~penalty_fn, labeller = labeller)
+
 write.csv(hist_dat, "components/data/figure5.csv")
@@
 Histograms for the different contributions labelled $[1]-[4]$ here when
-taken across 100 replicate runs are shown are shown in Figure 5
-(contribution $[1]$ red, $[2]$ green, $[3]$ blue, and $[4]$ mauve). The
+taken across 100 replicate runs are shown are shown in Figure 5.
+<!--(contribution $[1]$ red, $[2]$ green, $[3]$ blue, and $[4]$ mauve).--> The
 cost of assuming policy adjustments are present when in fact they are
@@
 sum from term $[1]$ from the contribution to the second infinite sum of
-term $[3]$ (blue - red in the Figure). (Note that convergence properties
+term $[3]$. (Note that convergence properties
 required to do this are met because we assume a positive discount rate).
@@
 names(table1) = c("penalty.fn", "ignoring", "assuming", "reduction")
-
 table1_long <- melt(table1, id = c('penalty.fn', 'reduction'))
 table1_long$reduction <- as.factor(table1_long$reduction)
+table1_long <- subset(table1_long, reduction != "0.3")
 ggplot(table1_long, aes(penalty.fn, value, fill = variable)) + 
-  geom_bar(stat="identity", position="dodge") + facet_wrap(~reduction) 
+  geom_bar(stat="identity", position="dodge") + 
+  facet_wrap(~reduction, ncol=2) + 
+  scale_x_discrete(labels = c('L1' = substitute(paste(Pi[1])),
+                              'L2' = substitute(paste(Pi[2])),
+                              'fixed' = substitute(paste(Pi[3])))) + 
+  xlab("Penalty function")
 write.csv(table1_long, "components/data/figure6.csv")
@@
 
-When policy costs are present, assuming the wrong functional form may or may not be worse than ignoring the presence of policy costs all together.
-Figure 7 considers several such cases.
-The X axis labels indicate first which policy is being used to drive the harvest decisions, and then which penalty is actually being applied.
-Thus `L1_L2` indicates a policy calculated under the linear $L_1$ costs, when the reality involves quadratic $L_2$ costs.
-Though the coefficients of the $L_2$ costs have been scaled such that the net effect is the same, the inferred policies differ.
-As a result, the value is slightly more than half of the optimal free solution when the expected reduction should only be 10% less than optimal free.
-In this case, ignoring the costs all together is still worse than using L1 costs -- the red bar is lower than the blue.
+When policy costs are present, assuming the wrong functional form may or
+may not be worse than ignoring the presence of policy costs all together.
+Figure 7 considers several such cases.  The X axis labels indicate
+first which policy is being used to drive the harvest decisions, and
+then which penalty is actually being applied.  Thus $\Pi_1\_\Pi_2$ indicates
+a policy calculated under the linear ($\Pi_1$) costs, when the reality
+involves quadratic ($\Pi_2$) costs.  Though the coefficients of the ($\Pi_2$)
+costs have been scaled such that the net effect is the same, the inferred
+policies differ.  As a result, the value is slightly more than half of
+the optimal free solution when the expected reduction should only be 10%
+less than optimal free. In this case, ignoring the costs all together
+is still worse than using $\Pi_1$ costs -- the red bar is lower than the blue.
 
-For fixed costs, the reverse is true.
-Because fixed costs increase the volatility of the optimal solution while L2 costs decrease it, simply ignoring the cost of adjustment all together results in a higher value than either assuming costs are quadratic $L_2$ when they are fixed, or assuming they are fixed when they are quadratic.
+For fixed costs ($\Pi_3$), the reverse is true.  Because fixed costs increase the
+volatility of the optimal solution while $\Pi_2$ costs decrease it, simply
+ignoring the cost of adjustment all together results in a higher value
+than either assuming costs are quadratic ($\Pi_2$) when they are fixed ($\Pi_3$),
+or assuming they are fixed when they are quadratic.
 
-Nevertheless, assuming quadaratic costs is always the most conservative option -- scenarios in which true costs are quadratic (regardless of what cost structure is assumed by the policy) do significantly worse than those that are not (i.e.
-all cases that assume quadratic but actually have linear or fixed costs).
+Nevertheless, assuming quadratic costs is always the most conservative
+option -- scenarios in which true costs are quadratic (regardless of what
+cost structure is assumed by the policy) do significantly worse than
+those that are not (i.e. all cases that assume quadratic but actually
+have linear or fixed costs).
 
-These patterns hold across the different size reductions shown (from 10% to 25%), though net present value becomes negative under the quadratic form for the larger penalties as costs paid for adjustments exceed profits derived from harvest.
-(Though optimal solutions will always avoid negative net present values, these scenarios in which policies are applied under conditions other than assumed in the optimality calculation have no such guarentee.) For each scenario, results are averaged over 100 replicates.
+These patterns hold across the different size reductions shown (from 10%
+to 25%), though net present value becomes negative under the quadratic
+form for the larger penalties as costs paid for adjustments exceed
+profits derived from harvest.  (Though optimal solutions will always
+avoid negative net present values, these scenarios in which policies are
+applied under conditions other than assumed in the optimality calculation
+have no such guarantee.) For each scenario, results are averaged over
+100 replicates.
 
@@
   geom_bar(stat="identity", position="dodge") + 
-  facet_wrap(~reduction, scales="free_y")
-
+  facet_wrap(~reduction, scales="free_y") +
+  scale_x_discrete(labels = c('L1_L2' = substitute(paste(Pi[1],"_", Pi[2])), 
+                              'L2_L1' =  substitute(paste(Pi[2],"_", Pi[1])),
+                              'L1_fixed' = substitute(paste(Pi[1],"_", Pi[3])), 
+                              'fixed_L1' =  substitute(paste(Pi[3],"_", Pi[1])),
+                              'fixed_L2' = substitute(paste(Pi[3],"_", Pi[2])), 
+                              'L2_fixed' =  substitute(paste(Pi[2],"_", Pi[3])))) + 
+  xlab("Penalty function")
 write.csv(table2_long, "components/data/figure7.csv")
@@
 
-<!--
+<!-- Pasted from external word doc, see Boettiger_Discussion_draft.docx for latest version of discussion -->
 
-TO COME PENDING WHAT THE RESULTS SHOW.
+Policy-makers managing ecological systems that vary in space and time
+must evaluate how much of that variation to reflect in management
+recommendations. Fine-tuning a policy to respond to frequent variations
+in ecological dynamics may incur increased transaction costs associated
+with constantly revisiting past policy decisions. A more pragmatic
+approach would be one that balances benefits from responding to frequent
+variations in ecological conditions with the increased transaction costs
+involved. As a first step towards exploring these ideas, we revisited
+a classic problem from bioeconomics concerning the optimal management
+of a fish stock subject to stochastically varying recruitment [@Reed1979; @Clark2010]. 
+We examined how optimal policy recommendations, here
+annual catch quotas, changed when accounting for costs associated with
+policy adjustment and what the implications of following these policy
+recommendations would be for the exploited population. We also compared
+how the value of the fishery is affected by managers either under-
+or over-estimating the importance of policy adjustment costs of this type.
 
--   From Meeting 3: Interest in how the inclusion of these costs would
-    operationally put a population at greater risk of extinction (e.g.
-    if including the transaction costs increases the variance and
-    autocorrelation of $N$ when subject to the optimal policy). Should
-    expect this, because as the transaction costs become infinite, you
-    would never change your policy which puts you in the world of open
-    loop control - TAC fixed for all time, which we know puts the stock
-    at greater risk of extinction.
+Estimating policy adjustment costs and how they respond to the size of
+proposed policy changes would be empirically challenging. Recognizing
+this fact, in our analyses, we compared different plausible forms that
+these costs might take. We compared two cost structures where we assumed
+the magnitude of policy adjustment costs increased with the magnitude
+of the change in policy being proposed with an alternative formulation
+in which we assumed there was a fixed cost associated with making any
+change to current policy. While each formulation clearly provides only a
+very phenomenological representation of the policy setting environment,
+we believe that each enables us to explore meaningful differences in how
+policy adjustment costs might operate. That being said, in the real-world
+we might expect the different types of adjustment cost to operate in
+combination. Interestingly, there are analogues between how we have
+represented different types of policy adjustment costs in our models
+and regularization techniques that are sometimes used in model fitting
+to address concerns about over-specifying models (e.g. ridge or lasso
+regression or total variation denoising approaches
+[@Rudin1992]).
 
--   On Table 1 should flag that might also be good to look at
-    autocorrelated environmental noise and how that affects thing. Here
-    we look at how the optimal policy induces more color in the stock
-    size EVEN though the environmental variability going into it is
-    white noise. - QUERY - HOW MUCH AUTOCORRELATION INDUCED BY STOCK
-    DYNAMICS IN THE ABSENCE OF HARVESTING
+<!-- NOTE
 
--   for case of bluefin, interpreting (1), (2), (3), and (4) in terms of
-    how much you would have available to pay the Japanese and Canadians
-    to convince them to participate in an expedited process to change
-    TACs. Similarly for other contexts.
+Have wondered about cutting this, but does broaden things out a bit from
+just econ referencing and context.
 
--   Comparison of the optimal policy solution to the Reed model,
-    traditional economic smoothing penalty - which now appears in SI
+Also more people will have heard about ridge and lasso, but I actually
+think they're not as relevant as the total variation suggestion, because
+it applies to the gradient whereas they do not. So really a more accurate
+statement is that the difference between lasso and ridge and the total
+variation approach is in some ways analogous to the difference between
+costs on h or E and costs on dh/dt or dE/dt. But that's way too many
+words now
 
--   Comparison between the different functional forms -- smoothing (L2)
-    non-smoothing (L1), and de-stablizing (fixed).
+Carl B - when it comes to references, you may have others you would
+prefer here
 
--   Induced costs (relative to free adjustment) vs direct costs (paid
-    for adjusting)
-
--   Contrast steady-state results to dynamic solutions under stochastic
-    shocks.
-
-**Key conclusions:**
-
-1.  **Lesson for modelers**: Ignoring the reality of policy costs leads
-    to less effective management (decreased value) (increased extinction
-    risk?)
-
-2.  **Lesson for policy makers**: Decreasing adjustment costs not only
-    saves direct costs, but permits higher-value solutions.
 -->
 
-<!-- Pasted from external word doc, see Boettiger_Discussion_draft.docx for latest version of discussion -->
+The biggest differences between the representations of policy adjustment
+cost that we consider are between those that have a smoothing effect
+on annual quotas and those that do not. The few past studies that
+incorporate policy adjustment costs in models of fisheries management
+[@Ludwig1980; @Feichtinger1994; @Wirl1999] assumed costs of
+policy adjustment increased as a quadratic function of the magnitude of
+the policy change being proposed (our $\Pi_2$ formulation in Eqn.) In
+effect, this means that small changes to annual quotas incur little
+extra cost, but large changes to annual quotas become disproportionately
+expensive to make. Including costs of this form smoothes inter-annual
+variation in the catch quotas that would be recommended. However, as
+catches become less variable through time, the variability in the fish
+population itself increases. In essence, the optimal policy no longer
+soaks up as much of the natural variability in recruitment that is
+affecting the population. Also, the catches and remaining stock sizes
+corresponding to optimal management become more autocorrelated in time,
+because it takes the fishery longer to harvest down peaks in abundance
+that follow large recruitment pulses. The effects of smoothing here are
+similar to those predicted when assuming the cost per unit effort is
+increasing in the amount of effort expended (e.g., @Lewis1981, @McGough2009; 
+see Supporting Information for a summary of the relevant
+results) as opposed to associating extra costs with changes to policy
+*per se*. Smoothing effects of this type are what one might have
+expected when including policy adjustment costs.
 
-Policy-makers managing ecological systems that vary in space and time must evaluate how much of that variation to reflect in management recommendations in order to achieve a desirable management outcome.
-Fine-tuning a policy to respond to frequent variations in ecological dynamics may incur increased transaction costs associated with constantly revisiting past policy decisions.
-A more pragmatic approach might be one that balances benefits from responding to frequent variations in ecological conditions with the increased transactions costs involved.
-As a first step towards exploring these ideas, we revisited a classic problem from bioeconomics concerning the optimal management of a fish stock subject to stochastically varying recruitment (Reed, Clark).
-We examined how optimal policy recommendations, here annual catch quotas, changed when accounting for costs associated with policy adjustment and what the implications of following these policy recommendations would be for the exploited population.
-We also compared how the value of the fishery is affected by managers either under- or over-estimating the importance of policy adjustment costs of this type.
+Standing in sharp contrast to these smoothing predictions is our
+finding that including policy adjustment costs can actually _increase_ the
+variability of quotas through time if there is a fixed cost associated
+with making any changes to current policy (e.g. costs of running relevant
+stakeholder meetings and public consultations on proposed policy changes,
+$\Pi_3$). With this formulation, as stock sizes vary in response to
+recruitment, the fishery manager must balance the cost of brokering
+a policy change with the cost in forgone fisheries revenue from not
+responding to favorable recruitment pulses. The optimal policy involves
+ignoring small variations in recruitment, but then assigns a larger quota
+when particularly strong recruitment years arise than would have been
+the case in the absence of policy adjustment costs. The other functional
+form we consider, in which the costs of policy adjustment scale linearly
+with the size of the adjustment ($Pi_1$), has less obvious effects on
+optimal policies. But interestingly, it is the only formulation for
+which we observed positive unchanging quotas of the type most commonly
+encountered in real-world applications.
 
-Estimating policy adjustment costs and how they respond to the size of proposed policy changes would be empirically challenging.
-Recognizing this fact, in our analyses, we compared different plausible forms that these costs might take.
-We compared two cost structures where we assumed the magnitude of policy adjustment costs increased with the magnitude of the change in policy being proposed with an alternative formulation in which we assumed there was a fixed cost associated with making any change to current policy.
-While each formulation clearly provides only a very phenomenological representation of the policy setting environment, we believe that each enables us to explore meaningful differences in how policy adjustment costs might operate.
-That being said, in the real-world we might expect the different types of adjustment cost to operate in combination.
-Interestingly, there are analogues between how we have represented different types of policy adjustment costs in our models and regularization techniques (e.g.
-ridge or lasso regression approaches) that are sometimes in model fitting to address concerns about over-specifying models (REFERENCES).
+That the different representations of policy adjustment costs result in
+such different dynamics suggests that researchers constructing fisheries
+economics models should proceed cautiously when choosing how to represent
+these costs. However, in our own experience, we have found that while
+modeling studies sometimes mention policy adjustment costs when motivating
+model assumptions (references), they rarely provide much justification
+for the choice of functional form used or test the sensitivity of any
+conclusions drawn to alternative specifications. Indeed, we were surprised
+to find such clear differences between the functional forms, because
+we anticipated that the limiting case of increasing policy adjustment
+costs within each functional form should be the same, namely a constant
+annual quota that does not change through time (open-loop control).
 
-The biggest differences between the different representations of policy adjustment cost that we consider are between those that have a smoothing effect on annual quotas and those that do not.
-The few past studies that incorporate policy adjustment costs in models of fisheries management (e.g.
-Ludwig, Feichtinger, Wirl) assumed costs of policy adjustment increased as a quadratic function of the magnitude of the policy change being proposed (our $\Pi_2$ formulation in Eqn.) In effect, this means that small changes to annual quotas incur little extra cost, but large changes to annual quotas become disproportionately expensive to make.
-Including costs of this form smoothes inter-annual variation in the catch quotas that would be recommended.
-However, as catches become less variable through time, the variability in the fish population itself increases.
-In essence, the optimal policy no longer soaks up as much of the natural variability in recruitment that is affecting the population.
-Also, the catches and remaining stock sizes corresponding to optimal management become more autocorrelated in time, because it takes the fishery longer to fish down peaks in abundance that follow large recruitment pulses.
-The effects of smoothing here are similar to those predicted when assuming the cost per unit effort is increasing in the amount of effort expended, as is common in many fisheries bioeconomics models (references).
-Note this assumption is different from associating extra costs with changes to policy per se (see Supporting Information for the relevant results).
-Moreover, smoothing effects of this type are what one would have expected when including policy adjustment costs.
+We also compared the efficiency costs that would result from failing
+to account for policy adjustment cost if they are present with those
+involved in assuming them when in fact they are absent. The results
+of this comparison were not sensitive to the particular form of policy
+adjustment costs assumed. Instead, we always found the efficiency costs
+of ignoring policy adjustment costs when they were present to be much
+larger than the efficiency costs of assuming policy adjustment costs
+applied when they were in fact absent. Policy adjustment costs affect
+the overall value of the fishery in two ways here. First, there is the
+direct cost associated with each quota change. Second there is a cost in
+foregone revenue from missed catches when not following what would be the
+optimal policy if quotas were free to track recruitment variability. Our
+finding that it is more costly to ignore policy adjustment costs when
+they are present arises because the first, more direct, cost contribution
+here is larger than the second.
 
-Therefore, standing in sharp contrast to these smoothing predictions is our finding that including policy adjustment costs can actually increase the variability of quotas through time if there is a fixed cost associated with making any changes to current policy (e.g.
-costs of running relevant stakeholder meetings and public consultations on proposed policy changes, $\Pi_3$).
-With this formulation, as stock sizes vary in response to recruitment, the fishery manager must balance the cost of brokering a policy change with the cost in forgone fisheries revenue from not responding to favorable recruitment pulses.
-The optimal policy involves ignoring small variations in recruitment, but then assigns a larger quota when particularly strong recruitment years arise than would have been the case in the absence of policy adjustment costs.
-The other functional form we consider, in which the costs of policy adjustment scale linearly with the size of the adjustment ($Pi_1$), has less obvious effects on optimal policies.
-But interestingly, it is the only formulation for which we observed positive unchanging quotas of the type most commonly encountered in real-world applications.
+Assuming an adjustment cost exists when in fact it is absent is not the
+same as using the wrong functional form when it is present.  Here, our
+results showed that choice of the functional form makes a significant
+difference.  We show it can be better to ignore policy costs than to derive a 
+policy based on assuming the wrong functional form.  This result further
+underscores the importance of modelers using caution when seeking to account
+for these costs. Assuming an arbitrary form in order to capture the influence
+of adjustment costs is thus unlikely to be instructive.
 
-That the different representations of policy adjustment costs result in such different dynamics suggests that researchers constructing fisheries economics models should proceed cautiously when choosing how to represent these costs.
-However, in our own experience, we have found that while modeling studies sometimes mention policy adjustment costs when motivating model assumptions (references), they rarely provide much justification for the choice of functional form used or test the sensitivity of any conclusions drawn to alternative specifications.
-That we found such clear differences between the functional forms is perhaps also surprising, because one might anticipate that the limiting case of increasing policy adjustment costs within each functional form should be the same, namely a constant annual quota that does not change through time (open-loop control).
+As with any modeling analysis, our formulation makes many assumptions. For
+example, we assume that the fishery in question is being optimally managed
+by a policy-maker who acts as the 'sole owner' of the stock. This approach
+is different to models that assume fisheries are not well-managed,
+e.g. by assuming open access conditions (references [^1]),
+or ones that derive policy recommendations endogenously by modeling
+interactions between different stakeholders [@Kaitala1993, @Laukkanen2003].
+As such, we anticipate that our approach will be more relevant to
+some fisheries, particularly domestic fisheries in developed countries
+that are subject to relatively strong regulatory regimes, than to others
+(e.g., artisanal fisheries that are subject to weaker regulation). To
+focus on the effects of policy adjustment costs, we focused narrowly
+on the basic model specification of @Reed1979 and examined how the
+predictions of this classic problem were changed by introducing policy
+adjustment costs of different forms. However, there have been many
+elaborations on Reed's basic approach that increase the realism of
+the optimization models involved by relaxing other assumptions (see for
+example @Sethi2005; @Singh2006; @McGough2009). For
+example, in following Reed's approach closely another important
+assumption we made is that the fishery manager observes the current stock
+size correctly when setting the annual quota (see @Clark1986,
+@Williams2001 for alternative specifications). However, predictions of
+current cohort sizes from stock assessments are subject to uncertainty
+[@Ralston2011]. Were uncertainty regarding reported recruitment
+pulses also included, an optimizing manager might moderate their policy
+responses to initial reports of particularly good recruitment years
+increase yet further.
 
-We also compared the efficiency costs that would result from failing to account for policy adjustment cost if they are present with those involved in assuming them when in fact they are absent.
-The results of this comparison were not sensitive to the particular form of policy adjustment costs assumed.
-Instead, we always found the efficiency costs of ignoring policy adjustment costs when they were present to be much larger than the efficiency costs of assuming policy adjustment costs applied when they were in fact absent.
-Policy adjustment costs affect the overall value of the fishery in two ways here.
-First, there is the direct cost associated with each quota change.
-Second there is a cost in foregone revenue from missed catches when not following what would be the optimal policy if quotas were free to track recruitment variability.
-Our finding that it is more costly to ignore policy adjustment costs when they are present arises because the first, more direct, cost contribution here is larger than the second.
+[^1]: NOTE Would be good to give an open access model in a fluctuating
+environment here. From Andersen and Sutinen's review (Mar Res Econ
+1, 117-136) it looks like one basal citation is Andersen 1981 The
+exploitation of fish resources under stock uncertainty. But it is a
+'staff paper'. Our library don't hold it. Has anyone else got it?
 
-As with any modeling analysis, our formulation makes many assumptions.
-For example, we assume that the fishery in question is being optimally managed by a policy-maker who acts as the 'sole owner' of the stock.
-This approach is different to models that assume fisheries are not well-managed, e.g.
-by assuming open access conditions (references), or ones that derive policy recommendations endogenously by modeling interactions between different stakeholders (game theory references).
-As such, we anticipate that our approach will be more relevant to some fisheries, particularly domestic fisheries in developed countries that are subject to relatively strong regulatory regimes, than to others (e.g., artisanal fisheries that are subject to weaker regulation).
-A second important assumption we made is that the fishery manager observes the current stock size correctly when setting the annual quota (see Clark and Kirkwood, Williams + more for alternative specifications).
-However, stock assessments struggle to predict current cohort sizes based as they are on observing past catch history (Ralston et al).
-We might anticipate that when uncertainty regarding reported recruitment pulses is included, we see the tendency for an optimizing manager to moderate their policy responses to initial reports of particularly good recruitment years increase yet further.
+One obvious research avenue suggested by our models is that of empirically
+estimating costs of policy adjustment. A direct estimation approach
+could quantify some sources of policy adjustment costs, e.g. costs to
+processing plants that arise from having more variable catches. However,
+other more intangible sources of policy adjustment costs, e.g. preferences
+of policy-makers or different stakeholders for less variable quotas,
+might be missed. An alternative, more holistic, approach would be to
+apply revealed preference methods to fisheries management agencies
+themselves, in the tradition of [@McFadden1975; @McFadden1976]. Such an analysis
+would involve comparing quotas that were set relative to stock sizes as
+they were estimated at the time each management decision was taken to
+try to infer what objective managers were maximizing.
 
-One obvious research avenue suggested by our models is that of empirically estimating costs of policy adjustment.
-A direct estimation approach could quantify some sources of policy adjustment costs, e.g.
-costs to processing plants that arise from having more variable catches.
-However, other more intangible sources of policy adjustment costs, e.g.
-preferences of policy-makers or different stakeholders for less variable quotas, might be missed.
-An alternative, more holistic, approach would be to apply revealed preference methods to fisheries management agencies themselves, in the tradition of McFadden (1975, 1976).
-Such an analysis would involve comparing quotas that were set relative to stock sizes as they were estimated at the time each management decision was taken to try to infer what objective managers were maximizing.
-Some stocks are assessed and some quotas revisited more frequently than others, which provides relevant patterns of variation in policy environments that econometric analyses of this type could try to exploit.
+A worthwhile modeling extension suggested by our results would be to
+examine the implications of policy adjustment costs for risks of stock
+collapse. Examining risks of stock collapse is not possible with the
+Reed model-formulation that we followed here but would be worthwhile
+in light of our finding that the variance and autocorrelation in stock
+sizes through time can be affected when accounting for costs of policy
+adjustment. Both are properties known in other modeling settings to
+be associated with changes to the risk of extinction or of transitions
+between alternative stable states [@Scheffer2009; @Boettiger2013].
 
-A worthwhile modeling extension suggested by our results would be to examine the implications of policy adjustment costs for risks of stock collapse.
-Examining risks of stock collapse is not possible with the Reed model-formulation that we followed here.
-But using an alternative approach also would be worthwhile in light of our finding that the variance and autocorrelation in stock sizes through time can be affected when accounting for costs of policy adjustment.
-Both are properties known in other modeling settings to be associated with changes to the risk of extinction or of transitions between alternative stable states.
-In such an analysis, it would be interesting to explore more complicated patterns of environmental variability than we have here (e.g., colored environmental noise).
-Another obvious extension would be to combine the different functional forms that we consider rather than studying them in isolation as we have here.
-Finally, a third would be to consider how policy adjustment costs affect approach paths to the long-run management outcomes, which provide the focus for this study.
+<!-- NOTE: Too many extensions being suggested now -->
 
-Conclusions
-===========
+When facing highly variable ecological systems, how often should
+natural resource managers respond? A highly interventionist strategy
+would track ecosystem variation very closely. Alternatively, a manager
+might choose only to take action or change policy only when conditions
+look very different to those previously experienced. We took a modeling
+approach to begin to explore these ideas. Specifically, we focused on
+a well-known problem from fisheries management and examined how optimal
+management recommendations changed when we accounted for costs associated
+with frequently changing management decisions. While we focused on a
+fisheries context, our findings would be relevant to many other settings
+where natural resource managers revisit management decisions through
+time in light of ecological variability, including game management,
+management of in-stream flow rates, fire management, habitat restoration,
+and managing for endangered species. In some ways, the analyses that
+we present can also be thought of as providing a temporal counter-part
+to discussions about the optimal spatial scale over which ecosystem
+management should be conducted.
 
-Lessons for modelers - ignoring reality of policy costs leads to less effective management (decreased value)
-
-Lesons for policy makers - decreasing adjustment costs not only saves direct costs but permits higher value solutions.
+<!-- NOTE Paul writes: I can provide some references on this paragraph. But
+would suggest that I wait and let you and others overhaul it first. I
+am not sure it really adds much of value, but it does give us a
+dismount. Moreover,  I'm trying to help you hit your desire to broaden
+out beyond a fisheries context. The key barometer is we should be able
+to point at a suitable sdp application which we could have used just as
+easily as the fisheries management context. I think we can probably do
+that for the list provided here.  -->
 
@@
 
-```{r Figure_1S, dependson="tidy", fig.cap="Multiple realizations of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.
-Note that while fish stock dynamics appear similar in penalty and non-penalty scenarios, the harvest dyanmics show clear patterns depending on the type of penalty.", fig.height=3, fig.width=8, cache=fig.cache}
+```{r Figure_S1, dependson="tidy", fig.cap="Multiple realizations of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=10, fig.width=8, cache=fig.cache}
 
-fig1s_df <- as.data.frame(subset(dt, replicate %in% paste0('rep_', 1:5)))
+fig1s_df <- as.data.frame(subset(dt, replicate %in% paste0('rep_', 11:20)))
 fig1s_df <- fig1s_df[c("time", "fishstock", "alternate", "harvest", "harvest_alt", "penalty_fn", "replicate")]
@@
 
-ggplot(fig1s_df, aes(time, value, col=baseline, lty=replicate)) +
-  geom_line() +
-  facet_grid(variable~penalty_fn) + 
+fig1s_df <- subset(fig1s_df, variable=="harvest")
+labeller <- function(variable,value){
+if (variable=='penalty_fn') {
+    return(relabel[value])
+  } else {
+    return(value)
+  }
+}
+
+ggplot(fig1s_df, aes(time, value, col=baseline)) +
+  geom_line(lwd=1) +
+  facet_grid(replicate ~ penalty_fn, labeller=labeller) + 
+  labs(x="time", y="stock size", title = "Example Stock & Harvest Dynamics")  
+write.csv(fig1s_df, "components/data/figure_s1.csv")
+
+```
+
+```{r Figure_S2, dependson="tidy", fig.cap="Example realization of resulting fish stock sizes under the different functional forms of adjustment costs, corresponding to policies shown in Figure 3.
+Because stock sizes are measured before harvests, the effect of the penalty on the stock size is not as pronounced.", fig.height=3, fig.width=8, cache = fig.cache}
+
+labeller <- function(variable,value){
+    return(relabel[value])
+}
+
+ggplot(fishstock_fig3, aes(time, value, col=baseline)) +
+  geom_line(lwd=1) +
+  facet_grid(penalty_fn~., labeller = labeller) + 
   labs(x="time", y="stock size", title = "Example Stock & Harvest Dynamics")
 
+write.csv(fishstock_fig3, "components/data/figure_s2.csv")
 ```
@@
 Percent reduction refers to penalty coefficient being calibrated to achieve the given percent reduction relative to ENPV0 when the penalty is optimally accounted for.
-Comparing the second and third columns shows that ignoring a real cost is a significantly graver error, particularly in the case of quadratic (L2) costs."
+Comparing the second and third columns shows that ignoring a real cost is a significantly graver error, particularly in the case of quadratic costs."
 ```
@@
 
+```{r Figure_5_alt, fig.cap="**Alternate Figure 5**.
+Distribution of profits from fishing and costs paid to adjustment.
+Distributions are shown when managing a system in which the adjustment costs present are determined by the model indicated, and compared to the same costs and profits of managing the same system using a Reed model, which ignores adjustment costs, and thus tends to pay much higher fees for adjustment.
+In contrast, the difference in profit after accounting for costs is only marginally less than the value derived by managing the population to optimize profits when ignoring adjustment costs (Reed model).", fig.width=3, fig.height=5, dependson="histogram-calc"}
+
+hist_dat_alt <- melt(cbind(profits, costs = costs$V1, 
+                       reed_profits = reed_profits$profits, reed_costs = reed_costs$V1),
+                 id = c("penalty_fn", "replicate"))
+
+ggplot(hist_dat_alt) + 
+  geom_density(aes(value, fill=variable, color=variable), alpha=0.8)+
+  facet_grid(penalty_fn~., labeller = labeller)
+
+```
+
 # References

### 2014-07-24 manuscripts/presentation.Rmd
skeleton for esa slides

--- 2014-07-24 manuscripts/manuscript.Rmd
@@
 ---
-title: Optimal management of a stochastically varying population when policy adjustment is costly
+title: "Fisheries management when quotas are costly to change"
+date: "07/24/2014"
+output: ioslides_presentation
+
 author: 
@@
 
-abstract: |
-          Ecological systems are dynamic and policies to manage them need to
-          respond to that variation. However, policy adjustments will sometimes
-          be costly, which means that fine-tuning a policy to track variability in
-          the environment very tightly will only sometimes be worthwhile. We use a
-          classic fisheries management question -- how to manage a stochastically
-          varying population using annually varying quotas in order to maximize
-          profit  - to examine how costs of policy adjustment change optimal
-          management recommendations. Costs of policy adjustment (here changes in
-          fishing quotas through time) could take different forms. For example,
-          these costs may respond to the size of the change being implemented or
-          there could be a fixed cost any time a quota change is made. We show
-          how different forms of policy costs have contrasting implications for
-          optimal policies. While some types of cost act to smooth out variation in
-          quotas and stock sizes, as one might have expected, others can actually
-          increase variation in stock sizes and quotas through time. We also show
-          that the potential economic impact on the fishery of managers assuming
-          policy adjustment costs are present when in fact they are absent is much
-          smaller than the impact of managers assuming such costs are absent if
-          they are present.
-
-layout: review,12pt
-linenumbers: true
-
-bibliography: components/references.bib
-csl: components/ecology.csl
-documentclass: components/elsarticle
-
-output:
-  pdf_document:
-    template: components/elsarticle.latex
-    fig_caption: true
 ---
@@
 library("knitr")
-basename <- "manuscript"
+basename <- "presentation"
 opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
@@
 
-Introduction
-============
-
-Ecosystems are dynamic and exhibit rich patterns of variability in
-both time and space. In designing management policies for ecosystems,
-managers need to decide how much of that variation to respond to. Managers
-could try to track variations in ecosystem dynamics very closely by
-setting policies that are extremely responsive to the environment. Many
-theoretical studies that seek to identify optimal policies for exploited
-populations and communities adopt this approach and largely ignore the
-challenges that would be involved in implementing such recommendations
-[e.g., @Reed1979; @Neubert2003; @Sethi2005; @Halpern2011]. However, 
-the policy process can often be much more sluggish
-to respond to variations in ecosystem dynamics [@Walters1978; @Armsworth2010]. 
-Moreover, stakeholders impacted by ecosystem management
-may prefer some stability and not want to deal with continually changing
-management recommendations [@Biais1995; @Armsworth2003;
-@Patterson2007a; @Patterson2007b; @Sanchirico2008].
-In other words, whatever gains are available from fine-tuning a
-policy prescription to reflect environmental variation more closely
-should be traded off against potential costs associated with the more
-interventionist approach to management this would require.
-
-```{r Figure_1, fig.cap="Quota on Blue Fin Tuna Catch", fig.width=4, fig.height=4}
+```{r Figure_1, fig.cap="Quota on Blue Fin Tuna Catch", dev=c("svg", "png")}
 tuna <- read.csv("components/data/tuna.csv")
@@
 
-To illustrate these concepts, Figure 1 show an example from fisheries
-management. On the left axis, the figure shows a time series for the
-estimated population size, represented as spawning stock biomass, of
-west Atlantic bluefin tuna (_Thunnus thynnus_, henceforth bluefin) from
-a recent stock assessment [@ICCAT20XX].  On the right axis the figure
-also shows the catch quota for the stock that was set by the relevant
-management agency [@ICCAT20XX]. Despite the estimated population size
-declining by XX% between YYYY and ZZZZ, the quota was not changed during
-this period. Instead, the quota only changed occasionally and in between
-times was left unaltered. Fishery management decisions regarding this
-species can be highly contentious (@Safina1998, @Sissenwine1998,
-@Porch2005). Moreover, the stock is fished by fleets from many nations
-with quotas being set by a multilaterial management agency through a
-process of negotiation. As such, we might reasonably anticipate that
-for this species there could be substantial transaction costs involved
-in reaching agreement over any quota change, which could contribute to
-the observed quota stability. More generally, reviews by @Biais1995 and
-@Patterson2007a document many cases where changes in catch
-quotas that a management agency set were more modest than changes that
-would be recommended just by considering variations in stock abundance.
-
-We use a classic fisheries management question to examine how accounting
-for costs of policy adjustment can change optimal policies (see also
-@Ludwig1980, @Feichtinger1994, @Wirl1999). We focus on how
-harvest quotas for a stochastically varying fish population can be
-chosen to maximize the net present value of a fishery. Our formulation
-and solution method largely follow Reed's classic treatment on this
-question, a treatment repeated widely in bioeconomic textbooks. We 
-note that while later work has extended this treatment to deal with 
-a variety of other issues (e.g. @Sethi2005; @Singh2006; @McGough2009),
-we start from the classical model for simplicity of presentation and analysis.
-
-With his formulation, Reed showed that a constant escapement policy could be
-optimal under certain conditions. Such a policy involves choosing annual
-quotas that are perfectly responsive to recruitment variation in a fish
-stock. In poor recruitment years, the quota is set to zero and no fishing
-is allowed. But any time there is a good recruitment pulse, a quota is
-set that allows the fishery to exactly compensate through harvesting,
-thereby maintaining the optimal escapement level. However, in that
-analysis, Reed did not account for any costs of policy adjustment, which
-for such a responsive management strategy potentially could be large.
-
-<!-- NOTE perhaps comment on the deviation from constant escapement !-->
-
-As the example in Figure 1 makes clear, management policies will rarely be
-as responsive as this constant escapement policy assumes. In this paper,
-we explore conditions under which this lack of responsiveness may be a
-rationale response on the part of managers. Specifically, we consider a
-case where managers seek to balance the benefits in terms of increased
-profits from fishing from more finely tracking recruitment variations
-with the growing costs associated with adjusting policies quickly to do
-so. The policy adjustment costs involved could reflect pure administrative
-transaction costs or preferences held by fishermen, fish processing plants
-or other stakeholders, for less variable quotas. In seeking to account
-for these policy adjustment costs, we recognize that we do not know just
-what functional form they should take and that it will require a lot of
-empirical work to estimate that. Therefore, we scope three candidate
-functional forms that represent different assumptions about how these
-costs operate to determine whether the results we obtain are sensitive
-to such differences.
-
-Methods
-=======
-
 Fish population dynamics (state equation)
@@
 
-We will assume Beverton-Holt dynamics with multiplicative environmental noise
-
 $$N_{t+1} = Z_t \frac{A (N_t - h_t)}{1 + B (N_t - h_t)}, \label{eq:state_equation}$$
 
-where $N_t$ the stock size, $h_t$ the harvested level, 
-$Z_t$ gives the stochastic shocks, which we
-assume are lognormally distributed and $A$ and $B$ are positive
-constants.
+Optimization
+------------
 
-We assume managers set an annual quota for harvesting $h_t$ (the control
-variable) after observing the stock size that year $N_t$ (the state
-variable), but while still being uncertain about future environmental
-conditions and stock sizes. Through time, this gives a time path of
-management actions ${\bf h}=(h_1,h_2,\dots)$ that depend on the stock
-sizes that were observed (a state dependent control rule).
+$$\max_{{\bf h}}\mathbf{ E} ( NPV_{0} )=\max_{{\bf h}} \sum_0^\infty \mathbf{E} \left( \displaystyle \frac{\Pi_0(N_t,h_t)}{(1+\delta)^{t+1}} \right)$$
 
-We assume that managers choose annual quotas to maximize the expected
-net present value (NPV) of the fishery. We take as a base case the
-situation where there are no costs associated with policy adjustment and
-the managers' objective is
-
-\begin{equation}
-\max_{{\bf h}}\mathbf{ E} ( NPV_{0} )=\max_{{\bf h}} \sum_0^\infty \mathbf{E} \left( \displaystyle \frac{\Pi_0(N_t,h_t)}{(1+\delta)^{t+1}} \right) \label{eq:objective}
-\end{equation}
-
-where $\mathbf{E}$ is the expectation operator, $\delta>0$ is the
-discount rate and $\Pi_0$ is the net revenue from operating the fishery
-in a given year. In this base case, we assume the annual net revenue
-from fishing is
-
-\begin{equation}
-\Pi_0(N_t,h_t) = p h_t -  c_0 E_t \label{eq:annual_netrevenue}
-\end{equation}
-
-where $E_t$ represents fishing effort. We assume catch is proportional
-to stock size and effort expended fishing that year, $h_t = q E_t N_t$ and
-constant $q>0$ is the catchability coefficient. In
-Eqn. \eqref{eq:annual_netrevenue}, $p$ is the price per unit harvest and
-$c_0$ the cost of fishing and, to simplify the presentation of results,
-we assume that these are constants with $p>0$ and $c_0>0$. (Examples
-shown here use $p$= `r price` and $c_0$ = `r c0`, complete code is
-provided in the supplementary materials to re-run these analyses with
-arbitrarily specified values and replot the figures shown).
-
-Taken together this objective function \eqref{eq:objective} and the state
-equation \eqref{eq:state_equation} define a stochastic dynamic programming
-problem that we solve using backwards recursion via Bellman's equation.
-We denote the resulting state-dependent, optimal control as $h_0^{\ast}$.
-
-We solve this problem on a finite time horizon of $T =$ `r OptTime` using
-value iteration [@Mangel1988; @Clark2000].
+$$\Pi_0(N_t,h_t) = p h_t -  c_0 E_t $$
 
@@
 
-We compare this base case to three alternative problem formulations,
-each reflecting different plausible functional forms that costs of
-policy adjustment could take. In each, we assume managers can adjust the
-quota set in the fishery $h_t$ in a given year and that any policy
-adjustment costs are associated with changes to this control variable.
-
-First we assume that policy adjustment costs are directly proportional
-to the magnitude of the change in policy being proposed, such that
-larger changes to annual harvesting quotas incur greater policy
-adjustment penalties. Specifically, we replace $\Pi_0$ in the $NPV_0$
-equation with
+We replace $\Pi_0$ in the $NPV_0$ equation with
 
@@
 
-Next we continue to assume that policy adjustment costs depend on the
-magnitude of the change in policy being proposed. However, we consider a
-case where this dependence is nonlinear with big changes in policy being
-disproportionately expensive:
-
 $$\Pi_{2}(N_t,h_t, h_{t-1}) = \Pi_0 - c_2 (  h_t - h_{t-1})^2 \,.$$
 
-Finally, we assume instead that there is a fixed cost associated with
-any adjustment of policy, regardless of how large that adjustment might
-be
-
 $$\Pi_{3}(N_t,h_t, h_{t-1}) = \Pi_0 - c_3 (1-\mathbf{I}(h_t, h_{t-1}))  \,,$$
-
-where indicator function $\mathbf{I}(h_t, h_{t-1})$ takes the value 1 if
-$h_t=h_{t-1}$ and zero otherwise. For each $\Pi_i$, we can then define a
-new objective function $NPV_i$ similar to that in Eqn. \eqref{eq:objective}.
-
-We note that the fixed cost has conceptual analogues to the set-up cost of
-@Reed1974 and @Spulber1982 but here the fee is associated with a change
-in harvesting ($h_t\neq h_{t-1}$) and not with harvesting *per se*
-($h_t>0$) as in those studies.
-
-Taken together with the state equation Eqn. \eqref{eq:state_equation}, each
-of these new objective functions defines a different stochastic dynamic
-programming problem. Again, we solve them numerically using backwards
-recursion. To include costs of policy adjustment, we expand the state
-space to include both the current stock size and the management action
-taken on the previous time step $(N_t,h_{t-1})$. For each new objective
-function $\max NPV_i$, we denote the corresponding optimal control
-policy $h_i^*$.
-
-In addition in the Supplementary Material, we compare our results with 
-more conventional fisheries economic formulation in which additional
-costs are applied to the control variables themselves, as opposed to
-adjustments to the controls: $\Pi_4 (N_t,h_t) = p h_t -  c_0 E_t-c_4E_t^2$. 
-Additional costs of this form tend to have a smoothing effect on optimal quotas, but also change
-the long-term average stock size or quota size that is optimal.
 
@@
 
-<!--NOTE ci notation is confusing because it does not usually refer to c0 or c4 -->
-
-Each of the policy adjustment cost function is characterized in terms of
-a cost coefficient $c_i$. However, $c_i$ takes different units for each
-functional form. Therefore, if seeking to compare the relative effect of
-each penalty function on optimal management, it is unclear what
-parameter values should be used. To address this issue, we calibrate
-choices of $c_i$ so that each has a comparable impact on the optimal net
-present value of fishery, broadly following the example of @Bovenberg2008.
-
-<!--NOTE Jake to confirm these are still relevant and needed. 
-        We are using a less sophisticated normalization than was 
-        once discussed and may or may not need the citations now. -->
-
-Figure 2 shows the calibration graphically. Each curve plots the change
-in maximum expected NPV for a given penalty function as the penalty cost
-parameter is increased. In each case, the figure shows maximum expected
-NPV with policy adjustment costs as a proportion of the maximum expected
-NPV available in the basic problem $NPV_0({\bf h_0^*})$ without policy
-adjustment costs.
-
-```{r Figure_2, fig.cap="Expected net present value by functional form of penalty.
-Horizontal axis shows the coefficient $c_i$ governing the magnitude of the policy cost, while vertical axis shows fraction of the maximum expected net present value dissipated by the policy cost, $\\tfrac{NPV_0 - NPV_i}{NPV_0}$.
-The horizontal line indicates a value of the stock that is reduced by `r reduction * 100`% from the maximum expected value in the absence of policy adjustment costs, $NPV_0({\\bf h_0^*})$.
-Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.", dependson="quadcosts", fig.width=4, fig.height=3, cache = fig.cache}
+```{r Figure_2, fig.cap="",  dev=c("svg", "png")}
 
@@
 
-write.csv(dt, "components/data/100reps.csv")
-write.csv(fees, "components/data/figure2.csv")
-
 ```
-
-To compare the impact of penalty functions on optimal management across
-the different functional forms, we select penalty cost coefficients that
-induce the same reduction in maximum expected NPV. For example, the
-dashed vertical lines in Figure 1 map the needed cost coefficient $c_i$,
-for each penalty function, such that the fishery is worth `r 100*(1-reduction)`% of its
-unconstrained value when optimally managed.
-
-We focus our examination of the models on how the type and severity of
-policy adjustment costs affects the optimal management strategy. To
-simplify presentation of the results, we will illustrate cases where the
-growth parameters are chosen so that the intrinsic rate of increase of
-the fish population is 1 and the equilibrium biomass for the equivalent
-deterministic model without harvesting is 10; (specifically, $A=$ `r pars[1]` and
-$B=$ `r pars[2]` in Eqn. (1)). To characterize environmental variability, we
-assume multiplicative shock $Z_t$ is distributed log-normally with 
-log standard deviation $\sigma_g$ = `r sigma_g`. In addition, we
-show cases where $p=$ `r price`, $\delta=$ `r delta` and $c_0=$ `r c0`.
-
-<!-- is chosen such that the
-optimal stock size in the analogous deterministic problem is 5% larger
-than that corresponding to the maximum sustainable yield in biomass
-($c_0=XXX$). -->
-
-Results
-=======
 
@@
 
-```{r Figure_3, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=3, fig.width=5, cache = fig.cache}
+```{r Figure_3, dependson="tidy", fig.cap="", dev=c("svg", "png")}
 
@@
   labs(x="time", y="stock size", title = "Example Stock & Harvest Dynamics")  
-
-write.csv(harvest_fig3, "components/data/figure3.csv")
 ```
 
-Figure 3 illustrates how the different forms of adjustment cost can impact
-the optimal harvest policy. Corresponding stock sizes, which are measured
-here before harvest ($h_t$ being determined after observing stock size
-$x_t$) and thus show less influence of the policy cost can be seen in the
-supplement.  Each panel is generated against the same sequence of random
-shocks so that they can be compared directly.  The harvest policy chosen
-shows a systematic deviations from the penalty free optimum, depending on
-the nature of the cost.  In each case, the optimal solution without any
-adjustment cost is shown in against the policy induced by optimization
-under the given adjustment penalty (equivalent to a `r 100*reduction`%
-reduction in maximum expected NPV) is overlaid in blue.
+## Figure 4
 
-<!-- NOTE FIXME make this consistent! -->
-
-When considering the first formulation of policy adjustment costs
-(linear costs, $\Pi_1$), the first panel of Figure 3 shows a typical pattern, in which
-the optimal policy tends to avoid small policy adjustments, resulting in
-periods of constant policy followed by sudden bursts of adjustment.
-This results in a relatively step-like policy pattern. In contrast, the
-second formulation (quadratic costs, $\Pi_2$) disproportionately penalizes large policy
-adjustments. The corresponding optimal policy tracks all of the changes
-made by the cost-free policy, but with smaller magnitude. This results
-in a smoother $h_t$ curve, one that undershoots the larger oscillations
-seen in the cost-free optimum in favor of a policy that changes
-incrementally each year. Finally, the optimal policy for the third,
-'fixed fee' formulation ($\Pi_3$) only makes large adjustments, as one
-might expect, because the magnitude of the adjustment made is not
-reflected in the resulting penalty.
-
-The comparisons shown in Figure 3 are for one realization (i.e. a
-particular sequence of random number draws representing environmental
-variability) and are made for a particular magnitude of policy
-adjustment costs equal to `r reduction`% of the maximum expected net present value 
-in the base case ($NPV_0({\bf h_0^*})$). Figure 4 generalizes to show
-how optimal harvest levels and corresponding optimal stock sizes are
-affected by the magnitude of the costs of policy adjustment. This time
-we show summary statistics across 50 replicate sets of environmental
-conditions. We show the impact of policy adjustment costs on the
-variance of both harvests and stock sizes through time; on the
-autocorrelation of harvests and stock sizes through time. <!-- NOTE Are we showing cross-correlations or not? --> <!-- See figure 4, probably not-->
-
-For example, when small policy adjustment costs cost little but large
-adjustments are expensive ($\Pi_2$), we see the smoothing signal that we
-might have expected (see also @Ludwig1980 for this particular case). As
-cost penalties increase in severity (i.e., $c_2$ increases), the
-variance in quotas through time decreases and the autocorrelation of
-quotas through time increases. This smoothing of the harvest quotas
-through time has knock-on effects for the corresponding optimal stock
-sizes, which also become more autocorrelated as the scaling on policy
-adjustment costs ($c_2$) is increased. The autocorrelation in stock
-sizes here reflects the lag involved in a more modest increase in
-harvests taking longer to eliminate the signal of strong recruitment
-events, when compared to a more immediately responsive constant
-escapement policy.
-
-Interestingly, as suggested by the realization in Fig. 3, including a
-fixed cost of policy adjustment increases the variation in harvests
-through time. This is the opposite of a smoothing effect. Follow-on
-consequences for the other statistics are not as clear in this case.
-
-Finally, the case where policy adjustment costs scale linearly with the
-size of the adjustment ($\Pi_1$ in Eqn. 4) appear to be something of a
-middle of the road strategy, in that increasing the severity of policy
-adjustment costs (increasing $c_1$ has little effect on the variance or
-autocorrelation of optimal harvest rates or stock sizes. To reveal the
-particular impact of policy adjustment costs of this type requires a
-more targeted summary statistic. Specifically, for each run we
-calculated the frequency with which the optimal policy involved
-maintaining a positive quota across multiple time steps unaltered. This
-type of policy is arguably the most commonly observed behavior in TAC
-management, but is one that is almost never observed to be part of the
-optimal management strategy in the basic model without policy adjustment
-costs (Eqn. 3) or when optimizing against $\Pi_2$ or $\Pi_3$.
-
-```{r}
-fraction_no_shift <- function(x){
-
-noshift <- x[2:length(x)] - x[1:length(x)-1] == 0
-strictly_positive <- (x > 0.01 )[-1] # drop first point, 
-who <- noshift & strictly_positive # True whenever consecutive pairs did not shift and the second in the pair was nonzero harvest
- sum(who)/length(who)
-}
-
-shifts <- dt[, fraction_no_shift(harvest), by=c("penalty_fn", "replicate")]
-ave <- shifts[, mean(V1), by=penalty_fn]
-
-no_shifts <- ave$V1
-names(no_shifts) <- ave$penalty_fn
-```
-
-While still not common for the particular parameter combinations we examine,
-we find that positive unaltered quotas through time are much more likely
-to occur when optimizing against $\Pi_1$ where policy adjustment costs
-scale linearly with the size of proposed policy changes: in the 100 replicates
-of data presented above the harvest policy is strictly positive and identical in consecutive intervals
-only `r no_shifts[["L2"]] * 100`% of the time for quadratic costs $\Pi_2$, compared with
-`r no_shifts[["L1"]] * 100` with linear costs $\Pi_1$ and `r no_shifts[["fixed"]]*100`%
-for fixed costs $\Pi_3$. Moreover, these occurrences increase in frequency as the severity of
-these costs ($c_1$) increases.
-
-<!-- to include cross.correlation, drop subset call and facet_wrap by variable. But shows no pattern-->
-
-```{r Figure_4, fig.cap="Variance and autocorrelation of stock dynamics and harvest dynamics, as a function of the penalty coefficient.
-Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8, cache=fig.cache}
+```{r Figure_4, fig.cap="", dev=c("svg", "png")}
 ggplot(subset(figure4_df, statistic != "cross.correlation"), 
@@
 
-```{r Figure_5, fig.cap="Distribution of profits from fishing and costs paid to adjustment.
-Distributions are shown when managing a system in which the adjustment costs present are determined by the model indicated, and compared to the same costs and profits of managing the same system using a Reed model, which ignores adjustment costs, and thus tends to pay much higher fees for adjustment.
-In contrast, the difference in profit after accounting for costs is only marginally less than the value derived by managing the population to optimize profits when ignoring adjustment costs (Reed model).", fig.width=6, fig.height=5, dependson="histogram-calc"}
+```{r Figure_5, fig.cap="",  dependson="histogram-calc", dev=c("svg", "png")}
 
@@
 
-Next we examine the consequences either of ignoring policy adjustment
-costs when they are present or assuming they are present when they are
-not. To do so, it helps to break-down the different contributions to the
-maximum expected $NPV_i$ when employing the optimal policy $\bf{h_i}^*$
-versus when employing the policy that would be optimal were there no
-costs to policy adjustment $\bf{h_0}^*$. For example, if we take the
-first of the adjustment penalty forms, $\Pi_1$
+## Penalty
 
@@
 
-Histograms for the different contributions labelled $[1]-[4]$ here when
-taken across 100 replicate runs are shown are shown in Figure 5.
-<!--(contribution $[1]$ red, $[2]$ green, $[3]$ blue, and $[4]$ mauve).--> The
-cost of assuming policy adjustments are present when in fact they are
-absent is given by subtracting the contribution to the first infinite
-sum from term $[1]$ from the contribution to the second infinite sum of
-term $[3]$. (Note that convergence properties
-required to do this are met because we assume a positive discount rate).
-This cost is positive because the optimal controls recommended when
-assuming policy adjustment costs are present do not track variations in
-stock size as closely. Therefore, this harvesting strategy provides
-lower net revenue dockside.
+## Figure 6
 
-In contrast, the cost of ignoring policy adjustment costs when in fact
-they are present is given by subtracting the second infinite sum from
-the first (contributions $([1]-[2])-([3]-[4]))$ in the equations. These
-costs are positive because the lost revenues from not tracking stock
-variations as closely are smaller than the penalties of policy
-adjustment that are incurred if managers try to track stock variations
-more tightly.
-
-```{r Figure_6, fig.cap="Relative cost of ignoring adjustment costs when they are present ('ignoring', red) vs assuming the adjustment costs when they are absent ('assuming', blue), shown by penalty function over increasing magnitudes of cost.
-All values are relative to the cost-free adjustment optimum, NPV0.
-In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present.
-The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs."}
+```{r Figure_6, fig.cap="", dev=c("svg", "png")}
 
@@
   xlab("Penalty function")
-write.csv(table1_long, "components/data/figure6.csv")
 ```
 
-Figure 6 compares these different contributions, namely the $NPV$ lost by
-assuming policy adjustment costs when none are present (first entry in
-each cell, $[3]-[1]$ in the equations)) and the $NPV$ lost when
-ignoring policy adjustment costs when they are present (second entry in
-each cell of the table, contributions $([1]-[2])-([3]-[4]))$ in the
-equations) across the three different functional forms. Specifically,
-the table shows how these values change as we vary the severity of
-policy adjustment costs. In each case, values are shown as percentages
-of the maximum expected $NPV$ in the base case where no policy
-adjustment costs apply or are assumed to apply $NPV_0({\bf h_0^*})$.
+## Mismatches
 
-We find a pronounced asymmetry when comparing the impact on the net
-present value of the fishery of assuming policy adjustment costs are
-present when they are absent with the impact of assuming they are absent
-when they are present. For all three types of policy adjustment cost,
-the impact on NPV of ignoring these costs if they are in fact present is
-much bigger than that incurred by fallaciously managing as if they are
-present when they do not occur. This asymmetry arises, because there is
-less difference in the dockside revenue under the two management
-recommendations than there is in the potential policy adjustment costs
-themselves, as is evident in for the particular parameters shown in
-Figure 5.
-
-We also see that the impacts on net present value of the fishery of
-incorrectly assuming or ignoring policy adjustment costs are most severe
-when these costs are assumed to scale quadratically with the size of the
-policy change being implemented ($\Pi_2$).
-
-When policy costs are present, assuming the wrong functional form may or
-may not be worse than ignoring the presence of policy costs all together.
-Figure 7 considers several such cases.  The X axis labels indicate
-first which policy is being used to drive the harvest decisions, and
-then which penalty is actually being applied.  Thus $\Pi_1\_\Pi_2$ indicates
-a policy calculated under the linear ($\Pi_1$) costs, when the reality
-involves quadratic ($\Pi_2$) costs.  Though the coefficients of the ($\Pi_2$)
-costs have been scaled such that the net effect is the same, the inferred
-policies differ.  As a result, the value is slightly more than half of
-the optimal free solution when the expected reduction should only be 10%
-less than optimal free. In this case, ignoring the costs all together
-is still worse than using $\Pi_1$ costs -- the red bar is lower than the blue.
-
-For fixed costs ($\Pi_3$), the reverse is true.  Because fixed costs increase the
-volatility of the optimal solution while $\Pi_2$ costs decrease it, simply
-ignoring the cost of adjustment all together results in a higher value
-than either assuming costs are quadratic ($\Pi_2$) when they are fixed ($\Pi_3$),
-or assuming they are fixed when they are quadratic.
-
-Nevertheless, assuming quadratic costs is always the most conservative
-option -- scenarios in which true costs are quadratic (regardless of what
-cost structure is assumed by the policy) do significantly worse than
-those that are not (i.e. all cases that assume quadratic but actually
-have linear or fixed costs).
-
-These patterns hold across the different size reductions shown (from 10%
-to 25%), though net present value becomes negative under the quadratic
-form for the larger penalties as costs paid for adjustments exceed
-profits derived from harvest.  (Though optimal solutions will always
-avoid negative net present values, these scenarios in which policies are
-applied under conditions other than assumed in the optimality calculation
-have no such guarantee.) For each scenario, results are averaged over
-100 replicates.
-
-```{r Figure_7, fig.cap="Mismatches.
-X axis labels indicate the model used to derive the policy, followed by the model used to simulate the penalty.
-Blue bars show the net present value of that scenario.
-Compare to red bars, which show the consequence of using a policy that ignores costs all together in the same scenario (i.e.
-costs as indicated by second code), rather than assuming the policy indicated by the first code in the pair.
-All values are scaled to a fraction of the adjustment free net present value.
-Successive panels show increasing reduction of the net present value by increasing penalty coefficients: e.g.
-a policy in the first panel should lose only 10% of its net present value to adjustment costs if it had the correct form of those costs."}
+```{r Figure_7, fig.cap="", dev=c("svg", "png")}
 who <- c("penalty_fn", "ignore_fraction", "mismatched_fraction", "reduction")
@@
   xlab("Penalty function")
-write.csv(table2_long, "components/data/figure7.csv")
 ```
-
-Discussion
-==========
-
-<!-- Pasted from external word doc, see Boettiger_Discussion_draft.docx for latest version of discussion -->
-
-Policy-makers managing ecological systems that vary in space and time
-must evaluate how much of that variation to reflect in management
-recommendations. Fine-tuning a policy to respond to frequent variations
-in ecological dynamics may incur increased transaction costs associated
-with constantly revisiting past policy decisions. A more pragmatic
-approach would be one that balances benefits from responding to frequent
-variations in ecological conditions with the increased transaction costs
-involved. As a first step towards exploring these ideas, we revisited
-a classic problem from bioeconomics concerning the optimal management
-of a fish stock subject to stochastically varying recruitment [@Reed1979; @Clark2010]. 
-We examined how optimal policy recommendations, here
-annual catch quotas, changed when accounting for costs associated with
-policy adjustment and what the implications of following these policy
-recommendations would be for the exploited population. We also compared
-how the value of the fishery is affected by managers either under-
-or over-estimating the importance of policy adjustment costs of this type.
-
-Estimating policy adjustment costs and how they respond to the size of
-proposed policy changes would be empirically challenging. Recognizing
-this fact, in our analyses, we compared different plausible forms that
-these costs might take. We compared two cost structures where we assumed
-the magnitude of policy adjustment costs increased with the magnitude
-of the change in policy being proposed with an alternative formulation
-in which we assumed there was a fixed cost associated with making any
-change to current policy. While each formulation clearly provides only a
-very phenomenological representation of the policy setting environment,
-we believe that each enables us to explore meaningful differences in how
-policy adjustment costs might operate. That being said, in the real-world
-we might expect the different types of adjustment cost to operate in
-combination. Interestingly, there are analogues between how we have
-represented different types of policy adjustment costs in our models
-and regularization techniques that are sometimes used in model fitting
-to address concerns about over-specifying models (e.g. ridge or lasso
-regression or total variation denoising approaches
-[@Rudin1992]).
-
-<!-- NOTE
-
-Have wondered about cutting this, but does broaden things out a bit from
-just econ referencing and context.
-
-Also more people will have heard about ridge and lasso, but I actually
-think they're not as relevant as the total variation suggestion, because
-it applies to the gradient whereas they do not. So really a more accurate
-statement is that the difference between lasso and ridge and the total
-variation approach is in some ways analogous to the difference between
-costs on h or E and costs on dh/dt or dE/dt. But that's way too many
-words now
-
-Carl B - when it comes to references, you may have others you would
-prefer here
-
--->
-
-The biggest differences between the representations of policy adjustment
-cost that we consider are between those that have a smoothing effect
-on annual quotas and those that do not. The few past studies that
-incorporate policy adjustment costs in models of fisheries management
-[@Ludwig1980; @Feichtinger1994; @Wirl1999] assumed costs of
-policy adjustment increased as a quadratic function of the magnitude of
-the policy change being proposed (our $\Pi_2$ formulation in Eqn.) In
-effect, this means that small changes to annual quotas incur little
-extra cost, but large changes to annual quotas become disproportionately
-expensive to make. Including costs of this form smoothes inter-annual
-variation in the catch quotas that would be recommended. However, as
-catches become less variable through time, the variability in the fish
-population itself increases. In essence, the optimal policy no longer
-soaks up as much of the natural variability in recruitment that is
-affecting the population. Also, the catches and remaining stock sizes
-corresponding to optimal management become more autocorrelated in time,
-because it takes the fishery longer to harvest down peaks in abundance
-that follow large recruitment pulses. The effects of smoothing here are
-similar to those predicted when assuming the cost per unit effort is
-increasing in the amount of effort expended (e.g., @Lewis1981, @McGough2009; 
-see Supporting Information for a summary of the relevant
-results) as opposed to associating extra costs with changes to policy
-*per se*. Smoothing effects of this type are what one might have
-expected when including policy adjustment costs.
-
-Standing in sharp contrast to these smoothing predictions is our
-finding that including policy adjustment costs can actually _increase_ the
-variability of quotas through time if there is a fixed cost associated
-with making any changes to current policy (e.g. costs of running relevant
-stakeholder meetings and public consultations on proposed policy changes,
-$\Pi_3$). With this formulation, as stock sizes vary in response to
-recruitment, the fishery manager must balance the cost of brokering
-a policy change with the cost in forgone fisheries revenue from not
-responding to favorable recruitment pulses. The optimal policy involves
-ignoring small variations in recruitment, but then assigns a larger quota
-when particularly strong recruitment years arise than would have been
-the case in the absence of policy adjustment costs. The other functional
-form we consider, in which the costs of policy adjustment scale linearly
-with the size of the adjustment ($Pi_1$), has less obvious effects on
-optimal policies. But interestingly, it is the only formulation for
-which we observed positive unchanging quotas of the type most commonly
-encountered in real-world applications.
-
-That the different representations of policy adjustment costs result in
-such different dynamics suggests that researchers constructing fisheries
-economics models should proceed cautiously when choosing how to represent
-these costs. However, in our own experience, we have found that while
-modeling studies sometimes mention policy adjustment costs when motivating
-model assumptions (references), they rarely provide much justification
-for the choice of functional form used or test the sensitivity of any
-conclusions drawn to alternative specifications. Indeed, we were surprised
-to find such clear differences between the functional forms, because
-we anticipated that the limiting case of increasing policy adjustment
-costs within each functional form should be the same, namely a constant
-annual quota that does not change through time (open-loop control).
-
-We also compared the efficiency costs that would result from failing
-to account for policy adjustment cost if they are present with those
-involved in assuming them when in fact they are absent. The results
-of this comparison were not sensitive to the particular form of policy
-adjustment costs assumed. Instead, we always found the efficiency costs
-of ignoring policy adjustment costs when they were present to be much
-larger than the efficiency costs of assuming policy adjustment costs
-applied when they were in fact absent. Policy adjustment costs affect
-the overall value of the fishery in two ways here. First, there is the
-direct cost associated with each quota change. Second there is a cost in
-foregone revenue from missed catches when not following what would be the
-optimal policy if quotas were free to track recruitment variability. Our
-finding that it is more costly to ignore policy adjustment costs when
-they are present arises because the first, more direct, cost contribution
-here is larger than the second.
-
-Assuming an adjustment cost exists when in fact it is absent is not the
-same as using the wrong functional form when it is present.  Here, our
-results showed that choice of the functional form makes a significant
-difference.  We show it can be better to ignore policy costs than to derive a 
-policy based on assuming the wrong functional form.  This result further
-underscores the importance of modelers using caution when seeking to account
-for these costs. Assuming an arbitrary form in order to capture the influence
-of adjustment costs is thus unlikely to be instructive.
-
-As with any modeling analysis, our formulation makes many assumptions. For
-example, we assume that the fishery in question is being optimally managed
-by a policy-maker who acts as the 'sole owner' of the stock. This approach
-is different to models that assume fisheries are not well-managed,
-e.g. by assuming open access conditions (references [^1]),
-or ones that derive policy recommendations endogenously by modeling
-interactions between different stakeholders [@Kaitala1993, @Laukkanen2003].
-As such, we anticipate that our approach will be more relevant to
-some fisheries, particularly domestic fisheries in developed countries
-that are subject to relatively strong regulatory regimes, than to others
-(e.g., artisanal fisheries that are subject to weaker regulation). To
-focus on the effects of policy adjustment costs, we focused narrowly
-on the basic model specification of @Reed1979 and examined how the
-predictions of this classic problem were changed by introducing policy
-adjustment costs of different forms. However, there have been many
-elaborations on Reed's basic approach that increase the realism of
-the optimization models involved by relaxing other assumptions (see for
-example @Sethi2005; @Singh2006; @McGough2009). For
-example, in following Reed's approach closely another important
-assumption we made is that the fishery manager observes the current stock
-size correctly when setting the annual quota (see @Clark1986,
-@Williams2001 for alternative specifications). However, predictions of
-current cohort sizes from stock assessments are subject to uncertainty
-[@Ralston2011]. Were uncertainty regarding reported recruitment
-pulses also included, an optimizing manager might moderate their policy
-responses to initial reports of particularly good recruitment years
-increase yet further.
-
-[^1]: NOTE Would be good to give an open access model in a fluctuating
-environment here. From Andersen and Sutinen's review (Mar Res Econ
-1, 117-136) it looks like one basal citation is Andersen 1981 The
-exploitation of fish resources under stock uncertainty. But it is a
-'staff paper'. Our library don't hold it. Has anyone else got it?
-
-One obvious research avenue suggested by our models is that of empirically
-estimating costs of policy adjustment. A direct estimation approach
-could quantify some sources of policy adjustment costs, e.g. costs to
-processing plants that arise from having more variable catches. However,
-other more intangible sources of policy adjustment costs, e.g. preferences
-of policy-makers or different stakeholders for less variable quotas,
-might be missed. An alternative, more holistic, approach would be to
-apply revealed preference methods to fisheries management agencies
-themselves, in the tradition of [@McFadden1975; @McFadden1976]. Such an analysis
-would involve comparing quotas that were set relative to stock sizes as
-they were estimated at the time each management decision was taken to
-try to infer what objective managers were maximizing.
-
-A worthwhile modeling extension suggested by our results would be to
-examine the implications of policy adjustment costs for risks of stock
-collapse. Examining risks of stock collapse is not possible with the
-Reed model-formulation that we followed here but would be worthwhile
-in light of our finding that the variance and autocorrelation in stock
-sizes through time can be affected when accounting for costs of policy
-adjustment. Both are properties known in other modeling settings to
-be associated with changes to the risk of extinction or of transitions
-between alternative stable states [@Scheffer2009; @Boettiger2013].
-
-<!-- NOTE: Too many extensions being suggested now -->
-
-When facing highly variable ecological systems, how often should
-natural resource managers respond? A highly interventionist strategy
-would track ecosystem variation very closely. Alternatively, a manager
-might choose only to take action or change policy only when conditions
-look very different to those previously experienced. We took a modeling
-approach to begin to explore these ideas. Specifically, we focused on
-a well-known problem from fisheries management and examined how optimal
-management recommendations changed when we accounted for costs associated
-with frequently changing management decisions. While we focused on a
-fisheries context, our findings would be relevant to many other settings
-where natural resource managers revisit management decisions through
-time in light of ecological variability, including game management,
-management of in-stream flow rates, fire management, habitat restoration,
-and managing for endangered species. In some ways, the analyses that
-we present can also be thought of as providing a temporal counter-part
-to discussions about the optimal spatial scale over which ecosystem
-management should be conducted.
-
-<!-- NOTE Paul writes: I can provide some references on this paragraph. But
-would suggest that I wait and let you and others overhaul it first. I
-am not sure it really adds much of value, but it does give us a
-dismount. Moreover,  I'm trying to help you hit your desire to broaden
-out beyond a fisheries context. The key barometer is we should be able
-to point at a suitable sdp application which we could have used just as
-easily as the fisheries management context. I think we can probably do
-that for the list provided here.  -->
-
-Supplementary material
-======================
-
-```{r Figure_S1, dependson="tidy", fig.cap="Multiple realizations of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=10, fig.width=8, cache=fig.cache}
-
-fig1s_df <- as.data.frame(subset(dt, replicate %in% paste0('rep_', 11:20)))
-fig1s_df <- fig1s_df[c("time", "fishstock", "alternate", "harvest", "harvest_alt", "penalty_fn", "replicate")]
-fig1s_df <- melt(fig1s_df, id = c("time", "penalty_fn", "replicate"))
-fig1s_df <- data.frame(fig1s_df, baseline = fig1s_df$variable)
-variable_map <- c(fishstock = "fish_stock", alternate = "fish_stock", harvest = "harvest", harvest_alt = "harvest")
-baseline_map <- c(fishstock = "penalty", alternate = "no_penalty", harvest = "penalty", harvest_alt = "no_penalty")
-fig1s_df$variable <- variable_map[fig1s_df$variable]
-fig1s_df$baseline <- baseline_map[fig1s_df$baseline]
-
-fig1s_df <- subset(fig1s_df, variable=="harvest")
-labeller <- function(variable,value){
-if (variable=='penalty_fn') {
-    return(relabel[value])
-  } else {
-    return(value)
-  }
-}
-
-ggplot(fig1s_df, aes(time, value, col=baseline)) +
-  geom_line(lwd=1) +
-  facet_grid(replicate ~ penalty_fn, labeller=labeller) + 
-  labs(x="time", y="stock size", title = "Example Stock & Harvest Dynamics")  
-write.csv(fig1s_df, "components/data/figure_s1.csv")
-
-```
-
-```{r Figure_S2, dependson="tidy", fig.cap="Example realization of resulting fish stock sizes under the different functional forms of adjustment costs, corresponding to policies shown in Figure 3.
-Because stock sizes are measured before harvests, the effect of the penalty on the stock size is not as pronounced.", fig.height=3, fig.width=8, cache = fig.cache}
-
-labeller <- function(variable,value){
-    return(relabel[value])
-}
-
-ggplot(fishstock_fig3, aes(time, value, col=baseline)) +
-  geom_line(lwd=1) +
-  facet_grid(penalty_fn~., labeller = labeller) + 
-  labs(x="time", y="stock size", title = "Example Stock & Harvest Dynamics")
-
-write.csv(fishstock_fig3, "components/data/figure_s2.csv")
-```
-
-```{r table-caption}
-caption = "Table 1: Column 'ignoring' shows the results of ignoring a adjustment penalty when it is present, Column 'assuming' shows the results of assuming an adjustment cost when it is absent.
-Values (ignoring, assuming) are given as the expected net present value (ENPV) as a fraction of that when no penalty is present, ENPV0.
-Percent reduction refers to penalty coefficient being calibrated to achieve the given percent reduction relative to ENPV0 when the penalty is optimally accounted for.
-Comparing the second and third columns shows that ignoring a real cost is a significantly graver error, particularly in the case of quadratic costs."
-```
-
-```{r Table1, results="asis"}
-pandoc.table(table1, caption=caption)
-```
-
-```{r Figure_5_alt, fig.cap="**Alternate Figure 5**.
-Distribution of profits from fishing and costs paid to adjustment.
-Distributions are shown when managing a system in which the adjustment costs present are determined by the model indicated, and compared to the same costs and profits of managing the same system using a Reed model, which ignores adjustment costs, and thus tends to pay much higher fees for adjustment.
-In contrast, the difference in profit after accounting for costs is only marginally less than the value derived by managing the population to optimize profits when ignoring adjustment costs (Reed model).", fig.width=3, fig.height=5, dependson="histogram-calc"}
-
-hist_dat_alt <- melt(cbind(profits, costs = costs$V1, 
-                       reed_profits = reed_profits$profits, reed_costs = reed_costs$V1),
-                 id = c("penalty_fn", "replicate"))
-
-ggplot(hist_dat_alt) + 
-  geom_density(aes(value, fill=variable, color=variable), alpha=0.8)+
-  facet_grid(penalty_fn~., labeller = labeller)
-
-```
-
-# References

### 2014-07-24 manuscripts/manuscript.Rmd
tweaking packrat config

@@
 
-```{r Figure_1, fig.cap="Quota on Blue Fin Tuna Catch", fig.width=4, fig.height=4}
+```{r Figure_1, fig.cap="Quota on Blue Fin Tuna Catch", fig.width=4, fig.height=4, dev=c("pdf", "svg", "png")}
 tuna <- read.csv("components/data/tuna.csv")
@@
 The horizontal line indicates a value of the stock that is reduced by `r reduction * 100`% from the maximum expected value in the absence of policy adjustment costs, $NPV_0({\\bf h_0^*})$.
-Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.", dependson="quadcosts", fig.width=4, fig.height=3, cache = fig.cache}
+Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.", dependson="quadcosts", fig.width=4, fig.height=3, cache = fig.cache, dev=c("pdf", "svg", "png")}
 
@@
 
-```{r Figure_3, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=3, fig.width=5, cache = fig.cache}
+```{r Figure_3, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=3, fig.width=5, cache = fig.cache, dev=c("pdf", "svg", "png")}
 
@@
 ```{r Figure_4, fig.cap="Variance and autocorrelation of stock dynamics and harvest dynamics, as a function of the penalty coefficient.
-Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8, cache=fig.cache}
+Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png")}
 ggplot(subset(figure4_df, statistic != "cross.correlation"), 
@@
 Distributions are shown when managing a system in which the adjustment costs present are determined by the model indicated, and compared to the same costs and profits of managing the same system using a Reed model, which ignores adjustment costs, and thus tends to pay much higher fees for adjustment.
-In contrast, the difference in profit after accounting for costs is only marginally less than the value derived by managing the population to optimize profits when ignoring adjustment costs (Reed model).", fig.width=6, fig.height=5, dependson="histogram-calc"}
+In contrast, the difference in profit after accounting for costs is only marginally less than the value derived by managing the population to optimize profits when ignoring adjustment costs (Reed model).", fig.width=6, fig.height=5, dependson="histogram-calc", dev=c("pdf", "svg", "png")}
 
@@
 In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present.
-The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs."}
+The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs.", dev=c("pdf", "svg", "png")}
 
@@
 Successive panels show increasing reduction of the net present value by increasing penalty coefficients: e.g.
-a policy in the first panel should lose only 10% of its net present value to adjustment costs if it had the correct form of those costs."}
+a policy in the first panel should lose only 10% of its net present value to adjustment costs if it had the correct form of those costs.", dev=c("pdf", "svg", "png")}
 who <- c("penalty_fn", "ignore_fraction", "mismatched_fraction", "reduction")
@@
 
-```{r Figure_S1, dependson="tidy", fig.cap="Multiple realizations of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=10, fig.width=8, cache=fig.cache}
+```{r Figure_S1, dependson="tidy", fig.cap="Multiple realizations of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=10, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png")}
 
@@
 ```{r Figure_S2, dependson="tidy", fig.cap="Example realization of resulting fish stock sizes under the different functional forms of adjustment costs, corresponding to policies shown in Figure 3.
-Because stock sizes are measured before harvests, the effect of the penalty on the stock size is not as pronounced.", fig.height=3, fig.width=8, cache = fig.cache}
+Because stock sizes are measured before harvests, the effect of the penalty on the stock size is not as pronounced.", fig.height=3, fig.width=8, cache = fig.cache, dev=c("pdf", "svg", "png")}
 
@@
 Distributions are shown when managing a system in which the adjustment costs present are determined by the model indicated, and compared to the same costs and profits of managing the same system using a Reed model, which ignores adjustment costs, and thus tends to pay much higher fees for adjustment.
-In contrast, the difference in profit after accounting for costs is only marginally less than the value derived by managing the population to optimize profits when ignoring adjustment costs (Reed model).", fig.width=3, fig.height=5, dependson="histogram-calc"}
+In contrast, the difference in profit after accounting for costs is only marginally less than the value derived by managing the population to optimize profits when ignoring adjustment costs (Reed model).", fig.width=3, fig.height=5, dependson="histogram-calc", dev=c("pdf", "svg", "png")}
 

### 2014-07-24 manuscripts/components/analysis.R

@@ -1,7 +1,7 @@
 
 
 
-ncpu = 24
+ncpu = 4
 
 
 ## ----profit_model--------------------------------------------------------

### 2014-07-25 manuscripts/manuscript.Rmd
presentation updated

@@
   facet_grid(penalty_fn~., labeller = labeller) + 
-  labs(x="time", y="stock size", title = "Example Stock & Harvest Dynamics")
+  labs(x="time", y="stock size", title = "Example Harvest Dynamics")  +
+  scale_color_discrete(labels=c("Reed solution", "With penalty"), name="")
 
@@
   scale_color_discrete(labels=relabel, name="Penalty function") + 
+  scale_fill_discrete(labels=relabel, name="Penalty function") +
   xlab("Penalty size (as fraction of NPV0)")

### 2014-07-25 manuscripts/presentation.Rmd
presentation updated

@@
 title: "Fisheries management when quotas are costly to change"
-date: "07/24/2014"
-output: ioslides_presentation
+date: "08/12/2014"
+output: 
+  ioslides_presentation:
+    self_contained: false
+    css: components/style.css
+    incremental: true
 
-author: 
-  - name: Carl Boettiger
-    affiliation: cstar
-    email: cboettig (at) gmail.com
-    footnote: Corresponding author
-  - name: Michael Bode
-    affiliation: melbourne
-  - name: James Sanchirico
-    affiliation: UCD
-  - name: Jacob LaRiviera
-    affiliation: UTK
-  - name: Alan Hastings
-    affiliation: UCD
-  - name: Paul Armsworth 
-    affiliation: UTK
-
-address: 
-  - code: cstar
-    address: | 
-      Center for Stock Assessment Research,
-      110 Shaffer Rd,
-      Santa Cruz, CA 95050, USA 
-  - code: UCD
-    address: Department of Environmental Science and Policy, University of California, Davis
-  - code: melbourne
-    address: University of Melbourne, Australia 
-  - code: UTK
-    address: University of Tennessee, Knoxville
+author: |
+        Carl Boettiger, Michael Bode, James Sanchirico, 
+        Jacob LaRiviera, Alan Hastings, Paul Armsworth
 
 ---
+
+<!-- 
+Time: 30 minutes with questions
+Presenting at: 2014-12-08 15:10:00 PDT
+-->
+
+## Our world is changing
+
+<img src="components/images/global-change.jpg" width="500" style="margin:0px auto;display:block">
+
+<small> Overpeck+ (2011) doi: [10.1126/science.1197869](http://doi.org/10.1126/science.1197869) </small>
+
+## Our policies are not
+
+<img src="components/images/nochange.jpg" width="700">
+
+<small> Alex Wong (Getty Images) </small>
+
+# Why?
+
+## Postulate: policy intertia
+
+> Policies are costly to change
+
+## We're quite good at accounting for _ecological_ dynamics
+
+## Dynamic optimization - Dynamic policies
+
+<small> Reed (1979) [10.1016/0095-0696(79)90014-7](http://doi.org/10.1016/0095-0696(79)90014-7) </small>
+
+## Not so good at _policy_ dynamics
+
+- We account for ecological dynamics but not political ones
+- We're not political scientists, we don't know the equations of politics (does anyone?)
+- Instead, we can investigate the potential impact that costly adjustments have on optimal policy
 
@@
 ```
-
 ```{r analysis, include=FALSE}
@@
 
+## Bluefin Tuna Quotas, ICCAT
+
 ```{r Figure_1, fig.cap="Quota on Blue Fin Tuna Catch", dev=c("svg", "png")}
 tuna <- read.csv("components/data/tuna.csv")
-ggplot(tuna, aes(year, quota)) + geom_point()
+ggplot(tuna, aes(year, quota)) + geom_point() + theme_bw()
 ```
@@
 
-$$N_{t+1} = Z_t \frac{A (N_t - h_t)}{1 + B (N_t - h_t)}, \label{eq:state_equation}$$
+$$N_{t+1} = Z_t \frac{A (N_t - h_t)}{1 + B (N_t - h_t)}$$
 
@@
 
-$$\max_{{\bf h}}\mathbf{ E} ( NPV_{0} )=\max_{{\bf h}} \sum_0^\infty \mathbf{E} \left( \displaystyle \frac{\Pi_0(N_t,h_t)}{(1+\delta)^{t+1}} \right)$$
+$$\max_{{\bf h}}\mathbf{ E} ( NPV_{0} )=\max_{{\bf h}} \sum_0^\infty \mathbf{E} \left(\frac{\Pi_0(N_t,h_t)}{(1+\delta)^{t+1}} \right)$$
 
@@
 
-Choice of parameters 
+Apples to Apples 
 --------------------
@@
 
-ggplot(fees, aes(c2, (npv0-value)/npv0, lty=variable)) + 
-  geom_line() + 
+ggplot(fees, aes(c2, (npv0-value)/npv0, color=variable)) + 
+  geom_line(lwd=1) + 
   geom_hline(aes(yintercept=reduction), linetype=4) + 
@@
   ylab("Reduction in net present value") + 
-  scale_linetype_discrete(labels=relabel)
+  scale_color_discrete(labels=relabel)
 
@@
   facet_grid(penalty_fn~., labeller = labeller) + 
-  labs(x="time", y="stock size", title = "Example Stock & Harvest Dynamics")  
+  labs(x="time", y="stock size", title = "Example Harvest Dynamics")  +
+  scale_color_discrete(labels=c("Reed solution", "With penalty"), name="")
 ```
@@
   scale_color_discrete(labels=relabel, name="Penalty function") + 
+  scale_fill_discrete(labels=relabel, name="Penalty function") + 
   xlab("Penalty size (as fraction of NPV0)")
@@
 
-$$NPV_i( \mathbf{h_1^*} ) = \sum_{t=0}^\infty (\overbrace{ p h^*_{1,t}-c_0E^*_{1t}}^{[1]}-\overbrace{c_1 | h^*_{1,t}- h^*_{1,t-1}|}^{[2]} ) \displaystyle \frac{1}{(1+\delta)^t}$$
+$$NPV_i( h_1^* ) = \sum_{t=0}^\infty (\overbrace{ p h^*_{1,t}-c_0E^*_{1t}}^{[1]}-\overbrace{c_1 | h^*_{1,t}- h^*_{1,t-1}|}^{[2]} )  \frac{1}{(1+\delta)^t}$$
 
-and
-
-$$NPV_i( \mathbf{h_0^*} ) = \sum_{t=0}^\infty (\underbrace{ p h^*_{0,t}-c_0E^*_{0t}}_{[3]}-\underbrace{c_1 | h^*_{0,t}- h^*_{0,t-1}|}_{[4]} ) \displaystyle \frac{1}{(1+\delta)^t}$$
+$$NPV_i( h_0^* ) = \sum_{t=0}^\infty (\underbrace{ p h^*_{0,t}-c_0E^*_{0t}}_{[3]}-\underbrace{c_1 | h^*_{0,t}- h^*_{0,t-1}|}_{[4]} )  \frac{1}{(1+\delta)^t}$$
 

### 2014-07-25 manuscripts/manuscript.Rmd
updated presentation, minor tweaks to manuscript from Paul feedback

@@
     affiliation: UCD
-  - name: Jacob LaRiviera
+  - name: Jacob LaRiviere
     affiliation: UTK
@@
 
+options(digits=2)
+
 theme_set(theme_tufte())
@@
 
-```{r Figure_1, fig.cap="Quota on Blue Fin Tuna Catch", fig.width=4, fig.height=4, dev=c("pdf", "svg", "png")}
+```{r Figure_1, fig.cap="ICCAT Stock assessments and US Quotas for Bluefin Tuna, 1987 - 2007", fig.width=6, fig.height=4, dev=c("pdf", "svg", "png")}
 tuna <- read.csv("components/data/tuna.csv")
-ggplot(tuna, aes(year, quota)) + geom_point()
+tuna<-melt(tuna, id="year")
+ggplot(tuna, aes(year, value)) + geom_point() +
+  facet_wrap(~variable, ncol=1, scale="free_y") + 
+  ylab("Bluefin Tuna harvest (tonnes)") + theme_bw()
 ```
@@
 we explore conditions under which this lack of responsiveness may be a
-rationale response on the part of managers. Specifically, we consider a
+rational response on the part of managers. Specifically, we consider a
 case where managers seek to balance the benefits in terms of increased
@@
 Horizontal axis shows the coefficient $c_i$ governing the magnitude of the policy cost, while vertical axis shows fraction of the maximum expected net present value dissipated by the policy cost, $\\tfrac{NPV_0 - NPV_i}{NPV_0}$.
-The horizontal line indicates a value of the stock that is reduced by `r reduction * 100`% from the maximum expected value in the absence of policy adjustment costs, $NPV_0({\\bf h_0^*})$.
-Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.", dependson="quadcosts", fig.width=4, fig.height=3, cache = fig.cache, dev=c("pdf", "svg", "png")}
+The horizontal line indicates a value of the stock that is reduced by 25% from the maximum expected value in the absence of policy adjustment costs, $NPV_0({\\bf h_0^*})$.
+Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.", dependson="quadcosts", fig.width=5, fig.height=3, cache = fig.cache, dev=c("pdf", "svg", "png")}
 
@@
 
-ggplot(fees, aes(c2, (npv0-value)/npv0, lty=variable)) + 
+ggplot(fees, aes(c2, (npv0-value)/npv0, lty=variable, color=variable)) + 
   geom_line() + 
@@
   ylab("Reduction in net present value") + 
-  scale_linetype_discrete(labels=relabel)
+  scale_linetype_discrete(labels=relabel) + 
+  scale_color_discrete(labels=relabel)
 
@@
 
-```{r Figure_3, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=3, fig.width=5, cache = fig.cache, dev=c("pdf", "svg", "png")}
+```{r Figure_3, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=5, fig.width=8, cache = fig.cache, dev=c("pdf", "svg", "png")}
 
@@
 variability) and are made for a particular magnitude of policy
-adjustment costs equal to `r reduction`% of the maximum expected net present value 
+adjustment costs equal to `r reduction *100`% of the maximum expected net present value 
 in the base case ($NPV_0({\bf h_0^*})$). Figure 4 generalizes to show
@@
 variance of both harvests and stock sizes through time; on the
-autocorrelation of harvests and stock sizes through time. <!-- NOTE Are we showing cross-correlations or not? --> <!-- See figure 4, probably not-->
+autocorrelation of harvests and stock sizes through time.
+
+<!-- to include cross.correlation, drop subset call and facet_wrap by variable. But shows no pattern-->
+
+```{r Figure_4, fig.cap="Variance and autocorrelation of stock dynamics and harvest dynamics, as a function of the penalty coefficient.
+Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png")}
+
+library("dplyr")
+
+ggplot(filter(stats_df, variable != 'cross.correlation'), 
+       aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn))  +
+  stat_summary(fun.y = mean, 
+               fun.ymin = function(x) mean(x) - sd(x), 
+               fun.ymax = function(x) mean(x) + sd(x), 
+               geom = "ribbon", alpha=0.3, colour=NA) +
+  stat_summary(fun.y = mean, geom = "line") + 
+  coord_cartesian(xlim = c(0, .3)) + 
+  facet_wrap(~ variable, scale="free_y") + 
+  scale_color_discrete(labels=relabel, name="Penalty function") + 
+  scale_fill_discrete(labels=relabel, name="Penalty function") +
+  xlab("Penalty size (as fraction of NPV0)")
+
+write.csv(stats_df, "components/data/figure4.csv")
+```
 
@@
 might have expected (see also @Ludwig1980 for this particular case). As
-cost penalties increase in severity (i.e., $c_2$ increases), the
+cost penalties increase in severity (i.e., $c_i$ increases), the
 variance in quotas through time decreases and the autocorrelation of
@@
 sizes, which also become more autocorrelated as the scaling on policy
-adjustment costs ($c_2$) is increased. The autocorrelation in stock
+adjustment costs ($c_i$) is increased. The autocorrelation in stock
 sizes here reflects the lag involved in a more modest increase in
@@
 middle of the road strategy, in that increasing the severity of policy
-adjustment costs (increasing $c_1$ has little effect on the variance or
+adjustment costs (increasing $c_i$ has little effect on the variance or
 autocorrelation of optimal harvest rates or stock sizes. To reveal the
@@
 to occur when optimizing against $\Pi_1$ where policy adjustment costs
-scale linearly with the size of proposed policy changes: in the 100 replicates
-of data presented above the harvest policy is strictly positive and identical in consecutive intervals
+scale linearly with the size of proposed policy changes: over the 100 replicates
+time series the harvest policy is strictly positive and identical in consecutive intervals
 only `r no_shifts[["L2"]] * 100`% of the time for quadratic costs $\Pi_2$, compared with
-`r no_shifts[["L1"]] * 100` with linear costs $\Pi_1$ and `r no_shifts[["fixed"]]*100`%
+`r no_shifts[["L1"]] * 100`% with linear costs $\Pi_1$ and `r no_shifts[["fixed"]]*100`%
 for fixed costs $\Pi_3$. Moreover, these occurrences increase in frequency as the severity of
-these costs ($c_1$) increases.
-
-<!-- to include cross.correlation, drop subset call and facet_wrap by variable. But shows no pattern-->
-
-```{r Figure_4, fig.cap="Variance and autocorrelation of stock dynamics and harvest dynamics, as a function of the penalty coefficient.
-Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png")}
-ggplot(subset(figure4_df, statistic != "cross.correlation"), 
-       aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn))  +
-  stat_summary(fun.y = mean, 
-               fun.ymin = function(x) mean(x) - sd(x), 
-               fun.ymax = function(x) mean(x) + sd(x), 
-               geom = "ribbon", alpha=0.3, colour=NA) +
-  stat_summary(fun.y = mean, geom = "line") + 
-  coord_cartesian(xlim = c(0, .3)) + 
-  facet_wrap(~ timeseries + statistic, scale="free_y") + 
-  scale_color_discrete(labels=relabel, name="Penalty function") + 
-  scale_fill_discrete(labels=relabel, name="Penalty function") +
-  xlab("Penalty size (as fraction of NPV0)")
-
-write.csv(figure4_df, "components/data/figure4.csv")
-```
+these costs ($c_i$) increases.
 
@@
 Distributions are shown when managing a system in which the adjustment costs present are determined by the model indicated, and compared to the same costs and profits of managing the same system using a Reed model, which ignores adjustment costs, and thus tends to pay much higher fees for adjustment.
-In contrast, the difference in profit after accounting for costs is only marginally less than the value derived by managing the population to optimize profits when ignoring adjustment costs (Reed model).", fig.width=6, fig.height=5, dependson="histogram-calc", dev=c("pdf", "svg", "png")}
+In contrast, the difference in profit after accounting for costs is only marginally less than the value derived by managing the population to optimize profits when ignoring adjustment costs (Reed model).", fig.width=8, fig.height=6, dependson="histogram-calc", dev=c("pdf", "svg", "png")}
 
@@
 In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present.
-The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs.", dev=c("pdf", "svg", "png")}
+The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs.", dev=c("pdf", "svg", "png"), fig.width=7}
 
@@
 the optimal free solution when the expected reduction should only be 10%
-less than optimal free. In this case, ignoring the costs all together
+less than optimal free based on the $c_i$ calibration. In this case, ignoring the costs all together
 is still worse than using $\Pi_1$ costs -- the red bar is lower than the blue.
@@
 than either assuming costs are quadratic ($\Pi_2$) when they are fixed ($\Pi_3$),
-or assuming they are fixed when they are quadratic.
-
-Nevertheless, assuming quadratic costs is always the most conservative
-option -- scenarios in which true costs are quadratic (regardless of what
+or assuming they are fixed when they are quadratic.  Scenarios in which true costs are quadratic (regardless of what
 cost structure is assumed by the policy) do significantly worse than
@@
 Successive panels show increasing reduction of the net present value by increasing penalty coefficients: e.g.
-a policy in the first panel should lose only 10% of its net present value to adjustment costs if it had the correct form of those costs.", dev=c("pdf", "svg", "png")}
+a policy in the first panel would lose only 10% of its net present value to adjustment costs if it had the correct form of those costs, as determined by the choice of penalty coefficient.", dev=c("pdf", "svg", "png"), fig.width=7}
 who <- c("penalty_fn", "ignore_fraction", "mismatched_fraction", "reduction")
@@
 form we consider, in which the costs of policy adjustment scale linearly
-with the size of the adjustment ($Pi_1$), has less obvious effects on
-optimal policies. But interestingly, it is the only formulation for
-which we observed positive unchanging quotas of the type most commonly
-encountered in real-world applications.
+with the size of the adjustment ($\Pi_1$), has less obvious effects on
+optimal policies. But interestingly, it is the only formulation that
+most frequently produces stretches of strictly positive but unchanging
+quotas of the type most commonly encountered in real-world applications.
 
@@
 
+Acknowledgements
+================
+
+This project arose out of a NIMBioS working group, "Pretty Darn Good Control".
+The authors acknowledge helpful discussions and input from working group
+co-organizers Megan Donahue and Carl Toews, and participants Marie-Josee Fortin, 
+Dan Ryan, Frank Doyle, Claire Paris, Iadine Chades and Mandy Karnauskas.   
+We also acknowledge the following support: NSF Grant DBI-1306697 (CB), ...
+
 Supplementary material
 ======================
+
+_Economic penalties promised for the supplement are still to come_
 
@@
 
-```{r table-caption}
+<!-- Ingoring this, not useful-->
+```{r Table1, results="asis", eval=FALSE}
 caption = "Table 1: Column 'ignoring' shows the results of ignoring a adjustment penalty when it is present, Column 'assuming' shows the results of assuming an adjustment cost when it is absent.
@@
 Comparing the second and third columns shows that ignoring a real cost is a significantly graver error, particularly in the case of quadratic costs."
-```
-
-```{r Table1, results="asis"}
 pandoc.table(table1, caption=caption)

### 2014-07-25 manuscripts/presentation.Rmd
updated presentation, minor tweaks to manuscript from Paul feedback

@@
     incremental: true
-
+transition: none
 author: |
@@
 
-<img src="components/images/global-change.jpg" width="500" style="margin:0px auto;display:block">
+<img src="components/images/global-change.jpg" width="500">
 
@@
 <small> Alex Wong (Getty Images) </small>
-
-# Why?
-
-## Postulate: policy intertia
-
-> Policies are costly to change
-
-## We're quite good at accounting for _ecological_ dynamics
-
-## Dynamic optimization - Dynamic policies
-
-<small> Reed (1979) [10.1016/0095-0696(79)90014-7](http://doi.org/10.1016/0095-0696(79)90014-7) </small>
-
-## Not so good at _policy_ dynamics
-
-- We account for ecological dynamics but not political ones
-- We're not political scientists, we don't know the equations of politics (does anyone?)
-- Instead, we can investigate the potential impact that costly adjustments have on optimal policy
 
@@
 
-theme_set(theme_tufte())
+theme_set(theme_tufte(base_size=18))
 ```
@@
 
-## Bluefin Tuna Quotas, ICCAT
+----
 
-```{r Figure_1, fig.cap="Quota on Blue Fin Tuna Catch", dev=c("svg", "png")}
+![](components/images/tuna_cc0.jpg)
+
+<small> NOAA </small>
+
+## Bluefin Tuna Stocks vs US Quota, ICCAT 1987 - 2007
+
+```{r Figure_1, fig.cap="Quota on Blue Fin Tuna Catch", dev=c("svg", "png"), cache=FALSE}
 tuna <- read.csv("components/data/tuna.csv")
-ggplot(tuna, aes(year, quota)) + geom_point() + theme_bw()
+tuna<-melt(tuna, id="year")
+ggplot(tuna, aes(year, value)) + geom_point() +
+  facet_wrap(~variable, ncol=1, scale="free_y") + 
+  ylab("Bluefin Tuna harvest (tonnes)") + theme_bw()
+
 ```
+
+## dynamic optimization, dynamic policies
+
+<img src="components/images/mangel_and_clark.jpg", width="300">
+
+----
+
+<img src="components/images/confusion0.png" width="600">
+
+----
+
+<img src="components/images/confusion1.png" width="600">
+
+----
+
+<img src="components/images/confusion_matrix.png" width="600">
+
+----
+
+<img src="components/images/numbers.png" width="600">
+
+----
+
+<img src="components/images/outcomes_numbers.png" width="600">
+
+----
+
+<img src="components/images/time_grid.png" width="600">
+
+----
+
+<img src="components/images/previous_action.png" width="600">
+
+<!--
+## Postulate: policy intertia
+
+> Policies are costly to change
+
+## We're quite good at accounting for _ecological_ dynamics
+
+----
+
+<small> Reed (1979) [10.1016/0095-0696(79)90014-7](http://doi.org/10.1016/0095-0696(79)90014-7) </small>
+
+## Not so good at _policy_ dynamics
+
+- We account for ecological dynamics but not political ones
+- We're not political scientists, we don't know the equations of politics (does anyone?)
+- Instead, we can investigate the potential impact that costly adjustments have on optimal policy
+
+-->
 
@@
 
-```{r Figure_2, fig.cap="",  dev=c("svg", "png")}
+```{r Figure_2, fig.cap="",  dev=c("svg", "png"), cache=FALSE}
 
@@
 
-```{r Figure_3, dependson="tidy", fig.cap="", dev=c("svg", "png")}
+```{r Figure_3, dependson="tidy", fig.cap="", dev=c("svg", "png"), cache=FALSE}
 
@@
 
-```{r Figure_4, fig.cap="", dev=c("svg", "png")}
+```{r Figure_4, fig.cap="", dev=c("svg", "png"), cache=FALSE}
 ggplot(subset(figure4_df, statistic != "cross.correlation"), 
@@
 
-```{r Figure_5, fig.cap="",  dependson="histogram-calc", dev=c("svg", "png")}
+```{r Figure_5, fig.cap="",  dependson="histogram-calc", dev=c("svg", "png"), cache=FALSE}
 
@@
 
-```{r Figure_6, fig.cap="", dev=c("svg", "png")}
+```{r Figure_6, fig.cap="", dev=c("svg", "png"), cache=FALSE}
 
@@
 
-```{r Figure_7, fig.cap="", dev=c("svg", "png")}
+```{r Figure_7, fig.cap="", dev=c("svg", "png"), cache=FALSE}
 who <- c("penalty_fn", "ignore_fraction", "mismatched_fraction", "reduction")
@@
                               'L2_fixed' =  substitute(paste(Pi[2],"_", Pi[3])))) + 
-  xlab("Penalty function")
+  xlab("Penalty function") + theme_tufte(base_size=14)
 ```
+
+```{r bluefin_landings, dev=c("svg", "png"), eval=FALSE}
+landings <- data.table(read.csv("components/data/iccat.csv"))
+bluefin <- landings[Species == "BFT" & PartyName=="UNITED STATES" & YearC %in% 1987:2007,]
+ggplot(bluefin, aes(x=YearC,y= Qty_t)) + 
+  stat_summary(fun.y = "sum", geom="line") + 
+  xlab("Year")+ylab("Catch (tonnes)")
+
+#library("rfisheries")
+#landings <- of_landings(species="BFT")
+#landings <- landings[landings$year %in% 1982:2007,]
+#ggplot(landings, aes(year, catch)) + geom_line() + ylab("Global landings (tonnes)")
+```

### 2014-07-30 manuscripts/presentation.Rmd
set output to reveal_js

@@
 output: 
-  ioslides_presentation:
-    self_contained: false
-    css: components/style.css
+#  ioslides_presentation:
+#    self_contained: false
+#    css: components/style.css
+#    incremental: true
+  revealjs_presentation:
+    theme: serif
+    self_contained: true
     incremental: true
+    transition: none
+    pandoc_args: ["--css", "style.css"]
 transition: none

### 2014-07-30 manuscripts/manuscript.Rmd

@@
 
-$$N_{t+1} = Z_t \frac{A (N_t - h_t)}{1 + B (N_t - h_t)}, \label{eq:state_equation}$$
+\begin{equation}
+N_{t+1} = Z_t \frac{A (N_t - h_t)}{1 + B (N_t - h_t)}, \label{eq:state_equation}
+\end{equation}
 
@@
 adjustment costs are associated with changes to this control variable.
+In each case, we assume there is no cost in initially setting the harvest
+policy at time 0.
 
@@
 
-Each of the policy adjustment cost function is characterized in terms of
+Each policy adjustment cost function is characterized in terms of
 a cost coefficient $c_i$. However, $c_i$ takes different units for each
@@
 deterministic model without harvesting is 10; (specifically, $A=$ `r pars[1]` and
-$B=$ `r pars[2]` in Eqn. (1)). To characterize environmental variability, we
+$B=$ `r pars[2]` in Eqn \eqref{eq:state_equation}. To characterize environmental variability, we
 assume multiplicative shock $Z_t$ is distributed log-normally with 
@@
 
-For example, when small policy adjustment costs cost little but large
+For example, when small policy adjustments cost little but large
 adjustments are expensive ($\Pi_2$), we see the smoothing signal that we
@@
 Finally, the case where policy adjustment costs scale linearly with the
-size of the adjustment ($\Pi_1$ in Eqn. 4) appear to be something of a
+size of the adjustment ($\Pi_1$) appear to be something of a
 middle of the road strategy, in that increasing the severity of policy
@@
 type of policy is arguably the most commonly observed behavior in TAC
-management, but is one that is almost never observed to be part of the
+management, but is one that is very rarely observed to be part of the
 optimal management strategy in the basic model without policy adjustment
@@
 Histograms for the different contributions labelled $[1]-[4]$ here when
-taken across 100 replicate runs are shown are shown in Figure 5.
-<!--(contribution $[1]$ red, $[2]$ green, $[3]$ blue, and $[4]$ mauve).--> The
-cost of assuming policy adjustments are present when in fact they are
+taken across 100 replicate runs are shown in Figure 5. Observe that the red
+distributions (dockside profits) are relatively unchanged between policies based on the adjustment-free assumption (Reed, bottom row) vs when adjustments are properly accounted for (adjustment penalty, top row), while the blue distributions (costs for adjustment) are much larger in the bottom row then
+in the top (when these costs have not been accounted for vs when they have
+been taken into account.)  The cost of assuming policy adjustments are present when in fact they are
 absent is given by subtracting the contribution to the first infinite
@@
 policies differ.  As a result, the value is slightly more than half of
-the optimal free solution when the expected reduction should only be 10%
+the optimal free solution when the expected reduction should only be 10% (panel A)
 less than optimal free based on the $c_i$ calibration. In this case, ignoring the costs all together
@@
 These patterns hold across the different size reductions shown (from 10%
-to 25%), though net present value becomes negative under the quadratic
+to 25%, panels a-d respectively), though net present value becomes negative under the quadratic
 form for the larger penalties as costs paid for adjustments exceed
@@
 Successive panels show increasing reduction of the net present value by increasing penalty coefficients: e.g.
-a policy in the first panel would lose only 10% of its net present value to adjustment costs if it had the correct form of those costs, as determined by the choice of penalty coefficient.", dev=c("pdf", "svg", "png"), fig.width=7}
+a policy in the first panel would lose only 10% (panel A) of its net present value to adjustment costs if it had the correct form of those costs, as determined by the choice of penalty coefficient.", dev=c("pdf", "svg", "png"), fig.width=7}
 who <- c("penalty_fn", "ignore_fraction", "mismatched_fraction", "reduction")
@@
 policy adjustment increased as a quadratic function of the magnitude of
-the policy change being proposed (our $\Pi_2$ formulation in Eqn.) In
+the policy change being proposed (our $\Pi_2$ formulation) In
 effect, this means that small changes to annual quotas incur little
@@
 expensive to make. Including costs of this form smoothes inter-annual
-variation in the catch quotas that would be recommended. However, as
-catches become less variable through time, the variability in the fish
-population itself increases. In essence, the optimal policy no longer
-soaks up as much of the natural variability in recruitment that is
-affecting the population. Also, the catches and remaining stock sizes
+variation in the catch quotas that would be recommended. Also, the catches and remaining stock sizes
 corresponding to optimal management become more autocorrelated in time,
@@
 with the size of the adjustment ($\Pi_1$), has less obvious effects on
-optimal policies. But interestingly, it is the only formulation that
+optimal policies. But interestingly, it is the formulation that
 most frequently produces stretches of strictly positive but unchanging
@@
 or ones that derive policy recommendations endogenously by modeling
-interactions between different stakeholders [@Kaitala1993, @Laukkanen2003].
+interactions between different stakeholders [@Kaitala1993; @Laukkanen2003].
 As such, we anticipate that our approach will be more relevant to

### 2014-07-30 manuscripts/presentation.Rmd

--- 2014-07-25 manuscripts/presentation.Rmd
@@
 output: 
-  ioslides_presentation:
+  revealjs_presentation:
+    theme: serif
     self_contained: false
-    css: components/style.css
     incremental: true
     transition: none
-author: |
-        Carl Boettiger, Michael Bode, James Sanchirico, 
-        Jacob LaRiviera, Alan Hastings, Paul Armsworth
+    pandoc_args: ["--css", "components/style.css"]
+author: Carl Boettiger, Michael Bode, James Sanchirico, Jacob LaRiviera, Alan Hastings, Paul Armsworth
 
@@
 
-theme_set(theme_tufte(base_size=18))
+theme_set(theme_bw(base_size=18))
 ```
@@
 
-![](components/images/tuna_cc0.jpg)
+![](components/images/tuna_cc0.png)
 

### 2014-07-31 manuscripts/presentation.Rmd
no-go without self-contained

@@
 date: "08/12/2014"
+revealjs-url:  "./presentation_files/revealjs-2.6.1"
 output: 

### 2014-07-31 manuscripts/presentation.Rmd
fix local path, but no luck

--- 2014-07-30 manuscripts/presentation.Rmd
@@
 date: "08/12/2014"
+revealjs-url:  "./presentation_files/reveal.js-2.6.1"
 output: 

### 2014-07-31 manuscripts/manuscript.Rmd
whoa, ggplot2 labeller started labeling incorrectly...

@@
 labeller <- function(variable,value){
-    return(relabel[value])
+    return(relabel[paste(value)])
 }
@@
 if (variable=='penalty_fn') {
-    return(relabel[value])
+    return(relabel[paste(value)])
   } else {
-    return(assume[value])
+    return(assume[paste(value)])
   }

### 2014-07-31 manuscripts/presentation.Rmd
whoa, ggplot2 labeller started labeling incorrectly...

--- 2014-07-30 manuscripts/presentation.Rmd
@@
 labeller <- function(variable,value){
-    return(relabel[value])
+    relabel[paste(value)]
 }

### 2014-07-31 manuscripts/presentation.Rmd
layout adjusted

--- 2014-07-31 manuscripts/presentation.Rmd
@@
 
-## dynamic optimization, dynamic policies
-
-<img src="components/images/mangel_and_clark.jpg", width="300">
-
 ----
 
-<img src="components/images/confusion0.png" width="600">
-
-----
-
-<img src="components/images/confusion1.png" width="600">
-
-----
-
-<img src="components/images/confusion_matrix.png" width="600">
-
-----
-
-<img src="components/images/numbers.png" width="600">
-
-----
-
-<img src="components/images/outcomes_numbers.png" width="600">
-
-----
-
-<img src="components/images/time_grid.png" width="600">
-
-----
-
-<img src="components/images/previous_action.png" width="600">
-
-<!--
-## Postulate: policy intertia
-
-> Policies are costly to change
-
-## We're quite good at accounting for _ecological_ dynamics
-
-----
-
-<small> Reed (1979) [10.1016/0095-0696(79)90014-7](http://doi.org/10.1016/0095-0696(79)90014-7) </small>
+> ## As ecologists, we've ever focused on accounting for _ecological_ dynamics
 
@@
 
--->
+Model setup
+------------
+
+- Focus on _stochastic_ dynamics: thus a constant harvest is not optimal.
+
+- Follow the textbook classic approach: Reed (1979) [10.1016/0095-0696(79)90014-7](http://doi.org/10.1016/0095-0696(79)90014-7)
 
@@
 
+Population grows under a Beverton-Holt stock-recruitment curve,
+
 $$N_{t+1} = Z_t \frac{A (N_t - h_t)}{1 + B (N_t - h_t)}$$
+
+- subject to multiplicitive log-normal growth shocks $Z_t$
 
@@
 ```
+
+## dynamic optimization, dynamic policies
+
+<img src="components/images/mangel_and_clark.jpg", width="300">
+
+----
+
+<img src="components/images/confusion0.png" width="600">
+
+----
+
+<img src="components/images/confusion1.png" width="600">
+
+----
+
+<img src="components/images/confusion_matrix.png" width="600">
+
+----
+
+<img src="components/images/numbers.png" width="600">
+
+----
+
+<img src="components/images/outcomes_numbers.png" width="600">
+
+----
+
+<img src="components/images/time_grid.png" width="600">
+
+----
+
+<img src="components/images/previous_action.png" width="600">
 

### 2014-07-31 manuscripts/presentation.Rmd
tweak layout

--- 2014-07-31 manuscripts/presentation.Rmd
@@
 date: "08/12/2014"
-revealjs-url:  "./presentation_files/reveal.js-2.6.1"
 output: 
@@
 
----
-
-<!-- 
+notes: |
   Time: 30 minutes with questions
   Presenting at: 2014-12-08 15:10:00 PDT
--->
+
+---
 

### 2014-08-05 manuscripts/presentation.Rmd
update slides

@@
 library("snowfall")
+library("tidyr")
+library("dplyr")
+transparent = theme(
+    panel.background = element_rect(fill = "transparent",colour = NA), 
+    plot.background = element_rect(fill = "transparent",colour = NA))
 
-theme_set(theme_bw(base_size=18))
+theme_set(theme_bw(base_size=18) + transparent)
 ```
+
 ```{r analysis, include=FALSE}
@@
 ----
+
+## Natural populations fluctuate...
+
+```{r ex_fish, fig.cap="", dev=c("svg", "png"), dev.args=list(bg="transparent")}
+ex <- filter(dt, replicate=="rep_17" & penalty_fn == "L1" & time < 20)
+ggplot(ex) + 
+  geom_line(aes(time, fishstock), col="darkblue", lwd=1)
+```
+
+## So then, do our optimal policies
+
+```{r ex_harvest, fig.cap="", dev=c("svg", "png"), dependson="ex_fish", dev.args=list(bg="transparent")}
+ggplot(ex) + 
+  geom_line(aes(time, harvest_alt), col="darkgreen", lwd=1) +
+  ylab("Optimal quota policy") 
+```
+
+## Real policies: not so much
 
@@
 
-```{r Figure_1, fig.cap="Quota on Blue Fin Tuna Catch", dev=c("svg", "png"), cache=FALSE}
+```{r Figure_1, fig.cap="Quota on Blue Fin Tuna Catch", dev=c("svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
 tuna <- read.csv("components/data/tuna.csv")
@@
   facet_wrap(~variable, ncol=1, scale="free_y") + 
-  ylab("Bluefin Tuna harvest (tonnes)") + theme_bw()
+  ylab("Bluefin Tuna (tonnes)") + theme_bw()
 
@@
 
-- We account for ecological dynamics but not political ones
-- We're not political scientists, we don't know the equations of politics (does anyone?)
+- We account for _ecological_ dynamics but not _political_ ones
+- We don't know the equations of politics (does anyone?)
 - Instead, we can investigate the potential impact that costly adjustments have on optimal policy
@@
 
-- Follow the textbook classic approach: Reed (1979) [10.1016/0095-0696(79)90014-7](http://doi.org/10.1016/0095-0696(79)90014-7)
+- Follow the textbook classic approach: __Reed (1979)__ [10.1016/0095-0696(79)90014-7](http://doi.org/10.1016/0095-0696(79)90014-7)
 
-Fish population dynamics (state equation)
------------------------------------------
+```{r, fig.cap="",  dev=c("svg", "png"), cache=FALSE, dev.args=list(bg="transparent"), fig.height=3}
+ex <- dt %>% 
+  filter(replicate=="rep_17" & penalty_fn == "L1" & time < 20) %>%
+  select(time, fishstock, harvest_alt) %>%
+  gather(variable, stock, -time) 
+ggplot(ex) + 
+  geom_line(aes(time, stock, col=variable), lwd=1) + 
+  scale_color_discrete(labels=c(fishstock = "Stock size", harvest_alt = "Harvest policy"), name="")
+
+```
+
+Fish population dynamics 
+--------------------------
+
+### (state equation)
 
@@
 
+Select harvest policy that maximizes the Net Present Value (NPV) of the stock:
+
 $$\max_{{\bf h}}\mathbf{ E} ( NPV_{0} )=\max_{{\bf h}} \sum_0^\infty \mathbf{E} \left(\frac{\Pi_0(N_t,h_t)}{(1+\delta)^{t+1}} \right)$$
 
-$$\Pi_0(N_t,h_t) = p h_t -  c_0 E_t $$
+- Profits from harvesting depend on price and costs $\Pi_0(N_t,h_t) = p h_t -  c_0 E_t(N_t, h_t) $
+- Harvest quota $h_t$ in year $t$
+- Stock size $N_t$, measured before harvest
+- discount rate $\delta$
 
-Costs of policy adjustment 
---------------------------
+### Costs of policy adjustment
 
-We replace $\Pi_0$ in the $NPV_0$ equation with
+- We replace $\Pi_0$ in the $NPV_0$ equation with...
 
-$$\Pi_{1}(N_t,h_t, h_{t-1}) = \Pi_0 - c_1  |  h_t - h_{t-1} | \,.$$
+"Linear costs"
+-------------
 
-$$\Pi_{2}(N_t,h_t, h_{t-1}) = \Pi_0 - c_2 (  h_t - h_{t-1})^2 \,.$$
+$$\Pi_{1}(N_t,h_t, h_{t-1}) = \Pi_0 - c_1  |  h_t - h_{t-1} | $$
 
-$$\Pi_{3}(N_t,h_t, h_{t-1}) = \Pi_0 - c_3 (1-\mathbf{I}(h_t, h_{t-1}))  \,,$$
+- All previous terms, minus: 
+- The cost to change the harvest policy (quota): proportional to the size of the change
+
+ "Quadratic costs"
+-----------------
+
+$$\Pi_{2}(N_t,h_t, h_{t-1}) = \Pi_0 - c_2 (  h_t - h_{t-1})^2 $$
+
+- Small adjustments are very cheap
+- Large adjustments are very expensive
+- Closest to typical assumptions of quadratic costs on harvest/effort (but hear it is the _change_ in harvest/effort)
+
+ "Fixed costs"
+------------
+
+$$\Pi_{3}(N_t,h_t, h_{t-1}) = \Pi_0 - c_3 (1-\mathbb{I}(h_t, h_{t-1}))  $$
+
+- A fixed transaction fee for any change to policy, independent of size.
+
+<br/>
+<br/>
+<small>($\mathbb{I(x,y)}$ is indicator function, equals 1 iff $x=y$, zero otherwise.) </small>
 
 Apples to Apples 
---------------------
+------------------
 
-```{r Figure_2, fig.cap="",  dev=c("svg", "png"), cache=FALSE}
+### How do we pick coefficients $c_i$ such that only the functional form and not the overall cost differ?
+
+Apples to Apples
+------------------
+
+```{r Figure_2, fig.cap="",  dev=c("svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
 
@@
 
-## dynamic optimization, dynamic policies
+----
+
+## Problem defined. Time to compute solutions.
+
+## Implementation:
+
+### Stochastic Dynamic Programming
 
@@
 
-```{r Figure_3, dependson="tidy", fig.cap="", dev=c("svg", "png"), cache=FALSE}
+What would you predict for...
+
+- Quadratic adjustment costs?
+- Linear adjustment costs?
+- Fixed adjustment costs?
+
+```{r reex, fig.cap="", dev=c("svg", "png"), cache=FALSE, dev.args=list(bg="transparent"), fig.height=3}
+ggplot(ex) + 
+  geom_line(aes(time, stock, col=variable), lwd=1) + 
+  scale_color_discrete(labels=c(fishstock = "Stock size", harvest_alt = "Harvest policy"), name="") 
+```
+
+Quadratic Costs ($\Pi_2$)
+-------------------------
+
+```{r quadratic, fig.cap="", dev=c("svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
+ex <- dt %>% 
+  filter(replicate=="rep_17" & penalty_fn == "L2") %>%
+  select(time, harvest, harvest_alt) %>%
+  gather(variable, value, -time) 
+ggplot(ex) + 
+  geom_line(aes(time, value, col=variable), lwd=1) + 
+  ylab("harvest quota") +
+  scale_color_discrete(labels=c(harvest = "adjusted policy", harvest_alt = "baseline policy"), name="") 
+```
+
+Fixed Costs ($\Pi_3$)
+---------------------
+
+```{r fixed, fig.cap="", dev=c("svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
+ex <- dt %>% 
+  filter(replicate=="rep_17" & penalty_fn == "fixed") %>%
+  select(time, harvest, harvest_alt) %>%
+  gather(variable, value, -time) 
+ggplot(ex) + 
+  geom_line(aes(time, value, col=variable), lwd=1) + 
+  ylab("harvest quota") +
+  scale_color_discrete(labels=c(harvest = "adjusted policy", harvest_alt = "baseline policy"), name="") 
+```
+
+Linear Costs ($\Pi_1$)
+---------------------
+
+```{r linear, fig.cap="", dev=c("svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
+ex <- dt %>% 
+  filter(replicate=="rep_17" & penalty_fn == "L1") %>%
+  select(time, harvest, harvest_alt) %>%
+  gather(variable, value, -time) 
+ggplot(ex) + 
+  geom_line(aes(time, value, col=variable), lwd=1) + 
+  ylab("harvest quota") +
+  scale_color_discrete(labels=c(harvest = "adjusted policy", harvest_alt = "baseline policy"), name="") 
+```
+
+(For comparison)
+----------------
+
+```{r Figure_3, dependson="tidy", fig.cap="", dev=c("svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
 
@@
 
-## Figure 4
+## General trends
 
-```{r Figure_4, fig.cap="", dev=c("svg", "png"), cache=FALSE}
+```{r Figure_4, fig.cap="", dev=c("svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
 ggplot(subset(figure4_df, statistic != "cross.correlation"), 
@@
   xlab("Penalty size (as fraction of NPV0)")
+```
 
-write.csv(figure4_df, "components/data/figure4.csv")
-```
+- Quadratic ($\Pi_2$) smooths, Linear ($\Pi_1$) flattens, Fixed ($\Pi_3$) jumps
+
+## Okay, so the policies "look" different. Does it matter?
+
+## Yes
+
+## Managing under the wrong assumptions
+
+$$NPV_i( h_1^* ) = \sum_{t=0}^\infty (\overbrace{ p h^*_{1,t}-c_0E^*_{1t}}^{[1]}-\overbrace{c_1 | h^*_{1,t}- h^*_{1,t-1}|}^{[2]} )  \frac{1}{(1+\delta)^t}$$
+
+$$NPV_i( h_0^* ) = \sum_{t=0}^\infty (\underbrace{ p h^*_{0,t}-c_0E^*_{0t}}_{[3]}-\underbrace{c_1 | h^*_{0,t}- h^*_{0,t-1}|}_{[4]} )  \frac{1}{(1+\delta)^t}$$
+
+<small>
+
+1. Dockside profits when accounting for adjustment cost 
+2. (Anticipated) Fees paid for adjusting the policy
+3. Theoretical maximum dockside profits 
+4. (Unanticipated) fees for those adjustments
+
+</small>
 
@@
 setnames(reed_profits, "V1", "profits")
-
 Reed <- cbind(reed_profits, costs = reed_costs$V1, Assumption = "Reed") 
 Adj <- cbind(profits, costs = costs$V1, Assumption = "Adjustment penalty")
-
 hist_dat <- melt(rbind(Adj, Reed), id=c("penalty_fn", "replicate", "Assumption"))
@@
 
-```{r Figure_5, fig.cap="",  dependson="histogram-calc", dev=c("svg", "png"), cache=FALSE}
+```{r Figure_5, fig.cap="",  dependson="histogram-calc", dev=c("svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
 
@@
   } else {
-    return(assume[paste(value)])
+    return(assume[value])
   }
@@
 
-write.csv(hist_dat, "components/data/figure5.csv")
 ```
 
-## Penalty
+Consequences of policy adjustment costs 
+---------------------------------------
 
-$$NPV_i( h_1^* ) = \sum_{t=0}^\infty (\overbrace{ p h^*_{1,t}-c_0E^*_{1t}}^{[1]}-\overbrace{c_1 | h^*_{1,t}- h^*_{1,t-1}|}^{[2]} )  \frac{1}{(1+\delta)^t}$$
+What is the impact of assuming costs are present when they are not?
 
-$$NPV_i( h_0^* ) = \sum_{t=0}^\infty (\underbrace{ p h^*_{0,t}-c_0E^*_{0t}}_{[3]}-\underbrace{c_1 | h^*_{0,t}- h^*_{0,t-1}|}_{[4]} )  \frac{1}{(1+\delta)^t}$$
+- _Very little change to your bottom line_ (regardless of cost structure) <br/><br/>
 
-## Figure 6
+What is the impact of ignoring costs when they are present?
 
-```{r Figure_6, fig.cap="", dev=c("svg", "png"), cache=FALSE}
+- _Substantially higher costs_ (particularly for quadratic costs).
+
+## To say that another way:
+
+```{r Figure_6, fig.cap="", dev=c("svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
 
@@
 
-## Mismatches
+## What about managing when costs are present...
 
-```{r Figure_7, fig.cap="", dev=c("svg", "png"), cache=FALSE}
+###  ..but you're using the wrong model??
+
+## Mismatches are even worse:
+
+```{r Figure_7, fig.cap="", dev=c("svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
 who <- c("penalty_fn", "ignore_fraction", "mismatched_fraction", "reduction")
@@
                               'L2_fixed' =  substitute(paste(Pi[2],"_", Pi[3])))) + 
-  xlab("Penalty function") + theme_tufte(base_size=14)
+  xlab("Penalty function as: assumed_reality") + theme_tufte(base_size=14)
 ```
 
-```{r bluefin_landings, dev=c("svg", "png"), eval=FALSE}
-landings <- data.table(read.csv("components/data/iccat.csv"))
-bluefin <- landings[Species == "BFT" & PartyName=="UNITED STATES" & YearC %in% 1987:2007,]
-ggplot(bluefin, aes(x=YearC,y= Qty_t)) + 
-  stat_summary(fun.y = "sum", geom="line") + 
-  xlab("Year")+ylab("Catch (tonnes)")
+## Mismatched costs are intuitive if we remember the general patterns
 
-#library("rfisheries")
-#landings <- of_landings(species="BFT")
-#landings <- landings[landings$year %in% 1982:2007,]
-#ggplot(landings, aes(year, catch)) + geom_line() + ylab("Global landings (tonnes)")
+- Quadratic ($\Pi_2$) smooths
+- Linear ($\Pi_1$) flattens
+- Fixed ($\Pi_3$) jumps
+
+Predict which is worse: assuming the wrong cost or no assuming no cost at all, when:
+
+- Costs are assumed linear but in reality quadratic?
+- True costs are assumed quadratic but in reality fixed?
+
+## Mismatched costs are intuitive
+
+```{r Figure_7again, fig.cap="", dev=c("svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
+ggplot(table2_long, aes(penalty.fn, value, fill = variable)) + 
+  geom_bar(stat="identity", position="dodge") + 
+  facet_wrap(~reduction, scales="free_y") +
+  scale_x_discrete(labels = c('L1_L2' = substitute(paste(Pi[1],"_", Pi[2])), 
+                              'L2_L1' =  substitute(paste(Pi[2],"_", Pi[1])),
+                              'L1_fixed' = substitute(paste(Pi[1],"_", Pi[3])), 
+                              'fixed_L1' =  substitute(paste(Pi[3],"_", Pi[1])),
+                              'fixed_L2' = substitute(paste(Pi[3],"_", Pi[2])), 
+                              'L2_fixed' =  substitute(paste(Pi[2],"_", Pi[3])))) + 
+  xlab("Penalty function as: assumed_reality") + theme_tufte(base_size=14)
 ```
+
+## Conclusions
+
+- Policies reflecting the best ecology may ultimately be impractical
+- Novel look at introducing costs to changes in policy
+- Details matter: some adjustment costs make policy less smooth, some more smooth
+- Solutions can satisfy the constraints of adjustment costs while performing nearly optimally
+- Ignoring adjustment costs can result in significant penalties
+- There are many benefits to joining a NIMBioS working group
+
+## Acknowledgements
+
+<img src="components/images/nsf.jpg" width="100" height="100"><img src="components/images/noaa.jpg" width="100" height="100"><img src="components/images/sloan.jpg" width="100" height="100">  <br/>
+
+<img src="components/images/nimbios.jpg" width="150" height="75"> 
+<img src="components/images/csgf.png" width="150" height="75"> <br/>
+
+<!-- Paid the bills and folks that have supported or otherwise
+tolerated this and so many other side projects -->
+
+<small>Slides, data, references, code and more at: http://io.carlboettiger.info/pdg_control</small>

### 2014-08-06 manuscripts/presentation.Rmd
self-contained with printing

@@
     theme: serif
-    self_contained: false
+    self_contained: true
     incremental: true
@@
 
-## Bluefin Tuna Stocks vs US Quota, ICCAT 1987 - 2007
+## Bluefin Tuna Stocks vs Quota (base TAC), ICCAT 1987 - 2007
 
@@
 ```
+
+<small> base TAC for the stock (before any underages or overages are applied or divided by country)</small>
 

### 2014-08-11 manuscripts/presentation.Rmd
update presentation

@@
     pandoc_args: ["--css", "components/style.css"]
-author: Carl Boettiger, Michael Bode, James Sanchirico, Jacob LaRiviera, Alan Hastings, Paul Armsworth
+author: Carl Boettiger, Michael Bode, James Sanchirico, Jacob LaRiviere, Alan Hastings, Paul Armsworth
 
@@
 
-> ## As ecologists, we've ever focused on accounting for _ecological_ dynamics
+> ## As ecologists, we've always focused on accounting for _ecological_ dynamics
 
@@
 
-- subject to multiplicitive log-normal growth shocks $Z_t$
+- subject to multiplicative log-normal growth shocks $Z_t$
 
@@
 - Large adjustments are very expensive
-- Closest to typical assumptions of quadratic costs on harvest/effort (but hear it is the _change_ in harvest/effort)
+- Closest to typical assumptions of quadratic costs on harvest/effort (but here it is the _change_ in harvest/effort)
 
@@
 
-- A fixed transaction fee for any change to policy, independent of size.
+- A fixed transaction fee for any change to policy, independent of size (or sign) of the change.
 
@@
 ### How do we pick coefficients $c_i$ such that only the functional form and not the overall cost differ?
+
+- All forms will create complete resistance to change if the costs are high enough
+- But how do we compare across forms that have different units and different coefficients?
 
@@
 
+## A 'Pretty Darn Good' Working Group
+
+![](components/images/pdg-group.jpg)
+
 ## Acknowledgements

### 2014-08-11 manuscripts/supplement.Rmd
additional analyses

--- 2014-08-05 manuscripts/presentation.Rmd
@@
 ---
-title: "Fisheries management when quotas are costly to change"
-date: "08/12/2014"
+title: Optimal management of a stochastically varying population when policy adjustment is costly
+author: 
+  - name: Carl Boettiger
+    affiliation: cstar
+    email: cboettig (at) gmail.com
+    footnote: Corresponding author
+  - name: Michael Bode
+    affiliation: melbourne
+  - name: James Sanchirico
+    affiliation: UCD
+  - name: Jacob LaRiviere
+    affiliation: UTK
+  - name: Alan Hastings
+    affiliation: UCD
+  - name: Paul Armsworth 
+    affiliation: UTK
+
+address: 
+  - code: cstar
+    address: | 
+      Center for Stock Assessment Research,
+      110 Shaffer Rd,
+      Santa Cruz, CA 95050, USA 
+  - code: UCD
+    address: Department of Environmental Science and Policy, University of California, Davis
+  - code: melbourne
+    address: University of Melbourne, Australia 
+  - code: UTK
+    address: University of Tennessee, Knoxville
+
+layout: review,12pt
+linenumbers: true
+
+bibliography: components/references.bib
+csl: components/ecology.csl
+documentclass: components/elsarticle
+
 output:
-  revealjs_presentation:
-    theme: serif
-    self_contained: false
-    incremental: true
-    transition: none
-    pandoc_args: ["--css", "components/style.css"]
-author: Carl Boettiger, Michael Bode, James Sanchirico, Jacob LaRiviera, Alan Hastings, Paul Armsworth
-
-notes: |
-  Time: 30 minutes with questions
-  Presenting at: 2014-12-08 15:10:00 PDT
+  pdf_document:
+    template: components/elsarticle.latex
+    fig_caption: true
 
 ---
-
-## Our world is changing
-
-<img src="components/images/global-change.jpg" width="500">
-
-<small> Overpeck+ (2011) doi: [10.1126/science.1197869](http://doi.org/10.1126/science.1197869) </small>
-
-## Our policies are not
-
-<img src="components/images/nochange.jpg" width="700">
-
-<small> Alex Wong (Getty Images) </small>
 
@@
 library("knitr")
-basename <- "presentation"
+basename <- "supplement"
 opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
@@
 ```{r analysis, include=FALSE}
-source("components/analysis.R")
+source("components/supp_analysis.R")
 ```
 
-----
-
-## Natural populations fluctuate...
-
-```{r ex_fish, fig.cap="", dev=c("svg", "png"), dev.args=list(bg="transparent")}
+```{r ex_fish, fig.cap="", dev=c("pdf", "svg", "png"), dev.args=list(bg="transparent")}
 ex <- filter(dt, replicate=="rep_17" & penalty_fn == "L1" & time < 20)
@@
 
-```{r ex_harvest, fig.cap="", dev=c("svg", "png"), dependson="ex_fish", dev.args=list(bg="transparent")}
+```{r ex_harvest, fig.cap="", dev=c("pdf", "svg", "png"), dependson="ex_fish", dev.args=list(bg="transparent")}
 ggplot(ex) + 
@@
 
-## Real policies: not so much
-
-![](components/images/tuna_cc0.png)
-
-<small> NOAA </small>
-
-## Bluefin Tuna Stocks vs US Quota, ICCAT 1987 - 2007
-
-```{r Figure_1, fig.cap="Quota on Blue Fin Tuna Catch", dev=c("svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
-tuna <- read.csv("components/data/tuna.csv")
-tuna<-melt(tuna, id="year")
-ggplot(tuna, aes(year, value)) + geom_point() +
-  facet_wrap(~variable, ncol=1, scale="free_y") + 
-  ylab("Bluefin Tuna (tonnes)") + theme_bw()
-
-```
-
-----
-
-> ## As ecologists, we've ever focused on accounting for _ecological_ dynamics
-
-## Not so good at _policy_ dynamics
-
-- We account for _ecological_ dynamics but not _political_ ones
-- We don't know the equations of politics (does anyone?)
-- Instead, we can investigate the potential impact that costly adjustments have on optimal policy
-
-Model setup
-------------
-
-- Focus on _stochastic_ dynamics: thus a constant harvest is not optimal.
-
-- Follow the textbook classic approach: __Reed (1979)__ [10.1016/0095-0696(79)90014-7](http://doi.org/10.1016/0095-0696(79)90014-7)
-
-```{r, fig.cap="",  dev=c("svg", "png"), cache=FALSE, dev.args=list(bg="transparent"), fig.height=3}
+```{r, fig.cap="",  dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent"), fig.height=3}
 ex <- dt %>% 
@@
 
-Fish population dynamics 
---------------------------
-
-### (state equation)
-
-Population grows under a Beverton-Holt stock-recruitment curve,
-
-$$N_{t+1} = Z_t \frac{A (N_t - h_t)}{1 + B (N_t - h_t)}$$
-
-- subject to multiplicitive log-normal growth shocks $Z_t$
-
-Optimization
-------------
-
-Select harvest policy that maximizes the Net Present Value (NPV) of the stock:
-
-$$\max_{{\bf h}}\mathbf{ E} ( NPV_{0} )=\max_{{\bf h}} \sum_0^\infty \mathbf{E} \left(\frac{\Pi_0(N_t,h_t)}{(1+\delta)^{t+1}} \right)$$
-
-- Profits from harvesting depend on price and costs $\Pi_0(N_t,h_t) = p h_t -  c_0 E_t(N_t, h_t) $
-- Harvest quota $h_t$ in year $t$
-- Stock size $N_t$, measured before harvest
-- discount rate $\delta$
-
-### Costs of policy adjustment
-
-- We replace $\Pi_0$ in the $NPV_0$ equation with...
-
-"Linear costs"
--------------
-
-$$\Pi_{1}(N_t,h_t, h_{t-1}) = \Pi_0 - c_1  |  h_t - h_{t-1} | $$
-
-- All previous terms, minus: 
-- The cost to change the harvest policy (quota): proportional to the size of the change
-
- "Quadratic costs"
------------------
-
-$$\Pi_{2}(N_t,h_t, h_{t-1}) = \Pi_0 - c_2 (  h_t - h_{t-1})^2 $$
-
-- Small adjustments are very cheap
-- Large adjustments are very expensive
-- Closest to typical assumptions of quadratic costs on harvest/effort (but hear it is the _change_ in harvest/effort)
-
- "Fixed costs"
-------------
-
-$$\Pi_{3}(N_t,h_t, h_{t-1}) = \Pi_0 - c_3 (1-\mathbb{I}(h_t, h_{t-1}))  $$
-
-- A fixed transaction fee for any change to policy, independent of size.
-
-<br/>
-<br/>
-<small>($\mathbb{I(x,y)}$ is indicator function, equals 1 iff $x=y$, zero otherwise.) </small>
-
 Apples to Apples
@@
 
-### How do we pick coefficients $c_i$ such that only the functional form and not the overall cost differ?
-
-Apples to Apples
-------------------
-
-```{r Figure_2, fig.cap="",  dev=c("svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
+```{r Figure_2, fig.cap="",  dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
 
@@
 
-----
-
-## Problem defined. Time to compute solutions.
-
-## Implementation:
-
-### Stochastic Dynamic Programming
-
-<img src="components/images/mangel_and_clark.jpg", width="300">
-
-----
-
-<img src="components/images/confusion0.png" width="600">
-
-----
-
-<img src="components/images/confusion1.png" width="600">
-
-----
-
-<img src="components/images/confusion_matrix.png" width="600">
-
-----
-
-<img src="components/images/numbers.png" width="600">
-
-----
-
-<img src="components/images/outcomes_numbers.png" width="600">
-
-----
-
-<img src="components/images/time_grid.png" width="600">
-
-----
-
-<img src="components/images/previous_action.png" width="600">
-
-Effect of policy adjustment costs on optimal quotas and stock sizes 
--------------------------------------------------------------------
-
-What would you predict for...
-
-- Quadratic adjustment costs?
-- Linear adjustment costs?
-- Fixed adjustment costs?
-
-```{r reex, fig.cap="", dev=c("svg", "png"), cache=FALSE, dev.args=list(bg="transparent"), fig.height=3}
+```{r reex, fig.cap="", dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent"), fig.height=3}
 ggplot(ex) + 
@@
 
-```{r quadratic, fig.cap="", dev=c("svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
+```{r quadratic, fig.cap="", dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
 ex <- dt %>% 
@@
 
-```{r fixed, fig.cap="", dev=c("svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
+```{r fixed, fig.cap="", dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
 ex <- dt %>% 
@@
 
-```{r linear, fig.cap="", dev=c("svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
+```{r linear, fig.cap="", dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
 ex <- dt %>% 
@@
 
-```{r Figure_3, dependson="tidy", fig.cap="", dev=c("svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
+```{r Figure_3, dependson="tidy", fig.cap="", dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
 
@@
 
-```{r Figure_4, fig.cap="", dev=c("svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
+```{r Figure_4, fig.cap="", dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
 ggplot(subset(figure4_df, statistic != "cross.correlation"), 
@@
 
-## Okay, so the policies "look" different. Does it matter?
-
-## Yes
-
-## Managing under the wrong assumptions
-
-$$NPV_i( h_1^* ) = \sum_{t=0}^\infty (\overbrace{ p h^*_{1,t}-c_0E^*_{1t}}^{[1]}-\overbrace{c_1 | h^*_{1,t}- h^*_{1,t-1}|}^{[2]} )  \frac{1}{(1+\delta)^t}$$
-
-$$NPV_i( h_0^* ) = \sum_{t=0}^\infty (\underbrace{ p h^*_{0,t}-c_0E^*_{0t}}_{[3]}-\underbrace{c_1 | h^*_{0,t}- h^*_{0,t-1}|}_{[4]} )  \frac{1}{(1+\delta)^t}$$
-
-<small>
-
-1. Dockside profits when accounting for adjustment cost 
-2. (Anticipated) Fees paid for adjusting the policy
-3. Theoretical maximum dockside profits 
-4. (Unanticipated) fees for those adjustments
-
-</small>
-
 Consequences of policy adjustment costs 
@@
 
-```{r Figure_5, fig.cap="",  dependson="histogram-calc", dev=c("svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
+```{r Figure_5, fig.cap="",  dependson="histogram-calc", dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
 
@@
 
-Consequences of policy adjustment costs 
----------------------------------------
-
-What is the impact of assuming costs are present when they are not?
-
-- _Very little change to your bottom line_ (regardless of cost structure) <br/><br/>
-
-What is the impact of ignoring costs when they are present?
-
-- _Substantially higher costs_ (particularly for quadratic costs).
-
 ## To say that another way:
 
-```{r Figure_6, fig.cap="", dev=c("svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
+```{r Figure_6, fig.cap="", dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
 
@@
 
-## What about managing when costs are present...
-
-###  ..but you're using the wrong model??
-
 ## Mismatches are even worse:
 
-```{r Figure_7, fig.cap="", dev=c("svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
+```{r Figure_7, fig.cap="", dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
 who <- c("penalty_fn", "ignore_fraction", "mismatched_fraction", "reduction")
@@
 ```
-
-## Mismatched costs are intuitive if we remember the general patterns
-
-- Quadratic ($\Pi_2$) smooths
-- Linear ($\Pi_1$) flattens
-- Fixed ($\Pi_3$) jumps
-
-Predict which is worse: assuming the wrong cost or no assuming no cost at all, when:
-
-- Costs are assumed linear but in reality quadratic?
-- True costs are assumed quadratic but in reality fixed?
-
-## Mismatched costs are intuitive
-
-```{r Figure_7again, fig.cap="", dev=c("svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
-ggplot(table2_long, aes(penalty.fn, value, fill = variable)) + 
-  geom_bar(stat="identity", position="dodge") + 
-  facet_wrap(~reduction, scales="free_y") +
-  scale_x_discrete(labels = c('L1_L2' = substitute(paste(Pi[1],"_", Pi[2])), 
-                              'L2_L1' =  substitute(paste(Pi[2],"_", Pi[1])),
-                              'L1_fixed' = substitute(paste(Pi[1],"_", Pi[3])), 
-                              'fixed_L1' =  substitute(paste(Pi[3],"_", Pi[1])),
-                              'fixed_L2' = substitute(paste(Pi[3],"_", Pi[2])), 
-                              'L2_fixed' =  substitute(paste(Pi[2],"_", Pi[3])))) + 
-  xlab("Penalty function as: assumed_reality") + theme_tufte(base_size=14)
-```
-
-## Conclusions
-
-- Policies reflecting the best ecology may ultimately be impractical
-- Novel look at introducing costs to changes in policy
-- Details matter: some adjustment costs make policy less smooth, some more smooth
-- Solutions can satisfy the constraints of adjustment costs while performing nearly optimally
-- Ignoring adjustment costs can result in significant penalties
-- There are many benefits to joining a NIMBioS working group
-
-## Acknowledgements
-
-<img src="components/images/nsf.jpg" width="100" height="100"><img src="components/images/noaa.jpg" width="100" height="100"><img src="components/images/sloan.jpg" width="100" height="100">  <br/>
-
-<img src="components/images/nimbios.jpg" width="150" height="75"> 
-<img src="components/images/csgf.png" width="150" height="75"> <br/>
-
-<!-- Paid the bills and folks that have supported or otherwise
-tolerated this and so many other side projects -->
-
-<small>Slides, data, references, code and more at: http://io.carlboettiger.info/pdg_control</small>

### 2014-08-11 manuscripts/components/crash-analysis.R

@@ -1,0 +1,306 @@
+
+
+
+ncpu = 24
+
+
+## ----profit_model--------------------------------------------------------
+price = 10
+c0 = 30
+profit <- profit_harvest(price = price, c0 = c0, c1 = 0)
+
+
+## ----c2_grid-------------------------------------------------------------
+c2 <- exp(seq(0, log(41), length.out = 40))-1
+c2 <- seq(0, 40, length.out=100)
+
+
+## ----reduction-----------------------------------------------------------
+reduction <- 0.25 
+
+
+## ----setup---------------------------------------------------------------
+seed <- 123                 # Random seed (replicable results)
+delta <- 0.05               # economic discounting rate
+OptTime <- 20               # stopping time
+gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
+sigma_g <- 0.2              # Noise in population growth
+reward <- 0                 # bonus for satisfying the boundary condition
+z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
+z_m <- function() 1         # No measurement noise, 
+z_i <- function() 1         # No implemenation noise
+f <- RickerAllee                # Select the state equation
+pars <- c(2, 8, 5)        # parameters for the state equation
+K <- 10  # Carrying capacity (for reference 
+xT <- 0                     # boundary conditions
+x0 <- K
+x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
+h_grid <- seq(0.01, 0.8 * K, length = gridsize)  
+
+
+## ----reed, dependson=c("setup", "profit_model")--------------------------
+SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
+opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
+                     profit, delta, reward=reward)
+
+
+## ----fees----------------------------------------------------------------
+L1 <- function(c2) function(h, h_prev)  c2 * abs(h - h_prev) 
+fixed <-  function(c2) function(h, h_prev) c2 * as.numeric( !(h == h_prev) )
+L2 <- function(c2) function(h, h_prev)  c2 * (h - h_prev) ^ 2
+none <- function(h, h_prev)  0
+penaltyfns <- list(L2=L2, L1=L1, fixed=fixed)
+
+
[…]

### 2014-08-11 manuscripts/components/supp_analysis.R

@@ -1,0 +1,307 @@
+
+
+
+ncpu = 24
+
+
+## ----profit_model--------------------------------------------------------
+price = 10
+c0 = 30
+c1 = 1
+profit <- profit_harvest(price = price, c0 = c0, c1 = c1)
+
+
+## ----c2_grid-------------------------------------------------------------
+c2 <- exp(seq(0, log(41), length.out = 40))-1
+c2 <- seq(0, 40, length.out=100)
+
+
+## ----reduction-----------------------------------------------------------
+reduction <- 0.25 
+
+
+## ----setup---------------------------------------------------------------
+seed <- 123                 # Random seed (replicable results)
+delta <- 0.05               # economic discounting rate
+OptTime <- 20               # stopping time
+gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
+sigma_g <- 0.2              # Noise in population growth
+reward <- 0                 # bonus for satisfying the boundary condition
+z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
+z_m <- function() 1         # No measurement noise, 
+z_i <- function() 1         # No implemenation noise
+f <- BevHolt                # Select the state equation
+pars <- c(1.5, 0.05)        # parameters for the state equation
+K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
+xT <- 0                     # boundary conditions
+x0 <- K
+x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
+h_grid <- seq(0.01, 0.8 * K, length = gridsize)  
+
+
+## ----reed, dependson=c("setup", "profit_model")--------------------------
+SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
+opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
+                     profit, delta, reward=reward)
+
+
+## ----fees----------------------------------------------------------------
+L1 <- function(c2) function(h, h_prev)  c2 * abs(h - h_prev) 
+fixed <-  function(c2) function(h, h_prev) c2 * as.numeric( !(h == h_prev) )
+L2 <- function(c2) function(h, h_prev)  c2 * (h - h_prev) ^ 2
+none <- function(h, h_prev)  0
+penaltyfns <- list(L2=L2, L1=L1, fixed=fixed)
+
+
[…]

### 2014-08-21 manuscripts/crashes.Rmd
additional analyses
updated presentation, manuscript references, added quad_costs to appendix, with relevant code

--- 2014-07-31 manuscripts/manuscript.Rmd
@@
 library("knitr")
-basename <- "manuscript"
+basename <- "crashes"
 opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
@@
 ```{r analysis, include=FALSE}
-source("components/analysis.R")
+source("components/crash-analysis.R")
 ```

### 2014-08-21 manuscripts/manuscript.Rmd
updated presentation, manuscript references, added quad_costs to appendix, with relevant code

@@
   - name: Jacob LaRiviere
-    affiliation: UTK
+    affiliation: UTK_Econ
   - name: Alan Hastings
@@
   - name: Paul Armsworth 
-    affiliation: UTK
+    affiliation: UTK_EEB
 
@@
   - code: melbourne
-    address: University of Melbourne, Australia 
-  - code: UTK
-    address: University of Tennessee, Knoxville
+    address: School of Botany, University of Melbourne, Australia 
+  - code: UTK_EEB
+    address: Department of Ecology and Evolutionary Biology, University of Tennessee, Knoxville
+  - code: UTK_Econ
+    address: Department of Economics, University of Tennessee, Knoxville
 
@@
           smaller than the impact of managers assuming such costs are absent if
-          they are present.
+          they are present. Further, we demonstrate that the structural form of
+          these costs matters -- assuming one form when costs are are in fact
+          a different form can be even more costly.
 
@@
 Ecosystems are dynamic and exhibit rich patterns of variability in
-both time and space. In designing management policies for ecosystems,
+both time and space [@Durrett1994]. In designing management policies for ecosystems,
 managers need to decide how much of that variation to respond to. Managers
@@
 
-```{r Figure_1, fig.cap="ICCAT Stock assessments and US Quotas for Bluefin Tuna, 1987 - 2007", fig.width=6, fig.height=4, dev=c("pdf", "svg", "png")}
+```{r Figure_1, fig.cap="ICCAT Stock assessments and Total Allowable Catch (TAC, before adjustments for national underages and overages) for Bluefin Tuna, 1987 - 2007", fig.width=6, fig.height=4, dev=c("pdf", "svg", "png")}
 tuna <- read.csv("components/data/tuna.csv")
-tuna<-melt(tuna, id="year")
+tuna <- melt(tuna, id="year")
 ggplot(tuna, aes(year, value)) + geom_point() +
@@
 
-To illustrate these concepts, Figure 1 show an example from fisheries
-management. On the left axis, the figure shows a time series for the
+To illustrate these concepts, we use an example from fisheries
+management. Fig1a shows a time series for the
 estimated population size, represented as spawning stock biomass, of
 west Atlantic bluefin tuna (_Thunnus thynnus_, henceforth bluefin) from
-a recent stock assessment [@ICCAT20XX].  On the right axis the figure
-also shows the catch quota for the stock that was set by the relevant
+a recent stock assessment [@ICCAT20XX].  Fig1b 
+shows the catch quota (Total Allowable Catch or TAC, before being adjusted
+for overages or underages in the catch of each country in the previous year)
+ for the stock as set by the relevant
 management agency [@ICCAT20XX]. Despite the estimated population size
@@
 
-With his formulation, Reed showed that a constant escapement policy could be
+With his formulation, @Reed1979 showed that a constant escapement policy could be
 optimal under certain conditions. Such a policy involves choosing annual
@@
 \begin{equation}
-\max_{{\bf h}}\mathbf{ E} ( NPV_{0} )=\max_{{\bf h}} \sum_0^\infty \mathbf{E} \left( \displaystyle \frac{\Pi_0(N_t,h_t)}{(1+\delta)^{t+1}} \right) \label{eq:objective}
+\max_{{\bf h}}\mathbf{ E} ( NPV_{0} )=\max_{{\bf h}} \sum_0^{T_{\mathrm{max}}} \mathbf{E} \left( \displaystyle \frac{\Pi_0(N_t,h_t)}{(1+\delta)^{t+1}} \right) \label{eq:objective}
 \end{equation}
@@
 discount rate and $\Pi_0$ is the net revenue from operating the fishery
-in a given year. In this base case, we assume the annual net revenue
+in a given year. In this base case, we assume the annual dockside (that is, before accounting for any adjustment costs that may be incurred) net revenue
 from fishing is
@@
 we assume that these are constants with $p>0$ and $c_0>0$. (Examples
-shown here use $p$= `r price` and $c_0$ = `r c0`, complete code is
-provided in the supplementary materials to re-run these analyses with
-arbitrarily specified values and replot the figures shown).
+shown here use $p$= `r price` and $c_0$ = `r c0`.  Sensitivity analysis appears
+in the supplement, along with complete R code to replicate and further 
+vary the setup).
 
@@
 
-_Economic penalties promised for the supplement are still to come_
-
-```{r Figure_S1, dependson="tidy", fig.cap="Multiple realizations of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=10, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png")}
+## Economic penalties using quadratic costs
+
+```{r quadraticcosts}
+source("components/quad_costs.R")
+```
+
+Calibrated in the same way.
+
+```{r Figure_S1}
+ex <- dt_quad %>% 
+  filter(replicate=="rep_17" & time < 20) %>%
+  select(time, harvest, harvest_alt) %>%
+  gather(variable, stock, -time) 
+ggplot(ex) + 
+  geom_line(aes(time, stock, col=variable), lwd=1) + 
+  scale_color_discrete(labels=c(harvest = substitute(paste("Harvest Policy under ", paste(Pi[4]))), 
+                                harvest_alt = substitute(paste("Harvest under ", paste(Pi[0]), " (Reed)"))), 
+                       name="")
+
+```
+
+```{r}
+shifts <- dt[, fraction_no_shift(harvest), by=c("replicate")]
+ave <- shifts[, mean(V1)]
+```
+
+Like the $\Pi_2$ adjustment cost based penalty, this quadratic cost based penalty shows periods of contant, strictly positive policy only `r ave * 100`% of the time, and exhibits the same kind of smoothing of more small adjustments that is seen in $\Pi_2$ scenario.
+
+```{r Figure_S2, dependson="tidy", fig.cap="Multiple realizations of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=10, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png")}
 
@@
 
-```{r Figure_S2, dependson="tidy", fig.cap="Example realization of resulting fish stock sizes under the different functional forms of adjustment costs, corresponding to policies shown in Figure 3.
+```{r Figure_S3, dependson="tidy", fig.cap="Example realization of resulting fish stock sizes under the different functional forms of adjustment costs, corresponding to policies shown in Figure 3.
 Because stock sizes are measured before harvests, the effect of the penalty on the stock size is not as pronounced.", fig.height=3, fig.width=8, cache = fig.cache, dev=c("pdf", "svg", "png")}

### 2014-08-21 manuscripts/presentation.Rmd
updated presentation, manuscript references, added quad_costs to appendix, with relevant code

@@
 ---
-
-## Our world is changing
-
-<img src="components/images/global-change.jpg" width="500">
-
-<small> Overpeck+ (2011) doi: [10.1126/science.1197869](http://doi.org/10.1126/science.1197869) </small>
-
-## Our policies are not
-
-<img src="components/images/nochange.jpg" width="700">
-
-<small> Alex Wong (Getty Images) </small>
 
@@
 
+## Progress in modeling ecological complexity:
+
+- Importance of space
+- temporal heterogeneity 
+- individual heterogeneity
+- ecosystem models
+
 ----
+
+<blockquote class="twitter-tweet" lang="en"><p>No public policy issue is ultimately about science; it’s about stakeholders, values, economics, ideology.
+Goldston <a href="https://twitter.com/hashtag/ESA2014?src=hash">#ESA2014</a></p>&mdash; Liza Gross (@lizabio) <a href="https://twitter.com/lizabio/statuses/498971982998687744">August 11, 2014</a></blockquote>
+<script async src="widgets.js" charset="utf-8"></script>
+
+## Hmm...
+
+## Can we put that in our models too?
 
@@
   filter(replicate=="rep_17" & penalty_fn == "L1" & time < 20) %>%
-  select(time, fishstock, harvest_alt) %>%
+  select(time, fishstock, harvest, alternate, harvest_alt) %>%
   gather(variable, stock, -time) 
@@
   geom_line(aes(time, stock, col=variable), lwd=1) + 
-  scale_color_discrete(labels=c(fishstock = "Stock size", harvest_alt = "Harvest policy"), name="")
+  scale_color_discrete(labels=c(fishstock = "Stock Size", harvest = "Harvest", alternate = "Stock size (Adj)", harvest_alt = "Harvest policy (Adj)"), name="")
 

### 2014-08-21 manuscripts/components/quad_costs.R

@@ -1,0 +1,95 @@
+library("pdgControl")
+library("tidyr")
+library("dplyr")
+library("ggplot2")
+library("reshape2")
+library("data.table")
+library("snowfall")
+
+## ----profit_model--------------------------------------------------------
+price = 10
+c0 = 30
+profit <- profit_harvest(price = price, c0 = c0, c1 = 0)
+profit_quad <- function(c2) profit_harvest(price = price, c0 = c0, c1 = c2)
+
+
+## ----c2_grid-------------------------------------------------------------
+c2 <- exp(seq(0, log(41), length.out = 40))-1
+c2 <- seq(0, 40, length.out=100)
+ncpu <- 4
+reduction <- 0.25 
+
+## ----setup---------------------------------------------------------------
+seed <- 123                 # Random seed (replicable results)
+delta <- 0.05               # economic discounting rate
+OptTime <- 20               # stopping time
+gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
+sigma_g <- 0.2              # Noise in population growth
+reward <- 0                 # bonus for satisfying the boundary condition
+z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
+z_m <- function() 1         # No measurement noise, 
+z_i <- function() 1         # No implemenation noise
+f <- BevHolt                # Select the state equation
+pars <- c(1.5, 0.05)        # parameters for the state equation
+K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
+xT <- 0                     # boundary conditions
+x0 <- K
+x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
+h_grid <- seq(0.01, 0.8 * K, length = gridsize)  
+
+
+## ----reed, dependson=c("setup", "profit_model")--------------------------
+SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
+opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
+                     profit, delta, reward=reward)
+
+
+## ----fees----------------------------------------------------------------
+none <- function(h, h_prev)  0
+i <- which(x_grid > K)[1]
+
+sfInit(parallel=TRUE, cpus = ncpu)
+sfLibrary(pdgControl)
+sfExportAll()
+policies <- sfLapply(c2, function(c2){
[…]

### 2014-08-21 manuscripts/crashes-explore.Rmd
clean up

```{r, fig.cap="",  dev=c("svg", "png"), cache=FALSE, dev.args=list(bg="transparent"), fig.height=3}
ex <- dt %>% 
  filter(replicate=="rep_17" & penalty_fn == "L1" & time < 20) %>%
  select(time, fishstock, harvest_alt) %>%
  gather(variable, stock, -time) 
ggplot(ex) + 
  geom_line(aes(time, stock, col=variable), lwd=1) + 
  scale_color_discrete(labels=c(fishstock = "Stock size", harvest_alt = "Harvest policy"), name="")

```
```{r}
ex <- dt %>% 
  filter(replicate == "rep_1" & penalty_fn == "L1" & time < 20) %>%
  select(time, fishstock, harvest_alt) %>%
  gather(variable, stock, -time) 
ggplot(ex) + 
  geom_line(aes(time, stock, col=variable), lwd=1) + 
  scale_color_discrete(labels=c(fishstock = "Stock Size", harvest = "Harvest", alternate = "Stock size (Adj)", harvest_alt = "Harvest policy (Adj)"), name="") 
```

```{r}
ex <- dt %>% 
  filter(replicate %in% paste0("rep_", 1:10) & penalty_fn == "L1" & time < 20) %>%
  select(time, fishstock, harvest_alt) %>%
  gather(variable, stock, -time, -replicate) 
ggplot(ex) + 
  geom_line(aes(time, stock, col=variable), lwd=1) + 
  scale_color_discrete(labels=c(fishstock = "Stock Size", harvest = "Harvest", alternate = "Stock size (Adj)", harvest_alt = "Harvest policy (Adj)"), name="") +  
  facet_wrap(~replicate) 
```

### 2014-08-21 manuscripts/manuscript.Rmd
clean up

@@
   - name: Jacob LaRiviere
-    affiliation: UTK_Econ
+    affiliation: UTKEcon
   - name: Alan Hastings
@@
   - name: Paul Armsworth 
-    affiliation: UTK_EEB
+    affiliation: UTKEEB
 
@@
     address: School of Botany, University of Melbourne, Australia 
-  - code: UTK_EEB
+  - code: UTKEEB
     address: Department of Ecology and Evolutionary Biology, University of Tennessee, Knoxville
-  - code: UTK_Econ
+  - code: UTKEcon
     address: Department of Economics, University of Tennessee, Knoxville
@@
           they are present. Further, we demonstrate that the structural form of
-          these costs matters -- assuming one form when costs are are in fact
+          these costs matters: assuming one form when costs are are in fact
           a different form can be even more costly.
@@
     fig_caption: true
+    keep_tex: true
 ---
@@
 
-theme_set(theme_tufte())
+theme_set(theme_tufte() + theme(axis.line = element_line())
 ```
@@
   ylab("Reduction in net present value") + 
-  scale_linetype_discrete(labels=relabel) + 
-  scale_color_discrete(labels=relabel)
+  scale_linetype_discrete(labels=relabel, breaks = c('L1', 'L2', 'fixed')) + 
+  scale_color_discrete(labels=relabel, breaks = c('L1', 'L2', 'fixed'))
 
@@
 ```{r quadraticcosts}
+
 source("components/quad_costs.R")
@@
 
-```{r Figure_S1}
+```{r Figure_S1, dev=c('pdf', 'svg')}
 ex <- dt_quad %>% 
@@
 
-```{r}
+```{r quadshiftrate}
 shifts <- dt[, fraction_no_shift(harvest), by=c("replicate")]

### 2014-08-21 manuscripts/components/analysis.R

@@ -1,6 +1,3 @@
-
-
-
 ncpu = 24
 
 

### 2014-08-21 manuscripts/components/install.R

@@ -1,15 +1,0 @@
-#!/usr/bin/Rscript
-library("methods")
-# Let packrat set up the manuscript dependencies
-if(file.exists("packrat.sources") && file.exists(".Rprofile") && file.exists(".Renviron")){
-  if(exists("initPackrat"))
-    initPackrat()
-  else 
-    NULL
-} else {
-# Install packrat if not available
-  if(!require("devtools")) install.packages("devtools")
-  if(!require("packrat")) devtools::install_github("rstudio/packrat")
-  packrat::packify()
-  packrat::restore()
-}

### 2014-08-21 manuscripts/components/knit.R

@@ -1,32 +1,0 @@
-#!/usr/bin/Rscript
-args <- commandArgs(TRUE)
-
-if(!is.na(args[1])){
-  infile <- args[1]
-} else {
-  infile <- 'manuscript.Rmd'
-}
-
-
-## FIXME add second argument to handle figure types
-
-## Set the paths for cache and figure
-library("methods")
-library("knitr")
-basename <- gsub(".Rmd", "", infile) # knitr:::knit_concord$get('infile')) 
-opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
-               cache.path = paste("components/cache/", basename, "/", sep=""))
-opts_chunk$set(cache = 2)
-opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, comment = NA, verbose = TRUE, echo=FALSE)
-
-# PDF-based figures
-opts_chunk$set(dev='pdf')
-
-# Better to use a temporary markdown file (best to not overwrite basename.md since that can be used to display on GitHub)
-# For now use basename, since pandoc function in knitr 1.5 doesn't respect output name from config (fixed in knitr 1.5.32)
-output <- paste(basename, ".md", sep="")
-
-## Knit
-knit(infile, output)
-
-

### 2014-08-21 manuscripts/components/quad_costs.R

@@ -57,8 +57,7 @@ policies <- sfLapply(c2, function(c2){
 })
 
 
-fees <- sapply(policies, function(policy) max(policy$V[i,]))
-
+fee <- sapply(policies, function(policy) max(policy$V[i,]))
 npv0 <- fee[1]
 normalized_fee <- (npv0-fee)/npv0
 

### 2014-08-21 manuscripts/manuscript.Rmd
update theme and libraries, rebuild cache

@@
 library("snowfall")
-
+library("dplyr")
+library("tidyr")
 options(digits=2)
 
-theme_set(theme_tufte() + theme(axis.line = element_line())
+theme_set(theme_tufte() + theme(axis.line = element_line()))
 ```

### 2014-08-21 manuscripts/manuscript.Rmd
edits from paul

--- 2014-08-21 manuscripts/manuscript.Rmd
@@
 library("snowfall")
+library("tidyr")
+library("dplyr")
 
@@
 $c_0$ the cost of fishing and, to simplify the presentation of results,
-we assume that these are constants with $p>0$ and $c_0>0$. (Examples
-shown here use $p$= `r price` and $c_0$ = `r c0`.  Sensitivity analysis appears
+we assume that these are constants with $p>0$ and $c_0>0$.
+
+To simplify presentation of the results, we will illustrate cases where the
+growth parameters are chosen so that the intrinsic rate of increase of
+the fish population is 1 and the equilibrium biomass for the equivalent
+deterministic model without harvesting is 10; (specifically, $A=$ `r pars[1]` and
+$B=$ `r pars[2]` in Eqn \eqref{eq:state_equation}. To characterize environmental variability, we
+assume multiplicative shock $Z_t$ is distributed log-normally with 
+log standard deviation $\sigma_g$ = `r sigma_g`. In addition, we
+show cases where $p=$ `r price`, $\delta=$ `r delta` and $c_0=$ `r c0`.
+
+Sensitivity analysis appears
 in the supplement, along with complete R code to replicate and further 
@@
 NPV available in the basic problem $NPV_0({\bf h_0^*})$ without policy
-adjustment costs.
+adjustment costs. The $c_i$ values are given in Table 1.
+
+```{r table_1, results="asis"}
+pandoc.table(print_npv)
+```
 
@@
 for each penalty function, such that the fishery is worth `r 100*(1-reduction)`% of its
-unconstrained value when optimally managed.
-
-We focus our examination of the models on how the type and severity of
-policy adjustment costs affects the optimal management strategy. To
-simplify presentation of the results, we will illustrate cases where the
-growth parameters are chosen so that the intrinsic rate of increase of
-the fish population is 1 and the equilibrium biomass for the equivalent
-deterministic model without harvesting is 10; (specifically, $A=$ `r pars[1]` and
-$B=$ `r pars[2]` in Eqn \eqref{eq:state_equation}. To characterize environmental variability, we
-assume multiplicative shock $Z_t$ is distributed log-normally with 
-log standard deviation $\sigma_g$ = `r sigma_g`. In addition, we
-show cases where $p=$ `r price`, $\delta=$ `r delta` and $c_0=$ `r c0`.
+unconstrained value when optimally managed. We focus our examination of the models on how the type and severity of policy adjustment costs affects the optimal management strategy.
 
@@
 Figure 3 illustrates how the different forms of adjustment cost can impact
-the optimal harvest policy. Corresponding stock sizes, which are measured
-here before harvest ($h_t$ being determined after observing stock size
-$x_t$) and thus show less influence of the policy cost can be seen in the
+the optimal harvest policy. Corresponding stock sizes can be seen in the
 supplement.  Each panel is generated against the same sequence of random
@@
 ```{r Figure_S1, dev=c('pdf', 'svg')}
+
+labels <- c(harvest = substitute(paste("Harvest Policy under ", paste(Pi[4]))), 
+                                harvest_alt = substitute(paste("Harvest under ", paste(Pi[0]), " (Reed)")))
+
 ex <- dt_quad %>% 
@@
   geom_line(aes(time, stock, col=variable), lwd=1) + 
-  scale_color_discrete(labels=c(harvest = substitute(paste("Harvest Policy under ", paste(Pi[4]))), 
-                                harvest_alt = substitute(paste("Harvest under ", paste(Pi[0]), " (Reed)"))), 
+  scale_color_discrete(labels=labels, 
                        name="")
@@
 
+Recall that in our model definition, stock sizes are measured before harvest ($h_t$ being determined after observing stock size
+$x_t$) and thus show less influence of the policy cost than the harvest itself.
+
 ```{r Figure_S2, dependson="tidy", fig.cap="Multiple realizations of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=10, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png")}
 
-fig1s_df <- as.data.frame(subset(dt, replicate %in% paste0('rep_', 11:20)))
-fig1s_df <- fig1s_df[c("time", "fishstock", "alternate", "harvest", "harvest_alt", "penalty_fn", "replicate")]
-fig1s_df <- melt(fig1s_df, id = c("time", "penalty_fn", "replicate"))
-fig1s_df <- data.frame(fig1s_df, baseline = fig1s_df$variable)
-variable_map <- c(fishstock = "fish_stock", alternate = "fish_stock", harvest = "harvest", harvest_alt = "harvest")
-baseline_map <- c(fishstock = "penalty", alternate = "no_penalty", harvest = "penalty", harvest_alt = "no_penalty")
-fig1s_df$variable <- variable_map[fig1s_df$variable]
-fig1s_df$baseline <- baseline_map[fig1s_df$baseline]
-
-fig1s_df <- subset(fig1s_df, variable=="harvest")
-labeller <- function(variable,value){
-if (variable=='penalty_fn') {
-    return(relabel[value])
-  } else {
-    return(value)
-  }
-}
-
-ggplot(fig1s_df, aes(time, value, col=baseline)) +
-  geom_line(lwd=1) +
-  facet_grid(replicate ~ penalty_fn, labeller=labeller) + 
-  labs(x="time", y="stock size", title = "Example Stock & Harvest Dynamics")  
-write.csv(fig1s_df, "components/data/figure_s1.csv")
-
-```
-
-```{r Figure_S3, dependson="tidy", fig.cap="Example realization of resulting fish stock sizes under the different functional forms of adjustment costs, corresponding to policies shown in Figure 3.
-Because stock sizes are measured before harvests, the effect of the penalty on the stock size is not as pronounced.", fig.height=3, fig.width=8, cache = fig.cache, dev=c("pdf", "svg", "png")}
-
-labeller <- function(variable,value){
-    return(relabel[paste(value)])
-}
-
-ggplot(fishstock_fig3, aes(time, value, col=baseline)) +
-  geom_line(lwd=1) +
-  facet_grid(penalty_fn~., labeller = labeller) + 
-  labs(x="time", y="stock size", title = "Example Stock & Harvest Dynamics")
-
-write.csv(fishstock_fig3, "components/data/figure_s2.csv")
-```
-
-<!-- Ingoring this, not useful-->
-```{r Table1, results="asis", eval=FALSE}
-caption = "Table 1: Column 'ignoring' shows the results of ignoring a adjustment penalty when it is present, Column 'assuming' shows the results of assuming an adjustment cost when it is absent.
-Values (ignoring, assuming) are given as the expected net present value (ENPV) as a fraction of that when no penalty is present, ENPV0.
-Percent reduction refers to penalty coefficient being calibrated to achieve the given percent reduction relative to ENPV0 when the penalty is optimally accounted for.
-Comparing the second and third columns shows that ignoring a real cost is a significantly graver error, particularly in the case of quadratic costs."
-pandoc.table(table1, caption=caption)
-```
-
-```{r Figure_5_alt, fig.cap="**Alternate Figure 5**.
-Distribution of profits from fishing and costs paid to adjustment.
-Distributions are shown when managing a system in which the adjustment costs present are determined by the model indicated, and compared to the same costs and profits of managing the same system using a Reed model, which ignores adjustment costs, and thus tends to pay much higher fees for adjustment.
-In contrast, the difference in profit after accounting for costs is only marginally less than the value derived by managing the population to optimize profits when ignoring adjustment costs (Reed model).", fig.width=3, fig.height=5, dependson="histogram-calc", dev=c("pdf", "svg", "png")}
-
-hist_dat_alt <- melt(cbind(profits, costs = costs$V1, 
-                       reed_profits = reed_profits$profits, reed_costs = reed_costs$V1),
-                 id = c("penalty_fn", "replicate"))
-
-ggplot(hist_dat_alt) + 
-  geom_density(aes(value, fill=variable, color=variable), alpha=0.8)+
-  facet_grid(penalty_fn~., labeller = labeller)
-
+labels <- c(harvest = substitute(paste("Harvest Policy under ", paste(Pi[1-3]))), 
+            harvest_alt = substitute(paste("Harvest under ", paste(Pi[0]), " (Reed)")))
+            fishstock = substitute(paste("Stock dynamics under under ", paste(Pi[1-3]))), 
+            alternate = substitute(paste("Harvest under ", paste(Pi[0]), " (Reed)")
+ex <- dt %>% 
+  filter(replicate %in% paste0("rep_", 10:20) & penalty_fn == "L1" & time < 20) %>%
+  select(time, fishstock, harvest, alternate, harvest_alt) %>%
+  gather(variable, stock, -time, -replicate)
+
+ggplot(ex) + 
+  geom_line(aes(time, stock, col=variable), lwd=1) + 
+  scale_color_discrete(labels=labels, name="") +  
+  facet_wrap(~replicate)
+
+write.csv(ex, "components/data/figure_s2.csv")
 ```

### 2014-08-21 manuscripts/manuscript.Rmd

@@
 library("dplyr")
-
 options(digits=2)
 
-theme_set(theme_tufte() + theme(axis.line = element_line())
+theme_set(theme_tufte() + theme(axis.line = element_line()))
 ```

### 2014-08-25 manuscripts/manuscript.Rmd
updated runs

@@
 
-theme_set(theme_tufte() + theme(axis.line = element_line()))
+theme_set(theme_tufte(base_size=12) + theme(axis.line = element_line()))
 ```
@@
 
-fig3_df <- as.data.frame(subset(dt, replicate=='rep_17'))
-fig3_df <- fig3_df[c("time", "fishstock", "alternate", "harvest", "harvest_alt", "penalty_fn")]
-fig3_df <- melt(fig3_df, id = c("time", "penalty_fn"))
-fig3_df <- data.frame(fig3_df, baseline = fig3_df$variable)
-variable_map <- c(fishstock = "fish_stock", alternate = "fish_stock", harvest = "harvest", harvest_alt = "harvest")
-baseline_map <- c(fishstock = "penalty", alternate = "no_penalty", harvest = "penalty", harvest_alt = "no_penalty")
-fig3_df$variable <- variable_map[fig3_df$variable]
-fig3_df$baseline <- baseline_map[fig3_df$baseline]
-
-harvest_fig3 <- subset(fig3_df, variable=="harvest")
-fishstock_fig3 <- subset(fig3_df, variable=="fish_stock")
-
 labeller <- function(variable,value){
@@
 
-ggplot(harvest_fig3, aes(time, value, col=baseline)) +
+dt3 <- dt %>% 
+  filter(replicate=="rep_17" & time < 20) %>%
+  select(time, harvest, harvest_alt, penalty_fn) %>%
+  gather(variable, value, -time, -penalty_fn)
+
+ggplot(dt3, aes(time, value, col=variable, lty=variable)) +
   geom_line(lwd=1) +
@@
   labs(x="time", y="stock size", title = "Example Harvest Dynamics")  +
-  scale_color_discrete(labels=c("Reed solution", "With penalty"), name="")
-
-write.csv(harvest_fig3, "components/data/figure3.csv")
+  scale_color_discrete(labels=c("With Penalty", "Reed Solution"), name="") +
+  scale_linetype_discrete(labels=c("With Penalty", "Reed Solution"), name="")
+
+write.csv(dt3, "components/data/figure3.csv")
 ```
@@
 the optimal harvest policy. Corresponding stock sizes can be seen in the
-supplement.  Each panel is generated against the same sequence of random
-shocks so that they can be compared directly.  The harvest policy chosen
+supplement.  Each panel is generated against the same sequence of 
+environmental variability so that they can be compared directly.  The harvest policy chosen
 shows a systematic deviations from the penalty free optimum, depending on
 the nature of the cost.  In each case, the optimal solution without any
-adjustment cost is shown in against the policy induced by optimization
+adjustment cost is shown with the policy induced by optimization
 under the given adjustment penalty (equivalent to a `r 100*reduction`%
-reduction in maximum expected NPV) is overlaid in blue.
-
-<!-- NOTE FIXME make this consistent! -->
+reduction in maximum expected NPV) overlaid in blue.
 
@@
 
-<!-- to include cross.correlation, drop subset call and facet_wrap by variable. But shows no pattern-->
-
 ```{r Figure_4, fig.cap="Variance and autocorrelation of stock dynamics and harvest dynamics, as a function of the penalty coefficient.
@@
 
-```{r Figure_5, fig.cap="Distribution of profits from fishing and costs paid to adjustment.
-Distributions are shown when managing a system in which the adjustment costs present are determined by the model indicated, and compared to the same costs and profits of managing the same system using a Reed model, which ignores adjustment costs, and thus tends to pay much higher fees for adjustment.
-In contrast, the difference in profit after accounting for costs is only marginally less than the value derived by managing the population to optimize profits when ignoring adjustment costs (Reed model).", fig.width=8, fig.height=6, dependson="histogram-calc", dev=c("pdf", "svg", "png")}
-
-assume <- levels(as.factor(hist_dat$Assumption))
-labeller <- function(variable,value){
-if (variable=='penalty_fn') {
-    return(relabel[paste(value)])
-  } else {
-    return(assume[paste(value)])
-  }
-}
-
-ggplot(hist_dat) + 
-  geom_density(aes(value, fill=variable, color=variable), alpha=0.8)+
-  facet_grid(Assumption~penalty_fn, labeller = labeller)
+```{r}
+fig5_caption <- paste("Distribution of profits from fishing and costs paid to adjustment, under linear costs (Pi[1]).
+(Alternate penalties can be found in the supplementary materials)  Distributions are shown when managing a system in which the adjustment costs present compared to the same costs and profits of managing the system using a Reed model, which ignores adjustment costs, and thus tends to pay higher fees for adjustment.
+In contrast, the difference in profit after accounting for costs is only marginally less than the value derived by managing the population to optimize profits when ignoring adjustment costs (Reed model).")
+```
+
+```{r Figure_5, fig.cap=fig5_caption, fig.width=8, fig.height=6, dependson="histogram-calc", dev=c("pdf", "svg", "png")}
+
+fig5_dat <- hist_dat %>% 
+  filter(penalty_fn=="L1") %>%
+  select(-penalty_fn) %>%
+  unite(dist, Assumption, variable, sep = " : ")
+
+ggplot(fig5_dat) + 
+  geom_density(aes(value, fill=dist, color=dist), alpha=0.8)
 
@@
 table1_long <- subset(table1_long, reduction != "0.3")
-ggplot(table1_long, aes(penalty.fn, value, fill = variable)) + 
+
+ggplot(filter(table1_long, reduction == 0.25),
+  aes(penalty.fn, value, fill = variable)) + 
   geom_bar(stat="identity", position="dodge") + 
@@
 costs as indicated by second code), rather than assuming the policy indicated by the first code in the pair.
-All values are scaled to a fraction of the adjustment free net present value.
-Successive panels show increasing reduction of the net present value by increasing penalty coefficients: e.g.
-a policy in the first panel would lose only 10% (panel A) of its net present value to adjustment costs if it had the correct form of those costs, as determined by the choice of penalty coefficient.", dev=c("pdf", "svg", "png"), fig.width=7}
+All values are scaled to a fraction of the adjustment free net present value.", dev=c("pdf", "svg", "png"), fig.width=7}
 who <- c("penalty_fn", "ignore_fraction", "mismatched_fraction", "reduction")
@@
 
-ggplot(table2_long, aes(penalty.fn, value, fill = variable)) + 
+ggplot(filter(table2_long, reduction==0.25), 
+  aes(penalty.fn, value, fill = variable)) + 
   geom_bar(stat="identity", position="dodge") + 
@@
 labels <- c(harvest = substitute(paste("Harvest Policy under ", paste(Pi[1-3]))), 
-            harvest_alt = substitute(paste("Harvest under ", paste(Pi[0]), " (Reed)")))
+            harvest_alt = substitute(paste("Harvest under ", paste(Pi[0]), " (Reed)")),
             fishstock = substitute(paste("Stock dynamics under under ", paste(Pi[1-3]))), 
-            alternate = substitute(paste("Harvest under ", paste(Pi[0]), " (Reed)")
+            alternate = substitute(paste("Stock under ", paste(Pi[0]), " (Reed)")))
+labeller <- function(variable,value){
+if (variable=='penalty_fn') {
+    return(relabel[paste(value)])
+  } else {
+    return(value)
+  }
+}
+
 ex <- dt %>% 
-  filter(replicate %in% paste0("rep_", 10:20) & penalty_fn == "L1" & time < 20) %>%
-  select(time, fishstock, harvest, alternate, harvest_alt) %>%
-  gather(variable, stock, -time, -replicate)
+  filter(replicate %in% paste0("rep_", 16:20) & time < 20) %>%
+  select(time, fishstock, harvest, alternate, harvest_alt, replicate, penalty_fn) %>%
+  gather(variable, stock, -time, -replicate, -penalty_fn)
 
@@
   scale_color_discrete(labels=labels, name="") +  
-  facet_wrap(~replicate)
+  facet_grid(replicate ~ penalty_fn, labeller=labeller)
 
@@
 
+```{r Figure_S3, fig.cap="Distribution of profits from fishing and costs paid to adjustment.
+Distributions are shown when managing a system in which the adjustment costs present are determined by the model indicated, and compared to the same costs and profits of managing the same system using a Reed model, which ignores adjustment costs, and thus tends to pay much higher fees for adjustment.
+In contrast, the difference in profit after accounting for costs is only marginally less than the value derived by managing the population to optimize profits when ignoring adjustment costs (Reed model).", fig.width=8, fig.height=6, dependson="histogram-calc", dev=c("pdf", "svg", "png")}
+
+assume <- levels(as.factor(hist_dat$Assumption))
+labeller <- function(variable,value){
+if (variable=='penalty_fn') {
+    return(relabel[paste(value)])
+  } else {
+    return(assume[paste(value)])
+  }
+}
+
+ggplot(hist_dat) + 
+  geom_density(aes(value, fill=variable, color=variable), alpha=0.8)+
+  facet_grid(Assumption~penalty_fn, labeller = labeller)
+
+write.csv(hist_dat, "components/data/figure5.csv")
+```
+
+```{r Figure_S4, fig.cap="Relative cost of ignoring adjustment costs when they are present ('ignoring', red) vs assuming the adjustment costs when they are absent ('assuming', blue), shown by penalty function over increasing magnitudes of cost.
+All values are relative to the cost-free adjustment optimum, NPV0.
+In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present.
+The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs.", dev=c("pdf", "svg", "png"), fig.width=7}
+
+ggplot(table1_long, aes(penalty.fn, value, fill = variable)) + 
+  geom_bar(stat="identity", position="dodge") + 
+  facet_wrap(~reduction, ncol=2) + 
+  scale_x_discrete(labels = c('L1' = substitute(paste(Pi[1])),
+                              'L2' = substitute(paste(Pi[2])),
+                              'fixed' = substitute(paste(Pi[3])))) + 
+  xlab("Penalty function")
+write.csv(table1_long, "components/data/figure6.csv")
+```
+
+```{r Figure_S5, fig.cap="Effect of varying severity of adjustment costs on mismatches.
+Successive panels show increasing reduction of the net present value by increasing penalty coefficients: e.g.
+a policy in the first panel would lose only 10% (panel A) of its net present value to adjustment costs if it had the correct form of those costs, as determined by the choice of penalty coefficient.
+Plots structured as in figure 7, which corresponds to the fourth panel", dev=c("pdf", "svg", "png"), fig.width=7}
+ggplot(table2_long, aes(penalty.fn, value, fill = variable)) + 
+  geom_bar(stat="identity", position="dodge") + 
+  facet_wrap(~reduction, scales="free_y") +
+  scale_x_discrete(labels = c('L1_L2' = substitute(paste(Pi[1],"_", Pi[2])), 
+                              'L2_L1' =  substitute(paste(Pi[2],"_", Pi[1])),
+                              'L1_fixed' = substitute(paste(Pi[1],"_", Pi[3])), 
+                              'fixed_L1' =  substitute(paste(Pi[3],"_", Pi[1])),
+                              'fixed_L2' = substitute(paste(Pi[3],"_", Pi[2])), 
+                              'L2_fixed' =  substitute(paste(Pi[2],"_", Pi[3])))) + 
+  xlab("Penalty function")
+write.csv(table2_long, "components/data/figure7.csv")
+```
+
 # References

### 2014-08-25 manuscripts/components/analysis.R

@@ -1,4 +1,4 @@
-ncpu = 24
+ncpu = 4
 
 
 ## ----profit_model--------------------------------------------------------
@@ -35,7 +35,7 @@ x_grid <- seq(0.01, 1.2 * K, length = gridsize)
 h_grid <- seq(0.01, 0.8 * K, length = gridsize)  
 
 
-## ----reed, dependson=c("setup", "profit_model")--------------------------
+## ----reed--------------------------
 SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
 opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                      profit, delta, reward=reward)
@@ -50,12 +50,12 @@ penaltyfns <- list(L2=L2, L1=L1, fixed=fixed)
 
 
 ## ----parallel, include=FALSE---------------------------------------------
-sfInit(cpu=ncpu, parallel=T)
+sfInit(cpu=ncpu, parallel=TRUE)
 sfLibrary(pdgControl)
 sfExportAll()
 
 
-## ----bigloop, dependson=c("setup", "reed", "fees", "profit_model", "c2_grid")----
+## ----bigloop----
 policies <- lapply(penaltyfns, function(penalty){
   sfLapply(c2, function(c2){
     policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
@@ -65,7 +65,7 @@ policies <- lapply(penaltyfns, function(penalty){
 })
 
 
-## ----, dependson="quadcosts"---------------------------------------------
+## -------------------------------------------------
 i <- which(x_grid > K)[1]
 fees <- 
   lapply(policies, function(penalty) 
@@ -75,7 +75,7 @@ fees <-
   )
 
 
-## ----npv-plot, dependson="quadcosts"-------------------------------------
+## ----npv-plot-------------------------------------
 npv0 <- max(fees$L1) # all have same max, at c2=0 
 fees <- data.frame(c2=c2,fees)
 fees <- melt(fees, id="c2")
@@ -84,7 +84,7 @@ fees <- subset(fees, variable %in% c("L1", "L2", "fixed"))
 #ggplot(fees, aes(c2, value, col=variable)) + geom_point() + geom_line()
 
 
-## ----apples, dependson=c("quadcosts", "reduction")-----------------------
+## ----apples-----------------------
 closest <- function(x, v){
   which.min(abs(v-x))
 }
[…]

### 2014-10-18 manuscripts/manuscript.Rmd
add snowy grouper data;

@@
 tuna <- read.csv("components/data/tuna.csv")
-tuna <- melt(tuna, id="year")
-ggplot(tuna, aes(year, value)) + geom_point() +
-  facet_wrap(~variable, ncol=1, scale="free_y") + 
-  ylab("Bluefin Tuna harvest (tonnes)") + theme_bw()
+grouper <- read.csv("components/data/grouper.csv")
+
+ex <- rbind(cbind(tuna, species="tuna"), cbind(grouper, species="snowy grouper"))
+ex_long <- gather(ex, variable, value, year, species)
+
+ggplot(ex_long, aes(year,value)) + 
+  geom_line() + geom_point() + 
+  facet_wrap(variable~species, scales="free") + 
+  ylab("value (mt)") + theme_bw()
 ```

### 2014-11-27 manuscripts/manuscript.Rmd
tweak abstract. set workdir in Dockerfile appropriately

@@
           varying population using annually varying quotas in order to maximize
-          profit  - to examine how costs of policy adjustment change optimal
+          profit  -- to examine how costs of policy adjustment change optimal
           management recommendations. Costs of policy adjustment (here changes in
@@
           how different forms of policy costs have contrasting implications for
-          optimal policies. While some types of cost act to smooth out variation in
-          quotas and stock sizes, as one might have expected, others can actually
-          increase variation in stock sizes and quotas through time. We also show
-          that the potential economic impact on the fishery of managers assuming
-          policy adjustment costs are present when in fact they are absent is much
-          smaller than the impact of managers assuming such costs are absent if
-          they are present. Further, we demonstrate that the structural form of
-          these costs matters: assuming one form when costs are are in fact
-          a different form can be even more costly.
+          optimal policies. Though it is frequently assumed that costs to adjusting
+          policies will dampen variation in the policy, we show that certain cost
+          structures can actually increase variation through time. We further show
+          that failing to account for adjustment costs has a consistently worse
+          economic impact than would assuming these costs are present when they are not.
 
@@
 
-To illustrate these concepts, we use an example from fisheries
+To illustrate this tradeoff, we use an example from fisheries
 management. Fig1a shows a time series for the

### 2014-11-30 manuscripts/manuscript.Rmd
revising text

@@
 
-```{r Figure_1, fig.cap="ICCAT Stock assessments and Total Allowable Catch (TAC, before adjustments for national underages and overages) for Bluefin Tuna, 1987 - 2007", fig.width=6, fig.height=4, dev=c("pdf", "svg", "png")}
+```{r Figure_1, fig.cap="Estimated stock abundances (top panels) show much greater variation than the corresponding harvest policies (bottom).
+Left panels: ICCAT Stock assessments and Total Allowable Catch (TAC, before adjustments for national underages and overages) for bluefin tuna, 1987 - 2007.
+Right panels: SEDAR stock assessments and annual quotas for south Atlantic snowy grouper.", fig.width=6, fig.height=4, dev=c("pdf", "svg", "png"), cache=FALSE}
 tuna <- read.csv("components/data/tuna.csv")
@@
 ex <- rbind(cbind(tuna, species="tuna"), cbind(grouper, species="snowy grouper"))
-ex_long <- gather(ex, variable, value, year, species)
+ex_long <- gather(ex, variable, value, stock, quota)
 
@@
 To illustrate this tradeoff, we use an example from fisheries
-management. Fig1a shows a time series for the
+management. Figure 1, top-left panel, shows a time series for the
 estimated population size, represented as spawning stock biomass, of
 west Atlantic bluefin tuna (_Thunnus thynnus_, henceforth bluefin) from
-a recent stock assessment [@ICCAT20XX].  Fig1b 
+a recent stock assessment [@ICCAT20XX].  The bottom-left panel 
 shows the catch quota (Total Allowable Catch or TAC, before being adjusted
@@
 in reaching agreement over any quota change, which could contribute to
-the observed quota stability. More generally, reviews by @Biais1995 and
+the observed quota stability. Such patterns of variable stocks managed
+under far less variable quotas are extremely common; for instance, 
+in the management of south Atlantic snowy grouper (_Epinephelus niveatus_) 
+shown in the right-hand panels [@SEDAR2013]. More generally, reviews by @Biais1995 and
 @Patterson2007a document many cases where changes in catch
@@
 
-<!-- NOTE perhaps comment on the deviation from constant escapement !-->
-
-As the example in Figure 1 makes clear, management policies will rarely be
+As the examples in Figure 1 make clear, management policies will rarely be
 as responsive as this constant escapement policy assumes. In this paper,
@@
 discount rate and $\Pi_0$ is the net revenue from operating the fishery
-in a given year. In this base case, we assume the annual dockside (that is, before accounting for any adjustment costs that may be incurred) net revenue
+in a given year. In this base case, we assume the annual dockside (that is,
+before accounting for any adjustment costs that may be incurred) net revenue
 from fishing is
@@
 show cases where $p=$ `r price`, $\delta=$ `r delta` and $c_0=$ `r c0`.  
-
-Sensitivity analysis appears
-in the supplement, along with complete R code to replicate and further 
-vary the setup).
+In the supplement we illustrate that the qualitative patterns observed
+here are not sensitive to the specific choices for these parameter values.
 
@@
 We denote the resulting state-dependent, optimal control as $h_0^{\ast}$.
-
 We solve this problem on a finite time horizon of $T =$ `r OptTime` using
 value iteration [@Mangel1988; @Clark2000].
+
+Note that this problem is much larger computationally than the classic 
+formulation of this stochastic dynamic programming problem for a single stock.
+Whereas the classic problem considers each of $Q$ possible discrete quotas
+for $S$ possible stock values at each time $t$, for a search space of size $S \times Q$
+per timestep;  this formulation must also consider all possible values of quota
+in the _previous_ time step: a total of $S \times Q \times Q$ configurations.
+
+R code for implementing the dynamic programming algorithm in this context is
+provided as a supplementary R package to the paper. Scripts for replicating 
+all of the analysis presented here are also provided in the Supplementary Material.
+
+<!-- Cite & link to Zenodo DOI here(?)-->
 
@@
 
-$$\Pi_{1}(N_t,h_t, h_{t-1}) = \Pi_0 - c_1  |  h_t - h_{t-1} | \,.$$
+\begin{equation}
+\Pi_{1}(N_t,h_t, h_{t-1}) = \Pi_0 - c_1  |  h_t - h_{t-1} | \,.
+\label{eq:Pi_1}
+\end{equation}
 
@@
 
-$$\Pi_{2}(N_t,h_t, h_{t-1}) = \Pi_0 - c_2 (  h_t - h_{t-1})^2 \,.$$
+\begin{equation}
+\Pi_{2}(N_t,h_t, h_{t-1}) = \Pi_0 - c_2 (  h_t - h_{t-1})^2 \,.
+\label{eq:Pi_2}
+\end{equation}
 
@@
 
-$$\Pi_{3}(N_t,h_t, h_{t-1}) = \Pi_0 - c_3 (1-\mathbf{I}(h_t, h_{t-1}))  \,,$$
+\begin{equation}
+\Pi_{3}(N_t,h_t, h_{t-1}) = \Pi_0 - c_3 (1-\mathbf{I}(h_t, h_{t-1}))  \,,
+\label{eq:Pi_3}
+\end{equation}
 
@@
 
-In addition in the Supplementary Material, we compare our results with 
+In the Supplementary Material, we compare our results with 
 more conventional fisheries economic formulation in which additional
@@
 
-Choice of parameters 
---------------------
-
-<!--NOTE ci notation is confusing because it does not usually refer to c0 or c4 -->
+<!-- State conclusion of this supplement here! -->
+
+Comparing apples to apples
+--------------------------
+
+Before we can compare the policy dynamics resulting from each of these
+functional froms, we must be careful to ensure that we are only varying
+the _structure_ of the adjustment penalty and not the overall magnitude.
+At the extremes, a large enough adjustment cost can ensure a constant 
+policy, regardless of the structure; while a small enough one can be ignored
+regardless.  Defining this calibration correctly is thus key to the entire
+analysis.  Fortunately, the optimal control framework provides a completely
+natural way to make this comparison: in terms of the _economic value_
+(measured by $NPV$) of the stock in each case.  We will calibrate this relative
+to economic value of the stock when adjustments to the policy are free ($NPV_0$).
 
@@
 parameter values should be used. To address this issue, we calibrate
-choices of $c_i$ so that each has a comparable impact on the optimal net
-present value of fishery, broadly following the example of @Bovenberg2008.
-
-<!--NOTE Jake to confirm these are still relevant and needed. 
-        We are using a less sophisticated normalization than was 
-        once discussed and may or may not need the citations now. -->
+choices of $c_i$ so that each has a comparable impact on the optimal NPV
+fishery.
 
 Figure 2 shows the calibration graphically. Each curve plots the change
-in maximum expected NPV for a given penalty function as the penalty cost
+in maximum expected $NPV$ for a given penalty function as the penalty cost
 parameter is increased. In each case, the figure shows maximum expected
@@
 induce the same reduction in maximum expected NPV. For example, the
-dashed vertical lines in Figure 1 map the needed cost coefficient $c_i$,
+dashed vertical lines in Figure 2 map the needed cost coefficient $c_i$,
 for each penalty function, such that the fishery is worth `r 100*(1-reduction)`% of its
-unconstrained value when optimally managed. We focus our examination of the models on how the type and severity of policy adjustment costs affects the optimal management strategy.
-
-<!-- is chosen such that the
-optimal stock size in the analogous deterministic problem is 5% larger
-than that corresponding to the maximum sustainable yield in biomass
-($c_0=XXX$). -->
+unconstrained value when optimally managed. We focus our examination of the models on how
+the type and severity of policy adjustment costs affects the optimal management strategy.
 
@@
 
-When considering the first formulation of policy adjustment costs
-(linear costs, $\Pi_1$), the first panel of Figure 3 shows a typical pattern, in which
-the optimal policy tends to avoid small policy adjustments, resulting in
-periods of constant policy followed by sudden bursts of adjustment.
+The first panel shows a typical pattern resulting from linear adjustment costs ($\Pi_1$).
+The optimal policy tends to avoid very small policy adjustments, resulting in
+periods of a constant policy followed by sudden bursts of adjustment.
 This results in a relatively step-like policy pattern. In contrast, the
 second formulation (quadratic costs, $\Pi_2$) disproportionately penalizes large policy
-adjustments. The corresponding optimal policy tracks all of the changes
-made by the cost-free policy, but with smaller magnitude. This results
+adjustments. The corresponding optimal policy is typified by the middle panel, responding
+to each of the fluctuations in stock, made by the cost-free policy, but with smaller 
+magnitude response than the equivalent cost-free optimal solution. This results
 in a smoother $h_t$ curve, one that undershoots the larger oscillations
@@
 
-The comparisons shown in Figure 3 are for one realization (i.e. a
-particular sequence of random number draws representing environmental
-variability) and are made for a particular magnitude of policy
-adjustment costs equal to `r reduction *100`% of the maximum expected net present value 
-in the base case ($NPV_0({\bf h_0^*})$). Figure 4 generalizes to show
-how optimal harvest levels and corresponding optimal stock sizes are
-affected by the magnitude of the costs of policy adjustment. This time
-we show summary statistics across 50 replicate sets of environmental
-conditions. We show the impact of policy adjustment costs on the
-variance of both harvests and stock sizes through time; on the
-autocorrelation of harvests and stock sizes through time.
-
-```{r Figure_4, fig.cap="Variance and autocorrelation of stock dynamics and harvest dynamics, as a function of the penalty coefficient.
-Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png")}
+These patterns are consistent across stochastic replicates over a range
+of penalty magnitudes. The comparisons shown in Figure 3 are for one 
+realization (i.e. a particular sequence of random number draws representing
+environmental variability) and are made for one particular magnitude of 
+policy adjustment costs (Calibrated to equal to `r reduction *100`% of the 
+maximum expected net present valuein the base case ($NPV_0({\bf h_0^*})$,
+as discussed in Figure 2, permitting comparisons between different forms).
+To demonstrate this, we solved for the optimal policy under each of the
+three adjustment cost scenarios for `r length(c0)` different penalty 
+coefficients. For each resulting policy, we then simulated 50 stochastic
+replicates of the stock dynamics managed under that policy.  To summarize
+the patterns shown in Figure 3 and characterize the impact of increasingly
+large fraction of the economic value (NPV) being consumed by policy
+adjustment costs, we examine the response of several summary statistics
+to increasing adjustment penalties (as a fraction of the adjustment-free value)
+in Figure 4.  We show the impact of policy adjustment costs on the
+variance & autocorrelation of the harvests through time.
+
+```{r Figure_4, fig.cap="Variance and autocorrelation of harvest dynamics, as a function of the penalty coefficient.
+Adjustment penalty is calculated as percentage of the maximum expected $NPV$ in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png")}
 
@@
 
-ggplot(filter(stats_df, variable != 'cross.correlation'), 
-       aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn))  +
+f4df <- filter(figure4_df, timeseries=='harvest')
+ggplot(f4df, aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn)) + 
   stat_summary(fun.y = mean, 
@@
   coord_cartesian(xlim = c(0, .3)) + 
-  facet_wrap(~ variable, scale="free_y") + 
+  facet_wrap(~ statistic, scale="free_y") + 
   scale_color_discrete(labels=relabel, name="Penalty function") + 
@@
 
-write.csv(stats_df, "components/data/figure4.csv")
-```
-
+write.csv(f4df, "components/data/figure4.csv")
+```
+
+Despite summarizing across such a large ensemble, Figure 4 confirms the
+patterns we observed in the individual realizations shown in Figure 3.
 For example, when small policy adjustments cost little but large
@@
 might have expected (see also @Ludwig1980 for this particular case). As
-cost penalties increase in severity (i.e., $c_i$ increases), the
+cost penalties increase in severity (moving right along the horizontal axis,
+larger fractions of the economic value are consumed by adjustment costs), the
 variance in quotas through time decreases and the autocorrelation of
-quotas through time increases. This smoothing of the harvest quotas
-through time has knock-on effects for the corresponding optimal stock
-sizes, which also become more autocorrelated as the scaling on policy
-adjustment costs ($c_i$) is increased. The autocorrelation in stock
-sizes here reflects the lag involved in a more modest increase in
-harvests taking longer to eliminate the signal of strong recruitment
-events, when compared to a more immediately responsive constant
-escapement policy.
+quotas through time increases. 
+When adjustment costs are zero, all policies are slightly negatively autocorrelated:
+this reflects the fact that a high harvest year is usually followed by a low harvest year
+that allows the stocks to recover. However, as adjustment costs increase, the quadratic
+policy tends to undershoot when stocks jump to very high or low levels, adjusting to compensate
+over multiple years, as seen in Figure 3.  As a result, autocorrelation increases.
 
 Interestingly, as suggested by the realization in Fig. 3, including a
-fixed cost of policy adjustment increases the variation in harvests
-through time. This is the opposite of a smoothing effect. Follow-on
-consequences for the other statistics are not as clear in this case.
+fixed cost ($\Pi_1$) of policy adjustment increases the variation in harvests
+through time. This is the opposite of a smoothing effect.
 
@@
 middle of the road strategy, in that increasing the severity of policy
-adjustment costs (increasing $c_i$ has little effect on the variance or
-autocorrelation of optimal harvest rates or stock sizes. To reveal the
+adjustment costs. To reveal the
 particular impact of policy adjustment costs of this type requires a
@@
 While still not common for the particular parameter combinations we examine,
-we find that positive unaltered quotas through time are much more likely
+We find that positive unaltered quotas through time are much more likely
 to occur when optimizing against $\Pi_1$ where policy adjustment costs
@@
 ```{r}
-fig5_caption <- paste("Distribution of profits from fishing and costs paid to adjustment, under linear costs (Pi[1]).
+fig5_caption <- paste("Distribution of profits from fishing and costs paid to adjustment, under linear costs ($\Pi_1$).
 (Alternate penalties can be found in the supplementary materials)  Distributions are shown when managing a system in which the adjustment costs present compared to the same costs and profits of managing the system using a Reed model, which ignores adjustment costs, and thus tends to pay higher fees for adjustment.
@@
 
-```{r Figure_5, fig.cap=fig5_caption, fig.width=8, fig.height=6, dependson="histogram-calc", dev=c("pdf", "svg", "png")}
+```{r Figure_5, fig.cap=fig5_caption, fig.width=8, fig.height=6, dependson="histogram-calc", dev=c("pdf", "svg", "png"), cache=FALSE}
 
@@
 costs when they are present or assuming they are present when they are
-not. To do so, it helps to break-down the different contributions to the
-maximum expected $NPV_i$ when employing the optimal policy $\bf{h_i}^*$
-versus when employing the policy that would be optimal were there no
-costs to policy adjustment $\bf{h_0}^*$. For example, if we take the
-first of the adjustment penalty forms, $\Pi_1$
-
-$$NPV_i( \mathbf{h_1^*} ) = \sum_{t=0}^\infty (\overbrace{ p h^*_{1,t}-c_0E^*_{1t}}^{[1]}-\overbrace{c_1 | h^*_{1,t}- h^*_{1,t-1}|}^{[2]} ) \displaystyle \frac{1}{(1+\delta)^t}$$
-
-and
-
-$$NPV_i( \mathbf{h_0^*} ) = \sum_{t=0}^\infty (\underbrace{ p h^*_{0,t}-c_0E^*_{0t}}_{[3]}-\underbrace{c_1 | h^*_{0,t}- h^*_{0,t-1}|}_{[4]} ) \displaystyle \frac{1}{(1+\delta)^t}$$
-
-Histograms for the different contributions labelled $[1]-[4]$ here when
-taken across 100 replicate runs are shown in Figure 5. Observe that the red
-distributions (dockside profits) are relatively unchanged between policies based on the adjustment-free assumption (Reed, bottom row) vs when adjustments are properly accounted for (adjustment penalty, top row), while the blue distributions (costs for adjustment) are much larger in the bottom row then
-in the top (when these costs have not been accounted for vs when they have
-been taken into account.)  The cost of assuming policy adjustments are present when in fact they are
-absent is given by subtracting the contribution to the first infinite
-sum from term $[1]$ from the contribution to the second infinite sum of
-term $[3]$. (Note that convergence properties
-required to do this are met because we assume a positive discount rate).
-This cost is positive because the optimal controls recommended when
-assuming policy adjustment costs are present do not track variations in
-stock size as closely. Therefore, this harvesting strategy provides
-lower net revenue dockside.
-
-In contrast, the cost of ignoring policy adjustment costs when in fact
-they are present is given by subtracting the second infinite sum from
-the first (contributions $([1]-[2])-([3]-[4]))$ in the equations. These
-costs are positive because the lost revenues from not tracking stock
-variations as closely are smaller than the penalties of policy
-adjustment that are incurred if managers try to track stock variations
-more tightly.
+not. To do so, we run two kinds of simulations:
+
+1. Simulations in which the optimal policy accounts for adjustment costs, 
+   and those costs are present (in the form assumed),
+2. Simulations in which the optimal policy _does not_ account for adjustment costs,
+
+While the optimization guarentees that on average, the policy in the first simulation
+should outperform that of the second, it does not tell us by how much.  These simulations
+thus give us a lense to examine the magnitude of this effect.
+
+We provide 100 replicates of each kind for each of the three forms
+$\Pi_{1-3}$ (in which each ensemble of 100 replicates uses the same sequence of random seeds).
+For each, we record (a) the dockside profits derived from fishing as well
+as (b) any fees paid to make adjustments to the policy.  In the first kind of 
+simulation, dockyard profits are almost less than in the second for a given stochastic
+replicate, since the latter optimizes the expected dockside NPV.  However, the costs
+paid for adjustment are almost always less in the first scenario as well, since
+this solution explicitly tries to avoid higher adjustment costs.  We visualize this
+pattern in the distributions shown in Figure 5 (focusing on $\Pi_1$ for simplicity,
+as the pattern in $\Pi_2$ and $\Pi_3$ is similar, see Supplementary Material.)
+
+Figure 5 shows that the difference in dockside revenue (labelled "profits" in the figure) 
+between these two scenarios 
+(green vs purple distributions) is very small, while a larger difference exists between
+the costs paid for making policy adjustments (red vs blue). This is predicted by the optimization: 
+the first scenario must outperform (or at least equal) the NPV of the second scenario
+in aggregate, and as it cannot do so through higher profits it must do so through lower
+costs.  Interestingly, for this set of parameters very little is lost in dockside revenue.
+This suggests that the impact of assuming costs are present when they are not is rather small:
+since the dockside revenue is none-the-less near optimal.  This also suggests that the 
+converse error: ignoring costs when they are present, is more severe.
 
 ```{r Figure_6, fig.cap="Relative cost of ignoring adjustment costs when they are present ('ignoring', red) vs assuming the adjustment costs when they are absent ('assuming', blue), shown by penalty function over increasing magnitudes of cost.
-All values are relative to the cost-free adjustment optimum, NPV0.
+All values are relative to the cost-free adjustment optimum, $NPV_0$.
 In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present.
-The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs.", dev=c("pdf", "svg", "png"), fig.width=7}
+The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs.", dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE}
 
@@
 
-Figure 6 compares these different contributions, namely the $NPV$ lost by
-assuming policy adjustment costs when none are present (first entry in
-each cell, $[3]-[1]$ in the equations)) and the $NPV$ lost when
-ignoring policy adjustment costs when they are present (second entry in
-each cell of the table, contributions $([1]-[2])-([3]-[4]))$ in the
-equations) across the three different functional forms. Specifically,
-the table shows how these values change as we vary the severity of
-policy adjustment costs. In each case, values are shown as percentages
-of the maximum expected $NPV$ in the base case where no policy
-adjustment costs apply or are assumed to apply $NPV_0({\bf h_0^*})$.
-
-We find a pronounced asymmetry when comparing the impact on the net
-present value of the fishery of assuming policy adjustment costs are
-present when they are absent with the impact of assuming they are absent
-when they are present. For all three types of policy adjustment cost,
-the impact on NPV of ignoring these costs if they are in fact present is
-much bigger than that incurred by fallaciously managing as if they are
-present when they do not occur. This asymmetry arises, because there is
-less difference in the dockside revenue under the two management
-recommendations than there is in the potential policy adjustment costs
-themselves, as is evident in for the particular parameters shown in
-Figure 5.
-
+We visualize the differences between these two errors directly in Figure 6. Subtracting revenue from
+adjustment costs and considering only the mean across the replicates, we can dervive the expected $NPV$ 
+in each case.  To standardize against a common baseline, we will express this value as a fraction of 
+the cost-free optimum, $NPV_0$. Note that we have calibrated the optimal solutions to anticipate that
+`r reduction*100`% of their $NPV$ would go into adjustment costs. When these adjustment costs are not 
+actually present (blue bars, Fig 6), we thus expect a $NPV$ higher than the anticipated `r (1 -reduction)*100`%
+but not quite as high as the optimal policy for that scenario (100%).  When adjustment costs are present
+but the policy assumes that they are not (red bars), we would expect the $NPV$ to be less than `r (1 - reduction) * 100`%
+of $NPV_0$ (since that's as good as the optimal solution for this scenario can do).
+
+Figure 6 shows that across each penalty form $\Pi{1-3}$, the economic impact
+of ignoring adjustment costs when they are present is higher than accounting
+for them when they are absent. This holds even after accounting for effect 
+described above: the red bars are consistently well below (`r (1-reduction)`),
+while the blue bars are barely below 1.
 We also see that the impacts on net present value of the fishery of
@@
 policy change being implemented ($\Pi_2$).
-
-When policy costs are present, assuming the wrong functional form may or
-may not be worse than ignoring the presence of policy costs all together.
-Figure 7 considers several such cases.  The X axis labels indicate
-first which policy is being used to drive the harvest decisions, and
-then which penalty is actually being applied.  Thus $\Pi_1\_\Pi_2$ indicates
-a policy calculated under the linear ($\Pi_1$) costs, when the reality
-involves quadratic ($\Pi_2$) costs.  Though the coefficients of the ($\Pi_2$)
-costs have been scaled such that the net effect is the same, the inferred
-policies differ.  As a result, the value is slightly more than half of
-the optimal free solution when the expected reduction should only be 10% (panel A)
-less than optimal free based on the $c_i$ calibration. In this case, ignoring the costs all together
-is still worse than using $\Pi_1$ costs -- the red bar is lower than the blue.
-
-For fixed costs ($\Pi_3$), the reverse is true.  Because fixed costs increase the
-volatility of the optimal solution while $\Pi_2$ costs decrease it, simply
-ignoring the cost of adjustment all together results in a higher value
-than either assuming costs are quadratic ($\Pi_2$) when they are fixed ($\Pi_3$),
-or assuming they are fixed when they are quadratic.  Scenarios in which true costs are quadratic (regardless of what
-cost structure is assumed by the policy) do significantly worse than
-those that are not (i.e. all cases that assume quadratic but actually
-have linear or fixed costs).
-
-These patterns hold across the different size reductions shown (from 10%
-to 25%, panels a-d respectively), though net present value becomes negative under the quadratic
-form for the larger penalties as costs paid for adjustments exceed
-profits derived from harvest.  (Though optimal solutions will always
-avoid negative net present values, these scenarios in which policies are
-applied under conditions other than assumed in the optimality calculation
-have no such guarantee.) For each scenario, results are averaged over
-100 replicates.
-
-```{r Figure_7, fig.cap="Mismatches.
-X axis labels indicate the model used to derive the policy, followed by the model used to simulate the penalty.
-Blue bars show the net present value of that scenario.
-Compare to red bars, which show the consequence of using a policy that ignores costs all together in the same scenario (i.e.
-costs as indicated by second code), rather than assuming the policy indicated by the first code in the pair.
-All values are scaled to a fraction of the adjustment free net present value.", dev=c("pdf", "svg", "png"), fig.width=7}
-who <- c("penalty_fn", "ignore_fraction", "mismatched_fraction", "reduction")
-table2 <- arrange(mismatches_df[who], reduction) 
-names(table2) = c("penalty.fn", "ignoring", "mismatched", "reduction")
-table2_long <- melt(table2, id = c('penalty.fn', 'reduction'))
-table2_long$reduction <- as.factor(table2_long$reduction)
-
-ggplot(filter(table2_long, reduction==0.25), 
-  aes(penalty.fn, value, fill = variable)) + 
-  geom_bar(stat="identity", position="dodge") + 
-  facet_wrap(~reduction, scales="free_y") +
-  scale_x_discrete(labels = c('L1_L2' = substitute(paste(Pi[1],"_", Pi[2])), 
-                              'L2_L1' =  substitute(paste(Pi[2],"_", Pi[1])),
-                              'L1_fixed' = substitute(paste(Pi[1],"_", Pi[3])), 
-                              'fixed_L1' =  substitute(paste(Pi[3],"_", Pi[1])),
-                              'fixed_L2' = substitute(paste(Pi[3],"_", Pi[2])), 
-                              'L2_fixed' =  substitute(paste(Pi[2],"_", Pi[3])))) + 
-  xlab("Penalty function")
-write.csv(table2_long, "components/data/figure7.csv")
-```
+In the Supplementary Materials we show that pattern holds across different
+severity of adjustment costs (robust to choice of $c_i$), though the larger
+the adjustment cost, the greater the difference between these two errors.
+
+Note that this analysis does not consider the possibility that an adjustment cost
+is present, but of a different functional form than the policy assumes.  Not surprisingly,
+the consequences of managing under the wrong functional form can be as or more severe than
+simply ignoring adjustment costs in the optimization all-together.  We illustrate several
+of these mismatch errors in the Supplementary Material.
 
@@
 ==========
-
-<!-- Pasted from external word doc, see Boettiger_Discussion_draft.docx for latest version of discussion -->
 
@@
 we might expect the different types of adjustment cost to operate in
-combination. Interestingly, there are analogues between how we have
-represented different types of policy adjustment costs in our models
-and regularization techniques that are sometimes used in model fitting
-to address concerns about over-specifying models (e.g. ridge or lasso
-regression or total variation denoising approaches
-[@Rudin1992]).
-
-<!-- NOTE
-
-Have wondered about cutting this, but does broaden things out a bit from
-just econ referencing and context.
-
-Also more people will have heard about ridge and lasso, but I actually
-think they're not as relevant as the total variation suggestion, because
-it applies to the gradient whereas they do not. So really a more accurate
-statement is that the difference between lasso and ridge and the total
-variation approach is in some ways analogous to the difference between
-costs on h or E and costs on dh/dt or dE/dt. But that's way too many
-words now
-
-Carl B - when it comes to references, you may have others you would
-prefer here
-
--->
+combination.
 
@@
 is different to models that assume fisheries are not well-managed,
-e.g. by assuming open access conditions (references [^1]),
+e.g. by assuming open access conditions,
 or ones that derive policy recommendations endogenously by modeling
@@
 the optimization models involved by relaxing other assumptions (see for
-example @Sethi2005; @Singh2006; @McGough2009). For
-example, in following Reed's approach closely another important
-assumption we made is that the fishery manager observes the current stock
-size correctly when setting the annual quota (see @Clark1986,
-@Williams2001 for alternative specifications). However, predictions of
-current cohort sizes from stock assessments are subject to uncertainty
-[@Ralston2011]. Were uncertainty regarding reported recruitment
-pulses also included, an optimizing manager might moderate their policy
-responses to initial reports of particularly good recruitment years
-increase yet further.
-
-[^1]: NOTE Would be good to give an open access model in a fluctuating
-environment here. From Andersen and Sutinen's review (Mar Res Econ
-1, 117-136) it looks like one basal citation is Andersen 1981 The
-exploitation of fish resources under stock uncertainty. But it is a
-'staff paper'. Our library don't hold it. Has anyone else got it?
+example @Sethi2005; @Singh2006; @McGough2009).
 
@@
 
-<!-- NOTE: Too many extensions being suggested now -->
+<!-- Comment on increasing variance or increasing autocorrelation from changes in policy costs / optimal management-->
 
@@
 
-<!-- NOTE Paul writes: I can provide some references on this paragraph. But
-would suggest that I wait and let you and others overhaul it first. I
-am not sure it really adds much of value, but it does give us a
-dismount. Moreover,  I'm trying to help you hit your desire to broaden
-out beyond a fisheries context. The key barometer is we should be able
-to point at a suitable sdp application which we could have used just as
-easily as the fisheries management context. I think we can probably do
-that for the list provided here.  -->
-
 Acknowledgements
@@
 
-Supplementary material
-======================
-
-## Economic penalties using quadratic costs
-
-```{r quadraticcosts}
-
-source("components/quad_costs.R")
-```
-
-Calibrated in the same way.
-
-```{r Figure_S1, dev=c('pdf', 'svg')}
-
-labels <- c(harvest = substitute(paste("Harvest Policy under ", paste(Pi[4]))), 
-                                harvest_alt = substitute(paste("Harvest under ", paste(Pi[0]), " (Reed)")))
-
-ex <- dt_quad %>% 
+# References
+
+# Supplementary material #
+
+##  Impact on the stock dynamics ##
+
+```{r StockDynamics, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=5, fig.width=8, cache = fig.cache, dev=c("pdf", "svg", "png")}
+
+labeller <- function(variable,value){
+    return(relabel[paste(value)])
+}
+
+dt_s <- dt %>% 
   filter(replicate=="rep_17" & time < 20) %>%
-  select(time, harvest, harvest_alt) %>%
-  gather(variable, stock, -time) 
-ggplot(ex) + 
-  geom_line(aes(time, stock, col=variable), lwd=1) + 
-  scale_color_discrete(labels=labels, 
-                       name="")
-
-```
-
-```{r quadshiftrate}
-shifts <- dt[, fraction_no_shift(harvest), by=c("replicate")]
-ave <- shifts[, mean(V1)]
-```
-
-Like the $\Pi_2$ adjustment cost based penalty, this quadratic cost based penalty shows periods of contant, strictly positive policy only `r ave * 100`% of the time, and exhibits the same kind of smoothing of more small adjustments that is seen in $\Pi_2$ scenario.
+  select(time, fishstock, alternate, penalty_fn) %>%
+  gather(variable, value, -time, -penalty_fn)
+
+ggplot(dt_s, aes(time, value, col=variable, lty=variable)) +
+  geom_line(lwd=1) +
+  facet_grid(penalty_fn~., labeller = labeller) + 
+  labs(x="time", y="stock size", title = "Example Stock Dynamics")  +
+  scale_color_discrete(labels=c("With Penalty", "Reed Solution"), name="") +
+  scale_linetype_discrete(labels=c("With Penalty", "Reed Solution"), name="")
+
+```
+
+```{r StockStats, fig.cap="Variance and autocorrelation of stock dynamics, as a function of the penalty coefficient.
+Adjustment penalty is calculated as percentage of the maximum expected $NPV$ in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png")}
+
+stock_stats <- filter(figure4_df, timeseries=='stock')
+ggplot(stock_stats, aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn)) + 
+  stat_summary(fun.y = mean, 
+               fun.ymin = function(x) mean(x) - sd(x), 
+               fun.ymax = function(x) mean(x) + sd(x), 
+               geom = "ribbon", alpha=0.3, colour=NA) +
+  stat_summary(fun.y = mean, geom = "line") + 
+  coord_cartesian(xlim = c(0, .3)) + 
+  facet_wrap(~ statistic, scale="free_y") + 
+  scale_color_discrete(labels=relabel, name="Penalty function") + 
+  scale_fill_discrete(labels=relabel, name="Penalty function") +
+  xlab("Penalty size (as fraction of NPV0)")
+
+```
 
@@
 
-```{r Figure_S2, dependson="tidy", fig.cap="Multiple realizations of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=10, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png")}
+## Additional stochastic realizations ##
+
+Figure 3 of the main text shows a single stochastic realization.  Here we provide a sample of further realizations (including both stock and harvest dynamics).  Full
+
+```{r Figure_S2, dependson="tidy", fig.cap="Multiple realizations of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=10, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png"), cache=FALSE}
 
@@
 
+## Economic penalties using quadratic costs ##
+
+```{r quadraticcosts}
+
+source("components/quad_costs.R")
+```
+
+```{r Figure_S1, dev=c('pdf', 'svg'), cache=FALSE}
+
+labels <- c(harvest = substitute(paste("Harvest Policy under ", paste(Pi[4]))), 
+                                harvest_alt = substitute(paste("Harvest under ", paste(Pi[0]), " (Reed)")))
+
+ex <- dt_quad %>% 
+  filter(replicate=="rep_17" & time < 20) %>%
+  select(time, harvest, harvest_alt) %>%
+  gather(variable, stock, -time) 
+ggplot(ex) + 
+  geom_line(aes(time, stock, col=variable), lwd=1) + 
+  scale_color_discrete(labels=labels, 
+                       name="")
+
+```
+
+```{r quadshiftrate}
+shifts <- dt[, fraction_no_shift(harvest), by=c("replicate")]
+ave <- shifts[, mean(V1)]
+```
+
+Like the $\Pi_2$ adjustment cost based penalty, this quadratic cost based penalty shows periods of contant, strictly positive policy only `r ave * 100`% of the time, and exhibits the same kind of smoothing of more small adjustments that is seen in $\Pi_2$ scenario.
+
+<!-- Figure 5 extended across -->
+
 ```{r Figure_S3, fig.cap="Distribution of profits from fishing and costs paid to adjustment.
 Distributions are shown when managing a system in which the adjustment costs present are determined by the model indicated, and compared to the same costs and profits of managing the same system using a Reed model, which ignores adjustment costs, and thus tends to pay much higher fees for adjustment.
-In contrast, the difference in profit after accounting for costs is only marginally less than the value derived by managing the population to optimize profits when ignoring adjustment costs (Reed model).", fig.width=8, fig.height=6, dependson="histogram-calc", dev=c("pdf", "svg", "png")}
+In contrast, the difference in profit after accounting for costs is only marginally less than the value derived by managing the population to optimize profits when ignoring adjustment costs (Reed model).", fig.width=8, fig.height=6, dependson="histogram-calc", dev=c("pdf", "svg", "png"), cache=FALSE}
 
@@
   } else {
-    return(assume[paste(value)])
+    return(paste(value))
+    #return(assume[paste(value)])
   }
@@
 In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present.
-The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs.", dev=c("pdf", "svg", "png"), fig.width=7}
+The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs.", dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE}
 
@@
 
+When policy costs are present, assuming the wrong functional form may or
+may not be worse than ignoring the presence of policy costs all together.
+Figure S5 considers several such cases.  The X axis labels indicate
+first which policy is being used to drive the harvest decisions, and
+then which penalty is actually being applied.  Thus $\Pi_1\_\Pi_2$ indicates
+a policy calculated under the linear ($\Pi_1$) costs, when the reality
+involves quadratic ($\Pi_2$) costs.  Though the coefficients of the ($\Pi_2$)
+costs have been scaled such that the net effect is the same, the inferred
+policies differ.  As a result, the value is slightly more than half of
+the optimal free solution when the expected reduction should only be 10% (panel A)
+less than optimal free based on the $c_i$ calibration. In this case, ignoring the costs all together
+is still worse than using $\Pi_1$ costs -- the red bar is lower than the blue.
+
+For fixed costs ($\Pi_3$), the reverse is true.  Because fixed costs increase the
+volatility of the optimal solution while $\Pi_2$ costs decrease it, simply
+ignoring the cost of adjustment all together results in a higher value
+than either assuming costs are quadratic ($\Pi_2$) when they are fixed ($\Pi_3$),
+or assuming they are fixed when they are quadratic.  Scenarios in which true costs are quadratic (regardless of what
+cost structure is assumed by the policy) do significantly worse than
+those that are not (i.e. all cases that assume quadratic but actually
+have linear or fixed costs).
+
+These patterns hold across the different size reductions shown (from 10%
+to 25%, panels a-d respectively), though net present value becomes negative under the quadratic
+form for the larger penalties as costs paid for adjustments exceed
+profits derived from harvest.  (Though optimal solutions will always
+avoid negative net present values, these scenarios in which policies are
+applied under conditions other than assumed in the optimality calculation
+have no such guarantee.) For each scenario, results are averaged over
+100 replicates.
+
+```{r Figure_S5, fig.cap="Mismatches.
+X axis labels indicate the model used to derive the policy, followed by the model used to simulate the penalty.
+Blue bars show the net present value of that scenario.
+Compare to red bars, which show the consequence of using a policy that ignores costs all together in the same scenario (i.e.
+costs as indicated by second code), rather than assuming the policy indicated by the first code in the pair.
+All values are scaled to a fraction of the adjustment free net present value.", dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE}
+who <- c("penalty_fn", "ignore_fraction", "mismatched_fraction", "reduction")
+table2 <- arrange(mismatches_df[who], reduction) 
+names(table2) = c("penalty.fn", "ignoring", "mismatched", "reduction")
+table2_long <- melt(table2, id = c('penalty.fn', 'reduction'))
+table2_long$reduction <- as.factor(table2_long$reduction)
+
+ggplot(filter(table2_long, reduction==0.25), 
+  aes(penalty.fn, value, fill = variable)) + 
+  geom_bar(stat="identity", position="dodge") + 
+  facet_wrap(~reduction, scales="free_y") +
+  scale_x_discrete(labels = c('L1_L2' = substitute(paste(Pi[1],"_", Pi[2])), 
+                              'L2_L1' =  substitute(paste(Pi[2],"_", Pi[1])),
+                              'L1_fixed' = substitute(paste(Pi[1],"_", Pi[3])), 
+                              'fixed_L1' =  substitute(paste(Pi[3],"_", Pi[1])),
+                              'fixed_L2' = substitute(paste(Pi[3],"_", Pi[2])), 
+                              'L2_fixed' =  substitute(paste(Pi[2],"_", Pi[3])))) + 
+  xlab("Penalty function")
+write.csv(table2_long, "components/data/figure7.csv")
+```
+
+<!--
+
 ```{r Figure_S5, fig.cap="Effect of varying severity of adjustment costs on mismatches.
@@
 a policy in the first panel would lose only 10% (panel A) of its net present value to adjustment costs if it had the correct form of those costs, as determined by the choice of penalty coefficient.
-Plots structured as in figure 7, which corresponds to the fourth panel", dev=c("pdf", "svg", "png"), fig.width=7}
+Plots structured as in figure 7, which corresponds to the fourth panel", dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE}
 ggplot(table2_long, aes(penalty.fn, value, fill = variable)) + 
@@
 
-# References
+-->

### 2014-12-19 manuscripts/manuscript.Rmd
update Dockerfile, tweak manuscript, separate out supplement

@@
 ```{r configure, include=FALSE, cache=FALSE}
-#source("components/install.R")
-
 library("methods")
@@
 ```{r Figure_4, fig.cap="Variance and autocorrelation of harvest dynamics, as a function of the penalty coefficient.
-Adjustment penalty is calculated as percentage of the maximum expected $NPV$ in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png")}
+Adjustment penalty is calculated as percentage of the maximum expected $NPV$ in the basic case with no policy adjustment costs.", fig.height=4, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png")}
 
@@
 ```{r}
-fig5_caption <- paste("Distribution of profits from fishing and costs paid to adjustment, under linear costs ($\Pi_1$).
+fig5_caption <- paste("Distribution of profits from fishing and costs paid to adjustment, under linear costs ($\\Pi_1$).
 (Alternate penalties can be found in the supplementary materials)  Distributions are shown when managing a system in which the adjustment costs present compared to the same costs and profits of managing the system using a Reed model, which ignores adjustment costs, and thus tends to pay higher fees for adjustment.
@@
 proposed policy changes would be empirically challenging. Recognizing
-this fact, in our analyses, we compared different plausible forms that
+this fact, we compared different plausible forms that
 these costs might take. We compared two cost structures where we assumed
@@
 on annual quotas and those that do not. The few past studies that
-incorporate policy adjustment costs in models of fisheries management
-[@Ludwig1980; @Feichtinger1994; @Wirl1999] assumed costs of
+incorporate policy adjustment costs in models of fisheries or other environmental management contexts [@Feichtinger1994; @Wirl1999] have assumed costs of
 policy adjustment increased as a quadratic function of the magnitude of
-the policy change being proposed (our $\Pi_2$ formulation) In
+the policy change being proposed (analogous to $\Pi_2$ formulation). In
 effect, this means that small changes to annual quotas incur little
 extra cost, but large changes to annual quotas become disproportionately
-expensive to make. Including costs of this form smoothes inter-annual
+expensive to make. Including costs of this form smooths inter-annual
 variation in the catch quotas that would be recommended. Also, the catches and remaining stock sizes
@@
 modeling studies sometimes mention policy adjustment costs when motivating
-model assumptions (references), they rarely provide much justification
+model assumptions [e.g. @Feichtinger1994; @Wirl1999; @Lewis1981; @McGough2009], they rarely provide much justification
 for the choice of functional form used or test the sensitivity of any
@@
 Assuming an adjustment cost exists when in fact it is absent is not the
-same as using the wrong functional form when it is present.  Here, our
-results showed that choice of the functional form makes a significant
+same as using the wrong functional form when it is present.  In the supplement we show that choice of the functional form makes a significant
 difference.  We show it can be better to ignore policy costs than to derive a 
@@
 be associated with changes to the risk of extinction or of transitions
-between alternative stable states [@Scheffer2009; @Boettiger2013].
-
-<!-- Comment on increasing variance or increasing autocorrelation from changes in policy costs / optimal management-->
+between alternative stable states [@Scheffer2009]. This highlights the risk
+that changes in management policies can either mimic or mask such possible
+early warning signs of sudden transitions, and points to another way
+in which more context is needed before such approaches can be useful to
+management [@Boettiger2013].
 
@@
 # References
-
-# Supplementary material #
-
-##  Impact on the stock dynamics ##
-
-```{r StockDynamics, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=5, fig.width=8, cache = fig.cache, dev=c("pdf", "svg", "png")}
-
-labeller <- function(variable,value){
-    return(relabel[paste(value)])
-}
-
-dt_s <- dt %>% 
-  filter(replicate=="rep_17" & time < 20) %>%
-  select(time, fishstock, alternate, penalty_fn) %>%
-  gather(variable, value, -time, -penalty_fn)
-
-ggplot(dt_s, aes(time, value, col=variable, lty=variable)) +
-  geom_line(lwd=1) +
-  facet_grid(penalty_fn~., labeller = labeller) + 
-  labs(x="time", y="stock size", title = "Example Stock Dynamics")  +
-  scale_color_discrete(labels=c("With Penalty", "Reed Solution"), name="") +
-  scale_linetype_discrete(labels=c("With Penalty", "Reed Solution"), name="")
-
-```
-
-```{r StockStats, fig.cap="Variance and autocorrelation of stock dynamics, as a function of the penalty coefficient.
-Adjustment penalty is calculated as percentage of the maximum expected $NPV$ in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png")}
-
-stock_stats <- filter(figure4_df, timeseries=='stock')
-ggplot(stock_stats, aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn)) + 
-  stat_summary(fun.y = mean, 
-               fun.ymin = function(x) mean(x) - sd(x), 
-               fun.ymax = function(x) mean(x) + sd(x), 
-               geom = "ribbon", alpha=0.3, colour=NA) +
-  stat_summary(fun.y = mean, geom = "line") + 
-  coord_cartesian(xlim = c(0, .3)) + 
-  facet_wrap(~ statistic, scale="free_y") + 
-  scale_color_discrete(labels=relabel, name="Penalty function") + 
-  scale_fill_discrete(labels=relabel, name="Penalty function") +
-  xlab("Penalty size (as fraction of NPV0)")
-
-```
-
-Recall that in our model definition, stock sizes are measured before harvest ($h_t$ being determined after observing stock size
-$x_t$) and thus show less influence of the policy cost than the harvest itself.
-
-## Additional stochastic realizations ##
-
-Figure 3 of the main text shows a single stochastic realization.  Here we provide a sample of further realizations (including both stock and harvest dynamics).  Full
-
-```{r Figure_S2, dependson="tidy", fig.cap="Multiple realizations of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=10, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png"), cache=FALSE}
-
-labels <- c(harvest = substitute(paste("Harvest Policy under ", paste(Pi[1-3]))), 
-            harvest_alt = substitute(paste("Harvest under ", paste(Pi[0]), " (Reed)")),
-            fishstock = substitute(paste("Stock dynamics under under ", paste(Pi[1-3]))), 
-            alternate = substitute(paste("Stock under ", paste(Pi[0]), " (Reed)")))
-labeller <- function(variable,value){
-if (variable=='penalty_fn') {
-    return(relabel[paste(value)])
-  } else {
-    return(value)
-  }
-}
-
-ex <- dt %>% 
-  filter(replicate %in% paste0("rep_", 16:20) & time < 20) %>%
-  select(time, fishstock, harvest, alternate, harvest_alt, replicate, penalty_fn) %>%
-  gather(variable, stock, -time, -replicate, -penalty_fn)
-
-ggplot(ex) + 
-  geom_line(aes(time, stock, col=variable), lwd=1) + 
-  scale_color_discrete(labels=labels, name="") +  
-  facet_grid(replicate ~ penalty_fn, labeller=labeller)
-
-write.csv(ex, "components/data/figure_s2.csv")
-```
-
-## Economic penalties using quadratic costs ##
-
-```{r quadraticcosts}
-
-source("components/quad_costs.R")
-```
-
-```{r Figure_S1, dev=c('pdf', 'svg'), cache=FALSE}
-
-labels <- c(harvest = substitute(paste("Harvest Policy under ", paste(Pi[4]))), 
-                                harvest_alt = substitute(paste("Harvest under ", paste(Pi[0]), " (Reed)")))
-
-ex <- dt_quad %>% 
-  filter(replicate=="rep_17" & time < 20) %>%
-  select(time, harvest, harvest_alt) %>%
-  gather(variable, stock, -time) 
-ggplot(ex) + 
-  geom_line(aes(time, stock, col=variable), lwd=1) + 
-  scale_color_discrete(labels=labels, 
-                       name="")
-
-```
-
-```{r quadshiftrate}
-shifts <- dt[, fraction_no_shift(harvest), by=c("replicate")]
-ave <- shifts[, mean(V1)]
-```
-
-Like the $\Pi_2$ adjustment cost based penalty, this quadratic cost based penalty shows periods of contant, strictly positive policy only `r ave * 100`% of the time, and exhibits the same kind of smoothing of more small adjustments that is seen in $\Pi_2$ scenario.
-
-<!-- Figure 5 extended across -->
-
-```{r Figure_S3, fig.cap="Distribution of profits from fishing and costs paid to adjustment.
-Distributions are shown when managing a system in which the adjustment costs present are determined by the model indicated, and compared to the same costs and profits of managing the same system using a Reed model, which ignores adjustment costs, and thus tends to pay much higher fees for adjustment.
-In contrast, the difference in profit after accounting for costs is only marginally less than the value derived by managing the population to optimize profits when ignoring adjustment costs (Reed model).", fig.width=8, fig.height=6, dependson="histogram-calc", dev=c("pdf", "svg", "png"), cache=FALSE}
-
-assume <- levels(as.factor(hist_dat$Assumption))
-labeller <- function(variable,value){
-if (variable=='penalty_fn') {
-    return(relabel[paste(value)])
-  } else {
-    return(paste(value))
-    #return(assume[paste(value)])
-  }
-}
-
-ggplot(hist_dat) + 
-  geom_density(aes(value, fill=variable, color=variable), alpha=0.8)+
-  facet_grid(Assumption~penalty_fn, labeller = labeller)
-
-write.csv(hist_dat, "components/data/figure5.csv")
-```
-
-```{r Figure_S4, fig.cap="Relative cost of ignoring adjustment costs when they are present ('ignoring', red) vs assuming the adjustment costs when they are absent ('assuming', blue), shown by penalty function over increasing magnitudes of cost.
-All values are relative to the cost-free adjustment optimum, NPV0.
-In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present.
-The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs.", dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE}
-
-ggplot(table1_long, aes(penalty.fn, value, fill = variable)) + 
-  geom_bar(stat="identity", position="dodge") + 
-  facet_wrap(~reduction, ncol=2) + 
-  scale_x_discrete(labels = c('L1' = substitute(paste(Pi[1])),
-                              'L2' = substitute(paste(Pi[2])),
-                              'fixed' = substitute(paste(Pi[3])))) + 
-  xlab("Penalty function")
-write.csv(table1_long, "components/data/figure6.csv")
-```
-
-When policy costs are present, assuming the wrong functional form may or
-may not be worse than ignoring the presence of policy costs all together.
-Figure S5 considers several such cases.  The X axis labels indicate
-first which policy is being used to drive the harvest decisions, and
-then which penalty is actually being applied.  Thus $\Pi_1\_\Pi_2$ indicates
-a policy calculated under the linear ($\Pi_1$) costs, when the reality
-involves quadratic ($\Pi_2$) costs.  Though the coefficients of the ($\Pi_2$)
-costs have been scaled such that the net effect is the same, the inferred
-policies differ.  As a result, the value is slightly more than half of
-the optimal free solution when the expected reduction should only be 10% (panel A)
-less than optimal free based on the $c_i$ calibration. In this case, ignoring the costs all together
-is still worse than using $\Pi_1$ costs -- the red bar is lower than the blue.
-
-For fixed costs ($\Pi_3$), the reverse is true.  Because fixed costs increase the
-volatility of the optimal solution while $\Pi_2$ costs decrease it, simply
-ignoring the cost of adjustment all together results in a higher value
-than either assuming costs are quadratic ($\Pi_2$) when they are fixed ($\Pi_3$),
-or assuming they are fixed when they are quadratic.  Scenarios in which true costs are quadratic (regardless of what
-cost structure is assumed by the policy) do significantly worse than
-those that are not (i.e. all cases that assume quadratic but actually
-have linear or fixed costs).
-
-These patterns hold across the different size reductions shown (from 10%
-to 25%, panels a-d respectively), though net present value becomes negative under the quadratic
-form for the larger penalties as costs paid for adjustments exceed
-profits derived from harvest.  (Though optimal solutions will always
-avoid negative net present values, these scenarios in which policies are
-applied under conditions other than assumed in the optimality calculation
-have no such guarantee.) For each scenario, results are averaged over
-100 replicates.
-
-```{r Figure_S5, fig.cap="Mismatches.
-X axis labels indicate the model used to derive the policy, followed by the model used to simulate the penalty.
-Blue bars show the net present value of that scenario.
-Compare to red bars, which show the consequence of using a policy that ignores costs all together in the same scenario (i.e.
-costs as indicated by second code), rather than assuming the policy indicated by the first code in the pair.
-All values are scaled to a fraction of the adjustment free net present value.", dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE}
-who <- c("penalty_fn", "ignore_fraction", "mismatched_fraction", "reduction")
-table2 <- arrange(mismatches_df[who], reduction) 
-names(table2) = c("penalty.fn", "ignoring", "mismatched", "reduction")
-table2_long <- melt(table2, id = c('penalty.fn', 'reduction'))
-table2_long$reduction <- as.factor(table2_long$reduction)
-
-ggplot(filter(table2_long, reduction==0.25), 
-  aes(penalty.fn, value, fill = variable)) + 
-  geom_bar(stat="identity", position="dodge") + 
-  facet_wrap(~reduction, scales="free_y") +
-  scale_x_discrete(labels = c('L1_L2' = substitute(paste(Pi[1],"_", Pi[2])), 
-                              'L2_L1' =  substitute(paste(Pi[2],"_", Pi[1])),
-                              'L1_fixed' = substitute(paste(Pi[1],"_", Pi[3])), 
-                              'fixed_L1' =  substitute(paste(Pi[3],"_", Pi[1])),
-                              'fixed_L2' = substitute(paste(Pi[3],"_", Pi[2])), 
-                              'L2_fixed' =  substitute(paste(Pi[2],"_", Pi[3])))) + 
-  xlab("Penalty function")
-write.csv(table2_long, "components/data/figure7.csv")
-```
-
-<!--
-
-```{r Figure_S5, fig.cap="Effect of varying severity of adjustment costs on mismatches.
-Successive panels show increasing reduction of the net present value by increasing penalty coefficients: e.g.
-a policy in the first panel would lose only 10% (panel A) of its net present value to adjustment costs if it had the correct form of those costs, as determined by the choice of penalty coefficient.
-Plots structured as in figure 7, which corresponds to the fourth panel", dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE}
-ggplot(table2_long, aes(penalty.fn, value, fill = variable)) + 
-  geom_bar(stat="identity", position="dodge") + 
-  facet_wrap(~reduction, scales="free_y") +
-  scale_x_discrete(labels = c('L1_L2' = substitute(paste(Pi[1],"_", Pi[2])), 
-                              'L2_L1' =  substitute(paste(Pi[2],"_", Pi[1])),
-                              'L1_fixed' = substitute(paste(Pi[1],"_", Pi[3])), 
-                              'fixed_L1' =  substitute(paste(Pi[3],"_", Pi[1])),
-                              'fixed_L2' = substitute(paste(Pi[3],"_", Pi[2])), 
-                              'L2_fixed' =  substitute(paste(Pi[2],"_", Pi[3])))) + 
-  xlab("Penalty function")
-write.csv(table2_long, "components/data/figure7.csv")
-```
-
--->

### 2014-12-19 manuscripts/supplement.Rmd
update Dockerfile, tweak manuscript, separate out supplement

@@
   - name: Jacob LaRiviere
-    affiliation: UTK
+    affiliation: UTKEcon
   - name: Alan Hastings
@@
   - name: Paul Armsworth 
-    affiliation: UTK
+    affiliation: UTKEEB
 
@@
   - code: melbourne
-    address: University of Melbourne, Australia 
-  - code: UTK
-    address: University of Tennessee, Knoxville
+    address: School of Botany, University of Melbourne, Australia 
+  - code: UTKEEB
+    address: Department of Ecology and Evolutionary Biology, University of Tennessee, Knoxville
+  - code: UTKEcon
+    address: Department of Economics, University of Tennessee, Knoxville
 
@@
     fig_caption: true
-
 ---
 
-```{r configure, include=FALSE, cache=FALSE}
-#source("components/install.R")
+\appendix
 
-library("methods")
-library("knitr")
-basename <- "supplement"
-opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
-               cache.path = paste("components/cache/", basename, "/", sep=""))
-opts_chunk$set(cache = 2)
-opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, 
-               comment = NA, verbose = TRUE, echo=FALSE)
-# PDF-based figures
-opts_chunk$set(dev='pdf')
-fig.cache <- TRUE
+# Supplementary material #
 
-library("rmarkdown")
-library("pdgControl")
-library("reshape2")
-library("plyr")
-library("ggplot2")
-library("data.table")
-library("pander")
-library("cboettigR")
-library("ggthemes")
-library("snowfall")
-library("tidyr")
-library("dplyr")
-transparent = theme(
-    panel.background = element_rect(fill = "transparent",colour = NA), 
-    plot.background = element_rect(fill = "transparent",colour = NA))
+##  Impact on the stock dynamics ##
 
-theme_set(theme_bw(base_size=18) + transparent)
-```
+Figure S1 shows the corresponding stock dynamics for the replicates illustrated in Figure 3 of the main text.
+The impact of the adjustment cost on the stock dynamics is less dramatic than it is on the harvest dynamics, due to the stochastic growth in stock sizes and the sequence in which the steps are applied: stock values are assessed without error, then an optimal harvest is determined (using the pre-computed optimal policy based on both the stock assessment and the previous harvest, to account for possible adjustment costs), and then the stock that escapes harvesting recruits stochastically to set the population size for the next year.
 
-```{r analysis, include=FALSE}
-source("components/supp_analysis.R")
-```
+Though this results in an effect that is less pronounced, the stock dynamics clearly reflect the same general trends observed in Figure 3: the quadratic costs ($\Pi_2$) show a clear smoothing of the variation in stock dynamics, while the fixed fee $\Pi_3$ results in exaggerated fluctionations in the stock sizes.
+It is worth noting how changes in policy costs alone, such as introducing or rising fixed costs, can have important knock-on effects to population dynamics such as increased variance, a recent phenomenon observed in important fisheries that has recieved much attention elsewhere [@Anderson2008].
 
-```{r ex_fish, fig.cap="", dev=c("pdf", "svg", "png"), dev.args=list(bg="transparent")}
-ex <- filter(dt, replicate=="rep_17" & penalty_fn == "L1" & time < 20)
-ggplot(ex) + 
-  geom_line(aes(time, fishstock), col="darkblue", lwd=1)
-```
+```{r StockDynamics, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=5, fig.width=8, cache = fig.cache, dev=c("pdf", "svg", "png")}
 
-## So then, do our optimal policies
+labeller <- function(variable,value){
+    return(relabel[paste(value)])
+}
 
-```{r ex_harvest, fig.cap="", dev=c("pdf", "svg", "png"), dependson="ex_fish", dev.args=list(bg="transparent")}
-ggplot(ex) + 
-  geom_line(aes(time, harvest_alt), col="darkgreen", lwd=1) +
-  ylab("Optimal quota policy") 
-```
+dt_s <- dt %>% 
+  filter(replicate=="rep_17" & time < 20) %>%
+  select(time, fishstock, alternate, penalty_fn) %>%
+  gather(variable, value, -time, -penalty_fn)
 
-```{r, fig.cap="",  dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent"), fig.height=3}
-ex <- dt %>% 
-  filter(replicate=="rep_17" & penalty_fn == "L1" & time < 20) %>%
-  select(time, fishstock, harvest_alt) %>%
-  gather(variable, stock, -time) 
-ggplot(ex) + 
-  geom_line(aes(time, stock, col=variable), lwd=1) + 
-  scale_color_discrete(labels=c(fishstock = "Stock size", harvest_alt = "Harvest policy"), name="")
+ggplot(dt_s, aes(time, value, col=variable, lty=variable)) +
+  geom_line(lwd=1) +
+  facet_grid(penalty_fn~., labeller = labeller) + 
+  labs(x="time", y="stock size", title = "Example Stock Dynamics")  +
+  scale_color_discrete(labels=c("With Penalty", "Reed Solution"), name="") +
+  scale_linetype_discrete(labels=c("With Penalty", "Reed Solution"), name="")
 
@@
 
-Apples to Apples
-------------------
+```{r StockStats, fig.cap="Variance and autocorrelation of stock dynamics, as a function of the penalty coefficient.
+Adjustment penalty is calculated as percentage of the maximum expected $NPV$ in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png")}
 
-```{r Figure_2, fig.cap="",  dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
-
-relabel <- c(L1 = substitute(paste(Pi[1])),
-             L2 = substitute(paste(Pi[2])),
-             fixed = substitute(paste(Pi[3])))
-
-ggplot(fees, aes(c2, (npv0-value)/npv0, color=variable)) + 
-  geom_line(lwd=1) + 
-  geom_hline(aes(yintercept=reduction), linetype=4) + 
-  xlab("Penalty coefficient") +
-  ylab("Reduction in net present value") + 
-  scale_color_discrete(labels=relabel)
-
-```
-
-```{r reex, fig.cap="", dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent"), fig.height=3}
-ggplot(ex) + 
-  geom_line(aes(time, stock, col=variable), lwd=1) + 
-  scale_color_discrete(labels=c(fishstock = "Stock size", harvest_alt = "Harvest policy"), name="") 
-```
-
-Quadratic Costs ($\Pi_2$)
--------------------------
-
-```{r quadratic, fig.cap="", dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
-ex <- dt %>% 
-  filter(replicate=="rep_17" & penalty_fn == "L2") %>%
-  select(time, harvest, harvest_alt) %>%
-  gather(variable, value, -time) 
-ggplot(ex) + 
-  geom_line(aes(time, value, col=variable), lwd=1) + 
-  ylab("harvest quota") +
-  scale_color_discrete(labels=c(harvest = "adjusted policy", harvest_alt = "baseline policy"), name="") 
-```
-
-Fixed Costs ($\Pi_3$)
----------------------
-
-```{r fixed, fig.cap="", dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
-ex <- dt %>% 
-  filter(replicate=="rep_17" & penalty_fn == "fixed") %>%
-  select(time, harvest, harvest_alt) %>%
-  gather(variable, value, -time) 
-ggplot(ex) + 
-  geom_line(aes(time, value, col=variable), lwd=1) + 
-  ylab("harvest quota") +
-  scale_color_discrete(labels=c(harvest = "adjusted policy", harvest_alt = "baseline policy"), name="") 
-```
-
-Linear Costs ($\Pi_1$)
----------------------
-
-```{r linear, fig.cap="", dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
-ex <- dt %>% 
-  filter(replicate=="rep_17" & penalty_fn == "L1") %>%
-  select(time, harvest, harvest_alt) %>%
-  gather(variable, value, -time) 
-ggplot(ex) + 
-  geom_line(aes(time, value, col=variable), lwd=1) + 
-  ylab("harvest quota") +
-  scale_color_discrete(labels=c(harvest = "adjusted policy", harvest_alt = "baseline policy"), name="") 
-```
-
-(For comparison)
-----------------
-
-```{r Figure_3, dependson="tidy", fig.cap="", dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
-
-fig3_df <- as.data.frame(subset(dt, replicate=='rep_17'))
-fig3_df <- fig3_df[c("time", "fishstock", "alternate", "harvest", "harvest_alt", "penalty_fn")]
-fig3_df <- melt(fig3_df, id = c("time", "penalty_fn"))
-fig3_df <- data.frame(fig3_df, baseline = fig3_df$variable)
-variable_map <- c(fishstock = "fish_stock", alternate = "fish_stock", harvest = "harvest", harvest_alt = "harvest")
-baseline_map <- c(fishstock = "penalty", alternate = "no_penalty", harvest = "penalty", harvest_alt = "no_penalty")
-fig3_df$variable <- variable_map[fig3_df$variable]
-fig3_df$baseline <- baseline_map[fig3_df$baseline]
-
-harvest_fig3 <- subset(fig3_df, variable=="harvest")
-fishstock_fig3 <- subset(fig3_df, variable=="fish_stock")
-
-labeller <- function(variable,value){
-    relabel[paste(value)]
-}
-
-ggplot(harvest_fig3, aes(time, value, col=baseline)) +
-  geom_line(lwd=1) +
-  facet_grid(penalty_fn~., labeller = labeller) + 
-  labs(x="time", y="stock size", title = "Example Harvest Dynamics")  +
-  scale_color_discrete(labels=c("Reed solution", "With penalty"), name="")
-```
-
-## General trends
-
-```{r Figure_4, fig.cap="", dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
-ggplot(subset(figure4_df, statistic != "cross.correlation"), 
-       aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn))  +
+stock_stats <- filter(figure4_df, timeseries=='stock')
+ggplot(stock_stats, aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn)) + 
   stat_summary(fun.y = mean, 
@@
   coord_cartesian(xlim = c(0, .3)) + 
-  facet_wrap(~ timeseries + statistic, scale="free_y") + 
+  facet_wrap(~ statistic, scale="free_y") + 
   scale_color_discrete(labels=relabel, name="Penalty function") + 
@@
   xlab("Penalty size (as fraction of NPV0)")
+
 ```
 
-- Quadratic ($\Pi_2$) smooths, Linear ($\Pi_1$) flattens, Fixed ($\Pi_3$) jumps
+Recall that in our model definition, stock sizes are measured before harvest ($h_t$ being determined after observing stock size
+$x_t$) and thus show less influence of the policy cost than the harvest itself.
 
-Consequences of policy adjustment costs 
----------------------------------------
+## Additional stochastic realizations ##
 
-```{r histogram-calc}
-profits <- dt[, sum(profit_fishing), by=c('penalty_fn', 'replicate') ]
-costs <- dt[, sum(policy_cost), by=c('penalty_fn', 'replicate') ]
-reed_profits <- dt[, sum(profit_fishing_alt), by=c('penalty_fn', 'replicate') ]
-reed_costs <- dt[, sum(policy_cost_alt), by=c('penalty_fn', 'replicate') ]
-setnames(profits, "V1", "profits")
-setnames(reed_profits, "V1", "profits")
-Reed <- cbind(reed_profits, costs = reed_costs$V1, Assumption = "Reed") 
-Adj <- cbind(profits, costs = costs$V1, Assumption = "Adjustment penalty")
-hist_dat <- melt(rbind(Adj, Reed), id=c("penalty_fn", "replicate", "Assumption"))
-````
+Figure 3 of the main text shows a single stochastic realization.  Here we provide a sample of further realizations (including both stock and harvest dynamics).  Full
 
-```{r Figure_5, fig.cap="",  dependson="histogram-calc", dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
+```{r Figure_S2, dependson="tidy", fig.cap="Multiple realizations of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=10, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png"), cache=FALSE}
+
+labels <- c(harvest = substitute(paste("Harvest Policy under ", paste(Pi[1-3]))), 
+            harvest_alt = substitute(paste("Harvest under ", paste(Pi[0]), " (Reed)")),
+            fishstock = substitute(paste("Stock dynamics under under ", paste(Pi[1-3]))), 
+            alternate = substitute(paste("Stock under ", paste(Pi[0]), " (Reed)")))
+labeller <- function(variable,value){
+if (variable=='penalty_fn') {
+    return(relabel[paste(value)])
+  } else {
+    return(value)
+  }
+}
+
+ex <- dt %>% 
+  filter(replicate %in% paste0("rep_", 16:20) & time < 20) %>%
+  select(time, fishstock, harvest, alternate, harvest_alt, replicate, penalty_fn) %>%
+  gather(variable, stock, -time, -replicate, -penalty_fn)
+
+ggplot(ex) + 
+  geom_line(aes(time, stock, col=variable), lwd=1) + 
+  scale_color_discrete(labels=labels, name="") +  
+  facet_grid(replicate ~ penalty_fn, labeller=labeller)
+
+write.csv(ex, "components/data/figure_s2.csv")
+```
+
+## Economic penalties using quadratic costs ##
+
+```{r quadraticcosts}
+
+source("components/quad_costs.R")
+```
+
+```{r Figure_S1, dev=c('pdf', 'svg'), cache=FALSE}
+
+labels <- c(harvest = substitute(paste("Harvest Policy under ", paste(Pi[4]))), 
+                                harvest_alt = substitute(paste("Harvest under ", paste(Pi[0]), " (Reed)")))
+
+ex <- dt_quad %>% 
+  filter(replicate=="rep_17" & time < 20) %>%
+  select(time, harvest, harvest_alt) %>%
+  gather(variable, stock, -time) 
+ggplot(ex) + 
+  geom_line(aes(time, stock, col=variable), lwd=1) + 
+  scale_color_discrete(labels=labels, 
+                       name="")
+
+```
+
+```{r quadshiftrate}
+shifts <- dt[, fraction_no_shift(harvest), by=c("replicate")]
+ave <- shifts[, mean(V1)]
+```
+
+Like the $\Pi_2$ adjustment cost based penalty, this quadratic cost based penalty shows periods of contant, strictly positive policy only `r ave * 100`% of the time, and exhibits the same kind of smoothing of more small adjustments that is seen in $\Pi_2$ scenario.
+
+Ignoring adjustment costs is worst than wrongly assuming adjustment costs
+--------------------------------------------------------------------------
+
+Figure S3 extends Figure 5 of the main text across all three functional forms of adjustment costs, $\Pi_{1-3}$.
+To reduce overplotting of Figure 5 we have also separated the distributions of dockside revenue and adjustment fees by scenario, such that the top row shows the distributions when the policy accounts for adjustment costs, and the bottom shows the policy when it does not (that is, the original @Reed1979 model applied to the scenario of costly adjustment).
+
+```{r Figure_S3, fig.cap="Distribution of profits from fishing and costs paid to adjustment.
+Distributions are shown when managing a system in which the adjustment costs present are determined by the model indicated, and compared to the same costs and profits of managing the same system using a Reed model, which ignores adjustment costs, and thus tends to pay much higher fees for adjustment.
+In contrast, the difference in profit after accounting for costs is only marginally less than the value derived by managing the population to optimize profits when ignoring adjustment costs (Reed model).", fig.width=8, fig.height=6, dependson="histogram-calc", dev=c("pdf", "svg", "png"), cache=FALSE}
 
@@
   } else {
-    return(assume[value])
+    return(paste(value))
+    #return(assume[paste(value)])
   }
@@
 
+write.csv(hist_dat, "components/data/figure5.csv")
 ```
 
-## To say that another way:
+Figure S4 extends the results shown in Figure 6 across different severities of adjustment cost, totalling from 10% up to 25% of the NPV of the stock.
+While the same qualitative pattern is observed in all cases, it is strongest in the higher penalties.
 
-```{r Figure_6, fig.cap="", dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
+```{r Figure_S4, fig.cap="Relative cost of ignoring adjustment costs when they are present ('ignoring', red) vs assuming the adjustment costs when they are absent ('assuming', blue), shown by penalty function over increasing magnitudes of cost.
+All values are relative to the cost-free adjustment optimum, NPV0.
+In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present.
+The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs.", dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE}
 
-who <- c("penalty_fn", "ignore_fraction", "assume_fraction", "reduction")
-table1 <- arrange(error_df[who], reduction) 
-names(table1) = c("penalty.fn", "ignoring", "assuming", "reduction")
-table1_long <- melt(table1, id = c('penalty.fn', 'reduction'))
-table1_long$reduction <- as.factor(table1_long$reduction)
-table1_long <- subset(table1_long, reduction != "0.3")
 ggplot(table1_long, aes(penalty.fn, value, fill = variable)) + 
@@
   xlab("Penalty function")
+write.csv(table1_long, "components/data/figureS4.csv")
 ```
 
-## Mismatches are even worse:
+Mismatched penalty functions
+----------------------------
 
-```{r Figure_7, fig.cap="", dev=c("pdf", "svg", "png"), cache=FALSE, dev.args=list(bg="transparent")}
+When policy costs are present, assuming the wrong functional form may or
+may not be worse than ignoring the presence of policy costs all together.
+Figure S5 considers several such cases.  The X axis labels indicate
+first which policy is being used to drive the harvest decisions, and
+then which penalty is actually being applied.  Thus $\Pi_1\_\Pi_2$ indicates
+a policy calculated under the linear ($\Pi_1$) costs, when the reality
+involves quadratic ($\Pi_2$) costs.  Though the coefficients of the ($\Pi_2$)
+costs have been scaled such that the net effect is the same, the inferred
+policies differ.  As a result, the value is slightly more than half of
+the optimal free solution when the expected reduction should only be 10% (panel A)
+less than optimal free based on the $c_i$ calibration. In this case, ignoring the costs all together
+is still worse than using $\Pi_1$ costs -- the red bar is lower than the blue.
+
+For fixed costs ($\Pi_3$), the reverse is true.  Because fixed costs increase the
+volatility of the optimal solution while $\Pi_2$ costs decrease it, simply
+ignoring the cost of adjustment all together results in a higher value
+than either assuming costs are quadratic ($\Pi_2$) when they are fixed ($\Pi_3$),
+or assuming they are fixed when they are quadratic.  Scenarios in which true costs are quadratic (regardless of what
+cost structure is assumed by the policy) do significantly worse than
+those that are not (i.e. all cases that assume quadratic but actually
+have linear or fixed costs).
+
+```{r Figure_S5, fig.cap="Mismatches.
+X axis labels indicate the model used to derive the policy, followed by the model used to simulate the penalty.
+Blue bars show the net present value of that scenario.
+Compare to red bars, which show the consequence of using a policy that ignores costs all together in the same scenario (i.e.
+costs as indicated by second code), rather than assuming the policy indicated by the first code in the pair.
+All values are scaled to a fraction of the adjustment free net present value.", dev=c("pdf", "svg", "png"), fig.width=7}
 who <- c("penalty_fn", "ignore_fraction", "mismatched_fraction", "reduction")
@@
 
+ggplot(filter(table2_long, reduction==0.25), 
+  aes(penalty.fn, value, fill = variable)) + 
+  geom_bar(stat="identity", position="dodge") + 
+  facet_wrap(~reduction, scales="free_y") +
+  scale_x_discrete(labels = c('L1_L2' = substitute(paste(Pi[1],"_", Pi[2])), 
+                              'L2_L1' =  substitute(paste(Pi[2],"_", Pi[1])),
+                              'L1_fixed' = substitute(paste(Pi[1],"_", Pi[3])), 
+                              'fixed_L1' =  substitute(paste(Pi[3],"_", Pi[1])),
+                              'fixed_L2' = substitute(paste(Pi[3],"_", Pi[2])), 
+                              'L2_fixed' =  substitute(paste(Pi[2],"_", Pi[3])))) + 
+  xlab("Penalty function")
+write.csv(table2_long, "components/data/figureS5.csv")
+```
+
+These patterns hold across the different size reductions shown (from 10%
+to 25%, Figure S6 panels a-d respectively), though net present value becomes negative under the quadratic
+form for the larger penalties as costs paid for adjustments exceed
+profits derived from harvest.  (Though optimal solutions will always
+avoid negative net present values, these scenarios in which policies are
+applied under conditions other than assumed in the optimality calculation
+have no such guarantee.) For each scenario, results are averaged over
+100 replicates.
+
+```{r Figure_S6, fig.cap="Effect of varying severity of adjustment costs on mismatches.
+Successive panels show increasing reduction of the net present value by increasing penalty coefficients: e.g.
+a policy in the first panel would lose only 10% (panel A) of its net present value to adjustment costs if it had the correct form of those costs, as determined by the choice of penalty coefficient.
+Plots structured as in figure 7, which corresponds to the fourth panel", dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE}
 ggplot(table2_long, aes(penalty.fn, value, fill = variable)) + 
@@
                               'L2_fixed' =  substitute(paste(Pi[2],"_", Pi[3])))) + 
-  xlab("Penalty function as: assumed_reality") + theme_tufte(base_size=14)
+  xlab("Penalty function")
 ```

### 2014-12-24 manuscripts/supplement.Rmd
minor edits from Paul, flushing out supplement

@@
 ---
-title: Optimal management of a stochastically varying population when policy adjustment is costly
+title: "Supplement to: Optimal management of a stochastically varying population when policy adjustment is costly"
 author: 
@@
 
+```{r configure, include=FALSE, cache=FALSE}
+library("methods")
+library("knitr")
+basename <- "supplement"
+opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
+               cache.path = paste("components/cache/", basename, "/", sep=""))
+opts_chunk$set(cache = 2)
+opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, 
+               comment = NA, verbose = TRUE, echo=FALSE)
+# PDF-based figures
+opts_chunk$set(dev='pdf')
+fig.cache <- TRUE
+
+library("rmarkdown")
+library("pdgControl")
+library("reshape2")
+library("plyr")
+library("ggplot2")
+library("data.table")
+library("pander")
+library("cboettigR")
+library("ggthemes")
+library("snowfall")
+library("tidyr")
+library("dplyr")
+options(digits=2)
+
+theme_set(theme_tufte(base_size=12) + theme(axis.line = element_line()))
+```
+
 \appendix
+\renewcommand{\thefigure}{S\arabic{figure}}
 
@@
 
-Though this results in an effect that is less pronounced, the stock dynamics clearly reflect the same general trends observed in Figure 3: the quadratic costs ($\Pi_2$) show a clear smoothing of the variation in stock dynamics, while the fixed fee $\Pi_3$ results in exaggerated fluctionations in the stock sizes.
-It is worth noting how changes in policy costs alone, such as introducing or rising fixed costs, can have important knock-on effects to population dynamics such as increased variance, a recent phenomenon observed in important fisheries that has recieved much attention elsewhere [@Anderson2008].
+Though this results in an effect that is less pronounced, the stock dynamics of Figure S1 reflect the same general trends observed in Main text Figure 3; e.g.
+the fixed fee $\Pi_3$ results in the most exaggerated fluctuations in the stock sizes.
+It is worth noting how changes in policy costs alone, such as introducing or rising fixed costs, can have important knock-on effects to population dynamics such as increased variance, a recent phenomenon observed in important fisheries that has received much attention elsewhere [@Anderson2008].
 
-```{r StockDynamics, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=5, fig.width=8, cache = fig.cache, dev=c("pdf", "svg", "png")}
+```{r Figure_S1, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=5, fig.width=8, cache = fig.cache, dev=c("pdf", "svg", "png")}
 
@@
 
-```{r StockStats, fig.cap="Variance and autocorrelation of stock dynamics, as a function of the penalty coefficient.
-Adjustment penalty is calculated as percentage of the maximum expected $NPV$ in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png")}
+```{r Figure_S2, fig.cap="Variance and autocorrelation of stock dynamics, as a function of the penalty coefficient.
+Adjustment penalty is calculated as percentage of the maximum expected $NPV$ in the basic case with no policy adjustment costs.", fig.height=4, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png")}
 
@@
 
-Recall that in our model definition, stock sizes are measured before harvest ($h_t$ being determined after observing stock size
-$x_t$) and thus show less influence of the policy cost than the harvest itself.
+Recall that in our model definition, stock sizes are measured before
+harvest ($h_t$ being determined after observing stock size $x_t$) and
+thus show less influence of the policy cost than the harvest itself.
+
+Figure S2 shows the same summary statistics illustrating the trends
+of increasing adjustment costs on the _stock_ dynamics, instead of the
+_harvest_ dynamics shown in Figure 4 of the main text.  Note that 
+the variance in stock sizes under the quadratic penalty ($\Pi_2$) increases,
+while in Figure 4 of the main text the corresponding variance in the
+harvest decreases. Under costly adjustment, the undershooting behavior
+of the $\Pi_2$ harvest policy cannot absorb as much of the natural 
+fluctuation, resulting in increased variation in the stock sizes.
 
@@
 
-Figure 3 of the main text shows a single stochastic realization.  Here we provide a sample of further realizations (including both stock and harvest dynamics).  Full
+Figure 3 of the main text shows only a single stochastic realization.  Here in
+Figure S3 we provide a sample of further realizations (including both
+stock and harvest dynamics).
 
-```{r Figure_S2, dependson="tidy", fig.cap="Multiple realizations of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=10, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png"), cache=FALSE}
+```{r Figure_S3, dependson="tidy", fig.cap="Multiple realizations of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=10, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png"), cache=FALSE}
 
@@
 
-write.csv(ex, "components/data/figure_s2.csv")
+write.csv(ex, "components/data/figure_s3.csv")
 ```
@@
 
-```{r quadraticcosts}
+Figure S4 shows that adding quadratic terms to the cost of fishing effort directly, as in @Lewis1981 or @McGough2009, results in a similar smoothing effect as we observe in quadratic adjustment costs ($\Pi_2$), which contrasts sharply with the patterns we observe in other functional forms.
+This case corresponds to a profit function defined as:
+
+$$\Pi_4(N_t,h_t) = p h_t -  c_0 E_t - c_4 E_t^2$$
+
+Where $c_4$ is calibrated as in the case of the other coefficients to induce the fixed reduction of net present value relative to $NPV_0$.
+
+```{r quadraticcosts, include=FALSE, message=FALSE}
 
@@
 
-```{r Figure_S1, dev=c('pdf', 'svg'), cache=FALSE}
+```{r Figure_S4, dev=c('pdf', 'svg'), cache=FALSE, fig.cap="Quadratic costs to fishing effort show a similar pattern of smoothing to that which we observe in the quadratic adjustment cost model."}
 
@@
 
-Like the $\Pi_2$ adjustment cost based penalty, this quadratic cost based penalty shows periods of contant, strictly positive policy only `r ave * 100`% of the time, and exhibits the same kind of smoothing of more small adjustments that is seen in $\Pi_2$ scenario.
+Like the $\Pi_2$ adjustment cost based penalty, this quadratic cost based penalty shows periods of constant, strictly positive policy only `r ave * 100`% of the time, and exhibits the same kind of smoothing of more small adjustments that is seen in $\Pi_2$ scenario.
 
@@
 
-Figure S3 extends Figure 5 of the main text across all three functional forms of adjustment costs, $\Pi_{1-3}$.
-To reduce overplotting of Figure 5 we have also separated the distributions of dockside revenue and adjustment fees by scenario, such that the top row shows the distributions when the policy accounts for adjustment costs, and the bottom shows the policy when it does not (that is, the original @Reed1979 model applied to the scenario of costly adjustment).
+Figure S5 extends Figure 5 of the main text across all three functional forms of adjustment costs, $\Pi_{1-3}$.
+To reduce over-plotting of Figure 5 we have also separated the distributions of dockside revenue and adjustment fees by scenario, such that the top row shows the distributions when the policy accounts for adjustment costs, and the bottom shows the policy when it does not (that is, the original @Reed1979 model applied to the scenario of costly adjustment).
 
-```{r Figure_S3, fig.cap="Distribution of profits from fishing and costs paid to adjustment.
+```{r Figure_S5, fig.cap="Distribution of profits from fishing and costs paid to adjustment.
 Distributions are shown when managing a system in which the adjustment costs present are determined by the model indicated, and compared to the same costs and profits of managing the same system using a Reed model, which ignores adjustment costs, and thus tends to pay much higher fees for adjustment.
@@
 
-write.csv(hist_dat, "components/data/figure5.csv")
+write.csv(hist_dat, "components/data/figureS5.csv")
 ```
 
-Figure S4 extends the results shown in Figure 6 across different severities of adjustment cost, totalling from 10% up to 25% of the NPV of the stock.
+Figure S6 extends the results shown in Figure 6 across different severities of adjustment cost, totaling from 10% up to 25% of the $NPV$ of the stock.
 While the same qualitative pattern is observed in all cases, it is strongest in the higher penalties.
 
-```{r Figure_S4, fig.cap="Relative cost of ignoring adjustment costs when they are present ('ignoring', red) vs assuming the adjustment costs when they are absent ('assuming', blue), shown by penalty function over increasing magnitudes of cost.
+```{r Figure_S6, fig.cap="Relative cost of ignoring adjustment costs when they are present ('ignoring', red) vs assuming the adjustment costs when they are absent ('assuming', blue), shown by penalty function over increasing magnitudes of cost.
 All values are relative to the cost-free adjustment optimum, NPV0.
@@
   xlab("Penalty function")
-write.csv(table1_long, "components/data/figureS4.csv")
+write.csv(table1_long, "components/data/figureS6.csv")
 ```
@@
 may not be worse than ignoring the presence of policy costs all together.
-Figure S5 considers several such cases.  The X axis labels indicate
+Figure S7 considers several such cases.  The X axis labels indicate
 first which policy is being used to drive the harvest decisions, and
@@
 
-```{r Figure_S5, fig.cap="Mismatches.
+```{r Figure_S7, fig.cap="Mismatches.
 X axis labels indicate the model used to derive the policy, followed by the model used to simulate the penalty.
@@
   xlab("Penalty function")
-write.csv(table2_long, "components/data/figureS5.csv")
+write.csv(table2_long, "components/data/figureS7.csv")
 ```
@@
 These patterns hold across the different size reductions shown (from 10%
-to 25%, Figure S6 panels a-d respectively), though net present value becomes negative under the quadratic
+to 25%, Figure S8 panels a-d respectively), though net present value becomes negative under the quadratic
 form for the larger penalties as costs paid for adjustments exceed
@@
 
-```{r Figure_S6, fig.cap="Effect of varying severity of adjustment costs on mismatches.
+```{r Figure_S8, fig.cap="Effect of varying severity of adjustment costs on mismatches.
 Successive panels show increasing reduction of the net present value by increasing penalty coefficients: e.g.

### 2014-12-24 manuscripts/manuscript.Rmd
add nimbios ack

@@
 
-This project arose out of a NIMBioS working group, "Pretty Darn Good Control".
-The authors acknowledge helpful discussions and input from working group
-co-organizers Megan Donahue and Carl Toews, and participants Marie-Josee Fortin, 
-Dan Ryan, Frank Doyle, Claire Paris, Iadine Chades and Mandy Karnauskas.
+This work was assisted through participation in "Pretty Darn Good Control" Investigative Workshop at the National Institute for Mathematical and Biological Synthesis, sponsored by the National Science Foundation through NSF Award #DBI-1300426, with additional support from The University of Tennessee, Knoxville.
+The authors acknowledge helpful discussions and input from working group co-organizers Megan Donahue and Carl Toews, and participants Marie-Josee Fortin, Dan Ryan, Frank Doyle, Claire Paris, Iadine Chades and Mandy Karnauskas.
 We also acknowledge the following support: NSF Grant DBI-1306697 (CB), ...

### 2015-01-15 manuscripts/manuscript.Rmd
working on edits from paul and mike

@@
     affiliation: UCD
-  - name: Paul Armsworth 
+  - name: Paul R. Armsworth 
     affiliation: UTKEEB
@@
           fishing quotas through time) could take different forms. For example,
-          these costs may respond to the size of the change being implemented or
+          these costs may respond to the size of the change being implemented, or
           there could be a fixed cost any time a quota change is made. We show
@@
 In other words, whatever gains are available from fine-tuning a
-policy prescription to reflect environmental variation more closely
+policy prescription to more closely reflect environmental variation
 should be traded off against potential costs associated with the more
-interventionist approach to management this would require.
+responsive approach to management this would require.
 
@@
 for this species there could be substantial transaction costs involved
-in reaching agreement over any quota change, which could contribute to
+in reaching agreement over any quota change, or constraints on the frequency
+with which the those changes could occur.  Either could contribute to
 the observed quota stability. Such patterns of variable stocks managed
@@
 stock. In poor recruitment years, the quota is set to zero and no fishing
-is allowed. But any time there is a good recruitment pulse, a quota is
+is allowed. Any time a recruitment pulse exceeds the escapement threshold, a quota is
 set that allows the fishery to exactly compensate through harvesting,
@@
 profits from fishing from more finely tracking recruitment variations
-with the growing costs associated with adjusting policies quickly to do
+with the growing costs associated with adjusting policies frequently to do
 so. The policy adjustment costs involved could reflect pure administrative
@@
 empirical work to estimate that. Therefore, we scope three candidate
-functional forms that represent different assumptions about how these
+functional forms that represent qualitatively different assumptions about how these
 costs operate to determine whether the results we obtain are sensitive
@@
 Eqn. \eqref{eq:annual_netrevenue}, $p$ is the price per unit harvest and
-$c_0$ the cost of fishing and, to simplify the presentation of results,
+$c_0$ the cost of fishing per unit effort and, to simplify the presentation of results,
 we assume that these are constants with $p>0$ and $c_0>0$.
@@
 the fish population is 1 and the equilibrium biomass for the equivalent
-deterministic model without harvesting is 10; (specifically, $A=$ `r pars[1]` and
-$B=$ `r pars[2]` in Eqn \eqref{eq:state_equation}. To characterize environmental variability, we
+deterministic model without harvesting is `r K`; (specifically, $A=$ `r pars[1]` and
+$B=$ `r pars[2]` in Eqn \eqref{eq:state_equation}). To characterize environmental variability, we
 assume multiplicative shock $Z_t$ is distributed log-normally with
@@
 In the supplement we illustrate that the qualitative patterns observed
-here are not sensitive to the specific choices for these parameter values.
+here are not sensitive to the specific choices of these parameter values.
 
@@
 problem that we solve using backwards recursion via Bellman's equation.
-We denote the resulting state-dependent, optimal control as $h_0^{\ast}$.
+We denote the resulting state-dependent, optimal control as $\mathbf{h}_0^{\ast}$.
 We solve this problem on a finite time horizon of $T =$ `r OptTime` using
-value iteration [@Mangel1988; @Clark2000].
-
-Note that this problem is much larger computationally than the classic 
-formulation of this stochastic dynamic programming problem for a single stock.
-Whereas the classic problem considers each of $Q$ possible discrete quotas
-for $S$ possible stock values at each time $t$, for a search space of size $S \times Q$
-per timestep;  this formulation must also consider all possible values of quota
-in the _previous_ time step: a total of $S \times Q \times Q$ configurations.
+value iteration [@Mangel1988; @Clark2000]. (Longer horizon times have no
+qualitative difference but stretch the plots making it more difficult
+to visualize the fluctuations.)
 
@@
 new objective function $NPV_i$ similar to that in Eqn. \eqref{eq:objective}.
-
 We note that the fixed cost has conceptual analogues to the set-up cost of
@@
 function $\max NPV_i$, we denote the corresponding optimal control
-policy $h_i^*$.
+policy as the vector $\mathbf{h}_i^*$.
 
-In the Supplementary Material, we compare our results with 
-more conventional fisheries economic formulation in which additional
-costs are applied to the control variables themselves, as opposed to
-adjustments to the controls: $\Pi_4 (N_t,h_t) = p h_t -  c_0 E_t-c_4E_t^2$. 
-Additional costs of this form tend to have a smoothing effect on optimal quotas, but also change
-the long-term average stock size or quota size that is optimal.
+Note that this problem is much larger computationally than the classic 
+formulation of this stochastic dynamic programming problem for a single stock.
+Whereas the classic problem considers each of $Q$ possible discrete quotas
+for $S$ possible stock values at each time $t$, for a search space of size $S \times Q$
+per timestep;  this formulation must also consider all possible values of quota
+in the _previous_ time step: since the costs that will follow depend on whether
+and by how much the harvest policy will change. This creates a total of
+$S \times Q \times Q$ configurations.
 
-<!-- State conclusion of this supplement here! -->
+In the Supplementary Material, we compare our results with more
+conventional fisheries economic formulation in which additional costs are
+applied to the control variables themselves, as opposed to adjustments to
+the controls: $\Pi_4 (N_t,h_t) = p h_t -  c_0 E_t-c_4E_t^2$.  Additional
+costs of this form tend to have a smoothing effect on optimal quotas,
+but also change the long-term average stock size or quota size that
+is optimal.
 
@@
 
-Before we can compare the policy dynamics resulting from each of these
-functional froms, we must be careful to ensure that we are only varying
-the _structure_ of the adjustment penalty and not the overall magnitude.
-At the extremes, a large enough adjustment cost can ensure a constant 
-policy, regardless of the structure; while a small enough one can be ignored
-regardless.  Defining this calibration correctly is thus key to the entire
-analysis.  Fortunately, the optimal control framework provides a completely
-natural way to make this comparison: in terms of the _economic value_
-(measured by $NPV$) of the stock in each case.  We will calibrate this relative
-to economic value of the stock when adjustments to the policy are free ($NPV_0$).
+Each policy adjustment cost function is characterized in terms of a
+cost coefficient $c_i$. However, $c_i$ takes different units for each
+functional form. Therefore, if seeking to compare the relative effect
+of each penalty function on optimal management, it is unclear what
+parameter values should be used. To address this issue, we calibrate
+choices of $c_i$ so that each has a comparable impact on the optimal
+fishery $NPV$.  Fortunately, the optimal control framework provides a
+completely natural way to make this comparison: in terms of the _economic
+value_ (measured by $NPV$) of the stock in each case.  We will calibrate
+our realized economic value under each policy relative to economic value
+of the stock when adjustments to the policy are free ($NPV_0$).
 
-Each policy adjustment cost function is characterized in terms of
-a cost coefficient $c_i$. However, $c_i$ takes different units for each
-functional form. Therefore, if seeking to compare the relative effect of
-each penalty function on optimal management, it is unclear what
-parameter values should be used. To address this issue, we calibrate
-choices of $c_i$ so that each has a comparable impact on the optimal NPV
-fishery.
-
-Figure 2 shows the calibration graphically. Each curve plots the change
-in maximum expected $NPV$ for a given penalty function as the penalty cost
-parameter is increased. In each case, the figure shows maximum expected
+Figure 2 shows the calibration graphically. Each curve plots the change in
+maximum expected $NPV$ for a given cost structure as the $c_i$ coefficient
+is increased. In each case, the figure shows maximum expected
 NPV with policy adjustment costs as a proportion of the maximum expected
 NPV available in the basic problem $NPV_0({\bf h_0^*})$ without policy
-adjustment costs. The $c_i$ values are given in Table 1.
-
-```{r table_1, results="asis"}
-pandoc.table(print_npv)
-```
+adjustment costs.
 
@@
 To compare the impact of penalty functions on optimal management across
-the different functional forms, we select penalty cost coefficients that
-induce the same reduction in maximum expected NPV. For example, the
-dashed vertical lines in Figure 2 map the needed cost coefficient $c_i$,
-for each penalty function, such that the fishery is worth `r 100*(1-reduction)`% of its
-unconstrained value when optimally managed. We focus our examination of the models on how
-the type and severity of policy adjustment costs affects the optimal management strategy.
+the different functional forms, we select penalty cost coefficients
+that induce the same reduction in maximum expected NPV. For example,
+the dashed vertical line in Figure 2 maps the needed cost coefficient
+$c_i$, for each penalty function, such that the fishery is worth `r
+100*(1-reduction)`% of its unconstrained value when optimally managed.
 
@@
   labs(x="time", y="stock size", title = "Example Harvest Dynamics")  +
-  scale_color_discrete(labels=c("With Penalty", "Reed Solution"), name="") +
-  scale_linetype_discrete(labels=c("With Penalty", "Reed Solution"), name="")
+  scale_color_discrete(labels=c("Adjustment penalty", "No penalty"), name="") +
+  scale_linetype_discrete(labels=c("Adjustment penalty", "No penalty"), name="")
 
@@
 
-Figure 3 illustrates how the different forms of adjustment cost can impact
-the optimal harvest policy. Corresponding stock sizes can be seen in the
-supplement.  Each panel is generated against the same sequence of 
-environmental variability so that they can be compared directly.  The harvest policy chosen
-shows a systematic deviations from the penalty free optimum, depending on
-the nature of the cost.  In each case, the optimal solution without any
-adjustment cost is shown with the policy induced by optimization
-under the given adjustment penalty (equivalent to a `r 100*reduction`%
-reduction in maximum expected NPV) overlaid in blue.
+Figure 3 illustrates how the different forms of adjustment cost can
+impact the dynamics of the optimal harvest policy. Corresponding stock
+sizes can be seen in the supplement.  Each panel is generated against the
+same sequence of environmental variability so that they can be compared
+directly.  The harvest policy chosen shows a systematic deviations from
+the adjustment cost free optimum, depending on the structure of the cost function.  In each
+case, the optimal solution without any adjustment cost is shown with
+the policy induced by optimization under the given cost structure 
+(equivalent to a `r 100*reduction`% reduction in maximum expected NPV)
+overlaid in blue.
 
-The first panel shows a typical pattern resulting from linear adjustment costs ($\Pi_1$).
-The optimal policy tends to avoid very small policy adjustments, resulting in
-periods of a constant policy followed by sudden bursts of adjustment.
-This results in a relatively step-like policy pattern. In contrast, the
-second formulation (quadratic costs, $\Pi_2$) disproportionately penalizes large policy
-adjustments. The corresponding optimal policy is typified by the middle panel, responding
-to each of the fluctuations in stock, made by the cost-free policy, but with smaller 
-magnitude response than the equivalent cost-free optimal solution. This results
-in a smoother $h_t$ curve, one that undershoots the larger oscillations
-seen in the cost-free optimum in favor of a policy that changes
-incrementally each year. Finally, the optimal policy for the third,
-'fixed fee' formulation ($\Pi_3$) only makes large adjustments, as one
-might expect, because the magnitude of the adjustment made is not
-reflected in the resulting penalty.
+The first panel shows a typical pattern resulting from linear adjustment
+costs ($\Pi_1$).  The optimal policy tends to avoid very small policy
+adjustments, resulting in periods of a constant policy followed by
+sudden bursts of adjustment.  This results in a relatively step-like
+policy pattern. In contrast, the second formulation (quadratic costs,
+$\Pi_2$) disproportionately penalizes large policy adjustments. The
+corresponding optimal policy is typified by the middle panel, responding
+to each of the fluctuations in stock, made by the cost-free policy, but
+with smaller magnitude response than the equivalent cost-free optimal
+solution. This results in a smoother $h_t$ curve, one that undershoots
+the larger oscillations seen in the cost-free optimum in favor of a policy
+that changes incrementally each year. Finally, the optimal policy for the
+third, 'fixed fee' formulation ($\Pi_3$) only makes large adjustments,
+as one might expect, because the magnitude of the adjustment made is
+not reflected in the resulting cost.
 
-These patterns are consistent across stochastic replicates over a range
-of penalty magnitudes. The comparisons shown in Figure 3 are for one 
-realization (i.e. a particular sequence of random number draws representing
-environmental variability) and are made for one particular magnitude of 
-policy adjustment costs (Calibrated to equal to `r reduction *100`% of the 
-maximum expected net present valuein the base case ($NPV_0({\bf h_0^*})$,
-as discussed in Figure 2, permitting comparisons between different forms).
-To demonstrate this, we solved for the optimal policy under each of the
-three adjustment cost scenarios for `r length(c0)` different penalty 
-coefficients. For each resulting policy, we then simulated 50 stochastic
-replicates of the stock dynamics managed under that policy.  To summarize
-the patterns shown in Figure 3 and characterize the impact of increasingly
-large fraction of the economic value (NPV) being consumed by policy
-adjustment costs, we examine the response of several summary statistics
-to increasing adjustment penalties (as a fraction of the adjustment-free value)
-in Figure 4.  We show the impact of policy adjustment costs on the
-variance & autocorrelation of the harvests through time.
+These patterns are consistent across stochastic replicates over a
+range of penalty magnitudes. The comparisons shown in Figure 3 are
+for one realization (i.e. a particular sequence of random number draws
+representing environmental variability) and are made for one particular
+magnitude of policy adjustment costs, which have been calibrated to equal
+to `r reduction *100`% of $NPV_0({\bf h_0^*})$.  To demonstrate this,
+we solved for the optimal policy under each of the three adjustment
+cost scenarios for `r length(c2)` different $c_i$ coefficients. For each
+resulting policy, we then simulated 50 stochastic replicates of the stock
+dynamics managed under that policy.  To summarize the patterns shown
+in Figure 3 and characterize the impact of increasingly large fraction
+of the economic value (NPV) being consumed by policy adjustment costs,
+we examine the response of several summary statistics to increasing
+adjustment penalties (as a fraction of the adjustment-free value) in
+Figure 4.  We show the impact of policy adjustment costs on the variance &
+autocorrelation of the harvests through time.
 
@@
 
-While the optimization guarentees that on average, the policy in the first simulation
-should outperform that of the second, it does not tell us by how much.  These simulations
-thus give us a lense to examine the magnitude of this effect.
+While the optimization ensures that on average, the policy in the first
+simulation should outperform that of the second, it does not tell us by
+how much.  These simulations thus allow us to quantify this effect.
 
-We provide 100 replicates of each kind for each of the three forms
-$\Pi_{1-3}$ (in which each ensemble of 100 replicates uses the same sequence of random seeds).
-For each, we record (a) the dockside profits derived from fishing as well
-as (b) any fees paid to make adjustments to the policy.  In the first kind of 
-simulation, dockyard profits are almost less than in the second for a given stochastic
-replicate, since the latter optimizes the expected dockside NPV.  However, the costs
-paid for adjustment are almost always less in the first scenario as well, since
-this solution explicitly tries to avoid higher adjustment costs.  We visualize this
-pattern in the distributions shown in Figure 5 (focusing on $\Pi_1$ for simplicity,
-as the pattern in $\Pi_2$ and $\Pi_3$ is similar, see Supplementary Material.)
+We provide 100 replicates of each kind of scenario for each of the
+three forms $\Pi_1$, $\Pi_2$ & $\Pi_3$.  For each, we record (a)
+the dockside profits derived from fishing as well as (b) any fees paid
+to make adjustments to the policy.  In the first kind of simulation,
+dockside revenues are almost less than in the second for a given
+stochastic replicate, since the latter optimizes the expected NPV.
+However, the costs paid for adjustment are almost always less in the
+first scenario as well, since this solution explicitly tries to avoid
+higher adjustment costs.  We visualize this pattern in the distributions
+shown in Figure 5 (focusing on $\Pi_1$ for simplicity, as the pattern
+in $\Pi_2$ and $\Pi_3$ is similar, see Supplementary Material.)
 
-Figure 5 shows that the difference in dockside revenue (labelled "profits" in the figure) 
-between these two scenarios 
-(green vs purple distributions) is very small, while a larger difference exists between
-the costs paid for making policy adjustments (red vs blue). This is predicted by the optimization: 
-the first scenario must outperform (or at least equal) the NPV of the second scenario
-in aggregate, and as it cannot do so through higher profits it must do so through lower
-costs.  Interestingly, for this set of parameters very little is lost in dockside revenue.
-This suggests that the impact of assuming costs are present when they are not is rather small:
-since the dockside revenue is none-the-less near optimal.  This also suggests that the 
-converse error: ignoring costs when they are present, is more severe.
+Figure 5 shows that the difference in dockside revenue (labeled "profits"
+in the figure) between these two scenarios (green vs purple distributions)
+is very small, while a larger difference exists between the costs paid
+for making policy adjustments (red vs blue). This is predicted by the
+optimization: the first scenario must outperform (or at least equal)
+the NPV of the second scenario in aggregate, and as it cannot do so
+through higher profits it must do so through lower costs.  Interestingly,
+for this set of parameters very little is lost in dockside revenue.
+This suggests that the impact of assuming costs are present when they
+are not is rather small: since the dockside revenue is none-the-less
+near optimal.  This also suggests that the converse error: ignoring
+costs when they are present, is more severe.
 
@@
                               'fixed' = substitute(paste(Pi[3])))) + 
-  xlab("Penalty function")
+  xlab("Penalty function") + 
+  ylab(expression(NPV[0]))
 write.csv(table1_long, "components/data/figure6.csv")
@@
 
-We visualize the differences between these two errors directly in Figure 6. Subtracting revenue from
-adjustment costs and considering only the mean across the replicates, we can dervive the expected $NPV$ 
-in each case.  To standardize against a common baseline, we will express this value as a fraction of 
-the cost-free optimum, $NPV_0$. Note that we have calibrated the optimal solutions to anticipate that
-`r reduction*100`% of their $NPV$ would go into adjustment costs. When these adjustment costs are not 
-actually present (blue bars, Fig 6), we thus expect a $NPV$ higher than the anticipated `r (1 -reduction)*100`%
-but not quite as high as the optimal policy for that scenario (100%).  When adjustment costs are present
-but the policy assumes that they are not (red bars), we would expect the $NPV$ to be less than `r (1 - reduction) * 100`%
-of $NPV_0$ (since that's as good as the optimal solution for this scenario can do).
+We visualize the differences between these two errors directly in Figure
+6. Subtracting revenue from adjustment costs and considering only the mean
+across the replicates, we can dervive the expected $NPV$ in each case.
+To standardize against a common baseline, we will express this value as a
+fraction of the cost-free optimum, $NPV_0$. Note that we have calibrated
+the optimal solutions to anticipate that `r reduction*100`% of their
+$NPV$ would go into adjustment costs. When these adjustment costs are
+not actually present (blue bars, Fig 6), we thus expect a $NPV$ higher
+than the anticipated `r (1 -reduction)*100`% but not quite as high as
+the optimal policy for that scenario (100%).  When adjustment costs are
+present but the policy assumes that they are not (red bars), we would
+expect the $NPV$ to be less than `r (1 - reduction) * 100`% of $NPV_0$
+(since that's as good as the optimal solution for this scenario can do).
 
-Figure 6 shows that across each penalty form $\Pi{1-3}$, the economic impact
-of ignoring adjustment costs when they are present is higher than accounting
-for them when they are absent. This holds even after accounting for effect 
-described above: the red bars are consistently well below (`r (1-reduction)`),
-while the blue bars are barely below 1.
-We also see that the impacts on net present value of the fishery of
-incorrectly assuming or ignoring policy adjustment costs are most severe
-when these costs are assumed to scale quadratically with the size of the
-policy change being implemented ($\Pi_2$).
-In the Supplementary Materials we show that pattern holds across different
-severity of adjustment costs (robust to choice of $c_i$), though the larger
-the adjustment cost, the greater the difference between these two errors.
+Figure 6 shows that across each penalty form $\Pi_1$, $\Pi_2$ & $\Pi_3$,
+the economic impact of ignoring adjustment costs when they are present
+is higher than accounting for them when they are absent. This holds even
+after accounting for effect described above: the red bars are consistently
+well below the `r (1-reduction)*100`% of $NPV_0$, while the blue bars
+are barely below $NPV_0$ (a value of 1 on the vertical axis).  We also
+see that the impacts on net present value of the fishery of incorrectly
+assuming or ignoring policy adjustment costs are most severe when these
+costs are assumed to scale quadratically with the size of the policy
+change being implemented ($\Pi_2$).  In the Supplementary Materials we
+show that pattern holds across different severity of adjustment costs
+(robust to choice of $c_i$), though the larger the adjustment cost,
+the greater the difference between these two errors.
 
-Note that this analysis does not consider the possibility that an adjustment cost
-is present, but of a different functional form than the policy assumes.  Not surprisingly,
-the consequences of managing under the wrong functional form can be as or more severe than
-simply ignoring adjustment costs in the optimization all-together.  We illustrate several
-of these mismatch errors in the Supplementary Material.
+Note that this analysis does not consider the possibility that an
+adjustment cost is present, but of a different functional form than the
+policy assumes.  The consequences of managing under the wrong functional
+form can be as or more severe than simply ignoring adjustment costs in
+the optimization altogether.  We illustrate several of these mismatch
+errors in the Supplementary Material.
 
@@
 The biggest differences between the representations of policy adjustment
-cost that we consider are between those that have a smoothing effect
-on annual quotas and those that do not. The few past studies that
-incorporate policy adjustment costs in models of fisheries or other environmental management contexts [@Feichtinger1994; @Wirl1999] have assumed costs of
+cost that we consider are between those that have a smoothing effect on
+annual quotas and those that do not. The few past studies that incorporate
+policy adjustment costs in models of fisheries or other environmental
+management contexts [@Feichtinger1994; @Wirl1999] have assumed costs of
 policy adjustment increased as a quadratic function of the magnitude of
@@
 expensive to make. Including costs of this form smooths inter-annual
-variation in the catch quotas that would be recommended. Also, the catches and remaining stock sizes
-corresponding to optimal management become more autocorrelated in time,
-because it takes the fishery longer to harvest down peaks in abundance
-that follow large recruitment pulses. The effects of smoothing here are
-similar to those predicted when assuming the cost per unit effort is
-increasing in the amount of effort expended (e.g., @Lewis1981, @McGough2009; 
-see Supporting Information for a summary of the relevant
-results) as opposed to associating extra costs with changes to policy
-*per se*. Smoothing effects of this type are what one might have
+variation in the catch quotas that would be recommended. Also, the catches
+and remaining stock sizes corresponding to optimal management become more
+autocorrelated in time, because it takes the fishery longer to harvest
+down peaks in abundance that follow large recruitment pulses. The effects
+of smoothing here are similar to those predicted when assuming the cost
+per unit effort is increasing in the amount of effort expended (e.g.,
+@Lewis1981, @McGough2009; see Supporting Information for a summary of the
+relevant results) as opposed to associating extra costs with changes to
+policy *per se*. Smoothing effects of this type are what one might have
 expected when including policy adjustment costs.
@@
 
-This work was assisted through participation in "Pretty Darn Good Control" Investigative Workshop at the National Institute for Mathematical and Biological Synthesis, sponsored by the National Science Foundation through NSF Award #DBI-1300426, with additional support from The University of Tennessee, Knoxville.
-The authors acknowledge helpful discussions and input from working group co-organizers Megan Donahue and Carl Toews, and participants Marie-Josee Fortin, Dan Ryan, Frank Doyle, Claire Paris, Iadine Chades and Mandy Karnauskas.
-We also acknowledge the following support: NSF Grant DBI-1306697 (CB), ...
+This work was assisted through participation in "Pretty Darn Good Control"
+Investigative Workshop at the National Institute for Mathematical and
+Biological Synthesis, sponsored by the National Science Foundation through
+NSF Award #DBI-1300426, with additional support from The University of
+Tennessee, Knoxville.  The authors acknowledge helpful discussions and
+input from working group co-organizers Megan Donahue and Carl Toews, and
+participants Marie-Josee Fortin, Dan Ryan, Frank Doyle, Claire Paris,
+Iadine Chades and Mandy Karnauskas.  We also acknowledge the following
+support: NSF Grant DBI-1306697 (CB), ARC DECRA (DE130100572) and The
+ARC Centre of Excellence for Environmental Decisions (MB), ...
 

### 2015-01-15 manuscripts/supplement.Rmd
add nimbios ack
supplemental data files
working on edits from paul and mike

@@
 
+write.csv(dt_s, "components/data/figureS1.csv")
 ```
@@
 
+write.csv(stock_stats, "components/data/figureS2.csv")
+
 ```
@@
 Recall that in our model definition, stock sizes are measured before
-harvest ($h_t$ being determined after observing stock size $x_t$) and
+harvest ($h_t$ being determined after observing stock size $N_t$) and
 thus show less influence of the policy cost than the harvest itself.
@@
 
-write.csv(ex, "components/data/figure_s3.csv")
+write.csv(ex, "components/data/figureS3.csv")
 ```
@@
 ```{r quadraticcosts, include=FALSE, message=FALSE}
-
 source("components/quad_costs.R")

### 2015-01-15 manuscripts/manuscript.Rmd
editing text, captions

@@
 
-```{r Figure_3, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=5, fig.width=8, cache = fig.cache, dev=c("pdf", "svg", "png")}
+```{r Figure_3, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.
+When costs vary linearly with the size of the adjustment ($\\Pi_1$), periods with no adjustment are more common than if adjustments were free.
+When costs vary quadratically with adjustment size ($\\Pi_2$), small adjustments are relatively cheap and thus the resulting optimal policy always changes, but by a smaller amount than if adjustments were free.
+When adjustments incur a fixed fee independent of size ($\\Pi_$), the optimal strategy either remains unchanged or overshoots the cost-free optimum.
+", fig.height=5, fig.width=8, cache = fig.cache, dev=c("pdf", "svg", "png")}
 
@@
   scale_color_discrete(labels=c("Adjustment penalty", "No penalty"), name="") +
-  scale_linetype_discrete(labels=c("Adjustment penalty", "No penalty"), name="")
+  scale_linetype_discrete(labels=c("Adjustment penalty", "No penalty"), name="") + 
+  theme_bw()
 

### 2015-01-19 manuscripts/manuscript.Rmd
tuna citations

@@
 ```{r Figure_1, fig.cap="Estimated stock abundances (top panels) show much greater variation than the corresponding harvest policies (bottom).
-Left panels: ICCAT Stock assessments and Total Allowable Catch (TAC, before adjustments for national underages and overages) for bluefin tuna, 1987 - 2007.
+Left panels: ICCAT Stock assessments and Total Allowable Catch (TAC, before adjustments for national underages and overages) for bluefin tuna, 1982 - 2007.
 Right panels: SEDAR stock assessments and annual quotas for south Atlantic snowy grouper.", fig.width=6, fig.height=4, dev=c("pdf", "svg", "png"), cache=FALSE}
@@
 west Atlantic bluefin tuna (_Thunnus thynnus_, henceforth bluefin) from
-a recent stock assessment [@ICCAT20XX].  The bottom-left panel 
+a recent stock assessment [@ICCAT2009a].  The bottom-left panel 
 shows the catch quota (Total Allowable Catch or TAC, before being adjusted
@@
 for the stock as set by the relevant
-management agency [@ICCAT20XX]. Despite the estimated population size
-declining by XX% between YYYY and ZZZZ, the quota was not changed during
+management agency [@ICCAT2009a]. Despite the estimated population size
+declining by `r 1 - min(tuna$stock)/max(tuna$stock)`% between 1982 and 1991, the quota was not changed during
 this period. Instead, the quota only changed occasionally and in between
@@
 When costs vary quadratically with adjustment size ($\\Pi_2$), small adjustments are relatively cheap and thus the resulting optimal policy always changes, but by a smaller amount than if adjustments were free.
-When adjustments incur a fixed fee independent of size ($\\Pi_$), the optimal strategy either remains unchanged or overshoots the cost-free optimum.
+When adjustments incur a fixed fee independent of size ($\\Pi_3$), the optimal strategy either remains unchanged or overshoots the cost-free optimum.
 ", fig.height=5, fig.width=8, cache = fig.cache, dev=c("pdf", "svg", "png")}

### 2015-01-20 manuscripts/manuscript.Rmd
finishing off edits from paul and mike

@@
 Left panels: ICCAT Stock assessments and Total Allowable Catch (TAC, before adjustments for national underages and overages) for bluefin tuna, 1982 - 2007.
-Right panels: SEDAR stock assessments and annual quotas for south Atlantic snowy grouper.", fig.width=6, fig.height=4, dev=c("pdf", "svg", "png"), cache=FALSE}
+Right panels: SEDAR stock assessments and annual quotas for south Atlantic snowy grouper, 1994-2012.", fig.width=6, fig.height=4, dev=c("pdf", "svg", "png"), cache=FALSE}
 tuna <- read.csv("components/data/tuna.csv")
@@
 with which the those changes could occur.  Either could contribute to
-the observed quota stability. Such patterns of variable stocks managed
+the observed quota stability.
+
+Such patterns of variable stocks managed
 under far less variable quotas are extremely common; for instance, 
 in the management of south Atlantic snowy grouper (_Epinephelus niveatus_) 
-shown in the right-hand panels [@SEDAR2013]. More generally, reviews by @Biais1995 and
+shown in the righthand panels [@SEDAR2013]. Though the stock assessment
+shows similarly frequent variation between 1994 and 2012, the quota has
+only been adjusted twice during this period. In contrast to the adjustment
+in the bluefin quotas, both adjustments in snowy grouper quotas were phased
+in through steps over several years: 1994-96 and 2005-08.
+More generally, reviews by @Biais1995 and
 @Patterson2007a document many cases where changes in catch
@@
 $Z_t$ gives the stochastic shocks, which we
-assume are lognormally distributed and $A$ and $B$ are positive
+assume are log-normally distributed and $A$ and $B$ are positive
 constants.
@@
 \begin{equation}
-\max_{{\bf h}}\mathbf{ E} ( NPV_{0} )=\max_{{\bf h}} \sum_0^{T_{\mathrm{max}}} \mathbf{E} \left( \displaystyle \frac{\Pi_0(N_t,h_t)}{(1+\delta)^{t+1}} \right) \label{eq:objective}
+\max_{{\bf h}}\mathbf{ E} ( NPV_{0} )=\max_{{\bf h}} \sum_0^{T_{\mathrm{max}}} 
+\mathbf{E} \left( \displaystyle \frac{\Pi_0(N_t,h_t)}{(1+\delta)^{t+1}} \right) \label{eq:objective}
 \end{equation}
@@
   scale_color_discrete(labels=relabel, breaks = c('L1', 'L2', 'fixed')) 
+ # rename scale from 'variable' to 'adjustment cost for policy:'
 
@@
 directly.  The harvest policy chosen shows a systematic deviations from
-the adjustment cost free optimum, depending on the structure of the cost function.  In each
-case, the optimal solution without any adjustment cost is shown with
+the adjustment cost free optimum, depending on the structure of the cost function.  
+In each case, the optimal solution without any adjustment cost is 
+shown by the dashed grey line, with
 the policy induced by optimization under the given cost structure 
 (equivalent to a `r 100*reduction`% reduction in maximum expected NPV)
-overlaid in blue.
+overlaid in solid blue.
 
@@
 ```{r Figure_4, fig.cap="Variance and autocorrelation of harvest dynamics, as a function of the penalty coefficient.
-Adjustment penalty is calculated as percentage of the maximum expected $NPV$ in the basic case with no policy adjustment costs.", fig.height=4, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png")}
+Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=4, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png")}
 
@@
   coord_cartesian(xlim = c(0, .3)) + 
-  facet_wrap(~ statistic, scale="free_y") + 
+  facet_wrap(~ statistic, scale="free_y", ncol=1) + 
   scale_color_discrete(labels=relabel, name="Penalty function") + 
   scale_fill_discrete(labels=relabel, name="Penalty function") +
-  xlab("Penalty size (as fraction of NPV0)")
+  xlab(paste0("Penalty size (as fraction of", expression(NPV[0]), ")"))
 
@@
 for fixed costs $\Pi_3$. Moreover, these occurrences increase in frequency as the severity of
-these costs ($c_i$) increases.
+these costs ($c_i$) increases. Note that the restriction of only positive quotas lets us 
+distinguish between cases that are constant due purely to adjustment costs from cases that
+are constant purely due to boundary effects.
 
@@
 
-Reed <- cbind(reed_profits, costs = reed_costs$V1, Assumption = "Reed") 
+Reed <- cbind(reed_profits, costs = reed_costs$V1, Assumption = "No adjustment penalty") 
 Adj <- cbind(profits, costs = costs$V1, Assumption = "Adjustment penalty")
@@
 ```{r}
-fig5_caption <- paste("Distribution of profits from fishing and costs paid to adjustment, under linear costs ($\\Pi_1$).
-(Alternate penalties can be found in the supplementary materials)  Distributions are shown when managing a system in which the adjustment costs present compared to the same costs and profits of managing the system using a Reed model, which ignores adjustment costs, and thus tends to pay higher fees for adjustment.
-In contrast, the difference in profit after accounting for costs is only marginally less than the value derived by managing the population to optimize profits when ignoring adjustment costs (Reed model).")
+fig5_caption <- paste("Distribution of revenues from fishing and costs paid to adjustment.
+Plot shows distributions for the linear costs structure ($\\Pi_1$) only, alternate penalties can be found in the supplementary materials.
+Dockside revenues are always higher than adjustment costs.
+When those costs are not accounted for in the policy ("no adjustment costs"), it is possible to obtain only marginally higher revenues, but pay higher adjustment costs.")
 ```
@@
 
+<!-- this is confusing and could use better wording.  Consider naming the 
+scenarios, e.g. omission error vs optimal-->
+
 Next we examine the consequences either of ignoring policy adjustment
 costs when they are present or assuming they are present when they are
-not. To do so, we run two kinds of simulations:
+not.
 
-1. Simulations in which the optimal policy accounts for adjustment costs, 
-   and those costs are present (in the form assumed),
-2. Simulations in which the optimal policy _does not_ account for adjustment costs,
+To do so, we will simulate managing a fish stock when adjustments are costly.
+We will perform 100 replicate simulations of this for each of the three
+cost structures, $\Pi_1$, $\Pi_2$, & $\Pi_3$.  For each replicate, we will
+use two different management policies: one which ignores the adjustment costs,
+(that is, the Reed optimum policy, $\Pi_0$), and a second which accounts for the
+adjustment cost in place.
 
-While the optimization ensures that on average, the policy in the first
-simulation should outperform that of the second, it does not tell us by
-how much.  These simulations thus allow us to quantify this effect.
-
-We provide 100 replicates of each kind of scenario for each of the
-three forms $\Pi_1$, $\Pi_2$ & $\Pi_3$.  For each, we record (a)
-the dockside profits derived from fishing as well as (b) any fees paid
-to make adjustments to the policy.  In the first kind of simulation,
-dockside revenues are almost less than in the second for a given
-stochastic replicate, since the latter optimizes the expected NPV.
-However, the costs paid for adjustment are almost always less in the
-first scenario as well, since this solution explicitly tries to avoid
-higher adjustment costs.  We visualize this pattern in the distributions
-shown in Figure 5 (focusing on $\Pi_1$ for simplicity, as the pattern
-in $\Pi_2$ and $\Pi_3$ is similar, see Supplementary Material.)
+By comparing the NPV of this second scenario against the first, we can
+quantify the impact of ignoring costs when they are present.
 
@@
 the NPV of the second scenario in aggregate, and as it cannot do so
-through higher profits it must do so through lower costs.  Interestingly,
-for this set of parameters very little is lost in dockside revenue.
+through higher profits (these having already been maximized by the cost-free strategy),
+it must do so through lower costs.  Interestingly,
+for this set of parameters very little is lost in revenue.
 This suggests that the impact of assuming costs are present when they
-are not is rather small: since the dockside revenue is none-the-less
-near optimal.  This also suggests that the converse error: ignoring
-costs when they are present, is more severe.
+are not is rather small, as the revenue is nonetheless
+near optimal.  This also suggests that the converse error -- ignoring
+costs when they are present -- is more severe.
 
 ```{r Figure_6, fig.cap="Relative cost of ignoring adjustment costs when they are present ('ignoring', red) vs assuming the adjustment costs when they are absent ('assuming', blue), shown by penalty function over increasing magnitudes of cost.
-All values are relative to the cost-free adjustment optimum, $NPV_0$.
+All values are relative to the cost free adjustment optimum, $NPV_0$.
 In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present.
@@
 
-We visualize the differences between these two errors directly in Figure
+<!-- This needs to be worded more clearly. At least the first 2 sentences here.  -->
+
+We illustrate the differences between these two errors directly in Figure
 6. Subtracting revenue from adjustment costs and considering only the mean
-across the replicates, we can dervive the expected $NPV$ in each case.
+across the replicates, we can derive the expected $NPV$ in each case.
 To standardize against a common baseline, we will express this value as a
-fraction of the cost-free optimum, $NPV_0$. Note that we have calibrated
+fraction of the cost free optimum, $NPV_0$. Note that we have calibrated
 the optimal solutions to anticipate that `r reduction*100`% of their
@@
 
-Policy-makers managing ecological systems that vary in space and time
+Policymakers managing ecological systems that vary in space and time
 must evaluate how much of that variation to reflect in management
-recommendations. Fine-tuning a policy to respond to frequent variations
+recommendations. Finer tuning a policy to respond to frequent variations
 in ecological dynamics may incur increased transaction costs associated
@@
 of a fish stock subject to stochastically varying recruitment [@Reed1979; @Clark2010]. 
-We examined how optimal policy recommendations, here
-annual catch quotas, changed when accounting for costs associated with
+We examined how optimal policy recommendations -- here
+annual catch quotas -- changed when accounting for costs associated with
 policy adjustment and what the implications of following these policy
@@
 how the value of the fishery is affected by managers either under-
-or over-estimating the importance of policy adjustment costs of this type.
+or overestimating the importance of policy adjustment costs of this type.
 
@@
 in which we assumed there was a fixed cost associated with making any
-change to current policy. While each formulation clearly provides only a
-very phenomenological representation of the policy setting environment,
+change to current policy. While each formulation provides only
+very phenomenological representations of the policy-setting environment,
 we believe that each enables us to explore meaningful differences in how
-policy adjustment costs might operate. That being said, in the real-world
+policy adjustment costs might operate. That being said, in the real world
 we might expect the different types of adjustment cost to operate in
@@
 expensive to make. Including costs of this form smooths inter-annual
-variation in the catch quotas that would be recommended. Also, the catches
+variation in the recommended catch quotas. Also, the catches
 and remaining stock sizes corresponding to optimal management become more
-autocorrelated in time, because it takes the fishery longer to harvest
+autocorrelated in time, because it takes the fishery multiple timesteps to harvest
 down peaks in abundance that follow large recruitment pulses. The effects
@@
 with the size of the adjustment ($\Pi_1$), has less obvious effects on
-optimal policies. But interestingly, it is the formulation that
+optimal policies. Interestingly, it is this structure that
 most frequently produces stretches of strictly positive but unchanging
-quotas of the type most commonly encountered in real-world applications.
+quotas of the type most commonly encountered in real world applications.
 
@@
 modeling studies sometimes mention policy adjustment costs when motivating
-model assumptions [e.g. @Feichtinger1994; @Wirl1999; @Lewis1981; @McGough2009], they rarely provide much justification
+model assumptions [@Lewis1981; @Feichtinger1994; @Wirl1999; @McGough2009],
+they rarely provide much justification
 for the choice of functional form used or test the sensitivity of any
@@
 costs within each functional form should be the same, namely a constant
-annual quota that does not change through time (open-loop control).
+annual quota that does not change through time (open loop control).
 
 We also compared the efficiency costs that would result from failing
-to account for policy adjustment cost if they are present with those
+to account for policy adjustment costs, if they are present, with those
 involved in assuming them when in fact they are absent. The results
@@
 they are present arises because the first, more direct, cost contribution
-here is larger than the second.
+here is the larger.
 
 Assuming an adjustment cost exists when in fact it is absent is not the
-same as using the wrong functional form when it is present.  In the supplement we show that choice of the functional form makes a significant
+same as using the wrong functional form when it is present.  In the supplement
+we show that choice of the functional form makes a significant
 difference.  We show it can be better to ignore policy costs than to derive a 
@@
 example, we assume that the fishery in question is being optimally managed
-by a policy-maker who acts as the 'sole owner' of the stock. This approach
-is different to models that assume fisheries are not well-managed,
+by a policymaker who acts as the "sole owner" of the stock. This approach
+is different to models that assume fisheries are not well managed,
 e.g. by assuming open access conditions,
-or ones that derive policy recommendations endogenously by modeling
+or models that derive policy recommendations endogenously by modeling
 interactions between different stakeholders [@Kaitala1993; @Laukkanen2003].
@@
 other more intangible sources of policy adjustment costs, e.g. preferences
-of policy-makers or different stakeholders for less variable quotas,
+of policymakers or different stakeholders for less variable quotas,
 might be missed. An alternative, more holistic, approach would be to
@@
 collapse. Examining risks of stock collapse is not possible with the
-Reed model-formulation that we followed here but would be worthwhile
+Reed model formulation that we followed here but would be worthwhile
 in light of our finding that the variance and autocorrelation in stock
@@
 time in light of ecological variability, including game management,
-management of in-stream flow rates, fire management, habitat restoration,
-and managing for endangered species. In some ways, the analyses that
-we present can also be thought of as providing a temporal counter-part
-to discussions about the optimal spatial scale over which ecosystem
-management should be conducted.
+management of instream flow rates, fire management, habitat restoration,
+and managing for endangered species. The analyses that
+we present can also be thought of as providing a temporal counterpart
+to discussions about the spatial scale over which ecosystem
+management.
 

### 2015-01-21 manuscripts/manuscript.Rmd
fix misplaced quote string

@@
 Dockside revenues are always higher than adjustment costs.
-When those costs are not accounted for in the policy ("no adjustment costs"), it is possible to obtain only marginally higher revenues, but pay higher adjustment costs.")
+When those costs are not accounted for in the policy ('no adjustment costs'), it is possible to obtain only marginally higher revenues, but pay higher adjustment costs.")
 ```

### 2015-01-23 manuscripts/manuscript.Rmd
need to debug figure4 data.frame

@@
 ```{r Figure_4, fig.cap="Variance and autocorrelation of harvest dynamics, as a function of the penalty coefficient.
-Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=4, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png")}
+Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=6, fig.width=4, cache=fig.cache, dev=c("pdf", "svg", "png")}
 

### 2015-01-23 R/value_iteration.R

@@ -17,7 +17,8 @@
 #'  function at each point along the grid at each point in time.  
 #'  The returned V gives the value matrix at the first (last) time. 
 #' @export
-value_iteration <- function(SDP_Mat, x_grid, h_grid, OptTime=100, xT, profit, 
+value_iteration <- function(SDP_Mat, x_grid, h_grid, 
+                            OptTime=100, xT, profit, 
                             delta, epsilon = 1e-4){
   
   

### 2015-01-23 manuscripts/components/analysis.R

@@ -1,3 +1,6 @@
+
+#### SETUP #######
+
 parallel = FALSE
 ncpu = 4
 
@@ -6,7 +9,6 @@ ncpu = 4
 price = 10
 c0 = 30
 profit <- profit_harvest(price = price, c0 = c0, c1 = 0)
-
 
 ## ----c2_grid-------------------------------------------------------------
 c2 <- exp(seq(0, log(41), length.out = 40))-1
@@ -50,13 +52,17 @@ none <- function(h, h_prev)  0
 penaltyfns <- list(L2=L2, L1=L1, fixed=fixed)
 
 
+
+
 ## ----parallel, include=FALSE---------------------------------------------
 sfInit(cpu=ncpu, parallel=parallel)
 sfLibrary(pdgControl)
 sfExportAll()
 
+##### ANALYSIS #############
 
-## ----bigloop----
+
+## Apples to Apples comparison (Figure 2)
 policies <- lapply(penaltyfns, function(penalty){
   sfLapply(c2, function(c2){
     policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
@@ -65,8 +71,6 @@ policies <- lapply(penaltyfns, function(penalty){
   )
 })
 
-
-## -------------------------------------------------
 i <- which(x_grid > K)[1]
 fees <- 
   lapply(policies, function(penalty) 
@@ -81,9 +85,6 @@ npv0 <- max(fees$L1) # all have same max, at c2=0
 fees <- data.frame(c2=c2,fees)
 fees <- melt(fees, id="c2")
 fees <- subset(fees, variable %in% c("L1", "L2", "fixed"))
-
-#ggplot(fees, aes(c2, value, col=variable)) + geom_point() + geom_line()
-
 
 ## ----apples-----------------------
 closest <- function(x, v){
@@ -106,18 +107,13 @@ print_npv <- data.frame(model=index$variable, "value realized"=values,
 
 
 
-
-## ----npv_table--------------------
-#pandoc.table(print_npv)
-
-
-## ----policynames---------------------------------------------------------
+## ----Apply the apples-to-apples calibration------------------------------------
 L2_policy <- policies$L2[[apples_index["L2"]]]$D
 L1_policy <- policies$L1[[apples_index["L1"]]]$D
 fixed_policy <- policies$fixed[[apples_index["fixed"]]]$D
 
 
-## ----simulate_policy---------------
+## ----Simulations for Figure 3-------------------
 reps <- 1:100
[…]

### 2015-01-28 manuscripts/manuscript.Rmd
tweaking figures, fixes autocor issue

@@
 library("dplyr")
+library("gtable")
+library("gridExtra")
 options(digits=2)
@@
 
-library("dplyr")
+stats_df %>% 
+  filter(variable != "cross.correlation") %>%
+  separate(variable, c("measurement", "statistic"), sep="\\.") %>%
+  filter(measurement == 'harvest') %>% 
+  spread(statistic, value) ->
+  f4df
 
-f4df <- filter(figure4_df, timeseries=='harvest')
-ggplot(f4df, aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn)) + 
-  stat_summary(fun.y = mean, 
+p4 <- ggplot(f4df, aes(x = penalty_fraction, fill=penalty_fn, col=penalty_fn)) + 
+  coord_cartesian(xlim = c(0, .3)) + 
+  scale_color_discrete(labels=relabel, name="Adj. cost model") + 
+  scale_fill_discrete(labels=relabel, name="Adj. cost model")
+
+p4a <- p4 + 
+  stat_summary(aes(y=autocorrelation),
+               fun.y = mean, 
                fun.ymin = function(x) mean(x) - sd(x), 
@@
                geom = "ribbon", alpha=0.3, colour=NA) +
-  stat_summary(fun.y = mean, geom = "line") + 
-  coord_cartesian(xlim = c(0, .3)) + 
-  facet_wrap(~ statistic, scale="free_y", ncol=1) + 
-  scale_color_discrete(labels=relabel, name="Penalty function") + 
-  scale_fill_discrete(labels=relabel, name="Penalty function") +
-  xlab(paste0("Penalty size (as fraction of", expression(NPV[0]), ")"))
+  stat_summary(aes(y=autocorrelation), fun.y = mean, geom = "line") + 
+  xlab("")
+
+p4b <- p4 + 
+  stat_summary(aes(y=variance),
+               fun.y = mean, 
+               fun.ymin = function(x) mean(x) - sd(x), 
+               fun.ymax = function(x) mean(x) + sd(x), 
+               geom = "ribbon", alpha=0.3, colour=NA) +
+  stat_summary(aes(y=variance), fun.y = mean, geom = "line") +
+  xlab(expression(paste("Penalty size (as fraction of ", NPV[0], ")")))
+
+legend <- gtable_filter(ggplot_gtable(ggplot_build(p4a)), "guide-box") 
+grid.arrange(do.call(arrangeGrob, 
+            lapply(list(p4a, p4b),
+                   function(x) x + theme_bw() + theme(legend.position="none"))),
+    legend,
+    ncol = 2,
+    widths = c(5,1))
 

### 2015-01-28 manuscripts/supplement.Rmd
tweaking figures, fixes autocor issue

@@
 ```{r Figure_S2, fig.cap="Variance and autocorrelation of stock dynamics, as a function of the penalty coefficient.
-Adjustment penalty is calculated as percentage of the maximum expected $NPV$ in the basic case with no policy adjustment costs.", fig.height=4, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png")}
+Adjustment penalty is calculated as percentage of the maximum expected $NPV$ in the basic case with no policy adjustment costs.", fig.height=6, fig.width=4, cache=fig.cache, dev=c("pdf", "svg", "png")}
 
-stock_stats <- filter(figure4_df, timeseries=='stock')
-ggplot(stock_stats, aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn)) + 
-  stat_summary(fun.y = mean, 
+stats_df %>% 
+  filter(variable != "cross.correlation") %>%
+  separate(variable, c("measurement", "statistic"), sep="\\.") %>%
+  filter(measurement == 'stock') %>% 
+  spread(statistic, value) ->
+  s2df
+
+p4 <- ggplot(s2df, aes(x = penalty_fraction, fill=penalty_fn, col=penalty_fn)) + 
+  coord_cartesian(xlim = c(0, .3)) + 
+  scale_color_discrete(labels=relabel, name="Adj. cost model") + 
+  scale_fill_discrete(labels=relabel, name="Adj. cost model")
+
+p4a <- p4 + 
+  stat_summary(aes(y=autocorrelation),
+               fun.y = mean, 
                fun.ymin = function(x) mean(x) - sd(x), 
@@
                geom = "ribbon", alpha=0.3, colour=NA) +
-  stat_summary(fun.y = mean, geom = "line") + 
-  coord_cartesian(xlim = c(0, .3)) + 
-  facet_wrap(~ statistic, scale="free_y") + 
-  scale_color_discrete(labels=relabel, name="Penalty function") + 
-  scale_fill_discrete(labels=relabel, name="Penalty function") +
-  xlab("Penalty size (as fraction of NPV0)")
+  stat_summary(aes(y=autocorrelation), fun.y = mean, geom = "line") + 
+  xlab("")
 
-write.csv(stock_stats, "components/data/figureS2.csv")
+p4b <- p4 + 
+  stat_summary(aes(y=variance),
+               fun.y = mean, 
+               fun.ymin = function(x) mean(x) - sd(x), 
+               fun.ymax = function(x) mean(x) + sd(x), 
+               geom = "ribbon", alpha=0.3, colour=NA) +
+  stat_summary(aes(y=variance), fun.y = mean, geom = "line") +
+  xlab(expression(paste("Penalty size (as fraction of ", NPV[0], ")")))
+
+legend <- gtable_filter(ggplot_gtable(ggplot_build(p4a)), "guide-box") 
+grid.arrange(do.call(arrangeGrob, 
+            lapply(list(p4a, p4b),
+                   function(x) x + theme_bw() + theme(legend.position="none"))),
+    legend,
+    ncol = 2,
+    widths = c(5,1))
+
+write.csv(s2df, "components/data/figureS2.csv")
 

### 2015-01-28 manuscripts/components/analysis.R

@@ -255,21 +255,18 @@ summary_stats <- function(dt){
 stats_summaries <- lapply(sims_at_each_apple, summary_stats)
 # reformat list of data-frames as data frame with apple coef as a factor
 stats_df <- melt(stats_summaries, id=names(stats_summaries[[1]]))
+stats_df <- as_data_frame(stats_df)
 stats_df$L1 <- frac_lost[stats_df$L1]
-names(stats_df) <- c("penalty_fn", "reps", "variable", "value", "penalty_fraction")
+stats_df %>% 
+  dplyr::rename(penalty_fraction = L1) -> stats_df
 
 
-## ----split-factors-------------------------------------------------------
-# make statistic and timeseries separate factors
-figure4_df <- stats_df
-figure4_df$statistic <- figure4_df$variable
-figure4_df$timeseries <- figure4_df$variable
-stat_map <- c(harvest.variance = 'variance', stock.variance='variance', stock.autocorrelation='autocor',harvest.autocorrelation='autocor', cross.correlation='cross.correlation')
-  series_map <- c(harvest.variance = 'harvest', stock.variance='stock', stock.autocorrelation='stock',harvest.autocorrelation='harvest', cross.correlation='both')
-
-
-figure4_df$statistic <- stat_map[figure4_df$statistic]
-figure4_df$timeseries <- series_map[figure4_df$timeseries]
+stats_df %>% 
+  filter(variable != "cross.correlation") %>%
+  separate(variable, c("measurement", "statistic"), sep="\\.") %>%
+  filter(measurement == 'harvest') %>% 
+  spread(statistic, value) ->
+  f4df
 
 
 ## ----histograms----------------------------------------------------------

### 2015-01-28 manuscripts/manuscript.Rmd
tweaking figure 4

@@
 ```{r Figure_4, fig.cap="Variance and autocorrelation of harvest dynamics, as a function of the penalty coefficient.
-Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=6, fig.width=4, cache=fig.cache, dev=c("pdf", "svg", "png")}
+Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=6, fig.width=4.5, cache=fig.cache, dev=c("pdf", "svg", "png")}
 
@@
     ncol = 2,
-    widths = c(5,1))
+    widths = c(5,1.5))
 

### 2015-02-03 manuscripts/manuscript.Rmd
fine tuning figures

--- 2015-01-28 manuscripts/manuscript.Rmd
@@
     affiliation: melbourne
-  - name: James Sanchirico
+  - name: James N. Sanchirico
     affiliation: UCD
@@
 management agency [@ICCAT2009a]. Despite the estimated population size
-declining by `r 1 - min(tuna$stock)/max(tuna$stock)`% between 1982 and 1991, the quota was not changed during
+declining by `r 100 * (1 - min(tuna$stock) / max(tuna$stock))`% between
+1982 and 1991, the quota was not changed during
 this period. Instead, the quota only changed occasionally and in between
@@
 As the examples in Figure 1 make clear, management policies will rarely be
-as responsive as this constant escapement policy assumes. In this paper,
-we explore conditions under which this lack of responsiveness may be a
-rational response on the part of managers. Specifically, we consider a
+as responsive as this constant escapement policy assumes. In this paper, we consider a
 case where managers seek to balance the benefits in terms of increased
@@
 for these policy adjustment costs, we recognize that we do not know just
-what functional form they should take and that it will require a lot of
-empirical work to estimate that. Therefore, we scope three candidate
+what functional form they should take and that it will require substantial 
+empirical work to estimate that. Therefore, we investigate three candidate
 functional forms that represent qualitatively different assumptions about how these
@@
 To simplify presentation of the results, we will illustrate cases where the
-growth parameters are chosen so that the intrinsic rate of increase of
-the fish population is 1 and the equilibrium biomass for the equivalent
+growth parameters are chosen so that the equilibrium biomass for the equivalent
 deterministic model without harvesting is `r K`; (specifically, $A=$ `r pars[1]` and
@@
   ylab("Reduction in net present value") + 
-  scale_linetype_discrete(labels=relabel, breaks = c('L1', 'L2', 'fixed')) + 
-  scale_color_discrete(labels=relabel, breaks = c('L1', 'L2', 'fixed')) 
+  scale_linetype_discrete(labels=relabel, breaks = c('L1', 'L2', 'fixed'), name = 'cost model') + 
+  scale_color_discrete(labels=relabel, breaks = c('L1', 'L2', 'fixed'), name = 'cost model') 
  # rename scale from 'variable' to 'adjustment cost for policy:'
@@
   gather(variable, value, -time, -penalty_fn)
+
+dt3$penalty_fn <- factor(dt3$penalty_fn, levels=c("L1", "L2", "fixed"))
 
@@
 ```{r Figure_4, fig.cap="Variance and autocorrelation of harvest dynamics, as a function of the penalty coefficient.
-Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=6, fig.width=4, cache=fig.cache, dev=c("pdf", "svg", "png")}
+Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=6, fig.width=5, cache=fig.cache, dev=c("pdf", "svg", "png")}
 
@@
   coord_cartesian(xlim = c(0, .3)) + 
-  scale_color_discrete(labels=relabel, name="Adj. cost model") + 
-  scale_fill_discrete(labels=relabel, name="Adj. cost model")
+  scale_color_discrete(labels=relabel, name="cost model") + 
+  scale_fill_discrete(labels=relabel, name="cost model")
 
@@
     ncol = 2,
-    widths = c(5,1))
+    widths = c(5,2))
 
@@
 While still not common for the particular parameter combinations we examine,
-We find that positive unaltered quotas through time are much more likely
+we find that positive unaltered quotas through time are much more likely
 to occur when optimizing against $\Pi_1$ where policy adjustment costs
@@
   unite(dist, Assumption, variable, sep = " : ")
-
+labels <- c(expression(paste("Costs under ",  Pi[1])), 
+            expression(paste("Revenue under ", Pi[1])),
+            expression(paste("Cost under ", Pi[0])), 
+            expression(paste("Revenue under ", Pi[0])))
 ggplot(fig5_dat) + 
-  geom_density(aes(value, fill=dist, color=dist), alpha=0.8)
+  geom_density(aes(value, fill=dist, color=dist, lty=dist), alpha=0.5, size=1) +
+  scale_fill_discrete(name="", labels=labels) + 
+  scale_color_discrete(labels=labels, name="") + 
+   scale_linetype_discrete(labels=labels, name="") +
+  xlab("Realized NPV")
 
@@
   geom_bar(stat="identity", position="dodge") + 
-  facet_wrap(~reduction, ncol=2) + 
+  scale_fill_discrete(name="error type") + 
   scale_x_discrete(labels = c('L1' = substitute(paste(Pi[1])),
@@
                               'fixed' = substitute(paste(Pi[3])))) + 
-  xlab("Penalty function") + 
-  ylab(expression(NPV[0]))
+  xlab("Cost model") + 
+  ylab(expression(NPV[0])) + theme_tufte(base_size=16)
 write.csv(table1_long, "components/data/figure6.csv")
@@
 of smoothing here are similar to those predicted when assuming the cost
-per unit effort is increasing in the amount of effort expended (e.g.,
-@Lewis1981, @McGough2009; see Supporting Information for a summary of the
+per unit effort is increasing in the amount of effort expended [@Brown1974;
+@Lewis1981; @McGough2009]; (see Supporting Information for a summary of the
 relevant results) as opposed to associating extra costs with changes to
@@
 modeling studies sometimes mention policy adjustment costs when motivating
-model assumptions [@Lewis1981; @Feichtinger1994; @Wirl1999; @McGough2009],
+model assumptions [@Brown1974; @Lewis1981; @Feichtinger1994; @Wirl1999; @McGough2009],
 they rarely provide much justification
@@
 costs within each functional form should be the same, namely a constant
-annual quota that does not change through time (open loop control).
+annual quota that does not change through time.
 
@@
 is different to models that assume fisheries are not well managed,
-e.g. by assuming open access conditions,
-or models that derive policy recommendations endogenously by modeling
+e.g. by assuming regulated open access conditions [@Homans1997],
+or models that derive policy recommendations endogenously by modeling strategic 
 interactions between different stakeholders [@Kaitala1993; @Laukkanen2003].
@@
 participants Marie-Josee Fortin, Dan Ryan, Frank Doyle, Claire Paris,
-Iadine Chades and Mandy Karnauskas.  We also acknowledge the following
-support: NSF Grant DBI-1306697 (CB), ARC DECRA (DE130100572) and The
-ARC Centre of Excellence for Environmental Decisions (MB), ...
+Iadine Chades and Mandy Karnauskas.  We also acknowledge the support of
+NSF Grant DBI-1306697 to CB and ARC DECRA (DE130100572) & the
+ARC Centre of Excellence for Environmental Decisions to MB.
 

### 2015-04-30 manuscripts/manuscript.Rmd
some prior commits and new trials with more reps / longer OptTime

@@
 
-layout: review,12pt
+keywords: [optimal control, fisheries, ecological management, adjustment costs]
+
+layout: review,12pt,author-year,titlepage
 linenumbers: true
-
 bibliography: components/references.bib
@@
 documentclass: components/elsarticle
+geometry: [verbose,letterpaper,tmargin=2.54cm,bmargin=2.54cm,l
+margin=2.54cm,rmargin=2.54cm]
 
@@
 theme_set(theme_tufte(base_size=12) + theme(axis.line = element_line()))
+```
+
+```{r parameters, cache=FALSE}
+parallel = FALSE
+ncpu = 4
+price = 10
+c0 = 30
+profit <- profit_harvest(price = price, c0 = c0, c1 = 0)
+#c2 <- exp(seq(0, log(41), length.out = 40))-1
+c2 <- seq(0, 40, length.out=100)
+reduction <- 0.25 
+seed <- 123                 # Random seed (replicable results)
+delta <- 0.05               # economic discounting rate
+OptTime <- 50               # stopping time
+gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
+sigma_g <- 0.2              # Noise in population growth
+reward <- 0                 # bonus for satisfying the boundary condition
+z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
+z_m <- function() 1         # No measurement noise, 
+z_i <- function() 1         # No implemenation noise
+f <- BevHolt                # Select the state equation
+pars <- c(1.5, 0.05)        # parameters for the state equation
+K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
+xT <- 0                     # boundary conditions
+x0 <- K
+x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
+h_grid <- seq(0.01, 0.8 * K, length = gridsize)  
 ```
@@
 growth parameters are chosen so that the equilibrium biomass for the equivalent
-deterministic model without harvesting is `r K`; (specifically, $A=$ `r pars[1]` and
+deterministic model without harvesting is `r (pars[1]-1)/pars[2]`; (specifically, $A=$ `r pars[1]` and
 $B=$ `r pars[2]` in Eqn \eqref{eq:state_equation}). To characterize environmental variability, we

### 2015-04-30 manuscripts/components/analysis.R

@@ -1,43 +1,3 @@
-
-#### SETUP #######
-
-parallel = FALSE
-ncpu = 4
-
-
-## ----profit_model--------------------------------------------------------
-price = 10
-c0 = 30
-profit <- profit_harvest(price = price, c0 = c0, c1 = 0)
-
-## ----c2_grid-------------------------------------------------------------
-c2 <- exp(seq(0, log(41), length.out = 40))-1
-c2 <- seq(0, 40, length.out=100)
-
-
-## ----reduction-----------------------------------------------------------
-reduction <- 0.25 
-
-
-## ----setup---------------------------------------------------------------
-seed <- 123                 # Random seed (replicable results)
-delta <- 0.05               # economic discounting rate
-OptTime <- 20               # stopping time
-gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
-sigma_g <- 0.2              # Noise in population growth
-reward <- 0                 # bonus for satisfying the boundary condition
-z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() 1         # No measurement noise, 
-z_i <- function() 1         # No implemenation noise
-f <- BevHolt                # Select the state equation
-pars <- c(1.5, 0.05)        # parameters for the state equation
-K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
-xT <- 0                     # boundary conditions
-x0 <- K
-x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
-h_grid <- seq(0.01, 0.8 * K, length = gridsize)  
-
-
 ## ----reed--------------------------
 SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
 opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
@@ -114,9 +74,9 @@ fixed_policy <- policies$fixed[[apples_index["fixed"]]]$D
 
 
 ## ----Simulations for Figure 3-------------------
-reps <- 1:100
+reps <- 1:500
 names(reps) = paste("rep", 1:length(reps), sep="_") # treat as a factor
-seeds <- 1:100
+seeds <- 1:length(reps)
 sims <- list(
   L1 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                                                L1_policy, z_g, z_m, z_i, 
[…]

### 2015-04-30 manuscripts/manuscript.Rmd
scale to more cores

@@
 library("gridExtra")
+library("parallel")
 options(digits=2)
@@
 ```{r parameters, cache=FALSE}
-parallel = FALSE
-ncpu = 4
+parallel = TRUE
+ncpu = parallel::detectCores()
 price = 10

### 2015-05-03 manuscripts/manuscript.Rmd
Increase replicate number and OptTime length

@@
 dt3 <- dt %>% 
-  filter(replicate=="rep_17" & time < 20) %>%
+  filter(replicate=="rep_17" & time < OptTime) %>%
   select(time, harvest, harvest_alt, penalty_fn) %>%
@@
 
-ggplot(filter(table1_long, reduction == 0.25),
+ggplot(filter(table1_long, reduction == reduction),
   aes(penalty.fn, value, fill = variable)) + 

### 2015-05-03 manuscripts/supplement.Rmd
Increase replicate number and OptTime length

@@
 dt_s <- dt %>% 
-  filter(replicate=="rep_17" & time < 20) %>%
+  filter(replicate=="rep_17" & time < OptTime) %>%
   select(time, fishstock, alternate, penalty_fn) %>%
@@
 ex <- dt %>% 
-  filter(replicate %in% paste0("rep_", 16:20) & time < 20) %>%
+  filter(replicate %in% paste0("rep_", 16:20) & time < OptTime) %>%
   select(time, fishstock, harvest, alternate, harvest_alt, replicate, penalty_fn) %>%
@@
 ex <- dt_quad %>% 
-  filter(replicate=="rep_17" & time < 20) %>%
+  filter(replicate=="rep_17" & time < OptTime) %>%
   select(time, harvest, harvest_alt) %>%
@@
 
-ggplot(filter(table2_long, reduction==0.25), 
+ggplot(filter(table2_long, reduction==reduction), 
   aes(penalty.fn, value, fill = variable)) + 

### 2015-05-03 manuscripts/manuscript.Rmd
tidy and update documentation

@@
 We solve this problem on a finite time horizon of $T =$ `r OptTime` using
-value iteration [@Mangel1988; @Clark2000]. (Longer horizon times have no
-qualitative difference but stretch the plots making it more difficult
-to visualize the fluctuations.)
+value iteration [@Mangel1988; @Clark2000].
 
 R code for implementing the dynamic programming algorithm in this context is
-provided as a supplementary R package to the paper. Scripts for replicating 
-all of the analysis presented here are also provided in the Supplementary Material.
+provided as a supplementary R package to the paper, along with scripts for replicating 
+the analyses presented here. To address concerns about computational reproducibility [@Boettiger2015],
+a Docker container image of the software environment is also provided.
 
@@
   scale_linetype_discrete(labels=relabel, breaks = c('L1', 'L2', 'fixed'), name = 'cost model') + 
-  scale_color_discrete(labels=relabel, breaks = c('L1', 'L2', 'fixed'), name = 'cost model') 
+  scale_color_discrete(labels=relabel, breaks = c('L1', 'L2', 'fixed'), name = 'cost model') + 
+  annotate("text", mean(c2), reduction+.01, label = "Calibration for 25% reduction in NPV")
  # rename scale from 'variable' to 'adjustment cost for policy:'
 
-write.csv(dt, "components/data/100reps.csv")
 write.csv(fees, "components/data/figure2.csv")
@@
 the dashed vertical line in Figure 2 maps the needed cost coefficient
-$c_i$, for each penalty function, such that the fishery is worth `r
-100*(1-reduction)`% of its unconstrained value when optimally managed.
+$c_i$, for each penalty function, such that the fishery is worth `r 100*(1-reduction)`%
+of its unconstrained value when optimally managed.
 
@@
    scale_linetype_discrete(labels=labels, name="") +
-  xlab("Realized NPV")
+  xlab("Realized NPV") + 
+  ylab("Probability density of revenue/cost")
 

### 2015-05-03 manuscripts/supplement.Rmd
tidy and update documentation

@@
 # Supplementary material #
+
+## Code and data for methods and analysis ##
+
+All code and data used in this analysis can be found under the project's GitHub repository: [https://github.com/cboettig/pdg_control](https://github.com/cboettig/pdg_control).
+A snapshot of this repository representing the precise versions of the code used in this analysis has been permanently archived in the scientific software and data repository Zenodo, managed by CERN; and should be referenced or cited using its assigned digital object identifer, doi:xxx.
+(This DOI is also clearly linked from the GitHub repository).
+
+### Organization of code
+
+The project repository is organized as an R package.
+The intent is not to provide a general-purpose software tool for this kind of analysis, but rather to rely on a standardized directory structure for representing complex projects.
+It is our hope that this facilates understanding, reproducibility, and further exploration of these results sensu [Gentleman & Temple Lang 2007](http://biostats.bepress.com/bioconductor/paper2/), but caution that additional software engineering would be required before any of this could be applied in a different context.
+The functions provided are largely specific to the analyses presented here and may undocumented or incompletely documented.
+
+The source documents for both the manuscript and supplement are also found in the code repository using the dynamic document `.Rmd` format which embeds all of the code required for the analysis; see [http://rmarkdown.rstudio.com/](http://rmarkdown.rstudio.com/).
+
+Within the `.Rmd` files themselves are found only the blocks of code required to generate each of the figures shown in the manuscript.
+The analysis is sourced in from an external R script, `analysis.R` by a code block at the beginning of the `.Rmd` file.
+This script in turn relies on more modular functions defined in the `R/` directory that define the stochastic dynamic programming optimization algorithms, simulation routines, and so forth.
+
+### Data
+
+All empirical or simulated data shown in the figures can also be found as tabular .csv files in this repository.
+
+### Dependencies and machine images
 

### 2015-05-03 R/find_dp_cautious.R

@@ -5,7 +5,7 @@
 #' @param h_grid the discrete values of harvest levels to optimize over
 #' @param OptTime the stopping time 
 #' @param xT the boundary condition population size at OptTime
-#' @param c the cost/profit function, a function of harvested level
+#' @param profit the cost/profit function, a function of harvested level
 #' @param delta the exponential discounting rate
 #' @param reward  the profit for finishing with >= Xt fish at the end 
 #' (i.e. enforces the boundary condition)

### 2015-05-03 demo/Reed.R

@@ -1,47 +1,0 @@
-# file Reed.R
-# author Carl Boettiger, <cboettig@gmail.com>
-# date 2011-11-02
-# license BSD
-# modified from Reed_SDP.m, by Michael Bode.  
-# 
-# Implements a numerical version of the SDP described in:
-#   Reed, W.J., 1979. Optimal Escapement Levels in Stochastic
-#   and Deterministic Harvesting Models. Journal of Environmental 
-#   Economics and Management. 6: 350-363.
-#
-#           Fish population dynamics:
-#           X_{t+1} = Z_n f(X_n) 
-
-
-require(pdgControl)
-require(reshape2)
-require(ggplot2)
-
-## consider defaults for these
-# Define all parameters 
-delta <- 0.05      # economic discounting rate
-OptTime <- 50     # stopping time
-gridsize <- 10   # gridsize (discretized population)
-sigma_g <- 0.2    # Noise in population growth
-
-# load noise distributions  
-z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-
-
-### Chose the state equation / population dynamics function
-f <- BevHolt                # Select the state equation
-pars <- c(1.5, 0.05)        # parameters for the state equation
-xT <- 0                     # boundary conditions
-x0 <- 10 
-profit <- profit_harvest() 
-
-# Set up the discrete grids
-x_grid <- seq(0, 12, length = gridsize)  # population size
-h_grid <- x_grid  # vector of havest levels, use same resolution as for stock
-
-SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
-
-opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta)
-
-ForwardSimulate(f,pars,x_grid,h_grid,x0, opt$D, z_g)
-

### 2015-05-03 demo/bonvin.R

@@ -1,24 +1,0 @@
-# Bonvin NCO Control under model uncertainty
-
-
-# target S
-# Estimate S_hat
-
-# Use closure to define a profit function
-profit <- profit_harvest()
-
-# initialize system
-x_h <- numeric(OptTime) # population dynamics with harvest
-h <- numeric(OptTime) # havest level
-P <- numeric(OptTime) # Profit 
-S_hat <- numeric(OptTime) # Escapement (control strategy) 
-x_h[1] <- x0  # initial values
-S_hat[1] <- 0.2 # initial guess
-
-
-# next time step
-h[t] <- x_h[t]-S_hat[t] # harvest = stock minus escapement
-x_h[t+1] <- zg() * f(x_h[t], h[t], pars) # with harvest
-
-# calculate cost -- huh?  
-profit(x_h[t+1], h[t])

### 2015-05-03 demo/extractionCosts.R

@@ -1,133 +1,0 @@
-# file Reed.R
-# author Carl Boettiger, <cboettig@gmail.com>
-# date 2011-11-02
-# license BSD
-# modified from Reed_SDP.m, by Michael Bode.  
-# 
-# Implements a numerical version of the SDP described in:
-# 
-#   Sethi, G., Costello, C., Fisher, A., Hanemann, M., & Karp, L. (2005). 
-#   Fishery management under multiple uncertainty. Journal of Environmental
-#   Economics and Management, 50(2), 300-318. doi:10.1016/j.jeem.2004.11.005
-#
-#   Reed, W.J., 1979. Optimal Escapement Levels in Stochastic
-#   and Deterministic Harvesting Models. Journal of Environmental 
-#   Economics and Management. 6: 350-363.
-#
-# 
-#           Fish population dynamics:
-#           X_{t+1} = Z_n f(X_n) 
-
-
-rm(list=ls())   # Start wtih clean workspace 
-require(pdgControl)
-require(reshape2)
-require(ggplot2)
-
-
-## consider defaults for these
-# Define all parameters 
-delta <- 0.1      # economic discounting rate
-OptTime <- 50     # stopping time
-gridsize <- 100   # gridsize (discretized population)
-sigma_g <- 0.2    # Noise in population growth
-sigma_m <- 0.     # noise in stock assessment measurement
-sigma_i <- 0.     # noise in implementation of the quota
-
-# load noise distributions  
-source("noise_dists.R")
-
-## Chose the state equation / population dynamics function
-f <- BevHolt                # Select the state equation
-pars <- c(2, 4)             # parameters for the state equation
-K <- (pars[1] - 1)/pars[2]  # Carrying capacity 
-xT <- 0                     # boundary conditions
-e_star <- 0                 # model's bifurcation point (just for reference)
-control = "harvest"         # control variable is total harvest, h = e * x
-
-## An alternative state equation, with allee effect: (uncomment to select)
-#f <- Myer_harvest
-#pars <- c(1, 2, 6) 
-#p <- pars # shorthand 
-#K <- p[1] * p[3] / 2 + sqrt( (p[1] * p[3]) ^ 2 - 4 * p[3] ) / 2
-#xT <- p[1] * p[3] / 2 - sqrt( (p[1] * p[3]) ^ 2 - 4 * p[3] ) / 2 # allee threshold
-#e_star <- (p[1] * sqrt(p[3]) - 2) / 2 ## Bifurcation point 
[…]

### 2015-05-03 demo/heuristic_search.R

@@ -1,14 +1,0 @@
-# 
-#
-# Based on method outlined in  
-# Nicol, Sam, and Iadine Chadès. 2011. Beyond stochastic dynamic programming: 
-# a heuristic sampling method for optimizing conservation decisions in very
-# large state spaces. Methods in Ecology and Evolution, no.2 (April): 221-228.
-# doi:10.1111/j.2041-210X.2010.00069.x.
-#
-
-
-# Heuristic search for optimization
-
-# for each possible h, simulate forward 
-

### 2015-05-03 demo/multid_SDP_matrix.R

@@ -1,137 +1,0 @@
-
-#########################################################################
-# Parameter uncertainty attempts                                        #
-#########################################################################
-
-multid_SDP_matrix <- function(f, p, x_grid, h_grid, sigma_g){
-
-
-  gridsizes <- c(a=5, s=6, x=7 ,h=4)
-
-  sigma_g <- 0.2
-  a_grid <- seq(1, 2, length=gridsizes["a"])
-  s_grid <- seq(.0, .1, length=gridsizes["s"])  
-  x_grid <- seq(0, 1, length=gridsizes["x"]) 
-  h_grid <- seq(0, .5, length=gridsizes["h"])
-
-
-  f <- function(x,a,h,p){
-    max(0, (x - h) * a / (1 + (x - h) * p[1]))
-  }
-  p = c(1)
-
-## For each value of x_i, find the probability of going to x_j (given a_i and s_i)
-# P( x_i -> x_j; | a_i, s_i)
-    px <- function(a_i, s_i, x_i)
-      sapply(x_grid, function(x_j){
-        sum(
-          sapply(a_grid, function(a){
-            dlnorm(x_j, log(f(x_i, a, h, p)) - sigma_g ^ 2 / 2, sigma_g) *
-            dnorm(a, a_i, s_i)
-          })
-        )
-      })
-  x_
-      px(a_i, s_i, x_t_minus_1)
-  
-  # a_i -> a_j | x_i, s_i
-P_to_aj_given <- 
-
-  
-  sapply(a_grid, function(a_j){ 
-       dlnorm( log(f(x_tminus1_i, a_j, h,p) - sigma_g ^ 2 / 2, sigma_g)) * dnorm(a_j, a_i, s_i)
-      })
-
-P_to_sj_given <- 
-
-
-dat <-
-sapply(h_grid, function(h){
-  sapply(a_grid, function(a_hat){
-    sapply(s_grid, function(sigma_a){
-      sapply(x_grid, function(x){
-        sapply(a_grid, function(a){
-          sapply(x_grid, function(y){
-            dlnorm(y, log(f(x, a, h, p))-sigma_g^2/2, sigma_g) *
-            dnorm(a, a_hat, sigma_a)
-          })
-        })
-      })
-    })
-  })
-})
-
-
-get_column <- function(a,s,x,h, dat, gridsizes){
-  stride_a <- gridsize["x"] * gridsizes["a"] * gridsizes["x"] * gridsizes["s"]
[…]

### 2015-05-03 demo/plots.R

@@ -1,90 +1,0 @@
-# file plots.R
-# author Carl Boettiger, <cboettig@gmail.com>
-# date 2011-11-16
-# creates extra plots accompanying Reed.R
-
-# for stat plots
-require(ggplot2)
-require(Hmisc)
-require(pdgControl)
-
-## FIXME Once standardized, all these plots should become package fns
-
-## Reshape and summarize data ###
-dat <- melt(sims, id="time") # reshapes the data matrix to "long" form
-# some stats on the replicates, (stat_sumary can do this instead)
-m <- cast(dat, time ~ variable, mean) # mean population
-err <- cast(dat, time ~ variable, sd) # sd population
-
-
-## Show dynamics of a single replicate 
-ex <- sample(1:100,1) # a random replicate
-p0 <- ggplot(dat) +
-      geom_line(aes(time, value, color = variable), 
-                data = subset(dat, L1 == ex)) + 
-      geom_abline(intercept = opt$S, slope = 0, col = "darkred") + # show Reed's S: optimal escapement 
-      geom_abline(intercept = xT, slope = 0, lty = 2) #+ # show Allee threshold
-#print(p0)
-
-p1 <- plot_replicates(sims)
-
-## Update the main p1 plot to 
-## make the crashed trajectories stand out?
-#p1 <- p1 + geom_line(aes(time, value, group = L1), 
-#          data = subset(dat, variable == "harvest" & 
-#          (L1 %in% optimal_crashed$L1)),  col = "darkgreen", alpha = 0.5) +
-#     geom_line(aes(time, value, group = L1), 
-#          data = subset(dat, variable == "fishstock" &
-#          (L1 %in% optimal_crashed$L1)),  col = "darkblue", alpha = 0.5) 
-
-
-#### p2 Plots the unharvested dynamics ###
-crashed = subset(dat, variable =="unharvested" & time == OptTime - 1 & value < xT)
-p2 <- ggplot(data = subset(dat, variable == "unharvested"),
-             aes(time, value, group = L1)) + geom_line(alpha = 0.2) + 
-  # shows the mean +/- mult * sd , requires Hmisc
-  stat_summary(mapping = aes(group = 1), fun.data = mean_sdl, 
-               geom = "smooth", mult = 1) +
-  opts(title=sprintf("Unfished dynamics, %d populations crash", dim(crashed)[1]))
-
-
-
[…]

### 2015-05-03 demo/unit_test2.R

@@ -1,46 +1,0 @@
-require(PDGcontrol)
-
-# Define all parameters 
-delta <- 0.1      # economic discounting rate
-OptTime <- 50     # stopping time
-sigma_g <- 0.2      # Noise in population growth
-gridsize <- 10   # gridsize (discretized population)
-sigma_m <- .2  # 
-sigma_i <- .2 # 
-interval <- 1
-
-# Chose the state equation / population dynamics function
-f <- BevHolt 
-pars <- c(2,4)  
-K <- (pars[1]-1)/pars[2] 
-xT <- 0 
-e_star <- 0
-
-# Choose grids 
-x_grid <- seq(0, 2*K, length=gridsize)  # population size
-h_grid <- x_grid  # vector of havest levels, use same res as stock
-
-
-p <- pars
-i <- 3
-h <- x_grid[3]
-y <- x_grid[4]
-require(cubature)
-
-  expected <- f(y,h,p)
-      if(expected==0){
-        Prob <- numeric(gridsize)
-        Prob[1] <- 1
-      } else {
-        # dividing x by the expected value is same as scaling distribution to mean 1
-        pdf_zg <- function(x, expected) dlnorm(x/expected, 0, sigma_g)
-        pdf_zm <- function(x) dlnorm(x, 0, sigma_m)
-        pdf_zi <- function(x,q) dlnorm(x, log(q), sigma_i)
-        Prob <- sapply(x_grid, function(y){
-          F <- function(x) 
-            pdf_zg(y, f(x[1], x[2], p)) * pdf_zm(x[1]) * pdf_zi(x[2], h)
-          int <- adaptIntegrate(F, c(0, 0), c(10*K, 10*K))
-          int$integral
-        })   
-      }
-      Prob/sum(Prob)

### 2015-05-03 demo/unit_tests.R

@@ -1,62 +1,0 @@
-# file unit_tests.R
-# author Carl Boettiger <cboettig@gmail.com>
-# date 2011-11-16
-# license BSD
-# test the performance of SDP_by_simulation 
-
-require(pdgControl)
-# Define all parameters 
-delta <- 0.1      # economic discounting rate
-OptTime <- 50     # stopping time
-sigma_g <- 0.2      # Noise in population growth
-gridsize <- 100   # gridsize (discretized population)
-sigma_m <- .2  # 
-sigma_i <- .2 # 
-interval <- 1
-
-# Chose the state equation / population dynamics function
-f <- BevHolt 
-pars <- c(2,4)  
-K <- (pars[1]-1)/pars[2] 
-xT <- 0 
-e_star <- 0
-
-# Choose grids 
-x_grid <- seq(0, 2*K, length=gridsize)  # population size
-h_grid <- x_grid  # vector of havest levels, use same res as stock
-
-SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sqrt(sigma_g^2+sigma_m^2))
-int_SDP_Mat <- integrate_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, sigma_m, sigma_i)
-require(snowfall)
-sfInit(parallel=TRUE, cpu=4)
-sim_SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, sigma_g, sigma_m, sigma_i, reps=999)
-
-
-x <- matrix(NA, length(x_grid), 10) 
-x[,1] <- 0
-x0 <- .2
-x[which.min(abs(x_grid - x0)),1] <- 100
-y <- x
-z <- x
-
-plt <- function(i){
-  barplot(x[,i], col=rgb(0,0,1,.5))
-  barplot(y[,i], add=T, col=rgb(1,0,0,.5))
-  barplot(z[,i], add=T, col=rgb(0,0,1,.5))
-}
-
-
-for(i in 1:9){
-  x[,i+1] <- t(sim_SDP_Mat[[1]]) %*% x[,i]
-  y[,i+1] <- t(SDP_Mat[[1]]) %*% y[,i]
-  z[,i+1] <- t(int_SDP_Mat[[1]]) %*% z[,i]
-  Sys.sleep(.2)
-  plt(i)
-}
-
-
-png("test1.png"); plt(2); dev.off()
-png("test2.png"); plt(5); dev.off()
-require(socialR)
[…]

### 2015-05-07 manuscripts/manuscript.Rmd
more replicates

--- 2015-04-30 manuscripts/manuscript.Rmd
@@
 
-keywords: [optimal control, fisheries, ecological management, adjustment costs]
+layout: review,12pt
+linenumbers: true
 
-layout: review,12pt,author-year,titlepage
-linenumbers: true
 bibliography: components/references.bib
@@
 documentclass: components/elsarticle
-geometry: [verbose,letterpaper,tmargin=2.54cm,bmargin=2.54cm,l
-margin=2.54cm,rmargin=2.54cm]
 
@@
 library("gridExtra")
-library("parallel")
 options(digits=2)
@@
 
-```{r parameters, cache=FALSE}
-parallel = TRUE
-ncpu = parallel::detectCores()
-price = 10
-c0 = 30
-profit <- profit_harvest(price = price, c0 = c0, c1 = 0)
-#c2 <- exp(seq(0, log(41), length.out = 40))-1
-c2 <- seq(0, 40, length.out=100)
-reduction <- 0.25 
-seed <- 123                 # Random seed (replicable results)
-delta <- 0.05               # economic discounting rate
-OptTime <- 50               # stopping time
-gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
-sigma_g <- 0.2              # Noise in population growth
-reward <- 0                 # bonus for satisfying the boundary condition
-z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() 1         # No measurement noise, 
-z_i <- function() 1         # No implemenation noise
-f <- BevHolt                # Select the state equation
-pars <- c(1.5, 0.05)        # parameters for the state equation
-K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
-xT <- 0                     # boundary conditions
-x0 <- K
-x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
-h_grid <- seq(0.01, 0.8 * K, length = gridsize)  
-```
+```{r analysis, include=FALSE}
 
-```{r analysis, include=FALSE}
 source("components/analysis.R")
@@
 growth parameters are chosen so that the equilibrium biomass for the equivalent
-deterministic model without harvesting is `r (pars[1]-1)/pars[2]`; (specifically, $A=$ `r pars[1]` and
+deterministic model without harvesting is `r K`; (specifically, $A=$ `r pars[1]` and
 $B=$ `r pars[2]` in Eqn \eqref{eq:state_equation}). To characterize environmental variability, we

### 2015-05-07 manuscripts/components/analysis.R

@@ -1,8 +1,8 @@
 
 #### SETUP #######
 
-parallel = FALSE
-ncpu = 4
+parallel = TRUE
+ncpu = 16
 
 
 ## ----profit_model--------------------------------------------------------
@@ -22,7 +22,7 @@ reduction <- 0.25
 ## ----setup---------------------------------------------------------------
 seed <- 123                 # Random seed (replicable results)
 delta <- 0.05               # economic discounting rate
-OptTime <- 20               # stopping time
+OptTime <- 50               # stopping time
 gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
 sigma_g <- 0.2              # Noise in population growth
 reward <- 0                 # bonus for satisfying the boundary condition
@@ -114,9 +114,9 @@ fixed_policy <- policies$fixed[[apples_index["fixed"]]]$D
 
 
 ## ----Simulations for Figure 3-------------------
-reps <- 1:100
+reps <- 1:500
 names(reps) = paste("rep", 1:length(reps), sep="_") # treat as a factor
-seeds <- 1:100
+seeds <- 1:500
 sims <- list(
   L1 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                                                L1_policy, z_g, z_m, z_i, 
@@ -193,7 +193,7 @@ fig4 <- function(fraction_lost){
   quad_policy <- policies$quad[[apples_index["quad"]]]$D
   
   quad_profit <- profit_harvest(price = price, c0 = c0, c1 = apples["quad"]) 
-  sims <- lapply(1:50, function(reps) list(
+  sims <- lapply(1:500, function(reps) list(
     L1 = simulate_optim(f, pars, x_grid, h_grid, x0, 
                         L1_policy, z_g, z_m, z_i, 
                         opt$D, profit=profit, penalty=L1(apples["L1"])), 

### 2015-05-07 manuscripts/components/compute_error_table.R

@@ -8,9 +8,9 @@ compute_error_table <- function(r){
   L1_policy <- policies$L1[[apples_index["L1"]]]$D
   fixed_policy <- policies$fixed[[apples_index["fixed"]]]$D
 
-  reps <- 1:100
+  reps <- 1:500
   names(reps) = paste("rep", 1:length(reps), sep="_") # treat as a factor
-  seeds <- 1:100
+  seeds <- 1:length(reps)
   sims <- list(
     L1 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                                                  L1_policy, z_g, z_m, z_i, 

### 2015-05-07 manuscripts/manuscript.Rmd
avoid nasty dplyr nonstandard eval problem

--- 2015-05-03 manuscripts/manuscript.Rmd
@@
 
-ggplot(filter(table1_long, reduction == reduction),
+ggplot(filter(table1_long, reduction == 0.25),
   aes(penalty.fn, value, fill = variable)) + 

### 2015-05-07 R/value_iteration.R

@@ -5,10 +5,9 @@
 #' @param h_grid the discrete values of harvest levels to optimize over
 #' @param OptTime the stopping time 
 #' @param xT the boundary condition population size at OptTime
-#' @param c the cost/profit function, a function of harvested level
 #' @param delta the discounting rate (1-delta)
 #' @param epsilon value iteration tolerance
-
+#' @param profit the profit function
 #' (i.e. enforces the boundary condition)
 #' @return list containing the matrices D and V.  D is an x_grid by OptTime
 #'  matrix with the indices of h_grid giving the optimal h at each value x

### 2015-05-07 manuscripts/components/analysis.R

@@ -1,43 +1,3 @@
-
-#### SETUP #######
-
-parallel = TRUE
-ncpu = 16
-
-
-## ----profit_model--------------------------------------------------------
-price = 10
-c0 = 30
-profit <- profit_harvest(price = price, c0 = c0, c1 = 0)
-
-## ----c2_grid-------------------------------------------------------------
-c2 <- exp(seq(0, log(41), length.out = 40))-1
-c2 <- seq(0, 40, length.out=100)
-
-
-## ----reduction-----------------------------------------------------------
-reduction <- 0.25 
-
-
-## ----setup---------------------------------------------------------------
-seed <- 123                 # Random seed (replicable results)
-delta <- 0.05               # economic discounting rate
-OptTime <- 50               # stopping time
-gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
-sigma_g <- 0.2              # Noise in population growth
-reward <- 0                 # bonus for satisfying the boundary condition
-z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() 1         # No measurement noise, 
-z_i <- function() 1         # No implemenation noise
-f <- BevHolt                # Select the state equation
-pars <- c(1.5, 0.05)        # parameters for the state equation
-K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
-xT <- 0                     # boundary conditions
-x0 <- K
-x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
-h_grid <- seq(0.01, 0.8 * K, length = gridsize)  
-
-
 ## ----reed--------------------------
 SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
 opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
@@ -116,7 +76,7 @@ fixed_policy <- policies$fixed[[apples_index["fixed"]]]$D
 ## ----Simulations for Figure 3-------------------
 reps <- 1:500
 names(reps) = paste("rep", 1:length(reps), sep="_") # treat as a factor
-seeds <- 1:500
+seeds <- 1:length(reps)
 sims <- list(
   L1 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                                                L1_policy, z_g, z_m, z_i, 
[…]

### 2015-05-07 manuscripts/components/compute_error_table.R

@@ -8,9 +8,9 @@ compute_error_table <- function(r){
   L1_policy <- policies$L1[[apples_index["L1"]]]$D
   fixed_policy <- policies$fixed[[apples_index["fixed"]]]$D
 
-  reps <- 1:500
+  reps <- 1:100
   names(reps) = paste("rep", 1:length(reps), sep="_") # treat as a factor
-  seeds <- 1:length(reps)
+  seeds <- 1:100
   sims <- list(
     L1 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                                                  L1_policy, z_g, z_m, z_i, 

### 2015-05-07 manuscripts/components/quad_costs.R

@@ -1,5 +1,5 @@
-parallel = FALSE
-ncpu <- 4
+parallel = TRUE
+ncpu <- parallel::detectCores()
 
 library("pdgControl")
 library("tidyr")

### 2015-05-08 manuscripts/manuscript.Rmd
working on revisions

@@
   scale_color_discrete(labels=relabel, breaks = c('L1', 'L2', 'fixed'), name = 'cost model') + 
-  annotate("text", mean(c2), reduction+.01, label = "Calibration for 25% reduction in NPV")
- # rename scale from 'variable' to 'adjustment cost for policy:'
+  annotate("text", mean(c2), reduction+.02, label = "25% reduction in NPV")
 
@@
   f4df
+
+f4df$penalty_fn <- factor(f4df$penalty_fn, levels = c("L1", "L2", "fixed"))
 
@@
 
+table1_long$penalty.fn <- factor(table1_long$penalty.fn, levels = c("L1", "L2", "fixed"))
+
 ggplot(filter(table1_long, reduction == 0.25),
@@
   xlab("Cost model") + 
-  ylab(expression(NPV[0])) + theme_tufte(base_size=16)
+  ylab(expression(NPV[0])) 
 write.csv(table1_long, "components/data/figure6.csv")

### 2015-05-08 manuscripts/components/compute_error_table.R

@@ -8,9 +8,9 @@ compute_error_table <- function(r){
   L1_policy <- policies$L1[[apples_index["L1"]]]$D
   fixed_policy <- policies$fixed[[apples_index["fixed"]]]$D
 
-  reps <- 1:100
+  reps <- 1:500
   names(reps) = paste("rep", 1:length(reps), sep="_") # treat as a factor
-  seeds <- 1:100
+  seeds <- 1:500
   sims <- list(
     L1 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                                                  L1_policy, z_g, z_m, z_i, 

### 2015-05-08 manuscripts/components/compute_mismatches.R

@@ -8,9 +8,9 @@ compute_mismatches <- function(r){
   L1_policy <- policies$L1[[apples_index["L1"]]]$D
   fixed_policy <- policies$fixed[[apples_index["fixed"]]]$D
 
-  reps <- 1:100
+  reps <- 1:500
   names(reps) = paste("rep", 1:length(reps), sep="_") # treat as a factor
-  seeds <- 1:100
+  seeds <- 1:500
   sims <- list(
     L1_L2 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                                                  L1_policy, z_g, z_m, z_i, 

### 2015-05-08 manuscripts/supplement.Rmd
update supplement

@@
 ```{r quadraticcosts, include=FALSE, message=FALSE}
+
 source("components/quad_costs.R")
@@
                                 harvest_alt = substitute(paste("Harvest under ", paste(Pi[0]), " (Reed)")))
-
 ex <- dt_quad %>% 

### 2015-05-08 manuscripts/components/quad_costs.R

@@ -1,44 +1,4 @@
-parallel = TRUE
-ncpu <- parallel::detectCores()
-
-library("pdgControl")
-library("tidyr")
-library("dplyr")
-library("ggplot2")
-library("reshape2")
-library("data.table")
-library("snowfall")
-
-## ----profit_model--------------------------------------------------------
-price = 10
-c0 = 30
-profit <- profit_harvest(price = price, c0 = c0, c1 = 0)
 profit_quad <- function(c2) profit_harvest(price = price, c0 = c0, c1 = c2)
-
-
-## ----c2_grid-------------------------------------------------------------
-c2 <- exp(seq(0, log(41), length.out = 40))-1
-c2 <- seq(0, 40, length.out=100)
-reduction <- 0.25 
-
-## ----setup---------------------------------------------------------------
-seed <- 123                 # Random seed (replicable results)
-delta <- 0.05               # economic discounting rate
-OptTime <- 20               # stopping time
-gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
-sigma_g <- 0.2              # Noise in population growth
-reward <- 0                 # bonus for satisfying the boundary condition
-z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() 1         # No measurement noise, 
-z_i <- function() 1         # No implemenation noise
-f <- BevHolt                # Select the state equation
-pars <- c(1.5, 0.05)        # parameters for the state equation
-K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
-xT <- 0                     # boundary conditions
-x0 <- K
-x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
-h_grid <- seq(0.01, 0.8 * K, length = gridsize)  
-
 
 ## ----reed, dependson=c("setup", "profit_model")--------------------------
 SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
@@ -57,7 +17,6 @@ policies <- sfLapply(c2, function(c2){
   policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                          profit_quad(c2), delta, reward, penalty = none)
 })
-
 
 fee <- sapply(policies, function(policy) max(policy$V[i,]))
 npv0 <- fee[1]
[…]

### 2015-05-12 manuscripts/manuscript.Rmd
additional runs at different NPV reduction calibration points

@@
 $c_i$, for each penalty function, such that the fishery is worth `r 100*(1-reduction)`%
-of its unconstrained value when optimally managed.
+of its unconstrained value when optimally managed. To demonstrate that the results
+shown here are independent of this choice of calibrating to a `r 100*(1-reduction)`%
+reduction, we conduct the same analysis with a 10% and 30% reduction rate as well.
+The corresponding figures can be found in the Supplemental Materials.
 
@@
 cost scenarios for `r length(c2)` different $c_i$ coefficients. For each
-resulting policy, we then simulated 50 stochastic replicates of the stock
+resulting policy, we then simulated `r length(reps)` stochastic replicates of the stock
 dynamics managed under that policy.  To summarize the patterns shown
@@
 
+In the supplemental material, Figures S9-S12 illustrate that the 
+these qualitative patterns still hold at when the models are calibrated 
+to a reduction in NPV of 10% or 30%, though naturally the magnitude
+of the pattern is greater when the penalty is larger (e.g. 30% vs 10%).
+
 ```{r}
@@
 To do so, we will simulate managing a fish stock when adjustments are costly.
-We will perform 100 replicate simulations of this for each of the three
+We will perform `r length(reps)` replicate simulations of this for each of the three
 cost structures, $\Pi_1$, $\Pi_2$, & $\Pi_3$.  For each replicate, we will

### 2015-05-12 manuscripts/supplement.Rmd
additional runs at different NPV reduction calibration points

@@
 
+\renewcommand{\thefigure}{S\arabic{figure}}
 \appendix
-\renewcommand{\thefigure}{S\arabic{figure}}
 
@@
   gather(variable, value, -time, -penalty_fn) 
+dt_s$penalty_fn <- factor(dt3$penalty_fn, levels=c("L1", "L2", "fixed"))
 
@@
   s2df
+
+s2df$penalty_fn <- factor(f4df$penalty_fn, levels = c("L1", "L2", "fixed"))
 
@@
 }
+
+dt$penalty_fn <- factor(dt$penalty_fn, levels = c("L1", "L2", "fixed"))
 
@@
 The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs.", dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE}
+
+table1_long$penalty.fn <- factor(table1_long$penalty.fn, levels = c("L1", "L2", "fixed"))
 
@@
 ```
+
+## Robustness to reduction level
+
+```{r}
+source("components/vary_reduction.R")
+```
+
+Figures S9-S12 illustrate that the 
+these qualitative patterns still hold at when the models are calibrated 
+to a reduction in NPV of 10% or 30%, though naturally the magnitude
+of the pattern is greater when the penalty is larger (e.g. 30% vs 10%).
+
+```{r Figure_S9, dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE, fig.cap="Identical analysis to Figure 3 of the main text, but using a calibration corresponding to a 10% reduction in NPV.
+This results in a less pronounced version of the same qualitative pattern."}
+p3 <- ggplot(low$dt3, aes(time, value, col=variable, lty=variable)) +
+  geom_line(lwd=1) +
+  facet_grid(penalty_fn~., labeller = labeller) + 
+  labs(x="time", y="stock size", title = "Example Harvest Dynamics")  +
+  scale_color_discrete(labels=c("Adjustment penalty", "No penalty"), name="") +
+  scale_linetype_discrete(labels=c("Adjustment penalty", "No penalty"), name="") + 
+  theme_bw() + labs(title="example trajectories at 10% reduction in NPV")
+
+p3
+```
+
+```{r Figure_S10, dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE, fig.cap="Identical analysis to Figure 3 of the main text, but using a calibration corresponding to a 30% reduction in NPV.
+This results in a more pronounced version of the same qualitative pattern."}
+p3 <- ggplot(high$dt3, aes(time, value, col=variable, lty=variable)) +
+  geom_line(lwd=1) +
+  facet_grid(penalty_fn~., labeller = labeller) + 
+  labs(x="time", y="stock size", title = "Example Harvest Dynamics")  +
+  scale_color_discrete(labels=c("Adjustment penalty", "No penalty"), name="") +
+  scale_linetype_discrete(labels=c("Adjustment penalty", "No penalty"), name="") + 
+  theme_bw() + labs(title="example trajectories at 30% reduction in NPV")
+p3
+```
+
+```{r Figure_S11, dev=c("pdf", "svg", "png"), fig.width=5, fig.height=6, cache=FALSE, fig.cap="Identical analysis as in Figure 4 of the main text, but using a calibration to 10% reduction in NPV rather than 25%.
+The qualitatively similar pattern helps illustrate that these results are not specific to the value of the reduction chosen in the main text."}
+p4 <- ggplot(low$f4df, aes(x = penalty_fraction, fill=penalty_fn, col=penalty_fn)) + 
+  coord_cartesian(xlim = c(0, .3)) + 
+  scale_color_discrete(labels=relabel, name="cost model") + 
+  scale_fill_discrete(labels=relabel, name="cost model")
+
+p4a <- p4 + 
+  stat_summary(aes(y=autocorrelation),
+               fun.y = mean, 
+               fun.ymin = function(x) mean(x) - sd(x), 
+               fun.ymax = function(x) mean(x) + sd(x), 
+               geom = "ribbon", alpha=0.3, colour=NA) +
+  stat_summary(aes(y=autocorrelation), fun.y = mean, geom = "line") + 
+  xlab("") + 
+  labs(title="Summary statistics under a 10% reduction in NPV")
+
+p4b <- p4 + 
+  stat_summary(aes(y=variance),
+               fun.y = mean, 
+               fun.ymin = function(x) mean(x) - sd(x), 
+               fun.ymax = function(x) mean(x) + sd(x), 
+               geom = "ribbon", alpha=0.3, colour=NA) +
+  stat_summary(aes(y=variance), fun.y = mean, geom = "line") +
+  xlab(expression(paste("Penalty size (as fraction of ", NPV[0], ")")))
+
+legend <- gtable_filter(ggplot_gtable(ggplot_build(p4a)), "guide-box")
+
+grid.arrange(do.call(arrangeGrob, 
+            lapply(list(p4a, p4b),
+                   function(x) x + theme_bw() + theme(legend.position="none"))),
+    legend,
+    ncol = 2,
+    widths = c(5,2))
+```
+
+```{r Figure_S12, dev=c("pdf", "svg", "png"), fig.width=5, fig.height=6, cache=FALSE, fig.cap="Identical analysis as in Figure 4 of the main text, but using a calibration to 30% reduction in NPV rather than 25%.
+The qualitatively similar pattern helps illustrate that these results are not specific to the value of the reduction chosen in the main text."}
+p4 <- ggplot(high$f4df, aes(x = penalty_fraction, fill=penalty_fn, col=penalty_fn)) + 
+  coord_cartesian(xlim = c(0, .3)) + 
+  scale_color_discrete(labels=relabel, name="cost model") + 
+  scale_fill_discrete(labels=relabel, name="cost model")
+
+p4a <- p4 + 
+  stat_summary(aes(y=autocorrelation),
+               fun.y = mean, 
+               fun.ymin = function(x) mean(x) - sd(x), 
+               fun.ymax = function(x) mean(x) + sd(x), 
+               geom = "ribbon", alpha=0.3, colour=NA) +
+  stat_summary(aes(y=autocorrelation), fun.y = mean, geom = "line") + 
+  xlab("") + 
+  labs(title="Summary statistics under a 30% reduction in NPV")
+
+p4b <- p4 + 
+  stat_summary(aes(y=variance),
+               fun.y = mean, 
+               fun.ymin = function(x) mean(x) - sd(x), 
+               fun.ymax = function(x) mean(x) + sd(x), 
+               geom = "ribbon", alpha=0.3, colour=NA) +
+  stat_summary(aes(y=variance), fun.y = mean, geom = "line") +
+  xlab(expression(paste("Penalty size (as fraction of ", NPV[0], ")")))
+
+legend <- gtable_filter(ggplot_gtable(ggplot_build(p4a)), "guide-box")
+
+grid.arrange(do.call(arrangeGrob, 
+            lapply(list(p4a, p4b),
+                   function(x) x + theme_bw() + theme(legend.position="none"))),
+    legend,
+    ncol = 2,
+    widths = c(5,2))
+```

### 2015-05-13 manuscripts/manuscript.tex
tex file

--- 2015-05-07 manuscripts/manuscript.Rmd
@@
----
-title: Optimal management of a stochastically varying population when policy adjustment is costly
-author: 
-  - name: Carl Boettiger
-    affiliation: cstar
-    email: cboettig (at) gmail.com
-    footnote: Corresponding author
-  - name: Michael Bode
-    affiliation: melbourne
-  - name: James N. Sanchirico
-    affiliation: UCD
-  - name: Jacob LaRiviere
-    affiliation: UTKEcon
-  - name: Alan Hastings
-    affiliation: UCD
-  - name: Paul R. Armsworth 
-    affiliation: UTKEEB
+\documentclass[review,12pt,author-year,titlepage]{components/elsarticle} %review=doublespace preprint=single 5p=2 column
+%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
+\usepackage[hyphens]{url}
+\usepackage{lineno} % add 
+  \linenumbers % turns line numbering on 
+\bibliographystyle{elsarticle-harv}
+\biboptions{sort&compress} % For natbib
+\usepackage{graphicx}
+\usepackage{booktabs} % book-quality tables
+%% Redefines the elsarticle footer
+\makeatletter
+\def\ps@pprintTitle{%
+ \let\@oddhead\@empty
+ \let\@evenhead\@empty
+ \def\@oddfoot{\it \hfill\today}%
+ \let\@evenfoot\@oddfoot}
+\makeatother
 
-address: 
-  - code: cstar
-    address: | 
-      Center for Stock Assessment Research,
-      110 Shaffer Rd,
-      Santa Cruz, CA 95050, USA 
-  - code: UCD
-    address: Department of Environmental Science and Policy, University of California, Davis
-  - code: melbourne
-    address: School of Botany, University of Melbourne, Australia 
-  - code: UTKEEB
-    address: Department of Ecology and Evolutionary Biology, University of Tennessee, Knoxville
-  - code: UTKEcon
-    address: Department of Economics, University of Tennessee, Knoxville
+% A modified page layout
+\textwidth 6.75in
+\oddsidemargin -0.15in
+\evensidemargin -0.15in
+\textheight 9in
+\topmargin -0.5in
+%%%%%%%%%%%%%%%% end my additions to header
 
-abstract: |
+\usepackage[T1]{fontenc}
+\usepackage{lmodern}
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[utf8]{inputenc}
+\else % if luatex or xelatex
+  \usepackage{fontspec}
+  \ifxetex
+    \usepackage{xltxtra,xunicode}
+  \fi
+  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
+  \newcommand{\euro}{€}
+\fi
+% use microtype if available
+\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
+\usepackage[verbose,letterpaper,tmargin=2.54cm,bmargin=2.54cm,l margin=2.54cm,rmargin=2.54cm]{geometry}
+\usepackage{graphicx}
+% We will generate all images so they have a width \maxwidth. This means
+% that they will get their normal width if they fit onto the page, but
+% are scaled down if they would overflow the margins.
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
+\else\Gin@nat@width\fi}
+\makeatother
+\let\Oldincludegraphics\includegraphics
+\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}
+\ifxetex
+  \usepackage[setpagesize=false, % page size defined by xetex
+              unicode=false, % unicode breaks when used with xetex
+              xetex]{hyperref}
+\else
+  \usepackage[unicode=true]{hyperref}
+\fi
+\hypersetup{breaklinks=true,
+            bookmarks=true,
+            pdfauthor={},
+            pdftitle={Optimal management of a stochastically varying population when policy adjustment is costly},
+            colorlinks=true,
+            urlcolor=blue,
+            linkcolor=magenta,
+            pdfborder={0 0 0}}
+\urlstyle{same}  % don't use monospace font for urls
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+\setcounter{secnumdepth}{0}
+% Pandoc toggle for numbering sections (defaults to be off)
+\setcounter{secnumdepth}{0}
+% Pandoc header
+
+\usepackage[nomarkers]{endfloat}
+
+\begin{document}
+\begin{frontmatter}
+
+  \title{Optimal management of a stochastically varying population when policy
+adjustment is costly}
+    \author[cstar]{Carl Boettiger\corref{c1}}
+   \ead{cboettig (at) gmail.com} 
+   \cortext[c1]{Corresponding author}
+    \author[melbourne]{Michael Bode}
+
+    \author[UCD]{James N. Sanchirico}
+
+    \author[UTKEcon]{Jacob LaRiviere}
+
+    \author[UCD]{Alan Hastings}
+
+    \author[UTKEEB]{Paul R. Armsworth}
+
+      \address[cstar]{Center for Stock Assessment Research, 110 Shaffer Rd, Santa Cruz, CA
+95050, USA}    
+    \address[UCD]{Department of Environmental Science and Policy, University of
+California, Davis}    
+    \address[melbourne]{School of Botany, University of Melbourne, Australia}    
+    \address[UTKEEB]{Department of Ecology and Evolutionary Biology, University of Tennessee,
+Knoxville}    
+    \address[UTKEcon]{Department of Economics, University of Tennessee, Knoxville}
+
+  \begin{abstract}
   Ecological systems are dynamic and policies to manage them need to
-          respond to that variation. However, policy adjustments will sometimes
-          be costly, which means that fine-tuning a policy to track variability in
+  respond to that variation. However, policy adjustments will sometimes be
+  costly, which means that fine-tuning a policy to track variability in
   the environment very tightly will only sometimes be worthwhile. We use a
@@
   these costs may respond to the size of the change being implemented, or
-          there could be a fixed cost any time a quota change is made. We show
-          how different forms of policy costs have contrasting implications for
-          optimal policies. Though it is frequently assumed that costs to adjusting
-          policies will dampen variation in the policy, we show that certain cost
-          structures can actually increase variation through time. We further show
-          that failing to account for adjustment costs has a consistently worse
-          economic impact than would assuming these costs are present when they are not.
+  there could be a fixed cost any time a quota change is made. We show how
+  different forms of policy costs have contrasting implications for
+  optimal policies. Though it is frequently assumed that costs to
+  adjusting policies will dampen variation in the policy, we show that
+  certain cost structures can actually increase variation through time. We
+  further show that failing to account for adjustment costs has a
+  consistently worse economic impact than would assuming these costs are
+  present when they are not.
+  \end{abstract}
+   \begin{keyword} optimal control \sep fisheries \sep ecological management \sep adjustment costs \sep \end{keyword}
+ \end{frontmatter}
 
-keywords: [optimal control, fisheries, ecological management, adjustment costs]
+\begin{flushleft}
+\section{Introduction}\label{introduction}
 
-layout: review,12pt,author-year,titlepage
-linenumbers: true
-bibliography: components/references.bib
-csl: components/ecology.csl
-documentclass: components/elsarticle
-geometry: [verbose,letterpaper,tmargin=2.54cm,bmargin=2.54cm,l
-margin=2.54cm,rmargin=2.54cm]
+Ecosystems are dynamic and exhibit rich patterns of variability in both
+time and space (Durrett and Levin 1994). In designing management
+policies for ecosystems, managers need to decide how much of that
+variation to respond to. Managers could try to track variations in
+ecosystem dynamics very closely by setting policies that are extremely
+responsive to the environment. Many theoretical studies that seek to
+identify optimal policies for exploited populations and communities
+adopt this approach and largely ignore the challenges that would be
+involved in implementing such recommendations (e.g., Reed 1979, Neubert
+2003, Sethi et al. 2005, Halpern et al. 2011). However, the policy
+process can often be much more sluggish to respond to variations in
+ecosystem dynamics (Walters 1978, Armsworth et al. 2010). Moreover,
+stakeholders impacted by ecosystem management may prefer some stability
+and not want to deal with continually changing management
+recommendations (Biais 1995, Armsworth and Roughgarden 2003, Patterson
+2007, Patterson and Resimont 2007, Sanchirico et al. 2008). In other
+words, whatever gains are available from fine-tuning a policy
+prescription to more closely reflect environmental variation should be
+traded off against potential costs associated with the more responsive
+approach to management this would require.
 
-output:
-  pdf_document:
-    template: components/elsarticle.latex
-    fig_caption: true
-    keep_tex: true
----
-
-```{r configure, include=FALSE, cache=FALSE}
-library("methods")
-library("knitr")
-basename <- "manuscript"
-opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
-               cache.path = paste("components/cache/", basename, "/", sep=""))
-opts_chunk$set(cache = 2)
-opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, 
-               comment = NA, verbose = TRUE, echo=FALSE)
-# PDF-based figures
-opts_chunk$set(dev='pdf')
-fig.cache <- TRUE
-
-library("rmarkdown")
-library("pdgControl")
-library("reshape2")
-library("plyr")
-library("ggplot2")
-library("data.table")
-library("pander")
-library("cboettigR")
-library("ggthemes")
-library("snowfall")
-library("tidyr")
-library("dplyr")
-library("gtable")
-library("gridExtra")
-library("parallel")
-options(digits=2)
-
-theme_set(theme_tufte(base_size=12) + theme(axis.line = element_line()))
-```
-
-```{r parameters, cache=FALSE}
-parallel = TRUE
-ncpu = parallel::detectCores()
-price = 10
-c0 = 30
-profit <- profit_harvest(price = price, c0 = c0, c1 = 0)
-#c2 <- exp(seq(0, log(41), length.out = 40))-1
-c2 <- seq(0, 40, length.out=100)
-reduction <- 0.25 
-seed <- 123                 # Random seed (replicable results)
-delta <- 0.05               # economic discounting rate
-OptTime <- 50               # stopping time
-gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
-sigma_g <- 0.2              # Noise in population growth
-reward <- 0                 # bonus for satisfying the boundary condition
-z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
-z_m <- function() 1         # No measurement noise, 
-z_i <- function() 1         # No implemenation noise
-f <- BevHolt                # Select the state equation
-pars <- c(1.5, 0.05)        # parameters for the state equation
-K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
-xT <- 0                     # boundary conditions
-x0 <- K
-x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
-h_grid <- seq(0.01, 0.8 * K, length = gridsize)  
-```
-
-```{r analysis, include=FALSE}
-source("components/analysis.R")
-```
-
-Introduction
-============
-
-Ecosystems are dynamic and exhibit rich patterns of variability in
-both time and space [@Durrett1994]. In designing management policies for ecosystems,
-managers need to decide how much of that variation to respond to. Managers
-could try to track variations in ecosystem dynamics very closely by
-setting policies that are extremely responsive to the environment. Many
-theoretical studies that seek to identify optimal policies for exploited
-populations and communities adopt this approach and largely ignore the
-challenges that would be involved in implementing such recommendations
-[e.g., @Reed1979; @Neubert2003; @Sethi2005; @Halpern2011]. However, 
-the policy process can often be much more sluggish
-to respond to variations in ecosystem dynamics [@Walters1978; @Armsworth2010]. 
-Moreover, stakeholders impacted by ecosystem management
-may prefer some stability and not want to deal with continually changing
-management recommendations [@Biais1995; @Armsworth2003;
-@Patterson2007a; @Patterson2007b; @Sanchirico2008].
-In other words, whatever gains are available from fine-tuning a
-policy prescription to more closely reflect environmental variation
-should be traded off against potential costs associated with the more
-responsive approach to management this would require.
-
-```{r Figure_1, fig.cap="Estimated stock abundances (top panels) show much greater variation than the corresponding harvest policies (bottom).
-Left panels: ICCAT Stock assessments and Total Allowable Catch (TAC, before adjustments for national underages and overages) for bluefin tuna, 1982 - 2007.
-Right panels: SEDAR stock assessments and annual quotas for south Atlantic snowy grouper, 1994-2012.", fig.width=6, fig.height=4, dev=c("pdf", "svg", "png"), cache=FALSE}
-tuna <- read.csv("components/data/tuna.csv")
-grouper <- read.csv("components/data/grouper.csv")
-
-ex <- rbind(cbind(tuna, species="tuna"), cbind(grouper, species="snowy grouper"))
-ex_long <- gather(ex, variable, value, stock, quota)
-
-ggplot(ex_long, aes(year,value)) + 
-  geom_line() + geom_point() + 
-  facet_wrap(variable~species, scales="free") + 
-  ylab("value (mt)") + theme_bw()
-```
+\begin{figure}[htbp]
+\centering
+\includegraphics{components/figure/manuscript-Figure_1-1.pdf}
+\caption{Estimated stock abundances (top panels) show much greater
+variation than the corresponding harvest policies (bottom). Left panels:
+ICCAT Stock assessments and Total Allowable Catch (TAC, before
+adjustments for national underages and overages) for bluefin tuna, 1982
+- 2007. Right panels: SEDAR stock assessments and annual quotas for
+south Atlantic snowy grouper, 1994-2012.}
+\end{figure}
 
@@
 estimated population size, represented as spawning stock biomass, of
-west Atlantic bluefin tuna (_Thunnus thynnus_, henceforth bluefin) from
-a recent stock assessment [@ICCAT2009a].  The bottom-left panel 
-shows the catch quota (Total Allowable Catch or TAC, before being adjusted
-for overages or underages in the catch of each country in the previous year)
-for the stock as set by the relevant
-management agency [@ICCAT2009a]. Despite the estimated population size
-declining by `r 100 * (1 - min(tuna$stock) / max(tuna$stock))`% between
-1982 and 1991, the quota was not changed during
-this period. Instead, the quota only changed occasionally and in between
-times was left unaltered. Fishery management decisions regarding this
-species can be highly contentious (@Safina1998, @Sissenwine1998,
-@Porch2005). Moreover, the stock is fished by fleets from many nations
-with quotas being set by a multilaterial management agency through a
-process of negotiation. As such, we might reasonably anticipate that
-for this species there could be substantial transaction costs involved
-in reaching agreement over any quota change, or constraints on the frequency
-with which the those changes could occur.  Either could contribute to
-the observed quota stability.
+west Atlantic bluefin tuna (\emph{Thunnus thynnus}, henceforth bluefin)
+from a recent stock assessment (International Commission for the
+Conservation of Atlantic Tunas (ICCAT) 2009). The bottom-left panel
+shows the catch quota (Total Allowable Catch or TAC, before being
+adjusted for overages or underages in the catch of each country in the
+previous year) for the stock as set by the relevant management agency
+(International Commission for the Conservation of Atlantic Tunas (ICCAT)
+2009). Despite the estimated population size declining by 53.3\% between
+1982 and 1991, the quota was not changed during this period. Instead,
+the quota only changed occasionally and in between times was left
+unaltered. Fishery management decisions regarding this species can be
+highly contentious (Safina (1998), Sissenwine et al. (1998), Porch
+(2005)). Moreover, the stock is fished by fleets from many nations with
+quotas being set by a multilaterial management agency through a process
+of negotiation. As such, we might reasonably anticipate that for this
+species there could be substantial transaction costs involved in
+reaching agreement over any quota change, or constraints on the
+frequency with which the those changes could occur. Either could
+contribute to the observed quota stability.
 
-Such patterns of variable stocks managed
-under far less variable quotas are extremely common; for instance, 
-in the management of south Atlantic snowy grouper (_Epinephelus niveatus_) 
-shown in the righthand panels [@SEDAR2013]. Though the stock assessment
-shows similarly frequent variation between 1994 and 2012, the quota has
-only been adjusted twice during this period. In contrast to the adjustment
-in the bluefin quotas, both adjustments in snowy grouper quotas were phased
-in through steps over several years: 1994-96 and 2005-08.
-More generally, reviews by @Biais1995 and
-@Patterson2007a document many cases where changes in catch
-quotas that a management agency set were more modest than changes that
-would be recommended just by considering variations in stock abundance.
+Such patterns of variable stocks managed under far less variable quotas
+are extremely common; for instance, in the management of south Atlantic
+snowy grouper (\emph{Epinephelus niveatus}) shown in the righthand
+panels (SEDAR 2013). Though the stock assessment shows similarly
+frequent variation between 1994 and 2012, the quota has only been
+adjusted twice during this period. In contrast to the adjustment in the
+bluefin quotas, both adjustments in snowy grouper quotas were phased in
+through steps over several years: 1994-96 and 2005-08. More generally,
+reviews by Biais (1995) and Patterson (2007) document many cases where
+changes in catch quotas that a management agency set were more modest
+than changes that would be recommended just by considering variations in
+stock abundance.
 
@@
 for costs of policy adjustment can change optimal policies (see also
-@Ludwig1980, @Feichtinger1994, @Wirl1999). We focus on how
+Ludwig (1980), Feichtinger et al. (1994), Wirl (1999)). We focus on how
 harvest quotas for a stochastically varying fish population can be
@@
 and solution method largely follow Reed's classic treatment on this
-question, a treatment repeated widely in bioeconomic textbooks. We 
-note that while later work has extended this treatment to deal with 
-a variety of other issues (e.g. @Sethi2005; @Singh2006; @McGough2009),
-we start from the classical model for simplicity of presentation and analysis.
+question, a treatment repeated widely in bioeconomic textbooks. We note
+that while later work has extended this treatment to deal with a variety
+of other issues (e.g. Sethi et al. (2005); Singh et al. (2006); McGough
+et al. (2009)), we start from the classical model for simplicity of
+presentation and analysis.
 
-With his formulation, @Reed1979 showed that a constant escapement policy could be
-optimal under certain conditions. Such a policy involves choosing annual
-quotas that are perfectly responsive to recruitment variation in a fish
-stock. In poor recruitment years, the quota is set to zero and no fishing
-is allowed. Any time a recruitment pulse exceeds the escapement threshold, a quota is
-set that allows the fishery to exactly compensate through harvesting,
-thereby maintaining the optimal escapement level. However, in that
-analysis, Reed did not account for any costs of policy adjustment, which
-for such a responsive management strategy potentially could be large.
+With his formulation, Reed (1979) showed that a constant escapement
+policy could be optimal under certain conditions. Such a policy involves
+choosing annual quotas that are perfectly responsive to recruitment
+variation in a fish stock. In poor recruitment years, the quota is set
+to zero and no fishing is allowed. Any time a recruitment pulse exceeds
+the escapement threshold, a quota is set that allows the fishery to
+exactly compensate through harvesting, thereby maintaining the optimal
+escapement level. However, in that analysis, Reed did not account for
+any costs of policy adjustment, which for such a responsive management
+strategy potentially could be large.
 
-As the examples in Figure 1 make clear, management policies will rarely be
-as responsive as this constant escapement policy assumes. In this paper, we consider a
-case where managers seek to balance the benefits in terms of increased
-profits from fishing from more finely tracking recruitment variations
-with the growing costs associated with adjusting policies frequently to do
-so. The policy adjustment costs involved could reflect pure administrative
-transaction costs or preferences held by fishermen, fish processing plants
-or other stakeholders, for less variable quotas. In seeking to account
-for these policy adjustment costs, we recognize that we do not know just
-what functional form they should take and that it will require substantial 
-empirical work to estimate that. Therefore, we investigate three candidate
-functional forms that represent qualitatively different assumptions about how these
+As the examples in Figure 1 make clear, management policies will rarely
+be as responsive as this constant escapement policy assumes. In this
+paper, we consider a case where managers seek to balance the benefits in
+terms of increased profits from fishing from more finely tracking
+recruitment variations with the growing costs associated with adjusting
+policies frequently to do so. The policy adjustment costs involved could
+reflect pure administrative transaction costs or preferences held by
+fishermen, fish processing plants or other stakeholders, for less
+variable quotas. In seeking to account for these policy adjustment
+costs, we recognize that we do not know just what functional form they
+should take and that it will require substantial empirical work to
+estimate that. Therefore, we investigate three candidate functional
+forms that represent qualitatively different assumptions about how these
 costs operate to determine whether the results we obtain are sensitive
@@
 
-Methods
-=======
+\section{Methods}\label{methods}
 
-Fish population dynamics (state equation)
------------------------------------------
+\subsection{Fish population dynamics (state
+equation)}\label{fish-population-dynamics-state-equation}
 
-We will assume Beverton-Holt dynamics with multiplicative environmental noise
+We will assume Beverton-Holt dynamics with multiplicative environmental
+noise
 
@@
 
-where $N_t$ the stock size, $h_t$ the harvested level, 
-$Z_t$ gives the stochastic shocks, which we
-assume are log-normally distributed and $A$ and $B$ are positive
-constants.
+where \(N_t\) the stock size, \(h_t\) the harvested level, \(Z_t\) gives
+the stochastic shocks, which we assume are log-normally distributed and
+\(A\) and \(B\) are positive constants.
 
-We assume managers set an annual quota for harvesting $h_t$ (the control
-variable) after observing the stock size that year $N_t$ (the state
-variable), but while still being uncertain about future environmental
-conditions and stock sizes. Through time, this gives a time path of
-management actions ${\bf h}=(h_1,h_2,\dots)$ that depend on the stock
-sizes that were observed (a state dependent control rule).
+We assume managers set an annual quota for harvesting \(h_t\) (the
+control variable) after observing the stock size that year \(N_t\) (the
+state variable), but while still being uncertain about future
+environmental conditions and stock sizes. Through time, this gives a
+time path of management actions \({\bf h}=(h_1,h_2,\dots)\) that depend
+on the stock sizes that were observed (a state dependent control rule).
 
@@
 
-where $\mathbf{E}$ is the expectation operator, $\delta>0$ is the
-discount rate and $\Pi_0$ is the net revenue from operating the fishery
-in a given year. In this base case, we assume the annual dockside (that is,
-before accounting for any adjustment costs that may be incurred) net revenue
-from fishing is
+where \(\mathbf{E}\) is the expectation operator, \(\delta>0\) is the
+discount rate and \(\Pi_0\) is the net revenue from operating the
+fishery in a given year. In this base case, we assume the annual
+dockside (that is, before accounting for any adjustment costs that may
+be incurred) net revenue from fishing is
 
@@
 
-where $E_t$ represents fishing effort. We assume catch is proportional
-to stock size and effort expended fishing that year, $h_t = q E_t N_t$ and
-constant $q>0$ is the catchability coefficient. In
-Eqn. \eqref{eq:annual_netrevenue}, $p$ is the price per unit harvest and
-$c_0$ the cost of fishing per unit effort and, to simplify the presentation of results,
-we assume that these are constants with $p>0$ and $c_0>0$.
+where \(E_t\) represents fishing effort. We assume catch is proportional
+to stock size and effort expended fishing that year, \(h_t = q E_t N_t\)
+and constant \(q>0\) is the catchability coefficient. In Eqn.
+\eqref{eq:annual_netrevenue}, \(p\) is the price per unit harvest and
+\(c_0\) the cost of fishing per unit effort and, to simplify the
+presentation of results, we assume that these are constants with \(p>0\)
+and \(c_0>0\).
 
-To simplify presentation of the results, we will illustrate cases where the
-growth parameters are chosen so that the equilibrium biomass for the equivalent
-deterministic model without harvesting is `r (pars[1]-1)/pars[2]`; (specifically, $A=$ `r pars[1]` and
-$B=$ `r pars[2]` in Eqn \eqref{eq:state_equation}). To characterize environmental variability, we
-assume multiplicative shock $Z_t$ is distributed log-normally with
-log standard deviation $\sigma_g$ = `r sigma_g`. In addition, we
-show cases where $p=$ `r price`, $\delta=$ `r delta` and $c_0=$ `r c0`.
-In the supplement we illustrate that the qualitative patterns observed
-here are not sensitive to the specific choices of these parameter values.
+To simplify presentation of the results, we will illustrate cases where
+the growth parameters are chosen so that the equilibrium biomass for the
+equivalent deterministic model without harvesting is 10; (specifically,
+\(A=\) 1.5 and \(B=\) 0.05 in Eqn \eqref{eq:state_equation}). To
+characterize environmental variability, we assume multiplicative shock
+\(Z_t\) is distributed log-normally with log standard deviation
+\(\sigma_g\) = 0.2. In addition, we show cases where \(p=\) 10,
+\(\delta=\) 0.05 and \(c_0=\) 30. In the supplement we illustrate that
+the qualitative patterns observed here are not sensitive to the specific
+choices of these parameter values.
 
-Taken together this objective function \eqref{eq:objective} and the state
-equation \eqref{eq:state_equation} define a stochastic dynamic programming
-problem that we solve using backwards recursion via Bellman's equation.
-We denote the resulting state-dependent, optimal control as $\mathbf{h}_0^{\ast}$.
-We solve this problem on a finite time horizon of $T =$ `r OptTime` using
-value iteration [@Mangel1988; @Clark2000].
+Taken together this objective function \eqref{eq:objective} and the
+state equation \eqref{eq:state_equation} define a stochastic dynamic
+programming problem that we solve using backwards recursion via
+Bellman's equation. We denote the resulting state-dependent, optimal
+control as \(\mathbf{h}_0^{\ast}\). We solve this problem on a finite
+time horizon of \(T =\) 50 using value iteration (Mangel and Clark 1988,
+Clark and Mangel 2000).
 
-R code for implementing the dynamic programming algorithm in this context is
-provided as a supplementary R package to the paper, along with scripts for replicating 
-the analyses presented here. To address concerns about computational reproducibility [@Boettiger2015],
-a Docker container image of the software environment is also provided.
+R code for implementing the dynamic programming algorithm in this
+context is provided as a supplementary R package to the paper, along
+with scripts for replicating the analyses presented here. To address
+concerns about computational reproducibility (Boettiger 2015), a Docker
+container image of the software environment is also provided.
 
-<!-- Cite & link to Zenodo DOI here(?)-->
-
-Costs of policy adjustment 
---------------------------
+\subsection{Costs of policy
+adjustment}\label{costs-of-policy-adjustment}
 
@@
 policy adjustment could take. In each, we assume managers can adjust the
-quota set in the fishery $h_t$ in a given year and that any policy
+quota set in the fishery \(h_t\) in a given year and that any policy
 adjustment costs are associated with changes to this control variable.
-In each case, we assume there is no cost in initially setting the harvest
-policy at time 0.
+In each case, we assume there is no cost in initially setting the
+harvest policy at time 0.
 
@@
 larger changes to annual harvesting quotas incur greater policy
-adjustment penalties. Specifically, we replace $\Pi_0$ in the $NPV_0$
-equation with
+adjustment penalties. Specifically, we replace \(\Pi_0\) in the
+\(NPV_0\) equation with
 
@@
 
-where indicator function $\mathbf{I}(h_t, h_{t-1})$ takes the value 1 if
-$h_t=h_{t-1}$ and zero otherwise. For each $\Pi_i$, we can then define a
-new objective function $NPV_i$ similar to that in Eqn. \eqref{eq:objective}.
-We note that the fixed cost has conceptual analogues to the set-up cost of
-@Reed1974 and @Spulber1982 but here the fee is associated with a change
-in harvesting ($h_t\neq h_{t-1}$) and not with harvesting *per se*
-($h_t>0$) as in those studies.
+where indicator function \(\mathbf{I}(h_t, h_{t-1})\) takes the value 1
+if \(h_t=h_{t-1}\) and zero otherwise. For each \(\Pi_i\), we can then
+define a new objective function \(NPV_i\) similar to that in Eqn.
+\eqref{eq:objective}. We note that the fixed cost has conceptual
+analogues to the set-up cost of Reed (1974) and Spulber (1982) but here
+the fee is associated with a change in harvesting (\(h_t\neq h_{t-1}\))
+and not with harvesting \emph{per se} (\(h_t>0\)) as in those studies.
 
-Taken together with the state equation Eqn. \eqref{eq:state_equation}, each
-of these new objective functions defines a different stochastic dynamic
-programming problem. Again, we solve them numerically using backwards
-recursion. To include costs of policy adjustment, we expand the state
-space to include both the current stock size and the management action
-taken on the previous time step $(N_t,h_{t-1})$. For each new objective
-function $\max NPV_i$, we denote the corresponding optimal control
-policy as the vector $\mathbf{h}_i^*$.
+Taken together with the state equation Eqn. \eqref{eq:state_equation},
+each of these new objective functions defines a different stochastic
+dynamic programming problem. Again, we solve them numerically using
+backwards recursion. To include costs of policy adjustment, we expand
+the state space to include both the current stock size and the
+management action taken on the previous time step \((N_t,h_{t-1})\). For
+each new objective function \(\max NPV_i\), we denote the corresponding
+optimal control policy as the vector \(\mathbf{h}_i^*\).
 
 Note that this problem is much larger computationally than the classic
-formulation of this stochastic dynamic programming problem for a single stock.
-Whereas the classic problem considers each of $Q$ possible discrete quotas
-for $S$ possible stock values at each time $t$, for a search space of size $S \times Q$
-per timestep;  this formulation must also consider all possible values of quota
-in the _previous_ time step: since the costs that will follow depend on whether
-and by how much the harvest policy will change. This creates a total of
-$S \times Q \times Q$ configurations.
+formulation of this stochastic dynamic programming problem for a single
+stock. Whereas the classic problem considers each of \(Q\) possible
+discrete quotas for \(S\) possible stock values at each time \(t\), for
+a search space of size \(S \times Q\) per timestep; this formulation
+must also consider all possible values of quota in the \emph{previous}
+time step: since the costs that will follow depend on whether and by how
+much the harvest policy will change. This creates a total of
+\(S \times Q \times Q\) configurations.
 
 In the Supplementary Material, we compare our results with more
-conventional fisheries economic formulation in which additional costs are
-applied to the control variables themselves, as opposed to adjustments to
-the controls: $\Pi_4 (N_t,h_t) = p h_t -  c_0 E_t-c_4E_t^2$.  Additional
-costs of this form tend to have a smoothing effect on optimal quotas,
-but also change the long-term average stock size or quota size that
-is optimal.
+conventional fisheries economic formulation in which additional costs
+are applied to the control variables themselves, as opposed to
+adjustments to the controls:
+\(\Pi_4 (N_t,h_t) = p h_t - c_0 E_t-c_4E_t^2\). Additional costs of this
+form tend to have a smoothing effect on optimal quotas, but also change
+the long-term average stock size or quota size that is optimal.
 
-Comparing apples to apples
---------------------------
+\subsection{Comparing apples to
+apples}\label{comparing-apples-to-apples}
 
-Each policy adjustment cost function is characterized in terms of a
-cost coefficient $c_i$. However, $c_i$ takes different units for each
-functional form. Therefore, if seeking to compare the relative effect
-of each penalty function on optimal management, it is unclear what
+Each policy adjustment cost function is characterized in terms of a cost
+coefficient \(c_i\). However, \(c_i\) takes different units for each
+functional form. Therefore, if seeking to compare the relative effect of
+each penalty function on optimal management, it is unclear what
 parameter values should be used. To address this issue, we calibrate
-choices of $c_i$ so that each has a comparable impact on the optimal
-fishery $NPV$.  Fortunately, the optimal control framework provides a
-completely natural way to make this comparison: in terms of the _economic
-value_ (measured by $NPV$) of the stock in each case.  We will calibrate
-our realized economic value under each policy relative to economic value
-of the stock when adjustments to the policy are free ($NPV_0$).
+choices of \(c_i\) so that each has a comparable impact on the optimal
+fishery \(NPV\). Fortunately, the optimal control framework provides a
+completely natural way to make this comparison: in terms of the
+\emph{economic value} (measured by \(NPV\)) of the stock in each case.
+We will calibrate our realized economic value under each policy relative
+to economic value of the stock when adjustments to the policy are free
+(\(NPV_0\)).
 
-Figure 2 shows the calibration graphically. Each curve plots the change in
-maximum expected $NPV$ for a given cost structure as the $c_i$ coefficient
-is increased. In each case, the figure shows maximum expected
-NPV with policy adjustment costs as a proportion of the maximum expected
-NPV available in the basic problem $NPV_0({\bf h_0^*})$ without policy
-adjustment costs.
+Figure 2 shows the calibration graphically. Each curve plots the change
+in maximum expected \(NPV\) for a given cost structure as the \(c_i\)
+coefficient is increased. In each case, the figure shows maximum
+expected NPV with policy adjustment costs as a proportion of the maximum
+expected NPV available in the basic problem \(NPV_0({\bf h_0^*})\)
+without policy adjustment costs.
 
-```{r Figure_2, fig.cap="Expected net present value by functional form of penalty.
-Horizontal axis shows the coefficient $c_i$ governing the magnitude of the policy cost, while vertical axis shows fraction of the maximum expected net present value dissipated by the policy cost, $\\tfrac{NPV_0 - NPV_i}{NPV_0}$.
-The horizontal line indicates a value of the stock that is reduced by 25% from the maximum expected value in the absence of policy adjustment costs, $NPV_0({\\bf h_0^*})$.
-Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.", dependson="quadcosts", fig.width=5, fig.height=3, cache = fig.cache, dev=c("pdf", "svg", "png")}
-
-relabel <- c(L1 = substitute(paste(Pi[1])),
-             L2 = substitute(paste(Pi[2])),
-             fixed = substitute(paste(Pi[3])))
-
-ggplot(fees, aes(c2, (npv0-value)/npv0, lty=variable, color=variable)) + 
-  geom_line() + 
-  geom_hline(aes(yintercept=reduction), linetype=4) + 
-  xlab("Penalty coefficient") +
-  ylab("Reduction in net present value") + 
-  scale_linetype_discrete(labels=relabel, breaks = c('L1', 'L2', 'fixed'), name = 'cost model') + 
-  scale_color_discrete(labels=relabel, breaks = c('L1', 'L2', 'fixed'), name = 'cost model') + 
-  annotate("text", mean(c2), reduction+.01, label = "Calibration for 25% reduction in NPV")
- # rename scale from 'variable' to 'adjustment cost for policy:'
-
-write.csv(fees, "components/data/figure2.csv")
-
-```
+\begin{figure}[htbp]
+\centering
+\includegraphics{components/figure/manuscript-Figure_2-1.pdf}
+\caption{Expected net present value by functional form of penalty.
+Horizontal axis shows the coefficient \(c_i\) governing the magnitude of
+the policy cost, while vertical axis shows fraction of the maximum
+expected net present value dissipated by the policy cost,
+\(\tfrac{NPV_0 - NPV_i}{NPV_0}\). The horizontal line indicates a value
+of the stock that is reduced by 25\% from the maximum expected value in
+the absence of policy adjustment costs, \(NPV_0({\bf h_0^*})\).
+Selecting the coefficient \(c_i\) corresponding to this value in each
+functional form allows us to make consistent comparisons across the
+different functional forms of policy costs.}
+\end{figure}
 
 To compare the impact of penalty functions on optimal management across
-the different functional forms, we select penalty cost coefficients
-that induce the same reduction in maximum expected NPV. For example,
-the dashed vertical line in Figure 2 maps the needed cost coefficient
-$c_i$, for each penalty function, such that the fishery is worth `r 100*(1-reduction)`%
-of its unconstrained value when optimally managed.
+the different functional forms, we select penalty cost coefficients that
+induce the same reduction in maximum expected NPV. For example, the
+dashed vertical line in Figure 2 maps the needed cost coefficient
+\(c_i\), for each penalty function, such that the fishery is worth 75\%
+of its unconstrained value when optimally managed. To demonstrate that
+the results shown here are independent of this choice of calibrating to
+a 75\% reduction, we conduct the same analysis with a 10\% and 30\%
+reduction rate as well. The corresponding figures can be found in the
+Supplemental Materials.
 
-Results
-=======
+\section{Results}\label{results}
 
-Effect of policy adjustment costs on optimal quotas and stock sizes 
--------------------------------------------------------------------
+\subsection{Effect of policy adjustment costs on optimal quotas and
+stock
+sizes}\label{effect-of-policy-adjustment-costs-on-optimal-quotas-and-stock-sizes}
 
-```{r Figure_3, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.
-When costs vary linearly with the size of the adjustment ($\\Pi_1$), periods with no adjustment are more common than if adjustments were free.
-When costs vary quadratically with adjustment size ($\\Pi_2$), small adjustments are relatively cheap and thus the resulting optimal policy always changes, but by a smaller amount than if adjustments were free.
-When adjustments incur a fixed fee independent of size ($\\Pi_3$), the optimal strategy either remains unchanged or overshoots the cost-free optimum.
-", fig.height=5, fig.width=8, cache = fig.cache, dev=c("pdf", "svg", "png")}
-
-labeller <- function(variable,value){
-    return(relabel[paste(value)])
-}
-
-dt3 <- dt %>% 
-  filter(replicate=="rep_17" & time < OptTime) %>%
-  select(time, harvest, harvest_alt, penalty_fn) %>%
-  gather(variable, value, -time, -penalty_fn)
-
-dt3$penalty_fn <- factor(dt3$penalty_fn, levels=c("L1", "L2", "fixed"))
-
-ggplot(dt3, aes(time, value, col=variable, lty=variable)) +
-  geom_line(lwd=1) +
-  facet_grid(penalty_fn~., labeller = labeller) + 
-  labs(x="time", y="stock size", title = "Example Harvest Dynamics")  +
-  scale_color_discrete(labels=c("Adjustment penalty", "No penalty"), name="") +
-  scale_linetype_discrete(labels=c("Adjustment penalty", "No penalty"), name="") + 
-  theme_bw()
-
-write.csv(dt3, "components/data/figure3.csv")
-```
+\begin{figure}[htbp]
+\centering
+\includegraphics{components/figure/manuscript-Figure_3-1.pdf}
+\caption{Example realization of optimal harvesting strategy and
+resulting fish stock sizes under the different functional forms of
+adjustment costs. When costs vary linearly with the size of the
+adjustment (\(\Pi_1\)), periods with no adjustment are more common than
+if adjustments were free. When costs vary quadratically with adjustment
+size (\(\Pi_2\)), small adjustments are relatively cheap and thus the
+resulting optimal policy always changes, but by a smaller amount than if
+adjustments were free. When adjustments incur a fixed fee independent of
+size (\(\Pi_3\)), the optimal strategy either remains unchanged or
+overshoots the cost-free optimum.}
+\end{figure}
 
@@
 directly. The harvest policy chosen shows a systematic deviations from
-the adjustment cost free optimum, depending on the structure of the cost function.  
-In each case, the optimal solution without any adjustment cost is 
-shown by the dashed grey line, with
-the policy induced by optimization under the given cost structure 
-(equivalent to a `r 100*reduction`% reduction in maximum expected NPV)
-overlaid in solid blue.
+the adjustment cost free optimum, depending on the structure of the cost
+function.\\In each case, the optimal solution without any adjustment
+cost is shown by the dashed grey line, with the policy induced by
+optimization under the given cost structure (equivalent to a 25\%
+reduction in maximum expected NPV) overlaid in solid blue.
 
 The first panel shows a typical pattern resulting from linear adjustment
-costs ($\Pi_1$).  The optimal policy tends to avoid very small policy
+costs (\(\Pi_1\)). The optimal policy tends to avoid very small policy
 adjustments, resulting in periods of a constant policy followed by
@@
 policy pattern. In contrast, the second formulation (quadratic costs,
-$\Pi_2$) disproportionately penalizes large policy adjustments. The
+\(\Pi_2\)) disproportionately penalizes large policy adjustments. The
 corresponding optimal policy is typified by the middle panel, responding
@@
 with smaller magnitude response than the equivalent cost-free optimal
-solution. This results in a smoother $h_t$ curve, one that undershoots
-the larger oscillations seen in the cost-free optimum in favor of a policy
-that changes incrementally each year. Finally, the optimal policy for the
-third, 'fixed fee' formulation ($\Pi_3$) only makes large adjustments,
-as one might expect, because the magnitude of the adjustment made is
-not reflected in the resulting cost.
+solution. This results in a smoother \(h_t\) curve, one that undershoots
+the larger oscillations seen in the cost-free optimum in favor of a
+policy that changes incrementally each year. Finally, the optimal policy
+for the third, `fixed fee' formulation (\(\Pi_3\)) only makes large
+adjustments, as one might expect, because the magnitude of the
+adjustment made is not reflected in the resulting cost.
 
-These patterns are consistent across stochastic replicates over a
-range of penalty magnitudes. The comparisons shown in Figure 3 are
-for one realization (i.e. a particular sequence of random number draws
+These patterns are consistent across stochastic replicates over a range
+of penalty magnitudes. The comparisons shown in Figure 3 are for one
+realization (i.e.~a particular sequence of random number draws
 representing environmental variability) and are made for one particular
-magnitude of policy adjustment costs, which have been calibrated to equal
-to `r reduction *100`% of $NPV_0({\bf h_0^*})$.  To demonstrate this,
-we solved for the optimal policy under each of the three adjustment
-cost scenarios for `r length(c2)` different $c_i$ coefficients. For each
-resulting policy, we then simulated 50 stochastic replicates of the stock
-dynamics managed under that policy.  To summarize the patterns shown
-in Figure 3 and characterize the impact of increasingly large fraction
-of the economic value (NPV) being consumed by policy adjustment costs,
-we examine the response of several summary statistics to increasing
-adjustment penalties (as a fraction of the adjustment-free value) in
-Figure 4.  We show the impact of policy adjustment costs on the variance &
+magnitude of policy adjustment costs, which have been calibrated to
+equal to 25\% of \(NPV_0({\bf h_0^*})\). To demonstrate this, we solved
+for the optimal policy under each of the three adjustment cost scenarios
+for 100 different \(c_i\) coefficients. For each resulting policy, we
+then simulated 500 stochastic replicates of the stock dynamics managed
+under that policy. To summarize the patterns shown in Figure 3 and
+characterize the impact of increasingly large fraction of the economic
+value (NPV) being consumed by policy adjustment costs, we examine the
+response of several summary statistics to increasing adjustment
+penalties (as a fraction of the adjustment-free value) in Figure 4. We
+show the impact of policy adjustment costs on the variance \&
 autocorrelation of the harvests through time.
 
-```{r Figure_4, fig.cap="Variance and autocorrelation of harvest dynamics, as a function of the penalty coefficient.
-Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=6, fig.width=5, cache=fig.cache, dev=c("pdf", "svg", "png")}
-
-stats_df %>% 
-  filter(variable != "cross.correlation") %>%
-  separate(variable, c("measurement", "statistic"), sep="\\.") %>%
-  filter(measurement == 'harvest') %>% 
-  spread(statistic, value) ->
-  f4df
-
-p4 <- ggplot(f4df, aes(x = penalty_fraction, fill=penalty_fn, col=penalty_fn)) + 
-  coord_cartesian(xlim = c(0, .3)) + 
-  scale_color_discrete(labels=relabel, name="cost model") + 
-  scale_fill_discrete(labels=relabel, name="cost model")
-
-p4a <- p4 + 
-  stat_summary(aes(y=autocorrelation),
-               fun.y = mean, 
-               fun.ymin = function(x) mean(x) - sd(x), 
-               fun.ymax = function(x) mean(x) + sd(x), 
-               geom = "ribbon", alpha=0.3, colour=NA) +
-  stat_summary(aes(y=autocorrelation), fun.y = mean, geom = "line") + 
-  xlab("")
-
-p4b <- p4 + 
-  stat_summary(aes(y=variance),
-               fun.y = mean, 
-               fun.ymin = function(x) mean(x) - sd(x), 
-               fun.ymax = function(x) mean(x) + sd(x), 
-               geom = "ribbon", alpha=0.3, colour=NA) +
-  stat_summary(aes(y=variance), fun.y = mean, geom = "line") +
-  xlab(expression(paste("Penalty size (as fraction of ", NPV[0], ")")))
-
-legend <- gtable_filter(ggplot_gtable(ggplot_build(p4a)), "guide-box") 
-grid.arrange(do.call(arrangeGrob, 
-            lapply(list(p4a, p4b),
-                   function(x) x + theme_bw() + theme(legend.position="none"))),
-    legend,
-    ncol = 2,
-    widths = c(5,2))
-
-write.csv(f4df, "components/data/figure4.csv")
-```
+\begin{figure}[htbp]
+\centering
+\includegraphics{components/figure/manuscript-Figure_4-1.pdf}
+\caption{Variance and autocorrelation of harvest dynamics, as a function
+of the penalty coefficient. Adjustment penalty is calculated as
+percentage of the maximum expected NPV in the basic case with no policy
+adjustment costs.}
+\end{figure}
 
@@
 For example, when small policy adjustments cost little but large
-adjustments are expensive ($\Pi_2$), we see the smoothing signal that we
-might have expected (see also @Ludwig1980 for this particular case). As
-cost penalties increase in severity (moving right along the horizontal axis,
-larger fractions of the economic value are consumed by adjustment costs), the
-variance in quotas through time decreases and the autocorrelation of
-quotas through time increases.
-When adjustment costs are zero, all policies are slightly negatively autocorrelated:
-this reflects the fact that a high harvest year is usually followed by a low harvest year
-that allows the stocks to recover. However, as adjustment costs increase, the quadratic
-policy tends to undershoot when stocks jump to very high or low levels, adjusting to compensate
-over multiple years, as seen in Figure 3.  As a result, autocorrelation increases.
+adjustments are expensive (\(\Pi_2\)), we see the smoothing signal that
+we might have expected (see also Ludwig (1980) for this particular
+case). As cost penalties increase in severity (moving right along the
+horizontal axis, larger fractions of the economic value are consumed by
+adjustment costs), the variance in quotas through time decreases and the
+autocorrelation of quotas through time increases. When adjustment costs
+are zero, all policies are slightly negatively autocorrelated: this
+reflects the fact that a high harvest year is usually followed by a low
+harvest year that allows the stocks to recover. However, as adjustment
+costs increase, the quadratic policy tends to undershoot when stocks
+jump to very high or low levels, adjusting to compensate over multiple
+years, as seen in Figure 3. As a result, autocorrelation increases.
 
 Interestingly, as suggested by the realization in Fig. 3, including a
-fixed cost ($\Pi_1$) of policy adjustment increases the variation in harvests
-through time. This is the opposite of a smoothing effect.
+fixed cost (\(\Pi_1\)) of policy adjustment increases the variation in
+harvests through time. This is the opposite of a smoothing effect.
 
 Finally, the case where policy adjustment costs scale linearly with the
-size of the adjustment ($\Pi_1$) appear to be something of a
-middle of the road strategy, in that increasing the severity of policy
-adjustment costs. To reveal the
-particular impact of policy adjustment costs of this type requires a
-more targeted summary statistic. Specifically, for each run we
-calculated the frequency with which the optimal policy involved
-maintaining a positive quota across multiple time steps unaltered. This
-type of policy is arguably the most commonly observed behavior in TAC
-management, but is one that is very rarely observed to be part of the
-optimal management strategy in the basic model without policy adjustment
-costs (Eqn. 3) or when optimizing against $\Pi_2$ or $\Pi_3$.
+size of the adjustment (\(\Pi_1\)) appear to be something of a middle of
+the road strategy, in that increasing the severity of policy adjustment
+costs. To reveal the particular impact of policy adjustment costs of
+this type requires a more targeted summary statistic. Specifically, for
+each run we calculated the frequency with which the optimal policy
+involved maintaining a positive quota across multiple time steps
+unaltered. This type of policy is arguably the most commonly observed
+behavior in TAC management, but is one that is very rarely observed to
+be part of the optimal management strategy in the basic model without
+policy adjustment costs (Eqn. 3) or when optimizing against \(\Pi_2\) or
+\(\Pi_3\).
 
-```{r}
-fraction_no_shift <- function(x){
+In the supplemental material, Figures S9-S12 illustrate that the these
+qualitative patterns still hold at when the models are calibrated to a
+reduction in NPV of 10\% or 30\%, though naturally the magnitude of the
+pattern is greater when the penalty is larger (e.g.~30\% vs 10\%).
 
-noshift <- x[2:length(x)] - x[1:length(x)-1] == 0
-strictly_positive <- (x > 0.01 )[-1] # drop first point, 
-who <- noshift & strictly_positive # True whenever consecutive pairs did not shift and the second in the pair was nonzero harvest
- sum(who)/length(who)
-}
+While still not common for the particular parameter combinations we
+examine, we find that positive unaltered quotas through time are much
+more likely to occur when optimizing against \(\Pi_1\) where policy
+adjustment costs scale linearly with the size of proposed policy
+changes: over the 100 replicates time series the harvest policy is
+strictly positive and identical in consecutive intervals only 9.88\% of
+the time for quadratic costs \(\Pi_2\), compared with 20.78\% with
+linear costs \(\Pi_1\) and 0.37\% for fixed costs \(\Pi_3\). Moreover,
+these occurrences increase in frequency as the severity of these costs
+(\(c_i\)) increases. Note that the restriction of only positive quotas
+lets us distinguish between cases that are constant due purely to
+adjustment costs from cases that are constant purely due to boundary
+effects.
 
-shifts <- dt[, fraction_no_shift(harvest), by=c("penalty_fn", "replicate")]
-ave <- shifts[, mean(V1), by=penalty_fn]
+\subsection{Consequences of policy adjustment
+costs}\label{consequences-of-policy-adjustment-costs}
 
-no_shifts <- ave$V1
-names(no_shifts) <- ave$penalty_fn
-```
-
-While still not common for the particular parameter combinations we examine,
-we find that positive unaltered quotas through time are much more likely
-to occur when optimizing against $\Pi_1$ where policy adjustment costs
-scale linearly with the size of proposed policy changes: over the 100 replicates
-time series the harvest policy is strictly positive and identical in consecutive intervals
-only `r no_shifts[["L2"]] * 100`% of the time for quadratic costs $\Pi_2$, compared with
-`r no_shifts[["L1"]] * 100`% with linear costs $\Pi_1$ and `r no_shifts[["fixed"]]*100`%
-for fixed costs $\Pi_3$. Moreover, these occurrences increase in frequency as the severity of
-these costs ($c_i$) increases. Note that the restriction of only positive quotas lets us 
-distinguish between cases that are constant due purely to adjustment costs from cases that
-are constant purely due to boundary effects.
-
-Consequences of policy adjustment costs 
----------------------------------------
-
-```{r histogram-calc}
-profits <- dt[, sum(profit_fishing), by=c('penalty_fn', 'replicate') ]
-costs <- dt[, sum(policy_cost), by=c('penalty_fn', 'replicate') ]
-reed_profits <- dt[, sum(profit_fishing_alt), by=c('penalty_fn', 'replicate') ]
-reed_costs <- dt[, sum(policy_cost_alt), by=c('penalty_fn', 'replicate') ]
-setnames(profits, "V1", "profits")
-setnames(reed_profits, "V1", "profits")
-
-Reed <- cbind(reed_profits, costs = reed_costs$V1, Assumption = "No adjustment penalty") 
-Adj <- cbind(profits, costs = costs$V1, Assumption = "Adjustment penalty")
-
-hist_dat <- melt(rbind(Adj, Reed), id=c("penalty_fn", "replicate", "Assumption"))
-````
-
-```{r}
-fig5_caption <- paste("Distribution of revenues from fishing and costs paid to adjustment.
-Plot shows distributions for the linear costs structure ($\\Pi_1$) only, alternate penalties can be found in the supplementary materials.
-Dockside revenues are always higher than adjustment costs.
-When those costs are not accounted for in the policy ('no adjustment costs'), it is possible to obtain only marginally higher revenues, but pay higher adjustment costs.")
-```
-
-```{r Figure_5, fig.cap=fig5_caption, fig.width=8, fig.height=6, dependson="histogram-calc", dev=c("pdf", "svg", "png"), cache=FALSE}
-
-fig5_dat <- hist_dat %>% 
-  filter(penalty_fn=="L1") %>%
-  select(-penalty_fn) %>%
-  unite(dist, Assumption, variable, sep = " : ")
-labels <- c(expression(paste("Costs under ",  Pi[1])), 
-            expression(paste("Revenue under ", Pi[1])),
-            expression(paste("Cost under ", Pi[0])), 
-            expression(paste("Revenue under ", Pi[0])))
-ggplot(fig5_dat) + 
-  geom_density(aes(value, fill=dist, color=dist, lty=dist), alpha=0.5, size=1) +
-  scale_fill_discrete(name="", labels=labels) + 
-  scale_color_discrete(labels=labels, name="") + 
-   scale_linetype_discrete(labels=labels, name="") +
-  xlab("Realized NPV") + 
-  ylab("Probability density of revenue/cost")
-
-write.csv(hist_dat, "components/data/figure5.csv")
-```
-
-<!-- this is confusing and could use better wording.  Consider naming the 
-scenarios, e.g. omission error vs optimal-->
+\begin{figure}[htbp]
+\centering
+\includegraphics{components/figure/manuscript-Figure_5-1.pdf}
+\caption{Distribution of revenues from fishing and costs paid to
+adjustment. Plot shows distributions for the linear costs structure
+(\(\Pi_1\)) only, alternate penalties can be found in the supplementary
+materials. Dockside revenues are always higher than adjustment costs.
+When those costs are not accounted for in the policy (`no adjustment
+costs'), it is possible to obtain only marginally higher revenues, but
+pay higher adjustment costs.}
+\end{figure}
 
@@
 
-To do so, we will simulate managing a fish stock when adjustments are costly.
-We will perform 100 replicate simulations of this for each of the three
-cost structures, $\Pi_1$, $\Pi_2$, & $\Pi_3$.  For each replicate, we will
-use two different management policies: one which ignores the adjustment costs,
-(that is, the Reed optimum policy, $\Pi_0$), and a second which accounts for the
-adjustment cost in place.
+To do so, we will simulate managing a fish stock when adjustments are
+costly. We will perform 500 replicate simulations of this for each of
+the three cost structures, \(\Pi_1\), \(\Pi_2\), \& \(\Pi_3\). For each
+replicate, we will use two different management policies: one which
+ignores the adjustment costs, (that is, the Reed optimum policy,
+\(\Pi_0\)), and a second which accounts for the adjustment cost in
+place.
 
@@
 
-Figure 5 shows that the difference in dockside revenue (labeled "profits"
-in the figure) between these two scenarios (green vs purple distributions)
-is very small, while a larger difference exists between the costs paid
-for making policy adjustments (red vs blue). This is predicted by the
-optimization: the first scenario must outperform (or at least equal)
-the NPV of the second scenario in aggregate, and as it cannot do so
-through higher profits (these having already been maximized by the cost-free strategy),
-it must do so through lower costs.  Interestingly,
-for this set of parameters very little is lost in revenue.
-This suggests that the impact of assuming costs are present when they
-are not is rather small, as the revenue is nonetheless
-near optimal.  This also suggests that the converse error -- ignoring
-costs when they are present -- is more severe.
+Figure 5 shows that the difference in dockside revenue (labeled
+``profits'' in the figure) between these two scenarios (green vs purple
+distributions) is very small, while a larger difference exists between
+the costs paid for making policy adjustments (red vs blue). This is
+predicted by the optimization: the first scenario must outperform (or at
+least equal) the NPV of the second scenario in aggregate, and as it
+cannot do so through higher profits (these having already been maximized
+by the cost-free strategy), it must do so through lower costs.
+Interestingly, for this set of parameters very little is lost in
+revenue. This suggests that the impact of assuming costs are present
+when they are not is rather small, as the revenue is nonetheless near
+optimal. This also suggests that the converse error -- ignoring costs
+when they are present -- is more severe.
 
-```{r Figure_6, fig.cap="Relative cost of ignoring adjustment costs when they are present ('ignoring', red) vs assuming the adjustment costs when they are absent ('assuming', blue), shown by penalty function over increasing magnitudes of cost.
-All values are relative to the cost free adjustment optimum, $NPV_0$.
-In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present.
-The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs.", dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE}
+\begin{figure}[htbp]
+\centering
+\includegraphics{components/figure/manuscript-Figure_6-1.pdf}
+\caption{Relative cost of ignoring adjustment costs when they are
+present (`ignoring', red) vs assuming the adjustment costs when they are
+absent (`assuming', blue), shown by penalty function over increasing
+magnitudes of cost. All values are relative to the cost free adjustment
+optimum, \(NPV_0\). In each case, it is less costly to assume adjustment
+costs are present when they are not than it is to ignore them when they
+are present. The severity of the latter mistake increases sharply as
+adjustment costs make a larger fraction of the total costs.}
+\end{figure}
 
-who <- c("penalty_fn", "ignore_fraction", "assume_fraction", "reduction")
-table1 <- arrange(error_df[who], reduction) 
-names(table1) = c("penalty.fn", "ignoring", "assuming", "reduction")
-table1_long <- melt(table1, id = c('penalty.fn', 'reduction'))
-table1_long$reduction <- as.factor(table1_long$reduction)
-table1_long <- subset(table1_long, reduction != "0.3")
+We illustrate the differences between these two errors directly in
+Figure 6. Subtracting revenue from adjustment costs and considering only
+the mean across the replicates, we can derive the expected \(NPV\) in
+each case. To standardize against a common baseline, we will express
+this value as a fraction of the cost free optimum, \(NPV_0\). Note that
+we have calibrated the optimal solutions to anticipate that 25\% of
+their \(NPV\) would go into adjustment costs. When these adjustment
+costs are not actually present (blue bars, Fig 6), we thus expect a
+\(NPV\) higher than the anticipated 75\% but not quite as high as the
+optimal policy for that scenario (100\%). When adjustment costs are
+present but the policy assumes that they are not (red bars), we would
+expect the \(NPV\) to be less than 75\% of \(NPV_0\) (since that's as
+good as the optimal solution for this scenario can do).
 
-ggplot(filter(table1_long, reduction == 0.25),
-  aes(penalty.fn, value, fill = variable)) + 
-  geom_bar(stat="identity", position="dodge") + 
-  scale_fill_discrete(name="error type") + 
-  scale_x_discrete(labels = c('L1' = substitute(paste(Pi[1])),
-                              'L2' = substitute(paste(Pi[2])),
-                              'fixed' = substitute(paste(Pi[3])))) + 
-  xlab("Cost model") + 
-  ylab(expression(NPV[0])) + theme_tufte(base_size=16)
-write.csv(table1_long, "components/data/figure6.csv")
-```
-
-<!-- This needs to be worded more clearly. At least the first 2 sentences here.  -->
-
-We illustrate the differences between these two errors directly in Figure
-6. Subtracting revenue from adjustment costs and considering only the mean
-across the replicates, we can derive the expected $NPV$ in each case.
-To standardize against a common baseline, we will express this value as a
-fraction of the cost free optimum, $NPV_0$. Note that we have calibrated
-the optimal solutions to anticipate that `r reduction*100`% of their
-$NPV$ would go into adjustment costs. When these adjustment costs are
-not actually present (blue bars, Fig 6), we thus expect a $NPV$ higher
-than the anticipated `r (1 -reduction)*100`% but not quite as high as
-the optimal policy for that scenario (100%).  When adjustment costs are
-present but the policy assumes that they are not (red bars), we would
-expect the $NPV$ to be less than `r (1 - reduction) * 100`% of $NPV_0$
-(since that's as good as the optimal solution for this scenario can do).
-
-Figure 6 shows that across each penalty form $\Pi_1$, $\Pi_2$ & $\Pi_3$,
-the economic impact of ignoring adjustment costs when they are present
-is higher than accounting for them when they are absent. This holds even
-after accounting for effect described above: the red bars are consistently
-well below the `r (1-reduction)*100`% of $NPV_0$, while the blue bars
-are barely below $NPV_0$ (a value of 1 on the vertical axis).  We also
-see that the impacts on net present value of the fishery of incorrectly
-assuming or ignoring policy adjustment costs are most severe when these
-costs are assumed to scale quadratically with the size of the policy
-change being implemented ($\Pi_2$).  In the Supplementary Materials we
-show that pattern holds across different severity of adjustment costs
-(robust to choice of $c_i$), though the larger the adjustment cost,
-the greater the difference between these two errors.
+Figure 6 shows that across each penalty form \(\Pi_1\), \(\Pi_2\) \&
+\(\Pi_3\), the economic impact of ignoring adjustment costs when they
+are present is higher than accounting for them when they are absent.
+This holds even after accounting for effect described above: the red
+bars are consistently well below the 75\% of \(NPV_0\), while the blue
+bars are barely below \(NPV_0\) (a value of 1 on the vertical axis). We
+also see that the impacts on net present value of the fishery of
+incorrectly assuming or ignoring policy adjustment costs are most severe
+when these costs are assumed to scale quadratically with the size of the
+policy change being implemented (\(\Pi_2\)). In the Supplementary
+Materials we show that pattern holds across different severity of
+adjustment costs (robust to choice of \(c_i\)), though the larger the
+adjustment cost, the greater the difference between these two errors.
 
@@
 
-Discussion
-==========
+\section{Discussion}\label{discussion}
 
@@
 variations in ecological conditions with the increased transaction costs
-involved. As a first step towards exploring these ideas, we revisited
-a classic problem from bioeconomics concerning the optimal management
-of a fish stock subject to stochastically varying recruitment [@Reed1979; @Clark2010]. 
-We examined how optimal policy recommendations -- here
+involved. As a first step towards exploring these ideas, we revisited a
+classic problem from bioeconomics concerning the optimal management of a
+fish stock subject to stochastically varying recruitment (Reed 1979,
+Clark 2010). We examined how optimal policy recommendations -- here
 annual catch quotas -- changed when accounting for costs associated with
@@
 recommendations would be for the exploited population. We also compared
-how the value of the fishery is affected by managers either under-
-or overestimating the importance of policy adjustment costs of this type.
+how the value of the fishery is affected by managers either under- or
+overestimating the importance of policy adjustment costs of this type.
 
@@
 proposed policy changes would be empirically challenging. Recognizing
-this fact, we compared different plausible forms that
-these costs might take. We compared two cost structures where we assumed
-the magnitude of policy adjustment costs increased with the magnitude
-of the change in policy being proposed with an alternative formulation
-in which we assumed there was a fixed cost associated with making any
-change to current policy. While each formulation provides only
-very phenomenological representations of the policy-setting environment,
-we believe that each enables us to explore meaningful differences in how
-policy adjustment costs might operate. That being said, in the real world
-we might expect the different types of adjustment cost to operate in
-combination.
+this fact, we compared different plausible forms that these costs might
+take. We compared two cost structures where we assumed the magnitude of
+policy adjustment costs increased with the magnitude of the change in
+policy being proposed with an alternative formulation in which we
+assumed there was a fixed cost associated with making any change to
+current policy. While each formulation provides only very
+phenomenological representations of the policy-setting environment, we
+believe that each enables us to explore meaningful differences in how
+policy adjustment costs might operate. That being said, in the real
+world we might expect the different types of adjustment cost to operate
+in combination.
 
@@
 cost that we consider are between those that have a smoothing effect on
-annual quotas and those that do not. The few past studies that incorporate
-policy adjustment costs in models of fisheries or other environmental
-management contexts [@Feichtinger1994; @Wirl1999] have assumed costs of
-policy adjustment increased as a quadratic function of the magnitude of
-the policy change being proposed (analogous to $\Pi_2$ formulation). In
-effect, this means that small changes to annual quotas incur little
-extra cost, but large changes to annual quotas become disproportionately
-expensive to make. Including costs of this form smooths inter-annual
-variation in the recommended catch quotas. Also, the catches
-and remaining stock sizes corresponding to optimal management become more
-autocorrelated in time, because it takes the fishery multiple timesteps to harvest
-down peaks in abundance that follow large recruitment pulses. The effects
-of smoothing here are similar to those predicted when assuming the cost
-per unit effort is increasing in the amount of effort expended [@Brown1974;
-@Lewis1981; @McGough2009]; (see Supporting Information for a summary of the
+annual quotas and those that do not. The few past studies that
+incorporate policy adjustment costs in models of fisheries or other
+environmental management contexts (Feichtinger et al. 1994, Wirl 1999)
+have assumed costs of policy adjustment increased as a quadratic
+function of the magnitude of the policy change being proposed (analogous
+to \(\Pi_2\) formulation). In effect, this means that small changes to
+annual quotas incur little extra cost, but large changes to annual
+quotas become disproportionately expensive to make. Including costs of
+this form smooths inter-annual variation in the recommended catch
+quotas. Also, the catches and remaining stock sizes corresponding to
+optimal management become more autocorrelated in time, because it takes
+the fishery multiple timesteps to harvest down peaks in abundance that
+follow large recruitment pulses. The effects of smoothing here are
+similar to those predicted when assuming the cost per unit effort is
+increasing in the amount of effort expended (Brown 1974, Lewis 1981,
+McGough et al. 2009); (see Supporting Information for a summary of the
 relevant results) as opposed to associating extra costs with changes to
-policy *per se*. Smoothing effects of this type are what one might have
-expected when including policy adjustment costs.
+policy \emph{per se}. Smoothing effects of this type are what one might
+have expected when including policy adjustment costs.
 
-Standing in sharp contrast to these smoothing predictions is our
-finding that including policy adjustment costs can actually _increase_ the
+Standing in sharp contrast to these smoothing predictions is our finding
+that including policy adjustment costs can actually \emph{increase} the
 variability of quotas through time if there is a fixed cost associated
-with making any changes to current policy (e.g. costs of running relevant
-stakeholder meetings and public consultations on proposed policy changes,
-$\Pi_3$). With this formulation, as stock sizes vary in response to
-recruitment, the fishery manager must balance the cost of brokering
-a policy change with the cost in forgone fisheries revenue from not
-responding to favorable recruitment pulses. The optimal policy involves
-ignoring small variations in recruitment, but then assigns a larger quota
-when particularly strong recruitment years arise than would have been
-the case in the absence of policy adjustment costs. The other functional
-form we consider, in which the costs of policy adjustment scale linearly
-with the size of the adjustment ($\Pi_1$), has less obvious effects on
-optimal policies. Interestingly, it is this structure that
-most frequently produces stretches of strictly positive but unchanging
-quotas of the type most commonly encountered in real world applications.
+with making any changes to current policy (e.g.~costs of running
+relevant stakeholder meetings and public consultations on proposed
+policy changes, \(\Pi_3\)). With this formulation, as stock sizes vary
+in response to recruitment, the fishery manager must balance the cost of
+brokering a policy change with the cost in forgone fisheries revenue
+from not responding to favorable recruitment pulses. The optimal policy
+involves ignoring small variations in recruitment, but then assigns a
+larger quota when particularly strong recruitment years arise than would
+have been the case in the absence of policy adjustment costs. The other
+functional form we consider, in which the costs of policy adjustment
+scale linearly with the size of the adjustment (\(\Pi_1\)), has less
+obvious effects on optimal policies. Interestingly, it is this structure
+that most frequently produces stretches of strictly positive but
+unchanging quotas of the type most commonly encountered in real world
+applications.
 
@@
 such different dynamics suggests that researchers constructing fisheries
-economics models should proceed cautiously when choosing how to represent
-these costs. However, in our own experience, we have found that while
-modeling studies sometimes mention policy adjustment costs when motivating
-model assumptions [@Brown1974; @Lewis1981; @Feichtinger1994; @Wirl1999; @McGough2009],
-they rarely provide much justification
-for the choice of functional form used or test the sensitivity of any
-conclusions drawn to alternative specifications. Indeed, we were surprised
-to find such clear differences between the functional forms, because
-we anticipated that the limiting case of increasing policy adjustment
-costs within each functional form should be the same, namely a constant
-annual quota that does not change through time.
+economics models should proceed cautiously when choosing how to
+represent these costs. However, in our own experience, we have found
+that while modeling studies sometimes mention policy adjustment costs
+when motivating model assumptions (Brown 1974, Lewis 1981, Feichtinger
+et al. 1994, Wirl 1999, McGough et al. 2009), they rarely provide much
+justification for the choice of functional form used or test the
+sensitivity of any conclusions drawn to alternative specifications.
+Indeed, we were surprised to find such clear differences between the
+functional forms, because we anticipated that the limiting case of
+increasing policy adjustment costs within each functional form should be
+the same, namely a constant annual quota that does not change through
+time.
 
-We also compared the efficiency costs that would result from failing
-to account for policy adjustment costs, if they are present, with those
-involved in assuming them when in fact they are absent. The results
-of this comparison were not sensitive to the particular form of policy
+We also compared the efficiency costs that would result from failing to
+account for policy adjustment costs, if they are present, with those
+involved in assuming them when in fact they are absent. The results of
+this comparison were not sensitive to the particular form of policy
 adjustment costs assumed. Instead, we always found the efficiency costs
@@
 direct cost associated with each quota change. Second there is a cost in
-foregone revenue from missed catches when not following what would be the
-optimal policy if quotas were free to track recruitment variability. Our
-finding that it is more costly to ignore policy adjustment costs when
-they are present arises because the first, more direct, cost contribution
-here is the larger.
+foregone revenue from missed catches when not following what would be
+the optimal policy if quotas were free to track recruitment variability.
+Our finding that it is more costly to ignore policy adjustment costs
+when they are present arises because the first, more direct, cost
+contribution here is the larger.
 
 Assuming an adjustment cost exists when in fact it is absent is not the
-same as using the wrong functional form when it is present.  In the supplement
-we show that choice of the functional form makes a significant
-difference.  We show it can be better to ignore policy costs than to derive a 
-policy based on assuming the wrong functional form.  This result further
-underscores the importance of modelers using caution when seeking to account
-for these costs. Assuming an arbitrary form in order to capture the influence
-of adjustment costs is thus unlikely to be instructive.
+same as using the wrong functional form when it is present. In the
+supplement we show that choice of the functional form makes a
+significant difference. We show it can be better to ignore policy costs
+than to derive a policy based on assuming the wrong functional form.
+This result further underscores the importance of modelers using caution
+when seeking to account for these costs. Assuming an arbitrary form in
+order to capture the influence of adjustment costs is thus unlikely to
+be instructive.
 
-As with any modeling analysis, our formulation makes many assumptions. For
-example, we assume that the fishery in question is being optimally managed
-by a policymaker who acts as the "sole owner" of the stock. This approach
-is different to models that assume fisheries are not well managed,
-e.g. by assuming regulated open access conditions [@Homans1997],
-or models that derive policy recommendations endogenously by modeling strategic 
-interactions between different stakeholders [@Kaitala1993; @Laukkanen2003].
-As such, we anticipate that our approach will be more relevant to
-some fisheries, particularly domestic fisheries in developed countries
-that are subject to relatively strong regulatory regimes, than to others
-(e.g., artisanal fisheries that are subject to weaker regulation). To
-focus on the effects of policy adjustment costs, we focused narrowly
-on the basic model specification of @Reed1979 and examined how the
-predictions of this classic problem were changed by introducing policy
-adjustment costs of different forms. However, there have been many
-elaborations on Reed's basic approach that increase the realism of
-the optimization models involved by relaxing other assumptions (see for
-example @Sethi2005; @Singh2006; @McGough2009).
+As with any modeling analysis, our formulation makes many assumptions.
+For example, we assume that the fishery in question is being optimally
+managed by a policymaker who acts as the ``sole owner'' of the stock.
+This approach is different to models that assume fisheries are not well
+managed, e.g.~by assuming regulated open access conditions (Homans and
+Wilen 1997), or models that derive policy recommendations endogenously
+by modeling strategic interactions between different stakeholders
+(Kaitala 1993, Laukkanen 2003). As such, we anticipate that our approach
+will be more relevant to some fisheries, particularly domestic fisheries
+in developed countries that are subject to relatively strong regulatory
+regimes, than to others (e.g., artisanal fisheries that are subject to
+weaker regulation). To focus on the effects of policy adjustment costs,
+we focused narrowly on the basic model specification of Reed (1979) and
+examined how the predictions of this classic problem were changed by
+introducing policy adjustment costs of different forms. However, there
+have been many elaborations on Reed's basic approach that increase the
+realism of the optimization models involved by relaxing other
+assumptions (see for example Sethi et al. (2005); Singh et al. (2006);
+McGough et al. (2009)).
 
-One obvious research avenue suggested by our models is that of empirically
-estimating costs of policy adjustment. A direct estimation approach
-could quantify some sources of policy adjustment costs, e.g. costs to
-processing plants that arise from having more variable catches. However,
-other more intangible sources of policy adjustment costs, e.g. preferences
-of policymakers or different stakeholders for less variable quotas,
-might be missed. An alternative, more holistic, approach would be to
-apply revealed preference methods to fisheries management agencies
-themselves, in the tradition of [@McFadden1975; @McFadden1976]. Such an analysis
-would involve comparing quotas that were set relative to stock sizes as
-they were estimated at the time each management decision was taken to
-try to infer what objective managers were maximizing.
+One obvious research avenue suggested by our models is that of
+empirically estimating costs of policy adjustment. A direct estimation
+approach could quantify some sources of policy adjustment costs,
+e.g.~costs to processing plants that arise from having more variable
+catches. However, other more intangible sources of policy adjustment
+costs, e.g.~preferences of policymakers or different stakeholders for
+less variable quotas, might be missed. An alternative, more holistic,
+approach would be to apply revealed preference methods to fisheries
+management agencies themselves, in the tradition of (McFadden 1975,
+1976). Such an analysis would involve comparing quotas that were set
+relative to stock sizes as they were estimated at the time each
+management decision was taken to try to infer what objective managers
+were maximizing.
 
@@
 collapse. Examining risks of stock collapse is not possible with the
-Reed model formulation that we followed here but would be worthwhile
-in light of our finding that the variance and autocorrelation in stock
+Reed model formulation that we followed here but would be worthwhile in
+light of our finding that the variance and autocorrelation in stock
 sizes through time can be affected when accounting for costs of policy
-adjustment. Both are properties known in other modeling settings to
-be associated with changes to the risk of extinction or of transitions
-between alternative stable states [@Scheffer2009]. This highlights the risk
-that changes in management policies can either mimic or mask such possible
-early warning signs of sudden transitions, and points to another way
-in which more context is needed before such approaches can be useful to
-management [@Boettiger2013].
+adjustment. Both are properties known in other modeling settings to be
+associated with changes to the risk of extinction or of transitions
+between alternative stable states (Scheffer et al. 2009). This
+highlights the risk that changes in management policies can either mimic
+or mask such possible early warning signs of sudden transitions, and
+points to another way in which more context is needed before such
+approaches can be useful to management (Boettiger et al. 2013).
 
-When facing highly variable ecological systems, how often should
-natural resource managers respond? A highly interventionist strategy
-would track ecosystem variation very closely. Alternatively, a manager
-might choose only to take action or change policy only when conditions
-look very different to those previously experienced. We took a modeling
-approach to begin to explore these ideas. Specifically, we focused on
-a well-known problem from fisheries management and examined how optimal
-management recommendations changed when we accounted for costs associated
-with frequently changing management decisions. While we focused on a
-fisheries context, our findings would be relevant to many other settings
-where natural resource managers revisit management decisions through
-time in light of ecological variability, including game management,
-management of instream flow rates, fire management, habitat restoration,
-and managing for endangered species. The analyses that
-we present can also be thought of as providing a temporal counterpart
-to discussions about the spatial scale over which ecosystem
+When facing highly variable ecological systems, how often should natural
+resource managers respond? A highly interventionist strategy would track
+ecosystem variation very closely. Alternatively, a manager might choose
+only to take action or change policy only when conditions look very
+different to those previously experienced. We took a modeling approach
+to begin to explore these ideas. Specifically, we focused on a
+well-known problem from fisheries management and examined how optimal
+management recommendations changed when we accounted for costs
+associated with frequently changing management decisions. While we
+focused on a fisheries context, our findings would be relevant to many
+other settings where natural resource managers revisit management
+decisions through time in light of ecological variability, including
+game management, management of instream flow rates, fire management,
+habitat restoration, and managing for endangered species. The analyses
+that we present can also be thought of as providing a temporal
+counterpart to discussions about the spatial scale over which ecosystem
 management.
 
-Acknowledgements
-================
+\section{Acknowledgements}\label{acknowledgements}
 
-This work was assisted through participation in "Pretty Darn Good Control"
-Investigative Workshop at the National Institute for Mathematical and
-Biological Synthesis, sponsored by the National Science Foundation through
-NSF Award #DBI-1300426, with additional support from The University of
-Tennessee, Knoxville.  The authors acknowledge helpful discussions and
-input from working group co-organizers Megan Donahue and Carl Toews, and
-participants Marie-Josee Fortin, Dan Ryan, Frank Doyle, Claire Paris,
-Iadine Chades and Mandy Karnauskas.  We also acknowledge the support of
-NSF Grant DBI-1306697 to CB and ARC DECRA (DE130100572) & the
-ARC Centre of Excellence for Environmental Decisions to MB.
+This work was assisted through participation in ``Pretty Darn Good
+Control'' Investigative Workshop at the National Institute for
+Mathematical and Biological Synthesis, sponsored by the National Science
+Foundation through NSF Award \#DBI-1300426, with additional support from
+The University of Tennessee, Knoxville. The authors acknowledge helpful
+discussions and input from working group co-organizers Megan Donahue and
+Carl Toews, and participants Marie-Josee Fortin, Dan Ryan, Frank Doyle,
+Claire Paris, Iadine Chades and Mandy Karnauskas. We also acknowledge
+the support of NSF Grant DBI-1306697 to CB and ARC DECRA (DE130100572)
+\& the ARC Centre of Excellence for Environmental Decisions to MB.
 
-# References
+\section*{References}\label{references}
+\addcontentsline{toc}{section}{References}
+
+Armsworth, P. R., and J. E. Roughgarden. 2003. The economic value of
+ecological stability. Proceedings of the National Academy of Sciences of
+the United States of America 100:7147--51.
+
+Armsworth, P. R., B. A. Block, J. Eagle, and J. E. Roughgarden. 2010.
+The role of discounting and dynamics in determining the economic
+efficiency of time-area closures for managing fishery bycatch.
+Theoretical Ecology.
+
+Biais, G. 1995. An evaluation of the policy of fishery resources
+management by TACs in European Community waters from 1983 to 1992.
+Aquatic Living Resources 8:241--251.
+
+Boettiger, C. 2015. An introduction to Docker for reproducible research,
+with examples from the R environment. ACM SIGOPS Operating Systems
+Review 49:71--79.
+
+Boettiger, C., N. Ross, and A. Hastings. 2013. Early warning signals:
+the charted and uncharted territories. Theoretical Ecology.
+
+Brown, G. 1974. An optimal program for managing common property
+resources with congestion externalities. Journal of Political Economy.
+
+Clark, C. W. 2010. Mathematical Bioeconomics: The Mathematics of
+Conservation. Third editions. Wiley; Sons, Hoboken, NJ, USA.
+
+Clark, C. W., and M. Mangel. 2000. Dynamic state variable models in
+ecology. Oxford University Press, Oxford.
+
+Durrett, R., and S. A. Levin. 1994. The importance of being discrete
+(and spatial). Theoretical Population Biology 46:363--394.
+
+Feichtinger, G., A. Novak, and F. Wirl. 1994. Limit cycles in
+intertemporal adjustment models. Journal of Economic Dynamics and
+Control 18:353--380.
+
+Halpern, B. S., C. White, S. E. Lester, C. Costello, and S. D. Gaines.
+2011. Using portfolio theory to assess tradeoffs between return from
+natural capital and social equity across space. Biological Conservation
+144:1499--1507.
+
+Homans, F. R., and J. Wilen. 1997. A model of regulated open access
+resource use. JEEM 32:1--21.
+
+International Commission for the Conservation of Atlantic Tunas (ICCAT).
+2009. Report of the 2008 ICCAT bluefin stock assessment session. ICCAT
+Collective Volume of Scientific Papers 64:1--352.
+
+Kaitala, V. 1993. Equilibria in a stochastic resource management game
+under imperfect information. European Journal of Operational Research
+71:439--453.
+
+Laukkanen, M. 2003. Cooperative and non-cooperative harvesting in a
+stochastic sequential fishery. Journal of Environmental Economics and
+Management 45:454--473.
+
+Lewis, T. R. 1981. Exploitation of a renewable resource under
+uncertainty. The Canadian Journal of Economics 14:422.
+
+Ludwig, D. 1980. Harvesting strategies for a randomly fluctuating
+population. Journal du Conseil 39:168--174.
+
+Mangel, M., and C. W. Clark. 1988. Dynamic modeling in behavioral
+ecology. (J. Krebs and T. Clutton-Brock, Eds.). Princeton University
+Press, Princeton.
+
+McFadden, D. 1975. The revealed preferences of a government bureaucracy:
+Theory. The Bell Journal of Economics 6:401.
+
+McFadden, D. 1976. The revealed preferences of a government bureaucracy:
+Empirical evidence. The Bell Journal of Economics 7:55.
+
+McGough, B., P. A. J., and C. Costello. 2009. Optimally managing a
+stochastic renewable resource under general economic conditions. The
+B.E. Journal of Economic Analysis \& Policy 9:1--31.
+
+Neubert, M. G. 2003. Marine reserves and optimal harvesting. Ecology
+Letters 6:843--849.
+
+Patterson, K. 2007. Social resistance to the obvious good: A review of
+responses to a proposal for regulation of european fisheries. American
+Fisheries Society Symposium:587--596.
+
+Patterson, K., and M. Resimont. 2007. Change and stability in landings:
+the responses of fisheries to scientific advice and TACs. ICES Journal
+of Marine Science 64:714--717.
+
+Porch, C. E. 2005. The sustainability of western Atlantic bluefin tuna:
+a warm-blooded fish in a hot-blooded fishery. Bulletin of Marine Science
+76:363--384.
+
+Reed, W. J. 1974. A stochastic model for the economic management of a
+renewable animal resource. Mathematical Biosciences 22:313--337.
+
+Reed, W. J. 1979. Optimal escapement levels in stochastic and
+deterministic harvesting models. Journal of Environmental Economics and
+Management 6:350--363.
+
+Safina, C. 1998. Song for the blue ocean: Encounters along the world's
+coasts. Henry Holt, New York.
+
+Sanchirico, J. N., M. D. Smith, and D. W. Lipton. 2008. An empirical
+approach to ecosystem-based fishery management. Ecological Economics
+64:586--596.
+
+Scheffer, M., J. Bascompte, W. A. Brock, V. Brovkin, S. R. Carpenter, V.
+Dakos, H. Held, E. H. van Nes, M. Rietkerk, and G. Sugihara. 2009.
+Early-warning signals for critical transitions. Nature 461:53--9.
+
+SEDAR. 2013. SEDAR 36 stock assessment report: south Atlantic snowy
+grouper. Page 146. SEDAR, North Charleston SC.
+
+Sethi, G., C. Costello, A. Fisher, M. Hanemann, and L. Karp. 2005.
+Fishery management under multiple uncertainty. Journal of Environmental
+Economics and Management 50:300--318.
+
+Singh, R., Q. Weninger, and M. Doyle. 2006. Fisheries management with
+stock growth uncertainty and costly capital adjustment. Journal of
+Environmental Economics and Management 52:582--599.
+
+Sissenwine, M. P., P. M. Mace, J. E. Powers, and G. P. Scott. 1998. A
+Commentary on western Atlantic bluefin tuna assessments. Transactions of
+the American Fisheries Society 127:838--855.
+
+Spulber, D. F. 1982. Adaptive harvesting of a renewable resource and
+stable equilibrium. Pages 117--139 \emph{in} L. Mirman and D. Spulber,
+editors. Essays in the economics of renewable resources. North-Holland
+Publishing, Amsterdam.
+
+Walters, C. J. 1978. Some dynamic programming applications in fisheries
+management. \emph{in} J. Petkau, editor. Dynamic programming and its
+applications. Academic Press.
+
+Wirl, F. 1999. Complex, dynamic environmental policies. Resource and
+Energy Economics 21:19--41.
+\end{flushleft}
+
+\end{document}

### 2015-05-26 manuscripts/manuscript.Rmd
working through minor manuscript edits

@@
 Such patterns of variable stocks managed
-under far less variable quotas are extremely common; for instance, 
-in the management of south Atlantic snowy grouper (_Epinephelus niveatus_) 
+under far less variable quotas are extremely common, as in the instance of 
+the management of south Atlantic snowy grouper (_Epinephelus niveatus_) 
 shown in the righthand panels [@SEDAR2013]. Though the stock assessment

### 2015-05-27 manuscripts/manuscript.Rmd
tweaks

@@
 examine the implications of policy adjustment costs for risks of stock
-collapse. Examining risks of stock collapse is not possible with the
-Reed model formulation that we followed here but would be worthwhile
+collapse. This includes models with larger stochasticity as well as model
+formulations that can permit alternative stable states.
+Examining risks of stock collapse is not possible with the
+Reed model formulation that we followed here (both cases are inconsistent
+with the assumptions of @Reed1974) but would be worthwhile
 in light of our finding that the variance and autocorrelation in stock
@@
 participants Marie-Josee Fortin, Dan Ryan, Frank Doyle, Claire Paris,
-Iadine Chades and Mandy Karnauskas.  We also acknowledge the support of
+Iadine Chades and Mandy Karnauskas, as well as the two anonymous reviewers
+whose feedback strengthened this paper.  We also acknowledge the support of
 NSF Grant DBI-1306697 to CB and ARC DECRA (DE130100572) & the

### 2015-06-12 manuscripts/manuscript.Rmd
extending language on docker, zenodo archive

@@
 R code for implementing the dynamic programming algorithm in this context is
-provided as a supplementary R package to the paper, along with scripts for replicating 
+provided as a supplementary R package to the paper, [@zenodo], along with scripts for replicating 
 the analyses presented here. To address concerns about computational reproducibility [@Boettiger2015],

### 2015-06-12 manuscripts/supplement.Rmd
extending language on docker, zenodo archive

@@
 All code and data used in this analysis can be found under the project's GitHub repository: [https://github.com/cboettig/pdg_control](https://github.com/cboettig/pdg_control).
-A snapshot of this repository representing the precise versions of the code used in this analysis has been permanently archived in the scientific software and data repository Zenodo, managed by CERN; and should be referenced or cited using its assigned digital object identifer, doi:xxx.
+A snapshot of this repository representing the precise versions of the code used in this analysis has been permanently archived in the scientific software and data repository Zenodo, managed by CERN; and should be referenced or cited using its assigned digital object identifier, doi:xxx.
 (This DOI is also clearly linked from the GitHub repository).
@@
 The intent is not to provide a general-purpose software tool for this kind of analysis, but rather to rely on a standardized directory structure for representing complex projects.
-It is our hope that this facilates understanding, reproducibility, and further exploration of these results sensu [Gentleman & Temple Lang 2007](http://biostats.bepress.com/bioconductor/paper2/), but caution that additional software engineering would be required before any of this could be applied in a different context.
+It is our hope that this facilities understanding, reproducibility, and further exploration of these results sensu [Gentleman & Temple Lang 2004](http://biostats.bepress.com/bioconductor/paper2/), but caution that additional software engineering would be required before any of this could be applied in a different context.
 The functions provided are largely specific to the analyses presented here and may undocumented or incompletely documented.
@@
 
-All empirical or simulated data shown in the figures can also be found as tabular .csv files in this repository.
+All empirical or simulated data shown in the figures can also be found as tabular `.csv` files in this repository.
 
 ### Dependencies and machine images
+
+The package DESCRIPTION file lists the software dependencies required to run the included scripts.
+To facilitate portability and preservation of these dependencies, we also provide a machine image with all the necessary dependencies already installed which can be run on most common computer platforms using [Docker](http://docker.com).
+Our Docker image, `cboettig/pdg-control` can be freely downloaded from the Docker Hub, or built using the Dockerfile included in the package repository.
 

### 2015-06-21 manuscripts/manuscript.Rmd
add citation, fix scale (old uncommitted changes)

--- 2015-05-27 manuscripts/manuscript.Rmd
@@
 grouper <- read.csv("components/data/grouper.csv")
-
+library("scales")
 ex <- rbind(cbind(tuna, species="tuna"), cbind(grouper, species="snowy grouper"))
@@
   facet_wrap(variable~species, scales="free") + 
-  ylab("value (mt)") + theme_bw()
+  ylab("value (mt)") + theme_bw() + 
+  scale_x_continuous(breaks = pretty_breaks(n = 5))
 ```
@@
 R code for implementing the dynamic programming algorithm in this context is
-provided as a supplementary R package to the paper, along with scripts for replicating 
+provided as a supplementary R package to the paper, ([github.com/cboettig/pdg_control](https://github.com/cboettig/pdg_control)), along with scripts for replicating 
 the analyses presented here. To address concerns about computational reproducibility [@Boettiger2015],

### 2015-06-22 manuscripts/manuscript.Rmd
recompile docs, figures

@@
 
-```{r Figure_3, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.
+```{r Figure_3, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy under the different functional forms of adjustment costs.
 When costs vary linearly with the size of the adjustment ($\\Pi_1$), periods with no adjustment are more common than if adjustments were free.
@@
   facet_grid(penalty_fn~., labeller = labeller) + 
-  labs(x="time", y="stock size", title = "Example Harvest Dynamics")  +
+  labs(x="time", y="harvest", title = "Example Harvest Dynamics")  +
   scale_color_discrete(labels=c("Adjustment penalty", "No penalty"), name="") +
@@
 
-In the supplemental material, Figures S9-S12 illustrate that the 
-these qualitative patterns still hold at when the models are calibrated 
-to a reduction in NPV of 10% or 30%, though naturally the magnitude
-of the pattern is greater when the penalty is larger (e.g. 30% vs 10%).
+Figure 4 shows these qualitative patterns still hold at when the models are calibrated 
+to a range of different reductions in NPV, from 0% to 30%, though naturally the magnitude
+of the differences is greatest when the penalty is larger.
 
@@
 
-```{r Figure_6, fig.cap="Relative cost of ignoring adjustment costs when they are present ('ignoring', red) vs assuming the adjustment costs when they are absent ('assuming', blue), shown by penalty function over increasing magnitudes of cost.
+```{r Figure_6, fig.cap="Relative cost of ignoring adjustment costs when they are present ('ignoring', red) vs assuming the adjustment costs when they are absent ('assuming', blue).
 All values are relative to the cost free adjustment optimum, $NPV_0$.
-In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present.
-The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs.", dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE}
+In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present.Supplementary Figure S6 shows how the magnitude of this effect changes with the size of the reduction to $NPV$.", dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE}
 

### 2015-06-22 manuscripts/supplement.Rmd
update figures
recompile docs, figures

@@
 
-\renewcommand{\thefigure}{S\arabic{figure}}
 \appendix
+\renewcommand\thefigure{S\arabic{figure}}
 
@@
 
-```{r Figure_S1, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=5, fig.width=8, cache = fig.cache, dev=c("pdf", "svg", "png")}
+```{r Figure_S1, dependson="tidy", fig.cap="Example realization of optimal fish stock sizes under the different functional forms of adjustment costs, under the harvest policy dynamics shown in Figure 3 of the main text.", fig.height=5, fig.width=8, cache = fig.cache, dev=c("pdf", "svg", "png")}
 
@@
 ```{r}
+parallel = TRUE
+ncpu = parallel::detectCores()
+price = 10
+c0 = 30
+profit <- profit_harvest(price = price, c0 = c0, c1 = 0)
+#c2 <- exp(seq(0, log(41), length.out = 40))-1
+c2 <- seq(0, 40, length.out=100)
+reduction <- 0.25 
+seed <- 123                 # Random seed (replicable results)
+delta <- 0.05               # economic discounting rate
+OptTime <- 50               # stopping time
+gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
+sigma_g <- 0.2              # Noise in population growth
+reward <- 0                 # bonus for satisfying the boundary condition
+z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
+z_m <- function() 1         # No measurement noise, 
+z_i <- function() 1         # No implemenation noise
+f <- BevHolt                # Select the state equation
+pars <- c(1.5, 0.05)        # parameters for the state equation
+K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
+xT <- 0                     # boundary conditions
+x0 <- K
+x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
+h_grid <- seq(0.01, 0.8 * K, length = gridsize)
+
 source("components/vary_reduction.R")
 ```
+
+<!--
 
@@
 ```
+
+-->

### 2015-06-23 manuscripts/supplement.Rmd
figure tidying

--- 2015-06-12 manuscripts/supplement.Rmd
@@
 
-\renewcommand{\thefigure}{S\arabic{figure}}
+\makeatletter
+\renewcommand\appendix{\par
+  \setcounter{section}{0}%
+  \setcounter{subsection}{0}%
+  \setcounter{equation}{0}%
+  \setcounter{table}{0}%------------ << add
+  \setcounter{figure}{0}%----------- << add
+  \gdef\theequation{S\arabic{equation}}%
+  \gdef\thefigure{S\arabic{figure}}%
+  \gdef\thesection{S@section}%
+  \@addtoreset{equation}{section}%
+  \@addtoreset{table}{section}%----- << add
+  \@addtoreset{figure}{section}%---- << add
+}
+\makeatother
+
 \appendix
@@
 
-```{r Figure_S8, fig.cap="Effect of varying severity of adjustment costs on mismatches.
-Successive panels show increasing reduction of the net present value by increasing penalty coefficients: e.g.
-a policy in the first panel would lose only 10% (panel A) of its net present value to adjustment costs if it had the correct form of those costs, as determined by the choice of penalty coefficient.
-Plots structured as in figure 7, which corresponds to the fourth panel", dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE}
-ggplot(table2_long, aes(penalty.fn, value, fill = variable)) + 
-  geom_bar(stat="identity", position="dodge") + 
-  facet_wrap(~reduction, scales="free_y") +
-  scale_x_discrete(labels = c('L1_L2' = substitute(paste(Pi[1],"_", Pi[2])), 
-                              'L2_L1' =  substitute(paste(Pi[2],"_", Pi[1])),
-                              'L1_fixed' = substitute(paste(Pi[1],"_", Pi[3])), 
-                              'fixed_L1' =  substitute(paste(Pi[3],"_", Pi[1])),
-                              'fixed_L2' = substitute(paste(Pi[3],"_", Pi[2])), 
-                              'L2_fixed' =  substitute(paste(Pi[2],"_", Pi[3])))) + 
-  xlab("Penalty function")
-```
-
 ## Robustness to reduction level
@@
 ```{r}
+## Reset parameter values
+parallel = TRUE
+ncpu = parallel::detectCores()
+price = 10
+c0 = 30
+profit <- profit_harvest(price = price, c0 = c0, c1 = 0)
+c2 <- seq(0, 40, length.out=100)
+reduction <- 0.25 
+seed <- 123                 # Random seed (replicable results)
+delta <- 0.05               # economic discounting rate
+OptTime <- 50               # stopping time
+gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
+sigma_g <- 0.2              # Noise in population growth
+reward <- 0                 # bonus for satisfying the boundary condition
+z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
+z_m <- function() 1         # No measurement noise, 
+z_i <- function() 1         # No implemenation noise
+f <- BevHolt                # Select the state equation
+pars <- c(1.5, 0.05)        # parameters for the state equation
+K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
+xT <- 0                     # boundary conditions
+x0 <- K
+x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
+h_grid <- seq(0.01, 0.8 * K, length = gridsize)
+
+## Recompute
 source("components/vary_reduction.R")
@@
 
-Figures S9-S12 illustrate that the 
+Figures S8-S11 illustrate that the 
 these qualitative patterns still hold at when the models are calibrated 
@@
 
-```{r Figure_S9, dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE, fig.cap="Identical analysis to Figure 3 of the main text, but using a calibration corresponding to a 10% reduction in NPV.
+```{r Figure_S8, dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE, fig.cap="Identical analysis to Figure 3 of the main text, but using a calibration corresponding to a 10% reduction in NPV.
 This results in a less pronounced version of the same qualitative pattern."}
@@
 
-```{r Figure_S10, dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE, fig.cap="Identical analysis to Figure 3 of the main text, but using a calibration corresponding to a 30% reduction in NPV.
+```{r Figure_S9, dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE, fig.cap="Identical analysis to Figure 3 of the main text, but using a calibration corresponding to a 30% reduction in NPV.
 This results in a more pronounced version of the same qualitative pattern."}
@@
 
-```{r Figure_S11, dev=c("pdf", "svg", "png"), fig.width=5, fig.height=6, cache=FALSE, fig.cap="Identical analysis as in Figure 4 of the main text, but using a calibration to 10% reduction in NPV rather than 25%.
-The qualitatively similar pattern helps illustrate that these results are not specific to the value of the reduction chosen in the main text."}
-p4 <- ggplot(low$f4df, aes(x = penalty_fraction, fill=penalty_fn, col=penalty_fn)) + 
-  coord_cartesian(xlim = c(0, .3)) + 
-  scale_color_discrete(labels=relabel, name="cost model") + 
-  scale_fill_discrete(labels=relabel, name="cost model")
+```{r Figure_S10, fig.cap="Results as in Figure 5 of the main text, but using a net reduction of NPV equal to 10%.", fig.width=8, fig.height=6, dependson="histogram-calc", dev=c("pdf", "svg", "png"), cache=FALSE}
+fig5_dat <- low$dt5 %>% 
+  filter(penalty_fn=="L1") %>%
+  select(-penalty_fn) %>%
+  unite(dist, Assumption, variable, sep = " : ")
+labels <- c(expression(paste("Costs under ",  Pi[1])), 
+            expression(paste("Revenue under ", Pi[1])),
+            expression(paste("Cost under ", Pi[0])), 
+            expression(paste("Revenue under ", Pi[0])))
+ggplot(fig5_dat) + 
+  geom_density(aes(value, fill=dist, color=dist, lty=dist), alpha=0.5, size=1) +
+  scale_fill_discrete(name="", labels=labels) + 
+  scale_color_discrete(labels=labels, name="") + 
+   scale_linetype_discrete(labels=labels, name="") +
+  xlab("Realized NPV") + 
+  ylab("Probability density of revenue/cost")
 
-p4a <- p4 + 
-  stat_summary(aes(y=autocorrelation),
-               fun.y = mean, 
-               fun.ymin = function(x) mean(x) - sd(x), 
-               fun.ymax = function(x) mean(x) + sd(x), 
-               geom = "ribbon", alpha=0.3, colour=NA) +
-  stat_summary(aes(y=autocorrelation), fun.y = mean, geom = "line") + 
-  xlab("") + 
-  labs(title="Summary statistics under a 10% reduction in NPV")
-
-p4b <- p4 + 
-  stat_summary(aes(y=variance),
-               fun.y = mean, 
-               fun.ymin = function(x) mean(x) - sd(x), 
-               fun.ymax = function(x) mean(x) + sd(x), 
-               geom = "ribbon", alpha=0.3, colour=NA) +
-  stat_summary(aes(y=variance), fun.y = mean, geom = "line") +
-  xlab(expression(paste("Penalty size (as fraction of ", NPV[0], ")")))
-
-legend <- gtable_filter(ggplot_gtable(ggplot_build(p4a)), "guide-box")
-
-grid.arrange(do.call(arrangeGrob, 
-            lapply(list(p4a, p4b),
-                   function(x) x + theme_bw() + theme(legend.position="none"))),
-    legend,
-    ncol = 2,
-    widths = c(5,2))
 ```
 
-```{r Figure_S12, dev=c("pdf", "svg", "png"), fig.width=5, fig.height=6, cache=FALSE, fig.cap="Identical analysis as in Figure 4 of the main text, but using a calibration to 30% reduction in NPV rather than 25%.
-The qualitatively similar pattern helps illustrate that these results are not specific to the value of the reduction chosen in the main text."}
-p4 <- ggplot(high$f4df, aes(x = penalty_fraction, fill=penalty_fn, col=penalty_fn)) + 
-  coord_cartesian(xlim = c(0, .3)) + 
-  scale_color_discrete(labels=relabel, name="cost model") + 
-  scale_fill_discrete(labels=relabel, name="cost model")
+```{r Figure_S11, fig.cap="Results as in Figure 5, but using a net reduction equal to 30%", fig.width=8, fig.height=6, dependson="histogram-calc", dev=c("pdf", "svg", "png"), cache=FALSE}
+fig5_dat <- high$dt5 %>% 
+  filter(penalty_fn=="L1") %>%
+  select(-penalty_fn) %>%
+  unite(dist, Assumption, variable, sep = " : ")
+labels <- c(expression(paste("Costs under ",  Pi[1])), 
+            expression(paste("Revenue under ", Pi[1])),
+            expression(paste("Cost under ", Pi[0])), 
+            expression(paste("Revenue under ", Pi[0])))
+ggplot(fig5_dat) + 
+  geom_density(aes(value, fill=dist, color=dist, lty=dist), alpha=0.5, size=1) +
+  scale_fill_discrete(name="", labels=labels) + 
+  scale_color_discrete(labels=labels, name="") + 
+   scale_linetype_discrete(labels=labels, name="") +
+  xlab("Realized NPV") + 
+  ylab("Probability density of revenue/cost")
 
-p4a <- p4 + 
-  stat_summary(aes(y=autocorrelation),
-               fun.y = mean, 
-               fun.ymin = function(x) mean(x) - sd(x), 
-               fun.ymax = function(x) mean(x) + sd(x), 
-               geom = "ribbon", alpha=0.3, colour=NA) +
-  stat_summary(aes(y=autocorrelation), fun.y = mean, geom = "line") + 
-  xlab("") + 
-  labs(title="Summary statistics under a 30% reduction in NPV")
-
-p4b <- p4 + 
-  stat_summary(aes(y=variance),
-               fun.y = mean, 
-               fun.ymin = function(x) mean(x) - sd(x), 
-               fun.ymax = function(x) mean(x) + sd(x), 
-               geom = "ribbon", alpha=0.3, colour=NA) +
-  stat_summary(aes(y=variance), fun.y = mean, geom = "line") +
-  xlab(expression(paste("Penalty size (as fraction of ", NPV[0], ")")))
-
-legend <- gtable_filter(ggplot_gtable(ggplot_build(p4a)), "guide-box")
-
-grid.arrange(do.call(arrangeGrob, 
-            lapply(list(p4a, p4b),
-                   function(x) x + theme_bw() + theme(legend.position="none"))),
-    legend,
-    ncol = 2,
-    widths = c(5,2))
+write.csv(hist_dat, "components/data/figure5.csv")
 ```

### 2015-06-23 manuscripts/components/vary_reduction.R

@@ -121,18 +121,19 @@ dt3 <- dt %>%
 
 dt3$penalty_fn <- factor(dt3$penalty_fn, levels=c("L1", "L2", "fixed"))
 
+profits <- dt[, sum(profit_fishing), by=c('penalty_fn', 'replicate') ]
+costs <- dt[, sum(policy_cost), by=c('penalty_fn', 'replicate') ]
+reed_profits <- dt[, sum(profit_fishing_alt), by=c('penalty_fn', 'replicate') ]
+reed_costs <- dt[, sum(policy_cost_alt), by=c('penalty_fn', 'replicate') ]
+setnames(profits, "V1", "profits")
+setnames(reed_profits, "V1", "profits")
 
-## Figure 4
-stats_df %>% 
-  filter(variable != "cross.correlation") %>%
-  separate(variable, c("measurement", "statistic"), sep="\\.") %>%
-  filter(measurement == 'harvest') %>% 
-  spread(statistic, value) ->
-  f4df
+Reed <- cbind(reed_profits, costs = reed_costs$V1, Assumption = "No adjustment penalty") 
+Adj <- cbind(profits, costs = costs$V1, Assumption = "Adjustment penalty")
 
-f4df$penalty_fn <- factor(f4df$penalty_fn, levels = c("L1", "L2", "fixed"))
+hist_dat <- melt(rbind(Adj, Reed), id=c("penalty_fn", "replicate", "Assumption"))
 
-list(dt3 = dt3, f4df = f4df) 
+list(dt3 = dt3, dt5 = hist_dat) 
 
 }
 

### 2015-07-28 manuscripts/manuscript.Rmd
figure tidying
formatting for final submission

@@
   - name: Carl Boettiger
-    affiliation: cstar
-    email: cboettig (at) gmail.com
+    affiliation: UCB 
+    email: cboettig (at) berkeley.edu 
     footnote: Corresponding author
@@
 address: 
-  - code: cstar
+  - code: UCB
     address: | 
-      Center for Stock Assessment Research,
-      110 Shaffer Rd,
-      Santa Cruz, CA 95050, USA 
+      Department of Environmental Science, Policy and Management,
+      University of California, Berkeley,
+      130 Mulford Hall \#3114,
+      Berkeley, CA 94720-3114, USA
   - code: UCD
@@
 margin=2.54cm,rmargin=2.54cm]
+endfloat: true
+doublespacing: true
 
@@
 R code for implementing the dynamic programming algorithm in this context is
-provided as a supplementary R package to the paper, ([github.com/cboettig/pdg_control](https://github.com/cboettig/pdg_control)), along with scripts for replicating 
+provided as a supplementary R package to the paper, ([github.com/cboettig/pdg_control](https://github.com/cboettig/pdg_control), @zenodo_copy), along with scripts for replicating 
 the analyses presented here. To address concerns about computational reproducibility [@Boettiger2015],
@@
 to a range of different reductions in NPV, from 0% to 30%, though naturally the magnitude
-of the differences is greatest when the penalty is larger.
+of the differences is greatest when the penalty is larger. Note that the supplementary material provide
+further evidence that these patterns are independent of the exact reduction shown by providing
+results analogous to Figure 3 (A8, A9) and Figure 5 (A10, A11), and Figure 6 (A6).
 
@@
 All values are relative to the cost free adjustment optimum, $NPV_0$.
-In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present.Supplementary Figure S6 shows how the magnitude of this effect changes with the size of the reduction to $NPV$.", dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE}
+In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present.Supplementary Figure A6 shows how the magnitude of this effect changes with the size of the reduction to $NPV$.", dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE}
 

### 2015-07-28 manuscripts/supplement.Rmd
formatting for final submission

@@
 
-layout: review,12pt
-linenumbers: true
+layout: preprint,12pt
+linenumbers: false
+endfloat: false
 
@@
   \setcounter{figure}{0}%----------- << add
-  \gdef\theequation{S\arabic{equation}}%
-  \gdef\thefigure{S\arabic{figure}}%
-  \gdef\thesection{S@section}%
+  \gdef\theequation{A\arabic{equation}}%
+  \gdef\thefigure{A\arabic{figure}}%
+  \gdef\thesection{A@section}%
   \@addtoreset{equation}{section}%
@@
 All code and data used in this analysis can be found under the project's GitHub repository: [https://github.com/cboettig/pdg_control](https://github.com/cboettig/pdg_control).
-A snapshot of this repository representing the precise versions of the code used in this analysis has been permanently archived in the scientific software and data repository Zenodo, managed by CERN; and should be referenced or cited using its assigned digital object identifier, doi:xxx.
-(This DOI is also clearly linked from the GitHub repository).
+A snapshot of this repository representing the precise versions of the code used in this analysis has been permanently archived in the scientific software and data repository Zenodo, managed by CERN; and should be referenced or cited using its assigned digital object identifier, doi:10.5281/zenodo.21416  (This DOI is also clearly linked from the GitHub repository).
 
@@
 ```
+
+\newpage
+
+# References

### 2015-08-05 manuscripts/manuscript.Rmd
number supplement with A\d not S\d

@@
     keep_tex: true
+    includes:
+      after_body: appendix_description.tex
+
 ---
@@
 show cases where $p=$ `r price`, $\delta=$ `r delta` and $c_0=$ `r c0`.
-In the supplement we illustrate that the qualitative patterns observed
+In Appendix A we illustrate that the qualitative patterns observed
 here are not sensitive to the specific choices of these parameter values.
@@
 
-In the Supplementary Material, we compare our results with more
+In Appendix A, we compare our results with more
 conventional fisheries economic formulation in which additional costs are
@@
 reduction, we conduct the same analysis with a 10% and 30% reduction rate as well.
-The corresponding figures can be found in the Supplemental Materials.
+The corresponding figures can be found in Appendix A.
 
@@
 impact the dynamics of the optimal harvest policy. Corresponding stock
-sizes can be seen in the supplement.  Each panel is generated against the
+sizes can be seen in Appendix A.  Each panel is generated against the
 same sequence of environmental variability so that they can be compared
@@
 to a range of different reductions in NPV, from 0% to 30%, though naturally the magnitude
-of the differences is greatest when the penalty is larger. Note that the supplementary material provide
+of the differences is greatest when the penalty is larger. Note that results shown in Appendix A provide
 further evidence that these patterns are independent of the exact reduction shown by providing
@@
 fig5_caption <- paste("Distribution of revenues from fishing and costs paid to adjustment.
-Plot shows distributions for the linear costs structure ($\\Pi_1$) only, alternate penalties can be found in the supplementary materials.
+Plot shows distributions for the linear costs structure ($\\Pi_1$) only, alternate penalties can be found in the Appendix A.
 Dockside revenues are always higher than adjustment costs.
@@
 All values are relative to the cost free adjustment optimum, $NPV_0$.
-In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present.Supplementary Figure A6 shows how the magnitude of this effect changes with the size of the reduction to $NPV$.", dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE}
+In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present.
+Appendix A, Figure A6 shows how the magnitude of this effect changes with the size of the reduction to $NPV$.", dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE}
 
@@
 costs are assumed to scale quadratically with the size of the policy
-change being implemented ($\Pi_2$).  In the Supplementary Materials we
+change being implemented ($\Pi_2$).  In Appendix A we
 show that pattern holds across different severity of adjustment costs
@@
 the optimization altogether.  We illustrate several of these mismatch
-errors in the Supplementary Material.
+errors in Appendix A.
 
@@
 per unit effort is increasing in the amount of effort expended [@Brown1974;
-@Lewis1981; @McGough2009]; (see Supporting Information for a summary of the
+@Lewis1981; @McGough2009]; (see Appendix A for a summary of the
 relevant results) as opposed to associating extra costs with changes to
@@
 Assuming an adjustment cost exists when in fact it is absent is not the
-same as using the wrong functional form when it is present.  In the supplement
+same as using the wrong functional form when it is present.  In Appendix A
 we show that choice of the functional form makes a significant

### 2015-08-05 manuscripts/supplement.Rmd
number supplement with A\d not S\d

@@
     keep_tex: true
+  html_document: 
+    toc: true
+    toc_depth: 2
+    number_sections: true
 ---
@@
 
-# Supplementary material #
+# Appendix A #
 
@@
 
-Figure S1 shows the corresponding stock dynamics for the replicates illustrated in Figure 3 of the main text.
+Figure A1 shows the corresponding stock dynamics for the replicates illustrated in Figure 3 of the main text.
 The impact of the adjustment cost on the stock dynamics is less dramatic than it is on the harvest dynamics, due to the stochastic growth in stock sizes and the sequence in which the steps are applied: stock values are assessed without error, then an optimal harvest is determined (using the pre-computed optimal policy based on both the stock assessment and the previous harvest, to account for possible adjustment costs), and then the stock that escapes harvesting recruits stochastically to set the population size for the next year.
 
-Though this results in an effect that is less pronounced, the stock dynamics of Figure S1 reflect the same general trends observed in Main text Figure 3; e.g.
+Though this results in an effect that is less pronounced, the stock dynamics of Figure A1 reflect the same general trends observed in Main text Figure 3; e.g.
 the fixed fee $\Pi_3$ results in the most exaggerated fluctuations in the stock sizes.
@@
 
-Figure S2 shows the same summary statistics illustrating the trends
+Figure A2 shows the same summary statistics illustrating the trends
 of increasing adjustment costs on the _stock_ dynamics, instead of the
@@
 Figure 3 of the main text shows only a single stochastic realization.  Here in
-Figure S3 we provide a sample of further realizations (including both
+Figure A3 we provide a sample of further realizations (including both
 stock and harvest dynamics).
@@
 
-Figure S4 shows that adding quadratic terms to the cost of fishing effort directly, as in @Lewis1981 or @McGough2009, results in a similar smoothing effect as we observe in quadratic adjustment costs ($\Pi_2$), which contrasts sharply with the patterns we observe in other functional forms.
+Figure A4 shows that adding quadratic terms to the cost of fishing effort directly, as in @Lewis1981 or @McGough2009, results in a similar smoothing effect as we observe in quadratic adjustment costs ($\Pi_2$), which contrasts sharply with the patterns we observe in other functional forms.
 This case corresponds to a profit function defined as:
@@
 
-Figure S5 extends Figure 5 of the main text across all three functional forms of adjustment costs, $\Pi_{1-3}$.
+Figure A5 extends Figure 5 of the main text across all three functional forms of adjustment costs, $\Pi_{1-3}$.
 To reduce over-plotting of Figure 5 we have also separated the distributions of dockside revenue and adjustment fees by scenario, such that the top row shows the distributions when the policy accounts for adjustment costs, and the bottom shows the policy when it does not (that is, the original @Reed1979 model applied to the scenario of costly adjustment).
@@
 
-Figure S6 extends the results shown in Figure 6 across different severities of adjustment cost, totaling from 10% up to 25% of the $NPV$ of the stock.
+Figure A6 extends the results shown in Figure 6 across different severities of adjustment cost, totaling from 10% up to 25% of the $NPV$ of the stock.
 While the same qualitative pattern is observed in all cases, it is strongest in the higher penalties.
@@
 may not be worse than ignoring the presence of policy costs all together.
-Figure S7 considers several such cases.  The X axis labels indicate
+Figure A7 considers several such cases.  The X axis labels indicate
 first which policy is being used to drive the harvest decisions, and
@@
 These patterns hold across the different size reductions shown (from 10%
-to 25%, Figure S8 panels a-d respectively), though net present value becomes negative under the quadratic
+to 25%, Figure A8 panels a-d respectively), though net present value becomes negative under the quadratic
 form for the larger penalties as costs paid for adjustments exceed
@@
 
-Figures S8-S11 illustrate that the 
+Figures A8-A11 illustrate that the 
 these qualitative patterns still hold at when the models are calibrated 

### 2015-08-05 manuscripts/components/vary_reduction.R

@@ -1,3 +1,36 @@
+## ----reed--------------------------
+SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
+opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
+                     profit, delta, reward=reward)
+
+
+## ----fees----------------------------------------------------------------
+L1 <- function(c2) function(h, h_prev)  c2 * abs(h - h_prev) 
+fixed <-  function(c2) function(h, h_prev) c2 * as.numeric( !(h == h_prev) )
+L2 <- function(c2) function(h, h_prev)  c2 * (h - h_prev) ^ 2
+none <- function(h, h_prev)  0
+penaltyfns <- list(L2=L2, L1=L1, fixed=fixed)
+
+
+
+
+## ----parallel, include=FALSE---------------------------------------------
+sfInit(cpu=ncpu, parallel=parallel)
+sfLibrary(pdgControl)
+sfExportAll()
+
+##### ANALYSIS #############
+
+
+## Apples to Apples comparison (Figure 2)
+policies <- lapply(penaltyfns, function(penalty){
+  sfLapply(c2, function(c2){
+    policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
+                           profit, delta, reward, penalty = penalty(c2))
+  }
+  )
+})
+
 
 
 robust_reduction <- function(reduction){
